### 2015-06-23 draft.tex
First commit

%%%% Various options for document class.
%%\documentclass[usenatbib, a4paper, 11pt]{aastex}
%%\documentclass[preprint, 11pt, a4paper]{aastex}
%%\documentclass[twocolum]{revtex4}
%%\documentclass{report}
\documentclass[useAMS,usenatbib]{mn2e_x}

%\usepackage{psfig,morefloats,url}
%use preprint2 for 2 columns paper.

%% declare any packages used
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage{color}
\usepackage{pdfpages}
\usepackage{appendix}
\usepackage{subfigure}
%\usepackage{epsfig}
%\usepackage[dvips]{color}
%\usepackage{aabib}

%\marginparwidth = 25pt
\citestyle{aa}
\addtolength{\topmargin}{-.5in}
%\addtolength{\bottommargin}{-1in}
%% This command added as margins are wrong in mn2e, it appears. 
%% Not needed for other classes
\usepackage{float}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
%% define bibstyle and other definitions
\bibliographystyle{aabib}
%% renew commands
%%\renewcommand{\labelitemi}{$.$}

%% Codes
\def\py{\textsc{Python} }
\def\tar{\textsc{Tardis} }
\def\cld{\textsc{Cloudy} }
\def\agn{\textsc{Agnspec} }

%% Lines and ions
\def\civ{C~\textsc{iv}}
\def\nv{N~\textsc{v}}
\def\heii{He~\textsc{ii}}
\def\ovi{O~\textsc{vi}}
\def\la{Ly$\alpha$}
\def\ha{H$\alpha$}

%% Journal definitions
\def\araa{ARAA}
\def\nat{Nature}
\def\apjl{ApJ Letters}
\def\aapr{AAPR}
\def\ssr{SSR}
\def\apj{ApJ}
\def\pasp{PASP}
\def\aap{A\&A}
\def\mnras{MNRAS}
\def\aj{AJ}
\def\rmxaa{RMXAA}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%          TITLE AND AUTHORS
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title
{
The effect of clumpy outflows
and disk anisotropy on quasar unification scenarios
}

% [Matthews, J.]
% \author[Matthews, J.]{James Matthews \\
% {\sl  Supervisor: Prof. Christian Knigge} \\
% {\sl School of Physics \& Astronomy, University of Southampton,
%   Southampton, SO17 1BJ, UK}}

\author[Matthews et al.]{J.~H.~Matthews$^1$\thanks{jm8g08@soton.ac.uk}, C.~Knigge,$^1$
N.~Higginbottom,$^1$ K.~S.~Long,$^2$ S.~A.~Sim,$^3$ and S.~W.~Mangham
\medskip  
\\$^1$School of Physics and Astronomy, University of Southampton, Highfield, Southampton, SO17 1BJ, United Kingdom
\\$^2$Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD, 21218
\\$^3$School of Mathematics and Physics, Queens University Belfast, University Road, Belfast, BT7 1NN, Northern Ireland, UK}

\date{\today}
%\\
%Supervisor: Prof. Christian Knigge\\
%{\sl School of Physics \& Astronomy, University of Southampton,
%  Southampton, SO17 1BJ, UK}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%          ABSTRACT
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\maketitle

\begin{abstract} 
% Broad absorption lines (BALs) in the ultraviolet 
% are seen in $\sim20\%$ of quasi-stellar objects (QSOs). 
% Blue-shifted broad absorption lines (BALs) are the most direct evidence of 
% accretion disk `winds' in such systems; mass loaded outflows
% emanating from the disk that may be driven by line forces or
% magnetic processes. 
Various unification schemes for
QSOs and active galactic nuclei (AGN) have proposed
that the broad emission line region is roughly cospatial
with broad absorption line (BAL) gas and much of the phenomenonology of AGN
can be explained by a simple geometrical picture involving an accretion
disk and associated outflow. Here, we test this paradigm by 
utilising our state-of-the-art radiative transfer code to produce synthetic spectra
from simple biconical disk wind models. In particular, we expand on our previous 
work in which a benchmark model for BAL quasars was produced. 
We find that a simple treatment of clumping (`microclumping') 
allows for a more realistic X-ray luminosity in the model by lowering the 
ionization parameter. We examine the X-ray properties of this new model
and find good agreement with existing X-ray samples of AGN and QSOs.
We find that clumping enhances the H recombination and collisionally excited resonance lines,
causing strong line emission (???EW) to emerge at the low inclination angles, 
which represent quasars within this unification scenario.
We also treat Hydrogen using a `macro-atom' approach in order to 
examine the effect of recombination on Hydrogen emission lines, and
this results in significant line emission in Lyman~$\alpha$ and the Balmer series.
However, we are unable to produce line emission with comparable equivalent widths
to existing quasar composites, due to a fundamental constraint arising
from the anisotropy of emission from a classical thin disk. We briefly 
explore the effect of relativistic beaming, gravitational redshift and 
light bending on the angular distribution of disk continuum emission. 
We find that these general relativistic effects do cause the disk to
emit more isotropically, but this is not yet sufficient to produce a
self-consistent model. We discuss a number of potential solutions. 
Overall, our work suggests that geometric unification
involving an ADW is a promising scenario, but our results 
pose a number of difficult challenges to such a model.
Determining the true geometry of ADWs and uncovering the true disk spectral 
(and angular) energy distribution are key next steps if we are to build up a 
holistic picture of the Quasar population.
\end{abstract}

%\begin{keywords}
%AGN: outflows
%\end{keywords}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%          INTRODUCTION
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

Introduction focussing on key points

\begin{itemize}
\item standard wind + BALQSO introduction
\item focus on unification and that we are testing it
\item some discussion of scales, referencing e.g. reverb maps, variability, microlensing, Arav 
\item clumping background: stellar winds, clumping in AGN winds, variability
\end{itemize}
%%\item

% Outflows are ubiquitous in active galactic nuclei (AGN) and quasi-stellar objects (QSOs).
% They can take the form of highly collimated radio jets \citep{bellonijet2010}, 
% or mass-loaded `winds' emanating from the accretion disk. 
Approximately $20\%$ of QSOs exhibit broad absorption lines (BALs) in the ultraviolet,
providing clear evidence for outflowing absorbing material
\citep{weymann1991, knigge2008, turnermiller2009,allen2011}.
The simplest explanation for the incidence of 
BALs in quasar samples is in terms of an accretion disk wind (ADW). 
In this paradigm, the BALQSO fraction is associated with
the covering factor of the outflow.
Indeed, many have gone further, and suggested that the diverse phenemonology
of luminous AGN and QSOs can be broadly explained by
into a simple picture of geometric unification \citep[e.g.]{MCGV95, elvis2000}. 
In such a model, a biconical wind rises from 
a thin accretion disk \cite{shakurasunyaev1973}, approaching velocities
close to $\sim0.1c$. Depending on viewing angle, an observer 
may then see a BALQSO, LoBAL-QSO or normal `Type 1' quasar- with 
broad emission lines superposed on a disk-like continuum.

The UV spectrum of {\em non-BAL} QSOs is typified by a series
of strong emission lines (e.g. \la, \civ, \nv) with an underlying blue continuum
- the so-called {\sl `big blue bump'} (BBB). The BBB is normally attributed to blackbody-like
emission from an accretion disk surrounding the central black hole (REF), similar
to that described by \cite{shakurasunyaev1973}. However,
a number of issues have arisen relating to this model. First, 
AGN/QSO spectra exhibit a `break' in the spectrum at around $1000$~\AA 
which scales only weakly with black hole mass. This potentially 
suggests a problem with a thin disk model (e.g. Antonucci). 
However, it is possible that this is the result of incorrect intergalactic medium
(IGM) corrections (REF) or corresponds to the temperature 
at which a line-driven wind carries mass away from the system (laor davis).
Second, results from microlensing (REFs) imply that the disk emission 
region is $\sim4$ times larger than one might expect from a Shakura-Sunyaev
model. Inhomogenous disks have been proposed as an alternative (REFs).
These observations appear to pose problems for the thin disk model of luminous,
sub-Eddington AGN. However, recent results from \cite{capellupo2015} find 
that if one includes a combination of mass-loss, general relativity (GR) and Comptonisation
then AGN SEDs can, in general, be fitted well with accretion disk models.
Uncovering the intrinsic disk SED and understanding the effect of the outflow on the accretion 
mechanism is clearly crucial if we are to properly understand the physical nature
of AGN.

The geometry and size of the BLR is also a matter of contention. 
The main constraints on the emission region size come from microlensing (REFs)
and reverberation mapping (REFs). While these observations have mostly been
carried out for Seyfert galaxies, there are also a few instances of these methods
being applied to quasars (REFs). A number of different proposals have been made 
for the origin of the BLR. Early AGN unification scenarios posited that the broad emission lines
where produced by clouds of plasma orbiting fairly close to the BH (refs).
Since then, multiple interpretations of a disk wind model have been proposed,
with varying radii and geometries (refs).

In this paper, we attempt to test the disk wind paradigm 
using Monte Carlo radiative transfer and photoionization calculations.
In section 2, we describe our code. In section 3, we briefly discuss some 
of the successes and failures of our previous benchmark model for BALQSOs 
\citep[][hereafter H13]{higginbottom2013} and outline the model, including 
a description of our clumping prescription. In section 4, we present the results 
from a clumped model which successfully reproduces
the observed ionization state while maintaing realistic X-ray properties.
In section 5 we discuss our results, focussing particular on the anisotropy of 
disk emission and GR effects, and finally, in section 6, we summarise our findings.

%  a simple model in which
% quasars are unified by BH mass, Eddington ratio and viewing angle can successfully
% reproduce UV, optical and X-ray properties of {\em both} 
% BALQSO's and normal emission line quasars.

% Geometrical unification pictures have suggested that 
% the BAL fraction can be interpreted as the covering factor
% of an accretion disk wind (refs), and some also propose
% that this disk wind may also be the source of the broad emission
% lines (BELs) seen in QSOs (refs). 
% Alternatively, there are a number of evolutionary models in which
% QSOs spend approximately $20\%$ of their lifetime as BALQSOs in which the outflow
% has a high covering factor (refs). 
% It is also possible that BALQSOs lie in a distinct region
% in terms of Eddington ratio (refs), but this is somewhat refuted 
% by observations (refs). % to e.g. Allen and Eigenvector I papers Ledd of BALQSOs
% Orientation, evolution, black hole mass and eddington ratio 
% may all have an effect on the BAL fraction (refs),  % to e.g. Allen
% and the importance of each must be understood to build up coherent picture.

% The driving mechanism for accretion disk winds is uncertain. The winds responsible 
% for BALs must at least have some line-driven component,
% as very strong resonance lines exert a strong line force on the 
% gas (refs). Line-driven winds are notoriously unstable (refs),
% meaning that one may expect an unstable and inhomogenous 
% velocity and density structure (refs). Magnetically driven
% winds may also produce clumpy winds or `clouds' of material which
% are magnetically confined (refs here to Shlosman, Begelman and the like).
% Describe mechanism.

% Evidence for an inhomogenous density structure in an accretion disk wind 
% and/or the broad emission line region comes from multiple sources. 
% Microlensing observations of absorption troughs suggest that different lines of sight 
% exhibit varying velocity components (refs), and BALQSO troughs 
% are known to exhibit variability (refs).

% trend of L_X with radio jets and Sy 1s
% trend of BALs with radio loudness
% see MCGV95

\section{Method: Ionization and Radiative Transfer}

We use a code Python described extensively by LK02, S05, H13, M15...

\subsection{Ionization Scheme}

We adopt the same hybrid scheme described by \cite{M15}...
% , but we have improved our ionization scheme
% for simple ions to explicitly solve the rate equations based on MC estimators.

\subsection{Macro-atoms}

\section{A Simple Biconical Disk Wind Model for QSOs}

\begin{figure}
\centering
\includegraphics[width=0.45\textwidth]{figures/fig2_cartoon.png}
\caption
{
A cartoon showing the geometry and some key parameters of
our biconical wind model.
}
\label{fig:alpha_ox}
\end{figure}

\subsection{A Benchmark Model for BALQSOs}

\cite{higginbottom2013} presented a benchmark model for
(BAL)QSOs...introduce key parameters. 
% which successfully reproduced BAL features 
% in synthetic spectra using \py. However, the model
% had a few key drawbacks when considering its potential
% for unification. First, it failed to produce significant
% broad emission lines at non-BAL viewing angles; this is 
% a key requirement for a unified QSO model. Second,
% the model was significantly X-ray weak, as it was found
% that an X-ray luminosity comparable to that of a QSO 
% over-ionized the wind, resulting in no UV resonance 
% line absorption features.

% \begin{table}
% \begin{tabular}{p{3cm}p{4cm}}
% \hline Free Parameters 	&	 Value \\ 
% \hline \hline 
% $M_{BH}$ 	 &	 $1\times 10^9~\rm{M_{\odot}}$ \\ 
% $\dot{M}_{acc}$ 	 &	 $5~M_{\odot}yr^{-1} \simeq 0.2~\dot{M}_{Edd}$\\ 
% $\alpha_X$ 	 &	 $-0.9$ \\ 
% $L_{X} $ 	 &	 $1\times10^{43}~\rm{ergs~s^{-1}}$\\ 
% $r_{disk}(min)=r_{X}$   &	 $6r_g=8.8\times10^{14}~{\rm cm}$ \\ 
% $r_{disk}(max)$   &	 $3400r_g = 5\times10^{17}~{\rm cm}$ \\ 
% $\dot{M}_{wind}$  &	 $5~M_{\odot}yr^{-1}$ \\ 
% $r_{min}$ 	&	 $300r_{g} = 4.4\times10^{16}~{\rm cm}$\\ 
% $r_{max}$ 	&	 $600r_{g} = 8.8\times10^{16}~{\rm cm}$ \\ 
% $\theta_{min}$ 	&	 $70.0^{\circ}$ \\ 
% $\theta_{max}$ 	&	 $82.0^{\circ}$ \\ 
% $\lambda$ 	&	 $0$ \\ 
% $v_{\infty}$ 	&	 $v_{esc}$(f=1) \\ 
% $R_v$ 	        &	 $1\times10^{18}$cm \\ 
% $\alpha$ 	&	 $1.0$ \\
% \hline 
% Derived Parameters 	&	 Value \\ 
% \hline \hline
% $L_{\nu}(2500\mbox{\scriptsize{\AA}})$&	 $6.3\times10^{30}~\rm{ergs~s^{-1}~Hz^{-1}}$\\ 
% $L_{\nu}(2keV)$   &	 $1.2\times10^{25}~\rm{ergs~s^{-1}~Hz^{-1}}$\\ 
% $L_{bol}$ 	 &	 $2.4\times10^{46}~\rm{ergs~s^{-1}}$\\
% $M_{bol}$ 	 &	 -27.4\\ 
% $M_u$            &	 -26.2\\ 
%  $\alpha_{OX} $ 	 &	 -2.2\\ 
% \end{tabular}
% \caption{Wind geometry parameters used in the benchmark model.}
% \label{wind_param}
% \end{table}

\subsection{Potential for unification}

\subsection{Clumping}

To take account of clumping in our outflow we adopt a simple parameterization
used in stellar wind modelling, known as {\em microclumping}. 
The key assumption here is that typical clump sizes
are much smaller than the typical photon mean free path, and thus the clumps are 
both geometrically and optically thin. This approach is typically 
known as microclumping and allows one to introduce a `filling factor', $f$, which is the 
fraction of the volume of the plasma filled by clumps. We can then introduce the 
density enhancement, $D$, which is simply

\begin{equation}
D = \frac{1}{f}
\end{equation}

One can then multiply all densities in the model by $D$, and all emitting volumes
by $f$, meaning that all $\rho^2$ processes 
(such as collisional excitation and recombination) will be enhanced, 
while opacities remain unchanged (for fixed ionization state). A factor $f$ is also
applied to the opacities such that opacities which scale only with $\rho$ are not
increased. Clumping the wind has an important effect on the ionization state and has
been proposed as a solution to the so-called `over-ionization problem' in 
disk winds (refs). This is the main motivation for incorporating microclumping
into our model.

\section{Results}

\subsection{Physical Conditions and Ionization State}

Show that clumping stops over-ionization.

\subsection{Synthetic Spectra}

Present a spectrum of the UV and possible optical too.

\subsection{X-ray Properties}

discuss the figure showing X-ray properties briefly. 
Present an X-ray spectrum? compare to observations e.g. Giustini?

\begin{figure*}
\centering
\includegraphics[width=1.0\textwidth]{figures/alpha_ox_both.png}
\caption
{
X-ray properties of the H13 and clumped model (text filled 
squares), plotted against monochromatic luminosity 
at 2500\AA. Also plotted are the samples considered by
Saez et al. 2012 on a similar plot; The COMBI-7 AGN sample (ref),
the BQS sample (ref) and the Saez et al. (2012) sample of BALQSOs.
}
\label{fig:alpha_ox}
\end{figure*}

\section{Discussion}

\subsection{Anisotropy of disk emission}

Discuss the importance of the angular distribution of the disk SED on line
(limb-darkened, foreshortened, etc.)

\subsection{General relativistic effects}

Can GR effects offer a potential solution? (not quite!)

\subsection{Wind reprocessing}

How would wind reprocessing help?

\subsection{The BALQSO fraction and wind covering factor}

A brief comment, citing Goodrich / Krolik \& Voit on the 
way in which anisotropy / attenuation affect the inferred
BAL fraction. We also need to be aware that there will be a number of selection
effects in building up the composites, and we should discuss these
and the subtleties involved.

\begin{figure}
\centering
\includegraphics[width=0.45\textwidth]{figures/f2000_m9.png}
\caption
{
$F_\lambda$ at $2000$~\AA\ as a function of inclination from
\agn\ models. Spectra are computed for BH of $10^9~M_\odot$ with
a number of different BH spins and Eddington fractions. The black line
shows a standard multi-temperature blackbody AD model.
}
\label{fig:alpha_ox}
\end{figure}

\section{Summary}

Main points:

\begin{enumerate}
\item We have introduced a simple, first-order treatment 
of clumping in our model, and found that it can now maintain
the required ionization state while agreeing well with the X-ray
properties of AGN/QSOs.
\item We find that clumping also causes a significant 
increase in the strength of the  emission
lines produced by the model. This is true both
of collisionally excited resonance lines (such as \civ, \nv)
and recombination lines (such as \la, \ha\ and the Balmer series).
\item The line EWs in our models are not comparable to those in Quasar composite
spectra. This is due to a fundamental constraint discussed in section ?. If the BLR
emits fairly isotropically then for an anisotropic classical thin accretion disk
it is not possible to achieve line ratios at low inclinations that are comparable to
those at high inclinations. This is a robust conclusion which 
is independent of the assumed BLR geometry. 
\item We have examined the effect of GR on our disk SED, using the disk atmosphere
and GR ray-tracing code AGNSPEC. While including GR effects
does cause the disk SED to become significantly more isotropic,
the effect is not large enough to produce uniform line to continuum ratios
with viewing angle. We discuss other solutions to this problem in section ?; 
It is possible that a combination of GR and reprocessing by the wind could provide a 
solution, and a number of complicated selection effects may be at work
in the building of the quasar composites. Nevertheless,
our conclusions pose a challenge to the current unification picture.
\end{enumerate}

\section*{Acknowledgements}

%% \texttt{mn2e.cls} \textsc{Latex} document class.

\bibliography{mybib.bib}
\newpage
%\appendix
\end{document}

### 2015-07-06 paper.tex
added a bunch of figures

--- 2015-06-23 draft.tex
@@
 %% Codes
-\def\py{\textsc{Python} }
-\def\tar{\textsc{Tardis} }
-\def\cld{\textsc{Cloudy} }
-\def\agn{\textsc{Agnspec} }
+\def\py{\textsc{Python}}
+\def\tar{\textsc{Tardis}}
+\def\cld{\textsc{Cloudy}}
+\def\agn{\textsc{Agnspec}}
 
@@
 The effect of clumpy outflows
-and disk anisotropy on quasar unification scenarios
+and disc anisotropy on quasar unification scenarios
 }
@@
 % Blue-shifted broad absorption lines (BALs) are the most direct evidence of 
-% accretion disk `winds' in such systems; mass loaded outflows
-% emanating from the disk that may be driven by line forces or
+% accretion disc `winds' in such systems; mass loaded outflows
+% emanating from the disc that may be driven by line forces or
 % magnetic processes. 
 Various unification schemes for
-QSOs and active galactic nuclei (AGN) have proposed
+quasars and luminous active galactic nuclei (AGN) have proposed
 that the broad emission line region is roughly cospatial
-with broad absorption line (BAL) gas and much of the phenomenonology of AGN
+with broad absorption line (BAL) gas and much of the phenomenology of luminous AGN
 can be explained by a simple geometrical picture involving an accretion
-disk and associated outflow. Here, we test this paradigm by 
+disc and associated outflow. Here, we test this paradigm by 
 utilising our state-of-the-art radiative transfer code to produce synthetic spectra
-from simple biconical disk wind models. In particular, we expand on our previous 
+from simple biconical disc wind models. In particular, we expand on our previous 
 work in which a benchmark model for BAL quasars was produced. 
@@
 We find that clumping enhances the H recombination and collisionally excited resonance lines,
-causing strong line emission (???EW) to emerge at the low inclination angles, 
+causing strong line emission (EW=?) to emerge at the low inclination angles, 
 which represent quasars within this unification scenario.
-We also treat Hydrogen using a `macro-atom' approach in order to 
-examine the effect of recombination on Hydrogen emission lines, and
-this results in significant line emission in Lyman~$\alpha$ and the Balmer series.
+% We also treat Hydrogen using a `macro-atom' approach in order to 
+% examine the effect of recombination on Hydrogen emission lines, and
+% this results in significant line emission in Lyman~$\alpha$ and the Balmer series.
 However, we are unable to produce line emission with comparable equivalent widths
 to existing quasar composites, due to a fundamental constraint arising
-from the anisotropy of emission from a classical thin disk. We briefly 
+from the anisotropy of emission from a classical thin disc. We briefly 
 explore the effect of relativistic beaming, gravitational redshift and 
-light bending on the angular distribution of disk continuum emission. 
-We find that these general relativistic effects do cause the disk to
+light bending on the angular distribution of disc continuum emission. 
+We find that these general relativistic effects do cause the disc to
 emit more isotropically, but this is not yet sufficient to produce a
@@
 Overall, our work suggests that geometric unification
-involving an ADW is a promising scenario, but our results 
+involving an accretion disc wind is a promising scenario, but our results 
 pose a number of difficult challenges to such a model.
-Determining the true geometry of ADWs and uncovering the true disk spectral 
-(and angular) energy distribution are key next steps if we are to build up a 
-holistic picture of the Quasar population.
+% Determining the true geometry of ADWs and uncovering the true disc spectral 
+% (and angular) energy distribution are key next steps if we are to build up a 
+% holistic picture of the quasar population.
 \end{abstract}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Introduction}
@@
 
-% Outflows are ubiquitous in active galactic nuclei (AGN) and quasi-stellar objects (QSOs).
-% They can take the form of highly collimated radio jets \citep{bellonijet2010}, 
-% or mass-loaded `winds' emanating from the accretion disk. 
+\clearpage
+
+Outflows are ubiquitous in active galactic nuclei (AGN) and quasi-stellar objects (QSOs).
+They can take the form of highly collimated radio jets \citep{bellonijet2010}, 
+or mass-loaded `winds' emanating from the accretion disc. 
 Approximately $20\%$ of QSOs exhibit broad absorption lines (BALs) in the ultraviolet,
@@
 The simplest explanation for the incidence of 
-BALs in quasar samples is in terms of an accretion disk wind (ADW). 
+BALs in quasar samples is in terms of an accretion disc wind (ADW). 
 In this paradigm, the BALQSO fraction is associated with
 the covering factor of the outflow.
-Indeed, many have gone further, and suggested that the diverse phenemonology
+
+It has also suggested that the  diverse phenemonology
 of luminous AGN and QSOs can be broadly explained by
@@
 In such a model, a biconical wind rises from 
-a thin accretion disk \cite{shakurasunyaev1973}, approaching velocities
+a thin accretion disc \cite{shakurasunyaev1973}, approaching velocities
 close to $\sim0.1c$. Depending on viewing angle, an observer 
 may then see a BALQSO, LoBAL-QSO or normal `Type 1' quasar- with 
-broad emission lines superposed on a disk-like continuum.
+broad emission lines superposed on a disc-like continuum.
 
@@
 - the so-called {\sl `big blue bump'} (BBB). The BBB is normally attributed to blackbody-like
-emission from an accretion disk surrounding the central black hole (REF), similar
+emission from an accretion disc surrounding the central black hole (REF), similar
 to that described by \cite{shakurasunyaev1973}. However,
@@
 which scales only weakly with black hole mass. This potentially 
-suggests a problem with a thin disk model (e.g. Antonucci). 
+suggests a problem with a thin disc model (e.g. Antonucci). 
 However, it is possible that this is the result of incorrect intergalactic medium
@@
 at which a line-driven wind carries mass away from the system (laor davis).
-Second, results from microlensing (REFs) imply that the disk emission 
+Second, results from microlensing (REFs) imply that the disc emission 
 region is $\sim4$ times larger than one might expect from a Shakura-Sunyaev
-model. Inhomogenous disks have been proposed as an alternative (REFs).
-These observations appear to pose problems for the thin disk model of luminous,
+model. Inhomogenous discs have been proposed as an alternative (REFs).
+These observations appear to pose problems for the thin disc model of luminous,
 sub-Eddington AGN. However, recent results from \cite{capellupo2015} find 
 that if one includes a combination of mass-loss, general relativity (GR) and Comptonisation
-then AGN SEDs can, in general, be fitted well with accretion disk models.
-Uncovering the intrinsic disk SED and understanding the effect of the outflow on the accretion 
+then AGN SEDs can, in general, be fitted well with accretion disc models.
+Uncovering the intrinsic disc SED and understanding the effect of the outflow on the accretion 
 mechanism is clearly crucial if we are to properly understand the physical nature
@@
 where produced by clouds of plasma orbiting fairly close to the BH (refs).
-Since then, multiple interpretations of a disk wind model have been proposed,
+Since then, multiple interpretations of a disc wind model have been proposed,
 with varying radii and geometries (refs).
 
-In this paper, we attempt to test the disk wind paradigm 
+In this paper, we attempt to test the disc wind paradigm 
 using Monte Carlo radiative transfer and photoionization calculations.
@@
 In section 5 we discuss our results, focussing particular on the anisotropy of 
-disk emission and GR effects, and finally, in section 6, we summarise our findings.
+disc emission and GR effects, and finally, in section 6, we summarise our findings.
 
@@
 % the BAL fraction can be interpreted as the covering factor
-% of an accretion disk wind (refs), and some also propose
-% that this disk wind may also be the source of the broad emission
+% of an accretion disc wind (refs), and some also propose
+% that this disc wind may also be the source of the broad emission
 % lines (BELs) seen in QSOs (refs). 
@@
 
-% The driving mechanism for accretion disk winds is uncertain. The winds responsible 
+% The driving mechanism for accretion disc winds is uncertain. The winds responsible 
 % for BALs must at least have some line-driven component,
 % as very strong resonance lines exert a strong line force on the 
-% gas (refs). Line-driven winds are notoriously unstable (refs),
+% gas (refs). Line-driven winds are notoriously unstable 
+% \citep{lucysolomon1970,macgregor1979,owockirybicki1984,owockirybicki1985}.
 % meaning that one may expect an unstable and inhomogenous 
@@
 
-% Evidence for an inhomogenous density structure in an accretion disk wind 
+% Evidence for an inhomogenous density structure in an accretion disc wind 
 % and/or the broad emission line region comes from multiple sources. 
@@
 
-\section{Method: Ionization and Radiative Transfer}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-We use a code Python described extensively by LK02, S05, H13, M15...
+% MCRT
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Ionization and Radiative Transfer}
+
+We use the MCRT code \py\ to carry out our radiative transfer and photoionization
+calculations in non-local thermodynamic equilibrium (non-LTE). 
+The code is described extensively by a series of authors (LK02, S05, H13, M15).
+For that reason we only briefly describe the key elements of the global 
+ionization calculation and other important aspects.
+
+\subsection{Line transfer}
+
+To treat line transfer, we adopt the same hybrid scheme 
+described by M15, 
+in which the energy flows
+through the system are described in terms of indivisible
+energy quanta interacting with either `simple ions'
+or `macro-atoms'. The macro-atom implementation 
+is described in full by \cite{lucy2002, lucy2003}.
+The scheme allows one to treat non-LTE line transfer without
+approximation for elements which are identified as 
+full macro-atoms.
 
@@
 
-We adopt the same hybrid scheme described by \cite{M15}...
-% , but we have improved our ionization scheme
-% for simple ions to explicitly solve the rate equations based on MC estimators.
+Macro-atoms have their ion and level populations derived from
+MC rate estimators as described by M15. To calculate the ionization fractions
+of simple-ions the dilute-blackbody modified Saha approach \citep{ML93} is no longer appropriate
+due to the presence of a power-law X-ray source. Instead, we model
+the SED in a cell using the technique described by H13.
 
-\subsection{Macro-atoms}
+We improve on this method by abandoning the modified Saha approach
+entirely, and instead computing the ionization state by 
+explicitly solving the rate equations in between ions in non-LTE. 
+Photoionization and recombination rates are calculated using MC estimators recorded
+during the photon propagation. Not only does this dispense with a number of
+small assumptions made in the modified Saha approach, it is also more numerically stable, 
+and in principle allows the direct addition of extra physical processes such as Auger ionization, which would have to be approximated if using the previous technique.
 
-\section{A Simple Biconical Disk Wind Model for QSOs}
+\subsection{Atomic Data}
+
+We use the same atomic data as described by LK02 and since
+updated by H13 and M15, with the addition of direct ionization data from Dere (????). 
+Photoionization cross-sections are from Topbase (REF) and 
+\cite{vfky}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% MODEL DESCRIPTION
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\bigskip
+\bigskip
+\bigskip
+
+\section{A Clumpy Biconical Disk Wind Model for QSOs}
+
+Our kinematic prescription for a biconical disc wind model
+follows \cite{SV93}, and is described further by
+LK02, H13 and M15.
 
@@
 \centering
-\includegraphics[width=0.45\textwidth]{figures/fig2_cartoon.png}
+\includegraphics[width=0.45\textwidth]{figures/fig2_cartoon.eps}
 \caption
@@
 }
-\label{fig:alpha_ox}
+\label{fig:cartoon}
 \end{figure}
@@
 (BAL)QSOs...introduce key parameters.
+
+\subsubsection{Photon Sources}
+
+Describe the photon sources in the model.
+
+The accretion disc in our model is geometrically thin, but optically thick
+and this adopt a standard multi-temperature blackbody
+using a \cite{shakurasunyaev1973} temperature profile. 
+The emergent SED is thus determined by the specified accretion rate ($\dot{m}$)
+and central BH mass ($M_{BH}$).
+The inner radius of the disc extends to the innermost stable circular orbit
+(ISCO) of the BH. 
+%% OUTER RADIUS? 
+We assume a Schwarzchild BH with an ISCO at $6~R_G$.
+The X-ray source in our model is treated as an isotropic sphere at the ISCO,
+which emits photons according to a power law,
+
+% \begin{equation}
+
+% \end{equation}
+
+% With a normalisation such that it produces the correct 2-10kev luminosity.
+
+% Photons striking the
+
 % which successfully reproduced BAL features 
@@
 % $L_{X} $ 	 &	 $1\times10^{43}~\rm{ergs~s^{-1}}$\\ 
-% $r_{disk}(min)=r_{X}$   &	 $6r_g=8.8\times10^{14}~{\rm cm}$ \\ 
-% $r_{disk}(max)$   &	 $3400r_g = 5\times10^{17}~{\rm cm}$ \\ 
+% $r_{disc}(min)=r_{X}$   &	 $6r_g=8.8\times10^{14}~{\rm cm}$ \\ 
+% $r_{disc}(max)$   &	 $3400r_g = 5\times10^{17}~{\rm cm}$ \\ 
 % $\dot{M}_{wind}$  &	 $5~M_{\odot}yr^{-1}$ \\ 
@@
 
+What was wrong with H13 model - X-rays + BELs.
+
 \subsection{Clumping}
 
-To take account of clumping in our outflow we adopt a simple parameterization
-used in stellar wind modelling, known as {\em microclumping}. 
-The key assumption here is that typical clump sizes
-are much smaller than the typical photon mean free path, and thus the clumps are 
-both geometrically and optically thin. This approach is typically 
-known as microclumping and allows one to introduce a `filling factor', $f$, which is the 
-fraction of the volume of the plasma filled by clumps. We can then introduce the 
-density enhancement, $D$, which is simply
+Introduce microclumping.
 
-\begin{equation}
-D = \frac{1}{f}
-\end{equation}
+% To take account of clumping in our outflow we adopt a simple parameterization
+% used in stellar wind modelling, known as {\em microclumping} \citep{hamann1998}. 
+% The key assumption here is that typical clump sizes
+% are much smaller than the typical photon mean free path, and thus the clumps are 
+% both geometrically and optically thin. This approach is typically 
+% known as microclumping and allows one to introduce a `filling factor', $f$, which is the 
+% fraction of the volume of the plasma filled by clumps. We can then introduce the 
+% density enhancement, $D$, which is simply
 
-One can then multiply all densities in the model by $D$, and all emitting volumes
-by $f$, meaning that all $\rho^2$ processes 
-(such as collisional excitation and recombination) will be enhanced, 
-while opacities remain unchanged (for fixed ionization state). A factor $f$ is also
-applied to the opacities such that opacities which scale only with $\rho$ are not
-increased. Clumping the wind has an important effect on the ionization state and has
-been proposed as a solution to the so-called `over-ionization problem' in 
-disk winds (refs). This is the main motivation for incorporating microclumping
-into our model.
+% \begin{equation}
+% D = \frac{1}{f}
+% \end{equation}
+
+% One can then multiply all densities in the model by $D$, and all emitting volumes
+% by $f$, meaning that all $\rho^2$ processes 
+% (such as collisional excitation and recombination) will be enhanced, 
+% while opacities remain unchanged (for fixed ionization state). A factor $f$ is also
+% applied to the opacities such that opacities which scale only with $\rho$ are not
+% increased. Clumping the wind has an important effect on the ionization state and has
+% been proposed as a solution to the so-called `over-ionization problem' in 
+% disc winds (refs). This is the main motivation for incorporating microclumping
+% into our model.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% RESULTS
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\clearpage
 
@@
 
-\subsection{Physical Conditions and Ionization State}
-
-Show that clumping stops over-ionization.
-
-\subsection{Synthetic Spectra}
-
-Present a spectrum of the UV and possible optical too.
-
-\subsection{X-ray Properties}
-
-discuss the figure showing X-ray properties briefly. 
-Present an X-ray spectrum? compare to observations e.g. Giustini?
+\begin{figure*}
+\centering
+\includegraphics[width=1.0\textwidth]{figures/wind.eps}
+\caption
+{
+Physical properties of the outflow.
+}
+\label{fig:uvspec}
+\end{figure*}
 
@@
 \centering
-\includegraphics[width=1.0\textwidth]{figures/alpha_ox_both.png}
+\includegraphics[width=1.0\textwidth]{figures/uvspec.eps}
+\caption
+{
+Synthetic spectra at four viewing angles in the clumpy model. Plot would look different probably,
+and may show composites, but this would be the main synthetic spectrum plot.
+}
+\label{fig:uvspec}
+\end{figure*}
+
+\begin{figure*}
+\centering
+\includegraphics[width=1.0\textwidth]{figures/opt.eps}
+\caption
+{
+Figure designed to show optical spectrum and comparison to composite.
+}
+\label{fig:uvspec}
+\end{figure*}
+
+\begin{figure*}
+\centering
+\includegraphics[width=1.0\textwidth]{figures/alpha_ox_both.eps}
 \caption
@@
 }
-\label{fig:alpha_ox}
+\label{fig:xray}
 \end{figure*}
 
+\subsection{Physical Conditions and Ionization State}
+
+Show that clumping stops over-ionization.
+
+{\bf Figure 2: Physical conditions of the wind, showing e.g. CIV fraction.}
+
+\subsection{Synthetic Spectra}
+
+Present a spectrum of the UV and possible optical too.
+
+{\bf Figures 3 and 4: UV and optical spectra.}
+
+\subsection{X-ray Properties}
+
+discuss the figure showing X-ray properties briefly. 
+Present an X-ray spectrum? compare to observations e.g. Giustini?
+
+{\bf Figures 5 and 6: $L_{2kev}$ v $L_{2500}$ plot and X-ray spectrum compared to Grupe and Nousek (broadband SED?)}
+
+\subsection{LoBALs and trends with inclination}
+
+{\bf Figure 7: line profiles of CIV, Mg II and Al III as a function of inclination.}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.5\textwidth]{figures/xray_spectrum_lnu.eps}
+\caption
+{
+Broadband SEDs compared to IR and X-ray SEDs for selected BALQSOs 
+from Grupe \& Nousek (2015).
+}
+\label{fig:xray}
+\end{figure}
+
+\begin{figure*}
+\centering
+\includegraphics[width=1.0\textwidth]{figures/c4_with_i.eps}
+\caption
+{
+Carbon IV, Al III and Mg II line profiles with inclination for wind angles.
+Showing how the line profiles change
+and how LoBALs kick in at particularly high inclinations.
+}
+\label{fig:xray}
+\end{figure*}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% DISCUSSION
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\clearpage
 \section{Discussion}
 
-\subsection{Anisotropy of disk emission}
+\subsection{Anisotropy of disc emission}
 
-Discuss the importance of the angular distribution of the disk SED on line
+Discuss the importance of the angular distribution of the disc SED on line
 (limb-darkened, foreshortened, etc.)
@@
 Can GR effects offer a potential solution? (not quite!)
+
+{\bf Figures 8 and 9: AGNSPEC F(2000) as a function of viewing angle compared to a BB disc.
+spectrum compared to composites with AGNSPEC correction.}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.5\textwidth]{figures/f2000_m9.eps}
+\caption
+{
+$F_{2000}$\ as a function of inclination from
+\agn\ models, compared to a classical AD. 
+{\bf This is a placeholder- it will show the effect of GR on the anisotropy
+of the disk for different wavelengths and eddington fractions, compared
+to limb darkened and foreshortened classical AD}.
+}
+\label{fig:f2000}
+\end{figure}
+
+\begin{figure*}
+\centering
+\includegraphics[width=1.0\textwidth]{figures/adjusted_withbals.eps}
+\caption
+{
+$F_\lambda$ normalised to $F_{2000}$.
+{\bf Again, this is a placeholder- but I'm thinking some kind of comparison to composite including the adjusted continuum, showing that we can't get it exactly right}.
+}
+\label{fig:finalcomp}
+\end{figure*}
 
@@
 
-\begin{figure}
-\centering
-\includegraphics[width=0.45\textwidth]{figures/f2000_m9.png}
-\caption
-{
-$F_\lambda$ at $2000$~\AA\ as a function of inclination from
-\agn\ models. Spectra are computed for BH of $10^9~M_\odot$ with
-a number of different BH spins and Eddington fractions. The black line
-shows a standard multi-temperature blackbody AD model.
-}
-\label{fig:alpha_ox}
-\end{figure}
+% \begin{figure}
+% \centering
+% \includegraphics[width=0.45\textwidth]{figures/f2000_m9.eps}
+% \caption
+% {
+% $F_\lambda$ at $2000$~\AA\ as a function of inclination from
+% \agn\ models. Spectra are computed for BH of $10^9~M_\odot$ with
+% a number of different BH spins and Eddington fractions. The black line
+% shows a standard multi-temperature blackbody AD model.
+% }
+% \label{fig:alpha_ox}
+% \end{figure}
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% SUMMARY
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
 \section{Summary}
 
-Main points:
+We have carried out MCRT simulations using a simple
+prescription for a biconical disc wind, with
+the aim of expanding on the work of H13 and assessing 
+the viability of such a model for geometric unification of quasars.
+We find the following main points:
 
@@
 properties of AGN/QSOs.
+\smallskip
 \item We find that clumping also causes a significant 
@@
 and recombination lines (such as \la, \ha\ and the Balmer series).
+\smallskip
 \item The line EWs in our models are not comparable to those in Quasar composite
 spectra. This is due to a fundamental constraint discussed in section ?. If the BLR
-emits fairly isotropically then for an anisotropic classical thin accretion disk
+emits fairly isotropically then for a foreshortened, limb-darkened classical thin accretion disc
 it is not possible to achieve line ratios at low inclinations that are comparable to
@@
 is independent of the assumed BLR geometry. 
-\item We have examined the effect of GR on our disk SED, using the disk atmosphere
-and GR ray-tracing code AGNSPEC. While including GR effects
-does cause the disk SED to become significantly more isotropic,
+\smallskip
+\item We have examined the effect of GR on our disc SED, using the disc atmosphere
+and GR ray-tracing code \agn. While including GR effects
+does cause the disc SED to become significantly more isotropic,
 the effect is not large enough to produce uniform line to continuum ratios
@@
 solution, and a number of complicated selection effects may be at work
-in the building of the quasar composites. Nevertheless,
-our conclusions pose a challenge to the current unification picture.
+in the building of the quasar composites.
 \end{enumerate}
+
+Our work confirms a number of expected outcomes from such a model, and suggests 
+that a simple geometry such as this can come close to explaining much of the 
+phenomenology of quasars. Nevertheless, our conclusions pose a clear challenge 
+to the current unification picture.
 

### 2015-07-08 paper.tex
started writing paper proper

@@
 \clearpage
+Quasars and luminous active galactic nuclei (AGN) 
+exhibit spectral energy distributions (SEDs) that
+typically exhibit a series of strong emission lines (e.g. \la, \civ, \nv) 
+with an underlying blue continuum - the so-called {\sl `big blue bump'} (BBB). 
+The BBB is normally attributed to 
+emission from a geometrically thin, optically thick accretion disc 
+surrounding the central black hole (REF), similar
+to that described by \cite{shakurasunyaev1973}.
 
-Outflows are ubiquitous in active galactic nuclei (AGN) and quasi-stellar objects (QSOs).
-They can take the form of highly collimated radio jets \citep{bellonijet2010}, 
+In addition to the inflowing accreting material, 
+outflowing material is ubiquitous in active galactic nuclei (AGN) 
+and quasi-stellar objects (QSOs). These outflows can take the form of 
+highly collimated radio jets \citep{bellonijet2010}, 
 or mass-loaded `winds' emanating from the accretion disc. 
@@
 providing clear evidence for outflowing absorbing material
-\citep{weymann1991, knigge2008, turnermiller2009,allen2011}.
+\citep{weymann1991, knigge2008, turnermiller2009, allen2011}.
 The simplest explanation for the incidence of 
 BALs in quasar samples is in terms of an accretion disc wind (ADW). 
-In this paradigm, the BALQSO fraction is associated with
+Within this paradigm, the BALQSO fraction is associated with
 the covering factor of the outflow.
 
-It has also suggested that the  diverse phenemonology
+It is possible that the  diverse phenemonology
 of luminous AGN and QSOs can be broadly explained by
-into a simple picture of geometric unification \citep[e.g.]{MCGV95, elvis2000}. 
+into a simple picture of geometric unification \citep[e.g.][]{MCGV95, elvis2000}. 
 In such a model, a biconical wind rises from 
-a thin accretion disc \cite{shakurasunyaev1973}, approaching velocities
-close to $\sim0.1c$. Depending on viewing angle, an observer 
-may then see a BALQSO, LoBAL-QSO or normal `Type 1' quasar- with 
-broad emission lines superposed on a disc-like continuum.
+the accretion disc, and the class of object is explained by the material
+intercepting the line of sight. Depending on viewing angle, an observer 
+may then see a BALQSO, LoBAL-QSO or normal `Type 1' quasar.
 
-The UV spectrum of {\em non-BAL} QSOs is typified by a series
-of strong emission lines (e.g. \la, \civ, \nv) with an underlying blue continuum
-- the so-called {\sl `big blue bump'} (BBB). The BBB is normally attributed to blackbody-like
-emission from an accretion disc surrounding the central black hole (REF), similar
-to that described by \cite{shakurasunyaev1973}. However,
-a number of issues have arisen relating to this model. First, 
-AGN/QSO spectra exhibit a `break' in the spectrum at around $1000$~\AA 
-which scales only weakly with black hole mass. This potentially 
-suggests a problem with a thin disc model (e.g. Antonucci). 
-However, it is possible that this is the result of incorrect intergalactic medium
-(IGM) corrections (REF) or corresponds to the temperature 
-at which a line-driven wind carries mass away from the system (laor davis).
-Second, results from microlensing (REFs) imply that the disc emission 
-region is $\sim4$ times larger than one might expect from a Shakura-Sunyaev
-model. Inhomogenous discs have been proposed as an alternative (REFs).
-These observations appear to pose problems for the thin disc model of luminous,
-sub-Eddington AGN. However, recent results from \cite{capellupo2015} find 
+As well as acting as a source of photoionized plasma, 
+a disc wind may also have a profound effect on the structure and 
+emergent continuum of the accretion disc itself.
+Mass-loss will alter the accretion rate and resultant 
+temperature of the accretion disc, possibly explaining some 
+of the features we typically see in luminous AGN (REF).
+Recent results from \cite{capellupo2015} find 
 that if one includes a combination of mass-loss, general relativity (GR) and Comptonisation
 then AGN SEDs can, in general, be fitted well with accretion disc models.
-Uncovering the intrinsic disc SED and understanding the effect of the outflow on the accretion 
-mechanism is clearly crucial if we are to properly understand the physical nature
-of AGN.
+In general, mass-loss treatments appear to be critical if an $\alpha$-disc
+model is to successfully fit AGN SEDs, particular in the UV region of the spectrum.
 
-The geometry and size of the BLR is also a matter of contention. 
-The main constraints on the emission region size come from microlensing (REFs)
-and reverberation mapping (REFs). While these observations have mostly been
-carried out for Seyfert galaxies, there are also a few instances of these methods
-being applied to quasars (REFs). A number of different proposals have been made 
-for the origin of the BLR. Early AGN unification scenarios posited that the broad emission lines
-where produced by clouds of plasma orbiting fairly close to the BH (refs).
-Since then, multiple interpretations of a disc wind model have been proposed,
-with varying radii and geometries (refs).
+% The UV spectrum of {\em non-BAL} QSOs is typified by a series
+% of strong emission lines (e.g. \la, \civ, \nv) with an underlying blue continuum
+% - the so-called {\sl `big blue bump'} (BBB). The BBB is normally attributed to blackbody-like
+% emission from an accretion disc surrounding the central black hole (REF), similar
+% to that described by \cite{shakurasunyaev1973}. However,
+% a number of issues have arisen relating to this model. First, 
+% AGN/QSO spectra exhibit a `break' in the spectrum at around $1000$~\AA 
+% which scales only weakly with black hole mass. This potentially 
+% suggests a problem with a thin disc model (e.g. Antonucci). 
+% However, it is possible that this is the result of incorrect intergalactic medium
+% (IGM) corrections (REF) or corresponds to the temperature 
+% at which a line-driven wind carries mass away from the system (laor davis).
+% Second, results from microlensing (REFs) imply that the disc emission 
+% region is $\sim4$ times larger than one might expect from a Shakura-Sunyaev
+% model. Inhomogenous discs have been proposed as an alternative (REFs).
+% These observations appear to pose problems for the thin disc model of luminous,
+% sub-Eddington AGN. However, recent results from \cite{capellupo2015} find 
+% that if one includes a combination of mass-loss, general relativity (GR) and Comptonisation
+% then AGN SEDs can, in general, be fitted well with accretion disc models.
+% Uncovering the intrinsic disc SED and understanding the effect of the outflow on the accretion 
+% mechanism is clearly crucial if we are to properly understand the physical nature
+% of AGN.
+
+% The geometry and size of the BLR is also a matter of contention. 
+% The main constraints on the emission region size come from microlensing (REFs)
+% and reverberation mapping (REFs). While these observations have mostly been
+% carried out for Seyfert galaxies, there are also a few instances of these methods
+% being applied to quasars (REFs). A number of different proposals have been made 
+% for the origin of the BLR. Early AGN unification scenarios posited that the broad emission lines
+% where produced by clouds of plasma orbiting fairly close to the BH (refs).
+% Since then, multiple interpretations of a disc wind model have been proposed,
+% with varying radii and geometries (refs).
 

### 2015-07-15 draft.tex
a bunch of text in results, may clash with laptop

@@
 
-\author[Matthews et al.]{J.~H.~Matthews$^1$\thanks{jm8g08@soton.ac.uk}, C.~Knigge,$^1$
-N.~Higginbottom,$^1$ K.~S.~Long,$^2$ S.~A.~Sim,$^3$ and S.~W.~Mangham
+\author[Matthews et al.]{J.~H.~Matthews$^1$\thanks{jm8g08@soton.ac.uk}, C.~Knigge$^1$,
+N.~Higginbottom$^1$, K.~S.~Long$^2$, S.~A.~Sim$^3$, S.~W.~Mangham$^1$.
 \medskip  
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Introduction}
 
-Introduction focussing on key points
+Introduction focussing on key points.
+Paragraphs:
 
-\begin{itemize}
+\begin{enumerate}
 \item standard wind + BALQSO introduction
-\item focus on unification and that we are testing it
+\item Can an outflow also be the BLR? (unification)
 \item some discussion of scales, referencing e.g. reverb maps, variability, microlensing, Arav 
-\item clumping background: stellar winds, clumping in AGN winds, variability
-\end{itemize}
+\item AGN variability leading to clumping background: stellar winds, clumping in AGN winds.
+\item Modelling efforts so far (Proga, Higginbottom, etc.)
+\item Plan of paper
+\end{enumerate}
 %%\item
+
+\clearpage
 
@@
 % They can take the form of highly collimated radio jets \citep{bellonijet2010}, 
-% or mass-loaded `winds' emanating from the accretion disk. 
-Approximately $20\%$ of QSOs exhibit broad absorption lines (BALs) in the ultraviolet,
-providing clear evidence for outflowing absorbing material
-\citep{weymann1991, knigge2008, turnermiller2009,allen2011}.
-The simplest explanation for the incidence of 
-BALs in quasar samples is in terms of an accretion disk wind (ADW). 
-In this paradigm, the BALQSO fraction is associated with
-the covering factor of the outflow.
-Indeed, many have gone further, and suggested that the diverse phenemonology
-of luminous AGN and QSOs can be broadly explained by
-into a simple picture of geometric unification \citep[e.g.]{MCGV95, elvis2000}. 
-In such a model, a biconical wind rises from 
-a thin accretion disk \cite{shakurasunyaev1973}, approaching velocities
-close to $\sim0.1c$. Depending on viewing angle, an observer 
-may then see a BALQSO, LoBAL-QSO or normal `Type 1' quasar- with 
-broad emission lines superposed on a disk-like continuum.
+% or mass-loaded `winds' emanating from the accretion disc. 
+% Approximately $20\%$ of QSOs exhibit broad absorption lines (BALs) in the ultraviolet,
+% providing clear evidence for outflowing absorbing material
+% \citep{weymann1991, knigge2008, turnermiller2009,allen2011}.
+% The simplest explanation for the incidence of 
+% BALs in quasar samples is in terms of an accretion disc wind (ADW). 
+% In this paradigm, the BALQSO fraction is associated with
+% the covering factor of the outflow.
+% Indeed, many have gone further, and suggested that the diverse phenemonology
+% of luminous AGN and QSOs can be broadly explained by
+% into a simple picture of geometric unification \citep[e.g.]{MCGV95, elvis2000}. 
+% In such a model, a biconical wind rises from 
+% a thin accretion disc \cite{shakurasunyaev1973}, approaching velocities
+% close to $\sim0.1c$. Depending on viewing angle, an observer 
+% may then see a BALQSO, LoBAL-QSO or normal `Type 1' quasar- with 
+% broad emission lines superposed on a disc-like continuum.
 
-The UV spectrum of {\em non-BAL} QSOs is typified by a series
-of strong emission lines (e.g. \la, \civ, \nv) with an underlying blue continuum
-- the so-called {\sl `big blue bump'} (BBB). The BBB is normally attributed to blackbody-like
-emission from an accretion disk surrounding the central black hole (REF), similar
-to that described by \cite{shakurasunyaev1973}. However,
-a number of issues have arisen relating to this model. First, 
-AGN/QSO spectra exhibit a `break' in the spectrum at around $1000$~\AA 
-which scales only weakly with black hole mass. This potentially 
-suggests a problem with a thin disk model (e.g. Antonucci). 
-However, it is possible that this is the result of incorrect intergalactic medium
-(IGM) corrections (REF) or corresponds to the temperature 
-at which a line-driven wind carries mass away from the system (laor davis).
-Second, results from microlensing (REFs) imply that the disk emission 
-region is $\sim4$ times larger than one might expect from a Shakura-Sunyaev
-model. Inhomogenous disks have been proposed as an alternative (REFs).
-These observations appear to pose problems for the thin disk model of luminous,
-sub-Eddington AGN. However, recent results from \cite{capellupo2015} find 
-that if one includes a combination of mass-loss, general relativity (GR) and Comptonisation
-then AGN SEDs can, in general, be fitted well with accretion disk models.
-Uncovering the intrinsic disk SED and understanding the effect of the outflow on the accretion 
-mechanism is clearly crucial if we are to properly understand the physical nature
-of AGN.
+% The UV spectrum of {\em non-BAL} QSOs is typified by a series
+% of strong emission lines (e.g. \la, \civ, \nv) with an underlying blue continuum
+% - the so-called {\sl `big blue bump'} (BBB). The BBB is normally attributed to blackbody-like
+% emission from an accretion disc surrounding the central black hole (REF), similar
+% to that described by \cite{shakurasunyaev1973}. However,
+% a number of issues have arisen relating to this model. First, 
+% AGN/QSO spectra exhibit a `break' in the spectrum at around $1000$~\AA 
+% which scales only weakly with black hole mass. This potentially 
+% suggests a problem with a thin disc model (e.g. Antonucci). 
+% However, it is possible that this is the result of incorrect intergalactic medium
+% (IGM) corrections (REF) or corresponds to the temperature 
+% at which a line-driven wind carries mass away from the system (laor davis).
+% Second, results from microlensing (REFs) imply that the disc emission 
+% region is $\sim4$ times larger than one might expect from a Shakura-Sunyaev
+% model. Inhomogenous discs have been proposed as an alternative (REFs).
+% These observations appear to pose problems for the thin disc model of luminous,
+% sub-Eddington AGN. However, recent results from \cite{capellupo2015} find 
+% that if one includes a combination of mass-loss, general relativity (GR) and Comptonisation
+% then AGN SEDs can, in general, be fitted well with accretion disc models.
+% Uncovering the intrinsic disc SED and understanding the effect of the outflow on the accretion 
+% mechanism is clearly crucial if we are to properly understand the physical nature
+% of AGN.
 
-The geometry and size of the BLR is also a matter of contention. 
-The main constraints on the emission region size come from microlensing (REFs)
-and reverberation mapping (REFs). While these observations have mostly been
-carried out for Seyfert galaxies, there are also a few instances of these methods
-being applied to quasars (REFs). A number of different proposals have been made 
-for the origin of the BLR. Early AGN unification scenarios posited that the broad emission lines
-where produced by clouds of plasma orbiting fairly close to the BH (refs).
-Since then, multiple interpretations of a disk wind model have been proposed,
-with varying radii and geometries (refs).
+% The geometry and size of the BLR is also a matter of contention. 
+% The main constraints on the emission region size come from microlensing (REFs)
+% and reverberation mapping (REFs). While these observations have mostly been
+% carried out for Seyfert galaxies, there are also a few instances of these methods
+% being applied to quasars (REFs). A number of different proposals have been made 
+% for the origin of the BLR. Early AGN unification scenarios posited that the broad emission lines
+% where produced by clouds of plasma orbiting fairly close to the BH (refs).
+% Since then, multiple interpretations of a disc wind model have been proposed,
+% with varying radii and geometries (refs).
 
-In this paper, we attempt to test the disk wind paradigm 
-using Monte Carlo radiative transfer and photoionization calculations.
-In section 2, we describe our code. In section 3, we briefly discuss some 
-of the successes and failures of our previous benchmark model for BALQSOs 
-\citep[][hereafter H13]{higginbottom2013} and outline the model, including 
-a description of our clumping prescription. In section 4, we present the results 
-from a clumped model which successfully reproduces
-the observed ionization state while maintaing realistic X-ray properties.
-In section 5 we discuss our results, focussing particular on the anisotropy of 
-disk emission and GR effects, and finally, in section 6, we summarise our findings.
+% In this paper, we attempt to test the disc wind paradigm 
+% using Monte Carlo radiative transfer and photoionization calculations.
+% In section 2, we describe our code. In section 3, we briefly discuss some 
+% of the successes and failures of our previous benchmark model for BALQSOs 
+% \citep[][hereafter H13]{higginbottom2013} and outline the model, including 
+% a description of our clumping prescription. In section 4, we present the results 
+% from a clumped model which successfully reproduces
+% the observed ionization state while maintaing realistic X-ray properties.
+% In section 5 we discuss our results, focussing particular on the anisotropy of 
+% disc emission and GR effects, and finally, in section 6, we summarise our findings.
 
@@
 
-\section{Method: Ionization and Radiative Transfer}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-We use a code Python described extensively by LK02, S05, H13, M15...
+% MCRT
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Ionization and Radiative Transfer}
+
+We use the MCRT code \py\ to carry out our radiative transfer and photoionization
+calculations in non-local thermodynamic equilibrium (non-LTE). 
+The code is described extensively by a series of authors (LK02, S05, H13, M15).
+For that reason we only briefly describe the key elements of the global 
+ionization calculation and other important aspects.
+
+\subsection{Line transfer}
+
+To treat line transfer, we adopt the same hybrid scheme 
+described by M15...
+%in which the energy flows
+% through the system are described in terms of indivisible
+% energy quanta interacting with either `simple ions'
+% or `macro-atoms'. The macro-atom implementation 
+% is described in full by \cite{lucy2002, lucy2003}.
+% The scheme allows one to treat
 
@@
 
-We adopt the same hybrid scheme described by \cite{M15}...
-% , but we have improved our ionization scheme
-% for simple ions to explicitly solve the rate equations based on MC estimators.
+Describe the ionization scheme. Combination of H13 and M15 but with rate equations
+solved explicitly for ionization solution.
 
-\subsection{Macro-atoms}
+% Macro-atoms have their ion and level populations derived from
+% MC rate estimators as described by M15. To calculate the ionization fractions
+% of simple-ions the dilute-blackbody modified Saha approach \citep{ML93} is no longer appropriate
+% due to the presence of a power-law X-ray source. Instead, we model
+% the SED in a cell using the technique described by H13.
 
-\section{A Simple Biconical Disk Wind Model for QSOs}
+% We improve on this method by abandoning the modified Saha approach
+% entirely, and instead computing the ionization state by 
+% explicitly solving the rate equations in between ions in non-LTE. 
+% Photoionization and recombination rates are calculated using MC estimators recorded
+% during the photon propagation. Not only does this dispense with a number of
+% small assumptions made in the modified Saha approach, it is also more numerically stable, 
+% and in principle allows the direct addition of extra physical processes such as Auger ionization,
+% which would have to be approximated if using the previous technique.
+
+\subsection{Atomic Data}
+
+% We use the same atomic data as described by LK02 and since
+% updated by H13 and M15, with the addition of direct ionization data from Dere (????). 
+% Photoionization cross-sections are from Topbase (REF) and 
+% \cite{vfky}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% MODEL DESCRIPTION
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\bigskip
+\bigskip
+\bigskip
+
+\section{A Clumpy Biconical Disk Wind Model for QSOs}
+
+Our kinematic prescription for a biconical disc wind model
+follows \cite{SV93}, and is described further by
+LK02, H13 and M15.
 
@@
 }
-\label{fig:alpha_ox}
+\label{fig:cartoon}
 \end{figure}
 
-\subsection{A Benchmark Model for BALQSOs}
+\subsection{A Simple Biconical Disc Wind Model}
 
@@
 (BAL)QSOs...introduce key parameters.
+
+\subsubsection{Photon Sources}
+
+Describe the photon sources in the model.
+
+% The accretion disc in our model is geometrically thin, but optically thick
+% and this adopt a standard multi-temperature blackbody
+% using a \cite{shakurasunyaev1973} temperature profile. 
+% The emergent SED is thus determined by the specified accretion rate ($\dot{m}$)
+% and central BH mass ($M_{BH}$).
+% The inner radius of the disc extends to the innermost stable circular orbit
+% (ISCO) of the BH. 
+% %% OUTER RADIUS? 
+% We assume a Schwarzchild BH with an ISCO at $6~R_G$.
+% The X-ray source in our model is treated as an isotropic sphere at the ISCO,
+% which emits photons according to a power law,
+
+% \begin{equation}
+
+% \end{equation}
+
+% With a normalisation such that it produces the correct 2-10kev luminosity.
+
+% Photons striking the
+
 % which successfully reproduced BAL features 
@@
 }
-\label{fig:alpha_ox}
+\label{fig:xray}
 \end{figure*}
 
+\subsection{Physical Conditions and Ionization State}
+
+The wind rises slowly from the disc at first, with clumped densities
+of $n_H \sim 10^{11}~\rm{cm^{-3}}$ close to the disc plane.
+The flow then accelerates over a scale length of $R_V=10^{19}~\rm{cm}$
+up to a terminal velocity of around $3$ times the escape velocity 
+($\sim10,000~\rm{km~s^{-1}}$). This gradual acceleration means that
+the wind exhibits a stratified ionization structure, with low ionization material
+in the base of the wind giving way to highly ionized plasma further out.
+By clumping the wind, we are able to produce the range of ionization states observed
+in Quasars and BALQSOs, while adopting a realistic $2-10$ keV X-ray luminosity
+of $L_{X}1\times10^{43}~\rm{ergs~s^{-1}}$. Without clumping, this wind would be over-ionized 
+to the extent that opacities in e.g., \civ\ would be entirely negligible (see H13).
+
+One useful measure of the ionization state is the ionization parameter, $U$, given by
+\begin{equation}
+U = \frac{4\pi}{n_H c}\int_{13.6{\rm{eV}}}^{\infty}\frac{{J_{\nu}d\nu}}{h\nu}.
+\end{equation}
+\noindent where $\rm{n_H}$ is the local number density of H, and $\nu$ denotes photon 
+frequency. The ionization parameter is a useful measure of the ionization state of a plasma, 
+as it evaluates the ratio of the number density of ionizing photons to the local 
+H density.
+
+\subsection{Synthetic Spectra}
+
+Present a spectrum of the UV and possible optical too.
+
+{\bf Figures 3 and 4: UV and optical spectra.}
+
+\subsection{X-ray Properties}
+
+discuss the figure showing X-ray properties briefly. 
+Present an X-ray spectrum? compare to observations e.g. Giustini?
+
+{\bf Figures 5 and 6: $L_{2kev}$ v $L_{2500}$ plot and X-ray spectrum compared to Grupe and Nousek (broadband SED?)}
+
+\subsection{LoBALs and trends with inclination}
+
+{\bf Figure 7: line profiles of CIV, Mg II and Al III as a function of inclination.}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.5\textwidth]{figures/xray_spectrum_lnu.eps}
+\caption
+{
+Broadband SEDs compared to IR and X-ray SEDs for selected BALQSOs 
+from Grupe \& Nousek (2015).
+}
+\label{fig:xray}
+\end{figure}
+
+\begin{figure*}
+\centering
+\includegraphics[width=1.0\textwidth]{figures/c4_with_i.eps}
+\caption
+{
+Carbon IV, Al III and Mg II line profiles with inclination for wind angles.
+Showing how the line profiles change
+and how LoBALs kick in at particularly high inclinations.
+}
+\label{fig:xray}
+\end{figure*}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% DISCUSSION
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\clearpage
 \section{Discussion}
 
-\subsection{Anisotropy of disk emission}
+\subsection{Anisotropy of disc emission}
 
-Discuss the importance of the angular distribution of the disk SED on line
+Discuss the importance of the angular distribution of the disc SED on line
 (limb-darkened, foreshortened, etc.)
@@
 solution, and a number of complicated selection effects may be at work
-in the building of the quasar composites. Nevertheless,
-our conclusions pose a challenge to the current unification picture.
+in the building of the quasar composites.
 \end{enumerate}
+
+Our work confirms a number of expected outcomes from such a model, and suggests 
+that a simple geometry such as this can come close to explaining much of the 
+phenomenology of quasars. Nevertheless, our conclusions pose a clear challenge 
+to the current unification picture.
+
+% In particular, we are left with the following possibilities:
+
+% \begin{enumerate}
+% \item BALQSOs are not, as a rule, drawn from the quasar population, and 
+% instead represent a subclass of objects with strong outflows and differing
+% emission line properties to normal luminous AGN and quasars.
+% \item A combination of GR effects and reprocessing of the disc continuum
+% by the outflow results in a more or less isotropic continuum, explaining
+% the comparable line EWs between BALQSOs and quasars. 
+% \item The line emission is anisotropic in such a way so as to counter the 
+% anisotropy of the disc continuum.
+% \end{enumerate}
+
+% We favour a combination of the first two scenarios, based on a combination
+% of physical and ontological arguments. It is clear from samples of BALQSOs
+% and normal quasars that they have a fairly large range of Eddington fractions, 
+% black hole masses and inclinations. The composite spectra will therefore
+% be subject to a myriad of complex selection effects.
 

### 2015-07-15 paper.tex
a bunch of text in results, may clash with laptop

@@
 \def\nv{N~\textsc{v}}
+\def\hei{He~\textsc{i}}
+\def\heii{He~\textsc{ii}}
+\def\mg{Mg~\textsc{ii}}
+\def\al{Al~\textsc{iii}}
 \def\heii{He~\textsc{ii}}
 \def\ovi{O~\textsc{vi}}
-\def\la{Ly$\alpha$}
-\def\ha{H$\alpha$}
+\def\la{Ly~$\alpha$}
+\def\ha{H~$\alpha$}
+\def\hb{H~$\beta$}
 
@@
 
-Introduction focussing on key points
+% Introduction focussing on key points
+% \begin{itemize}
+% \item standard wind + BALQSO introduction
+% \item focus on unification and that we are testing it
+% \item some discussion of scales, referencing e.g. reverb maps, variability, microlensing, Arav 
+% \item clumping background: stellar winds, clumping in AGN winds, variability
+% \end{itemize}
+% %%\item 
+% \clearpage
 
-\begin{itemize}
-\item standard wind + BALQSO introduction
-\item focus on unification and that we are testing it
-\item some discussion of scales, referencing e.g. reverb maps, variability, microlensing, Arav 
-\item clumping background: stellar winds, clumping in AGN winds, variability
-\end{itemize}
-%%\item
-
-\clearpage
-Quasars and luminous active galactic nuclei (AGN) 
-exhibit spectral energy distributions (SEDs) that
+The spectral energy distributions (SEDs) of 
+quasars and luminous active galactic nuclei (AGN) 
 typically exhibit a series of strong emission lines (e.g. \la, \civ, \nv) 
 with an underlying blue continuum - the so-called {\sl `big blue bump'} (BBB). 
-The BBB is normally attributed to 
-emission from a geometrically thin, optically thick accretion disc 
-surrounding the central black hole (REF), similar
+The BBB is normally attributed to emission from a geometrically thin, 
+optically thick accretion disc surrounding the central black hole (REF), similar
 to that described by \cite{shakurasunyaev1973}.
@@
 We use the same atomic data as described by LK02 and since
-updated by H13 and M15, with the addition of direct ionization data from Dere (????). 
-Photoionization cross-sections are from Topbase (REF) and 
-\cite{vfky}.
+updated by H13 and M15, with the addition of direct ionization data from Dere (YEAR). 
+Photoionization cross-sections are from Topbase (REF) and  \cite{vfky}.
 
@@
 
-\section{A Clumpy Biconical Disk Wind Model for QSOs}
+\section{A Clumpy Biconical Disk Wind Model for Quasars}
 
@@
 follows \cite{SV93}, and is described further by
-LK02, H13 and M15.
+LK02, H13 and M15. A schematic is shown in figure~\ref{fig:cartoon},
+with key aspects marked. The general biconical
+geometry is similar to that invoked by \cite{MCGV95} and 
+\cite{elvis2000} in order to explain the phenomenonology
+of quasars and BALQSOs.
 
@@
 
-Describe the photon sources in the model.
+%Describe the photon sources in the model.
 
@@
 and central BH mass ($M_{BH}$).
-The inner radius of the disc extends to the innermost stable circular orbit
-(ISCO) of the BH. 
-%% OUTER RADIUS? 
+The inner radius of the disc extends to the innermost 
+stable circular orbit (ISCO) of the BH. 
 We assume a Schwarzchild BH with an ISCO at $6~R_G$.
 The X-ray source in our model is treated as an isotropic sphere at the ISCO,
-which emits photons according to a power law,
-
+which emits photons according to a power law with index $\alpha_X$.
+The normalisation of this power law is such that it produces the specified 
+2-10kev luminosity.
+In addition to the disc and X-ray source, 
+the wind is able to reprocess radiation. However, new 
+photon packets are not produced in the wind (as in LK02). 
+Instead, this reprocessing is dealt with by enforcing strict
+radiative equilibrium via an indivisible energy packet
+constraint (see Lucy 2002, M15).
 % \begin{equation}
@@
 
-\clearpage
+\section{Results}
 
-\section{Results}
+Here we describe the results from our model.
 
@@
 {
-Physical properties of the outflow.
+Physical properties of the outflow, shown by the coloured contours.
+The solid black line marks a sphere at $1000~R_G$.
+The dotted lines show the $75^\circ$ and $80^\circ$ sightlines 
+to the centre of the system, and illustrate that different sightlines
+intersect material of different ionization states.
 }
@@
 
+\begin{figure}
+\centering
+\includegraphics[width=0.5\textwidth]{figures/sightlines.eps}
+\caption
+{
+The classes of sightlines and the corresponding possible 
+system types in the framework of our model.
+[FIGURE NEEDS IMPROVING]
+}
+\label{fig:lobal}
+\end{figure}
+
 \begin{figure*}
 \centering
-\includegraphics[width=1.0\textwidth]{figures/uvspec.eps}
+\includegraphics[width=0.8\textwidth]{figures/uvspec.eps}
 \caption
@@
 
-\subsection{Physical Conditions and Ionization State}
-
-Show that clumping stops over-ionization.
-
-{\bf Figure 2: Physical conditions of the wind, showing e.g. CIV fraction.}
-
-\subsection{Synthetic Spectra}
-
-Present a spectrum of the UV and possible optical too.
-
-{\bf Figures 3 and 4: UV and optical spectra.}
-
-\subsection{X-ray Properties}
-
-discuss the figure showing X-ray properties briefly. 
-Present an X-ray spectrum? compare to observations e.g. Giustini?
-
-{\bf Figures 5 and 6: $L_{2kev}$ v $L_{2500}$ plot and X-ray spectrum compared to Grupe and Nousek (broadband SED?)}
-
-\subsection{LoBALs and trends with inclination}
-
-{\bf Figure 7: line profiles of CIV, Mg II and Al III as a function of inclination.}
-
 \begin{figure}
@@
 
+\subsection{Physical Conditions and Ionization State}
+
+The wind rises slowly from the disc at first, with clumped densities
+of $n_H \sim 10^{11}~\rm{cm^{-3}}$ close to the disc plane.
+The flow then accelerates over a scale length of $R_V=10^{19}~\rm{cm}$
+up to a terminal velocity of around $3$ times the escape velocity 
+($\sim10,000~\rm{km~s^{-1}}$). This gradual acceleration means that
+the wind exhibits a stratified ionization structure, with low ionization material
+in the base of the wind giving way to highly ionized plasma further out.
+By clumping the wind, we are able to produce the range of ionization states observed
+in Quasars and BALQSOs, while adopting a realistic $2-10$ keV X-ray luminosity
+of $L_{X}=10^{43}~\rm{ergs~s^{-1}}$. Without clumping, this wind would be over-ionized 
+to the extent that opacities in e.g., \civ\ would be entirely negligible (see H13).
+
+One commonly used measure of the ionization state is the ionization parameter, $U$, given by
+\begin{equation}
+U = \frac{4\pi}{n_H c}\int_{13.6{\rm{eV}}}^{\infty}\frac{{J_{\nu}d\nu}}{h\nu}.
+\end{equation}
+\noindent where $\rm{n_H}$ is the local number density of H, and $\nu$ denotes photon 
+frequency. The ionization parameter represents the ratio of the number density of 
+ionizing photons to the local H density. It is however, a poor measure of the 
+ionization state of the resonance species such as \civ\ as it encodes no information
+about the shape of the SED. In this case the X-ray photons 
+are dominant in the photoionization of the UV resonance line ions. 
+This explains why a factor of 100 increase in X-ray luminosity requires
+a clumping factor of 0.01, even though the value of U changes by roughly ?? compared to 
+H13.
+
+Clumping also causes the total line luminosity to increase dramatically,
+as recombination and collisional excitation are both proportional to
+$n_e^2$. This line emission typically emerges on the edge of the wind
+nearest the central source. The location of the line emitting regions
+is dependent on the ionization state, as well as the X-rays heating the plasma.
+The radii of these emitting regions is important,
+and can be compared to observations. Our \civ\ line emission region 
+is located at about $1000~R_G$ ($\sim10^{18}~\rm{cm}$).
+This is in rough agreement with the reverberation mapping 
+results of Kaspi (2000) for the $2.6\times10^{9} M_\odot$ quasar S5 0836+71,
+and also compares favourably with microlensing measurements of the size of the
+\civ\ emission line region in the BALQSO H1413+117 \citep{odowd2015}.
+
+\subsection{Synthetic Spectra}
+
+Present a spectrum of the UV and possible optical too.
+
+\subsection{X-ray Properties and Broadband SEDs}
+
+The bottom panel of figure~\ref{fig:xray} shows the emergent $L_{2keV}$ 
+monochromatic luminosity ($L_\nu$) and $\alpha_{OX}$ plotted against 
+$L_\nu$ at $2500$\AA\ for a number of different viewing angles in our model.
+$\alpha_{OX}$ is a spectral index from near UV to X-rays defined by
+
+\begin{equation}
+\alpha_{OX}=0.3838\log\left(\frac{L_{\nu}(2~keV)}{L_{\nu}(2500~\mbox{\scriptsize{\AA}})}\right).
+\end{equation}
+
+The properties are calculated from the synthetic spectra and thus include
+the effects of wind reprocessing and attenuation. In addition to model outputs,
+we also show the BALQSO sample of Saez et al. (2012) and luminous AGN and quasar
+samples from Steffen et al. (2006). For low inclination, `quasar-like' viewing angles,
+we now show excellent agreement with AGN samples. The trend with inclination
+in our models is caused by a combination of disc foreshortening/limb-darkening 
+(resulting in a lower $L_{2500}$ for higher inclinations) and the fact that the disk 
+is opaque and thus the X-ray source subtends a smaller solid angle at high inclinations
+(resulting in a lower $L_{2keV}$ for higher inclinations).
+
+Although the low inclination, `BALQSO-like' viewing angles show moderate agreement with the data,
+it appears that our models tend to underpredict the emergent X-ray luminosity at 
+although we are limited by poor statistics. It appears that our models tend
+It is possible that this is due to our wind being overly optically thick to 
+electron scattering at angles which look through the wind. It could also be that the
+isotropic X-ray source assumption is incorrect and BALQSOs are {\em intrinsically} 
+X-ray weak, as suggested by REFS. Nevertheless, our input X-ray spectrum
+now reproduces the X-ray properties of a luminous quasar.
+
+We can also examine the emergent X-ray spectra. 
+Figure 6 shows the broadband SED from the model, compared to a number of BALQSO spectra
+from Grupe \& Nousek (2015) - note that lower mass and super-Eddington sources
+are excluded. Our code is not yet optimized for producing X-ray spectra, as we do not yet 
+include all lines and levels of e.g. Fe or macro-atom treatments of 
+higher order ions (cf. Sim et al. 2008, 2010). 
+However, the bound-free opacity sources are complete, and comparisons of the shape
+of the heavily absorbed spectra can be useful.
+
+% discuss the figure showing X-ray properties briefly. 
+% Present an X-ray spectrum? compare to observations e.g. Giustini?
+
+% {\bf Figures 5 and 6: $L_{2kev}$ v $L_{2500}$ plot and X-ray spectrum compared to Grupe and Nousek (broadband SED?)}
+
+\subsection{LoBALs and trends with inclination}
+
+At certain sightlines, our model now produces blue-shifted BALs in \al\ and \mg --
+the absorption lines seen in LoBALQSOs. Line profiles in velocity space 
+for \civ, \al\ and \mg, are shown in figure~\ref{fig:lobal} for a range
+of BALQSO viewing angles. We confirm the behaviour expected from 
+a unification model such as Elvis (2000), in which ionization stratification
+explains the incidence of LoBALQSOs. In this framework, the lower
+ionization material is intercepted by a smaller family of sightlines.
+This is also the explanation here, as shown by figure~\ref{fig:wind}.
+
+These line profiles also indicate a potential problem with our model. 
+\cite{odowd2015} find that the LoBAL profiles in H1413+117 have a 
+higher velocity onset than the higher ionization BALs, suggesting that the
+wind becomes less ionized as radius increases. 
+We find the opposite trend in velocity onsets. In addition, examination of 
+figure~\ref{fig:wind} shows that ionization parameter decreases with radius, 
+because the decrease in density wins over geometric dilution of the radiation 
+field. While the \cite{odowd2015} hypothesis comes from one object,
+it is clear that {\em at least some} BALQSOs must become less ionized at 
+higher velocities, contrary to what one expects from our modelling.
+
 \begin{figure*}
@@
 }
-\label{fig:xray}
+\label{fig:lobal}
 \end{figure*}
@@
 \begin{enumerate}
-\item We have introduced a simple, first-order treatment 
+\item We have introduced a first-order treatment 
 of clumping in our model, and found that it can now maintain
@@
 
+We would like to thank Omer Blaes, Ivan Hubeny, Shane Davis, 
+Michael Crenshaw, Nahum Arav, Daniel Proga,
+
 %% \texttt{mn2e.cls} \textsc{Latex} document class.

### 2015-07-15 paper.tex
local laptop edits, intro and refs

--- 2015-07-08 paper.tex
@@
 
-Introduction focussing on key points
+% Introduction focussing on key points
 
-\begin{itemize}
-\item standard wind + BALQSO introduction
-\item focus on unification and that we are testing it
-\item some discussion of scales, referencing e.g. reverb maps, variability, microlensing, Arav 
-\item clumping background: stellar winds, clumping in AGN winds, variability
-\end{itemize}
+% \begin{itemize}
+% \item standard wind + BALQSO introduction
+% \item focus on unification and that we are testing it
+% \item some discussion of scales, referencing e.g. reverb maps, variability, microlensing, Arav 
+% \item clumping background: stellar winds, clumping in AGN winds, variability
+% \end{itemize}
 %%\item 
-
-\clearpage
 Quasars and luminous active galactic nuclei (AGN) 
@@
 to that described by \cite{shakurasunyaev1973}.
-
 In addition to the inflowing accreting material, 
-outflowing material is ubiquitous in active galactic nuclei (AGN) 
-and quasi-stellar objects (QSOs). These outflows can take the form of 
-highly collimated radio jets \citep{bellonijet2010}, 
+outflows are ubiquitous in AGN
+and quasars (REFs). These outflows can take the form of 
+highly collimated radio jets \citep{bellonijet2010}(BETTER REF), 
 or mass-loaded `winds' emanating from the accretion disc. 
-Approximately $20\%$ of QSOs exhibit broad absorption lines (BALs) in the ultraviolet,
+Approximately $20\%$ of quasars exhibit broad absorption lines (BALs) in the ultraviolet,
 providing clear evidence for outflowing absorbing material
@@
 The simplest explanation for the incidence of 
-BALs in quasar samples is in terms of an accretion disc wind (ADW). 
+BAL quasars (BALQSOs) is in terms of an accretion disc wind (ADW). 
 Within this paradigm, the BALQSO fraction is associated with
@@
 may then see a BALQSO, LoBAL-QSO or normal `Type 1' quasar.
-
-As well as acting as a source of photoionized plasma, 
-a disc wind may also have a profound effect on the structure and 
+Within this framework, the broad-line region (BLR) is normally
+assumed to correspond to the dense wind base.
+% As well as acting as a source of photoionized plasma, a 
+A disc wind may also have a profound effect on the structure and 
 emergent continuum of the accretion disc itself.
@@
 temperature of the accretion disc, possibly explaining some 
-of the features we typically see in luminous AGN (REF).
+of the features we typically see in luminous AGN \citep{laordavis2014}.
 Recent results from \cite{capellupo2015} find 
@@
 model is to successfully fit AGN SEDs, particular in the UV region of the spectrum.
+
+Despite the clear importance of ADWs in understanding AGN SEDs and accretion physics, 
+much of the underlying outflow physics remains highly uncertain. 
+Several possible driving mechanisms for ADWs have been proposed, including
+thermal pressure (REFs), magnetocentrifugal forces \citep{blandfordpayne} and 
+radiation pressure on spectral lines \citep[`line-driving'][]{lucysolomon1970, MCGV95}.
+Of these, line-driving is possibly the most attractive, due 
+to the strong absorption lines seen in BALQSOs and the X-ray spectra of AGN (REFs).
+The presence of line-locked features (REFs) and the so-called `ghost of \la' \citep{arav1996}
+in the spectra of such objects also gives clearer evidence that line-driving is
+at least partially contributing to the acceleration of the wind.
+The efficiency of line-driving is crucially dependent on the ionization state 
+of the outflowing plasma. \cite{MCGV95} proposed a potential solution: 
+a region of `hitchhiking gas' that could shield the wind from the central X-ray source. 
+Hydrodynamic simulations of line-driven disc winds also found a shielding region
+was required to maintain the correct ionization state \citep{PSK2000,PK04}. 
+However, \cite{H14} showed that including multiple scattering means the ionizing radiation 
+field could still reach the previously shielded regions in those particular models.
+
+An alternative solution is that the wind is clumped (REFs), possibly on multiple scale lengths.
+Local density enhancements could lower the ionization parameter of the plasma
+while still maintaining the same mass-loss rate and column density. 
+An inhomogenous outflow has been proposed as a model for the BLR (REFs)
+Clumping is expected in outflows and BLRs.
 
@@
 
-\bibliography{mybib.bib}
+\bibliography{mybib.bib,stellar.bib,h14.bib,h13.bib}
 \newpage

### 2015-07-16 paper.tex

--- 2015-07-15 paper.tex
@@
 % \end{itemize}
-% %%\item 
-% \clearpage
 

### 2015-07-16 paper_mnras.tex
some more references and text, mnras script

--- 2015-07-16 paper.tex
@@
+\documentclass[useAMS,usenatbib]{mn2e_x}
 %%%% Various options for document class.
-%%\documentclass[usenatbib, a4paper, 11pt]{aastex}
-%%\documentclass[preprint, 11pt, a4paper]{aastex}
-%%\documentclass[twocolum]{revtex4}
-%%\documentclass{report}
-\documentclass[useAMS,usenatbib]{mn2e_x}
-
 %\usepackage{psfig,morefloats,url}
@@
 
-\author[Matthews et al.]{J.~H.~Matthews$^1$\thanks{jm8g08@soton.ac.uk}, C.~Knigge,$^1$
-N.~Higginbottom,$^1$ K.~S.~Long,$^2$ S.~A.~Sim,$^3$ and S.~W.~Mangham
+%\author[Matthews et al.]
+\author[Matthews et al.]{
+\parbox[t]{\textwidth}{
+J.~H.~Matthews$^1$\thanks{jm8g08@soton.ac.uk}, C.~Knigge$^1$,
+N.~Higginbottom$^1$, K.~S.~Long$^2$, S.~A.~Sim$^3$, and S.~W.~Mangham$^1$
+}
 \medskip  
@@
 \\$^2$Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD, 21218
-\\$^3$School of Mathematics and Physics, Queens University Belfast, University Road, Belfast, BT7 1NN, Northern Ireland, UK}
+\\$^3$School of Mathematics and Physics, Queens University Belfast, University Road, Belfast, BT7 1NN, Northern Ireland, UK
+}
 
@@
 \maketitle
-
 \begin{abstract} 
@@
 providing clear evidence for outflowing absorbing material
-\citep{weymann1991, knigge2008, turnermiller2009, allen2011}.
+\citep{weymann1991, reichard2003, knigge2008, turnermiller2009, allen2011}.
 The simplest explanation for the incidence of 
@@
 to the strong absorption lines seen in BALQSOs and the X-ray spectra of AGN (REFs).
-The presence of line-locked features (REFs) and the so-called `ghost of \la' \citep{arav1996}
+The presence of line-locked features \citep{bowler2014} and the so-called `ghost of \la' \citep{arav1996}
 in the spectra of such objects also gives clearer evidence that line-driving is
@@
 
-\begin{figure*}
+\begin{figure*} %fullpage
 \centering
@@
 \label{fig:uvspec}
-\end{figure*}
+\end{figure*} %fullpage
 
@@
 \label{fig:uvspec}
-\end{figure*}
+\end{figure*} %fullpage
 
-\begin{figure*}
+\begin{figure*} %fullpage
 \centering
@@
 \label{fig:xray}
-\end{figure*}
+\end{figure*} %fullpage
 
@@
 it appears that our models tend to underpredict the emergent X-ray luminosity at 
-although we are limited by poor statistics. It appears that our models tend
+although we are limited by poor statistics. 
 It is possible that this is due to our wind being overly optically thick to 
@@
 
-We can also examine the emergent X-ray spectra. 
-Figure 6 shows the broadband SED from the model, compared to a number of BALQSO spectra
-from Grupe \& Nousek (2015) - note that lower mass and super-Eddington sources
-are excluded. Our code is not yet optimized for producing X-ray spectra, as we do not yet 
+Typically, BALQSOs show strong X-ray absorption with columns 
+of $N_H\sim10^{23}~\rm{cm^{-2}}$ 
+\citep{green1996,brandt2000,mathur2000,green2001,grupemathur2003}.
+This is often cited as evidence that the BAL outflow is shielded from
+the X-ray source, especially as sources with strong X-ray absorption tend
+to exhibit deep BAL troughs and high outflow velocities (REFs).
+Our results tend to imply that a clumpy BAL outflow
+itself can be responsible for the strong X-ray absorption, and possibly 
+explains why mini-BALs have weaker X-ray absorption than BALQSOs 
+\citep[e.g.][]{brandt2000,hamann2013}.
+
+We can also examine the emergent X-ray spectra from our model. 
+Our code is not yet optimized for producing X-ray spectra, as we do not yet 
 include all lines and levels of e.g. Fe or macro-atom treatments of 
@@
 of the heavily absorbed spectra can be useful.
+Figure 6 shows the broadband SED from the model, compared to a number of BALQSO spectra
+from Grupe \& Nousek (2015) - note that lower mass and super-Eddington sources
+are excluded.
 
@@
 \label{fig:lobal}
-\end{figure*}
+\end{figure*} %fullpage
 
@@
 \label{fig:finalcomp}
-\end{figure*}
+\end{figure*} %fullpage
 
@@
 
-\bibliography{mybib.bib,stellar.bib,h14.bib,h13.bib}
+\bibliography{mybib.bib,stellar.bib,h14.bib,h13.bib,hamann.bib}
 \newpage

### 2015-07-16 mnras.py

@@ -1,0 +1,44 @@
+
+
+import sys
+import numpy as np
+filename = sys.argv[1]
+outfilename = sys.argv[2]
+
+
+texfile =  open(filename, "r")
+outfile = open(outfilename, "w")
+
+
+outfile.write("\documentclass[useAMS,usenatbib]{mn2e_x}\n")
+
+fig_env = False
+
+for line in texfile:
+	if "begin{abstract}" in line:
+		outfile.write("\maketitle\n")
+		outfile.write(line)
+
+	elif "\\author{" in line:
+		outfile.write("\\author[Matthews et al.]{\n")
+
+	elif "indent" in line and "rule" in line:
+		if "%" not in line:
+			outfile.write("\\noindent\\rule{8cm}{0.4pt}\n")
+
+	elif "fullpage" in line and "begin{figure}" in line:
+		if fig_env == False:
+			outfile.write("\\begin{figure*}\n")
+			fig_env = True 
+
+	elif fig_env and "end{figure}" in line:
+		outfile.write("\end{figure*}")
+		outfile.write("\n")
+		fig_env = False 
+
+	elif "documentclass" not in line and "maketitle" not in line:
+		outfile.write(line)
+
+
+
+outfile.close()

### 2015-07-20 paper.tex
added more text

@@
 %%\documentclass{report}
-\documentclass[useAMS,usenatbib]{mn2e_x}
-
+%\documentclass[useAMS,usenatbib]{mn2e_x}
+\documentclass[preprint, a4paper, 11pt]{aastex}
 %\usepackage{psfig,morefloats,url}
@@
 \usepackage{subfigure}
+\usepackage{url}
 %\usepackage{epsfig}
@@
 \def\apj{ApJ}
+\def\apjs{ApJs}
 \def\pasp{PASP}
@@
 
-\author[Matthews et al.]{J.~H.~Matthews$^1$\thanks{jm8g08@soton.ac.uk}, C.~Knigge,$^1$
-N.~Higginbottom,$^1$ K.~S.~Long,$^2$ S.~A.~Sim,$^3$ and S.~W.~Mangham
+%\author[Matthews et al.]
+\author{
+\parbox[t]{\textwidth}{
+J.~H.~Matthews$^1$\thanks{jm8g08@soton.ac.uk}, C.~Knigge$^1$,
+N.~Higginbottom$^1$, K.~S.~Long$^2$, S.~A.~Sim$^3$ and S.~W.~Mangham$^1$
+}
 \medskip  
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\maketitle
 
@@
 
+\maketitle
 %\begin{keywords}
@@
 quasars and luminous active galactic nuclei (AGN) 
-typically exhibit a series of strong emission lines (e.g. \la, \civ, \nv) 
+typically exhibit a series of strong emission lines
 with an underlying blue continuum - the so-called {\sl `big blue bump'} (BBB). 
@@
 outflows are ubiquitous in AGN
-and quasars (REFs). These outflows can take the form of 
-highly collimated radio jets \citep{bellonijet2010}(BETTER REF), 
-or mass-loaded `winds' emanating from the accretion disc. 
+and quasars \citep{kellerman1989,ganguly2008}. These outflows can take the form of 
+highly collimated radio jets \citep[e.g.][]{hazard1963,potash1980,perley1984,marscher2006}, 
+or mass-loaded `winds' emanating from the accretion disc 
+\citep{weymann1991,turnermiller2009}. 
+Outflows in AGN offer a 
+natural feedback mechanism through which the central source can 
+affect its environment \citep{king2003,king2005,fabian2012}
+-- feedback that is required by models of galaxy evolution (REFs) 
+and may explain the `$M-\sigma$' relation \citep{silkrees1998,haring2004}.
+
 Approximately $20\%$ of quasars exhibit broad absorption lines (BALs) in the ultraviolet,
 providing clear evidence for outflowing absorbing material
-\citep{weymann1991, knigge2008, turnermiller2009, allen2011}.
+\citep{weymann1991, reichard2003, knigge2008, turnermiller2009, allen2011}.
 The simplest explanation for the incidence of 
@@
 the covering factor of the outflow.
-
-It is possible that the  diverse phenemonology
-of luminous AGN and QSOs can be broadly explained by
-into a simple picture of geometric unification \citep[e.g.][]{MCGV95, elvis2000}. 
+In addition, ADWs may offer a natural explanation for the
+diverse phenemonology of luminous AGN and QSOs \citep[e.g.][]{MCGV95, elvis2000}. 
 In such a model, a biconical wind rises from 
@@
 then AGN SEDs can, in general, be fitted well with accretion disc models.
-In general, mass-loss treatments appear to be critical if an $\alpha$-disc
+Mass-loss therefore appears to be critical if an $\alpha$-disc
 model is to successfully fit AGN SEDs, particular in the UV region of the spectrum.
@@
 Several possible driving mechanisms for ADWs have been proposed, including
-thermal pressure (REFs), magnetocentrifugal forces \citep{blandfordpayne} and 
-radiation pressure on spectral lines \citep[`line-driving'][]{lucysolomon1970, MCGV95}.
-Of these, line-driving is possibly the most attractive, due 
-to the strong absorption lines seen in BALQSOs and the X-ray spectra of AGN (REFs).
-The presence of line-locked features (REFs) and the so-called `ghost of \la' \citep{arav1996}
-in the spectra of such objects also gives clearer evidence that line-driving is
+thermal pressure \citep{weymann1982, begelman1991}, magnetocentrifugal forces 
+\citep{blandfordpayne,pelletier_pudritz} and 
+radiation pressure on spectral lines \citep[`line-driving';][]{lucysolomon1970,shlosman1985,MCGV95}.
+Of these, line-driving is possibly the most attractive, as
+strong absorption lines are already seen in BALQSOs and the X-ray spectra of AGN 
+\citep{reeves2003,poundsreeves2009,tombesi2010a}.
+The presence of line-locked features \citep{bowler2014} 
+and the `ghost of \la' (Arav et al. 1996; Arav 1996; North 2006; but see 
+also Cottis et al. 2010) \nocite{arav1995, arav1996, north2006,cottis2010}
+in the spectra of some BALQSOs also gives clearer evidence that line-driving is
 at least partially contributing to the acceleration of the wind.
+
 The efficiency of line-driving is crucially dependent on the ionization state 
@@
 while still maintaining the same mass-loss rate and column density. 
-An inhomogenous outflow has been proposed as a model for the BLR (REFs)
-Clumping is expected in outflows and BLRs.
+Clumping is expected in outflows and the BLR in a number of separate models
+with different motivations.
+
+Physically, clumping can be present due to magnetic confinement of 
+dense regions (REFs) or the instabilities that are theoretically predicted 
+in line-driven winds (REFs).
+
+% An inhomogenous outflow has been proposed as a model for the BLR (REFs)
+% Clumping is expected in outflows and BLRs.
 
@@
 approximation for elements which are identified as 
-full macro-atoms.
+full macro-atoms, while maintaining the fast `two-level' 
+treatment of resonance lines when elements are identified 
+as simple-ions. In this study,
+only H \& He are treated as macro-atoms, because 
+we expect recombination to be important
+in determining their level populations (see M15).
 
@@
 Macro-atoms have their ion and level populations derived from
-MC rate estimators as described by M15. To calculate the ionization fractions
-of simple-ions the dilute-blackbody modified Saha approach \citep{ML93} is no longer appropriate
-due to the presence of a power-law X-ray source. Instead, we model
-the SED in a cell using the technique described by H13.
+MC rate estimators as described by M15. Previously (LK02, H13, M15),
+we adopted a modified Saha approach to calculate the ionization fractions
+of simple-ions. We have now improved our code to explicitly solve the 
+rate equations in between ions in non-LTE. 
+Not only does this
+dispense with a number of small assumptions made in the modified Saha approach, 
+it is also more numerically stable, 
+and in principle allows the direct addition of extra physical 
+processes such as Auger ionization, which would have to be approximated 
+if using the previous technique.
 
-We improve on this method by abandoning the modified Saha approach
-entirely, and instead computing the ionization state by 
-explicitly solving the rate equations in between ions in non-LTE. 
-Photoionization and recombination rates are calculated using MC estimators recorded
-during the photon propagation. Not only does this dispense with a number of
-small assumptions made in the modified Saha approach, it is also more numerically stable, 
-and in principle allows the direct addition of extra physical processes such as Auger ionization, which would have to be approximated if using the previous technique.
+To avoid approximating the complex AGN SED as e.g. a dilute blackbody \citep[][M15]{ML93},
+we model the SED in a cell using the technique described by H13. In this scheme,
+the mean intensity in a series of bands is modeled as a normalised power law 
+\begin{equation}
+J_{\nu,j}=K_{pl}\nu^{\alpha_{pl}},
+\end{equation}
+or an exponential 
+\begin{equation}
+J_{\nu,j}=K_{exp}e^{(-h\nu/kT_{exp})}.
+\end{equation}
+The photoionization rate from ion $i$ can then be written as
+
+\begin{equation}
+R_{i,i+1}(J)= 
+\displaystyle{n_i \sum_{band~j=0}^{n}}~{\int_{\nu_j}^{~\nu_j+1}{J_{\nu,j}\sigma_i(\nu)\nu^{-1}d\nu}},
+\end{equation}
+while the radiative recombination rate is simply given by 
+\begin{equation}
+R_{i+1,i}(T_e) = \alpha_{i+1,i} n_{i+1} n_e
+\end{equation}
+$\alpha_{i+1,i}$ here is the recombination rate coefficient from the ground state
+of the upper ion to the ground state of the lower ion- we thus neglect recombination
+to and from excited states in this calculation. In addition to these
+radiative rates, we include dielectronic recombination and collisional ionization
+as additive processes. We assume dilute level populations 
+for simple-ions.
+
+% We improve on this method by abandoning the modified Saha approach
+% entirely, and instead computing the ionization state by 
+% explicitly solving the rate equations in between ions in non-LTE. 
+% Photoionization and recombination rates are calculated using MC estimators recorded
+% during the photon propagation. Not only does this dispense with a number of
+% small assumptions made in the modified Saha approach, it is also more numerically stable, 
+% and in principle allows the direct addition of extra physical processes such as Auger ionization, which would have to be approximated if using the previous technique.
 
@@
 We use the same atomic data as described by LK02 and since
-updated by H13 and M15, with the addition of direct ionization data from Dere (YEAR). 
-Photoionization cross-sections are from Topbase (REF) and  \cite{vfky}.
+updated by H13 and M15, with the addition of direct ionization data from Dere (xxxx). 
+Photoionization cross-sections are from \textsc{Topbase} \citep{cunto1993} and  \cite{vfky}.
+We use dielectronic recombination from \cite{badnell2006} and free-free 
+Gaunt factors from \cite{sutherland1998}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\bigskip
-\bigskip
-\bigskip
 
@@
 
-Here we describe the results from our model.
+Here we describe the results from our model. This set of parameters
+was arrived at by conducting a limited grid search over a 
+5-dimensional parameter space involving the variables
+$r_{min}$, $\theta_{min}$, $f$, $\alpha$ and $R_V$.
+We then evaluated these models qualitavely based on the following
+criteria:
 
-\begin{figure*}
+\begin{itemize}
+\item Does the model maintain the correct ionization state and produce strong BALs?
+\item Does strong line emission emerge at low inclinations?
+\item Do H recombination lines appear in the spectrum?
+\item Do a certain range of angles produce LoBAL features?
+\end{itemize}
+
+We arrived at a model which is one of the most promising,
+but also representative of a family of models. Examination 
+of this individual model allows us to gain insight
+into fundamental geometrical and physical constraints, 
+as discussed in section 5. 
+The full grid, including output spectral files and plots can be found at
+\url{jhmatthews.github.io/agn-grid-archive}.
+
+\begin{figure*} %fullpage
 \centering
@@
 
-\begin{figure*}
-\centering
-\includegraphics[width=0.8\textwidth]{figures/uvspec.eps}
-\caption
-{
-Synthetic spectra at four viewing angles in the clumpy model. Plot would look different probably,
-and may show composites, but this would be the main synthetic spectrum plot.
-}
-\label{fig:uvspec}
-\end{figure*}
-
-\begin{figure*}
-\centering
-\includegraphics[width=1.0\textwidth]{figures/opt.eps}
-\caption
-{
-Figure designed to show optical spectrum and comparison to composite.
-}
-\label{fig:uvspec}
-\end{figure*}
-
-\begin{figure*}
-\centering
-\includegraphics[width=1.0\textwidth]{figures/alpha_ox_both.eps}
-\caption
-{
-X-ray properties of the H13 and clumped model (text filled 
-squares), plotted against monochromatic luminosity 
-at 2500\AA. Also plotted are the samples considered by
-Saez et al. 2012 on a similar plot; The COMBI-7 AGN sample (ref),
-the BQS sample (ref) and the Saez et al. (2012) sample of BALQSOs.
-}
-\label{fig:xray}
-\end{figure*}
-
-\begin{figure}
-\centering
-\includegraphics[width=0.5\textwidth]{figures/xray_spectrum_lnu.eps}
-\caption
-{
-Broadband SEDs compared to IR and X-ray SEDs for selected BALQSOs 
-from Grupe \& Nousek (2015).
-}
-\label{fig:xray}
-\end{figure}
+\begin{table}
+\begin{tabular}{p{3cm}p{4cm}}
+\hline Free Parameters 	&	 Value \\ 
+\hline \hline 
+$M_{BH}$ 	 &	 $1\times 10^9~\rm{M_{\odot}}$ \\ 
+$\dot{M}_{acc}$ 	 &	 $5~M_{\odot}yr^{-1} \simeq 0.2~\dot{M}_{Edd}$\\ 
+$\alpha_X$ 	 &	 $-0.9$ \\ 
+$L_{X} $ 	 &	 $10^{45}~\rm{ergs~s^{-1}}$\\ 
+$r_{disc}(min)=r_{X}$   &	 $6r_g=8.8\times10^{14}~{\rm cm}$ \\ 
+$r_{disc}(max)$   &	 $3400r_g = 5\times10^{17}~{\rm cm}$ \\ 
+$\dot{M}_{wind}$  &	 $5~M_{\odot}yr^{-1}$ \\ 
+$r_{min}$ 	&	 $300r_{g} = 4.4\times10^{16}~{\rm cm}$\\ 
+$r_{max}$ 	&	 $600r_{g} = 8.8\times10^{16}~{\rm cm}$ \\ 
+$\theta_{min}$ 	&	 $70.0^{\circ}$ \\ 
+$\theta_{max}$ 	&	 $82.0^{\circ}$ \\ 
+$\lambda$ 	&	 $0$ \\ 
+$v_{\infty}$ 	&	 $v_{esc}$(f=1) \\ 
+$R_v$ 	        &	 $10^{19}$cm \\ 
+$\alpha$ 	&	 $1.0$ \\
+$f$ 	&	 $0.01$ \\
+\hline 
+% Derived Parameters 	&	 Value \\ 
+% \hline \hline
+% $L_{\nu}(2500\mbox{\scriptsize{\AA}})$&	 $6.3\times10^{30}~\rm{ergs~s^{-1}~Hz^{-1}}$\\ 
+% $L_{\nu}(2keV)$   &	 $1.2\times10^{25}~\rm{ergs~s^{-1}~Hz^{-1}}$\\ 
+% $L_{bol}$ 	 &	 $2.4\times10^{46}~\rm{ergs~s^{-1}}$\\
+% $M_{bol}$ 	 &	 -27.4\\ 
+% $M_u$            &	 -26.2\\ 
+%  $\alpha_{OX} $ 	 &	 -2.2\\ 
+\end{tabular}
+\caption{Wind geometry parameters used in the model.}
+\label{wind_param}
+\end{table}
 
@@
 in Quasars and BALQSOs, while adopting a realistic $2-10$ keV X-ray luminosity
-of $L_{X}=10^{43}~\rm{ergs~s^{-1}}$. Without clumping, this wind would be over-ionized 
+of $L_{X}=10^{45}~\rm{ergs~s^{-1}}$. Without clumping, this wind would be over-ionized 
 to the extent that opacities in e.g., \civ\ would be entirely negligible (see H13).
@@
 
-Present a spectrum of the UV and possible optical too.
+\begin{figure*} %fullpage
+\centering
+\includegraphics[width=0.8\textwidth]{figures/uvspec.eps}
+\caption
+{
+Synthetic spectra at four viewing angles in the clumpy model. Plot would look different probably,
+and may show composites, but this would be the main synthetic spectrum plot.
+}
+\label{fig:uvspec}
+\end{figure*} %fullpage
+
+\begin{figure*} %fullpage
+\centering
+\includegraphics[width=1.0\textwidth]{figures/opt.eps}
+\caption
+{
+Figure designed to show optical spectrum and comparison to composite.
+}
+\label{fig:uvspec}
+\end{figure*} %fullpage
+
+Figure 4 shows the synthetic spectrum in the UV from the two models, with the
+benchmark model from H13 also shown for comparison. We also show a comparison
+to composite quasar and BALQSO spectra in figure 5, with the optical waveband 
+included. In the UV, strong BAL profiles are formed in both models. This
+highlights the first success of our model: clumping allows the correct ionization state 
+to be maintained in the presence of strong X-rays. 
+The BAL profiles are saturated, 
+and generally show the strongest absorption at the terminal velocity.
+This contradicts observed profiles of many BALQSOs (REFs), 
+although there are some objects which do show this behaviour (REFs). 
+However, we have found that this profile shape is by no means ubiquitous.
+Figure 6 shows how the line profile varies with angle for three of the UV lines
+(see also section 4.4). In addition, the line profile
+shape is strongly dependent on the density, ionization and velocity 
+profiles intersected by the line of sight. Thus, small tweaks of the velocity
+law and angular distributions of streamlines can dramatically alter
+the line profile shape. Figure ?? shows selection of line profiles 
+for different kinematic parameters to demonstrate this. 
+The degeneracy between parameters, and lack of available
+physical and observational constraints goes someway to showing why individual 
+fitting of line profile shapes with kinematic models is such a difficult
+exercise.
+
+We find that model A can produce significant line emission
+at low inclinations, particular in \civ, 
+and the improved treatment of recombination results in a strong \la\
+line. However, the red wing of the BAL profiles 
+is far stronger than seen in BALQSO spectra and composites.
+This is due to a combination of strong collisionally excited emission
+and continuum attenuation. To illustrate the amount of 
+continuum attenuation we also show the continuum from a disc-only model.
+The line-to-continuum ratios at low inclinations are also
+significantly affected by disc foreshortening and limb darkening.
+The angular distribution of the disc radiation is clearly
+crucially important in determining the emergent line equivalent widths 
+(EWs) -- this is discussed further in section~5.
+
+To assess the ability of the model to match real 
+quasar spectra, we show a comparison to an HST quasar composite in figure 5. 
+All the spectra are normalised to the flux at 2000\AA in these plots.
+Model A matches the \civ\ line profile well, but the \la\ profile
+is a factor of $\sim3$ weaker than in the composite spectrum.
+Figure 5 also shows the spectrum into the optical,
+showing that the outflow produces signiciant optical emission lines
+as well as having a noticeable effect on the continuum shape. This
+is particularly true around the Balmer jump at $3646\AA$ and is due to
+a prominent wind-formed recombination continuum.
 
 \subsection{X-ray Properties and Broadband SEDs}
+
+\begin{figure*} %fullpage
+\centering
+\includegraphics[width=1.0\textwidth]{figures/alpha_ox_both.eps}
+\caption
+{
+X-ray properties of the H13 and clumped model (text filled 
+squares), plotted against monochromatic luminosity 
+at 2500\AA. Also plotted are the samples considered by
+Saez et al. 2012 on a similar plot; The COMBI-7 AGN sample (ref),
+the BQS sample (ref) and the Saez et al. (2012) sample of BALQSOs.
+}
+\label{fig:xray}
+\end{figure*} %fullpage
+
+\begin{figure}
+\centering
+\includegraphics[width=0.5\textwidth]{figures/xray_spectrum_lnu.eps}
+\caption
+{
+Broadband SEDs compared to IR and X-ray SEDs for selected BALQSOs 
+from Grupe \& Nousek (2015).
+}
+\label{fig:xray}
+\end{figure}
 
@@
 \smallskip
+\item We have shown that the degree of ionization stratification
+in the model is sufficient that LoBAL line profiles
+are seen at a subset of viewing angles. 
+\smallskip
 \item We find that clumping also causes a significant 
@@
 We would like to thank Omer Blaes, Ivan Hubeny, Shane Davis, 
-Michael Crenshaw, Nahum Arav, Daniel Proga,
+Michael Crenshaw, Nahum Arav, Daniel Proga, Daniel Capellupo, Dirk Grupe etc.
 

### 2015-07-20 paper_mnras.tex
added more text

@@
 J.~H.~Matthews$^1$\thanks{jm8g08@soton.ac.uk}, C.~Knigge$^1$,
-N.~Higginbottom$^1$, K.~S.~Long$^2$, S.~A.~Sim$^3$, and S.~W.~Mangham$^1$
+N.~Higginbottom$^1$, K.~S.~Long$^2$, S.~A.~Sim$^3$ and S.~W.~Mangham$^1$
 }
@@
 outflows are ubiquitous in AGN
-and quasars (REFs). These outflows can take the form of 
-highly collimated radio jets \citep{bellonijet2010}(BETTER REF), 
-or mass-loaded `winds' emanating from the accretion disc. 
+and quasars \citep{kellerman1989,ganguly2008}. These outflows can take the form of 
+highly collimated radio jets \citep[e.g.][]{hazard1963,potash1980,perley1984,marscher2006}, 
+or mass-loaded `winds' emanating from the accretion disc 
+\citep{weymann1991,turnermiller2009}. 
+Outflows in AGN offer a 
+natural feedback mechanism through which the central source can 
+affect its environment \citep{king2003,king2005,fabian2012}
+-- feedback that is required by models of galaxy evolution (REFs) 
+and may explain the `$M-\sigma$' relation \citep{silkrees1998,haring2004}.
+
 Approximately $20\%$ of quasars exhibit broad absorption lines (BALs) in the ultraviolet,
@@
 Several possible driving mechanisms for ADWs have been proposed, including
-thermal pressure (REFs), magnetocentrifugal forces \citep{blandfordpayne} and 
-radiation pressure on spectral lines \citep[`line-driving'][]{lucysolomon1970, MCGV95}.
-Of these, line-driving is possibly the most attractive, due 
-to the strong absorption lines seen in BALQSOs and the X-ray spectra of AGN (REFs).
-The presence of line-locked features \citep{bowler2014} and the so-called `ghost of \la' \citep{arav1996}
-in the spectra of such objects also gives clearer evidence that line-driving is
+thermal pressure \citep{weymann1982, begelman1991}, magnetocentrifugal forces 
+\citep{blandfordpayne,pelletier_pudritz} and 
+radiation pressure on spectral lines \citep[`line-driving';][]{lucysolomon1970,shlosman1985,MCGV95}.
+Of these, line-driving is possibly the most attractive, as
+strong absorption lines are already seen in BALQSOs and the X-ray spectra of AGN 
+\citep{reeves2003,poundsreeves2009,tombesi2010a}.
+The presence of line-locked features \citep{bowler2014} 
+and the `ghost of \la' (Arav et al. 1996; Arav 1996; North 2006; but see 
+also Cottis et al. 2010) \nocite{arav1995, arav1996, north2006,cottis2010}
+in the spectra of some BALQSOs also gives clearer evidence that line-driving is
 at least partially contributing to the acceleration of the wind.
+
 The efficiency of line-driving is crucially dependent on the ionization state 
@@
 
-Here we describe the results from our model.
+Here we describe the results from our model. This set of parameters
+was arrived at by conducting a limited grid search over a 
+5-dimensional parameter space involving the variables
+$r_{min}$, $\theta_{min}$, $f$, $\alpha$ and $R_V$.
+We then evaluated these models qualitavely based on the following
+criteria:
+
+\begin{itemize}
+\item Does the model maintain the correct ionization state and produce strong BALs?
+\item Does strong line emission emerge at low inclinations?
+\item Do H recombination lines appear in the spectrum?
+\item Do a certain range of angles produce LoBAL features?
+\end{itemize}
+
+We arrived at a model which is one of the most promising,
+but also representative of a family of models. Examination 
+of this individual model allows us to gain insight
+into fundamental geometrical and physical constraints, 
+as discussed in section 5. 
+The full grid, including output spectral files and plots can be found at
+\url{jhmatthews.github.io/agn-grid-archive}.
 
@@
 
-\begin{figure*} %fullpage
-\centering
-\includegraphics[width=0.8\textwidth]{figures/uvspec.eps}
-\caption
-{
-Synthetic spectra at four viewing angles in the clumpy model. Plot would look different probably,
-and may show composites, but this would be the main synthetic spectrum plot.
-}
-\label{fig:uvspec}
-\end{figure*} %fullpage
-
-\begin{figure*} %fullpage
-\centering
-\includegraphics[width=1.0\textwidth]{figures/opt.eps}
-\caption
-{
-Figure designed to show optical spectrum and comparison to composite.
-}
-\label{fig:uvspec}
-\end{figure*} %fullpage
-
-\begin{figure*} %fullpage
-\centering
-\includegraphics[width=1.0\textwidth]{figures/alpha_ox_both.eps}
-\caption
-{
-X-ray properties of the H13 and clumped model (text filled 
-squares), plotted against monochromatic luminosity 
-at 2500\AA. Also plotted are the samples considered by
-Saez et al. 2012 on a similar plot; The COMBI-7 AGN sample (ref),
-the BQS sample (ref) and the Saez et al. (2012) sample of BALQSOs.
-}
-\label{fig:xray}
-\end{figure*} %fullpage
-
-\begin{figure}
-\centering
-\includegraphics[width=0.5\textwidth]{figures/xray_spectrum_lnu.eps}
-\caption
-{
-Broadband SEDs compared to IR and X-ray SEDs for selected BALQSOs 
-from Grupe \& Nousek (2015).
-}
-\label{fig:xray}
-\end{figure}
+\begin{table}
+\begin{tabular}{p{3cm}p{4cm}}
+\hline Free Parameters 	&	 Value \\ 
+\hline \hline 
+$M_{BH}$ 	 &	 $1\times 10^9~\rm{M_{\odot}}$ \\ 
+$\dot{M}_{acc}$ 	 &	 $5~M_{\odot}yr^{-1} \simeq 0.2~\dot{M}_{Edd}$\\ 
+$\alpha_X$ 	 &	 $-0.9$ \\ 
+$L_{X} $ 	 &	 $10^{45}~\rm{ergs~s^{-1}}$\\ 
+$r_{disc}(min)=r_{X}$   &	 $6r_g=8.8\times10^{14}~{\rm cm}$ \\ 
+$r_{disc}(max)$   &	 $3400r_g = 5\times10^{17}~{\rm cm}$ \\ 
+$\dot{M}_{wind}$  &	 $5~M_{\odot}yr^{-1}$ \\ 
+$r_{min}$ 	&	 $300r_{g} = 4.4\times10^{16}~{\rm cm}$\\ 
+$r_{max}$ 	&	 $600r_{g} = 8.8\times10^{16}~{\rm cm}$ \\ 
+$\theta_{min}$ 	&	 $70.0^{\circ}$ \\ 
+$\theta_{max}$ 	&	 $82.0^{\circ}$ \\ 
+$\lambda$ 	&	 $0$ \\ 
+$v_{\infty}$ 	&	 $v_{esc}$(f=1) \\ 
+$R_v$ 	        &	 $10^{19}$cm \\ 
+$\alpha$ 	&	 $1.0$ \\
+$f$ 	&	 $0.01$ \\
+\hline 
+% Derived Parameters 	&	 Value \\ 
+% \hline \hline
+% $L_{\nu}(2500\mbox{\scriptsize{\AA}})$&	 $6.3\times10^{30}~\rm{ergs~s^{-1}~Hz^{-1}}$\\ 
+% $L_{\nu}(2keV)$   &	 $1.2\times10^{25}~\rm{ergs~s^{-1}~Hz^{-1}}$\\ 
+% $L_{bol}$ 	 &	 $2.4\times10^{46}~\rm{ergs~s^{-1}}$\\
+% $M_{bol}$ 	 &	 -27.4\\ 
+% $M_u$            &	 -26.2\\ 
+%  $\alpha_{OX} $ 	 &	 -2.2\\ 
+\end{tabular}
+\caption{Wind geometry parameters used in the model.}
+\label{wind_param}
+\end{table}
 

### 2015-07-23 paper.tex
finished for the day

@@
 \def\rmxaa{RMXAA}
+\def\aaps{A\&As}
 
@@
 {
-The effect of clumpy outflows
-and disc anisotropy on quasar unification scenarios
+Modelling quasar outflows:
+clumpy winds and broad emission lines
 }
@@
 
-The spectral energy distributions (SEDs) of 
+The spectra of 
 quasars and luminous active galactic nuclei (AGN) 
@@
 Outflows in AGN offer a 
-natural feedback mechanism through which the central source can 
+potential feedback mechanism through which the central source can 
 affect its environment \citep{king2003,king2005,fabian2012}
--- feedback that is required by models of galaxy evolution (REFs) 
+-- feedback that is required in models of galaxy evolution (REFs) 
 and may explain the `$M-\sigma$' relation \citep{silkrees1998,haring2004}.
@@
 intercepting the line of sight. Depending on viewing angle, an observer 
-may then see a BALQSO, LoBAL-QSO or normal `Type 1' quasar.
+may then see a BALQSO or normal `Type 1' quasar.
 Within this framework, the broad-line region (BLR) is normally
 assumed to correspond to the dense wind base.
+There are various spectroscopic sub-classifications of BALQSOs: 
+HiBALQSOs, which only exhibit higher
+ionization line absorption; LoBALQSOs which also show
+absorption in lower ionization state species such as \mg\ and \al; and
+FeLoBALQSOs which show further absorption in Fe~\textsc{ii} and \textsc{iii}.
+In unified models, this is generally attributed to ionization stratification
+of the outflow \citep[e.g.][]{elvis2000}.
+
 % As well as acting as a source of photoionized plasma, a 
-A disc wind may also have a profound effect on the structure and 
-emergent continuum of the accretion disc itself.
+As well as imprinting clear line absorption features,
+disc wind may also have a profound effect on the structure and 
+emergent {\em continuum} of the accretion disc itself.
 Mass-loss will alter the accretion rate and resultant 
@@
 that if one includes a combination of mass-loss, general relativity (GR) and Comptonisation
-then AGN SEDs can, in general, be fitted well with accretion disc models.
+then AGN spectral energy distributions (SEDs) can, in general, be fitted well with accretion disc models.
 Mass-loss therefore appears to be critical if an $\alpha$-disc
@@
 field could still reach the previously shielded regions in those particular models.
-
-An alternative solution is that the wind is clumped (REFs), possibly on multiple scale lengths.
-Local density enhancements could lower the ionization parameter of the plasma
-while still maintaining the same mass-loss rate and column density. 
-Clumping is expected in outflows and the BLR in a number of separate models
-with different motivations.
-
-Physically, clumping can be present due to magnetic confinement of 
-dense regions (REFs) or the instabilities that are theoretically predicted 
-in line-driven winds (REFs).
+An alternative solution is that the wind is clumped \citep[e.g.][]{hamann2013}
+possibly on multiple scale lengths. Local density enhancements could lower the 
+ionization parameter of the plasma while still maintaining the same mass-loss 
+rate and column density.
+
+Evidence for dense substructures in AGN winds is widespread.
+BALQSOs show complex absorption line profiles \citep{ganguly2006, simonhamann2010}
+and exhibit variability in these profile shapes \citep{capellupo2011,capellupo2012,capellupo2014}.
+AGN generally show variability in X-ray absorption components \citep[e.g.][]{risaliti2002}
+and many models for the BLR consist of clumps embedded in an outflow 
+\citep{krolik1981, emmering1992, dekool1995, cassidyraine1996}.
+Clumping can be caused by magnetic confinement \cite{dekool1995},
+or the instabilities inherent to line-driven winds 
+\citep{lucysolomon1970,macgregor1979,carlberg1980,owockirybicki1984,owockirybicki1985}.
+Additionally, clumping is required in line-driven hot star winds 
+in order to explain observations \citep{hillier1991eswingsmodel}. Complex substructures 
+on a variety of scales are also produced in simulations of line-driven 
+outflows in AGN \citep{PSK2000,PK04,progakurosawa2010,proga2014}.
+Clumpy winds therefore offer an observationally motivated and theoretically 
+predicted way to lower the ionization state of a plasma, possibly in tandem
+with a shielding scenario.
 
@@
 
-In this paper, we attempt to test the disc wind paradigm 
-using Monte Carlo radiative transfer and photoionization calculations.
-In section 2, we describe our code. In section 3, we briefly discuss some 
-of the successes and failures of our previous benchmark model for BALQSOs 
-\citep[][hereafter H13]{higginbottom2013} and outline the model, including 
+There has been some success using simple
+kinematic prescriptions for biconical disc winds to model 
+AGN and quasar outflows \citep{simlong2008,higginbottom2013}. 
+\cite[][hereafter H13]{higginbottom2013},
+successfully produced a benchmark model for BALQSOs. However, the model
+had two key drawbacks. Firstly, an unrealistically low X-ray luminosity
+was required in order to prevent over-ionization of the outflow.
+Secondly, the model failed to produce the strong emission lines 
+required at low inclinations in a unified model.
+In this paper, we attempt to address these issues, and test the disc wind 
+unification model using Monte Carlo radiative transfer (MCRT) and photoionization 
+calculations. The paper is organised as follows.
+In section 2, we describe our code. In section 3, we outline the model, including 
 a description of our clumping prescription. In section 4, we present the results 
-from a clumped model which successfully reproduces
-the observed ionization state while maintaing realistic X-ray properties.
-In section 5 we discuss our results, focussing particular on the anisotropy of 
+from a clumped model. In section 5 we discuss our results, 
+focussing particular on the anisotropy of 
 disc emission and GR effects, and finally, in section 6, we summarise our findings.
@@
 through the system are described in terms of indivisible
-energy quanta interacting with either `simple ions'
+energy quanta of radiant or kinetic energy 
+(`$r-$packets' and `$k-$packets' respectively; see also section 2.3).
+These energy packets interacting with either `simple ions'
 or `macro-atoms'. The macro-atom implementation 
 is described in full by \cite{lucy2002, lucy2003}.
-The scheme allows one to treat non-LTE line transfer without
-approximation for elements which are identified as 
+The scheme allows one to treat non-LTE line transfer in radiative equilibrium
+without approximation for elements which are identified as 
 full macro-atoms, while maintaining the fast `two-level' 
@@
 we model the SED in a cell using the technique described by H13. In this scheme,
-the mean intensity in a series of bands is modeled as a normalised power law 
+the mean intensity in a series of bands is modeled as a normalised power law in 
+frequency $\nu$
 \begin{equation}
@@
 \end{equation}
-or an exponential 
+for a band $j$, or an exponential 
 \begin{equation}
-J_{\nu,j}=K_{exp}e^{(-h\nu/kT_{exp})}.
+J_{\nu,j}=K_{exp} e^{(-h\nu/k T_{exp})}.
 \end{equation}
-The photoionization rate from ion $i$ can then be written as
-
+Here, $K_{exp}$, $K_{pl}$, $T_{exp}$ and $\alpha_{pl}$ are spectral fit parameters
+deduced from the band-limited radiation field estimators.
+The ionization rate out of ion $i$ can then be written as 
 \begin{equation}
 R_{i,i+1}(J)= 
-\displaystyle{n_i \sum_{band~j=0}^{n}}~{\int_{\nu_j}^{~\nu_j+1}{J_{\nu,j}\sigma_i(\nu)\nu^{-1}d\nu}},
+\displaystyle{
+n_i \left(C_{i} n_e + 
+\sum_{band~j=0}^{n}~
+{\int_{\nu_j}^{~\nu_j+1}{J_{\nu,j}\sigma_i(\nu)\nu^{-1}d\nu}}
+\right),}
 \end{equation}
-while the radiative recombination rate is simply given by 
+where $\sigma_i$ is the photoionization cross-section and $C_{i}$
+represents the collisional ionization coefficient.
+The recombination rate {\em into} ion $i$ is simply given by 
 \begin{equation}
-R_{i+1,i}(T_e) = \alpha_{i+1,i} n_{i+1} n_e
+R_{i+1,i}(T_e) = (\alpha^i_{RR} + \alpha^i_{DR} + \alpha^i_{CR}) n_{i+1} n_e
 \end{equation}
-$\alpha_{i+1,i}$ here is the recombination rate coefficient from the ground state
-of the upper ion to the ground state of the lower ion- we thus neglect recombination
-to and from excited states in this calculation. In addition to these
-radiative rates, we include dielectronic recombination and collisional ionization
-as additive processes. We assume dilute level populations 
-for simple-ions.
+Where each $\alpha$ here is the recombination rate coefficient into the ground state of ion $i$.
+The subscripts denote radiative, dielectronic and 
+collisional (three-body) recombination respectively.
+We thus neglect recombination to and from excited states in the simple-ion calculation. 
+For simple-ions, we use a dilute Boltzmann equation to calculate 
+the population of level $k$ in ionic stage $j$,
+\begin{equation}
+\frac{n_{jk}}{n_j} = \frac{W g_k}{z_j(T_R)} \exp(-E_k/kT_R).
+\end{equation}
+Here $z_j$ is the partition function of ionic stage $j$,
+$T_R$ is the effective radiation temperature,
+$E_k$ is the energy difference between level $k$ and the ground state,
+and $g_k$ is the statistical weight of level $k$.
 
@@
 % and in principle allows the direct addition of extra physical processes such as Auger ionization, which would have to be approximated if using the previous technique.
+\subsection{Physical Processes}
+
+We include all free-free, bound-free and bound-bound heating
+and cooling processes in the model. For radiative transfer purposes
+we treat electron scattering in the Thomson limit, 
+but take full account of Compton heating and cooling when
+calculating the thermal balance of the plasma (see H13).
+Adiabatic cooling is included and represents the only
+departure from strict radiative equilibrium, but is insignificant 
+in most of the outflow.
+It is dealt with self consistently by the spontaneous destruction
+of $k$-packets with a probability
+
+\begin{equation}
+P_{\rm{adiabatic~destruction}} = \frac{C_{\rm{adiabatic}}}{C_{\rm{total}}},
+\end{equation}
+where $C_{\rm{adiabatic}}$ and ${C_{\rm{total}}}$ represent the 
+adiabatic and total cooling rates in the cell.
 
@@
 
-We use the same atomic data as described by LK02 and since
-updated by H13 and M15, with the addition of direct ionization data from Dere (xxxx). 
+We use the same atomic data as described by LK02 and since updated by H13 and M15, 
+with the addition of direct ionization data from \cite{dere2007}. 
 Photoionization cross-sections are from \textsc{Topbase} \citep{cunto1993} and  \cite{vfky}.
-We use dielectronic recombination from \cite{badnell2006} and free-free 
-Gaunt factors from \cite{sutherland1998}.
+Dielectronic and radiative recombination rate coefficients are taken from 
+the \textsc{Chianti} database version 7.0 \citep{dere1997,landi2012}.
+We use ground state recombination rates from \cite{badnell2006} where available,
+and otherwise default to calculating recombination rates from the Milne
+relation. Free-free Gaunt factors are from \cite{sutherland1998}.
 
@@
 
-\subsection{A Benchmark Model for BALQSOs}
-
-\cite{higginbottom2013} presented a benchmark model for
-(BAL)QSOs...introduce key parameters.
-
-\subsubsection{Photon Sources}
+% \subsection{A Benchmark Model for BALQSOs}
+
+% \cite{higginbottom2013} presented a benchmark model for
+% (BAL)QSOs...introduce key parameters.
+
+\subsection{Photon Sources}
 
@@
 
-% \begin{table}
-% \begin{tabular}{p{3cm}p{4cm}}
-% \hline Free Parameters 	&	 Value \\ 
-% \hline \hline 
-% $M_{BH}$ 	 &	 $1\times 10^9~\rm{M_{\odot}}$ \\ 
-% $\dot{M}_{acc}$ 	 &	 $5~M_{\odot}yr^{-1} \simeq 0.2~\dot{M}_{Edd}$\\ 
-% $\alpha_X$ 	 &	 $-0.9$ \\ 
-% $L_{X} $ 	 &	 $1\times10^{43}~\rm{ergs~s^{-1}}$\\ 
-% $r_{disc}(min)=r_{X}$   &	 $6r_g=8.8\times10^{14}~{\rm cm}$ \\ 
-% $r_{disc}(max)$   &	 $3400r_g = 5\times10^{17}~{\rm cm}$ \\ 
-% $\dot{M}_{wind}$  &	 $5~M_{\odot}yr^{-1}$ \\ 
-% $r_{min}$ 	&	 $300r_{g} = 4.4\times10^{16}~{\rm cm}$\\ 
-% $r_{max}$ 	&	 $600r_{g} = 8.8\times10^{16}~{\rm cm}$ \\ 
-% $\theta_{min}$ 	&	 $70.0^{\circ}$ \\ 
-% $\theta_{max}$ 	&	 $82.0^{\circ}$ \\ 
-% $\lambda$ 	&	 $0$ \\ 
-% $v_{\infty}$ 	&	 $v_{esc}$(f=1) \\ 
-% $R_v$ 	        &	 $1\times10^{18}$cm \\ 
-% $\alpha$ 	&	 $1.0$ \\
-% \hline 
-% Derived Parameters 	&	 Value \\ 
-% \hline \hline
-% $L_{\nu}(2500\mbox{\scriptsize{\AA}})$&	 $6.3\times10^{30}~\rm{ergs~s^{-1}~Hz^{-1}}$\\ 
-% $L_{\nu}(2keV)$   &	 $1.2\times10^{25}~\rm{ergs~s^{-1}~Hz^{-1}}$\\ 
-% $L_{bol}$ 	 &	 $2.4\times10^{46}~\rm{ergs~s^{-1}}$\\
-% $M_{bol}$ 	 &	 -27.4\\ 
-% $M_u$            &	 -26.2\\ 
-%  $\alpha_{OX} $ 	 &	 -2.2\\ 
-% \end{tabular}
-% \caption{Wind geometry parameters used in the benchmark model.}
-% \label{wind_param}
-% \end{table}
-
-\subsection{Potential for unification}
-
-What was wrong with H13 model - X-rays + BELs.
+\subsection{Kinematics and Geometry}
+
+Describe briefly the kinematics and geometry of the model.
 
@@
 
-Introduce microclumping.
-
-% To take account of clumping in our outflow we adopt a simple parameterization
-% used in stellar wind modelling, known as {\em microclumping} \citep{hamann1998}. 
-% The key assumption here is that typical clump sizes
-% are much smaller than the typical photon mean free path, and thus the clumps are 
-% both geometrically and optically thin. This approach is typically 
-% known as microclumping and allows one to introduce a `filling factor', $f$, which is the 
-% fraction of the volume of the plasma filled by clumps. We can then introduce the 
-% density enhancement, $D$, which is simply
-
-% \begin{equation}
-% D = \frac{1}{f}
-% \end{equation}
-
-% One can then multiply all densities in the model by $D$, and all emitting volumes
-% by $f$, meaning that all $\rho^2$ processes 
-% (such as collisional excitation and recombination) will be enhanced, 
-% while opacities remain unchanged (for fixed ionization state). A factor $f$ is also
+To take account of clumping in our outflow we adopt a simple parameterization
+used in stellar wind modelling, known as {\em microclumping} \citep{hamann1998}. 
+The key assumption here is that typical clump sizes
+are much smaller than the typical photon mean free path, and thus the clumps are 
+both geometrically and optically thin. This approach is typically 
+known as microclumping and allows one to introduce a `filling factor', $f$, which is the 
+fraction of the volume of the plasma filled by clumps. We can then introduce the 
+density enhancement, $D$, which is simply defined as 
+\begin{equation}
+D = \frac{1}{f}.
+\end{equation}
+We then multiply all densities in the model by $D$, and all emitting volumes
+by $f$, meaning that all $\rho^2$ emissivities and opacities
+(such as collisional excitation and recombination) will be enhanced, 
+while all $\rho$ process (such as electron scattering and bound-free opacity)
+remain unchanged for a given ionization state. 
+% A factor $f$ is also
 % applied to the opacities such that opacities which scale only with $\rho$ are not
-% increased. Clumping the wind has an important effect on the ionization state and has
-% been proposed as a solution to the so-called `over-ionization problem' in 
-% disc winds (refs). This is the main motivation for incorporating microclumping
-% into our model.
+% increased.
+
+Clumping the wind has an important effect on the ionization state and has
+been proposed as a solution to the so-called `over-ionization problem' in 
+disc winds (REFs). This is the main motivation for incorporating microclumping
+into our model. This treatment is first-order; it does not adequately
+represent the complex substructures and stratifications in ionization
+state we expect in AGN outflows. Nevertheless, clumping is clearly
+important in these flows, and this parameterization allows a simple estimate
+for the effect clumping might have on the ionization state and emergent 
+line emission. It is also encouraging that microclumping has been used 
+successfully in fits to O-star wind spectra (REFs).
 
@@
 The full grid, including output spectral files and plots can be found at
-\url{jhmatthews.github.io/agn-grid-archive}.
+\url{jhmatthews.github.io/quasar-wind-grid/}.
 
@@
 system types in the framework of our model.
-[FIGURE NEEDS IMPROVING]
+%[FIGURE NEEDS IMPROVING]
 }
@@
 
-\begin{figure}
+\begin{figure} %fullpage
 \centering
-\includegraphics[width=0.5\textwidth]{figures/xray_spectrum_lnu.eps}
+\includegraphics[width=1.0\textwidth]{figures/sed_all_balqsos.eps}
 \caption
@@
 \label{fig:xray}
-\end{figure}
+\end{figure} %fullpage
 
@@
 isotropic X-ray source assumption is incorrect and BALQSOs are {\em intrinsically} 
-X-ray weak, as suggested by REFS. Nevertheless, our input X-ray spectrum
+X-ray weak \citep[e.g.][]{morabito2013}. Nevertheless, our input X-ray spectrum
 now reproduces the X-ray properties of a luminous quasar.
@@
 Figure 6 shows the broadband SED from the model, compared to a number of BALQSO spectra
-from Grupe \& Nousek (2015) - note that lower mass and super-Eddington sources
+from \cite{grupenousek2015} - note that lower mass and super-Eddington sources
 are excluded.
@@
 
-\subsection{LoBALs and trends with inclination}
+\subsection{LoBALs and ionization stratification}
+
+\begin{figure*} %fullpage
+\centering
+\includegraphics[width=1.0\textwidth]{figures/c4_with_i.eps}
+\caption
+{
+Carbon IV, Al III and Mg II line profiles with inclination for wind angles.
+Showing how the line profiles change
+and how LoBALs kick in at particularly high inclinations.
+}
+\label{fig:lobal}
+\end{figure*} %fullpage
 
@@
 
-\begin{figure*} %fullpage
-\centering
-\includegraphics[width=1.0\textwidth]{figures/c4_with_i.eps}
-\caption
-{
-Carbon IV, Al III and Mg II line profiles with inclination for wind angles.
-Showing how the line profiles change
-and how LoBALs kick in at particularly high inclinations.
-}
-\label{fig:lobal}
-\end{figure*} %fullpage
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \clearpage
-\section{Discussion}
+\section{Discussion: The Disc SED}
 
@@
 
-Can GR effects offer a potential solution? (not quite!)
-
-{\bf Figures 8 and 9: AGNSPEC F(2000) as a function of viewing angle compared to a BB disc.
-spectrum compared to composites with AGNSPEC correction.}
+General relativistic effects -- specifically, light bending
+and relativistic beaming -- can cause 
+the accretion disc SED to become more isotropic \citep[e.g.][]{zhang1997,munozdarias2013}.
+To generate GR disc spectra, we use the code \agn\ \citep{hubeny2000,davishubeny2006,davis2007}. 
+The output flux at $2000$~\AA\ as a function of inclination
+for an \agn\ model with the same disc and BH parameters
+as our clumpy wind model is shown in figure~\ref{f2000}.
+The effect of relativistic effects on disc anisotropy can be clearly seen.
+
+To examine the effect of GR on our models, we carry out the following procedure.
+First, we fit our output spectrum with a polynomial. This continuum fit can 
+be subtracted from the actual spectrum 
+to produce a model of the line emission only. We then calculate the 
+`wind continuum factor', by comparing the model fit with the emergent 
+disc spectrum without a wind. This factor gives us an approximate way to quantify the 
+effect of the wind on a disc continuum. It will generally be $>1$ at high inclinations,
+and $<1$ at low inclinations. This calculates emergent accretion disc spectra from an AGN disc atmosphere
+including relativistic effects. Finally, produce our final synthetic spectrum 
+by convolving this the line emission spectrum with the \agn\ model for the model parameters.
+
+Figure 10 shows the resultant spectrum. Including GR clearly helps
+
+% Can GR effects offer a potential solution? (not quite!)
+
+% {\bf Figures 8 and 9: AGNSPEC F(2000) as a function of viewing angle compared to a BB disc.
+% spectrum compared to composites with AGNSPEC correction.}
 
@@
 
-A brief comment, citing Goodrich / Krolik \& Voit on the 
-way in which anisotropy / attenuation affect the inferred
-BAL fraction. We also need to be aware that there will be a number of selection
-effects in building up the composites, and we should discuss these
-and the subtleties involved.
+The disc SED has a profound effect on the intrinsic BAL fraction
+inferred from flux-limited samples. This in turn impacts on 
+the geometry and covering factor assumed for BALQSO and unified wind models,
+and even effects the efficiency of feedback.
+\cite{krolik1998} noted that the effect of limb darkening and foreshortening
+would result in a signicantly underestimated covering factor for BALQSO winds.
+The effect is complicated further by the quasar luminosity function -- if 
+BALQSOs have lower observed luminosities for given accretion disc properties 
+then they may be drawn from a different bin in the quasar luminosity function 
+\citep{goodrich1997}. These effects are understandably not taken into account
+by current estimates of the intrinsic BALQSO fraction \citep{weymann1991, reichard2003, knigge2008, turnermiller2009, allen2011}.
+% These factors will also combine in the building-up 
+% of BALQSO composite spectra, and mean that is very difficult to 
+% disentangle the true nature of BALQSOs
+% without BH mass and eddington ratio estimates.
+The way forward is somewhat unclear. 
+Given the lack of available observational constraints, models cannot readily 
+be used to inform the selection criteria when calculating the BALQSO fraction.
+Nevertheless, understanding the true nature of the disc SED, including the
+angular distribution of radiation, is clearly crucial in order
+to accurately estimate the true covering factor of BALQSO winds.
+
+% A brief comment, citing Goodrich / Krolik \& Voit on the 
+% way in which anisotropy / attenuation affect the inferred
+% BAL fraction. We also need to be aware that there will be a number of selection
+% effects in building up the composites, and we should discuss these
+% and the subtleties involved.
 

### 2015-07-23 paper_mnras.tex
finished for the day

@@
 
-\begin{figure}
+\begin{figure*}
 \centering
-\includegraphics[width=0.5\textwidth]{figures/xray_spectrum_lnu.eps}
+\includegraphics[width=1.0\textwidth]{figures/sed_all_balqsos.eps}
 \caption
@@
 \label{fig:xray}
-\end{figure}
+\end{figure*}
 

### 2015-07-30 paper.tex
nearly there for first draft

@@
 \usepackage{url}
-%\usepackage{epsfig}
+%\usepackage{pngfig}
 %\usepackage[dvips]{color}
@@
 {
-Modelling quasar outflows:
-clumpy winds and broad emission lines
+% Modelling quasar outflows:
+% clumpy winds and broad emission lines
+Unifying quasars with clumpy wind models
 }
@@
 work in which a benchmark model for BAL quasars was produced. 
+We have conducted a limited parameter search with the aim of unifying quasar phenomenology,
+and arrive at an improved model. The grid is now publicly available.
 We find that a simple treatment of clumping (`microclumping') 
@@
 and find good agreement with existing X-ray samples of AGN and QSOs.
-We find that clumping enhances the H recombination and collisionally excited resonance lines,
-causing strong line emission (EW=?) to emerge at the low inclination angles, 
+We find that the dense, X-ray heated wind 
+produces strong H recombination and collisionally excited resonance 
+line emission to emerge at the low inclination angles, 
 which represent quasars within this unification scenario.
@@
 % this results in significant line emission in Lyman~$\alpha$ and the Balmer series.
-However, we are unable to produce line emission with comparable equivalent widths
-to existing quasar composites, due to a fundamental constraint arising
-from the anisotropy of emission from a classical thin disc. We briefly 
-explore the effect of relativistic beaming, gravitational redshift and 
+However, we are unable to reproduce the remarkably similar of line-to-continuum
+ratios between BAL and non-BAL quasar composites.
+This is due to a fundamental constraint arising
+from the anisotropy of emission from a classical thin disc. 
+We briefly explore the effect of relativistic beaming, gravitational redshift and 
 light bending on the angular distribution of disc continuum emission. 
 We find that these general relativistic effects do cause the disc to
-emit more isotropically, but this is not yet sufficient to produce a
-self-consistent model. We discuss a number of potential solutions. 
+emit slightly more isotropically, but this is not yet sufficient to produce a
+self-consistent model. We discuss wind reprocessing as a potential solution.
 Overall, our work suggests that geometric unification
@@
 % Determining the true geometry of ADWs and uncovering the true disc spectral 
-% (and angular) energy distribution are key next steps if we are to build up a 
+% (and angular) energy distribution are key next stpng if we are to build up a 
 % holistic picture of the quasar population.
@@
 
-Approximately $20\%$ of quasars exhibit broad absorption lines (BALs) in the ultraviolet,
+Approximately $20\%$ of quasars exhibit blueshifted ($\sim 0.1c$)
+broad absorption lines (BALs) in the ultraviolet,
 providing clear evidence for outflowing absorbing material
@@
 As well as imprinting clear line absorption features,
-disc wind may also have a profound effect on the structure and 
+disc winds may also have a profound effect on the structure and 
 emergent {\em continuum} of the accretion disc itself.
@@
 The efficiency of line-driving is crucially dependent on the ionization state 
-of the outflowing plasma. \cite{MCGV95} proposed a potential solution: 
+of the outflowing plasma, meaning that it is difficult to prevent 
+the wind becoming over-ionized and `failing' in the presence of strong X-rays. 
+\cite{MCGV95} proposed a potential solution: 
 a region of `hitchhiking gas' that could shield the wind from the central X-ray source. 
@@
 kinematic prescriptions for biconical disc winds to model 
-AGN and quasar outflows \citep{simlong2008,higginbottom2013}. 
-\cite[][hereafter H13]{higginbottom2013},
-successfully produced a benchmark model for BALQSOs. However, the model
+AGN and quasar outflows \citep[][hereafter H13]{simlong2008,sim2010,higginbottom2013}. 
+H13 successfully produced a benchmark model for BALQSOs. However, the model
 had two key drawbacks. Firstly, an unrealistically low X-ray luminosity
@@
 calculations. The paper is organised as follows.
-In section 2, we describe our code. In section 3, we outline the model, including 
-a description of our clumping prescription. In section 4, we present the results 
+In section 2, we describe some of the important photoionization 
+and MCRT aspects of the code. In section 3, we outline the model, including 
+a description of our clumping implementation. In section 4, we present the results 
 from a clumped model. In section 5 we discuss our results, 
@@
 calculations in non-local thermodynamic equilibrium (non-LTE). 
-The code is described extensively by a series of authors (LK02, S05, H13, M15).
-For that reason we only briefly describe the key elements of the global 
+The has been used to model accreting white dwarfs 
+(Long \& Knigge 2002, hereafter LK02; Noebauer et al. 2010; 
+Matthews et al. 2015, hereafter M15), young-stellar objects \citep{simmacro2005}
+and quasars (H13). \nocite{noebauer, M15, LK02}
+These studies contain extensive detail on the code, 
+so we only briefly describe the key elements of the global 
 ionization calculation and other important aspects.
@@
 (`$r-$packets' and `$k-$packets' respectively; see also section 2.3).
-These energy packets interacting with either `simple ions'
-or `macro-atoms'. The macro-atom implementation 
+These energy packets interact with either two-level `simple ions'
+or full `macro-atoms'. The macro-atom implementation 
 is described in full by \cite{lucy2002, lucy2003}.
-The scheme allows one to treat non-LTE line transfer in radiative equilibrium
+Our scheme allows one to treat non-LTE line transfer in radiative equilibrium
 without approximation for elements which are identified as 
@@
 treatment of resonance lines when elements are identified 
-as simple-ions. In this study,
+as simple-ions (see M15). In this study,
 only H \& He are treated as macro-atoms, because 
 we expect recombination to be important
-in determining their level populations (see M15).
+in determining their level populations and resultant line emission.
 
@@
 \end{equation}
-Where each $\alpha$ here is the recombination rate coefficient into the ground state of ion $i$.
+Where each $\alpha^i$ here is the recombination rate coefficient into the ground state of ion $i$.
 The subscripts denote radiative, dielectronic and 
@@
 in most of the outflow.
-It is dealt with self consistently by the spontaneous destruction
-of $k$-packets with a probability
-
-\begin{equation}
-P_{\rm{adiabatic~destruction}} = \frac{C_{\rm{adiabatic}}}{C_{\rm{total}}},
-\end{equation}
-where $C_{\rm{adiabatic}}$ and ${C_{\rm{total}}}$ represent the 
-adiabatic and total cooling rates in the cell.
+% It is dealt with self consistently by the spontaneous destruction
+% of $k$-packets with a probability
+
+% \begin{equation}
+% P_{\rm{adiabatic~destruction}} = \frac{C_{\rm{adiabatic}}}{C_{\rm{total}}},
+% \end{equation}
+% where $C_{\rm{adiabatic}}$ and ${C_{\rm{total}}}$ represent the 
+% adiabatic and total cooling rates in the cell.
 
@@
 \centering
-\includegraphics[width=0.45\textwidth]{figures/fig2_cartoon.eps}
+\includegraphics[width=0.45\textwidth]{figures/fig2_cartoon.png}
 \caption
@@
 The accretion disc in our model is geometrically thin, but optically thick
-and this adopt a standard multi-temperature blackbody
+and thus adopt a standard multi-temperature blackbody
 using a \cite{shakurasunyaev1973} temperature profile.
+
 The emergent SED is thus determined by the specified accretion rate ($\dot{m}$)
 and central BH mass ($M_{BH}$).
+All photon sources in our model are assumed opaque, meaning
+that photons which strike them are destroyed.
 The inner radius of the disc extends to the innermost 
@@
 The X-ray source in our model is treated as an isotropic sphere at the ISCO,
-which emits photons according to a power law with index $\alpha_X$.
-The normalisation of this power law is such that it produces the specified 
-2-10kev luminosity.
+which emits r-packets according to a power law in flux with index $\alpha_X$ such that
+\begin{equation}
+F_X (\nu) = K \nu^{\alpha_X}.
+\end{equation}
+The normalisation, $K_X$ of this power law is such that it 
+produces the specified 2-10~keV luminosity, $L_X$.
 In addition to the disc and X-ray source, 
@@
 Instead, this reprocessing is dealt with by enforcing strict
-radiative equilibrium via an indivisible energy packet
-constraint (see Lucy 2002, M15).
+radiative equilibrium ({\em modulo} adiabatic cooling)
+via an indivisible energy packet
+constraint (see Lucy 2002, M15; also section 2.3).
 % \begin{equation}
@@
 
-Describe briefly the kinematics and geometry of the model.
+In this prescription, a biconical disc wind rises from the accretion 
+disc between launch radii $r_{min}$ and $r_{max}$.
+The opening angles of the wind are set to $\theta_{min}$ and $\theta_{max}$.
+The poloidal velocity along each individual streamline at a poloidal distance $l$ 
+is then given by
+\begin{equation}
+v_l=v_0+\left[v_{\infty}(r_0)-v_0\right]\frac{\left(l/R_v\right)^{\alpha}}{\left(l/R_v\right)^{\alpha}+1},
+\label{v_law}
+\end{equation}
+where $v_0$ is the velocity at the base of the streamline, $\alpha$ is
+an exponent governing how quickly the wind accelerations and 
+$R_v$ is the `acceleration length', defined as the distance at which
+the outflow reaches half of its terminal velocity, $v_{\infty}$.
+The terminal velocity is set to a fixed multiple of the escape
+velocity, $v_{esc}$ at the base of the streamline (radius $r_0$).
+The rotational velocity, $v_{\phi}$, is initially Keplerian ($v_k = [GM/r_0]^{1/2}$),
+and the wind conserves specific angular momentum such that 
+\begin{equation}
+v_{\phi} r = v_k r_0.
+\label{v_law}
+\end{equation}
+The velocity law is crucial in determining the output spectra,
+as it affects not only the projected velocities along the line of sight,
+but also the density and ionization state of the outflow.
+A wind which accelerates more slowly will have a denser wind base
+with correspondingly different ionization and emission characteristics.
 
@@
 line emission. It is also encouraging that microclumping has been used 
-successfully in fits to O-star wind spectra (REFs).
+successfully in fits to O-star wind spectra \citep{hillier1991eswingsmodel}.
 
@@
 
-Here we describe the results from our model. This set of parameters
+Here we describe the results from our model, the parameters
+of which are shown in table~1.
+Parameters differing from the benchmark model of
+H13 are highlighted with an asterisk.
+This set of parameters
 was arrived at by conducting a limited grid search over a 
@@
 $r_{min}$, $\theta_{min}$, $f$, $\alpha$ and $R_V$.
-We then evaluated these models qualitavely based on the following
+The full grid, including output spectral files and plots can be found at
+\url{jhmatthews.github.io/quasar-wind-grid/}.
+We evaluated these models qualitavely based on the following
 criteria:
-
 \begin{itemize}
@@
 \item Do a certain range of angles produce LoBAL features?
+\item Does the model compare favourably to quasar composite spectra?
 \end{itemize}
-
 We arrived at a model which is one of the most promising,
-but also representative of a family of models. Examination 
-of this individual model allows us to gain insight
+but also broadly representative of a family of models. 
+Examination of this individual model allows us to gain insight
 into fundamental geometrical and physical constraints, 
-as discussed in section 5. 
-The full grid, including output spectral files and plots can be found at
-\url{jhmatthews.github.io/quasar-wind-grid/}.
+as discussed in section 5, and assess the models potential
+for unification.
 
@@
 \centering
-\includegraphics[width=1.0\textwidth]{figures/wind.eps}
+\includegraphics[width=1.0\textwidth]{figures/wind.png}
 \caption
@@
 The solid black line marks a sphere at $1000~R_G$.
-The dotted lines show the $75^\circ$ and $80^\circ$ sightlines 
+The dotted lines show the $72^\circ$ and $78^\circ$ sightlines 
 to the centre of the system, and illustrate that different sightlines
@@
 \centering
-\includegraphics[width=0.5\textwidth]{figures/sightlines.eps}
+\includegraphics[width=0.5\textwidth]{figures/sightlines.png}
 \caption
@@
 $\alpha_X$ 	 &	 $-0.9$ \\ 
-$L_{X} $ 	 &	 $10^{45}~\rm{ergs~s^{-1}}$\\ 
+$L_{X} $ 	 &	 $10^{45}~\rm{ergs~s^{-1}}$$^*$ \\ 
 $r_{disc}(min)=r_{X}$   &	 $6r_g=8.8\times10^{14}~{\rm cm}$ \\ 
@@
 $\lambda$ 	&	 $0$ \\ 
-$v_{\infty}$ 	&	 $v_{esc}$(f=1) \\ 
-$R_v$ 	        &	 $10^{19}$cm \\ 
-$\alpha$ 	&	 $1.0$ \\
-$f$ 	&	 $0.01$ \\
+$v_{\infty}(r_0)$ 	&	 $v_{esc}(r_0)$ \\ 
+$R_v$  	        &	 $10^{19}$cm$^*$ \\ 
+$\alpha$ 	&	 $0.6^*$ \\
+$f$ 	&	 $0.01^*$  \\
 \hline 
@@
 By clumping the wind, we are able to produce the range of ionization states observed
-in Quasars and BALQSOs, while adopting a realistic $2-10$ keV X-ray luminosity
+in wuasars and BALQSOs, while adopting a realistic $2-10$ keV X-ray luminosity
 of $L_{X}=10^{45}~\rm{ergs~s^{-1}}$. Without clumping, this wind would be over-ionized 
@@
 This explains why a factor of 100 increase in X-ray luminosity requires
-a clumping factor of 0.01, even though the value of U changes by roughly ?? compared to 
-H13.
+a clumping factor of 0.01, even though the value of U decreases by only a factor of $\sim10$ 
+compared to H13. This is also the reason for significant Lyman edge photoabsorption
+at the highest inclinations (see section 4.3).
 
@@
 \centering
-\includegraphics[width=0.8\textwidth]{figures/uvspec.eps}
+\includegraphics[width=1.0\textwidth]{figures/uvspec.png}
 \caption
@@
 
-\begin{figure*} %fullpage
-\centering
-\includegraphics[width=1.0\textwidth]{figures/opt.eps}
-\caption
-{
-Figure designed to show optical spectrum and comparison to composite.
-}
-\label{fig:uvspec}
-\end{figure*} %fullpage
+% \begin{figure*} %fullpage
+% \centering
+% \includegraphics[width=1.0\textwidth]{figures/opt.png}
+% \caption
+% {
+% Figure designed to show optical spectrum and comparison to composite.
+% }
+% \label{fig:uvspec}
+% \end{figure*} %fullpage
 
@@
 to be maintained in the presence of strong X-rays. 
-The BAL profiles are saturated, 
-and generally show the strongest absorption at the terminal velocity.
-This contradicts observed profiles of many BALQSOs (REFs), 
-although there are some objects which do show this behaviour (REFs). 
-However, we have found that this profile shape is by no means ubiquitous.
-Figure 6 shows how the line profile varies with angle for three of the UV lines
-(see also section 4.4). In addition, the line profile
-shape is strongly dependent on the density, ionization and velocity 
+The BAL profiles are often saturated, and the location in velocity space
+of the strongest absorption in the profile varies with inclination.
+At lower inclinations, the strongest absorption occurs at the red edge,
+whereas at high inclinations (and for the strongest BALs)
+the trough has a sharp edge at the terminal velocity.
+This offers one potential explanation for the wide range of BALQSO absorption
+line shapes (see e.g. Trump et al. 2006; Knigge et al 2008).
+In addition, the line profile shape is strongly dependent 
+on the density, ionization and velocity 
 profiles intersected by the line of sight. Thus, small tweaks of the velocity
 law and angular distributions of streamlines can dramatically alter
-the line profile shape. Figure ?? shows selection of line profiles 
-for different kinematic parameters to demonstrate this. 
-The degeneracy between parameters, and lack of available
-physical and observational constraints goes someway to showing why individual 
-fitting of line profile shapes with kinematic models is such a difficult
-exercise.
-
-We find that model A can produce significant line emission
+the shape of the line.
+% the line profile shape. Figure ?? shows selection of line profiles 
+% for different kinematic parameters to demonstrate this. 
+% The degeneracy between parameters, and lack of available
+% physical and observational constraints goes someway to showing why individual 
+% fitting of line profile shapes with kinematic models is such a difficult
+% exercise.
+
+We find that the model can produce significant line emission
 at low inclinations, particular in \civ, 
 and the improved treatment of recombination results in a strong \la\
-line. However, the red wing of the BAL profiles 
-is far stronger than seen in BALQSO spectra and composites.
+line. In the context of unification, this is a promising results, 
+and shows that a biconical wind can produce significant 
+emission at `quasar-like' angles.
+However, the red wing of the BAL profiles 
+is generally stronger than seen in BALQSO spectra and composites.
 This is due to a combination of strong collisionally excited emission
@@
 To assess the ability of the model to match real 
-quasar spectra, we show a comparison to an HST quasar composite in figure 5. 
-All the spectra are normalised to the flux at 2000\AA in these plots.
-Model A matches the \civ\ line profile well, but the \la\ profile
-is a factor of $\sim3$ weaker than in the composite spectrum.
-Figure 5 also shows the spectrum into the optical,
-showing that the outflow produces signiciant optical emission lines
-as well as having a noticeable effect on the continuum shape. This
-is particularly true around the Balmer jump at $3646\AA$ and is due to
-a prominent wind-formed recombination continuum.
+quasar spectra, we also show {\sl Sloan Digital Sky Survey} (SDSS) quasar composites from
+\cite{reichard2003}, normalised to the flux at 2000\AA\ in each panel.
+The model matches the \civ\ and \mg\ line profiles fairly well, 
+but the \la\ profile is a factor of $\sim3$ weaker than in the composite spectrum.
+This is implies that a larger recombination line formation region is required in order 
+to successfully reproduce the strong \la\ emission seen in 
+all quasars. At the highest inclinations, the 
+cooler, lower ionization material at the base of the wind
+starts to intersect the line of sight. This produces 
+multiple absorption lines lower ionization species such as \mg,
+\al and Fe~\textsc{ii}, as well as strong Lyman continuum absorption.
+The potential links to LoBALQSOs and FeLoBALQSOs are discussed in section 2.4.
+% Figure 5 also shows the spectrum into the optical,
+% showing that the outflow produces signiciant optical emission lines
+% as well as having a noticeable effect on the continuum shape. This
+% is particularly true around the Balmer jump at $3646\AA$ and is due to
+% a prominent wind-formed recombination continuum.
 
@@
 \centering
-\includegraphics[width=1.0\textwidth]{figures/alpha_ox_both.eps}
+\includegraphics[width=1.0\textwidth]{figures/alpha_ox_both.png}
 \caption
@@
 at 2500\AA. Also plotted are the samples considered by
-Saez et al. 2012 on a similar plot; The COMBI-7 AGN sample (ref),
-the BQS sample (ref) and the Saez et al. (2012) sample of BALQSOs.
+Saez et al. 2012 on a similar plot; The COMBI-7 AGN and
+the BQS samples Steffen et al. (2006) and the Saez et al. (2012) sample of BALQSOs.
+The dotted lines show the best fit relations for non-BALQSOs from Steffen et al. (2006).
 }
@@
 
-\begin{figure} %fullpage
-\centering
-\includegraphics[width=1.0\textwidth]{figures/sed_all_balqsos.eps}
-\caption
-{
-Broadband SEDs compared to IR and X-ray SEDs for selected BALQSOs 
-from Grupe \& Nousek (2015).
-}
-\label{fig:xray}
-\end{figure} %fullpage
-
-The bottom panel of figure~\ref{fig:xray} shows the emergent $L_{2keV}$ 
-monochromatic luminosity ($L_\nu$) and $\alpha_{OX}$ plotted against 
+% \begin{figure} %fullpage
+% \centering
+% \includegraphics[width=1.0\textwidth]{figures/sed_all_balqsos.png}
+% \caption
+% {
+% Broadband SEDs compared to IR and X-ray SEDs for selected BALQSOs 
+% from Grupe \& Nousek (2015).
+% }
+% \label{fig:xray}
+% \end{figure} %fullpage
+
+Figure~\ref{fig:xray} shows the emergent
+monochromatic luminosity ($L_\nu$) at 2~keV and $\alpha_{OX}$ plotted against 
 $L_\nu$ at $2500$\AA\ for a number of different viewing angles in our model.
@@
 \begin{equation}
-\alpha_{OX}=0.3838\log\left(\frac{L_{\nu}(2~keV)}{L_{\nu}(2500~\mbox{\scriptsize{\AA}})}\right).
+\alpha_{OX}=0.3838\log\left(\frac{L_{\nu}(2~keV)}{L_{\nu}(2500~\mbox{\scriptsize{\AA}})}\right),
 \end{equation}
 
-The properties are calculated from the synthetic spectra and thus include
+which effectively represents a near-UV to X-ray flux ratio and a measure of X-ray 
+weakness. The properties are calculated from the synthetic spectra and thus include
 the effects of wind reprocessing and attenuation. In addition to model outputs,
 we also show the BALQSO sample of Saez et al. (2012) and luminous AGN and quasar
-samples from Steffen et al. (2006). For low inclination, `quasar-like' viewing angles,
+samples from Steffen et al. (2006). The best fit relations from Steffen et al. (2006)
+are also shown.
+For low inclination, `quasar-like' viewing angles,
 we now show excellent agreement with AGN samples. The trend with inclination
@@
 Although the low inclination, `BALQSO-like' viewing angles show moderate agreement with the data,
-it appears that our models tend to underpredict the emergent X-ray luminosity at 
+it appears that our models tend to over-predict the emergent X-ray luminosity at BAL angles, 
 although we are limited by poor statistics. 
-It is possible that this is due to our wind being overly optically thick to 
-electron scattering at angles which look through the wind. It could also be that the
-isotropic X-ray source assumption is incorrect and BALQSOs are {\em intrinsically} 
-X-ray weak \citep[e.g.][]{morabito2013}. Nevertheless, our input X-ray spectrum
-now reproduces the X-ray properties of a luminous quasar.
+% It is possible that this is due to our wind being overly optically thick to 
+% electron scattering at angles which look through the wind. 
+It could also be that the isotropic X-ray source assumption 
+is incorrect and BALQSOs are {\em intrinsically} 
+X-ray weak \citep[e.g.][]{morabito2013}. 
+an anisotropic X-ray source might result in a lower clumping factor being
+required in our model.
+Nevertheless, our input X-ray spectrum
+now reproduces the X-ray properties of a luminous quasar,
+and at least some BAL angles match the .
 
@@
 of $N_H\sim10^{23}~\rm{cm^{-2}}$ 
-\citep{green1996,brandt2000,mathur2000,green2001,grupemathur2003}.
+\citep{green1996,mathur2000,green2001,grupemathur2003}.
 This is often cited as evidence that the BAL outflow is shielded from
 the X-ray source, especially as sources with strong X-ray absorption tend
-to exhibit deep BAL troughs and high outflow velocities (REFs).
+to exhibit deep BAL troughs and high outflow velocities 
+\citep{brandt2000,laorbrandt2002,gallagher2006}.
 Our results tend to imply that a clumpy BAL outflow
-itself can be responsible for the strong X-ray absorption, and possibly 
-explains why mini-BALs have weaker X-ray absorption than BALQSOs 
-\citep[e.g.][]{brandt2000,hamann2013}.
-
-We can also examine the emergent X-ray spectra from our model. 
-Our code is not yet optimized for producing X-ray spectra, as we do not yet 
-include all lines and levels of e.g. Fe or macro-atom treatments of 
-higher order ions (cf. Sim et al. 2008, 2010). 
-However, the bound-free opacity sources are complete, and comparisons of the shape
-of the heavily absorbed spectra can be useful.
-Figure 6 shows the broadband SED from the model, compared to a number of BALQSO spectra
-from \cite{grupenousek2015} - note that lower mass and super-Eddington sources
-are excluded.
+itself can be responsible for the strong X-ray absorption, 
+and supports Hamann et al.'s (2013) suggestion that 
+this explains the weaker X-ray absorption in mini-BALs 
+compared to BALQSOs.
+
+% We can also examine the emergent X-ray spectra from our model. 
+% Our code is not yet optimized for producing X-ray spectra, as we do not yet 
+% include all lines and levels of e.g. Fe or macro-atom treatments of 
+% higher order ions (cf. Sim et al. 2008, 2010). 
+% However, the bound-free opacity sources are complete, and comparisons of the shape
+% of the heavily absorbed spectra can be useful.
+% Figure 6 shows the broadband SED from the model, compared to a number of BALQSO spectra
+% from \cite{grupenousek2015} - note that lower mass and super-Eddington sources
+% are excluded.
 
@@
 \centering
-\includegraphics[width=1.0\textwidth]{figures/c4_with_i.eps}
+\includegraphics[width=1.0\textwidth]{figures/c4_angles.png}
 \caption
 {
-Carbon IV, Al III and Mg II line profiles with inclination for wind angles.
-Showing how the line profiles change
-and how LoBALs kick in at particularly high inclinations.
+\civ , \mg , \al\ and Fe~\textsc{ii} line profiles for wind angles
+from $72-79^\circ$. The profiles are plotted relative to the local
+continuum with an offset applied for clarity. Lower ionization
+profiles appear at a subset of high inclinations, compared
+to the ubiquitous \civ\ profile.
 }
@@
 At certain sightlines, our model now produces blue-shifted BALs in \al\ and \mg --
-the absorption lines seen in LoBALQSOs. Line profiles in velocity space 
+the absorption lines seen in LoBALQSOs, and we even see absorption in Fe~\textsc{ii}
+at the highest inclinations. Line profiles in velocity space 
 for \civ, \al\ and \mg, are shown in figure~\ref{fig:lobal} for a range
@@
 a unification model such as Elvis (2000), in which ionization stratification
-explains the incidence of LoBALQSOs. In this framework, the lower
-ionization material is intercepted by a smaller family of sightlines.
-This is also the explanation here, as shown by figure~\ref{fig:wind}.
-
-These line profiles also indicate a potential problem with our model. 
-\cite{odowd2015} find that the LoBAL profiles in H1413+117 have a 
-higher velocity onset than the higher ionization BALs, suggesting that the
-wind becomes less ionized as radius increases. 
-We find the opposite trend in velocity onsets. In addition, examination of 
-figure~\ref{fig:wind} shows that ionization parameter decreases with radius, 
-because the decrease in density wins over geometric dilution of the radiation 
-field. While the \cite{odowd2015} hypothesis comes from one object,
-it is clear that {\em at least some} BALQSOs must become less ionized at 
-higher velocities, contrary to what one expects from our modelling.
+explains the incidence of LoBALQSOs. We find, that the lower
+ionization material is intercepted by a smaller family of sightlines as shown by 
+figures~\ref{fig:wind} and \ref{fig:lobal}.
+There is also a correlation between the strength of LoBAL features
+and the amount of continuum attenuation at that sightline. 
+This offers a potential explanation for the rarity of LoBAL and
+FeLoBAL quasars (but see also section~\ref{sec:balfrac}).
+
+% These line profiles also indicate a potential problem with our model. 
+% \cite{odowd2015} find that the LoBAL profiles in H1413+117 have a 
+% higher velocity onset than the higher ionization BALs, suggesting that the
+% wind becomes less ionized as radius increases. 
+% We find the opposite trend in velocity onsets. In addition, examination of 
+% figure~\ref{fig:wind} shows that ionization parameter decreases with radius, 
+% because the decrease in density wins over geometric dilution of the radiation 
+% field. While the \cite{odowd2015} hypothesis comes from one object,
+% it is clear that {\em at least some} BALQSOs must become less ionized at 
+% higher velocities, contrary to what one expects from our modelling.
 
@@
 
-\clearpage
 \section{Discussion: The Disc SED}
 
-\subsection{Anisotropy of disc emission}
-
-Discuss the importance of the angular distribution of the disc SED on line
-(limb-darkened, foreshortened, etc.)
+When comparing BALQSO and quasar composites, it is apparent
+that they possess remarkably similar line strengths and widths 
+\citep[e.g.][]{reichard2003}.
+This presents a challenge to our model, as well as the geometric 
+unification picture in general.
+Limb darkening and foreshortening causes the disc continuum emission to be 
+strongly anisotropic. Coupled with attenuation from the wind, 
+this has the effect of enhancing the 
+line-to-continuum ratios at high inclinations, to the extent
+that the \civ\ line can have an equivalent widths of ?? at $80^\circ$
+compared to ?? at $20^\circ$. To construct a scenario where emission 
+line equivalent widths are comparable at all inclinations requires 
+significant fine-tuning when considering a classical thin disc. 
+An alternative, simpler solution is that the emergent continuum is roughly isotropic.
+This could potentially be achieved by wind reprocessing or a more realistic, GR treatment
+of the accretion disc. We briefly discuss both these possibilities.
+
+\subsection{Wind reprocessing}
+
+If the majority of continuum radiation was reprocessed by nearby photoionized plasma (such 
+as the outflow itself), then this would result in a roughly
+isotropic radiation field. There are a number of appealing aspects to this scenario.
+First, it may go some way to explaining recent microlensing (REFs) and timing (REFs)
+observations which suggest that accretion disc sizes are a factor of $\sim3$ 
+larger than one expects from a Shakura \& Sunyaev (1973) thin disc. 
+Second, it implies a wide angle, large covering factor wind in order to 
+intercept most of the disc continuum. This would make the outflow 
+an effective feedback mechanism \citep[e.g.][]{borguet2012}, 
+and would imply that BALQSO outflows
+have a similar geometry to the ultra-fast outflows seen in nearby AGN 
+\citep[e.g.][]{reeves2003,poundsreeves2009,tombesi2010a}.
+We note that spectropolarimetry of BALQSOs shows that the light from BAL troughs is $\sim10\%$ 
+linearly polarised, but the continuum generally has negligible polarisation \citep{lamy2000}.
+This suggests that the continuum of BALQSOs cannot be significantly enhanced by
+{\em single} scattering into the line of sight, but does not rule out 
+{\em multiple} scatterings leading to a more isotropic continuum.
 
@@
 To generate GR disc spectra, we use the code \agn\ \citep{hubeny2000,davishubeny2006,davis2007}. 
-The output flux at $2000$~\AA\ as a function of inclination
-for an \agn\ model with the same disc and BH parameters
-as our clumpy wind model is shown in figure~\ref{f2000}.
-The effect of relativistic effects on disc anisotropy can be clearly seen.
-
-To examine the effect of GR on our models, we carry out the following procedure.
-First, we fit our output spectrum with a polynomial. This continuum fit can 
-be subtracted from the actual spectrum 
-to produce a model of the line emission only. We then calculate the 
-`wind continuum factor', by comparing the model fit with the emergent 
-disc spectrum without a wind. This factor gives us an approximate way to quantify the 
-effect of the wind on a disc continuum. It will generally be $>1$ at high inclinations,
-and $<1$ at low inclinations. This calculates emergent accretion disc spectra from an AGN disc atmosphere
-including relativistic effects. Finally, produce our final synthetic spectrum 
-by convolving this the line emission spectrum with the \agn\ model for the model parameters.
-
-Figure 10 shows the resultant spectrum. Including GR clearly helps
+The output flux at three different wavelengths
+as a function of inclination for an \agn\ model with the same disc and BH parameters
+as our clumpy wind model is shown in figure~\ref{fig:f2000}.
+The effects of GR on an AGN disc are much less extreme 
+in the UV portion of the spectrum than the calculations
+by \cite{zhang1997} for the X-rays in X-ray binaries.
+As a result, the disc emission is still strongly anisotropic.
+GR alone therefore cannot explain the line ratio trends in quasars.
+
+% To examine the effect of GR on our models, we carry out the following procedure.
+% First, we fit our output spectrum with a polynomial. This continuum fit can 
+% be subtracted from the actual spectrum 
+% to produce a model of the line emission only. We then calculate the 
+% `wind continuum factor', by comparing the model fit with the emergent 
+% disc spectrum without a wind. This factor gives us an approximate way to quantify the 
+% effect of the wind on a disc continuum. It will generally be $>1$ at high inclinations,
+% and $<1$ at low inclinations. This calculates emergent accretion disc spectra from an AGN disc atmosphere
+% including relativistic effects. Finally, produce our final synthetic spectrum 
+% by convolving this the line emission spectrum with the \agn\ model for the model parameters.
+
+% Figure 10 shows the resultant spectrum. Including GR clearly helps
 
@@
 \centering
-\includegraphics[width=0.5\textwidth]{figures/f2000_m9.eps}
+\includegraphics[width=0.5\textwidth]{figures/agnspec.png}
 \caption
 {
-$F_{2000}$\ as a function of inclination from
-\agn\ models, compared to a classical AD. 
-{\bf This is a placeholder- it will show the effect of GR on the anisotropy
-of the disk for different wavelengths and eddington fractions, compared
-to limb darkened and foreshortened classical AD}.
+$F_\lambda$ for three different wavelengths
+as a function of inclination from \agn\ models, 
+compared to a classical AD. 
+The \agn\ models are computed for Kerr and Scharzschild
+BHs with the same $M_{BH}$ and $\dot{m}$ as our model.
 }
@@
 
-\begin{figure*} %fullpage
-\centering
-\includegraphics[width=1.0\textwidth]{figures/adjusted_withbals.eps}
-\caption
-{
-$F_\lambda$ normalised to $F_{2000}$.
+% \begin{figure*} %fullpage
+% \centering
+% \includegraphics[width=1.0\textwidth]{figures/adjusted_withbals.png}
+% \caption
+% {
+% $F_\lambda$ normalised to $F_{2000}$.
 {\bf Again, this is a placeholder- but I'm thinking some kind of comparison to composite including the adjusted continuum, showing that we can't get it exactly right}.
-}
-\label{fig:finalcomp}
-\end{figure*} %fullpage
-
-\subsection{Wind reprocessing}
-
-How would wind reprocessing help?
+% }
+% \label{fig:finalcomp}
+% \end{figure*} %fullpage
 
 \subsection{The BALQSO fraction and wind covering factor}
+\label{sec:balfrac}
 
@@
 then they may be drawn from a different bin in the quasar luminosity function 
-\citep{goodrich1997}. These effects are understandably not taken into account
-by current estimates of the intrinsic BALQSO fraction \citep{weymann1991, reichard2003, knigge2008, turnermiller2009, allen2011}.
-% These factors will also combine in the building-up 
-% of BALQSO composite spectra, and mean that is very difficult to 
-% disentangle the true nature of BALQSOs
-% without BH mass and eddington ratio estimates.
-The way forward is somewhat unclear. 
-Given the lack of available observational constraints, models cannot readily 
-be used to inform the selection criteria when calculating the BALQSO fraction.
-Nevertheless, understanding the true nature of the disc SED, including the
+\citep{goodrich1997}. This will also have a similar impact
+on the LoBALQSOs and FeLoBALQSOs sub-populations.
+The complex (and as yet unknown) selection effects are understandably 
+not taken into account by current estimates of the intrinsic BALQSO fraction 
+\citep{weymann1991, reichard2003, knigge2008, turnermiller2009, allen2011}.
+
+The way forward is somewhat unclear. Given the lack of available observational 
+constraints, models cannot readily be used to inform the selection criteria when 
+calculating the BALQSO fraction. There are two main possibilities:
+First, the disc emission is roughly isotropic, in which case the BAL fraction
+estimates should be a good estimate of the covering factor of the outflow,
+but the question about how this isotropy is achieved remains outstanding.
+Or second, the disc emission is strongly anisotropic, which follows more
+naturally from a disc geometry but has large implications
+for the inferred covering factors, as well as leaving the similar line strengths
+in BAL and non-BAL quasar compoosites unexplained (see previous sections).
+Understanding the true nature of the disc SED, including the
 angular distribution of radiation, is clearly crucial in order
@@
 % \centering
-% \includegraphics[width=0.45\textwidth]{figures/f2000_m9.eps}
+% \includegraphics[width=0.45\textwidth]{figures/f2000_m9.png}
 % \caption
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
+
 \section{Summary}
@@
 in the model is sufficient that LoBAL line profiles
-are seen at a subset of viewing angles. 
+are seen at a subset of viewing angles, and Fe~\textsc{ii}
+absorption is seen at particularly high inclinations.
 \smallskip
@@
 \smallskip
-\item The line EWs in our models are not comparable to those in Quasar composite
-spectra. This is due to a fundamental constraint discussed in section ?. If the BLR
+\item The line EWs in our models increase with inclination.
+BAL and non-BAL quasar composites have comparable EWs, so our model
+fails to reproduce this behaviour.
+This is due to a fundamental constraint discussed further in section 5. If the BLR
 emits fairly isotropically then for a foreshortened, limb-darkened classical thin accretion disc
-it is not possible to achieve line ratios at low inclinations that are comparable to
+it is simply not possible to achieve line ratios at low inclinations that are comparable to
 those at high inclinations. This is a robust conclusion which 
-is independent of the assumed BLR geometry. 
+is independent of the assumed BLR geometry and size.
 \smallskip
@@
 and GR ray-tracing code \agn. While including GR effects
-does cause the disc SED to become significantly more isotropic,
+does cause the disc SED to become slightly more isotropic,
 the effect is not large enough to produce uniform line to continuum ratios
-with viewing angle. We discuss other solutions to this problem in section ?; 
-It is possible that a combination of GR and reprocessing by the wind could provide a 
-solution, and a number of complicated selection effects may be at work
-in the building of the quasar composites.
+with viewing angle. We briefly discuss other solutions.
 \end{enumerate}
-
-Our work confirms a number of expected outcomes from such a model, and suggests 
-that a simple geometry such as this can come close to explaining much of the 
-phenomenology of quasars. Nevertheless, our conclusions pose a clear challenge 
-to the current unification picture.
+Our work confirms a number of expected outcomes from a geometric unification 
+model, and suggests that a simple biconical geometry such as this can come close to 
+explaining much of the  phenomenology of quasars. Nevertheless, our conclusions pose 
+a clear challenge to the current disc wind unification picture.
 
@@
 \bibliography{mybib.bib,stellar.bib,h14.bib,h13.bib,hamann.bib}
-\newpage
+\clearpage
+\clearpage
 %\appendix
+% \appendix
+% \section{Notes}
+
+% Here are some notes on various parts of the text.
+% \smallskip
+
+% \begin{itemize}
+% 	\item 
+% 	\item Figure 3 should be improved to include some kind of real colormap of the model
+% 	\item At the moment I haven't included another plot for the optical spectrum, or discussed
+% 	it in the paper.
+% 	\item Figure 5 needs to show a sample at the higher luminosity end, and include the actual relationship as the dotted line instead of a by eye version as is currently 
+% 	\item
+% 	\item
+% 	\item
+% 	\item
+% 	\item
+% 	\item
+% 	\item
+% \end{itemize}
+
 \end{document}

### 2015-07-30 paper_mnras.tex
nearly there for first draft

@@
 \begin{figure*}
-\centering
-\includegraphics[width=1.0\textwidth]{figures/sed_all_balqsos.eps}
-\caption
-{
-Broadband SEDs compared to IR and X-ray SEDs for selected BALQSOs 
-from Grupe \& Nousek (2015).
-}
-\label{fig:xray}
+% \centering
+% \includegraphics[width=1.0\textwidth]{figures/sed_all_balqsos.png}
+% \caption
+% {
+% Broadband SEDs compared to IR and X-ray SEDs for selected BALQSOs 
+% from Grupe \& Nousek (2015).
+% }
+% \label{fig:xray}
 \end{figure*}
 
-The bottom panel of figure~\ref{fig:xray} shows the emergent $L_{2keV}$ 
-monochromatic luminosity ($L_\nu$) and $\alpha_{OX}$ plotted against 
+Figure~\ref{fig:xray} shows the emergent
+monochromatic luminosity ($L_\nu$) at 2~keV and $\alpha_{OX}$ plotted against 
 $L_\nu$ at $2500$\AA\ for a number of different viewing angles in our model.

### 2015-07-31 paper.tex
few more mods

@@
 }
-\label{fig:uvspec}
+\label{fig:wind}
 \end{figure*} %fullpage
@@
 }
-\label{fig:lobal}
+\label{fig:sightline}
 \end{figure}
@@
 
+Figure~\ref{fig:wind} shows the physical properties of the wind.
 The wind rises slowly from the disc at first, with clumped densities
@@
 The radii of these emitting regions is important,
-and can be compared to observations. Our \civ\ line emission region 
-is located at about $1000~R_G$ ($\sim10^{18}~\rm{cm}$).
+and can be compared to observations. As shown in ~\ref{fig:wind},
+the \civ\ line in our model is typically formed between 
+$100-1000~R_G$ ($\sim10^{17}-10^{18}~\rm{cm}$).
 This is in rough agreement with the reverberation mapping 
@@
 included. In the UV, strong BAL profiles are formed in both models. This
-highlights the first success of our model: clumping allows the correct ionization state 
-to be maintained in the presence of strong X-rays. 
+highlights the first success of our model: clumping means the correct ionization state 
+is maintained in the presence of strong X-rays, allowing large resonance line opacities. 
+At the highest inclinations, the 
+cooler, lower ionization material at the base of the wind
+starts to intersect the line of sight. This produces 
+multiple absorption lines lower ionization species such as \mg,
+\al\ and Fe~\textsc{ii}, as well as strong Lyman continuum absorption.
+The potential links to LoBALQSOs and FeLoBALQSOs are discussed in section 2.4.
+
 The BAL profiles are often saturated, and the location in velocity space
@@
 to successfully reproduce the strong \la\ emission seen in 
-all quasars. At the highest inclinations, the 
-cooler, lower ionization material at the base of the wind
-starts to intersect the line of sight. This produces 
-multiple absorption lines lower ionization species such as \mg,
-\al and Fe~\textsc{ii}, as well as strong Lyman continuum absorption.
-The potential links to LoBALQSOs and FeLoBALQSOs are discussed in section 2.4.
+all quasars. We do not produce the semi-forbidden 
+intercombination lines seen in quasar spectra because we
+currently do not have a treatment for semi-forbidden lines.
+This is especially noteiceable with the strong [C~\textsc{iii}~1909\AA\, 
+line in the quasar composite spectra.
+The critical density of the [C~\textsc{iii}~1909\AA\, line 
+is $n_e\sim10^9.5~\rm{cm^{-3}}$, which is higher than much of the 
+outer portion of our wind. We therefore expect intercombination lines
+to become important coolants in the outer portion of the wind.
+
 % Figure 5 also shows the spectrum into the optical,
@@
 have a similar geometry to the ultra-fast outflows seen in nearby AGN 
-\citep[e.g.][]{reeves2003,poundsreeves2009,tombesi2010a}.
+\citep{reeves2003,poundsreeves2009,tombesi2010a}.
 We note that spectropolarimetry of BALQSOs shows that the light from BAL troughs is $\sim10\%$ 

### 2015-08-10 paper.tex
few more tweaks for CK

@@
 {
-Synthetic spectra at four viewing angles in the clumpy model. Plot would look different probably,
-and may show composites, but this would be the main synthetic spectrum plot.
+Synthetic spectra at five viewing angles in our. The coloured lines
+show different quasar and BAL quasar composites, and the dotted line shows a disc
+only continuum to show the effect of the outflow on the continuum level.
 }
@@
 
-Figure 4 shows the synthetic spectrum in the UV from the two models, with the
-benchmark model from H13 also shown for comparison. We also show a comparison
-to composite quasar and BALQSO spectra in figure 5, with the optical waveband 
-included. In the UV, strong BAL profiles are formed in both models. This
-highlights the first success of our model: clumping means the correct ionization state 
-is maintained in the presence of strong X-rays, allowing large resonance line opacities. 
+Figure 4 shows the synthetic spectrum in the UV from our model. 
+We also show a comparison
+to composite quasar and BALQSO spectra in figure 5.
+The UV spectrum is characterised by strong BAL 
+profiles at high inclinations ($> 70^\circ$). 
+This highlights the first success of our model: 
+clumping means the correct ionization state 
+is maintained in the presence of strong X-rays, 
+allowing large resonance line opacities. 
 At the highest inclinations, the 
@@
 The model matches the \civ\ and \mg\ line profiles fairly well, 
-but the \la\ profile is a factor of $\sim3$ weaker than in the composite spectrum.
+but the \la\ profile is a factor of $\sim2$ weaker than in the composite spectrum.
+
 This is implies that a larger recombination line formation region is required in order 
 to successfully reproduce the strong \la\ emission seen in 
-all quasars. We do not produce the semi-forbidden 
+all quasars.
+
+We do not produce the semi-forbidden 
 intercombination lines seen in quasar spectra because we
 currently do not have a treatment for semi-forbidden lines.
-This is especially noteiceable with the strong [C~\textsc{iii}~1909\AA\, 
+This is especially noticable with the strong C~\textsc{iii}]~1909\AA\, 
 line in the quasar composite spectra.
-The critical density of the [C~\textsc{iii}~1909\AA\, line 
-is $n_e\sim10^9.5~\rm{cm^{-3}}$, which is higher than much of the 
+The critical density of the C~\textsc{iii}]~1909\AA\, line 
+is $n_e\sim10^{9.5}~\rm{cm^{-3}}$, which is higher than much of the 
 outer portion of our wind. We therefore expect intercombination lines

### 2015-08-19 paper.tex
adding CK changes slowly

@@
 of simple-ions. We have now improved our code to explicitly solve the 
-rate equations in between ions in non-LTE. 
-Not only does this
-dispense with a number of small assumptions made in the modified Saha approach, 
-it is also more numerically stable, 
-and in principle allows the direct addition of extra physical 
-processes such as Auger ionization, which would have to be approximated 
-if using the previous technique.
-
-To avoid approximating the complex AGN SED as e.g. a dilute blackbody \citep[][M15]{ML93},
-we model the SED in a cell using the technique described by H13. In this scheme,
+rate equations between ions in non-LTE. 
+This dispenses with a number of small assumptions made in the modified Saha approach, 
+is more numerically stable, 
+and, in principle, allows the direct addition of extra physical 
+processes such as Auger ionization.
+
+%To avoid approximating the complex AGN SED as e.g. a dilute blackbody \citep[][M15]{ML93},
+We model the SED in a cell using the technique described by H13. In this scheme,
 the mean intensity in a series of bands is modeled as a normalised power law in 
@@
 represents the collisional ionization coefficient.
-The recombination rate {\em into} ion $i$ is simply given by 
+The recombination rate {\em into} ion $i$ is given by 
 \begin{equation}
-R_{i+1,i}(T_e) = (\alpha^i_{RR} + \alpha^i_{DR} + \alpha^i_{CR}) n_{i+1} n_e
+R_{i+1,i}(T_e) = (\alpha^i_{RR} + \alpha^i_{DR} + \alpha^i_{CR}) n_{i+1} n_e,
 \end{equation}
-Where each $\alpha^i$ here is the recombination rate coefficient into the ground state of ion $i$.
+where each $\alpha^i$ here is the recombination rate coefficient into the ground state of ion $i$.
 The subscripts denote radiative, dielectronic and 
-collisional (three-body) recombination respectively.
-We thus neglect recombination to and from excited states in the simple-ion calculation. 
+collisional (three-body) recombination, respectively.
+We neglect recombination to and from excited states in the simple-ion calculation. 
 For simple-ions, we use a dilute Boltzmann equation to calculate 
@@
 
-The accretion disc in our model is geometrically thin, but optically thick
-and thus adopt a standard multi-temperature blackbody
+The accretion disc in our model is geometrically thin, but optically thick.
+We thus adopt a standard multi-temperature blackbody
 using a \cite{shakurasunyaev1973} temperature profile.
 
-The emergent SED is thus determined by the specified accretion rate ($\dot{m}$)
+The emergent SED is then determined by the specified accretion rate ($\dot{m}$)
 and central BH mass ($M_{BH}$).
-All photon sources in our model are assumed opaque, meaning
+All photon sources in our model are assumed to beopaque, meaning
 that photons which strike them are destroyed.
@@
 The X-ray source in our model is treated as an isotropic sphere at the ISCO,
-which emits r-packets according to a power law in flux with index $\alpha_X$ such that
+which emits r-packets according to a power law in flux with index $\alpha_X$, of the form
 \begin{equation}
@@
 
-In this prescription, a biconical disc wind rises from the accretion 
+In our model, a biconical disc wind rises from the accretion 
 disc between launch radii $r_{min}$ and $r_{max}$.
@@
 The terminal velocity is set to a fixed multiple of the escape
-velocity, $v_{esc}$ at the base of the streamline (radius $r_0$).
+velocity, $v_{esc}$, at the base of the streamline (radius $r_0$).
 The rotational velocity, $v_{\phi}$, is initially Keplerian ($v_k = [GM/r_0]^{1/2}$),
-and the wind conserves specific angular momentum such that 
+and the wind conserves specific angular momentum, such that 
 \begin{equation}
@@
 
-To take account of clumping in our outflow we adopt a simple parameterization
-used in stellar wind modelling, known as {\em microclumping} \citep{hamann1998}. 
-The key assumption here is that typical clump sizes
-are much smaller than the typical photon mean free path, and thus the clumps are 
-both geometrically and optically thin. This approach is typically 
-known as microclumping and allows one to introduce a `filling factor', $f$, which is the 
-fraction of the volume of the plasma filled by clumps. We can then introduce the 
-density enhancement, $D$, which is simply defined as 
+To allow for clumping in our outflow we adopt a simple approximation
+used extensively in stellar wind modelling, known as 
+{\em microclumping} \citep{hamann1998}. The key assumption here is that 
+typical clump sizes are much smaller than the typical photon mean free path, 
+and thus the clumps are 
+both geometrically and optically thin. This approach 
+allows one to introduce a `filling factor', $f$, which is the 
+fraction of the volume of the plasma filled by clumps. The intra-clump
+medium is assumed to be a vacuum. We can then introduce the 
+density enhancement, $D$, which is defined as 
 \begin{equation}
@@
 \url{jhmatthews.github.io/quasar-wind-grid/}.
-We evaluated these models qualitavely based on the following
+We evaluated these models qualitatively based on the following
 criteria:
@@
 The flow then accelerates over a scale length of $R_V=10^{19}~\rm{cm}$
-up to a terminal velocity of around $3$ times the escape velocity 
+up to a terminal velocity equal to the escape velocity at the streamline base
 ($\sim10,000~\rm{km~s^{-1}}$). This gradual acceleration means that
@@
 By clumping the wind, we are able to produce the range of ionization states observed
-in wuasars and BALQSOs, while adopting a realistic $2-10$ keV X-ray luminosity
+in quasars and BALQSOs, while adopting a realistic $2-10$ keV X-ray luminosity
 of $L_{X}=10^{45}~\rm{ergs~s^{-1}}$. Without clumping, this wind would be over-ionized 
@@
 
-One commonly used measure of the ionization state is the ionization parameter, $U$, given by
+One commonly used measure of the ionization state is the ionization parameter, $U_H$, given by
 \begin{equation}
-U = \frac{4\pi}{n_H c}\int_{13.6{\rm{eV}}}^{\infty}\frac{{J_{\nu}d\nu}}{h\nu}.
+U_H = \frac{4\pi}{n_H c}\int_{13.6{\rm{eV}}}^{\infty}\frac{{J_{\nu}d\nu}}{h\nu}.
 \end{equation}
@@
 frequency. The ionization parameter represents the ratio of the number density of 
-ionizing photons to the local H density. It is however, a poor measure of the 
-ionization state of the resonance species such as \civ\ as it encodes no information
-about the shape of the SED. In this case the X-ray photons 
+H ionizing photons to the local H density. It is, however, a poor measure of the 
+ionization state of species such as \civ\ as it encodes no information
+about the shape of the SED. In our case, the X-ray photons 
 are dominant in the photoionization of the UV resonance line ions. 
 This explains why a factor of 100 increase in X-ray luminosity requires
-a clumping factor of 0.01, even though the value of U decreases by only a factor of $\sim10$ 
+a clumping factor of 0.01, even though the value of $U_H$ decreases by only a factor of $\sim10$ 
 compared to H13. This is also the reason for significant Lyman edge photoabsorption
@@
 The radii of these emitting regions is important,
-and can be compared to observations. As shown in ~\ref{fig:wind},
+and can be compared to observations. As shown in figure~\ref{fig:wind},
 the \civ\ line in our model is typically formed between 
@@
 
-The BAL profiles are often saturated, and the location in velocity space
+The high ionization BAL profiles are often saturated, and the location in velocity space
 of the strongest absorption in the profile varies with inclination.
@@
 and the improved treatment of recombination results in a strong \la\
-line. In the context of unification, this is a promising results, 
+line. In the context of unification, this is a promising result, 
 and shows that a biconical wind can produce significant 
@@
 but the \la\ profile is a factor of $\sim2$ weaker than in the composite spectrum.
-
-This is implies that a larger recombination line formation region is required in order 
-to successfully reproduce the strong \la\ emission seen in 
-all quasars.
+This is one of the main weaknesses of our models.
 

### 2015-08-27 paper.tex
version for sending to collabs

@@
 % magnetic processes. 
-Various unification schemes for
-quasars and luminous active galactic nuclei (AGN) have proposed
-that the broad emission line region is roughly cospatial
-with broad absorption line (BAL) gas and much of the phenomenology of luminous AGN
-can be explained by a simple geometrical picture involving an accretion
-disc and associated outflow. Here, we test this paradigm by 
-utilising our state-of-the-art radiative transfer code to produce synthetic spectra
-from simple biconical disc wind models. In particular, we expand on our previous 
-work in which a benchmark model for BAL quasars was produced. 
-We have conducted a limited parameter search with the aim of unifying quasar phenomenology,
-and arrive at an improved model. The grid is now publicly available.
+% Various unification schemes for
+% quasars and luminous active galactic nuclei (AGN) have proposed
+% that the broad emission line region is roughly cospatial
+% with broad absorption line (BAL) gas and much of the phenomenology of luminous AGN
+% can be explained by a simple geometrical picture involving an accretion
+% disc and associated outflow. Here, we test this paradigm by 
+% utilising our state-of-the-art radiative transfer code to produce synthetic spectra
+% from simple biconical disc wind models. 
+% In particular, we expand on our previous 
+% work in which a benchmark model for BAL quasars was produced. 
+% We have conducted a limited parameter search with the aim of unifying quasar phenomenology,
+% and arrive at an improved model. The grid is now publicly available.
+% We find that a simple treatment of clumping (`microclumping') 
+% allows for a more realistic X-ray luminosity in the model by lowering the 
+% ionization parameter. We examine the X-ray properties of this new model
+% and find good agreement with existing X-ray samples of AGN and QSOs.
+% We find that the dense, X-ray heated wind 
+% produces strong H recombination and collisionally excited resonance 
+% line emission to emerge at the low inclination angles, 
+% which represent quasars within this unification scenario.
+% % We also treat Hydrogen using a `macro-atom' approach in order to 
+% % examine the effect of recombination on Hydrogen emission lines, and
+% % this results in significant line emission in Lyman~$\alpha$ and the Balmer series.
+% However, we are unable to reproduce the remarkably similar of line-to-continuum
+% ratios between BAL and non-BAL quasar composites.
+% This is due to a fundamental constraint arising
+% from the anisotropy of emission from a classical thin disc. 
+% We briefly explore the effect of relativistic beaming, gravitational redshift and 
+% light bending on the angular distribution of disc continuum emission. 
+% We find that these general relativistic effects do cause the disc to
+% emit slightly more isotropically, but this is not yet sufficient to produce a
+% self-consistent model. We discuss wind reprocessing as a potential solution.
+% Overall, our work suggests that geometric unification
+% involving an accretion disc wind is a promising scenario, but our results 
+% pose a number of difficult challenges to such a model.
+% Determining the true geometry of ADWs and uncovering the true disc spectral 
+% (and angular) energy distribution are key next stpng if we are to build up a 
+% holistic picture of the quasar population.
+Various unification schemes for quasars and luminous active galactic nuclei (AGN) 
+propose that much of their complex phenomenology can be explained by a simple 
+geometrical picture involving an accretion disc and associated outflow.
+Here, we test this paradigm by utilising our state-of-the-art radiative transfer 
+and photoionization code to produce synthetic spectra from simple biconical disc wind models. 
+In particular, we expand on our previous work by presenting a model that
+exhibits many of the spectral features expected from a quasar unification model.
 We find that a simple treatment of clumping (`microclumping') 
-allows for a more realistic X-ray luminosity in the model by lowering the 
-ionization parameter. We examine the X-ray properties of this new model
-and find good agreement with existing X-ray samples of AGN and QSOs.
+allows for a more realistic X-ray luminosity in the model,
+while maintaining the ionization state necessary for strong BAL features. 
+We examine the X-ray properties of this new model
+and find good agreement with existing X-ray samples of AGN and quasars.
 We find that the dense, X-ray heated wind 
-produces strong H recombination and collisionally excited resonance 
-line emission to emerge at the low inclination angles, 
-which represent quasars within this unification scenario.
-% We also treat Hydrogen using a `macro-atom' approach in order to 
-% examine the effect of recombination on Hydrogen emission lines, and
-% this results in significant line emission in Lyman~$\alpha$ and the Balmer series.
-However, we are unable to reproduce the remarkably similar of line-to-continuum
-ratios between BAL and non-BAL quasar composites.
+produces strong recombination and collisionally excited line emission in, 
+e.g., \civ\ and \la, to emerge at the low inclination, `Type 1 quasar-like' angles. 
+The highest inclination models possess prominent \mg\ and \al\ BALs, the absorption 
+features seen in LoBAL quasars. Despite these successes, we are unable to reproduce 
+the remarkably uniform emission line properties 
+% remarkably similar of line-to-continuum ratios apparent 
+seen in BAL and non-BAL quasar composites.
 This is due to a fundamental constraint arising
 from the anisotropy of emission from a classical thin disc. 
-We briefly explore the effect of relativistic beaming, gravitational redshift and 
-light bending on the angular distribution of disc continuum emission. 
-We find that these general relativistic effects do cause the disc to
-emit slightly more isotropically, but this is not yet sufficient to produce a
-self-consistent model. We discuss wind reprocessing as a potential solution.
+We briefly explore the impact of general relativistic effects
+on the angular distribution of disc continuum emission, and find that 
+they are not sufficient to produce a self-consistent model.
+% relativistic beaming, gravitational redshift and 
+% light bending on the angular distribution of disc continuum emission. 
+% We find that these general relativistic effects are not yet sufficient to produce a
+% self-consistent model. 
 Overall, our work suggests that geometric unification
@@
 pose a number of difficult challenges to such a model.
-% Determining the true geometry of ADWs and uncovering the true disc spectral 
-% (and angular) energy distribution are key next stpng if we are to build up a 
-% holistic picture of the quasar population.
 \end{abstract}
@@
 with an underlying blue continuum - the so-called {\sl `big blue bump'} (BBB). 
-The BBB is normally attributed to emission from a geometrically thin, 
-optically thick accretion disc surrounding the central black hole (REF), similar
+The BBB is often attributed to emssion from a 
+geometrically thin, optically thick accretion disc surrounding the central black hole, similar
 to that described by \cite{shakurasunyaev1973}.
-In addition to the inflowing accreting material, 
+In addition to the inflowing accreting material, i
 outflows are ubiquitous in AGN
@@
 affect its environment \citep{king2003,king2005,fabian2012}
--- feedback that is required in models of galaxy evolution (REFs) 
+-- feedback that is required in models of galaxy evolution \citep{springel2005}
 and may explain the `$M-\sigma$' relation \citep{silkrees1998,haring2004}.
@@
 BAL quasars (BALQSOs) is in terms of an accretion disc wind (ADW). 
-Within this paradigm, the BALQSO fraction is associated with
+Within the ADW paradigm, a biconical wind rises from 
+the accretion disc and the BALQSO fraction is associated with
 the covering factor of the outflow. 
-In addition, ADWs may offer a natural explanation for the
+The wind is expected to be roughly equatorial from polarisation results
+\citep{goodrich1995, cohen1995}.
+ADWs offer a natural explanation for the
 diverse phenemonology of luminous AGN and QSOs \citep[e.g.][]{MCGV95, elvis2000}. 
-In such a model, a biconical wind rises from 
-the accretion disc, and the class of object is explained by the material
-intercepting the line of sight. Depending on viewing angle, an observer 
-may then see a BALQSO or normal `Type 1' quasar.
-Within this framework, the broad-line region (BLR) is normally
-assumed to correspond to the dense wind base.
-There are various spectroscopic sub-classifications of BALQSOs: 
-HiBALQSOs, which only exhibit higher
-ionization line absorption; LoBALQSOs which also show
+Depending on viewing angle, an observer 
+may see a BALQSO or normal `Type 1' quasar.
+Within this framework, the broad-line region (BLR) can 
+correspond either to the dense wind base or dense clumps embedded
+in the outflows. Indeed, \cite{elitzur2014} found that a disc-wind BLR scenario
+naturally explains the emission line evolution of AGN.
+A biconical wind model can also readily explain the various sub-classifications of BALQSOs: 
+HiBALQSOs, which only exhibit higher ionization line absorption; LoBALQSOs which also show
 absorption in lower ionization state species such as \mg\ and \al; and
@@
 % As well as acting as a source of photoionized plasma, a 
-As well as imprinting clear line absorption features,
-disc winds may also have a profound effect on the structure and 
+As well as imprinting clear line absorption and emission
+features, disc winds may also have a profound effect on the structure and 
 emergent {\em continuum} of the accretion disc itself.
@@
 temperature of the accretion disc, possibly explaining some 
-of the features we typically see in luminous AGN \citep{laordavis2014}.
-Recent results from \cite{capellupo2015} find 
-that if one includes a combination of mass-loss, general relativity (GR) and Comptonisation
-then AGN spectral energy distributions (SEDs) can, in general, be fitted well with accretion disc models.
-Mass-loss therefore appears to be critical if an $\alpha$-disc
-model is to successfully fit AGN SEDs, particular in the UV region of the spectrum.
+of the features typically seen in luminous AGN \citep{knigge1999,laordavis2014}.
+There have been numerous difficulties when confronting 
+theoretical accretion disc models with observations 
+\citep[see e.g.][]{blaes1998}. However, AGN spectral energy distributions (SEDs) can now, 
+in general, be fitted well with accretion disc models
+when the effects of general relativity (GR), Comptonisation
+and mass-loss are included \citep{capellupo2015}. Mass-loss therefore appears to be 
+critical if an accretion disc model is to successfully fit AGN SEDs, 
+particular in the UV region of the spectrum.
 
@@
 field could still reach the previously shielded regions in those particular models.
-An alternative solution is that the wind is clumped \citep[e.g.][]{hamann2013}
+An additional or alternative solution is that the wind is clumped \citep[e.g.][]{hamann2013}
 possibly on multiple scale lengths. Local density enhancements could lower the 
@@
 \citep{lucysolomon1970,macgregor1979,carlberg1980,owockirybicki1984,owockirybicki1985}.
-Additionally, clumping is required in line-driven hot star winds 
-in order to explain observations \citep{hillier1991eswingsmodel}. Complex substructures 
+Additionally, clumping is required to explain the electron scattering wings of emission lines formed
+in line-driven hot star winds \citep{hillier1991eswingsmodel}. Complex substructures 
 on a variety of scales are also produced in simulations of line-driven 
@@
 H13 successfully produced a benchmark model for BALQSOs. However, the model
-had two key drawbacks. Firstly, an unrealistically low X-ray luminosity
+had two key drawbacks. First, an unrealistically low X-ray luminosity
 was required in order to prevent over-ionization of the outflow.
-Secondly, the model failed to produce the strong emission lines 
+Second, the model failed to produce the strong emission lines 
 required at low inclinations in a unified model.
@@
 calculations in non-local thermodynamic equilibrium (non-LTE). 
-The has been used to model accreting white dwarfs 
+The code has been used to model accreting white dwarfs 
 (Long \& Knigge 2002, hereafter LK02; Noebauer et al. 2010; 
@@
 We model the SED in a cell using the technique described by H13. In this scheme,
-the mean intensity in a series of bands is modeled as a normalised power law in 
+the mean intensity in a series of $n$ bands is modeled as a normalised power law in 
 frequency $\nu$
 \begin{equation}
-J_{\nu,j}=K_{pl}\nu^{\alpha_{pl}},
+J_{\nu,i}=K_{pl}\nu^{\alpha_{pl}},
 \end{equation}
-for a band $j$, or an exponential 
+for a band $i$, or an exponential 
 \begin{equation}
-J_{\nu,j}=K_{exp} e^{(-h\nu/k T_{exp})}.
+J_{\nu,i}=K_{exp} e^{(-h\nu/k T_{exp})}.
 \end{equation}
@@
 deduced from the band-limited radiation field estimators.
-The ionization rate out of ion $i$ can then be written as 
+The ionization rate out of ion $j$ can then be written as 
 \begin{equation}
-R_{i,i+1}(J)= 
+R_{j,j+1}(J)= 
 \displaystyle{
-n_i \left(C_{i} n_e + 
-\sum_{band~j=0}^{n}~
-{\int_{\nu_j}^{~\nu_j+1}{J_{\nu,j}\sigma_i(\nu)\nu^{-1}d\nu}}
+n_i \left(C_{j} n_e + 
+\sum_{band~i=0}^{n}~
+{\int_{\nu_i}^{~\nu_i+1}{J_{\nu,i}\sigma_j(\nu)\nu^{-1}d\nu}}
 \right),}
 \end{equation}
-where $\sigma_i$ is the photoionization cross-section and $C_{i}$
+where $\sigma_j$ is the photoionization cross-section and $C_{j}$
 represents the collisional ionization coefficient.
-The recombination rate {\em into} ion $i$ is given by 
+The recombination rate {\em into} ion $j$ is given by 
 \begin{equation}
-R_{i+1,i}(T_e) = (\alpha^i_{RR} + \alpha^i_{DR} + \alpha^i_{CR}) n_{i+1} n_e,
+R_{j+1,j}(T_e) = (\alpha^j_{RR} + \alpha^j_{DR} + \alpha^j_{CR}) n_{j+1} n_e,
 \end{equation}
-where each $\alpha^i$ here is the recombination rate coefficient into the ground state of ion $i$.
+where each $\alpha^j$ here is the recombination rate coefficient into the ground state of ion $j$.
 The subscripts denote radiative, dielectronic and 
@@
 The accretion disc in our model is geometrically thin, but optically thick.
-We thus adopt a standard multi-temperature blackbody
-using a \cite{shakurasunyaev1973} temperature profile.
-
+We thus treat the disc as an ensemble of blackbodies with a 
+\cite{shakurasunyaev1973} effective temperature profile. 
 The emergent SED is then determined by the specified accretion rate ($\dot{m}$)
@@
 stable circular orbit (ISCO) of the BH. 
-We assume a Schwarzchild BH with an ISCO at $6~R_G$.
+We assume a Schwarzchild BH with an ISCO at $6~r_G$, where 
+$r_G = GM_{BH}/c^2$ is the gravitational radius.
+For a $10^9~M_\odot$ black hole, this is equal to $8.8\times10^{14}~{\rm cm}$ 
+or $\sim10^{-4}~{\rm pc}$.
+
 The X-ray source in our model is treated as an isotropic sphere at the ISCO,
@@
 Instead, this reprocessing is dealt with by enforcing strict
-radiative equilibrium ({\em modulo} adiabatic cooling)
+radiative equilibrium ({\em modulo} adiabatic cooling; see section~2.3)
 via an indivisible energy packet
-constraint (see Lucy 2002, M15; also section 2.3).
+constraint (see Lucy 2002, M15).
 % \begin{equation}
@@
 We then multiply all densities in the model by $D$, and all emitting volumes
-by $f$, meaning that all $\rho^2$ emissivities and opacities
-(such as collisional excitation and recombination) will be enhanced, 
-while all $\rho$ process (such as electron scattering and bound-free opacity)
-remain unchanged for a given ionization state. 
+by $f$. This has the effect of enhancing all emissivities and opacities
+that scale with the square of density (such as collisional excitation and recombination) 
+by a factor $D$. All processes that scale linearly with density 
+(such as electron scattering and bound-free opacity)
+will remain unchanged for a given ionization state. 
 % A factor $f$ is also
@@
 
-\section{Results}
+\section{Results and Discussion}
 
@@
 \begin{itemize}
-\item Does the model maintain the correct ionization state and produce strong BALs?
-\item Does strong line emission emerge at low inclinations?
+\item Does the model maintain the right ionization state to produce strong BALs?
+\item Does significant line emission emerge at low inclinations?
 \item Do H recombination lines appear in the spectrum?
@@
 \end{itemize}
-We arrived at a model which is one of the most promising,
-but also broadly representative of a family of models. 
-Examination of this individual model allows us to gain insight
-into fundamental geometrical and physical constraints, 
-as discussed in section 5, and assess the models potential
-for unification.
+In this section, we present one of the most promising models and discuss
+the various successes and failures.
+This allows us to gain insight into fundamental geometrical 
+and physical constraints and assess the potential for unification.
 
@@
 \centering
-\includegraphics[width=1.0\textwidth]{figures/wind.png}
+\includegraphics[width=1.0\textwidth]{figures/link.png}
 \caption
@@
 Physical properties of the outflow, shown by the coloured contours.
-The solid black line marks a sphere at $1000~R_G$.
+The solid black line marks a sphere at $1000~r_G$.
 The dotted lines show the $72^\circ$ and $78^\circ$ sightlines 
@@
 \end{figure*} %fullpage
-
-\begin{figure}
-\centering
-\includegraphics[width=0.5\textwidth]{figures/sightlines.png}
-\caption
-{
-The classes of sightlines and the corresponding possible 
-system types in the framework of our model.
-%[FIGURE NEEDS IMPROVING]
-}
-\label{fig:sightline}
-\end{figure}
 
@@
 
-One commonly used measure of the ionization state is the ionization parameter, $U_H$, given by
+One common way to quantify the ionization state of a plasma
+is through the ionization parameter, $U_H$, given by
 \begin{equation}
@@
 \noindent where $\rm{n_H}$ is the local number density of H, and $\nu$ denotes photon 
-frequency. The ionization parameter represents the ratio of the number density of 
-H ionizing photons to the local H density. It is, however, a poor measure of the 
+frequency. Shown in figure~\ref{fig:wind},
+the ionization parameter is a useful measure of the global ionization state,
+as it represents the ratio of the number density of 
+H ionizing photons to the local H density.
+It is, however, a poor representation of the 
 ionization state of species such as \civ\ as it encodes no information
@@
 the \civ\ line in our model is typically formed between 
-$100-1000~R_G$ ($\sim10^{17}-10^{18}~\rm{cm}$).
+$100-1000~r_G$ ($\sim10^{17}-10^{18}~\rm{cm}$).
 This is in rough agreement with the reverberation mapping 
@@
 
+\begin{figure}
+\centering
+\includegraphics[width=0.5\textwidth]{figures/windnew3.png}
+\caption
+{
+A cartoon describing the broad classes of sightline 
+in our model, illustrates how geometric effects lead to 
+the different emergent spectra. The colour gradient is approximate,
+but indicates the stratified ionization structure, 
+from highly ionized (yellow) to low ionization (purple) material.
+%[FIGURE NEEDS IMPROVING]
+}
+\label{fig:sightline}
+\end{figure}
+
 % \begin{figure*} %fullpage
@@
 
-Figure 4 shows the synthetic spectrum in the UV from our model. 
-We also show a comparison
-to composite quasar and BALQSO spectra in figure 5.
+Figure~\ref{fig:uvspec} shows the synthetic spectrum in the UV from our model. 
+We also show a comparison to composite quasar and BALQSO spectra.
+We show a cartoon illustrating how geometric effects determine
+the output spectra in figure~\ref{fig:sightline}.
+
+\subsubsection{Broad absorption lines}
+
 The UV spectrum is characterised by strong BAL 
@@
 starts to intersect the line of sight. This produces 
-multiple absorption lines lower ionization species such as \mg,
-\al\ and Fe~\textsc{ii}, as well as strong Lyman continuum absorption.
-The potential links to LoBALQSOs and FeLoBALQSOs are discussed in section 2.4.
+multiple absorption lines in lower ionization species such as \mg,
+\al\ and Fe~\textsc{ii}. The potential links to LoBALQSOs and 
+FeLoBALQSOs are discussed in section 2.4.
 
@@
 the shape of the line.
-% the line profile shape. Figure ?? shows selection of line profiles 
-% for different kinematic parameters to demonstrate this. 
-% The degeneracy between parameters, and lack of available
-% physical and observational constraints goes someway to showing why individual 
-% fitting of line profile shapes with kinematic models is such a difficult
-% exercise.
+
+Nonblack saturation is observed in the absorption troughs of BALQSOs \citep{arav1999a,arav1999b}.
+This can be caused either by partial covering of the continuum
+source or by scattered contributions to the BAL troughs, necessarily
+from an opacity source not cospatial with the BAL forming region.
+The scattered light explanation is supported by spectropolarimetry results
+\citep{lamy2000}. Our spectra do not show nonblack saturation.
+Instead, we find black, saturated troughs at angles $i > 73^\circ$, and the BALs
+are non-saturated at lower inclinations. The reasons for this are readily apparent. 
+First, the microclumping assumption does not allow for 
+porosity in the wind, meaning that it does not naturally produce
+a partial covering absorber. To do this, an alternative approach
+such as {\em macroclumping} would be required \citep[e.g.][]{surlan2012,hamann2008}.
+Second, our wind does not have a significant scattering 
+contribution along sightlines which do not pass through the BAL region,
+meaning that any scattered contribution is obscured by the saturated troughs.
+This suggests that either the scattering cross-section of the wind must
+be increased (with higher mass loss rates or covering factors), or 
+that an additional source of electron opacity is required, potentially
+in a polar direction above the disc.
+
+\subsubsection{Broad emission lines}
 
@@
 and shows that a biconical wind can produce significant 
-emission at `quasar-like' angles.
-However, the red wing of the BAL profiles 
-is generally stronger than seen in BALQSO spectra and composites.
-This is due to a combination of strong collisionally excited emission
-and continuum attenuation. To illustrate the amount of 
-continuum attenuation we also show the continuum from a disc-only model.
-The line-to-continuum ratios at low inclinations are also
-significantly affected by disc foreshortening and limb darkening.
-The angular distribution of the disc radiation is clearly
-crucially important in determining the emergent line equivalent widths 
-(EWs) -- this is discussed further in section~5.
-
-To assess the ability of the model to match real 
+emission at `quasar-like' angles. To assess the ability of the model to match real 
 quasar spectra, we also show {\sl Sloan Digital Sky Survey} (SDSS) quasar composites from
 \cite{reichard2003}, normalised to the flux at 2000\AA\ in each panel.
-The model matches the \civ\ and \mg\ line profiles fairly well, 
-but the \la\ profile is a factor of $\sim2$ weaker than in the composite spectrum.
-This is one of the main weaknesses of our models.
-
 We do not produce the semi-forbidden 
@@
 
+The model produces strong emission lines in \civ, \nv\ and \la,
+as well as a weak \mg\ line. The shapes and widths of these lines
+match the composites fairly well. However, the line-to-continuum ratios 
+at low inclinations in our model are significantly weaker than the quasar 
+composites. Increasing the density of the outflow, by altering the mass 
+loss rate  or velocity law, can produce more line emission.
+However, the red wing of the BAL profiles is generally stronger than 
+seen in BALQSO spectra and composites. This illustrates a fundamental 
+problem with a geometric unification model such as this:
+that the line-to-continuum ratios at low inclinations are
+significantly affected by disc foreshortening and limb darkening.
+The angular distribution of the disc radiation is clearly
+crucially important in determining the emergent line ratios.
+
+\subsubsection{The Disc SED}
+\label{discsed}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.5\textwidth]{figures/agnspec.png}
+\caption
+{
+$F_\lambda$ for three different wavelengths
+as a function of inclination from \agn\ models, 
+compared to a classical AD. 
+The \agn\ models are computed for Kerr and Scharzschild
+BHs with the same $M_{BH}$ and $\dot{m}$ as our model.
+}
+\label{fig:f2000}
+\end{figure}
+
+When comparing BALQSO and quasar composites, it is apparent
+that they possess remarkably similar line strengths and widths 
+\citep[e.g.][]{reichard2003}.
+This presents a challenge to our model, as well as the geometric 
+unification picture in general.
+Limb darkening and foreshortening causes the disc continuum emission to be 
+strongly anisotropic, yet the line emission in our models is much more isotropic. 
+This has the effect of enhancing the line-to-continuum ratios at high inclinations. 
+To construct a scenario where emission 
+line equivalent widths are comparable at all inclinations requires 
+significant fine-tuning when considering a classical thin disc. 
+An alternative, simpler solution is that the emergent continuum is roughly isotropic.
+
+General relativistic effects -- specifically, light bending
+and relativistic beaming -- can cause 
+the accretion disc SED to become more isotropic \citep[e.g.][]{zhang1997,munozdarias2013}.
+To generate GR disc spectra, we use the code \agn\ \citep{hubeny2000,davishubeny2006,davis2007}. 
+The output flux at three different wavelengths
+as a function of inclination for an \agn\ model with the same disc and BH parameters
+as our clumpy wind model is shown in figure~\ref{fig:f2000}.
+The effects of GR on an AGN disc are much less extreme 
+in the UV portion of the spectrum than the calculations
+by \cite{zhang1997} for the X-rays in X-ray binaries.
+As a result, the disc emission is still strongly anisotropic.
+GR alone therefore cannot explain the line ratio trends in quasars by making the disc
+emit more isotropically.
+This supports the findings of \cite{risaliti2011}, who find that EW distributions 
+in quasars are consistent with anisotropic emission from optically thick, 
+disc-like structures for {\em both} the continuum source and BLR. 
+We will explore these ideas further in a future study.
+
 % Figure 5 also shows the spectrum into the optical,
@@
 \centering
-\includegraphics[width=1.0\textwidth]{figures/alpha_ox_both.png}
+\includegraphics[width=1.0\textwidth]{figures/lx.png}
 \caption
 {
-X-ray properties of the H13 and clumped model (text filled 
+X-ray properties of the H13 (purple squares) and clumped model (red
 squares), plotted against monochromatic luminosity 
-at 2500\AA. Also plotted are the samples considered by
-Saez et al. 2012 on a similar plot; The COMBI-7 AGN and
-the BQS samples Steffen et al. (2006) and the Saez et al. (2012) sample of BALQSOs.
-The dotted lines show the best fit relations for non-BALQSOs from Steffen et al. (2006).
+at 2500\AA. The points are labeled according to inclination; angles
+$>70^\circ$ correspond to BALs in our scheme.
+Also plotted are the samples considered by Saez et al. 2012 on a similar plot; 
+The COMBI-7 AGN and the BQS samples Steffen et al. (2006) and the Saez et al. (2012) 
+sample of BALQSOs. The dotted lines show the best fit relations for non-BALQSOs 
+from Steffen et al. (2006).
 }
@@
 Figure~\ref{fig:xray} shows the emergent
-monochromatic luminosity ($L_\nu$) at 2~keV and $\alpha_{OX}$ plotted against 
-$L_\nu$ at $2500$\AA\ for a number of different viewing angles in our model.
-$\alpha_{OX}$ is a spectral index from near UV to X-rays defined by
-
-\begin{equation}
-\alpha_{OX}=0.3838\log\left(\frac{L_{\nu}(2~keV)}{L_{\nu}(2500~\mbox{\scriptsize{\AA}})}\right),
-\end{equation}
-
-which effectively represents a near-UV to X-ray flux ratio and a measure of X-ray 
-weakness. The properties are calculated from the synthetic spectra and thus include
+monochromatic luminosity ($L_\nu$) at 2~keV and 
+%$\alpha_{OX}$ 
+plotted against $L_\nu$ at $2500$\AA\ for a number of different viewing angles in our model.
+% $\alpha_{OX}$ is a spectral index from near UV to X-rays defined by
+% \begin{equation}
+% \alpha_{OX}=0.3838\log\left(\frac{L_{\nu}(2~keV)}{L_{\nu}(2500~\mbox{\scriptsize{\AA}})}\right),
+% \end{equation}
+% which effectively represents a near-UV to X-ray flux ratio and a measure of X-ray 
+% weakness. 
+The monochromatic luminosities are calculated from the synthetic spectra and thus include
 the effects of wind reprocessing and attenuation. In addition to model outputs,
 we also show the BALQSO sample of Saez et al. (2012) and luminous AGN and quasar
-samples from Steffen et al. (2006). The best fit relations from Steffen et al. (2006)
-are also shown.
-For low inclination, `quasar-like' viewing angles,
-we now show excellent agreement with AGN samples. The trend with inclination
-in our models is caused by a combination of disc foreshortening/limb-darkening 
+samples from Steffen et al. (2006). The best fit relation from Steffen et al. (2006) 
+is also shown. For low inclination, `quasar-like' viewing angles,
+we now show excellent agreement with AGN samples. The gradient from $20^\circ$ to
+$60^\circ$ in our models is caused by a combination of disc foreshortening/limb-darkening 
 (resulting in a lower $L_{2500}$ for higher inclinations) and the fact that the disk 
-is opaque and thus the X-ray source subtends a smaller solid angle at high inclinations
+is opaque, and thus the X-ray source subtends a smaller solid angle at high inclinations
 (resulting in a lower $L_{2keV}$ for higher inclinations).
 
-Although the low inclination, `BALQSO-like' viewing angles show moderate agreement with the data,
-it appears that our models tend to over-predict the emergent X-ray luminosity at BAL angles, 
-although we are limited by poor statistics. 
-% It is possible that this is due to our wind being overly optically thick to 
-% electron scattering at angles which look through the wind. 
-It could also be that the isotropic X-ray source assumption 
-is incorrect and BALQSOs are {\em intrinsically} 
-X-ray weak \citep[e.g.][]{morabito2013}. 
-an anisotropic X-ray source might result in a lower clumping factor being
-required in our model.
-Nevertheless, our input X-ray spectrum
-now reproduces the X-ray properties of a luminous quasar,
-and at least some BAL angles match the .
-
+The low inclination, `BALQSO-like' viewing angles show moderate agreement with the data,
+and are X-ray weak due to bound-free and electron scattering opacities in the wind.
 Typically, BALQSOs show strong X-ray absorption with columns 
@@
 \citep{brandt2000,laorbrandt2002,gallagher2006}.
-Our results tend to imply that a clumpy BAL outflow
+Our results imply that the clumpy BAL outflow
 itself can be responsible for the strong X-ray absorption, 
@@
 compared to BALQSOs.
+
+Our models slightly over-predict the emergent X-ray luminosity at BAL angles, 
+although we are limited by poor sample sizes. 
+% It is possible that this is due to our wind being overly optically thick to 
+% electron scattering at angles which look through the wind. 
+If BALQSOs were {\em intrinsically} 
+X-ray weak \citep[as suggested by, e.g.][]{morabito2013},
+our isotropic assumption foe the X-ray source would be incorrect. 
+A polar-biased X-ray source would result in a lower clumping factor being
+required in our model. Our specific wind
+prescription will also affect the opacities, densities and resultant
+ionization structure, which can change the absorption characteristics and resultant
+luminosities.
+Nevertheless, our input X-ray spectrum
+now reproduces the X-ray properties of a luminous quasar as an output,
+and at least some BAL angles match the observations.
+This satisifies the first-order requirement for the X-ray properties of 
+a unified quasar model.
 
@@
 for \civ, \al\ and \mg, are shown in figure~\ref{fig:lobal} for a range
-of BALQSO viewing angles. We confirm the behaviour expected from 
-a unification model such as Elvis (2000), in which ionization stratification
-explains the incidence of LoBALQSOs. We find, that the lower
-ionization material is intercepted by a smaller family of sightlines as shown by 
-figures~\ref{fig:wind} and \ref{fig:lobal}.
+of BALQSO viewing angles. We find that ionization stratification
+of the wind causes lower ionization material has a smaller covering factor, 
+as demonstrated by figures~\ref{fig:wind} and \ref{fig:lobal}.
+This confirms the behaviour expected from a unification model such as Elvis (2000). 
+LoBALs are only present at viewing angles close to edge-on ($i>75^\circ$),
+as predicted by polarisation results \citep{brotherton1997}.
 There is also a correlation between the strength of LoBAL features
-and the amount of continuum attenuation at that sightline. 
-This offers a potential explanation for the rarity of LoBAL and
-FeLoBAL quasars (but see also section~\ref{sec:balfrac}).
+and the amount of continuum attenuation at that sightline, particularly
+blueward of the Lyman edge as the low ionization base 
+intersects the line-of-sight. 
+Our model therefore predicts that LoBALQSOs and FeLoBALQSOs 
+have stronger Lyman edge absorption and 
+be more Compton-thick than HiBALQSOs and Type 1 quasars.
+An edge-on scenario also offers a potential explanation for the rarity of LoBAL and
+FeLoBAL quasars, due to a foreshortened and attenuated continuum, 
+although, as noted in section~\ref{discsed}, BAL fraction 
+inferences are fraught with complex selection effects.
 
@@
 
-\section{Discussion: The Disc SED}
-
-When comparing BALQSO and quasar composites, it is apparent
-that they possess remarkably similar line strengths and widths 
-\citep[e.g.][]{reichard2003}.
-This presents a challenge to our model, as well as the geometric 
-unification picture in general.
-Limb darkening and foreshortening causes the disc continuum emission to be 
-strongly anisotropic. Coupled with attenuation from the wind, 
-this has the effect of enhancing the 
-line-to-continuum ratios at high inclinations, to the extent
-that the \civ\ line can have an equivalent widths of ?? at $80^\circ$
-compared to ?? at $20^\circ$. To construct a scenario where emission 
-line equivalent widths are comparable at all inclinations requires 
-significant fine-tuning when considering a classical thin disc. 
-An alternative, simpler solution is that the emergent continuum is roughly isotropic.
-This could potentially be achieved by wind reprocessing or a more realistic, GR treatment
-of the accretion disc. We briefly discuss both these possibilities.
-
-\subsection{Wind reprocessing}
-
-If the majority of continuum radiation was reprocessed by nearby photoionized plasma (such 
-as the outflow itself), then this would result in a roughly
-isotropic radiation field. There are a number of appealing aspects to this scenario.
-First, it may go some way to explaining recent microlensing (REFs) and timing (REFs)
-observations which suggest that accretion disc sizes are a factor of $\sim3$ 
-larger than one expects from a Shakura \& Sunyaev (1973) thin disc. 
-Second, it implies a wide angle, large covering factor wind in order to 
-intercept most of the disc continuum. This would make the outflow 
-an effective feedback mechanism \citep[e.g.][]{borguet2012}, 
-and would imply that BALQSO outflows
-have a similar geometry to the ultra-fast outflows seen in nearby AGN 
-\citep{reeves2003,poundsreeves2009,tombesi2010a}.
-We note that spectropolarimetry of BALQSOs shows that the light from BAL troughs is $\sim10\%$ 
-linearly polarised, but the continuum generally has negligible polarisation \citep{lamy2000}.
-This suggests that the continuum of BALQSOs cannot be significantly enhanced by
-{\em single} scattering into the line of sight, but does not rule out 
-{\em multiple} scatterings leading to a more isotropic continuum.
-
-\subsection{General relativistic effects}
-
-General relativistic effects -- specifically, light bending
-and relativistic beaming -- can cause 
-the accretion disc SED to become more isotropic \citep[e.g.][]{zhang1997,munozdarias2013}.
-To generate GR disc spectra, we use the code \agn\ \citep{hubeny2000,davishubeny2006,davis2007}. 
-The output flux at three different wavelengths
-as a function of inclination for an \agn\ model with the same disc and BH parameters
-as our clumpy wind model is shown in figure~\ref{fig:f2000}.
-The effects of GR on an AGN disc are much less extreme 
-in the UV portion of the spectrum than the calculations
-by \cite{zhang1997} for the X-rays in X-ray binaries.
-As a result, the disc emission is still strongly anisotropic.
-GR alone therefore cannot explain the line ratio trends in quasars.
+% This could potentially be achieved by wind reprocessing or a more realistic, GR treatment
+% of the accretion disc. We briefly discuss both these possibilities.
+
+% \subsection{Wind reprocessing}
+
+% If the majority of continuum radiation was reprocessed by nearby photoionized plasma (such 
+% as the outflow itself), then this would result in a roughly
+% isotropic radiation field. There are a number of appealing aspects to this scenario.
+% First, it may go some way to explaining recent microlensing (REFs) and timing (REFs)
+% observations which suggest that accretion disc sizes are a factor of $\sim3$ 
+% larger than one expects from a Shakura \& Sunyaev (1973) thin disc. 
+% Second, it implies a wide angle, large covering factor wind in order to 
+% intercept most of the disc continuum. This would make the outflow 
+% an effective feedback mechanism \citep[e.g.][]{borguet2012}, 
+% and would imply that BALQSO outflows
+% have a similar geometry to the ultra-fast outflows seen in nearby AGN 
+% \citep{reeves2003,poundsreeves2009,tombesi2010a}.
+% We note that spectropolarimetry of BALQSOs shows that the light from BAL troughs is $\sim10\%$ 
+% linearly polarised, but the continuum generally has negligible polarisation \citep{lamy2000}.
+% This suggests that the continuum of BALQSOs cannot be significantly enhanced by
+% {\em single} scattering into the line of sight, but does not rule out 
+% {\em multiple} scatterings leading to a more isotropic continuum.
+
+% \subsection{General relativistic effects}
+
+% General relativistic effects -- specifically, light bending
+% and relativistic beaming -- can cause 
+% the accretion disc SED to become more isotropic \citep[e.g.][]{zhang1997,munozdarias2013}.
+% To generate GR disc spectra, we use the code \agn\ \citep{hubeny2000,davishubeny2006,davis2007}. 
+% The output flux at three different wavelengths
+% as a function of inclination for an \agn\ model with the same disc and BH parameters
+% as our clumpy wind model is shown in figure~\ref{fig:f2000}.
+% The effects of GR on an AGN disc are much less extreme 
+% in the UV portion of the spectrum than the calculations
+% by \cite{zhang1997} for the X-rays in X-ray binaries.
+% As a result, the disc emission is still strongly anisotropic.
+% GR alone therefore cannot explain the line ratio trends in quasars.
 
@@
 
-\begin{figure}
-\centering
-\includegraphics[width=0.5\textwidth]{figures/agnspec.png}
-\caption
-{
-$F_\lambda$ for three different wavelengths
-as a function of inclination from \agn\ models, 
-compared to a classical AD. 
-The \agn\ models are computed for Kerr and Scharzschild
-BHs with the same $M_{BH}$ and $\dot{m}$ as our model.
-}
-\label{fig:f2000}
-\end{figure}
-
 % \begin{figure*} %fullpage
@@
 
-\subsection{The BALQSO fraction and wind covering factor}
-\label{sec:balfrac}
-
-The disc SED has a profound effect on the intrinsic BAL fraction
-inferred from flux-limited samples. This in turn impacts on 
-the geometry and covering factor assumed for BALQSO and unified wind models,
-and even effects the efficiency of feedback.
-\cite{krolik1998} noted that the effect of limb darkening and foreshortening
-would result in a signicantly underestimated covering factor for BALQSO winds.
-The effect is complicated further by the quasar luminosity function -- if 
-BALQSOs have lower observed luminosities for given accretion disc properties 
-then they may be drawn from a different bin in the quasar luminosity function 
-\citep{goodrich1997}. This will also have a similar impact
-on the LoBALQSOs and FeLoBALQSOs sub-populations.
-The complex (and as yet unknown) selection effects are understandably 
-not taken into account by current estimates of the intrinsic BALQSO fraction 
-\citep{weymann1991, reichard2003, knigge2008, turnermiller2009, allen2011}.
-
-The way forward is somewhat unclear. Given the lack of available observational 
-constraints, models cannot readily be used to inform the selection criteria when 
-calculating the BALQSO fraction. There are two main possibilities:
-First, the disc emission is roughly isotropic, in which case the BAL fraction
-estimates should be a good estimate of the covering factor of the outflow,
-but the question about how this isotropy is achieved remains outstanding.
-Or second, the disc emission is strongly anisotropic, which follows more
-naturally from a disc geometry but has large implications
-for the inferred covering factors, as well as leaving the similar line strengths
-in BAL and non-BAL quasar compoosites unexplained (see previous sections).
-Understanding the true nature of the disc SED, including the
-angular distribution of radiation, is clearly crucial in order
-to accurately estimate the true covering factor of BALQSO winds.
+% \subsection{The BALQSO fraction and wind covering factor}
+% \label{sec:balfrac}
+
+% The disc SED has a profound effect on the intrinsic BAL fraction
+% inferred from flux-limited samples. This in turn impacts on 
+% the geometry and covering factor assumed for BALQSO and unified wind models,
+% and even effects the efficiency of feedback.
+% \cite{krolik1998} noted that the effect of limb darkening and foreshortening
+% would result in a signicantly underestimated covering factor for BALQSO winds.
+% The effect is complicated further by the quasar luminosity function -- if 
+% BALQSOs have lower observed luminosities for given accretion disc properties 
+% then they may be drawn from a different bin in the quasar luminosity function 
+% \citep{goodrich1997}. This will also have a similar impact
+% on the LoBALQSOs and FeLoBALQSOs sub-populations.
+% The complex (and as yet unknown) selection effects are understandably 
+% not taken into account by current estimates of the intrinsic BALQSO fraction 
+% \citep{weymann1991, reichard2003, knigge2008, turnermiller2009, allen2011}.
+
+% The way forward is somewhat unclear. Given the lack of available observational 
+% constraints, models cannot readily be used to inform the selection criteria when 
+% calculating the BALQSO fraction. There are two main possibilities:
+% First, the disc emission is roughly isotropic, in which case the BAL fraction
+% estimates should be a good estimate of the covering factor of the outflow,
+% but the question about how this isotropy is achieved remains outstanding.
+% Or second, the disc emission is strongly anisotropic, which follows more
+% naturally from a disc geometry but has large implications
+% for the inferred covering factors, as well as leaving the similar line strengths
+% in BAL and non-BAL quasar compoosites unexplained (see previous sections).
+% Understanding the true nature of the disc SED, including the
+% angular distribution of radiation, is clearly crucial in order
+% to accurately estimate the true covering factor of BALQSO winds.
 
@@
 
-We would like to thank Omer Blaes, Ivan Hubeny, Shane Davis, 
-Michael Crenshaw, Nahum Arav, Daniel Proga, Daniel Capellupo, Dirk Grupe etc.
+The work of JHM, SWM, NSH and CK is supported by the 
+Science and Technology Facilities Council (STFC), 
+via two studentships and a consolidated grant, respectively.
+We would like to thank Omer Blaes, Ivan Hubeny and Shane Davis for their
+assistance with \agn. We would also like to thank Daniel Proga, 
+Daniel Capellupo, Sam Connolly and Dirk Grupe for useful discussions.
+Simulations were conducted using \py\ version 79c, and made use of
+the IRIDIS High Performance Computing Facility at the University of Southampton.
+Figures were produced using {\tt matplotlib} \citep{matplotlib}.
 
@@
 
-\bibliography{mybib.bib,stellar.bib,h14.bib,h13.bib,hamann.bib}
+\bibliography{mybib.bib,stellar.bib,h14.bib,h13.bib,hamann.bib,krolik.bib}
 \clearpage

### 2015-08-27 paper_mnras.tex
version for sending to collabs

@@
 of simple-ions. We have now improved our code to explicitly solve the 
-rate equations in between ions in non-LTE. 
-Not only does this
-dispense with a number of small assumptions made in the modified Saha approach, 
-it is also more numerically stable, 
-and in principle allows the direct addition of extra physical 
-processes such as Auger ionization, which would have to be approximated 
-if using the previous technique.
-
-To avoid approximating the complex AGN SED as e.g. a dilute blackbody \citep[][M15]{ML93},
-we model the SED in a cell using the technique described by H13. In this scheme,
-the mean intensity in a series of bands is modeled as a normalised power law in 
+rate equations between ions in non-LTE. 
+This dispenses with a number of small assumptions made in the modified Saha approach, 
+is more numerically stable, 
+and, in principle, allows the direct addition of extra physical 
+processes such as Auger ionization.
+
+%To avoid approximating the complex AGN SED as e.g. a dilute blackbody \citep[][M15]{ML93},
+We model the SED in a cell using the technique described by H13. In this scheme,
+the mean intensity in a series of $n$ bands is modeled as a normalised power law in 
 frequency $\nu$
 \begin{equation}
-J_{\nu,j}=K_{pl}\nu^{\alpha_{pl}},
+J_{\nu,i}=K_{pl}\nu^{\alpha_{pl}},
 \end{equation}
-for a band $j$, or an exponential 
+for a band $i$, or an exponential 
 \begin{equation}
-J_{\nu,j}=K_{exp} e^{(-h\nu/k T_{exp})}.
+J_{\nu,i}=K_{exp} e^{(-h\nu/k T_{exp})}.
 \end{equation}
@@
 deduced from the band-limited radiation field estimators.
-The ionization rate out of ion $i$ can then be written as 
+The ionization rate out of ion $j$ can then be written as 
 \begin{equation}
-R_{i,i+1}(J)= 
+R_{j,j+1}(J)= 
 \displaystyle{
-n_i \left(C_{i} n_e + 
-\sum_{band~j=0}^{n}~
-{\int_{\nu_j}^{~\nu_j+1}{J_{\nu,j}\sigma_i(\nu)\nu^{-1}d\nu}}
+n_i \left(C_{j} n_e + 
+\sum_{band~i=0}^{n}~
+{\int_{\nu_i}^{~\nu_i+1}{J_{\nu,i}\sigma_j(\nu)\nu^{-1}d\nu}}
 \right),}
 \end{equation}
-where $\sigma_i$ is the photoionization cross-section and $C_{i}$
+where $\sigma_j$ is the photoionization cross-section and $C_{j}$
 represents the collisional ionization coefficient.
-The recombination rate {\em into} ion $i$ is simply given by 
+The recombination rate {\em into} ion $j$ is given by 
 \begin{equation}
-R_{i+1,i}(T_e) = (\alpha^i_{RR} + \alpha^i_{DR} + \alpha^i_{CR}) n_{i+1} n_e
+R_{j+1,j}(T_e) = (\alpha^j_{RR} + \alpha^j_{DR} + \alpha^j_{CR}) n_{j+1} n_e,
 \end{equation}
-Where each $\alpha^i$ here is the recombination rate coefficient into the ground state of ion $i$.
+where each $\alpha^j$ here is the recombination rate coefficient into the ground state of ion $j$.
 The subscripts denote radiative, dielectronic and 
-collisional (three-body) recombination respectively.
-We thus neglect recombination to and from excited states in the simple-ion calculation. 
+collisional (three-body) recombination, respectively.
+We neglect recombination to and from excited states in the simple-ion calculation. 
 For simple-ions, we use a dilute Boltzmann equation to calculate 
@@
 
-The accretion disc in our model is geometrically thin, but optically thick
-and thus adopt a standard multi-temperature blackbody
-using a \cite{shakurasunyaev1973} temperature profile.
-
-The emergent SED is thus determined by the specified accretion rate ($\dot{m}$)
+The accretion disc in our model is geometrically thin, but optically thick.
+We thus treat the disc as an ensemble of blackbodies with a 
+\cite{shakurasunyaev1973} effective temperature profile. 
+The emergent SED is then determined by the specified accretion rate ($\dot{m}$)
 and central BH mass ($M_{BH}$).
-All photon sources in our model are assumed opaque, meaning
+All photon sources in our model are assumed to beopaque, meaning
 that photons which strike them are destroyed.
@@
 stable circular orbit (ISCO) of the BH. 
-We assume a Schwarzchild BH with an ISCO at $6~R_G$.
+We assume a Schwarzchild BH with an ISCO at $6~r_G$, where 
+$r_G = GM_{BH}/c^2$ is the gravitational radius.
+For a $10^9~M_\odot$ black hole, this is equal to $8.8\times10^{14}~{\rm cm}$ 
+or $\sim10^{-4}~{\rm pc}$.
+
 The X-ray source in our model is treated as an isotropic sphere at the ISCO,
-which emits r-packets according to a power law in flux with index $\alpha_X$ such that
+which emits r-packets according to a power law in flux with index $\alpha_X$, of the form
 \begin{equation}
@@
 \url{jhmatthews.github.io/quasar-wind-grid/}.
-We evaluated these models qualitavely based on the following
+We evaluated these models qualitatively based on the following
 criteria:
 \begin{itemize}
-\item Does the model maintain the correct ionization state and produce strong BALs?
-\item Does strong line emission emerge at low inclinations?
+\item Does the model maintain the right ionization state to produce strong BALs?
+\item Does significant line emission emerge at low inclinations?
 \item Do H recombination lines appear in the spectrum?
@@
 
-One commonly used measure of the ionization state is the ionization parameter, $U$, given by
+One common way to quantify the ionization state of a plasma
+is through the ionization parameter, $U_H$, given by
 \begin{equation}
-U = \frac{4\pi}{n_H c}\int_{13.6{\rm{eV}}}^{\infty}\frac{{J_{\nu}d\nu}}{h\nu}.
+U_H = \frac{4\pi}{n_H c}\int_{13.6{\rm{eV}}}^{\infty}\frac{{J_{\nu}d\nu}}{h\nu}.
 \end{equation}
 \noindent where $\rm{n_H}$ is the local number density of H, and $\nu$ denotes photon 
-frequency. The ionization parameter represents the ratio of the number density of 
-ionizing photons to the local H density. It is however, a poor measure of the 
-ionization state of the resonance species such as \civ\ as it encodes no information
-about the shape of the SED. In this case the X-ray photons 
+frequency. Shown in figure~\ref{fig:wind},
+the ionization parameter is a useful measure of the global ionization state,
+as it represents the ratio of the number density of 
+H ionizing photons to the local H density.
+It is, however, a poor representation of the 
+ionization state of species such as \civ\ as it encodes no information
+about the shape of the SED. In our case, the X-ray photons 
 are dominant in the photoionization of the UV resonance line ions. 
 This explains why a factor of 100 increase in X-ray luminosity requires
-a clumping factor of 0.01, even though the value of U decreases by only a factor of $\sim10$ 
+a clumping factor of 0.01, even though the value of $U_H$ decreases by only a factor of $\sim10$ 
 compared to H13. This is also the reason for significant Lyman edge photoabsorption
@@
 The radii of these emitting regions is important,
-and can be compared to observations. As shown in ~\ref{fig:wind},
+and can be compared to observations. As shown in figure~\ref{fig:wind},
 the \civ\ line in our model is typically formed between 
-$100-1000~R_G$ ($\sim10^{17}-10^{18}~\rm{cm}$).
+$100-1000~r_G$ ($\sim10^{17}-10^{18}~\rm{cm}$).
 This is in rough agreement with the reverberation mapping 
@@
 starts to intersect the line of sight. This produces 
-multiple absorption lines lower ionization species such as \mg,
-\al\ and Fe~\textsc{ii}, as well as strong Lyman continuum absorption.
-The potential links to LoBALQSOs and FeLoBALQSOs are discussed in section 2.4.
-
-The BAL profiles are often saturated, and the location in velocity space
+multiple absorption lines in lower ionization species such as \mg,
+\al\ and Fe~\textsc{ii}. The potential links to LoBALQSOs and 
+FeLoBALQSOs are discussed in section 2.4.
+
+The high ionization BAL profiles are often saturated, and the location in velocity space
 of the strongest absorption in the profile varies with inclination.
@@
 and the improved treatment of recombination results in a strong \la\
-line. In the context of unification, this is a promising results, 
+line. In the context of unification, this is a promising result, 
 and shows that a biconical wind can produce significant 
-emission at `quasar-like' angles.
-However, the red wing of the BAL profiles 
-is generally stronger than seen in BALQSO spectra and composites.
-This is due to a combination of strong collisionally excited emission
-and continuum attenuation. To illustrate the amount of 
-continuum attenuation we also show the continuum from a disc-only model.
-The line-to-continuum ratios at low inclinations are also
-significantly affected by disc foreshortening and limb darkening.
-The angular distribution of the disc radiation is clearly
-crucially important in determining the emergent line equivalent widths 
-(EWs) -- this is discussed further in section~5.
-
-To assess the ability of the model to match real 
+emission at `quasar-like' angles. To assess the ability of the model to match real 
 quasar spectra, we also show {\sl Sloan Digital Sky Survey} (SDSS) quasar composites from
 \cite{reichard2003}, normalised to the flux at 2000\AA\ in each panel.
-The model matches the \civ\ and \mg\ line profiles fairly well, 
-but the \la\ profile is a factor of $\sim2$ weaker than in the composite spectrum.
-
-This is implies that a larger recombination line formation region is required in order 
-to successfully reproduce the strong \la\ emission seen in 
-all quasars.
-
 We do not produce the semi-forbidden 

### 2015-08-28 paper_mnras.tex
improved figure captions

@@
 to that described by \cite{shakurasunyaev1973}.
-In addition to the inflowing accreting material, i
+In addition to the inflowing accreting material,
 outflows are ubiquitous in AGN
@@
 as simple-ions (see M15). In this study,
-only H \& He are treated as macro-atoms, because 
+only H is treated as a macro-atom, because 
 we expect recombination to be important
-in determining their level populations and resultant line emission.
+in determining its level populations and resultant line emission.
 
@@
 {
-Synthetic spectra at five viewing angles in our. The coloured lines
+Synthetic spectra at five viewing angles in our model. The coloured lines
 show different quasar and BAL quasar composites, and the dotted line shows a disc
@@
 A cartoon describing the broad classes of sightline 
-in our model, illustrates how geometric effects lead to 
+in our model, illustrating how geometric effects lead to 
 the different emergent spectra. The colour gradient is approximate,
@@
 as a function of inclination from \agn\ models, 
-compared to a classical AD. 
-The \agn\ models are computed for Kerr and Scharzschild
-BHs with the same $M_{BH}$ and $\dot{m}$ as our model.
+compared to a classical AD. The \agn\ models are computed 
+for Kerr and Scharzschild BHs with the same $M_{BH}$ and 
+$\dot{m}$ as our model. 
 }
@@
 that they possess remarkably similar line strengths and widths 
-\citep[e.g.][]{reichard2003}.
+\citep[e.g.][]{weymann1991,reichard2003}.
 This presents a challenge to our model, as well as the geometric 
@@
 GR alone therefore cannot explain the line ratio trends in quasars by making the disc
-emit more isotropically.
-This supports the findings of \cite{risaliti2011}, who find that EW distributions 
-in quasars are consistent with anisotropic emission from optically thick, 
+emit more isotropically. This supports the findings of \cite{risaliti2011}, 
+who find that EW distributions in quasars are consistent with anisotropic emission 
+from optically thick, 
 disc-like structures for {\em both} the continuum source and BLR. 
+If this is the case, it has a dramatic affect on the intrinsic
+BAL fraction inferred from flux-limited samples \citep{goodrich1997,krolikvoit1998}.
 We will explore these ideas further in a future study.
@@
 {
-X-ray properties of the H13 (purple squares) and clumped model (red
-squares), plotted against monochromatic luminosity 
+X-ray ($2$~keV) luminosity of the our clumped model (red squares) 
+and the H13 model (purple squares), plotted against monochromatic luminosity 
 at 2500\AA. The points are labeled according to inclination; angles
-$>70^\circ$ correspond to BALs in our scheme.
+$>70^\circ$ correspond to BALs in our scheme (see figure 4).
 Also plotted are the samples considered by Saez et al. 2012 on a similar plot; 
 The COMBI-7 AGN and the BQS samples Steffen et al. (2006) and the Saez et al. (2012) 
-sample of BALQSOs. The dotted lines show the best fit relations for non-BALQSOs 
+sample of BALQSOs. The dotted line shows the best fit relation for non-BALQSOs 
 from Steffen et al. (2006).
@@
 inferences are fraught with complex selection effects.
-
-% These line profiles also indicate a potential problem with our model. 
-% \cite{odowd2015} find that the LoBAL profiles in H1413+117 have a 
-% higher velocity onset than the higher ionization BALs, suggesting that the
-% wind becomes less ionized as radius increases. 
-% We find the opposite trend in velocity onsets. In addition, examination of 
-% figure~\ref{fig:wind} shows that ionization parameter decreases with radius, 
-% because the decrease in density wins over geometric dilution of the radiation 
-% field. While the \cite{odowd2015} hypothesis comes from one object,
-% it is clear that {\em at least some} BALQSOs must become less ionized at 
-% higher velocities, contrary to what one expects from our modelling.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% DISCUSSION
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% This could potentially be achieved by wind reprocessing or a more realistic, GR treatment
-% of the accretion disc. We briefly discuss both these possibilities.
-
-% \subsection{Wind reprocessing}
-
-% If the majority of continuum radiation was reprocessed by nearby photoionized plasma (such 
-% as the outflow itself), then this would result in a roughly
-% isotropic radiation field. There are a number of appealing aspects to this scenario.
-% First, it may go some way to explaining recent microlensing (REFs) and timing (REFs)
-% observations which suggest that accretion disc sizes are a factor of $\sim3$ 
-% larger than one expects from a Shakura \& Sunyaev (1973) thin disc. 
-% Second, it implies a wide angle, large covering factor wind in order to 
-% intercept most of the disc continuum. This would make the outflow 
-% an effective feedback mechanism \citep[e.g.][]{borguet2012}, 
-% and would imply that BALQSO outflows
-% have a similar geometry to the ultra-fast outflows seen in nearby AGN 
-% \citep{reeves2003,poundsreeves2009,tombesi2010a}.
-% We note that spectropolarimetry of BALQSOs shows that the light from BAL troughs is $\sim10\%$ 
-% linearly polarised, but the continuum generally has negligible polarisation \citep{lamy2000}.
-% This suggests that the continuum of BALQSOs cannot be significantly enhanced by
-% {\em single} scattering into the line of sight, but does not rule out 
-% {\em multiple} scatterings leading to a more isotropic continuum.
-
-% \subsection{General relativistic effects}
-
-% General relativistic effects -- specifically, light bending
-% and relativistic beaming -- can cause 
-% the accretion disc SED to become more isotropic \citep[e.g.][]{zhang1997,munozdarias2013}.
-% To generate GR disc spectra, we use the code \agn\ \citep{hubeny2000,davishubeny2006,davis2007}. 
-% The output flux at three different wavelengths
-% as a function of inclination for an \agn\ model with the same disc and BH parameters
-% as our clumpy wind model is shown in figure~\ref{fig:f2000}.
-% The effects of GR on an AGN disc are much less extreme 
-% in the UV portion of the spectrum than the calculations
-% by \cite{zhang1997} for the X-rays in X-ray binaries.
-% As a result, the disc emission is still strongly anisotropic.
-% GR alone therefore cannot explain the line ratio trends in quasars.
-
-% To examine the effect of GR on our models, we carry out the following procedure.
-% First, we fit our output spectrum with a polynomial. This continuum fit can 
-% be subtracted from the actual spectrum 
-% to produce a model of the line emission only. We then calculate the 
-% `wind continuum factor', by comparing the model fit with the emergent 
-% disc spectrum without a wind. This factor gives us an approximate way to quantify the 
-% effect of the wind on a disc continuum. It will generally be $>1$ at high inclinations,
-% and $<1$ at low inclinations. This calculates emergent accretion disc spectra from an AGN disc atmosphere
-% including relativistic effects. Finally, produce our final synthetic spectrum 
-% by convolving this the line emission spectrum with the \agn\ model for the model parameters.
-
-% Figure 10 shows the resultant spectrum. Including GR clearly helps
-
-% Can GR effects offer a potential solution? (not quite!)
-
-% {\bf Figures 8 and 9: AGNSPEC F(2000) as a function of viewing angle compared to a BB disc.
-% spectrum compared to composites with AGNSPEC correction.}
-
-% \begin{figure*} %fullpage
-% \centering
-% \includegraphics[width=1.0\textwidth]{figures/adjusted_withbals.png}
-% \caption
-% {
-% $F_\lambda$ normalised to $F_{2000}$.
-{\bf Again, this is a placeholder- but I'm thinking some kind of comparison to composite including the adjusted continuum, showing that we can't get it exactly right}.
-% }
-% \label{fig:finalcomp}
-% \end{figure*} %fullpage
-
-% \subsection{The BALQSO fraction and wind covering factor}
-% \label{sec:balfrac}
-
-% The disc SED has a profound effect on the intrinsic BAL fraction
-% inferred from flux-limited samples. This in turn impacts on 
-% the geometry and covering factor assumed for BALQSO and unified wind models,
-% and even effects the efficiency of feedback.
-% \cite{krolik1998} noted that the effect of limb darkening and foreshortening
-% would result in a signicantly underestimated covering factor for BALQSO winds.
-% The effect is complicated further by the quasar luminosity function -- if 
-% BALQSOs have lower observed luminosities for given accretion disc properties 
-% then they may be drawn from a different bin in the quasar luminosity function 
-% \citep{goodrich1997}. This will also have a similar impact
-% on the LoBALQSOs and FeLoBALQSOs sub-populations.
-% The complex (and as yet unknown) selection effects are understandably 
-% not taken into account by current estimates of the intrinsic BALQSO fraction 
-% \citep{weymann1991, reichard2003, knigge2008, turnermiller2009, allen2011}.
-
-% The way forward is somewhat unclear. Given the lack of available observational 
-% constraints, models cannot readily be used to inform the selection criteria when 
-% calculating the BALQSO fraction. There are two main possibilities:
-% First, the disc emission is roughly isotropic, in which case the BAL fraction
-% estimates should be a good estimate of the covering factor of the outflow,
-% but the question about how this isotropy is achieved remains outstanding.
-% Or second, the disc emission is strongly anisotropic, which follows more
-% naturally from a disc geometry but has large implications
-% for the inferred covering factors, as well as leaving the similar line strengths
-% in BAL and non-BAL quasar compoosites unexplained (see previous sections).
-% Understanding the true nature of the disc SED, including the
-% angular distribution of radiation, is clearly crucial in order
-% to accurately estimate the true covering factor of BALQSO winds.
-
-% A brief comment, citing Goodrich / Krolik \& Voit on the 
-% way in which anisotropy / attenuation affect the inferred
-% BAL fraction. We also need to be aware that there will be a number of selection
-% effects in building up the composites, and we should discuss these
-% and the subtleties involved.
-
-% \begin{figure}
-% \centering
-% \includegraphics[width=0.45\textwidth]{figures/f2000_m9.png}
-% \caption
-% {
-% $F_\lambda$ at $2000$~\AA\ as a function of inclination from
-% \agn\ models. Spectra are computed for BH of $10^9~M_\odot$ with
-% a number of different BH spins and Eddington fractions. The black line
-% shows a standard multi-temperature blackbody AD model.
-% }
-% \label{fig:alpha_ox}
-% \end{figure}
 

### 2015-09-01 paper.tex
Knox's first set of changes, trying to commit them again

@@
 %\usepackage{pngfig}
-%\usepackage[dvips]{color}
+%\usepackage[dvips]{color}mak
 %\usepackage{aabib}
@@
 \def\aaps{A\&As}
+\def\LA{Lyman\thinspace$\alpha$}
+
+\newcommand{\EXPN}[2]{\mbox{$#1\times 10^{#2}$}}
+\newcommand{\EXPU}[3]{\mbox{\rm $#1 \times 10^{#2} \rm\:#3$}}  % exponent with units
+\newcommand{\POW}[2]{\mbox{$\rm10^{#1}\rm\:#2$}}
+\def\LUM{\:{\rm ergs\:s^{-1}}}
+\def\FLUX{\:{\rm ergs\:cm^{-2}\:s^{-1}}}
+\def\OIGS{\:{\rm ergs\:cm^{-2}\:s^{-1}\:\AA^{-1}}}
 
@@
 \parbox[t]{\textwidth}{
-J.~H.~Matthews$^1$\thanks{jm8g08@soton.ac.uk}, C.~Knigge$^1$,
-N.~Higginbottom$^1$, K.~S.~Long$^2$, S.~A.~Sim$^3$ and S.~W.~Mangham$^1$
+James~H.~Matthews$^1$\thanks{jm8g08@soton.ac.uk}, Christian~Knigge$^1$,
+Nick~Higginbottom$^1$, Knox~S.~Long$^2$, Stuart~A.~Sim$^3$ and Sam~W.~Mangham$^1$
 }
@@
 % holistic picture of the quasar population.
-Various unification schemes for quasars and luminous active galactic nuclei (AGN) 
-propose that much of their complex phenomenology can be explained by a simple 
-geometrical picture involving an accretion disc and associated outflow.
-Here, we test this paradigm by utilising our state-of-the-art radiative transfer 
-and photoionization code to produce synthetic spectra from simple biconical disc wind models. 
-In particular, we expand on our previous work by presenting a model that
-exhibits many of the spectral features expected from a quasar unification model.
+Various unification schemes have been proposed to interpret the complex phenomenology of quasars and luminous active galactic nuclei (AGN) in terms of  a simple axisymmetric picture involving a central black hole, an accretion disc and an associated outflow.
+Here, we continue our tests of  this paradigm by comparing ``average'' AGN spectra to synthetic spectra of simple biconical disc wind models, using  with our Monte Carlo radiative transfer and photoionization code {\sc Python}.
+In particular, we investigate whether clumping of the outflow allows us to produce synthetic spectra in the rest-frame UV that have the characteristics of AGN, assuming total luminosities as high as 10$^{45}$ ergs s$^{-1}$.
 We find that a simple treatment of clumping (`microclumping') 
-allows for a more realistic X-ray luminosity in the model,
-while maintaining the ionization state necessary for strong BAL features. 
-We examine the X-ray properties of this new model
+allows for a more realistic AGN luminosities,
+while maintaining the ionization state necessary for strong BAL features in the rest-frame UV. 
+We examine the X-ray properties of these simple clumped models
 and find good agreement with existing X-ray samples of AGN and quasars.
-We find that the dense, X-ray heated wind 
+The dense, X-ray heated wind 
 produces strong recombination and collisionally excited line emission in, 
 e.g., \civ\ and \la, to emerge at the low inclination, `Type 1 quasar-like' angles. 
-The highest inclination models possess prominent \mg\ and \al\ BALs, the absorption 
+At the highest inclinations, the synthetic spectra possess prominent \mg\ and \al\ BALs, the absorption 
 features seen in LoBAL quasars. Despite these successes, we are unable to reproduce 
@@
 % remarkably similar of line-to-continuum ratios apparent 
-seen in BAL and non-BAL quasar composites.
+seen in BAL and non-BAL quasar composites. {\bf This sentence needs to be more precise, especially in light ot the statement earlier in the abstract about ``good agreement''}
 This is due to a fundamental constraint arising
@@
 pose a number of difficult challenges to such a model.
+{\bf There is confusion in the abstract, at least, in what is the model and what is the synthetic spectra, as well as whether there is one model or many models.
+We need to try to be clear.
+The model should be a clumped biconical outflow.
+There are then particular instantiations of the model.
+And then there are synthetic spectra}
 \end{abstract}
@@
 to that described by \cite{shakurasunyaev1973}.
-In addition to the inflowing accreting material, i
+The lines are usually attributed to scattering and absorption of material above the disk.
+{\bf Note: the first half of this paragraph and the second do not follow from one another.
+The first half is about spectra the second about outflows and the connection to spectra is not made until the next paragrph.
+This needs fixing.}
+In addition to the inflowing accreting material, 
 outflows are ubiquitous in AGN
@@
 
-Despite the clear importance of ADWs in understanding AGN SEDs and accretion physics, 
+{\bf ksl: I don't see what this paragraph has to do with our problem, which we need to clearly explain} Despite the clear importance of ADWs in understanding AGN SEDs and accretion physics, 
 much of the underlying outflow physics remains highly uncertain. 
@@
 
-There has been some success using simple
-kinematic prescriptions for biconical disc winds to model 
-AGN and quasar outflows \citep[][hereafter H13]{simlong2008,sim2010,higginbottom2013}. 
-H13 successfully produced a benchmark model for BALQSOs. However, the model
-had two key drawbacks. First, an unrealistically low X-ray luminosity
-was required in order to prevent over-ionization of the outflow.
-Second, the model failed to produce the strong emission lines 
-required at low inclinations in a unified model.
-In this paper, we attempt to address these issues, and test the disc wind 
-unification model using Monte Carlo radiative transfer (MCRT) and photoionization 
-calculations. The paper is organised as follows.
+We have been engaged in a project to determine whether it is possible to simulate the properties of the spectra of AGN, including BAL QSOs, using simple kinematic prescriptions for biconical disc winds using a Monte Carlo radiative transfer code that calculates the ionization structure of the wind and simulates the spectra from such a system \citep[][hereafter H13]{simlong2008,sim2010,higginbottom2013}.
+The results have encouraging in the sense that in H13, we showed we could produce simulated spectra that resembled that of BAL QSOs, as long as the luminosity of the central engine was relatively low, of order \POW{43}{\LUM} and the mass loss rate was relatively high, of order the mass accretion rate.
+However, at higher luminosities, the wind was so ionized that UV absorption lines were not produced.
+In addition, and in part due to limitations in our radiative transfer code, the model failed to produce spectra with strong emission lines at any inclination angle.
+
+Here we attempt to address both of these issues, by introducing clumping into our model and a more complete treatment of H and He into our radiative transfer calculations.
+The remainder of this paper is organized as follows:
+% There has been some success using simple kinematic prescriptions for biconical disc winds to model  AGN and quasar outflows \citep[][hereafter H13]{simlong2008,sim2010,higginbottom2013}.
+H13 successfully produced a benchmark model for BALQSOs.
+However, the model had two key drawbacks.
+First, an unrealistically low X-ray luminosity was required in order to prevent over-ionization of the outflow.
+Second, the model failed to produce the strong emission lines  required at low inclinations in a unified model.
+In this paper, we attempt to address these issues, and test the disc wind  unification model using Monte Carlo radiative transfer (MCRT) and photoionization  calculations.
+The paper is organised as follows.
 In section 2, we describe some of the important photoionization 
@@
 
-We use the MCRT code \py\ to carry out our radiative transfer and photoionization
-calculations in non-local thermodynamic equilibrium (non-LTE). 
-The code has been used to model accreting white dwarfs 
+For this study, we use the MCRT code \py\  we have developed to carry out our radiative transfer and photoionization
+calculations in non-local thermodynamic equilibrium (non-LTE) in a variety of disk-wind systems. 
+We have used the code  to model accreting white dwarfs 
 (Long \& Knigge 2002, hereafter LK02; Noebauer et al. 2010; 
 Matthews et al. 2015, hereafter M15), young-stellar objects \citep{simmacro2005}
-and quasars (H13). \nocite{noebauer, M15, LK02}
-These studies contain extensive detail on the code, 
-so we only briefly describe the key elements of the global 
-ionization calculation and other important aspects.
+and quasars (H13).\nocite{noebauer, M15, LK02}  LK02 provides the basic description of the original code; improvements, see especially H14 and M15, have been described in subsequent reports.
+A full description of the code will be published elsewhere; here we focus on the changes made to improve the ionization calculation and to allow for clumping in the wind.
+%These studies contain extensive detail on the code,  so we only briefly describe the key elements of the global ionization calculation and other important aspects.
+
+{\bf ksl - I a a bit torn over whether we add a few 3 sentences to describe the basic idea.
+Some will be reading this for the first time.
+Items that one would include are that we calculate the radiative transfer in a cylindrical coordinate system of dimension ??
+x ??.
+We have ionization and spectral cycles.
+In each cycle, ??
+photon bundles are generated.
+We stop the ionization cycles after they converge, without any details.
+I think this would be useful because we introduce terms like ``cell' later on.', and without some kind of description they have no context}
 
@@
 
-To treat line transfer, we adopt the same hybrid scheme 
-described by M15, 
+Our approach to line transfer is based upon the macro-atom implementation developed by \cite{lucy2002, lucy2003}.
+In our case, for reasons of computational effieciency, we adopt the  hybrid macro-atom scheme
+described by M15 (an improvement over that used by H14 for our earlier quasar study), 
 in which the energy flows
@@
 These energy packets interact with either two-level `simple ions'
-or full `macro-atoms'. The macro-atom implementation 
-is described in full by \cite{lucy2002, lucy2003}.
+or full `macro-atoms'. 
 Our scheme allows one to treat non-LTE line transfer in radiative equilibrium
@@
 we expect recombination to be important
-in determining their level populations and resultant line emission.
+in determining their level populations and resultant line emission, and because we were especially interested in the contribution to AGN spectra of \LA.
+In H14, all atoms were treated in a two-level approximation.
 
@@
 MC rate estimators as described by M15. Previously (LK02, H13, M15),
-we adopted a modified Saha approach to calculate the ionization fractions
-of simple-ions. We have now improved our code to explicitly solve the 
+we used a modified Saha approach to calculate the ionization fractions
+of simple-ions. As part of  this effort, we have now improved {\sc PYTHON} to explicitly solve the 
 rate equations between ions in non-LTE. 
@@
 
+{\bf ksl - Do we need the rest of this, or could it be postponed until a detailed paper on the program }
+
 %To avoid approximating the complex AGN SED as e.g. a dilute blackbody \citep[][M15]{ML93},
-We model the SED in a cell using the technique described by H13. In this scheme,
+We model the SED in a grid cell using the technique described by H13. In this scheme,
 the mean intensity in a series of $n$ bands is modeled as a normalised power law in 
@@
 
+{\bf This needs an introductory paragraph.
+Should state our earlier modeling of AGN H13 was based on a smooth outflow.
+It should reference the introduction where we say there are observational indications of clumping.
+Should say that the difficulty associated with clumping is two fold - computationally implies many grid cells,  many potential parameters.
+Ultimately, say that for simplicity we use microclumping.
+Then say this has been used elsewhere, but with more recent references than what we have.
+The point is we need to motivate micro clumping before we say what it means to the code  It's all mixed up as written.
+Aside: at some point this paper should mention H14, and hydro models more generally}
+
 To allow for clumping in our outflow we adopt a simple approximation
@@
 \section{Results and Discussion}
+
+{\bf We need to describe what we did before getting to results.
+We started with parameters similar to those of H14, we created a small grid.
+Limits of the grid are given in table 1.
+This should be a paragraph or section before this one.
+Not all quasars have to have the same parameters and so we have to explain that we have elected to describe one model in detail.
+Was our goal to fix the luminosity and see what was required.
+
+In next sections, we really need to deal with the difference between this class of models and "the model", and especially "our model".
+We may need to at least in words discuss whether we have "fine tuned" or not, by saying something about other models.}
 
@@
 
-\subsection{Synthetic Spectra}
+\subsection{Synthetic Spectra: Comparison to Observations}
 
@@
 {
-A cartoon describing the broad classes of sightline 
+A cartoon showing the broad classes of sightlines 
 in our model, illustrates how geometric effects lead to 
@@
 We show a cartoon illustrating how geometric effects determine
-the output spectra in figure~\ref{fig:sightline}.
+the output spectra in figure~\ref{fig:sightline}.  {\bf - Need to explain the source of the BAL composites}
 
@@
 quasar spectra, we also show {\sl Sloan Digital Sky Survey} (SDSS) quasar composites from
-\cite{reichard2003}, normalised to the flux at 2000\AA\ in each panel.
-We do not produce the semi-forbidden 
-intercombination lines seen in quasar spectra because we
-currently do not have a treatment for semi-forbidden lines.
-This is especially noticable with the strong C~\textsc{iii}]~1909\AA\, 
+\cite{reichard2003}, normalised to the flux at 2000\AA\ in each panel. Our simulated spectra do not contain
+the semi-forbidden 
+intercombination lines seen in quasar spectra because our radiative transfer code 
+currently does not have a treatment for semi-forbidden lines.  {\bf Isn't this just a statement about the fact that we have not implemented CIII as a full macro-atom; if so we should say that}
+This is especially noticeable with the strong C~\textsc{iii}]~1909\AA\, 
 line in the quasar composite spectra.  
@@
 to become important coolants in the outer portion of the wind.
+{\bf we have gone from their being lines we should see, to important coolants.
+I think we should stick to the fact that we would think our code would see them if we put C in as a macro atom.
+Also I think this who discussion of CIII should be after we have discussed what looks right with the emission lines.}
 
@@
 
+{\bf: I am not convinced this in the right place in the paper, because here we explore an alternative hypythesis.
+It might go better at the end.
+But a good many of the following sections are not that well motivated.}
+
 \begin{figure}
@@
 \citep[e.g.][]{reichard2003}.
+{\bf I think we mean EW here; otherwise I don't understand what we are talking about.
+We could say ``line shapes and equivalent widths''.
+I also think this requries more than one sentence of introduction.}
 This presents a challenge to our model, as well as the geometric 
-unification picture in general.
+unification picture in general, because these quantities should vary with inclination angle.
 Limb darkening and foreshortening causes the disc continuum emission to be 
@@
 line equivalent widths are comparable at all inclinations requires 
-significant fine-tuning when considering a classical thin disc. 
-An alternative, simpler solution is that the emergent continuum is roughly isotropic.
-
+significant fine-tuning when considering a classical thin disc. {\bf Is the previous sentence a throwaway line, or has some person done this.  If so, please reference; if not please delete.}
+%An alternative, simpler solution is that the emergent continuum is roughly isotropic.
+
+Obviously,  one possible solution to this problem is hypothesize a more isotropic distribution for the emergent condition than predicted by a ``classical'' disc. 
 General relativistic effects -- specifically, light bending
@@
 the accretion disc SED to become more isotropic \citep[e.g.][]{zhang1997,munozdarias2013}.
-To generate GR disc spectra, we use the code \agn\ \citep{hubeny2000,davishubeny2006,davis2007}. 
+Incorporating these effects into {\sc PYTHON} would be a very difficult and time-consuming challenge.
+Therefore, for the purposes of this discussion we have chosen to investigate whether GR effects could produce enough isotropy to address the EW problem, we have generated
+\ GR disc spectra, we use the code \agn\ \citep{hubeny2000,davishubeny2006,davis2007}. 
 The output flux at three different wavelengths
 as a function of inclination for an \agn\ model with the same disc and BH parameters
-as our clumpy wind model is shown in figure~\ref{fig:f2000}.
-The effects of GR on an AGN disc are much less extreme 
+as our clumpy wind model is shown in figure~\ref{fig:f2000}.  The results indicate that 
+the effects of GR on an AGN disc are much less extreme 
 in the UV portion of the spectrum than the calculations
 by \cite{zhang1997} for the X-rays in X-ray binaries.
-As a result, the disc emission is still strongly anisotropic.
+The emission for the disks of AGN is still strongly anisotropic.
 GR alone therefore cannot explain the line ratio trends in quasars by making the disc
@@
 We will explore these ideas further in a future study.
+{\bf Wait!
+All this says is that there has to be an alternative explanation.
+It is not support for any specific explanation!.
+This last few sentences should be a separate paragraph.
+They should start out: An alernative explanation proposed by risalite is that...}
 
@@
 % \end{figure} %fullpage
+
+{\bf:  Again this section needs an introduction.  Why is this important?}
 
@@
 % \end{figure}
+
+{\bf Note: One of the things I definitely wondered about is whether our "model" would produce the fraction of BALs seen in the sky}
 

### 2015-09-01 paper_mnras.tex
Knox's first set of changes, trying to commit them again

--- 2015-08-27 paper_mnras.tex
@@
 \end{figure*}
+
+{\bf:  Again this section needs an introduction.  Why is this important?}
 

### 2015-09-01 paper.tex
few more changes

--- 2015-08-27 paper.tex
@@
 the accretion disc SED to become more isotropic \citep[e.g.][]{zhang1997,munozdarias2013}.
-To generate GR disc spectra, we use the code \agn\ \citep{hubeny2000,davishubeny2006,davis2007}. 
+To generate GR disc spectra, we use the code \agn.\citep{hubeny2000,davis2007}. 
 The output flux at three different wavelengths

### 2015-09-19 paper.tex

--- 2015-09-01 paper.tex
@@
 the covering factor of the outflow. 
-The wind is expected to be roughly equatorial from polarisation results
+Polarisation studies expect the wind to be roughly equatorial
 \citep{goodrich1995, cohen1995}.
@@
 A biconical wind model can also readily explain the various sub-classifications of BALQSOs: 
-HiBALQSOs, which only exhibit higher ionization line absorption; LoBALQSOs which also show
+HiBALQSOs, which only exhibit high ionization line absorption; LoBALQSOs, which also show
 absorption in lower ionization state species such as \mg\ and \al; and
@@
 We stop the ionization cycles after they converge, without any details.
-I think this would be useful because we introduce terms like ``cell' later on.', and without some kind of description they have no context}
+I think this would be useful because we introduce terms like ``cell'' later on.', and without some kind of description they have no context}
 
@@
 as simple-ions (see M15). In this study,
-only H \& He are treated as macro-atoms, because 
+only H is treated as a macro-atom, because 
 we expect recombination to be important
@@
 \sum_{band~i=0}^{n}~
-{\int_{\nu_i}^{~\nu_i+1}{J_{\nu,i}\sigma_j(\nu)\nu^{-1}d\nu}}
+{\int_{\nu_i}^{~\nu_i+1} \frac{4 \pi J_{\nu,i}\sigma_j(\nu)}  {h \nu} d\nu}
 \right),}
@@
 collisional (three-body) recombination, respectively.
-We neglect recombination to and from excited states in the simple-ion calculation. 
+%% We neglect recombination to and from excited states in the simple-ion calculation. 
 For simple-ions, we use a dilute Boltzmann equation to calculate 
@@
 \subsection{Clumping}
+
+Our previous modelling efforts assumed a smooth outflow, 
+in which the density at a given point was determined only by the 
+kinematic parameters and mass loss rate. However, as already discussed,
+AGN winds exhibit significant substructure -- the outflow is expected to be
+{\em clumpy}, rather than smooth, and probably on a variety of scales. 
+Implementing a treatment of clumping is challenging, for
+two main reasons. First, there are significant 
+computational difficulties associated with adequately
+resolving and realistically modelling a series of small scale, high density
+regions with a MCRT code. Second, the addition of multiple additional degrees of
+freedom in the model results in significantly wider parameter space.
+Unfortuantely, the physical scale lengths and density contrasts 
+associated with these parameters cannot be well-constrained from observations.
 
@@
 {
-A cartoon showing the broad classes of sightlines 
-in our model, illustrates how geometric effects lead to 
+A cartoon describing the broad classes of sightline 
+in our model, illustrating how geometric effects lead to 
 the different emergent spectra. The colour gradient is approximate,
@@
 Figure~\ref{fig:uvspec} shows the synthetic spectrum in the UV from our model. 
-We also show a comparison to composite quasar and BALQSO spectra.
+To assess the ability of the model to match real 
+quasar spectra, we also show {\sl Sloan Digital Sky Survey} (SDSS) quasar and BALQSO 
+composites from \cite{reichard2003}, normalised to the flux at 2000\AA\ in each panel. 
 We show a cartoon illustrating how geometric effects determine
-the output spectra in figure~\ref{fig:sightline}.  {\bf - Need to explain the source of the BAL composites}
+the output spectra in figure~\ref{fig:sightline}.
 
@@
 and shows that a biconical wind can produce significant 
-emission at `quasar-like' angles. To assess the ability of the model to match real 
-quasar spectra, we also show {\sl Sloan Digital Sky Survey} (SDSS) quasar composites from
-\cite{reichard2003}, normalised to the flux at 2000\AA\ in each panel. Our simulated spectra do not contain
-the semi-forbidden 
-intercombination lines seen in quasar spectra because our radiative transfer code 
-currently does not have a treatment for semi-forbidden lines.  {\bf Isn't this just a statement about the fact that we have not implemented CIII as a full macro-atom; if so we should say that}
-This is especially noticeable with the strong C~\textsc{iii}]~1909\AA\, 
-line in the quasar composite spectra.  
+emission at `quasar-like' angles. 
+Our simulated spectra do not contain the strong C~\textsc{iii}]~1909\AA\, 
+line seen in the quasar composite spectra. This is because we do not yet
+treat C as a full macro-atom with a full collisional rates between forbidden
+or semi-forbidden transitions, as would be required.
 The critical density of the C~\textsc{iii}]~1909\AA\, line 
 is $n_e\sim10^{9.5}~\rm{cm^{-3}}$, which is higher than much of the 
-outer portion of our wind. We therefore expect intercombination lines
-to become important coolants in the outer portion of the wind.
-{\bf we have gone from their being lines we should see, to important coolants.
+outer portion of our wind. We therefore expect a model with these 
+parameters to produce C~\textsc{iii}]~1909\AA\ with a proper treament. 
+% {\bf we have gone from their being lines we should see, to important coolants.
 I think we should stick to the fact that we would think our code would see them if we put C in as a macro atom.
@@
 that they possess remarkably similar line strengths and widths 
-\citep[e.g.][]{reichard2003}.
+\citep[e.g.][]{weymann1991,reichard2003}.  
 {\bf I think we mean EW here; otherwise I don't understand what we are talking about.
@@
 I also think this requries more than one sentence of introduction.}
+>>>>>>> 3c3265bb9688e4788107378165d92e06c2aa7abe
 This presents a challenge to our model, as well as the geometric 
@@
 GR alone therefore cannot explain the line ratio trends in quasars by making the disc
-emit more isotropically.
-This supports the findings of \cite{risaliti2011}, who find that EW distributions 
-in quasars are consistent with anisotropic emission from optically thick, 
+emit more isotropically. This supports the findings of \cite{risaliti2011}, 
+who find that EW distributions in quasars are consistent with anisotropic emission 
+from optically thick, 
 disc-like structures for {\em both} the continuum source and BLR. 
+If this is the case, it has a dramatic affect on the intrinsic
+BAL fraction inferred from flux-limited samples \citep{goodrich1997,krolikvoit1998}.
+We will explore these ideas further in a future study.
 We will explore these ideas further in a future study.

### 2015-09-19 paper_mnras.tex

@@
 \sum_{band~i=0}^{n}~
-{\int_{\nu_i}^{~\nu_i+1}{J_{\nu,i}\sigma_j(\nu)\nu^{-1}d\nu}}
+{\int_{\nu_i}^{~\nu_i+1} \frac{4 \pi J_{\nu,i}\sigma_j(\nu)}  {h \nu^{-1}} d\nu}
 \right),}

### 2015-09-20 paper.tex
did more stuff

@@
 % clumpy winds and broad emission lines
-Unifying quasars with clumpy wind models
+Testing Quasar Unification with Clumpy Wind Models
+%Unifying quasars with clumpy wind models
 }
-
-% [Matthews, J.]
-% \author[Matthews, J.]{James Matthews \\
-% {\sl  Supervisor: Prof. Christian Knigge} \\
-% {\sl School of Physics \& Astronomy, University of Southampton,
-%   Southampton, SO17 1BJ, UK}}
 
@@
 % holistic picture of the quasar population.
-Various unification schemes have been proposed to interpret the complex phenomenology of quasars and luminous active galactic nuclei (AGN) in terms of  a simple axisymmetric picture involving a central black hole, an accretion disc and an associated outflow.
-Here, we continue our tests of  this paradigm by comparing ``average'' AGN spectra to synthetic spectra of simple biconical disc wind models, using  with our Monte Carlo radiative transfer and photoionization code {\sc Python}.
-In particular, we investigate whether clumping of the outflow allows us to produce synthetic spectra in the rest-frame UV that have the characteristics of AGN, assuming total luminosities as high as 10$^{45}$ ergs s$^{-1}$.
+Various unification schemes have been proposed to interpret the complex phenomenology 
+of quasars and luminous active galactic nuclei (AGN) in terms of  a simple axisymmetric 
+picture involving a central black hole, an accretion disc and an associated outflow.
+Here, we continue our tests of  this paradigm by comparing ``average'' AGN spectra to 
+synthetic spectra of simple biconical disc wind models, using our state-of-the-art 
+Monte Carlo radiative transfer and photoionization code.
+In particular, we investigate whether clumping of the outflow allows us to 
+produce synthetic spectra in the rest-frame UV that have the characteristics of AGN, 
+assuming total luminosities as high as 10$^{45}$ ergs s$^{-1}$. 
 We find that a simple treatment of clumping (`microclumping') 
@@
 At the highest inclinations, the synthetic spectra possess prominent \mg\ and \al\ BALs, the absorption 
-features seen in LoBAL quasars. Despite these successes, we are unable to reproduce 
+features seen in LoBAL quasars. 
+Despite these successes, we are unable to reproduce 
 the remarkably uniform emission line properties 
-% remarkably similar of line-to-continuum ratios apparent 
-seen in BAL and non-BAL quasar composites. {\bf This sentence needs to be more precise, especially in light ot the statement earlier in the abstract about ``good agreement''}
+seen in BAL and non-BAL quasar composites. 
+{\bf This sentence needs to be more precise, especially in 
+light of the statement earlier in the abstract about ``good agreement''}
 This is due to a fundamental constraint arising
 from the anisotropy of emission from a classical thin disc. 
-We briefly explore the impact of general relativistic effects
-on the angular distribution of disc continuum emission, and find that 
-they are not sufficient to produce a self-consistent model.
-% relativistic beaming, gravitational redshift and 
-% light bending on the angular distribution of disc continuum emission. 
-% We find that these general relativistic effects are not yet sufficient to produce a
-% self-consistent model. 
 Overall, our work suggests that geometric unification
@@
 
-% Introduction focussing on key points
-% \begin{itemize}
-% \item standard wind + BALQSO introduction
-% \item focus on unification and that we are testing it
-% \item some discussion of scales, referencing e.g. reverb maps, variability, microlensing, Arav 
-% \item clumping background: stellar winds, clumping in AGN winds, variability
-% \end{itemize}
-
 The spectra of 
@@
 geometrically thin, optically thick accretion disc surrounding the central black hole, similar
-to that described by \cite{shakurasunyaev1973}.
-The lines are usually attributed to scattering and absorption of material above the disk.
+to that described by \cite{shakurasunyaev1973}.  The lines are usually attributed to scattering and absorption of material above the disk.  
 {\bf Note: the first half of this paragraph and the second do not follow from one another.  
 The first half is about spectra the second about outflows and the connection to spectra is not made until the next paragrph.  
-This needs fixing.}
+This needs fixing. JM: Knox, I like this structure...I start with inflow, then move to outflow.}
 In addition to the inflowing accreting material, 
@@
 Polarisation studies expect the wind to be roughly equatorial
-\citep{goodrich1995, cohen1995}.
+\citep{goodrich1995, cohen1995}, although this geometry is contradicted
+by more recent studies of radio spectral indices (REFS DIPOMPEO; see section ?).
 ADWs offer a natural explanation for the
@@
 correspond either to the dense wind base or dense clumps embedded
-in the outflows. Indeed, \cite{elitzur2014} found that a disc-wind BLR scenario
+in the outflows. Indeed, \cite{elitzur2014} show that a disc-wind BLR scenario
 naturally explains the emission line evolution of AGN.
@@
 FeLoBALQSOs which show further absorption in Fe~\textsc{ii} and \textsc{iii}.
-In unified models, this is generally attributed to ionization stratification
+In unified geometric models, this is generally attributed to ionization stratification
 of the outflow \citep[e.g.][]{elvis2000}.
@@
 
-{\bf This needs an introductory paragraph.
+% {\bf This needs an introductory paragraph.
 Should state our earlier modeling of AGN H13 was based on a smooth outflow.
@@
 used extensively in stellar wind modelling, known as 
-{\em microclumping} \citep{hamann1998}. The key assumption here is that 
+{\em microclumping} \citep{hamann1998}(MORE REFS). The key assumption here is that 
 typical clump sizes are much smaller than the typical photon mean free path, 
@@
 $r_{min}$, $\theta_{min}$, $f$, $\alpha$ and $R_V$.
-The full grid, including output spectral files and plots can be found at
-\url{jhmatthews.github.io/quasar-wind-grid/}.
-We evaluated these models qualitatively based on the following
+We evaluated these models based on the following
 criteria:
 \begin{itemize}
-\item Does the model maintain the right ionization state to produce strong BALs?
-\item Does significant line emission emerge at low inclinations?
-\item Do H recombination lines appear in the spectrum?
+\item Does the model maintain the right ionization state to produce strong BALs ($BI > ??$)?
+\item Does significant line emission emerge at low inclinations, with $EW\sim50\AA$ in \civ?
+\item Do H recombination lines appear in the spectrum, $EW\sim50\AA$ in \la?
 \item Do a certain range of angles produce LoBAL features?
@@
 and physical constraints and assess the potential for unification. 
+The full grid, including output synthetic spectra and plots can be found at
+\url{jhmatthews.github.io/quasar-wind-grid/}.
 
@@
 
-\subsubsection{The Disc SED}
+\subsubsection{The Angular Distribution of Line And Continuum Emission}
 \label{discsed}
@@
 But a good many of the following sections are not that well motivated.}
-
-\begin{figure}
-\centering
-\includegraphics[width=0.5\textwidth]{figures/agnspec.png}
-\caption
-{
-$F_\lambda$ for three different wavelengths
-as a function of inclination from \agn\ models, 
-compared to a classical AD. The \agn\ models are computed 
-for Kerr and Scharzschild BHs with the same $M_{BH}$ and 
-$\dot{m}$ as our model. 
-}
-\label{fig:f2000}
-\end{figure}
 
@@
 I also think this requries more than one sentence of introduction.}
->>>>>>> 3c3265bb9688e4788107378165d92e06c2aa7abe
 This presents a challenge to our model, as well as the geometric 
@@
 We will explore these ideas further in a future study.  
-We will explore these ideas further in a future study.
-{\bf Wait!
-All this says is that there has to be an alternative explanation.
-It is not support for any specific explanation!.
-This last few sentences should be a separate paragraph.
-They should start out: An alernative explanation proposed by risalite is that...}
+{\bf Wait!  All this says is that there has to be an alternative explanation.
+It is not support for any specific explanation!. This last few sentences should
+be a separate paragraph.  They should start out: An alernative explanation proposed 
+by risalite is that...}
 
@@
 
-% Here are some notes on various parts of the text.
-% \smallskip
-
-% \begin{itemize}
-% 	\item 
-% 	\item Figure 3 should be improved to include some kind of real colormap of the model
-% 	\item At the moment I haven't included another plot for the optical spectrum, or discussed
-% 	it in the paper.
-% 	\item Figure 5 needs to show a sample at the higher luminosity end, and include the actual relationship as the dotted line instead of a by eye version as is currently 
-% 	\item
-% 	\item
-% 	\item
-% 	\item
-% 	\item
-% 	\item
-% 	\item
-% \end{itemize}
-
 \end{document}

### 2015-09-20 paper_mnras.tex
did more stuff

@@
 \sum_{band~i=0}^{n}~
-{\int_{\nu_i}^{~\nu_i+1} \frac{4 \pi J_{\nu,i}\sigma_j(\nu)}  {h \nu^{-1}} d\nu}
+{\int_{\nu_i}^{~\nu_i+1} \frac{4 \pi J_{\nu,i}\sigma_j(\nu)}  {h \nu} d\nu}
 \right),}

### 2015-11-10 paper.tex
bringing up to date with polarisation etc

@@
 We find that a simple treatment of clumping (`microclumping') 
-allows for a more realistic AGN luminosities,
-while maintaining the ionization state necessary for strong BAL features in the rest-frame UV. 
+allows for a more realistic AGN luminosities, while maintaining the ionization 
+state necessary for strong BAL features in the rest-frame UV. 
 We examine the X-ray properties of these simple clumped models
 and find good agreement with existing X-ray samples of AGN and quasars.
-The dense, X-ray heated wind 
-produces strong recombination and collisionally excited line emission in, 
-e.g., \civ\ and \la, to emerge at the low inclination, `Type 1 quasar-like' angles. 
-At the highest inclinations, the synthetic spectra possess prominent \mg\ and \al\ BALs, the absorption 
-features seen in LoBAL quasars. 
+The dense, X-ray heated wind produces strong recombination and collisionally 
+excited line emission in, e.g., \civ\ and \la, to emerge at the low inclination, 
+`Type 1 quasar-like' angles. 
+At the highest inclinations, the synthetic spectra possess prominent \mg\ and \al\ BALs, the absorption features seen in LoBAL quasars. 
 Despite these successes, we are unable to reproduce 
@@
 seen in BAL and non-BAL quasar composites. 
-{\bf This sentence needs to be more precise, especially in 
-light of the statement earlier in the abstract about ``good agreement''}
+% {\bf This sentence needs to be more precise, especially in 
+% light of the statement earlier in the abstract about ``good agreement''}
 This is due to a fundamental constraint arising
@@
 pose a number of difficult challenges to such a model.
-{\bf There is confusion in the abstract, at least, in what is the model and what is the synthetic spectra, as well as whether there is one model or many models.
+% {\bf There is confusion in the abstract, at least, in what is the model and what is the synthetic spectra, as well as whether there is one model or many models.
 We need to try to be clear.
@@
 with an underlying blue continuum - the so-called {\sl `big blue bump'} (BBB). 
-The BBB is often attributed to emssion from a 
+The BBB is often attributed to emission from a 
 geometrically thin, optically thick accretion disc surrounding the central black hole, similar
-to that described by \cite{shakurasunyaev1973}.  The lines are usually attributed to scattering and absorption of material above the disk.  
-{\bf Note: the first half of this paragraph and the second do not follow from one another.  
-The first half is about spectra the second about outflows and the connection to spectra is not made until the next paragrph.  
-This needs fixing. JM: Knox, I like this structure...I start with inflow, then move to outflow.}
-In addition to the inflowing accreting material, 
-outflows are ubiquitous in AGN
+to that described by \cite{shakurasunyaev1973}.
+% {\bf Note: the first half of this paragraph and the second do not follow from one another.  
+% The first half is about spectra the second about outflows and the connection to spectra is not made until the next paragrph.  
+% This needs fixing. JM: Knox, I like this structure...I start with inflow, then move to outflow.}
+In addition to the {\em inflowing} accreting material, 
+{\em outflows} are ubiquitous in AGN
 and quasars \citep{kellerman1989,ganguly2008}. These outflows can take the form of 
@@
 
-Approximately $20\%$ of quasars exhibit blueshifted ($\sim 0.1c$)
-broad absorption lines (BALs) in the ultraviolet,
-providing clear evidence for outflowing absorbing material
+Perhaps the clearest evidence of outflows in AGN is  
+the blueshifted ($\sim 0.1c$) broad absorption lines (BALs) in the 
+ultraviolet seen in approximately $20\%$ of quasars
 \citep{weymann1991, reichard2003, knigge2008, turnermiller2009, allen2011}.
@@
 Polarisation studies expect the wind to be roughly equatorial
-\citep{goodrich1995, cohen1995}, although this geometry is contradicted
-by more recent studies of radio spectral indices (REFS DIPOMPEO; see section ?).
+\citep{goodrich1995, cohen1995}, although there is also evidence
+for polar BAL outflows \citep{zhou2006}.
+% although this geometry is contradicted
+% by more recent studies of radio spectral indices \citep{dipompeo2012}.
 ADWs offer a natural explanation for the
@@
 may see a BALQSO or normal `Type 1' quasar.
-Within this framework, the broad-line region (BLR) can 
+
+Within the ADW  unification framework, the broad-line region (BLR) can 
 correspond either to the dense wind base or dense clumps embedded
@@
 absorption in lower ionization state species such as \mg\ and \al; and
-FeLoBALQSOs which show further absorption in Fe~\textsc{ii} and \textsc{iii}.
+FeLoBALQSOs, which show further absorption in Fe~\textsc{ii} and \textsc{iii}.
 In unified geometric models, this is generally attributed to ionization stratification
@@
 % As well as acting as a source of photoionized plasma, a 
-As well as imprinting clear line absorption and emission
-features, disc winds may also have a profound effect on the structure and 
-emergent {\em continuum} of the accretion disc itself.
-Mass-loss will alter the accretion rate and resultant 
-temperature of the accretion disc, possibly explaining some 
-of the features typically seen in luminous AGN \citep{knigge1999,laordavis2014}.
-There have been numerous difficulties when confronting 
-theoretical accretion disc models with observations 
-\citep[see e.g.][]{blaes1998}. However, AGN spectral energy distributions (SEDs) can now, 
-in general, be fitted well with accretion disc models
-when the effects of general relativity (GR), Comptonisation
-and mass-loss are included \citep{capellupo2015}. Mass-loss therefore appears to be 
-critical if an accretion disc model is to successfully fit AGN SEDs, 
-particular in the UV region of the spectrum.
-
-{\bf ksl: I don't see what this paragraph has to do with our problem, which we need to clearly explain} Despite the clear importance of ADWs in understanding AGN SEDs and accretion physics, 
+% As well as imprinting clear line absorption and emission
+% features, disc winds may also have a profound effect on the structure and 
+% emergent {\em continuum} of the accretion disc itself.
+% Mass-loss will alter the accretion rate and resultant 
+% temperature of the accretion disc, possibly explaining some 
+% of the features typically seen in luminous AGN \citep{knigge1999,laordavis2014}.
+% There have been numerous difficulties when confronting 
+% theoretical accretion disc models with observations 
+% \citep[see e.g.][]{blaes1998}. However, AGN spectral energy distributions (SEDs) can now, 
+% in general, be fitted well with accretion disc models
+% when the effects of general relativity (GR), Comptonisation
+% and mass-loss are included \citep{capellupo2015}. Mass-loss therefore appears to be 
+% critical if an accretion disc model is to successfully fit AGN SEDs, 
+% particular in the UV region of the spectrum.
+
+%{\bf ksl: I don't see what this paragraph has to do with our problem, which we need to clearly explain} Despite the clear importance of ADWs in understanding AGN SEDs and accretion physics,
+Despite the clear importance of ADWs in shaping quasar and AGN spectra,  
 much of the underlying outflow physics remains highly uncertain. 
@@
 \citep{reeves2003,poundsreeves2009,tombesi2010a}.
-The presence of line-locked features \citep{bowler2014} 
-and the `ghost of \la' (Arav et al. 1996; Arav 1996; North 2006; but see 
-also Cottis et al. 2010) \nocite{arav1995, arav1996, north2006,cottis2010}
-in the spectra of some BALQSOs also gives clearer evidence that line-driving is
-at least partially contributing to the acceleration of the wind.
-
+% The presence of line-locked features \citep{bowler2014} 
+% and the `ghost of \la' (Arav et al. 1996; Arav 1996; North 2006; but see 
+% also Cottis et al. 2010) \nocite{arav1995, arav1996, north2006,cottis2010}
+% in the spectra of some BALQSOs also gives clearer evidence that line-driving is
+% at least partially contributing to the acceleration of the wind.
 The efficiency of line-driving is crucially dependent on the ionization state 
@@
 a region of `hitchhiking gas' that could shield the wind from the central X-ray source. 
-Hydrodynamic simulations of line-driven disc winds also found a shielding region
-was required to maintain the correct ionization state \citep{PSK2000,PK04}. 
-However, \cite{H14} showed that including multiple scattering means the ionizing radiation 
-field could still reach the previously shielded regions in those particular models.
+% Hydrodynamic simulations of line-driven disc winds also found a shielding region
+% was required to maintain the correct ionization state \citep{PSK2000,PK04}. 
+% However, \cite{sim2010_hydro} and \cite{H14} showed that including multiple scattering means the ionizing radiation field could still reach the previously shielded regions 
+% in those particular models.
 An additional or alternative solution is that the wind is clumped \citep[e.g.][]{hamann2013}
@@
 \citep{krolik1981, emmering1992, dekool1995, cassidyraine1996}.
-Clumping can be caused by magnetic confinement \cite{dekool1995},
+Clumping can be caused by magnetic confinement \citep{dekool1995},
 or the instabilities inherent to line-driven winds 
@@
 in line-driven hot star winds \citep{hillier1991eswingsmodel}. Complex substructures 
-on a variety of scales are also produced in simulations of line-driven 
-outflows in AGN \citep{PSK2000,PK04,progakurosawa2010,proga2014}.
-Clumpy winds therefore offer an observationally motivated and theoretically 
+are also produced in simulations of line-driven 
+outflows in AGN, although on very different scales to line-driven instabilities 
+\citep{PSK2000,PK04,progakurosawa2010,proga2014}.
+Nevertheless, clumpy winds offer an observationally motivated and theoretically 
 predicted way to lower the ionization state of a plasma, possibly in tandem
@@
 In our case, for reasons of computational effieciency, we adopt the  hybrid macro-atom scheme
-described by M15 (an improvement over that used by H14 for our earlier quasar study), 
+described by M15 
+%(an improvement over that used by H14 for our earlier quasar study), 
 in which the energy flows
@@
 Our scheme allows one to treat non-LTE line transfer in radiative equilibrium
-without approximation for elements which are identified as 
+without approximation for elements that are identified as 
 full macro-atoms, while maintaining the fast `two-level' 
@@
 in determining their level populations and resultant line emission, and because we were especially interested in the contribution to AGN spectra of \LA.
-In H14, all atoms were treated in a two-level approximation.
+In H13, all atoms were treated in a two-level approximation.
 
@@
 Macro-atoms have their ion and level populations derived from
-MC rate estimators as described by M15. Previously (LK02, H13, M15),
+MC rate estimators as described by Lucy (2002,2003). Previously (LK02, H13, M15),
 we used a modified Saha approach to calculate the ionization fractions
 of simple-ions. As part of  this effort, we have now improved {\sc PYTHON} to explicitly solve the 
-rate equations between ions in non-LTE. 
-This dispenses with a number of small assumptions made in the modified Saha approach, 
-is more numerically stable, 
-and, in principle, allows the direct addition of extra physical 
-processes such as Auger ionization.
-
-{\bf ksl - Do we need the rest of this, or could it be postponed until a detailed paper on the program }
-
-%To avoid approximating the complex AGN SED as e.g. a dilute blackbody \citep[][M15]{ML93},
-We model the SED in a grid cell using the technique described by H13. In this scheme,
-the mean intensity in a series of $n$ bands is modeled as a normalised power law in 
-frequency $\nu$
-\begin{equation}
-J_{\nu,i}=K_{pl}\nu^{\alpha_{pl}},
-\end{equation}
-for a band $i$, or an exponential 
-\begin{equation}
-J_{\nu,i}=K_{exp} e^{(-h\nu/k T_{exp})}.
-\end{equation}
-Here, $K_{exp}$, $K_{pl}$, $T_{exp}$ and $\alpha_{pl}$ are spectral fit parameters
-deduced from the band-limited radiation field estimators.
+rate equations between ions in non-LTE. This dispenses with a number of small assumptions 
+made in the modified Saha approach, is more numerically stable, and, in principle, allows 
+the direct addition of extra physical processes that would previously have necessitated 
+approximate treatments.
+
+In order to calculate the photoionization rate, 
+we model the SED in a grid cell using the technique described by H13. In this scheme,
+the mean intensity in a series of $n$ bands is modeled as either a power law or exponential
+in frequency $\nu$, with the fit parameters deduced from band-limited radiation field estimators.
+% \begin{equation}
+% J_{\nu,i}=K_{pl}\nu^{\alpha_{pl}},
+% \end{equation}
+% for a band $i$, or an exponential 
+% \begin{equation}
+% J_{\nu,i}=K_{exp} e^{(-h\nu/k T_{exp})}.
+% \end{equation}
+% Here, $K_{exp}$, $K_{pl}$, $T_{exp}$ and $\alpha_{pl}$ are spectral fit parameters
+% deduced from the band-limited radiation field estimators.
 The ionization rate out of ion $j$ can then be written as 
@@
 
-% We improve on this method by abandoning the modified Saha approach
-% entirely, and instead computing the ionization state by 
-% explicitly solving the rate equations in between ions in non-LTE. 
-% Photoionization and recombination rates are calculated using MC estimators recorded
-% during the photon propagation. Not only does this dispense with a number of
-% small assumptions made in the modified Saha approach, it is also more numerically stable, 
-% and in principle allows the direct addition of extra physical processes such as Auger ionization, which would have to be approximated if using the previous technique.
 \subsection{Physical Processes}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+%
 % MODEL DESCRIPTION
-
+%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 geometry is similar to that invoked by \cite{MCGV95} and 
-\cite{elvis2000} in order to explain the phenomenonology
+\cite{elvis2000} to explain the phenomenonology
 of quasars and BALQSOs.
@@
 
-% \subsection{A Benchmark Model for BALQSOs}
-
-% \cite{higginbottom2013} presented a benchmark model for
-% (BAL)QSOs...introduce key parameters.
-
 \subsection{Photon Sources}
-
-%Describe the photon sources in the model.
 
@@
 and central BH mass ($M_{BH}$).
-All photon sources in our model are assumed to beopaque, meaning
+All photon sources in our model are assumed to be opaque, meaning
 that photons which strike them are destroyed.
@@
 constraint (see Lucy 2002, M15).
-% \begin{equation}
-
-% \end{equation}
-
-% With a normalisation such that it produces the correct 2-10kev luminosity.
-
-% Photons striking the
-
-% which successfully reproduced BAL features 
-% in synthetic spectra using \py. However, the model
-% had a few key drawbacks when considering its potential
-% for unification. First, it failed to produce significant
-% broad emission lines at non-BAL viewing angles; this is 
-% a key requirement for a unified QSO model. Second,
-% the model was significantly X-ray weak, as it was found
-% that an X-ray luminosity comparable to that of a QSO 
-% over-ionized the wind, resulting in no UV resonance 
-% line absorption features.
 
@@
 but also the density and ionization state of the outflow.
-A wind which accelerates more slowly will have a denser wind base
+A wind that accelerates more slowly will have a denser wind base
 with correspondingly different ionization and emission characteristics.
@@
 associated with these parameters cannot be well-constrained from observations.
-
-% {\bf This needs an introductory paragraph.
-Should state our earlier modeling of AGN H13 was based on a smooth outflow.
-It should reference the introduction where we say there are observational indications of clumping.
-Should say that the difficulty associated with clumping is two fold - computationally implies many grid cells,  many potential parameters.
-Ultimately, say that for simplicity we use microclumping.
-Then say this has been used elsewhere, but with more recent references than what we have.
-The point is we need to motivate micro clumping before we say what it means to the code  It's all mixed up as written.
-Aside: at some point this paper should mention H14, and hydro models more generally}
 
@@
 will remain unchanged for a given ionization state.
-% A factor $f$ is also
-% applied to the opacities such that opacities which scale only with $\rho$ are not
-% increased.
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% RESULTS
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Results and Discussion}
-
-{\bf We need to describe what we did before getting to results.
-We started with parameters similar to those of H14, we created a small grid.
-Limits of the grid are given in table 1.
-This should be a paragraph or section before this one.
-Not all quasars have to have the same parameters and so we have to explain that we have elected to describe one model in detail.
-Was our goal to fix the luminosity and see what was required.
-
-In next sections, we really need to deal with the difference between this class of models and "the model", and especially "our model".
-We may need to at least in words discuss whether we have "fine tuned" or not, by saying something about other models.}
-
-Here we describe the results from our model, the parameters
-of which are shown in table~1.
-Parameters differing from the benchmark model of
-H13 are highlighted with an asterisk.
-This set of parameters
-was arrived at by conducting a limited grid search over a 
-5-dimensional parameter space involving the variables
-$r_{min}$, $\theta_{min}$, $f$, $\alpha$ and $R_V$.
-We evaluated these models based on the following
-criteria:
+\subsection{The Simulation Grid: Arriving at a next-generation model}
+
+Using this prescription, we conducted a limited parameter
+search over a 5-dimensional parameter space involving the 
+variables $r_{min}$, $\theta_{min}$, $f$, $\alpha$ and $R_v$.
+The grid points are shown in table 1.
+The aim here was to first fix $M_{BH}$ and $\dot{m}$ to their H13 values,
+and increase $L_X$ to $10^{45}$~erg~s$^{-1}$ (a more realistic value for a 
+quasar of $10^9M_\odot$ and an eddington fraction of $0.2$; see section~\ref{sec:xray}). 
+We then evaluated these models based on the following criteria:
 \begin{itemize}
-\item Does the model maintain the right ionization state to produce strong BALs ($BI > ??$)?
+\item Does the model avoid over-ionization and thus produce strong BALs with $BI > ??$?
 \item Does significant line emission emerge at low inclinations, with $EW\sim50\AA$ in \civ?
@@
 \end{itemize}
+We arrived at a model
 In this section, we present one of the most promising models and discuss
@@
 \url{jhmatthews.github.io/quasar-wind-grid/}.
+
+\begin{table}
+\begin{tabular}{p{2cm}p{1cm}p{1cm}p{1cm}p{1cm}}
+Parameter & \multicolumn{4}{|l|}{Grid Point Values}  \\
+\hline \hline 
+$r_{min}$ 	&	 $6r_{g}$ & $60r_{g}$ & \multicolumn{2}{|l|}{$300r_{g}$} \\ 
+$\theta_{min}$ 	&	 $40^{\circ}$ & $55^{\circ}$ & \multicolumn{2}{|l|}{$70^{\circ}$} \\ 
+$R_v$  	        &	 $10^{18}$cm & \multicolumn{3}{|l|}{$10^{19}$cm} \\ 
+$\alpha$ 	&	 $0.5$ & $0.6$ & $0.75$ & $1.5$ \\
+$f$ 	&	 $0.01$ & $0.1$ & \multicolumn{2}{|l|}{$1$}  \\
+\hline 
+\end{tabular}
+\caption{The grid points used in the parameter search.}
+\label{grid_table}
+\end{table}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% RESULTS
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Results and Discussion}
+
+% {\bf We need to describe what we did before getting to results.
+We started with parameters similar to those of H14, we created a small grid.
+Limits of the grid are given in table 2.
+This should be a paragraph or section before this one.
+Not all quasars have to have the same parameters and so we have to explain that we have elected to describe one model in detail.
+Was our goal to fix the luminosity and see what was required.
+
+% In next sections, we really need to deal with the difference between this class of models and "the model", and especially "our model".
+We may need to at least in words discuss whether we have "fine tuned" or not, by saying something about other models.}
+
+Here we describe the results from our next-generation model,
+and discuss these results in the context of the criteria 
+presented in section 3.4. The parameters of this model are shown in table~2.
+Parameters differing from the benchmark model of H13 are 
+highlighted with an asterisk. In this section, we examine the physical 
+conditions of the flow, and present the synthetic spectra, before comparing
+the X-ray properties of this particular model to samples of
+quasars and luminous AGN. We also examine trends with inclination in the synthetic spectra, 
+both in terms of the range of ionization states of the absorption lines and equivalent widths 
+of the emission lines.
+
+% This set of parameters
+% was arrived at by conducting a limited grid search over a 
+% 5-dimensional parameter space involving the variables
+% $r_{min}$, $\theta_{min}$, $f$, $\alpha$ and $R_V$.
+% We evaluated these models based on the following
+% criteria:
+% \begin{itemize}
+% \item Does the model maintain the right ionization state to produce strong BALs ($BI > ??$)?
+% \item Does significant line emission emerge at low inclinations, with $EW\sim50\AA$ in \civ?
+% \item Do H recombination lines appear in the spectrum, $EW\sim50\AA$ in \la?
+% \item Do a certain range of angles produce LoBAL features?
+% \item Does the model compare favourably to quasar composite spectra?
+% \end{itemize}
+% In this section, we present one of the most promising models and discuss
+% the various successes and failures.
+% This allows us to gain insight into fundamental geometrical 
+% and physical constraints and assess the potential for unification. 
+% The full grid, including output synthetic spectra and plots can be found at
+% \url{jhmatthews.github.io/quasar-wind-grid/}.
 
@@
 \begin{tabular}{p{3cm}p{4cm}}
-\hline Free Parameters 	&	 Value \\ 
+\hline Next-generation Model Parameters 	&	 Value \\ 
 \hline \hline 
@@
 as recombination and collisional excitation are both proportional to
-$n_e^2$. This line emission typically emerges on the edge of the wind
+density squared. This line emission typically emerges on the edge of the wind
 nearest the central source. The location of the line emitting regions
@@
 
-% \begin{figure*} %fullpage
-% \centering
-% \includegraphics[width=1.0\textwidth]{figures/opt.png}
-% \caption
-% {
-% Figure designed to show optical spectrum and comparison to composite.
-% }
-% \label{fig:uvspec}
-% \end{figure*} %fullpage
+\begin{figure*} %fullpage
+\centering
+\includegraphics[width=1.0\textwidth]{figures/0946.png}
+\caption
+{
+Synthetic spectra at $72^\circ$ compared to an HST STIS spectrum
+of PG0946+301 (Arav et al. 2000). The spectrum is scaled to the flux at 1300\AA\
+for direct comparison. 
+}
+\label{fig:stis}
+\end{figure*} %fullpage
 
@@
 
-\subsubsection{Broad absorption lines}
+\subsubsection{Broad absorption lines (`BALQSO-like' angles)}
 
@@
 This offers one potential explanation for the wide range of BALQSO absorption
-line shapes (see e.g. Trump et al. 2006; Knigge et al 2008).
+line shapes (see e.g. Trump et al. 2006; Knigge et al 2008, Filiz Ak et al. 2014).
 In addition, the line profile shape is strongly dependent 
@@
 
-\subsubsection{Broad emission lines}
-
-We find that the model can produce significant line emission
-at low inclinations, particular in \civ, 
-and the improved treatment of recombination results in a strong \la\
-line. In the context of unification, this is a promising result, 
+\subsubsection{Broad emission lines (`quasar-like' angles)}
+
+\begin{figure*} %fullpage
+\centering
+\includegraphics[width=1.0\textwidth]{figures/ew.png}
+\caption
+{
+Physical properties of the outflow, shown by the coloured contours.
+The solid black line marks a sphere at $1000~r_G$.
+The dotted lines show the $72^\circ$ and $78^\circ$ sightlines 
+to the centre of the system, and illustrate that different sightlines
+intersect material of different ionization states.
+}
+\label{fig:ew}
+\end{figure*} %fullpage
+
+We find significant collisionally excited line emission emerges
+at low inclinations in the synthetic spectra, particular in the \civ line.
+The improved treatment of recombination also results in a strong \la\ line. 
+In the context of unification, this is a promising result, 
 and shows that a biconical wind can produce significant 
 emission at `quasar-like' angles. 
-Our simulated spectra do not contain the strong C~\textsc{iii}]~1909\AA\, 
-line seen in the quasar composite spectra. This is because we do not yet
-treat C as a full macro-atom with a full collisional rates between forbidden
+The spectra do not contain the strong C~\textsc{iii}]~1909\AA\, 
+line seen in the quasar composite spectra. 
+This is because we do not yet treat C as a full macro-atom with a 
+full collisional rates between forbidden
 or semi-forbidden transitions, as would be required.
 The critical density of the C~\textsc{iii}]~1909\AA\, line 
-is $n_e\sim10^{9.5}~\rm{cm^{-3}}$, which is higher than much of the 
-outer portion of our wind. We therefore expect a model with these 
-parameters to produce C~\textsc{iii}]~1909\AA\ with a proper treament. 
-% {\bf we have gone from their being lines we should see, to important coolants.
-I think we should stick to the fact that we would think our code would see them if we put C in as a macro atom.
-Also I think this who discussion of CIII should be after we have discussed what looks right with the emission lines.}
+is $n_e\sim10^{9.5}~\rm{cm^{-3}}$ \citep{wei1988}, which is higher than much of the 
+outer portion of our wind. 
+We therefore expect a model with these 
+parameters to produce a C~\textsc{iii}]~1909\AA\ line
+with a proper treament.
 
@@
 \subsubsection{The Angular Distribution of Line And Continuum Emission}
-\label{discsed}
-
-{\bf: I am not convinced this in the right place in the paper, because here we explore an alternative hypythesis.
-It might go better at the end.
-But a good many of the following sections are not that well motivated.}
-
-When comparing BALQSO and quasar composites, it is apparent
-that they possess remarkably similar line strengths and widths 
-\citep[e.g.][]{weymann1991,reichard2003}.  
-{\bf I think we mean EW here; otherwise I don't understand what we are talking about.
-We could say ``line shapes and equivalent widths''.
-I also think this requries more than one sentence of introduction.}
-This presents a challenge to our model, as well as the geometric 
-unification picture in general, because these quantities should vary with inclination angle.
-Limb darkening and foreshortening causes the disc continuum emission to be 
-strongly anisotropic, yet the line emission in our models is much more isotropic. 
-This has the effect of enhancing the line-to-continuum ratios at high inclinations. 
-To construct a scenario where emission 
-line equivalent widths are comparable at all inclinations requires 
-significant fine-tuning when considering a classical thin disc. {\bf Is the previous sentence a throwaway line, or has some person done this.  If so, please reference; if not please delete.}
-%An alternative, simpler solution is that the emergent continuum is roughly isotropic.
-
+\label{angular}
+
+In order to quantitatively assess how emission lines change with 
+inclination when blue-shifted absorption 
+may affect the line profile, we define the `red wing equivalent width' ($W_{\lambda,RW}$) as
+\begin{equation}
+W_{\lambda,RW} = \int_{\lambda_0}^{\lambda^\prime} \left( 1 - \frac{F_\lambda}{F_0} \right) d\lambda
+\label{rwew}
+\end{equation}
+where $F_0$ is the continuum flux and the integral is calculated from $\lambda_0$, line centre,
+to a wavelength $\lambda^\prime$ where the flux has returned to the continuum level.
+This quantity is shown as a function of inclination in figure 5 for the \civ\ and \mg\ UV lines.
+We also plot show the $W_{\lambda,RW}$ expected from isotropic line emission and a foreshortened 
+and limb darkened disc  as well as $1/2$ equivalent widths from \cite{dipompeo2012b}.
+
+BALQSOs and quasars generally possess very similar emission line properties 
+\citep[e.g.][]{weymann1991,reichard2003}. To demonstrate this, we show equivalent width
+mean values and standard devaitions from REF in table 3. Clearly, the variation
+with inclination in our models is far greater than than the variation 
+between quasar to BALQSO samples.  
+This presents a challenge to our model, as well as the geometric unification picture in general.
 Obviously,  one possible solution to this problem is hypothesize a more isotropic distribution for the emergent condition than predicted by a ``classical'' disc. 
@@
 the accretion disc SED to become more isotropic \citep[e.g.][]{zhang1997,munozdarias2013}. 
+However this effect is small in the UV and optical wavelength regimes, and the 
+disc is still anisotropic.
+
+Reprocessing by an extended outflow may also cause a more isotropic
+continuum to emerge. Hints that light scattered off a spatially extended 
+wind may contribute signiciantly to the emergent continuum come from radiative transfer s
+simulations \citep{simproga2012} and microlensing observations \citep{sluse2015}.
+However, neither of these examples have sufficient reprocessing efficiencies to 
+compensate for the disc anisotropy in this case.
+An alternative explanation, suggested by \cite{risaliti2011}, is that
+the BLR has the same angular distribution of emission as the accretion disc.
+They find that EW distributions in quasars are consistent with anisotropic emission 
+from optically thick, disc-like structures for {\em both} the continuum source and BLR. 
+If this is the case, it has a dramatic affect on the intrinsic
+BAL fraction inferred from flux-limited samples \citep{goodrich1997,krolikvoit1998}.
+
+The final possibility is that BALQSOs are not viewed equatorially. 
+This possibility is supported by measurements of the radio spectral indices
+of radio-loud BALQSOs (REF) and attempts to explain the polarisation dichotomy 
+of type 1 and 2 AGN (REF). This would imply that type 1 quasars and BALQSOs are generally 
+viewed from a fairly narrow range of angles ($0$-$50^\circ$, and could also mean 
+the BALQSO fraction requires {\em both} evolutionary and geometric explanations. 
+There is also clear conflict between this explanation and some
+polarisation results \citep{goodrich1995, cohen1995}(BROTHERTON).
+
+% When comparing BALQSO and quasar composites, it is apparent
+% that they possess remarkably similar line strengths and widths 
+% \citep[e.g.][]{weymann1991,reichard2003}.  
+% {\bf I think we mean EW here; otherwise I don't understand what we are talking about.
+We could say ``line shapes and equivalent widths''.
+I also think this requries more than one sentence of introduction.} This presents a challenge to our model, as well as the geometric
+% unification picture in general, because these quantities should vary with inclination angle.
+% Limb darkening and foreshortening causes the disc continuum emission to be 
+% strongly anisotropic, yet the line emission in our models is much more isotropic. 
+% This has the effect of enhancing the line-to-continuum ratios at high inclinations. 
+% To construct a scenario where emission 
+% line equivalent widths are comparable at all inclinations requires 
+% significant fine-tuning when considering a classical thin disc. {\bf Is the previous sentence a throwaway line, or has some person done this.  If so, please reference; if not please delete.}
+%An alternative, simpler solution is that the emergent continuum is roughly isotropic.
+
+% Obviously,  one possible solution to this problem is hypothesize a more isotropic distribution for the emergent condition than predicted by a ``classical'' disc. 
+% General relativistic effects -- specifically, light bending
+% and relativistic beaming -- can cause 
+% the accretion disc SED to become more isotropic \citep[e.g.][]{zhang1997,munozdarias2013}.
 Incorporating these effects into {\sc PYTHON} would be a very difficult and time-consuming challenge.
 Therefore, for the purposes of this discussion we have chosen to investigate whether GR effects could produce enough isotropy to address the EW problem, we have generated
-\ GR disc spectra, we use the code \agn\ \citep{hubeny2000,davishubeny2006,davis2007}. 
-The output flux at three different wavelengths
-as a function of inclination for an \agn\ model with the same disc and BH parameters
-as our clumpy wind model is shown in figure~\ref{fig:f2000}.  The results indicate that 
-the effects of GR on an AGN disc are much less extreme 
-in the UV portion of the spectrum than the calculations
-by \cite{zhang1997} for the X-rays in X-ray binaries.
-The emission for the disks of AGN is still strongly anisotropic.
-GR alone therefore cannot explain the line ratio trends in quasars by making the disc
-emit more isotropically. This supports the findings of \cite{risaliti2011}, 
-who find that EW distributions in quasars are consistent with anisotropic emission 
-from optically thick, 
-disc-like structures for {\em both} the continuum source and BLR. 
-If this is the case, it has a dramatic affect on the intrinsic
-BAL fraction inferred from flux-limited samples \citep{goodrich1997,krolikvoit1998}.
-We will explore these ideas further in a future study.  
-{\bf Wait!  All this says is that there has to be an alternative explanation.
-It is not support for any specific explanation!. This last few sentences should
-be a separate paragraph.  They should start out: An alernative explanation proposed 
-by risalite is that...}
+% \ GR disc spectra, we use the code \agn\ \citep{hubeny2000,davishubeny2006,davis2007}. 
+% The output flux at three different wavelengths
+% as a function of inclination for an \agn\ model with the same disc and BH parameters
+% as our clumpy wind model is shown in figure~\ref{fig:f2000}.  The results indicate that 
+% the effects of GR on an AGN disc are much less extreme 
+% in the UV portion of the spectrum than the calculations
+% by \cite{zhang1997} for the X-rays in X-ray binaries.
+% The emission for the disks of AGN is still strongly anisotropic.
+% GR alone therefore cannot explain the line ratio trends in quasars by making the disc
+% emit more isotropically. This supports the findings of \cite{risaliti2011}, 
+% who find that EW distributions in quasars are consistent with anisotropic emission 
+% from optically thick, 
+% disc-like structures for {\em both} the continuum source and BLR. 
+% If this is the case, it has a dramatic affect on the intrinsic
+% BAL fraction inferred from flux-limited samples \citep{goodrich1997,krolikvoit1998}.
+% We will explore these ideas further in a future study.  
+% {\bf Wait!  All this says is that there has to be an alternative explanation.
+% It is not support for any specific explanation!. This last few sentences should
+% be a separate paragraph.  They should start out: An alernative explanation proposed 
+% by risalite is that...}
 
@@
 \subsection{X-ray Properties and Broadband SEDs}
+\label{sec:xray}
 
@@
 \centering
-\includegraphics[width=1.0\textwidth]{figures/lx.png}
+\includegraphics[width=1.0\textwidth]{figures/lx_a05_pre.png}
 \caption
@@
 
-{\bf:  Again this section needs an introduction.  Why is this important?}
+%{\bf:  Again this section needs an introduction.  Why is this important?}
+
+One of the main motivations for including a treatment of clumping was
+to avoid over-ionization of the wind in the presence of strong X-rays. 
+Having verified that strong BALs appear in the synthetic spectra,
+it is also important to assess whether the X-ray properties of this
+next-generation model agree well with quasar and BALQSO samples for the relevant
+inclinations.
 
@@
 is also shown. For low inclination, `quasar-like' viewing angles,
-we now show excellent agreement with AGN samples. The gradient from $20^\circ$ to
+we now find excellent agreement with AGN samples. The gradient from $20^\circ$ to
 $60^\circ$ in our models is caused by a combination of disc foreshortening/limb-darkening 
@@
 X-ray weak \citep[as suggested by, e.g.][]{morabito2013},
-our isotropic assumption foe the X-ray source would be incorrect. 
+our isotropic assumption for the X-ray source would be incorrect. 
 A polar-biased X-ray source would result in a lower clumping factor being
@@
 {
-\civ , \mg , \al\ and Fe~\textsc{ii} line profiles for wind angles
+\civ , \mg , \al\ and Fe~\textsc{ii} line profiles for viewing angles
 from $72-79^\circ$. The profiles are plotted relative to the local
@@
 
-At certain sightlines, our model now produces blue-shifted BALs in \al\ and \mg --
+At certain sightlines, the synthetic spectra exhibit blue-shifted BALs in \al\ and \mg --
 the absorption lines seen in LoBALQSOs, and we even see absorption in Fe~\textsc{ii}
@@
 of BALQSO viewing angles. We find that ionization stratification
-of the wind causes lower ionization material has a smaller covering factor, 
+of the wind causes lower ionization material to have a smaller covering factor, 
 as demonstrated by figures~\ref{fig:wind} and \ref{fig:lobal}.
@@
 as predicted by polarisation results \citep{brotherton1997}.
+As observed in a BALQSO sample by \cite{filizak2014}, we find that
+BAL troughs are wider and deeper when lower ionization species are present,
+and high ionization lines have higher blue-edge velocities than the 
+lower ionization species.
 There is also a correlation between the strength of LoBAL features
@@
 intersects the line-of-sight. 
-Our model therefore predicts that LoBALQSOs and FeLoBALQSOs 
+A model such as this therefore predicts that LoBALQSOs and FeLoBALQSOs 
 have stronger Lyman edge absorption and 
-be more Compton-thick than HiBALQSOs and Type 1 quasars.
+are more Compton-thick than HiBALQSOs and Type 1 quasars.
 An edge-on scenario also offers a potential explanation for the rarity of LoBAL and
@@
 is independent of the assumed BLR geometry and size.
-\smallskip
-\item We have examined the effect of GR on our disc SED, using the disc atmosphere
-and GR ray-tracing code \agn. While including GR effects
-does cause the disc SED to become slightly more isotropic,
-the effect is not large enough to produce uniform line to continuum ratios
-with viewing angle. We briefly discuss other solutions.
+% \smallskip
+% \item We have examined the effect of GR on our disc SED, using the disc atmosphere
+% and GR ray-tracing code \agn. While including GR effects
+% does cause the disc SED to become slightly more isotropic,
+% the effect is not large enough to produce uniform line to continuum ratios
+% with viewing angle. We briefly discuss other solutions.
 \end{enumerate}
@@
 a clear challenge to the current disc wind unification picture.
+
+% To resolve these challenges, we suggest the following routes forward.
+% \begin{enumerate}
+% \smallskip
+% \item 
+% \smallskip
+% \item 
+% \smallskip
+% \item It is clear that the commonly accepted paradigm of an equatorial
+% wind with a covering factor of $\sim20\%$ does provide an adequate 
+% unified model, as shown here and by other authors 
+% (e.g. Marin \& Goosman 2013; DiPompeo et al. 2012a).
+% More collimated winds may solve some problems, but must be reconciled with
+% polarisation results that suggest an equatorial geometry.
+% Computing the polarisation of emergent energy packets in our 
+% MCRT code would allow direct comparison
+% between outputs from a known geometry and 
+% spectropolarimetry of quasars and AGN.
+% \smallskip
+% \item In addition to spectropolarimetry, one
+% of the best observational tools for probing outflow geometries
+% is reverberation mapping. We are starting to 
+% incorporate methods for predicting the reverberation
+% outputs from our models. By comparing with observational data, this
+% may provide stronger constraints on outflow geometries.
+% \end{enumerate}
 

### 2015-11-10 paper.tex
fixed edits

@@
 \citep{goodrich1995, cohen1995}, although there is also evidence
-for polar BAL outflows \citep{zhou2006}.
+for polar BAL outflows  in radio-loud (RL) sources \citep{zhou2006}.
 % although this geometry is contradicted
@@
 At the highest inclinations, the 
-cooler, lower ionization material at the base of the wind
+cooler, low ionization material at the base of the wind
 starts to intersect the line of sight. This produces 
-multiple absorption lines in lower ionization species such as \mg,
+multiple absorption lines in species such as \mg,
 \al\ and Fe~\textsc{ii}. The potential links to LoBALQSOs and 
@@
 of the strongest absorption in the profile varies with inclination.
-At lower inclinations, the strongest absorption occurs at the red edge,
-whereas at high inclinations (and for the strongest BALs)
+At the lowest inclination BAL sightlines, the strongest absorption occurs at the red edge,
+whereas at higher inclinations (and for the strongest BALs)
 the trough has a sharp edge at the terminal velocity.
@@
 with inclination in our models is far greater than than the variation 
-between quasar to BALQSO samples.  
+between, and standard deviation within, quasar and BALQSO samples.  
 This presents a challenge to our model, as well as the geometric unification picture in general.
-Obviously,  one possible solution to this problem is hypothesize a more isotropic distribution for the emergent condition than predicted by a ``classical'' disc. 
+One obvious potential solution to this problem is to hypothesize a more isotropic distribution 
+for the emergent condition than predicted by a classical thin disc. 
 General relativistic effects -- specifically, light bending
@@
 the accretion disc SED to become more isotropic \citep[e.g.][]{zhang1997,munozdarias2013}. 
-However this effect is small in the UV and optical wavelength regimes, and the 
-disc is still anisotropic.
+However, we have verified using AGNSPEC (REFs to Hubeny)
+that this effect is small in the UV and optical wavelength regimes, 
+and the disc is still anisotropic.
 
@@
 compensate for the disc anisotropy in this case.
-An alternative explanation, suggested by \cite{risaliti2011}, is that
-the BLR has the same angular distribution of emission as the accretion disc.
-They find that EW distributions in quasars are consistent with anisotropic emission 
+An alternative explanation is that the BLR has the same angular distribution 
+of emission as the accretion disc.
+Indeed, \cite{risaliti2011} find that EW distributions in quasars are consistent with anisotropic emission 
 from optically thick, disc-like structures for {\em both} the continuum source and BLR. 
@@
 
-The final possibility is that BALQSOs are not viewed equatorially. 
-This possibility is supported by measurements of the radio spectral indices
-of radio-loud BALQSOs (REF) and attempts to explain the polarisation dichotomy 
-of type 1 and 2 AGN (REF). This would imply that type 1 quasars and BALQSOs are generally 
-viewed from a fairly narrow range of angles ($0$-$50^\circ$, and could also mean 
-the BALQSO fraction requires {\em both} evolutionary and geometric explanations. 
-There is also clear conflict between this explanation and some
-polarisation results \citep{goodrich1995, cohen1995}(BROTHERTON).
+It is also possible that the equatorial paradigm invoked from early polarisation
+studies \citep{goodrich1995, cohen1995,brotherton2006} is an over-simplification, or is merely incorrect. 
+High brightness temperatures in some RL BALQSOs imply polar outflows \citep{zhou2006} 
+and \cite{bruni2012} find that
+RL BALQSOs possess similar radio spectral indices to normal RL quasars, 
+suggestive of comparable inclinations. 
+In addition, \cite{marin2013} find a bending angle of $\sim45^\circ$ is required to 
+explain the polarisation dichotomy of type 1 and 2 AGN using an Elvis-type wind 
+model (Elvis 2000). It is therefore possible 
+that type 1 quasars and BALQSOs are generally viewed from a fairly narrow range of angles 
+($\sim0$-$45^\circ$), or that {\em both} evolutionary and geometric explanations are required.
+We suggest that future modelling should include predictions of polarisation signatures
+from a detailed radiative transfer simulation, allowing direct comparison with spectropolarimetry
+of BALQSOs.
+
+% The final possibility is that BALQSOs are not viewed equatorially. 
+% This possibility is supported by measurements of the radio spectral indices
+% of radio-loud BALQSOs (REF) and attempts to explain the polarisation dichotomy 
+% of type 1 and 2 AGN (REF). This would imply that type 1 quasars and BALQSOs are generally 
+% viewed from a fairly narrow range of angles ($\sim0$-$50^\circ$), and could also mean 
+% the BALQSO fraction requires {\em both} evolutionary and geometric explanations. 
+% There is also clear conflict between this explanation and some
+% polarisation results \citep{goodrich1995, cohen1995}(BROTHERTON).
+% We suggest that future modelling should include predictions of polarisation signatures
+% from a detailed radiative transfer simulation, allowing
 
@@
 As observed in a BALQSO sample by \cite{filizak2014}, we find that
-BAL troughs are wider and deeper when lower ionization species are present,
+BAL troughs are wider and deeper when low ionization absorption features are present,
 and high ionization lines have higher blue-edge velocities than the 
-lower ionization species.
+low ionization species.
 There is also a correlation between the strength of LoBAL features
@@
 
-The work of JHM, SWM, NSH and CK is supported by the 
+The work of JHM, SWM, NSH and CKL is supported by the
 Science and Technology Facilities Council (STFC),
 via two studentships and a consolidated grant, respectively.
+CK also acknowledges a Leverhulme fellowship.
 We would like to thank Omer Blaes, Ivan Hubeny and Shane Davis for their
-assistance with \agn. We would also like to thank Daniel Proga, 
-Daniel Capellupo, Sam Connolly and Dirk Grupe for useful discussions.
-Simulations were conducted using \py\ version 79c, and made use of
-the IRIDIS High Performance Computing Facility at the University of Southampton.
-Figures were produced using {\tt matplotlib} \citep{matplotlib}.
+assistance with \agn. We are grateful to Mike Brotherton, Mike DiPompeo,
+Sebastien Hoenig and Frederic Marin for helpful correspondence regarding
+polarisation measurements and orientation indicators.
+We would also like to thank Daniel Proga, Daniel Capellupo, Sam Connolly and
+Dirk Grupe for useful discussions.  Simulations were conducted using \py\ version 80,
+and made use of the IRIDIS High Performance Computing Facility at the
+University of Southampton. Figures were produced using the {\tt matplotlib} plotting library
+\citep{matplotlib}.
 

### 2015-11-10 paper.tex
edited python intro

@@
 
-For this study, we use the MCRT code \py\  we have developed to carry out our radiative transfer and photoionization
-calculations in non-local thermodynamic equilibrium (non-LTE) in a variety of disk-wind systems. 
-We have used the code  to model accreting white dwarfs 
+For this study, we use the MCRT code \py\ we have developed to carry out our 
+radiative transfer and photoionization calculations in non-local thermodynamic 
+equilibrium (non-LTE) in a variety of disk-wind systems. 
+The code has been used to model accreting white dwarfs 
 (Long \& Knigge 2002, hereafter LK02; Noebauer et al. 2010; 
 Matthews et al. 2015, hereafter M15), young-stellar objects \citep{simmacro2005}
-and quasars (H13).\nocite{noebauer, M15, LK02}  LK02 provides the basic description of the original code; improvements, see especially H14 and M15, have been described in subsequent reports.
-A full description of the code will be published elsewhere; here we focus on the changes made to improve the ionization calculation and to allow for clumping in the wind.
+and quasars (H13).\nocite{noebauer, M15, LK02}  
+The basic premise involves generating photons from an accretion disc
+and central object, and computing their radiative transfer through an outflow.
+This outflow is discretized into $n_x \times n_z$ cells in a 2.5D
+cylindrical geometry with azimuthal symmetry.
+First, the code gradually converges on a global temperature and ionization structure.
+Once these ``ionization cycles'' are complete, then a series of further iterations
+are completed to obtain a detailed synthetic spectrum.
+LK02 provides the basic description of the original code; improvements, 
+see especially H14 and M15, have been described in subsequent reports.  
+%A full description of the code will be published elsewhere; 
+Therefore we focus here on the changes made to improve the ionization calculation 
+and to allow for clumping in the wind.
 %These studies contain extensive detail on the code,  so we only briefly describe the key elements of the global ionization calculation and other important aspects.
 
-{\bf ksl - I a a bit torn over whether we add a few 3 sentences to describe the basic idea.
+% {\bf ksl - I a a bit torn over whether we add a few 3 sentences to describe the basic idea.
 Some will be reading this for the first time.

### 2015-11-10 paper.tex
rm 0946

@@
 The simplest explanation for the incidence of 
-BAL quasars (BALQSOs) is in terms of an accretion disc wind (ADW). 
-Within the ADW paradigm, a biconical wind rises from 
+BAL quasars (BALQSOs) is in terms of an accretion disc wind. 
+According to this paradigm, a biconical wind rises from 
 the accretion disc and the BALQSO fraction is associated with
@@
 % by more recent studies of radio spectral indices \citep{dipompeo2012}.
-ADWs offer a natural explanation for the
+
+Due to their ubiquitous nature,
+disc winds offer a natural explanation for the
 diverse phenemonology of luminous AGN and QSOs \citep[e.g.][]{MCGV95, elvis2000}. 
@@
 may see a BALQSO or normal `Type 1' quasar.
-
-Within the ADW  unification framework, the broad-line region (BLR) can 
-correspond either to the dense wind base or dense clumps embedded
-in the outflows. Indeed, \cite{elitzur2014} show that a disc-wind BLR scenario
+Within this unification framework, the broad-line region (BLR) can 
+correspond either to the dense wind base or clumps embedded
+in the outflow. Indeed, \cite{elitzur2014} show that a disc-wind BLR scenario
 naturally explains the emission line evolution of AGN.
@@
 %{\bf ksl: I don't see what this paragraph has to do with our problem, which we need to clearly explain} Despite the clear importance of ADWs in understanding AGN SEDs and accretion physics,
-Despite the clear importance of ADWs in shaping quasar and AGN spectra,  
+Despite the clear importance of disc winds in shaping quasar and AGN spectra,  
 much of the underlying outflow physics remains highly uncertain. 
-Several possible driving mechanisms for ADWs have been proposed, including
+Several possible driving mechanisms have been proposed, including
 thermal pressure \citep{weymann1982, begelman1991}, magnetocentrifugal forces 
@@
 
-We have been engaged in a project to determine whether it is possible to simulate the properties of the spectra of AGN, including BAL QSOs, using simple kinematic prescriptions for biconical disc winds using a Monte Carlo radiative transfer code that calculates the ionization structure of the wind and simulates the spectra from such a system \citep[][hereafter H13]{simlong2008,sim2010,higginbottom2013}.
+We have been engaged in a project to determine whether it is possible to simulate the properties of the spectra of AGN, including BAL QSOs, using simple kinematic prescriptions for biconical disc winds using a Monte Carlo radiative transfer (MCRT) code that calculates the ionization structure of the wind and simulates the spectra from such a system \citep[][hereafter H13]{simlong2008,sim2010,higginbottom2013}.
 The results have encouraging in the sense that in H13, we showed we could produce simulated spectra that resembled that of BAL QSOs, as long as the luminosity of the central engine was relatively low, of order \POW{43}{\LUM} and the mass loss rate was relatively high, of order the mass accretion rate.
@@
 In section 2, we describe some of the important photoionization 
-and MCRT aspects of the code. In section 3, we outline the model, including 
-a description of our clumping implementation. In section 4, we present the results 
-from a clumped model. In section 5 we discuss our results, 
-focussing particular on the anisotropy of 
-disc emission and GR effects, and finally, in section 6, we summarise our findings.
+and MCRT aspects of the code. We then outline the model in section 3, including 
+a description of our clumping implementation and success criteria. 
+Section 4 contains the results from a clumped model, which we discuss results
+in comparison to observational data. Finally, we summarise our findings in section 5.
 
@@
 For this study, we use the MCRT code \py\ we have developed to carry out our 
-radiative transfer and photoionization calculations in non-local thermodynamic 
-equilibrium (non-LTE) in a variety of disk-wind systems. 
-The code has been used to model accreting white dwarfs 
+radiative transfer and photoionization simulations in non-local thermodynamic
+equilibrium (non-LTE). The code can be used to model a variety of
+disc-wind systems; it has been used with application to accreting white dwarfs 
 (Long \& Knigge 2002, hereafter LK02; Noebauer et al. 2010; 
-Matthews et al. 2015, hereafter M15), young-stellar objects \citep{simmacro2005}
-and quasars (H13).\nocite{noebauer, M15, LK02}  
+Matthews et al. 2015, hereafter M15), young-stellar objects 
+\citep{simmacro2005} and quasars/AGN (H13, H14).\nocite{noebauer, M15, LK02}
+
 The basic premise involves generating photons from an accretion disc
@@
 cylindrical geometry with azimuthal symmetry.
-First, the code gradually converges on a global temperature and ionization structure.
+First, the code gradually converges on the global temperature and ionization structure.
 Once these ``ionization cycles'' are complete, then a series of further iterations
-are completed to obtain a detailed synthetic spectrum.
+allow one to obtain a detailed synthetic spectrum.
 LK02 provides the basic description of the original code; improvements, 
-see especially H14 and M15, have been described in subsequent reports.  
+see especially \cite{simmacro2005}, H13 and M15, have been 
+described in subsequent reports.  
 %A full description of the code will be published elsewhere; 
-Therefore we focus here on the changes made to improve the ionization calculation 
+We focus here on the specific changes made to improve the ionization calculation 
 and to allow for clumping in the wind.
@@
 we model the SED in a grid cell using the technique described by H13. In this scheme,
-the mean intensity in a series of $n$ bands is modeled as either a power law or exponential
+the mean intensity, $J_{\nu}$ in a series of $n$ bands is modeled as either a power law or exponential
 in frequency $\nu$, with the fit parameters deduced from band-limited radiation field estimators.
@@
 \end{equation}
-where $\sigma_j$ is the photoionization cross-section and $C_{j}$
+where $\sigma_j$ is the photoionization cross-section, $n_e$
+is the electron density and $C_{j}$
 represents the collisional ionization coefficient.
@@
 \begin{equation}
-R_{j+1,j}(T_e) = (\alpha^j_{RR} + \alpha^j_{DR} + \alpha^j_{CR}) n_{j+1} n_e,
+R_{j+1,j}(T_e) = (\alpha^j_{RR} + \alpha^j_{CR}) n_{j+1} n_e,
 \end{equation}
 where each $\alpha^j$ here is the recombination rate coefficient into the ground state of ion $j$.
-The subscripts denote radiative, dielectronic and 
+The subscripts denote radiative and 
 collisional (three-body) recombination, respectively. 
+$T_e$ is the electron temperature.
 %% We neglect recombination to and from excited states in the simple-ion calculation. 
@@
 and $g_k$ is the statistical weight of level $k$. 
+We stress that this approximation is not required for ions
+treated as macro-atoms.
 
@@
 \centering
-\includegraphics[width=1.0\textwidth]{figures/link.png}
+\includegraphics[width=1.0\textwidth]{figures/link8.png}
 \caption
 {
-Physical properties of the outflow, shown by the coloured contours.
+Contour plots showing the logarithm of some important 
+physical properties of the outflow. Symbols are defined in the text.
 The solid black line marks a sphere at $1000~r_G$.
@@
 intersect material of different ionization states.
+The line luminosities represent the luminosity of photons
+escaping the Sobolev region for each line. These photons do not
+necessarily escape to infinity.
 }
@@
 $f$ 	&	 $0.01^*$  \\
+$n_x$ 	&	 $100$  \\
+$n_z$ 	&	 $200$  \\
 \hline 
@@
 in the base of the wind giving way to highly ionized plasma further out.
+This is illustrated in figure~\ref{fig:wind} 
+by the panels showing the ion fraction $F=n_j/n_{tot}$ of some important ions.
 By clumping the wind, we are able to produce the range of ionization states observed
@@
 The radii of these emitting regions is important,
-and can be compared to observations. As shown in figure~\ref{fig:wind},
+and can be compared to observations. The line luminosities 
+shown in the figure correspond to the luminosity in $\LUM$ of photons
+escaping the Sobolev region for each line. 
+This is equivalent to $\beta_{ul} n_u A_{ul}$, where the three quantities
+represent the Sobolev escape probability, upper level number density and 
+Einstein A coefficient for the line. 
+As shown in figure~\ref{fig:wind},
 the \civ\ line in our model is typically formed between 
@@
 
-\begin{figure*} %fullpage
-\centering
-\includegraphics[width=1.0\textwidth]{figures/0946.png}
-\caption
-{
-Synthetic spectra at $72^\circ$ compared to an HST STIS spectrum
-of PG0946+301 (Arav et al. 2000). The spectrum is scaled to the flux at 1300\AA\
-for direct comparison. 
-}
-\label{fig:stis}
-\end{figure*} %fullpage
+% \begin{figure*} %fullpage
+% \centering
+% \includegraphics[width=1.0\textwidth]{figures/0946.png}
+% \caption
+% {
+% Synthetic spectra at $72^\circ$ compared to an HST STIS spectrum
+% of PG0946+301 (Arav et al. 2000). The spectrum is scaled to the flux at 1300\AA\
+% for direct comparison. 
+% }
+% \label{fig:stis}
+% \end{figure*} %fullpage
 
@@
 contribution along sightlines which do not pass through the BAL region,
-meaning that any scattered contribution is obscured by the saturated troughs.
+meaning that any scattered component to the BAL troughs is absorbed by line opacity.
 This suggests that either the scattering cross-section of the wind must
@@
 We find significant collisionally excited line emission emerges
-at low inclinations in the synthetic spectra, particular in the \civ line.
+at low inclinations in the synthetic spectra, particular in the \civ\ line.
 The improved treatment of recombination also results in a strong \la\ line. 

### 2015-11-10 compare.tex
updated figure

--- 2015-11-10 paper.tex
@@
 %\usepackage{pngfig}
-%\usepackage[dvips]{color}mak
+%\usepackage[dvips]{color}
 %\usepackage{aabib}
@@
 \def\aaps{A\&As}
-\def\LA{Lyman\thinspace$\alpha$}
-
-\newcommand{\EXPN}[2]{\mbox{$#1\times 10^{#2}$}}
-\newcommand{\EXPU}[3]{\mbox{\rm $#1 \times 10^{#2} \rm\:#3$}}  % exponent with units
-\newcommand{\POW}[2]{\mbox{$\rm10^{#1}\rm\:#2$}}
-\def\LUM{\:{\rm ergs\:s^{-1}}}
-\def\FLUX{\:{\rm ergs\:cm^{-2}\:s^{-1}}}
-\def\OIGS{\:{\rm ergs\:cm^{-2}\:s^{-1}\:\AA^{-1}}}
 
@@
 % clumpy winds and broad emission lines
-Testing Quasar Unification with Clumpy Wind Models
-%Unifying quasars with clumpy wind models
+Unifying quasars with clumpy wind models
 }
+
+% [Matthews, J.]
+% \author[Matthews, J.]{James Matthews \\
+% {\sl  Supervisor: Prof. Christian Knigge} \\
+% {\sl School of Physics \& Astronomy, University of Southampton,
+%   Southampton, SO17 1BJ, UK}}
 
@@
 \parbox[t]{\textwidth}{
-James~H.~Matthews$^1$\thanks{jm8g08@soton.ac.uk}, Christian~Knigge$^1$,
-Nick~Higginbottom$^1$, Knox~S.~Long$^2$, Stuart~A.~Sim$^3$ and Sam~W.~Mangham$^1$
+J.~H.~Matthews$^1$\thanks{jm8g08@soton.ac.uk}, C.~Knigge$^1$,
+N.~Higginbottom$^1$, K.~S.~Long$^2$, S.~A.~Sim$^3$ and S.~W.~Mangham$^1$
 }
@@
 % holistic picture of the quasar population.
-Various unification schemes have been proposed to interpret the complex phenomenology 
-of quasars and luminous active galactic nuclei (AGN) in terms of  a simple axisymmetric 
-picture involving a central black hole, an accretion disc and an associated outflow.
-Here, we continue our tests of  this paradigm by comparing ``average'' AGN spectra to 
-synthetic spectra of simple biconical disc wind models, using our state-of-the-art 
-Monte Carlo radiative transfer and photoionization code.
-In particular, we investigate whether clumping of the outflow allows us to 
-produce synthetic spectra in the rest-frame UV that have the characteristics of AGN, 
-assuming total luminosities as high as 10$^{45}$ ergs s$^{-1}$. 
+Various unification schemes for quasars and luminous active galactic nuclei (AGN) 
+propose that much of their complex phenomenology can be explained by a simple 
+geometrical picture involving an accretion disc and associated outflow.
+Here, we test this paradigm by utilising our state-of-the-art radiative transfer 
+and photoionization code to produce synthetic spectra from simple biconical disc wind models. 
+In particular, we expand on our previous work by presenting a model that
+exhibits many of the spectral features expected from a quasar unification model.
 We find that a simple treatment of clumping (`microclumping') 
-allows for a more realistic AGN luminosities, while maintaining the ionization 
-state necessary for strong BAL features in the rest-frame UV. 
-We examine the X-ray properties of these simple clumped models
+allows for a more realistic X-ray luminosity in the model,
+while maintaining the ionization state necessary for strong BAL features. 
+We examine the X-ray properties of this new model
 and find good agreement with existing X-ray samples of AGN and quasars.
-The dense, X-ray heated wind produces strong recombination and collisionally 
-excited line emission in, e.g., \civ\ and \la, to emerge at the low inclination, 
-`Type 1 quasar-like' angles. 
-At the highest inclinations, the synthetic spectra possess prominent \mg\ and \al\ BALs, the absorption features seen in LoBAL quasars. 
-Despite these successes, we are unable to reproduce 
+We find that the dense, X-ray heated wind 
+produces strong recombination and collisionally excited line emission in, 
+e.g., \civ\ and \la, to emerge at the low inclination, `Type 1 quasar-like' angles. 
+The highest inclination models possess prominent \mg\ and \al\ BALs, the absorption 
+features seen in LoBAL quasars. Despite these successes, we are unable to reproduce 
 the remarkably uniform emission line properties 
+% remarkably similar of line-to-continuum ratios apparent 
 seen in BAL and non-BAL quasar composites.
-% {\bf This sentence needs to be more precise, especially in 
-% light of the statement earlier in the abstract about ``good agreement''}
 This is due to a fundamental constraint arising
 from the anisotropy of emission from a classical thin disc. 
+We briefly explore the impact of general relativistic effects
+on the angular distribution of disc continuum emission, and find that 
+they are not sufficient to produce a self-consistent model.
+% relativistic beaming, gravitational redshift and 
+% light bending on the angular distribution of disc continuum emission. 
+% We find that these general relativistic effects are not yet sufficient to produce a
+% self-consistent model. 
 Overall, our work suggests that geometric unification
@@
 pose a number of difficult challenges to such a model.
-% {\bf There is confusion in the abstract, at least, in what is the model and what is the synthetic spectra, as well as whether there is one model or many models.
-We need to try to be clear.
-The model should be a clumped biconical outflow.
-There are then particular instantiations of the model.
-And then there are synthetic spectra}
 \end{abstract}
@@
 
+% Introduction focussing on key points
+% \begin{itemize}
+% \item standard wind + BALQSO introduction
+% \item focus on unification and that we are testing it
+% \item some discussion of scales, referencing e.g. reverb maps, variability, microlensing, Arav 
+% \item clumping background: stellar winds, clumping in AGN winds, variability
+% \end{itemize}
+
 The spectra of 
@@
 with an underlying blue continuum - the so-called {\sl `big blue bump'} (BBB). 
-The BBB is often attributed to emission from a 
+The BBB is often attributed to emssion from a 
 geometrically thin, optically thick accretion disc surrounding the central black hole, similar
 to that described by \cite{shakurasunyaev1973}.
-% {\bf Note: the first half of this paragraph and the second do not follow from one another.  
-% The first half is about spectra the second about outflows and the connection to spectra is not made until the next paragrph.  
-% This needs fixing. JM: Knox, I like this structure...I start with inflow, then move to outflow.}
-In addition to the {\em inflowing} accreting material, 
-{\em outflows} are ubiquitous in AGN
+In addition to the inflowing accreting material,
+outflows are ubiquitous in AGN
 and quasars \citep{kellerman1989,ganguly2008}. These outflows can take the form of 
@@
 
-Perhaps the clearest evidence of outflows in AGN is  
-the blueshifted ($\sim 0.1c$) broad absorption lines (BALs) in the 
-ultraviolet seen in approximately $20\%$ of quasars
+Approximately $20\%$ of quasars exhibit blueshifted ($\sim 0.1c$)
+broad absorption lines (BALs) in the ultraviolet,
+providing clear evidence for outflowing absorbing material
 \citep{weymann1991, reichard2003, knigge2008, turnermiller2009, allen2011}.
@@
 the covering factor of the outflow. 
-Polarisation studies expect the wind to be roughly equatorial
-\citep{goodrich1995, cohen1995}, although there is also evidence
-for polar BAL outflows  in radio-loud (RL) sources \citep{zhou2006}.
-% although this geometry is contradicted
-% by more recent studies of radio spectral indices \citep{dipompeo2012}.
+The wind is expected to be roughly equatorial from polarisation results
+\citep{goodrich1995, cohen1995}.
 ADWs offer a natural explanation for the
@@
 may see a BALQSO or normal `Type 1' quasar.
-
-Within the ADW  unification framework, the broad-line region (BLR) can 
+Within this framework, the broad-line region (BLR) can 
 correspond either to the dense wind base or dense clumps embedded
-in the outflows. Indeed, \cite{elitzur2014} show that a disc-wind BLR scenario
+in the outflows. Indeed, \cite{elitzur2014} found that a disc-wind BLR scenario
 naturally explains the emission line evolution of AGN.
 A biconical wind model can also readily explain the various sub-classifications of BALQSOs: 
-HiBALQSOs, which only exhibit high ionization line absorption; LoBALQSOs, which also show
+HiBALQSOs, which only exhibit higher ionization line absorption; LoBALQSOs which also show
 absorption in lower ionization state species such as \mg\ and \al; and
-FeLoBALQSOs, which show further absorption in Fe~\textsc{ii} and \textsc{iii}.
-In unified geometric models, this is generally attributed to ionization stratification
+FeLoBALQSOs which show further absorption in Fe~\textsc{ii} and \textsc{iii}.
+In unified models, this is generally attributed to ionization stratification
 of the outflow \citep[e.g.][]{elvis2000}.
@@
 % As well as acting as a source of photoionized plasma, a 
-% As well as imprinting clear line absorption and emission
-% features, disc winds may also have a profound effect on the structure and 
-% emergent {\em continuum} of the accretion disc itself.
-% Mass-loss will alter the accretion rate and resultant 
-% temperature of the accretion disc, possibly explaining some 
-% of the features typically seen in luminous AGN \citep{knigge1999,laordavis2014}.
-% There have been numerous difficulties when confronting 
-% theoretical accretion disc models with observations 
-% \citep[see e.g.][]{blaes1998}. However, AGN spectral energy distributions (SEDs) can now, 
-% in general, be fitted well with accretion disc models
-% when the effects of general relativity (GR), Comptonisation
-% and mass-loss are included \citep{capellupo2015}. Mass-loss therefore appears to be 
-% critical if an accretion disc model is to successfully fit AGN SEDs, 
-% particular in the UV region of the spectrum.
-
-%{\bf ksl: I don't see what this paragraph has to do with our problem, which we need to clearly explain} Despite the clear importance of ADWs in understanding AGN SEDs and accretion physics,
-Despite the clear importance of ADWs in shaping quasar and AGN spectra,  
+As well as imprinting clear line absorption and emission
+features, disc winds may also have a profound effect on the structure and 
+emergent {\em continuum} of the accretion disc itself.
+Mass-loss will alter the accretion rate and resultant 
+temperature of the accretion disc, possibly explaining some 
+of the features typically seen in luminous AGN \citep{knigge1999,laordavis2014}.
+There have been numerous difficulties when confronting 
+theoretical accretion disc models with observations 
+\citep[see e.g.][]{blaes1998}. However, AGN spectral energy distributions (SEDs) can now, 
+in general, be fitted well with accretion disc models
+when the effects of general relativity (GR), Comptonisation
+and mass-loss are included \citep{capellupo2015}. Mass-loss therefore appears to be 
+critical if an accretion disc model is to successfully fit AGN SEDs, 
+particular in the UV region of the spectrum.
+
+Despite the clear importance of ADWs in understanding AGN SEDs and accretion physics, 
 much of the underlying outflow physics remains highly uncertain. 
@@
 \citep{reeves2003,poundsreeves2009,tombesi2010a}.
-% The presence of line-locked features \citep{bowler2014} 
-% and the `ghost of \la' (Arav et al. 1996; Arav 1996; North 2006; but see 
-% also Cottis et al. 2010) \nocite{arav1995, arav1996, north2006,cottis2010}
-% in the spectra of some BALQSOs also gives clearer evidence that line-driving is
-% at least partially contributing to the acceleration of the wind.
+The presence of line-locked features \citep{bowler2014} 
+and the `ghost of \la' (Arav et al. 1996; Arav 1996; North 2006; but see 
+also Cottis et al. 2010) \nocite{arav1995, arav1996, north2006,cottis2010}
+in the spectra of some BALQSOs also gives clearer evidence that line-driving is
+at least partially contributing to the acceleration of the wind.
+
 The efficiency of line-driving is crucially dependent on the ionization state 
@@
 a region of `hitchhiking gas' that could shield the wind from the central X-ray source. 
-% Hydrodynamic simulations of line-driven disc winds also found a shielding region
-% was required to maintain the correct ionization state \citep{PSK2000,PK04}. 
-% However, \cite{sim2010_hydro} and \cite{H14} showed that including multiple scattering means the ionizing radiation field could still reach the previously shielded regions 
-% in those particular models.
+Hydrodynamic simulations of line-driven disc winds also found a shielding region
+was required to maintain the correct ionization state \citep{PSK2000,PK04}. 
+However, \cite{H14} showed that including multiple scattering means the ionizing radiation 
+field could still reach the previously shielded regions in those particular models.
 An additional or alternative solution is that the wind is clumped \citep[e.g.][]{hamann2013}
@@
 \citep{krolik1981, emmering1992, dekool1995, cassidyraine1996}.
-Clumping can be caused by magnetic confinement \citep{dekool1995},
+Clumping can be caused by magnetic confinement \cite{dekool1995},
 or the instabilities inherent to line-driven winds 
@@
 in line-driven hot star winds \citep{hillier1991eswingsmodel}. Complex substructures 
-are also produced in simulations of line-driven 
-outflows in AGN, although on very different scales to line-driven instabilities 
-\citep{PSK2000,PK04,progakurosawa2010,proga2014}.
-Nevertheless, clumpy winds offer an observationally motivated and theoretically 
+on a variety of scales are also produced in simulations of line-driven 
+outflows in AGN \citep{PSK2000,PK04,progakurosawa2010,proga2014}.
+Clumpy winds therefore offer an observationally motivated and theoretically 
 predicted way to lower the ionization state of a plasma, possibly in tandem
@@
 
-We have been engaged in a project to determine whether it is possible to simulate the properties of the spectra of AGN, including BAL QSOs, using simple kinematic prescriptions for biconical disc winds using a Monte Carlo radiative transfer code that calculates the ionization structure of the wind and simulates the spectra from such a system \citep[][hereafter H13]{simlong2008,sim2010,higginbottom2013}.
-The results have encouraging in the sense that in H13, we showed we could produce simulated spectra that resembled that of BAL QSOs, as long as the luminosity of the central engine was relatively low, of order \POW{43}{\LUM} and the mass loss rate was relatively high, of order the mass accretion rate.
-However, at higher luminosities, the wind was so ionized that UV absorption lines were not produced.
-In addition, and in part due to limitations in our radiative transfer code, the model failed to produce spectra with strong emission lines at any inclination angle.
-
-Here we attempt to address both of these issues, by introducing clumping into our model and a more complete treatment of H and He into our radiative transfer calculations.
-The remainder of this paper is organized as follows:
-% There has been some success using simple kinematic prescriptions for biconical disc winds to model  AGN and quasar outflows \citep[][hereafter H13]{simlong2008,sim2010,higginbottom2013}.
-H13 successfully produced a benchmark model for BALQSOs.
-However, the model had two key drawbacks.
-First, an unrealistically low X-ray luminosity was required in order to prevent over-ionization of the outflow.
-Second, the model failed to produce the strong emission lines  required at low inclinations in a unified model.
-In this paper, we attempt to address these issues, and test the disc wind  unification model using Monte Carlo radiative transfer (MCRT) and photoionization  calculations.
-The paper is organised as follows.
+There has been some success using simple
+kinematic prescriptions for biconical disc winds to model 
+AGN and quasar outflows \citep[][hereafter H13]{simlong2008,sim2010,higginbottom2013}. 
+H13 successfully produced a benchmark model for BALQSOs. However, the model
+had two key drawbacks. First, an unrealistically low X-ray luminosity
+was required in order to prevent over-ionization of the outflow.
+Second, the model failed to produce the strong emission lines 
+required at low inclinations in a unified model.
+In this paper, we attempt to address these issues, and test the disc wind 
+unification model using Monte Carlo radiative transfer (MCRT) and photoionization 
+calculations. The paper is organised as follows.
 In section 2, we describe some of the important photoionization 
@@
 
-For this study, we use the MCRT code \py\  we have developed to carry out our radiative transfer and photoionization
-calculations in non-local thermodynamic equilibrium (non-LTE) in a variety of disk-wind systems. 
-We have used the code  to model accreting white dwarfs 
+We use the MCRT code \py\ to carry out our radiative transfer and photoionization
+calculations in non-local thermodynamic equilibrium (non-LTE). 
+The code has been used to model accreting white dwarfs 
 (Long \& Knigge 2002, hereafter LK02; Noebauer et al. 2010; 
 Matthews et al. 2015, hereafter M15), young-stellar objects \citep{simmacro2005}
-and quasars (H13).\nocite{noebauer, M15, LK02}  LK02 provides the basic description of the original code; improvements, see especially H14 and M15, have been described in subsequent reports.
-A full description of the code will be published elsewhere; here we focus on the changes made to improve the ionization calculation and to allow for clumping in the wind.
-%These studies contain extensive detail on the code,  so we only briefly describe the key elements of the global ionization calculation and other important aspects.
-
-{\bf ksl - I a a bit torn over whether we add a few 3 sentences to describe the basic idea.
-Some will be reading this for the first time.
-Items that one would include are that we calculate the radiative transfer in a cylindrical coordinate system of dimension ??
-x ??.
-We have ionization and spectral cycles.
-In each cycle, ??
-photon bundles are generated.
-We stop the ionization cycles after they converge, without any details.
-I think this would be useful because we introduce terms like ``cell'' later on.', and without some kind of description they have no context}
+and quasars (H13). \nocite{noebauer, M15, LK02}
+These studies contain extensive detail on the code, 
+so we only briefly describe the key elements of the global 
+ionization calculation and other important aspects.
 
@@
 
-Our approach to line transfer is based upon the macro-atom implementation developed by \cite{lucy2002, lucy2003}.
-In our case, for reasons of computational effieciency, we adopt the  hybrid macro-atom scheme
-described by M15 
-%(an improvement over that used by H14 for our earlier quasar study), 
+To treat line transfer, we adopt the same hybrid scheme 
+described by M15, 
 in which the energy flows
@@
 These energy packets interact with either two-level `simple ions'
-or full `macro-atoms'. 
+or full `macro-atoms'. The macro-atom implementation 
+is described in full by \cite{lucy2002, lucy2003}.
 Our scheme allows one to treat non-LTE line transfer in radiative equilibrium
-without approximation for elements that are identified as 
+without approximation for elements which are identified as 
 full macro-atoms, while maintaining the fast `two-level' 
@@
 we expect recombination to be important
-in determining their level populations and resultant line emission, and because we were especially interested in the contribution to AGN spectra of \LA.
-In H13, all atoms were treated in a two-level approximation.
+in determining its level populations and resultant line emission.
 
@@
 Macro-atoms have their ion and level populations derived from
-MC rate estimators as described by Lucy (2002,2003). Previously (LK02, H13, M15),
-we used a modified Saha approach to calculate the ionization fractions
-of simple-ions. As part of  this effort, we have now improved {\sc PYTHON} to explicitly solve the 
-rate equations between ions in non-LTE. This dispenses with a number of small assumptions 
-made in the modified Saha approach, is more numerically stable, and, in principle, allows 
-the direct addition of extra physical processes that would previously have necessitated 
-approximate treatments.
-
-In order to calculate the photoionization rate, 
-we model the SED in a grid cell using the technique described by H13. In this scheme,
-the mean intensity in a series of $n$ bands is modeled as either a power law or exponential
-in frequency $\nu$, with the fit parameters deduced from band-limited radiation field estimators.
-% \begin{equation}
-% J_{\nu,i}=K_{pl}\nu^{\alpha_{pl}},
-% \end{equation}
-% for a band $i$, or an exponential 
-% \begin{equation}
-% J_{\nu,i}=K_{exp} e^{(-h\nu/k T_{exp})}.
-% \end{equation}
-% Here, $K_{exp}$, $K_{pl}$, $T_{exp}$ and $\alpha_{pl}$ are spectral fit parameters
-% deduced from the band-limited radiation field estimators.
+MC rate estimators as described by M15. Previously (LK02, H13, M15),
+we adopted a modified Saha approach to calculate the ionization fractions
+of simple-ions. We have now improved our code to explicitly solve the 
+rate equations between ions in non-LTE. 
+This dispenses with a number of small assumptions made in the modified Saha approach, 
+is more numerically stable, 
+and, in principle, allows the direct addition of extra physical 
+processes such as Auger ionization.
+
+%To avoid approximating the complex AGN SED as e.g. a dilute blackbody \citep[][M15]{ML93},
+We model the SED in a cell using the technique described by H13. In this scheme,
+the mean intensity in a series of $n$ bands is modeled as a normalised power law in 
+frequency $\nu$
+\begin{equation}
+J_{\nu,i}=K_{pl}\nu^{\alpha_{pl}},
+\end{equation}
+for a band $i$, or an exponential 
+\begin{equation}
+J_{\nu,i}=K_{exp} e^{(-h\nu/k T_{exp})}.
+\end{equation}
+Here, $K_{exp}$, $K_{pl}$, $T_{exp}$ and $\alpha_{pl}$ are spectral fit parameters
+deduced from the band-limited radiation field estimators.
 The ionization rate out of ion $j$ can then be written as 
@@
 \sum_{band~i=0}^{n}~
-{\int_{\nu_i}^{~\nu_i+1} \frac{4 \pi J_{\nu,i}\sigma_j(\nu)}  {h \nu} d\nu}
+{\int_{\nu_i}^{~\nu_i+1}{J_{\nu,i}\sigma_j(\nu)\nu^{-1}d\nu}}
 \right),}
@@
 collisional (three-body) recombination, respectively.
-%% We neglect recombination to and from excited states in the simple-ion calculation. 
+We neglect recombination to and from excited states in the simple-ion calculation. 
 For simple-ions, we use a dilute Boltzmann equation to calculate 
@@
 
+% We improve on this method by abandoning the modified Saha approach
+% entirely, and instead computing the ionization state by 
+% explicitly solving the rate equations in between ions in non-LTE. 
+% Photoionization and recombination rates are calculated using MC estimators recorded
+% during the photon propagation. Not only does this dispense with a number of
+% small assumptions made in the modified Saha approach, it is also more numerically stable, 
+% and in principle allows the direct addition of extra physical processes such as Auger ionization, which would have to be approximated if using the previous technique.
 \subsection{Physical Processes}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
+
 % MODEL DESCRIPTION
-%
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 geometry is similar to that invoked by \cite{MCGV95} and 
-\cite{elvis2000} to explain the phenomenonology
+\cite{elvis2000} in order to explain the phenomenonology
 of quasars and BALQSOs.
@@
 
+% \subsection{A Benchmark Model for BALQSOs}
+
+% \cite{higginbottom2013} presented a benchmark model for
+% (BAL)QSOs...introduce key parameters.
+
 \subsection{Photon Sources}
+
+%Describe the photon sources in the model.
 
@@
 and central BH mass ($M_{BH}$).
-All photon sources in our model are assumed to be opaque, meaning
+All photon sources in our model are assumed to beopaque, meaning
 that photons which strike them are destroyed.
@@
 constraint (see Lucy 2002, M15).
+% \begin{equation}
+
+% \end{equation}
+
+% With a normalisation such that it produces the correct 2-10kev luminosity.
+
+% Photons striking the
+
+% which successfully reproduced BAL features 
+% in synthetic spectra using \py. However, the model
+% had a few key drawbacks when considering its potential
+% for unification. First, it failed to produce significant
+% broad emission lines at non-BAL viewing angles; this is 
+% a key requirement for a unified QSO model. Second,
+% the model was significantly X-ray weak, as it was found
+% that an X-ray luminosity comparable to that of a QSO 
+% over-ionized the wind, resulting in no UV resonance 
+% line absorption features.
 
@@
 but also the density and ionization state of the outflow.
-A wind that accelerates more slowly will have a denser wind base
+A wind which accelerates more slowly will have a denser wind base
 with correspondingly different ionization and emission characteristics.
@@
 \subsection{Clumping}
-
-Our previous modelling efforts assumed a smooth outflow, 
-in which the density at a given point was determined only by the 
-kinematic parameters and mass loss rate. However, as already discussed,
-AGN winds exhibit significant substructure -- the outflow is expected to be
-{\em clumpy}, rather than smooth, and probably on a variety of scales. 
-Implementing a treatment of clumping is challenging, for
-two main reasons. First, there are significant 
-computational difficulties associated with adequately
-resolving and realistically modelling a series of small scale, high density
-regions with a MCRT code. Second, the addition of multiple additional degrees of
-freedom in the model results in significantly wider parameter space.
-Unfortuantely, the physical scale lengths and density contrasts 
-associated with these parameters cannot be well-constrained from observations.
 
@@
 used extensively in stellar wind modelling, known as 
-{\em microclumping} \citep{hamann1998}(MORE REFS). The key assumption here is that 
+{\em microclumping} \citep{hamann1998}. The key assumption here is that 
 typical clump sizes are much smaller than the typical photon mean free path, 
@@
 will remain unchanged for a given ionization state. 
+% A factor $f$ is also
+% applied to the opacities such that opacities which scale only with $\rho$ are not
+% increased.
 
@@
 
-\subsection{The Simulation Grid: Arriving at a next-generation model}
-
-Using this prescription, we conducted a limited parameter
-search over a 5-dimensional parameter space involving the 
-variables $r_{min}$, $\theta_{min}$, $f$, $\alpha$ and $R_v$.
-The grid points are shown in table 1.
-The aim here was to first fix $M_{BH}$ and $\dot{m}$ to their H13 values,
-and increase $L_X$ to $10^{45}$~erg~s$^{-1}$ (a more realistic value for a 
-quasar of $10^9M_\odot$ and an eddington fraction of $0.2$; see section~\ref{sec:xray}). 
-We then evaluated these models based on the following criteria:
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% RESULTS
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Results and Discussion}
+
+Here we describe the results from our model, the parameters
+of which are shown in table~1.
+Parameters differing from the benchmark model of
+H13 are highlighted with an asterisk.
+This set of parameters
+was arrived at by conducting a limited grid search over a 
+5-dimensional parameter space involving the variables
+$r_{min}$, $\theta_{min}$, $f$, $\alpha$ and $R_V$.
+The full grid, including output spectral files and plots can be found at
+\url{jhmatthews.github.io/quasar-wind-grid/}.
+We evaluated these models qualitatively based on the following
+criteria:
 \begin{itemize}
-\item Does the model avoid over-ionization and thus produce strong BALs with $BI > ??$?
-\item Does significant line emission emerge at low inclinations, with $EW\sim50\AA$ in \civ?
-\item Do H recombination lines appear in the spectrum, $EW\sim50\AA$ in \la?
+\item Does the model maintain the right ionization state to produce strong BALs?
+\item Does significant line emission emerge at low inclinations?
+\item Do H recombination lines appear in the spectrum?
 \item Do a certain range of angles produce LoBAL features?
@@
 \end{itemize}
-We arrived at a model
 In this section, we present one of the most promising models and discuss
@@
 and physical constraints and assess the potential for unification.
-The full grid, including output synthetic spectra and plots can be found at
-\url{jhmatthews.github.io/quasar-wind-grid/}.
-
-\begin{table}
-\begin{tabular}{p{2cm}p{1cm}p{1cm}p{1cm}p{1cm}}
-Parameter & \multicolumn{4}{|l|}{Grid Point Values}  \\
-\hline \hline 
-$r_{min}$ 	&	 $6r_{g}$ & $60r_{g}$ & \multicolumn{2}{|l|}{$300r_{g}$} \\ 
-$\theta_{min}$ 	&	 $40^{\circ}$ & $55^{\circ}$ & \multicolumn{2}{|l|}{$70^{\circ}$} \\ 
-$R_v$  	        &	 $10^{18}$cm & \multicolumn{3}{|l|}{$10^{19}$cm} \\ 
-$\alpha$ 	&	 $0.5$ & $0.6$ & $0.75$ & $1.5$ \\
-$f$ 	&	 $0.01$ & $0.1$ & \multicolumn{2}{|l|}{$1$}  \\
-\hline 
-\end{tabular}
-\caption{The grid points used in the parameter search.}
-\label{grid_table}
-\end{table}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% RESULTS
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Results and Discussion}
-
-% {\bf We need to describe what we did before getting to results.
-We started with parameters similar to those of H14, we created a small grid.
-Limits of the grid are given in table 2.
-This should be a paragraph or section before this one.
-Not all quasars have to have the same parameters and so we have to explain that we have elected to describe one model in detail.
-Was our goal to fix the luminosity and see what was required.
-
-% In next sections, we really need to deal with the difference between this class of models and "the model", and especially "our model".
-We may need to at least in words discuss whether we have "fine tuned" or not, by saying something about other models.}
-
-Here we describe the results from our next-generation model,
-and discuss these results in the context of the criteria 
-presented in section 3.4. The parameters of this model are shown in table~2.
-Parameters differing from the benchmark model of H13 are 
-highlighted with an asterisk. In this section, we examine the physical 
-conditions of the flow, and present the synthetic spectra, before comparing
-the X-ray properties of this particular model to samples of
-quasars and luminous AGN. We also examine trends with inclination in the synthetic spectra, 
-both in terms of the range of ionization states of the absorption lines and equivalent widths 
-of the emission lines.
-
-% This set of parameters
-% was arrived at by conducting a limited grid search over a 
-% 5-dimensional parameter space involving the variables
-% $r_{min}$, $\theta_{min}$, $f$, $\alpha$ and $R_V$.
-% We evaluated these models based on the following
-% criteria:
-% \begin{itemize}
-% \item Does the model maintain the right ionization state to produce strong BALs ($BI > ??$)?
-% \item Does significant line emission emerge at low inclinations, with $EW\sim50\AA$ in \civ?
-% \item Do H recombination lines appear in the spectrum, $EW\sim50\AA$ in \la?
-% \item Do a certain range of angles produce LoBAL features?
-% \item Does the model compare favourably to quasar composite spectra?
-% \end{itemize}
-% In this section, we present one of the most promising models and discuss
-% the various successes and failures.
-% This allows us to gain insight into fundamental geometrical 
-% and physical constraints and assess the potential for unification. 
-% The full grid, including output synthetic spectra and plots can be found at
-% \url{jhmatthews.github.io/quasar-wind-grid/}.
 
@@
 \begin{tabular}{p{3cm}p{4cm}}
-\hline Next-generation Model Parameters 	&	 Value \\ 
+\hline Free Parameters 	&	 Value \\ 
 \hline \hline 
@@
 as recombination and collisional excitation are both proportional to
-density squared. This line emission typically emerges on the edge of the wind
+$n_e^2$. This line emission typically emerges on the edge of the wind
 nearest the central source. The location of the line emitting regions
@@
 
-\subsection{Synthetic Spectra: Comparison to Observations}
+\subsection{Synthetic Spectra}
 
@@
 
-\begin{figure*} %fullpage
-\centering
-\includegraphics[width=1.0\textwidth]{figures/0946.png}
-\caption
-{
-Synthetic spectra at $72^\circ$ compared to an HST STIS spectrum
-of PG0946+301 (Arav et al. 2000). The spectrum is scaled to the flux at 1300\AA\
-for direct comparison. 
-}
-\label{fig:stis}
-\end{figure*} %fullpage
+% \begin{figure*} %fullpage
+% \centering
+% \includegraphics[width=1.0\textwidth]{figures/opt.png}
+% \caption
+% {
+% Figure designed to show optical spectrum and comparison to composite.
+% }
+% \label{fig:uvspec}
+% \end{figure*} %fullpage
 
 Figure~\ref{fig:uvspec} shows the synthetic spectrum in the UV from our model. 
-To assess the ability of the model to match real 
-quasar spectra, we also show {\sl Sloan Digital Sky Survey} (SDSS) quasar and BALQSO 
-composites from \cite{reichard2003}, normalised to the flux at 2000\AA\ in each panel. 
+We also show a comparison to composite quasar and BALQSO spectra.
 We show a cartoon illustrating how geometric effects determine
@@
 
-\subsubsection{Broad absorption lines (`BALQSO-like' angles)}
+\subsubsection{Broad absorption lines}
 
@@
 At the highest inclinations, the 
-cooler, low ionization material at the base of the wind
+cooler, lower ionization material at the base of the wind
 starts to intersect the line of sight. This produces 
-multiple absorption lines in species such as \mg,
+multiple absorption lines in lower ionization species such as \mg,
 \al\ and Fe~\textsc{ii}. The potential links to LoBALQSOs and 
@@
 of the strongest absorption in the profile varies with inclination.
-At the lowest inclination BAL sightlines, the strongest absorption occurs at the red edge,
-whereas at higher inclinations (and for the strongest BALs)
+At lower inclinations, the strongest absorption occurs at the red edge,
+whereas at high inclinations (and for the strongest BALs)
 the trough has a sharp edge at the terminal velocity.
 This offers one potential explanation for the wide range of BALQSO absorption
-line shapes (see e.g. Trump et al. 2006; Knigge et al 2008, Filiz Ak et al. 2014).
+line shapes (see e.g. Trump et al. 2006; Knigge et al 2008).
 In addition, the line profile shape is strongly dependent 
@@
 
-\subsubsection{Broad emission lines (`quasar-like' angles)}
-
-\begin{figure*} %fullpage
-\centering
-\includegraphics[width=1.0\textwidth]{figures/ew.png}
-\caption
-{
-Physical properties of the outflow, shown by the coloured contours.
-The solid black line marks a sphere at $1000~r_G$.
-The dotted lines show the $72^\circ$ and $78^\circ$ sightlines 
-to the centre of the system, and illustrate that different sightlines
-intersect material of different ionization states.
-}
-\label{fig:ew}
-\end{figure*} %fullpage
-
-We find significant collisionally excited line emission emerges
-at low inclinations in the synthetic spectra, particular in the \civ line.
-The improved treatment of recombination also results in a strong \la\ line. 
-In the context of unification, this is a promising result, 
+\subsubsection{Broad emission lines}
+
+We find that the model can produce significant line emission
+at low inclinations, particular in \civ, 
+and the improved treatment of recombination results in a strong \la\
+line. In the context of unification, this is a promising result, 
 and shows that a biconical wind can produce significant 
-emission at `quasar-like' angles. 
-The spectra do not contain the strong C~\textsc{iii}]~1909\AA\, 
-line seen in the quasar composite spectra. 
-This is because we do not yet treat C as a full macro-atom with a 
-full collisional rates between forbidden
-or semi-forbidden transitions, as would be required.
+emission at `quasar-like' angles. To assess the ability of the model to match real 
+quasar spectra, we also show {\sl Sloan Digital Sky Survey} (SDSS) quasar composites from
+\cite{reichard2003}, normalised to the flux at 2000\AA\ in each panel.
+We do not produce the semi-forbidden 
+intercombination lines seen in quasar spectra because we
+currently do not have a treatment for semi-forbidden lines.
+This is especially noticable with the strong C~\textsc{iii}]~1909\AA\, 
+line in the quasar composite spectra.
 The critical density of the C~\textsc{iii}]~1909\AA\, line 
-is $n_e\sim10^{9.5}~\rm{cm^{-3}}$ \citep{wei1988}, which is higher than much of the 
-outer portion of our wind. 
-We therefore expect a model with these 
-parameters to produce a C~\textsc{iii}]~1909\AA\ line
-with a proper treament.
+is $n_e\sim10^{9.5}~\rm{cm^{-3}}$, which is higher than much of the 
+outer portion of our wind. We therefore expect intercombination lines
+to become important coolants in the outer portion of the wind.
 
@@
 
-\subsubsection{The Angular Distribution of Line And Continuum Emission}
-\label{angular}
-
-In order to quantitatively assess how emission lines change with 
-inclination when blue-shifted absorption 
-may affect the line profile, we define the `red wing equivalent width' ($W_{\lambda,RW}$) as
-\begin{equation}
-W_{\lambda,RW} = \int_{\lambda_0}^{\lambda^\prime} \left( 1 - \frac{F_\lambda}{F_0} \right) d\lambda
-\label{rwew}
-\end{equation}
-where $F_0$ is the continuum flux and the integral is calculated from $\lambda_0$, line centre,
-to a wavelength $\lambda^\prime$ where the flux has returned to the continuum level.
-This quantity is shown as a function of inclination in figure 5 for the \civ\ and \mg\ UV lines.
-We also plot show the $W_{\lambda,RW}$ expected from isotropic line emission and a foreshortened 
-and limb darkened disc  as well as $1/2$ equivalent widths from \cite{dipompeo2012b}.
-
-BALQSOs and quasars generally possess very similar emission line properties 
-\citep[e.g.][]{weymann1991,reichard2003}. To demonstrate this, we show equivalent width
-mean values and standard devaitions from REF in table 3. Clearly, the variation
-with inclination in our models is far greater than than the variation 
-between, and standard deviation within, quasar and BALQSO samples.  
-This presents a challenge to our model, as well as the geometric unification picture in general.
-One obvious potential solution to this problem is to hypothesize a more isotropic distribution 
-for the emergent condition than predicted by a classical thin disc. 
+\subsubsection{The Disc SED}
+\label{discsed}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.5\textwidth]{figures/agnspec.png}
+\caption
+{
+$F_\lambda$ for three different wavelengths
+as a function of inclination from \agn\ models, 
+compared to a classical AD. The \agn\ models are computed 
+for Kerr and Scharzschild BHs with the same $M_{BH}$ and 
+$\dot{m}$ as our model. 
+}
+\label{fig:f2000}
+\end{figure}
+
+When comparing BALQSO and quasar composites, it is apparent
+that they possess remarkably similar line strengths and widths 
+\citep[e.g.][]{weymann1991,reichard2003}.
+This presents a challenge to our model, as well as the geometric 
+unification picture in general.
+Limb darkening and foreshortening causes the disc continuum emission to be 
+strongly anisotropic, yet the line emission in our models is much more isotropic. 
+This has the effect of enhancing the line-to-continuum ratios at high inclinations. 
+To construct a scenario where emission 
+line equivalent widths are comparable at all inclinations requires 
+significant fine-tuning when considering a classical thin disc. 
+An alternative, simpler solution is that the emergent continuum is roughly isotropic.
+
 General relativistic effects -- specifically, light bending
@@
 the accretion disc SED to become more isotropic \citep[e.g.][]{zhang1997,munozdarias2013}.
-However, we have verified using AGNSPEC (REFs to Hubeny)
-that this effect is small in the UV and optical wavelength regimes, 
-and the disc is still anisotropic.
-
-Reprocessing by an extended outflow may also cause a more isotropic
-continuum to emerge. Hints that light scattered off a spatially extended 
-wind may contribute signiciantly to the emergent continuum come from radiative transfer s
-simulations \citep{simproga2012} and microlensing observations \citep{sluse2015}.
-However, neither of these examples have sufficient reprocessing efficiencies to 
-compensate for the disc anisotropy in this case.
-An alternative explanation is that the BLR has the same angular distribution 
-of emission as the accretion disc.
-Indeed, \cite{risaliti2011} find that EW distributions in quasars are consistent with anisotropic emission 
-from optically thick, disc-like structures for {\em both} the continuum source and BLR. 
+To generate GR disc spectra, we use the code \agn\ \citep{hubeny2000,davishubeny2006,davis2007}. 
+The output flux at three different wavelengths
+as a function of inclination for an \agn\ model with the same disc and BH parameters
+as our clumpy wind model is shown in figure~\ref{fig:f2000}.
+The effects of GR on an AGN disc are much less extreme 
+in the UV portion of the spectrum than the calculations
+by \cite{zhang1997} for the X-rays in X-ray binaries.
+As a result, the disc emission is still strongly anisotropic.
+GR alone therefore cannot explain the line ratio trends in quasars by making the disc
+emit more isotropically. This supports the findings of \cite{risaliti2011}, 
+who find that EW distributions in quasars are consistent with anisotropic emission 
+from optically thick, 
+disc-like structures for {\em both} the continuum source and BLR. 
 If this is the case, it has a dramatic affect on the intrinsic
 BAL fraction inferred from flux-limited samples \citep{goodrich1997,krolikvoit1998}.
-
-It is also possible that the equatorial paradigm invoked from early polarisation
-studies \citep{goodrich1995, cohen1995,brotherton2006} is an over-simplification, or is merely incorrect. 
-High brightness temperatures in some RL BALQSOs imply polar outflows \citep{zhou2006} 
-and \cite{bruni2012} find that
-RL BALQSOs possess similar radio spectral indices to normal RL quasars, 
-suggestive of comparable inclinations. 
-In addition, \cite{marin2013} find a bending angle of $\sim45^\circ$ is required to 
-explain the polarisation dichotomy of type 1 and 2 AGN using an Elvis-type wind 
-model (Elvis 2000). It is therefore possible 
-that type 1 quasars and BALQSOs are generally viewed from a fairly narrow range of angles 
-($\sim0$-$45^\circ$), or that {\em both} evolutionary and geometric explanations are required.
-We suggest that future modelling should include predictions of polarisation signatures
-from a detailed radiative transfer simulation, allowing direct comparison with spectropolarimetry
-of BALQSOs.
-
-% The final possibility is that BALQSOs are not viewed equatorially. 
-% This possibility is supported by measurements of the radio spectral indices
-% of radio-loud BALQSOs (REF) and attempts to explain the polarisation dichotomy 
-% of type 1 and 2 AGN (REF). This would imply that type 1 quasars and BALQSOs are generally 
-% viewed from a fairly narrow range of angles ($\sim0$-$50^\circ$), and could also mean 
-% the BALQSO fraction requires {\em both} evolutionary and geometric explanations. 
-% There is also clear conflict between this explanation and some
-% polarisation results \citep{goodrich1995, cohen1995}(BROTHERTON).
-% We suggest that future modelling should include predictions of polarisation signatures
-% from a detailed radiative transfer simulation, allowing
-
-% When comparing BALQSO and quasar composites, it is apparent
-% that they possess remarkably similar line strengths and widths 
-% \citep[e.g.][]{weymann1991,reichard2003}.  
-% {\bf I think we mean EW here; otherwise I don't understand what we are talking about.
-We could say ``line shapes and equivalent widths''.
-I also think this requries more than one sentence of introduction.} This presents a challenge to our model, as well as the geometric
-% unification picture in general, because these quantities should vary with inclination angle.
-% Limb darkening and foreshortening causes the disc continuum emission to be 
-% strongly anisotropic, yet the line emission in our models is much more isotropic. 
-% This has the effect of enhancing the line-to-continuum ratios at high inclinations. 
-% To construct a scenario where emission 
-% line equivalent widths are comparable at all inclinations requires 
-% significant fine-tuning when considering a classical thin disc. {\bf Is the previous sentence a throwaway line, or has some person done this.  If so, please reference; if not please delete.}
-%An alternative, simpler solution is that the emergent continuum is roughly isotropic.
-
-% Obviously,  one possible solution to this problem is hypothesize a more isotropic distribution for the emergent condition than predicted by a ``classical'' disc. 
-% General relativistic effects -- specifically, light bending
-% and relativistic beaming -- can cause 
-% the accretion disc SED to become more isotropic \citep[e.g.][]{zhang1997,munozdarias2013}.
-Incorporating these effects into {\sc PYTHON} would be a very difficult and time-consuming challenge.
-Therefore, for the purposes of this discussion we have chosen to investigate whether GR effects could produce enough isotropy to address the EW problem, we have generated
-% \ GR disc spectra, we use the code \agn\ \citep{hubeny2000,davishubeny2006,davis2007}. 
-% The output flux at three different wavelengths
-% as a function of inclination for an \agn\ model with the same disc and BH parameters
-% as our clumpy wind model is shown in figure~\ref{fig:f2000}.  The results indicate that 
-% the effects of GR on an AGN disc are much less extreme 
-% in the UV portion of the spectrum than the calculations
-% by \cite{zhang1997} for the X-rays in X-ray binaries.
-% The emission for the disks of AGN is still strongly anisotropic.
-% GR alone therefore cannot explain the line ratio trends in quasars by making the disc
-% emit more isotropically. This supports the findings of \cite{risaliti2011}, 
-% who find that EW distributions in quasars are consistent with anisotropic emission 
-% from optically thick, 
-% disc-like structures for {\em both} the continuum source and BLR. 
-% If this is the case, it has a dramatic affect on the intrinsic
-% BAL fraction inferred from flux-limited samples \citep{goodrich1997,krolikvoit1998}.
-% We will explore these ideas further in a future study.  
-% {\bf Wait!  All this says is that there has to be an alternative explanation.
-% It is not support for any specific explanation!. This last few sentences should
-% be a separate paragraph.  They should start out: An alernative explanation proposed 
-% by risalite is that...}
+We will explore these ideas further in a future study.
 
@@
 \subsection{X-ray Properties and Broadband SEDs}
-\label{sec:xray}
 
@@
 \centering
-\includegraphics[width=1.0\textwidth]{figures/lx_a05_pre.png}
+\includegraphics[width=1.0\textwidth]{figures/lx.png}
 \caption
@@
 % \end{figure} %fullpage
-
-%{\bf:  Again this section needs an introduction.  Why is this important?}
-
-One of the main motivations for including a treatment of clumping was
-to avoid over-ionization of the wind in the presence of strong X-rays. 
-Having verified that strong BALs appear in the synthetic spectra,
-it is also important to assess whether the X-ray properties of this
-next-generation model agree well with quasar and BALQSO samples for the relevant
-inclinations.
 
@@
 is also shown. For low inclination, `quasar-like' viewing angles,
-we now find excellent agreement with AGN samples. The gradient from $20^\circ$ to
+we now show excellent agreement with AGN samples. The gradient from $20^\circ$ to
 $60^\circ$ in our models is caused by a combination of disc foreshortening/limb-darkening 
@@
 X-ray weak \citep[as suggested by, e.g.][]{morabito2013},
-our isotropic assumption for the X-ray source would be incorrect. 
+our isotropic assumption foe the X-ray source would be incorrect. 
 A polar-biased X-ray source would result in a lower clumping factor being
@@
 {
-\civ , \mg , \al\ and Fe~\textsc{ii} line profiles for viewing angles
+\civ , \mg , \al\ and Fe~\textsc{ii} line profiles for wind angles
 from $72-79^\circ$. The profiles are plotted relative to the local
@@
 
-At certain sightlines, the synthetic spectra exhibit blue-shifted BALs in \al\ and \mg --
+At certain sightlines, our model now produces blue-shifted BALs in \al\ and \mg --
 the absorption lines seen in LoBALQSOs, and we even see absorption in Fe~\textsc{ii}
@@
 of BALQSO viewing angles. We find that ionization stratification
-of the wind causes lower ionization material to have a smaller covering factor, 
+of the wind causes lower ionization material has a smaller covering factor, 
 as demonstrated by figures~\ref{fig:wind} and \ref{fig:lobal}.
@@
 as predicted by polarisation results \citep{brotherton1997}.
-As observed in a BALQSO sample by \cite{filizak2014}, we find that
-BAL troughs are wider and deeper when low ionization absorption features are present,
-and high ionization lines have higher blue-edge velocities than the 
-low ionization species.
 There is also a correlation between the strength of LoBAL features
@@
 intersects the line-of-sight. 
-A model such as this therefore predicts that LoBALQSOs and FeLoBALQSOs 
+Our model therefore predicts that LoBALQSOs and FeLoBALQSOs 
 have stronger Lyman edge absorption and 
-are more Compton-thick than HiBALQSOs and Type 1 quasars.
+be more Compton-thick than HiBALQSOs and Type 1 quasars.
 An edge-on scenario also offers a potential explanation for the rarity of LoBAL and
@@
 inferences are fraught with complex selection effects.
-
-% These line profiles also indicate a potential problem with our model. 
-% \cite{odowd2015} find that the LoBAL profiles in H1413+117 have a 
-% higher velocity onset than the higher ionization BALs, suggesting that the
-% wind becomes less ionized as radius increases. 
-% We find the opposite trend in velocity onsets. In addition, examination of 
-% figure~\ref{fig:wind} shows that ionization parameter decreases with radius, 
-% because the decrease in density wins over geometric dilution of the radiation 
-% field. While the \cite{odowd2015} hypothesis comes from one object,
-% it is clear that {\em at least some} BALQSOs must become less ionized at 
-% higher velocities, contrary to what one expects from our modelling.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% DISCUSSION
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% This could potentially be achieved by wind reprocessing or a more realistic, GR treatment
-% of the accretion disc. We briefly discuss both these possibilities.
-
-% \subsection{Wind reprocessing}
-
-% If the majority of continuum radiation was reprocessed by nearby photoionized plasma (such 
-% as the outflow itself), then this would result in a roughly
-% isotropic radiation field. There are a number of appealing aspects to this scenario.
-% First, it may go some way to explaining recent microlensing (REFs) and timing (REFs)
-% observations which suggest that accretion disc sizes are a factor of $\sim3$ 
-% larger than one expects from a Shakura \& Sunyaev (1973) thin disc. 
-% Second, it implies a wide angle, large covering factor wind in order to 
-% intercept most of the disc continuum. This would make the outflow 
-% an effective feedback mechanism \citep[e.g.][]{borguet2012}, 
-% and would imply that BALQSO outflows
-% have a similar geometry to the ultra-fast outflows seen in nearby AGN 
-% \citep{reeves2003,poundsreeves2009,tombesi2010a}.
-% We note that spectropolarimetry of BALQSOs shows that the light from BAL troughs is $\sim10\%$ 
-% linearly polarised, but the continuum generally has negligible polarisation \citep{lamy2000}.
-% This suggests that the continuum of BALQSOs cannot be significantly enhanced by
-% {\em single} scattering into the line of sight, but does not rule out 
-% {\em multiple} scatterings leading to a more isotropic continuum.
-
-% \subsection{General relativistic effects}
-
-% General relativistic effects -- specifically, light bending
-% and relativistic beaming -- can cause 
-% the accretion disc SED to become more isotropic \citep[e.g.][]{zhang1997,munozdarias2013}.
-% To generate GR disc spectra, we use the code \agn\ \citep{hubeny2000,davishubeny2006,davis2007}. 
-% The output flux at three different wavelengths
-% as a function of inclination for an \agn\ model with the same disc and BH parameters
-% as our clumpy wind model is shown in figure~\ref{fig:f2000}.
-% The effects of GR on an AGN disc are much less extreme 
-% in the UV portion of the spectrum than the calculations
-% by \cite{zhang1997} for the X-rays in X-ray binaries.
-% As a result, the disc emission is still strongly anisotropic.
-% GR alone therefore cannot explain the line ratio trends in quasars.
-
-% To examine the effect of GR on our models, we carry out the following procedure.
-% First, we fit our output spectrum with a polynomial. This continuum fit can 
-% be subtracted from the actual spectrum 
-% to produce a model of the line emission only. We then calculate the 
-% `wind continuum factor', by comparing the model fit with the emergent 
-% disc spectrum without a wind. This factor gives us an approximate way to quantify the 
-% effect of the wind on a disc continuum. It will generally be $>1$ at high inclinations,
-% and $<1$ at low inclinations. This calculates emergent accretion disc spectra from an AGN disc atmosphere
-% including relativistic effects. Finally, produce our final synthetic spectrum 
-% by convolving this the line emission spectrum with the \agn\ model for the model parameters.
-
-% Figure 10 shows the resultant spectrum. Including GR clearly helps
-
-% Can GR effects offer a potential solution? (not quite!)
-
-% {\bf Figures 8 and 9: AGNSPEC F(2000) as a function of viewing angle compared to a BB disc.
-% spectrum compared to composites with AGNSPEC correction.}
-
-% \begin{figure*} %fullpage
-% \centering
-% \includegraphics[width=1.0\textwidth]{figures/adjusted_withbals.png}
-% \caption
-% {
-% $F_\lambda$ normalised to $F_{2000}$.
-{\bf Again, this is a placeholder- but I'm thinking some kind of comparison to composite including the adjusted continuum, showing that we can't get it exactly right}.
-% }
-% \label{fig:finalcomp}
-% \end{figure*} %fullpage
-
-% \subsection{The BALQSO fraction and wind covering factor}
-% \label{sec:balfrac}
-
-% The disc SED has a profound effect on the intrinsic BAL fraction
-% inferred from flux-limited samples. This in turn impacts on 
-% the geometry and covering factor assumed for BALQSO and unified wind models,
-% and even effects the efficiency of feedback.
-% \cite{krolik1998} noted that the effect of limb darkening and foreshortening
-% would result in a signicantly underestimated covering factor for BALQSO winds.
-% The effect is complicated further by the quasar luminosity function -- if 
-% BALQSOs have lower observed luminosities for given accretion disc properties 
-% then they may be drawn from a different bin in the quasar luminosity function 
-% \citep{goodrich1997}. This will also have a similar impact
-% on the LoBALQSOs and FeLoBALQSOs sub-populations.
-% The complex (and as yet unknown) selection effects are understandably 
-% not taken into account by current estimates of the intrinsic BALQSO fraction 
-% \citep{weymann1991, reichard2003, knigge2008, turnermiller2009, allen2011}.
-
-% The way forward is somewhat unclear. Given the lack of available observational 
-% constraints, models cannot readily be used to inform the selection criteria when 
-% calculating the BALQSO fraction. There are two main possibilities:
-% First, the disc emission is roughly isotropic, in which case the BAL fraction
-% estimates should be a good estimate of the covering factor of the outflow,
-% but the question about how this isotropy is achieved remains outstanding.
-% Or second, the disc emission is strongly anisotropic, which follows more
-% naturally from a disc geometry but has large implications
-% for the inferred covering factors, as well as leaving the similar line strengths
-% in BAL and non-BAL quasar compoosites unexplained (see previous sections).
-% Understanding the true nature of the disc SED, including the
-% angular distribution of radiation, is clearly crucial in order
-% to accurately estimate the true covering factor of BALQSO winds.
-
-% A brief comment, citing Goodrich / Krolik \& Voit on the 
-% way in which anisotropy / attenuation affect the inferred
-% BAL fraction. We also need to be aware that there will be a number of selection
-% effects in building up the composites, and we should discuss these
-% and the subtleties involved.
-
-% \begin{figure}
-% \centering
-% \includegraphics[width=0.45\textwidth]{figures/f2000_m9.png}
-% \caption
-% {
-% $F_\lambda$ at $2000$~\AA\ as a function of inclination from
-% \agn\ models. Spectra are computed for BH of $10^9~M_\odot$ with
-% a number of different BH spins and Eddington fractions. The black line
-% shows a standard multi-temperature blackbody AD model.
-% }
-% \label{fig:alpha_ox}
-% \end{figure}
-
-{\bf Note: One of the things I definitely wondered about is whether our "model" would produce the fraction of BALs seen in the sky}
 
@@
 is independent of the assumed BLR geometry and size.
-% \smallskip
-% \item We have examined the effect of GR on our disc SED, using the disc atmosphere
-% and GR ray-tracing code \agn. While including GR effects
-% does cause the disc SED to become slightly more isotropic,
-% the effect is not large enough to produce uniform line to continuum ratios
-% with viewing angle. We briefly discuss other solutions.
+\smallskip
+\item We have examined the effect of GR on our disc SED, using the disc atmosphere
+and GR ray-tracing code \agn. While including GR effects
+does cause the disc SED to become slightly more isotropic,
+the effect is not large enough to produce uniform line to continuum ratios
+with viewing angle. We briefly discuss other solutions.
 \end{enumerate}
@@
 
-% To resolve these challenges, we suggest the following routes forward.
-% \begin{enumerate}
-% \smallskip
-% \item 
-% \smallskip
-% \item 
-% \smallskip
-% \item It is clear that the commonly accepted paradigm of an equatorial
-% wind with a covering factor of $\sim20\%$ does provide an adequate 
-% unified model, as shown here and by other authors 
-% (e.g. Marin \& Goosman 2013; DiPompeo et al. 2012a).
-% More collimated winds may solve some problems, but must be reconciled with
-% polarisation results that suggest an equatorial geometry.
-% Computing the polarisation of emergent energy packets in our 
-% MCRT code would allow direct comparison
-% between outputs from a known geometry and 
-% spectropolarimetry of quasars and AGN.
-% \smallskip
-% \item In addition to spectropolarimetry, one
-% of the best observational tools for probing outflow geometries
-% is reverberation mapping. We are starting to 
-% incorporate methods for predicting the reverberation
-% outputs from our models. By comparing with observational data, this
-% may provide stronger constraints on outflow geometries.
-% \end{enumerate}
-
 \section*{Acknowledgements}
 
-The work of JHM, SWM, NSH and CKL is supported by the
+The work of JHM, SWM, NSH and CK is supported by the 
 Science and Technology Facilities Council (STFC), 
 via two studentships and a consolidated grant, respectively.
-CK also acknowledges a Leverhulme fellowship.
 We would like to thank Omer Blaes, Ivan Hubeny and Shane Davis for their
-assistance with \agn. We are grateful to Mike Brotherton, Mike DiPompeo,
-Sebastien Hoenig and Frederic Marin for helpful correspondence regarding
-polarisation measurements and orientation indicators.
-We would also like to thank Daniel Proga, Daniel Capellupo, Sam Connolly and
-Dirk Grupe for useful discussions.  Simulations were conducted using \py\ version 80,
-and made use of the IRIDIS High Performance Computing Facility at the
-University of Southampton. Figures were produced using the {\tt matplotlib} plotting library
-\citep{matplotlib}.
+assistance with \agn. We would also like to thank Daniel Proga, 
+Daniel Capellupo, Sam Connolly and Dirk Grupe for useful discussions.
+Simulations were conducted using \py\ version 79c, and made use of
+the IRIDIS High Performance Computing Facility at the University of Southampton.
+Figures were produced using {\tt matplotlib} \citep{matplotlib}.
 
@@
 
+% Here are some notes on various parts of the text.
+% \smallskip
+
+% \begin{itemize}
+% 	\item 
+% 	\item Figure 3 should be improved to include some kind of real colormap of the model
+% 	\item At the moment I haven't included another plot for the optical spectrum, or discussed
+% 	it in the paper.
+% 	\item Figure 5 needs to show a sample at the higher luminosity end, and include the actual relationship as the dotted line instead of a by eye version as is currently 
+% 	\item
+% 	\item
+% 	\item
+% 	\item
+% 	\item
+% 	\item
+% 	\item
+% \end{itemize}
+
 \end{document}

### 2015-11-10 paper.tex
updated figure

@@
 \centering
-\includegraphics[width=1.0\textwidth]{figures/uvspec.png}
+\includegraphics[width=1.0\textwidth]{figures/uvspec_estfix.png}
 \caption
@@
 problem with a geometric unification model such as this:
-that the line-to-continuum ratios at low inclinations are
+that the line-to-continuum ratios at hight inclinations are
 significantly affected by disc foreshortening and limb darkening.
@@
 BALQSOs and quasars generally possess very similar emission line properties 
-\citep[e.g.][]{weymann1991,reichard2003}. To demonstrate this, we show equivalent width
-mean values and standard devaitions from REF in table 3. Clearly, the variation
-with inclination in our models is far greater than than the variation 
-between, and standard deviation within, quasar and BALQSO samples.  
+\citep[e.g.][]{weymann1991,reichard2003}. 
+Clearly, the variation with inclination in our models is far greater than 
+than the variation between, and standard deviation within, quasar and BALQSO samples.  
 This presents a challenge to our model, as well as the geometric unification picture in general.
-One obvious potential solution to this problem is to hypothesize a more isotropic distribution 
+One obvious potential solution is to hypothesize a more isotropic distribution 
 for the emergent condition than predicted by a classical thin disc. 

### 2015-11-10 paper.tex
added hubeny refs

@@
 We use the same atomic data as described by LK02 and since updated by H13 and M15, 
-with the addition of direct ionization data from \cite{dere2007}. 
+with the addition of direct (collisional) ionization and recombination
+data from \cite{dere2007}. 
 Photoionization cross-sections are from \textsc{Topbase} \citep{cunto1993} and \cite{vfky}.
-Dielectronic and radiative recombination rate coefficients are taken from 
+%Dielectronic and 
+Radiative recombination rate coefficients are taken from 
 the \textsc{Chianti} database version 7.0 \citep{dere1997,landi2012}.
@@
 the accretion disc SED to become more isotropic \citep[e.g.][]{zhang1997,munozdarias2013}. 
-However, we have verified using AGNSPEC (REFs to Hubeny)
+However, we have verified using AGNSPEC \citep{hubeny2000,hubeny2001,hubenyhubeny1997}
 that this effect is small in the UV and optical wavelength regimes, 

### 2015-11-11 paper.tex
still updating

--- 2015-11-10 paper.tex
@@
 \usepackage{url}
+\usepackage{amsmath}
 %\usepackage{pngfig}
@@
 radiative transfer and photoionization simulations in non-local thermodynamic
-equilibrium (non-LTE). The code can be used to model a variety of
+equilibrium (non-LTE). The code can be model a variety of
 disc-wind systems; it has been used with application to accreting white dwarfs 
@@
 
-Our approach to line transfer is based upon the macro-atom implementation developed by \cite{lucy2002, lucy2003}.
-In our case, for reasons of computational effieciency, we adopt the  hybrid macro-atom scheme
-described by M15 
+Our approach to line transfer is based upon the macro-atom implementation developed by 
+\cite{lucy2002, lucy2003}, in which the energy flows through the system are described in 
+terms of indivisible energy quanta of radiant or kinetic energy 
+(`$r-$packets' and `$k-$packets' respectively; see also section~\ref{sec:photon_sources}). 
+In our case, for reasons of computational efficiency, we adopt the  hybrid macro-atom scheme 
+described by M15.
 %(an improvement over that used by H14 for our earlier quasar study), 
-in which the energy flows
-through the system are described in terms of indivisible
-energy quanta of radiant or kinetic energy 
-(`$r-$packets' and `$k-$packets' respectively; see also section 2.3).
-These energy packets interact with either two-level `simple ions'
-or full `macro-atoms'. 
-Our scheme allows one to treat non-LTE line transfer in radiative equilibrium
+In this scheme, the energy packets interact with either two-level `simple ions' 
+or full `macro-atoms'. This allows one to treat non-LTE line transfer in radiative equilibrium
 without approximation for elements that are identified as 
@@
 in determining their level populations and resultant line emission, and because we were especially interested in the contribution to AGN spectra of \LA.  
-In H13, all atoms were treated in a two-level approximation.
+H13 treated all atoms in a two-level approximation.
 
@@
 \displaystyle{
-n_i \left(C_{j} n_e + 
+n_j \left(C_{j} n_e + 
 \sum_{band~i=0}^{n}~
@@
 \subsection{Photon Sources}
-
-The accretion disc in our model is geometrically thin, but optically thick.
+\label{sec:photon_sources}
+
+We include two sources of r-packets in our model:
+An accretion disc and central X-ray source.
+The accretion disc is assumed to be geometrically thin, but optically thick.
 We thus treat the disc as an ensemble of blackbodies with a 
@@
 and central BH mass ($M_{BH}$).
-All photon sources in our model are assumed to be opaque, meaning
-that photons which strike them are destroyed.
+All photon sources in our model are opaque, meaning
+that r-packets which strike them are destroyed.
 The inner radius of the disc extends to the innermost 
@@
 
-The X-ray source in our model is treated as an isotropic sphere at the ISCO,
+The X-ray source is treated as an isotropic sphere at the ISCO,
 which emits r-packets according to a power law in flux with index $\alpha_X$, of the form
 \begin{equation}
-F_X (\nu) = K \nu^{\alpha_X}.
+F_X (\nu) = K_X \nu^{\alpha_X}.
 \end{equation}
@@
 
-\subsection{Clumping}
+\subsection{A First Approximation for Clumping}
 
@@
 freedom in the model results in significantly wider parameter space.
-Unfortuantely, the physical scale lengths and density contrasts 
+Unfortunately, the physical scale lengths and density contrasts 
 associated with these parameters cannot be well-constrained from observations.
@@
 To allow for clumping in our outflow we adopt a simple approximation
-used extensively in stellar wind modelling, known as 
-{\em microclumping} \citep{hamann1998}(MORE REFS). The key assumption here is that 
-typical clump sizes are much smaller than the typical photon mean free path, 
-and thus the clumps are 
+used successfully in stellar wind modelling, known as 
+{\em microclumping} \citep{hamann1998,hamann2008}(MORE REFS). 
+The key assumption is that typical clump sizes are much smaller than the 
+typical photon mean free path, and thus the clumps are 
 both geometrically and optically thin. This approach 
-allows one to introduce a `filling factor', $f$, which is the 
-fraction of the volume of the plasma filled by clumps. The intra-clump
-medium is assumed to be a vacuum. We can then introduce the 
-density enhancement, $D$, which is defined as 
+allows one to introduce a `volume filling factor', $f_V$. 
+The intra-clump medium is assumed to be a vacuum, so the 
+density of the clumps is then multiplied by the ``density enhancement'' 
+$D=1/f_V$. Opacities, $\kappa$, and emissivities, $\epsilon$, 
+can then be expressed as
+
+% \begin{subequations}
+% \begin{align}
+%         \kappa &= f_V \kappa_C(D) \\
+%         \epsilon &= f_V \epsilon_C(D)
+% \end{align}
+% \end{subequations}
 \begin{equation}
-D = \frac{1}{f}.
+\kappa = f_V \kappa_C(D);~~\epsilon = f_V \epsilon_C(D).
 \end{equation}
-We then multiply all densities in the model by $D$, and all emitting volumes
-by $f$. This has the effect of enhancing all emissivities and opacities
-that scale with the square of density (such as collisional excitation and recombination) 
-by a factor $D$. All processes that scale linearly with density 
-(such as electron scattering and bound-free opacity)
-will remain unchanged for a given ionization state.
+% \kappa = f_V \kappa_C(D) && \epsilon = f_V \epsilon_C(D).
+% \end{equation}
+Here the subscript $C$ denotes that the quantity is calculated using the 
+enhanced density in the clump. The resultant effect is that {\em linear} processes,
+such as electron scattering, are unchanged, as $f_V$ and $D$ will cancel out. 
+However, any quantity which scales with the {\em square} of density, 
+such as collisional excitation or recombination, will increase by a factor of $D$.
+
+% which is defined as 
+% \begin{equation}
+% D = \frac{1}{f} && 
+% \end{equation}
+% We then multiply all densities in the model by $D$, and all emitting volumes
+% by $f$. This has the effect of enhancing all emissivities and opacities
+% that scale with the square of density (such as collisional excitation and recombination) 
+% by a factor $D$. All processes that scale linearly with density 
+% (such as electron scattering and bound-free opacity)
+% will remain unchanged for a given ionization state.
 
@@
 been proposed as a solution to the so-called `over-ionization problem' in 
-disc winds (REFs). This is the main motivation for incorporating microclumping
+disc winds \citep{hamann2013}. This is the main motivation for incorporating microclumping
 into our model. This treatment is first-order; it does not adequately
@@
 for the effect clumping might have on the ionization state and emergent 
-line emission. It is also encouraging that microclumping has been used 
-successfully in fits to O-star wind spectra \citep{hillier1991eswingsmodel}.
+line emission. 
+% It is also encouraging that microclumping has been used 
+% successfully in fits to O-star wind spectra \citep{hillier1991eswingsmodel}.
 
@@
 search over a 5-dimensional parameter space involving the 
-variables $r_{min}$, $\theta_{min}$, $f$, $\alpha$ and $R_v$.
+variables $r_{min}$, $\theta_{min}$, $f_V$, $\alpha$ and $R_v$.
 The grid points are shown in table 1.
@@
 \end{itemize}
-We arrived at a model
 In this section, we present one of the most promising models and discuss
-the various successes and failures.
+the various successes and failures with respect to the above criteria.
 This allows us to gain insight into fundamental geometrical 
@@
 $\alpha$ 	&	 $0.5$ & $0.6$ & $0.75$ & $1.5$ \\
-$f$ 	&	 $0.01$ & $0.1$ & \multicolumn{2}{|l|}{$1$}  \\
+$f_V$ 	&	 $0.01$ & $0.1$ & \multicolumn{2}{|l|}{$1$}  \\
 \hline 
@@
 $\alpha$ 	&	 $0.6^*$ \\
-$f$ 	&	 $0.01^*$  \\
+$f_V$ 	&	 $0.01^*$  \\
 $n_x$ 	&	 $100$  \\
@@
 a clumping factor of 0.01, even though the value of $U_H$ decreases by only a factor of $\sim10$ 
-compared to H13. This is also the reason for significant Lyman edge photoabsorption
-at the highest inclinations (see section 4.3).
+compared to H13. 
+%This is also the reason for significant Lyman edge photoabsorption
+%at the highest inclinations (see section 4.3).
 

### 2015-11-11 paper_mnras.tex

@@
 In this section, we present one of the most promising models and discuss
-the various successes and failures.
+the various successes and failures with respect to the above criteria.
 This allows us to gain insight into fundamental geometrical 

### 2015-11-12 paper.tex
minor edits, added 0946 back

@@
 picture involving a central black hole, an accretion disc and an associated outflow.
-Here, we continue our tests of  this paradigm by comparing ``average'' AGN spectra to 
+Here, we continue our tests of  this paradigm by comparing ``average'' quasar spectra to 
 synthetic spectra of simple biconical disc wind models, using our state-of-the-art 
@@
 In particular, we investigate whether clumping of the outflow allows us to 
-produce synthetic spectra in the rest-frame UV that have the characteristics of AGN, 
-assuming total luminosities as high as 10$^{45}$ ergs s$^{-1}$. 
+produce synthetic spectra in the rest-frame UV that have the characteristics of quasars. 
 We find that a simple treatment of clumping (`microclumping') 
-allows for a more realistic AGN luminosities, while maintaining the ionization 
+allows for a more realistic X-ray luminosities, while maintaining the ionization 
 state necessary for strong BAL features in the rest-frame UV. 
@@
 \begin{itemize}
-\item Does the model avoid over-ionization and thus produce strong BALs with $BI > ??$?
-\item Does significant line emission emerge at low inclinations, with $EW\sim50\AA$ in \civ?
+\item Does the model avoid over-ionization and thus produce UV absorption lines 
+with $BI > 0$ at $\sim20\%$ of viewing angles?
+\item Does significant line emission emerge at low inclinations, with $EW\sim40\AA$ in \civ?
 \item Do H recombination lines appear in the spectrum, $EW\sim50\AA$ in \la?
-\item Do a certain range of angles produce LoBAL features?
+\item Do a small subset of BAL angles produce LoBAL features?
 \item Does the model compare favourably to quasar composite spectra?
@@
 % \url{jhmatthews.github.io/quasar-wind-grid/}.
-
-\begin{figure*} %fullpage
-\centering
-\includegraphics[width=1.0\textwidth]{figures/link8.png}
-\caption
-{
-Contour plots showing the logarithm of some important 
-physical properties of the outflow. Symbols are defined in the text.
-The solid black line marks a sphere at $1000~r_G$.
-The dotted lines show the $72^\circ$ and $78^\circ$ sightlines 
-to the centre of the system, and illustrate that different sightlines
-intersect material of different ionization states.
-The line luminosities represent the luminosity of photons
-escaping the Sobolev region for each line. These photons do not
-necessarily escape to infinity.
-}
-\label{fig:wind}
-\end{figure*} %fullpage
 
@@
 
+\begin{figure*} %fullpage
+\centering
+\includegraphics[width=1.0\textwidth]{figures/link8.png}
+\caption
+{
+Contour plots showing the logarithm of some important 
+physical properties of the outflow. Symbols are defined in the text.
+The solid black line marks a sphere at $1000~r_G$.
+The dotted lines show the $72^\circ$ and $78^\circ$ sightlines 
+to the centre of the system, and illustrate that different sightlines
+intersect material of different ionization states.
+The line luminosities represent the luminosity of photons
+escaping the Sobolev region for each line. These photons do not
+necessarily escape to infinity.
+}
+\label{fig:wind}
+\end{figure*} %fullpage
+
 Figure~\ref{fig:wind} shows the physical properties of the wind.
@@
 
-% \begin{figure*} %fullpage
-% \centering
-% \includegraphics[width=1.0\textwidth]{figures/0946.png}
-% \caption
-% {
-% Synthetic spectra at $72^\circ$ compared to an HST STIS spectrum
-% of PG0946+301 (Arav et al. 2000). The spectrum is scaled to the flux at 1300\AA\
-% for direct comparison. 
-% }
-% \label{fig:stis}
-% \end{figure*} %fullpage
+\begin{figure*} %fullpage
+\centering
+\includegraphics[width=1.0\textwidth]{figures/0946_estfix.png}
+\caption
+{
+Synthetic spectra at $72^\circ$ compared to an HST STIS spectrum
+of PG0946+301 (Arav et al. 2000). The spectrum is scaled to the flux at 1300\AA\
+for direct comparison. 
+}
+\label{fig:stis}
+\end{figure*} %fullpage
 
@@
 FeLoBALQSOs are discussed in section 2.4.
+Clearly, the absorption lines in the 
+synthetic spectra at BALQSO-like angles do not match the composites; this
+is {\em not} due to a failure of our model, but rather because a geometric mean
+BALQSO composite spectrum tends to wash out the broad absorption features due to the wide
+range of absorption characteristics. To demonstrate this, we show a comparison 
+to a {\sl Hubble Space Telescope} STIS spectrum of the high BALnicity BALQSO PG0946+301 
+(Arav et al. 2000) in figure \ref{fig:stis}.
 
@@
 \subsubsection{The Angular Distribution of Line And Continuum Emission}
-\label{angular}
+\label{{sec:angular}}
 
@@
 
-{\bf Note: One of the things I definitely wondered about is whether our "model" would produce the fraction of BALs seen in the sky}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 fails to reproduce this behaviour.
-This is due to a fundamental constraint discussed further in section 5. If the BLR
+This is due to a fundamental constraint discussed further in section~\ref{sec:angular}. If the BLR
 emits fairly isotropically then for a foreshortened, limb-darkened classical thin accretion disc

### 2015-11-19 paper.tex
Initial comments on paper.tex

@@
 Here, we continue our tests of  this paradigm by comparing ``average'' quasar spectra to 
-synthetic spectra of simple biconical disc wind models, using our state-of-the-art 
-Monte Carlo radiative transfer and photoionization code.
-In particular, we investigate whether clumping of the outflow allows us to 
-produce synthetic spectra in the rest-frame UV that have the characteristics of quasars. 
-We find that a simple treatment of clumping (`microclumping') 
-allows for a more realistic X-ray luminosities, while maintaining the ionization 
-state necessary for strong BAL features in the rest-frame UV. 
+synthetic spectra of simple biconical disc wind models, produced with our state-of-the-art 
+Monte Carlo radiative transfer and photoionization code PYTHON.
+Previously, we have shown that we could produce synthetic spectra resembling those of observed AGN for plausible wind models, but only if the X-ray luminosity was limited to about  10$^{42}$ ergs s$^{-1}$.
+Here , we investigate the  degree to which  clumping of the outflow allows us to
+produce synthetic spectra in the rest-frame UV that have the characteristics of quasars with X-ray luminosities as large as 10$^{45}$ ergs s$^{-1}$. 
+We conclude, perhaps not surprisingly,  that clumping does maintain the ionization state of the wind necessary for strong BAL features in the rest-frame UV at more realistic X-ray luminosities.
 We examine the X-ray properties of these simple clumped models
 and find good agreement with existing X-ray samples of AGN and quasars.
-The dense, X-ray heated wind produces strong recombination and collisionally 
+In addition, the dense, X-ray heated wind produces strong recombination and collisionally 
 excited line emission in, e.g., \civ\ and \la, to emerge at the low inclination, 
@@
 outflows in AGN, although on very different scales to line-driven instabilities 
-\citep{PSK2000,PK04,progakurosawa2010,proga2014}.
+\citep{PSK2000,PK04,progakurosawa2010,proga2014}.  {\bf I do not believe the AGN simulations have the resolution to produce clumping on the scale of hot star winds}
 Nevertheless, clumpy winds offer an observationally motivated and theoretically 
@@
 radiative transfer and photoionization simulations in non-local thermodynamic
-equilibrium (non-LTE). The code can be model a variety of
+equilibrium (non-LTE). The code can be used to model a variety of
 disc-wind systems; it has been used with application to accreting white dwarfs 
@@
 
-The basic premise involves generating photons from an accretion disc
-and central object, and computing their radiative transfer through an outflow.
-This outflow is discretized into $n_x \times n_z$ cells in a 2.5D
+The code operates as follows:   This outflow is discretized into $n_x \times n_z$ cells in a 2.5D
 cylindrical geometry with azimuthal symmetry.
-First, the code gradually converges on the global temperature and ionization structure.
-Once these ``ionization cycles'' are complete, then a series of further iterations
-allow one to obtain a detailed synthetic spectrum.
-LK02 provides the basic description of the original code; improvements, 
-see especially \cite{simmacro2005}, H13 and M15, have been 
-described in subsequent reports.  
+From some initial conditions in each cell, the code first calculates the ionization structure of the wind in a series of iterations.
+Each iteration in an ``ionization cycle'' consists of generating photons, actually photon packets, from an accretion disc
+and central object, and calculating how these photon bundles scatter through the wind (eventually escaping the outflow or hitting the disk).
+Then updating the ionization structure based on the properties of the radiation field in each cell, and the process is repeated.
+Once the ionization structure has converged, the ionization structure is held fixed, and  synthetic spectra are generated at specific inclination angles in a series of "spectral cycles".
+LK02 provide a more detailed  description of the original code; various improvements have been made since then and are descbied by
+ \cite{simmacro2005}, H13 and M15.  
 %A full description of the code will be published elsewhere; 
-We focus here on the specific changes made to improve the ionization calculation 
+We focus here on the specific changes made for this study intended to improve the ionization calculation of H and He
 and to allow for clumping in the wind.
@@
 
-\subsection{Line transfer}
+\subsection{Line transfer treatment}
 
@@
 In this scheme, the energy packets interact with either two-level `simple ions' 
-or full `macro-atoms'. This allows one to treat non-LTE line transfer in radiative equilibrium
+or full `macro-atoms'. This allows one to treat non-LTE line transfer in radiative equilibrium {\bf what does "in radiative equilibrium" here mean}
 without approximation for elements that are identified as 
@@
 as simple-ions (see M15). In this study,
-only H is treated as a macro-atom, because 
+only H {\bf and He} are treated as a macro-atom, because 
 we expect recombination to be important
 in determining their level populations and resultant line emission, and because we were especially interested in the contribution to AGN spectra of \LA.  
-H13 treated all atoms in a two-level approximation.
-
-\subsection{Ionization Scheme}
+H13 treated all atoms in a two-level approximation.  {\bf I thought we were also doing He}
+
+\subsection{Ionization treatment (anything but scheme)}
 
@@
 %% We neglect recombination to and from excited states in the simple-ion calculation. 
-For simple-ions, we use a dilute Boltzmann equation to calculate 
+For simple-ions, we use a dilute Boltzmann approximation to calculate 
 the population of level $k$ in ionic stage $j$,
@@
 We stress that this approximation is not required for ions
-treated as macro-atoms.
+treated as macro-atoms. {\bf It seems a bit odd that you explain what we do with simple ions our old approach, but don't say what is done for macro-atoms,.  You only say it is not the other.}
 
@@
 
-We include all free-free, bound-free and bound-bound heating
+We include  free-free, bound-free and bound-bound heating
 and cooling processes in the model. For radiative transfer purposes
@@
 calculating the thermal balance of the plasma (see H13).
-Adiabatic cooling is included and represents the only
-departure from strict radiative equilibrium, but is insignificant 
+Adiabatic cooling is included, but is insignificant 
 in most of the outflow.
@@
 
-We use the same atomic data as described by LK02 and since updated by H13 and M15, 
+We use the same atomic data  described by LK02 as updated by H13 and M15, 
 with the addition of direct (collisional) ionization and recombination
@@
 constraint (see Lucy 2002, M15).
+{\bf I confess, I do not understand what is being said here.
+I would like to understand it better, and I would like it explained better.
+How do we avoid, generating for example recombination photons from non-macro atoms.}
 
@@
 
-Our previous modelling efforts assumed a smooth outflow, 
+Our previous modelling efforts, we have assumed a smooth outflow, 
 in which the density at a given point was determined only by the 
@@
 Unfortunately, the physical scale lengths and density contrasts 
-associated with these parameters cannot be well-constrained from observations.
-
-To allow for clumping in our outflow we adopt a simple approximation
+associated with these parameters are not well-constrained from observations.
+{\bf Reverse the order of these difficulties.
+The most important is that it is not clear what kind of clumping an AGN wind has; the computational problem is a secondary one.}
+
+Given the lack of knowledge about the actual type of clumping, we have adopt a simple approximation
 used successfully in stellar wind modelling, known as 
-{\em microclumping} \citep{hamann1998,hamann2008}(MORE REFS). 
-The key assumption is that typical clump sizes are much smaller than the 
+{\em microclumping} \citep{hamann1998,hamann2008}(MORE REFS), which minimizes the computational difficulties. 
+The underlying assumption in microclumping is that clump sizes are much smaller than the 
 typical photon mean free path, and thus the clumps are 
@@
 represent the complex substructures and stratifications in ionization
-state we expect in AGN outflows. Nevertheless, clumping is clearly
-important in these flows, and this parameterization allows a simple estimate
-for the effect clumping might have on the ionization state and emergent 
+state we expect in AGN outflows. Nevertheless,  this parameterization allows simple estimates
+of the effect clumping might have on the ionization state and emergent 
 line emission. 
@@
 with $BI > 0$ at $\sim20\%$ of viewing angles?
-\item Does significant line emission emerge at low inclinations, with $EW\sim40\AA$ in \civ?
-\item Do H recombination lines appear in the spectrum, $EW\sim50\AA$ in \la?
-\item Do a small subset of BAL angles produce LoBAL features?
-\item Does the model compare favourably to quasar composite spectra?
+\item Do the synthetic spectra show  line emission emerge at low inclinations, with $EW\sim40\AA$ in \civ?
+\item Do H recombination lines appear in the spectra, $EW\sim50\AA$ in \la?
+\item Do the spectra  produce LoBAL features at a  small subset of BAL angles?
+\item Does the model spectra resemble quasar composite spectra?
 \end{itemize}
@@
 \url{jhmatthews.github.io/quasar-wind-grid/}.
+
+{\bf I still think we need to avoid using model to be a generic term to describe the outflow and the spectra.
+If you mean the spectra use "model spectra" or "synthetic spectra'.
+Note - the whole question of the model grid and the selection of one specific instantiation is not dealt with well.}
 
@@
 Figure~\ref{fig:wind} shows the physical properties of the wind.
-The wind rises slowly from the disc at first, with clumped densities
+The wind rises slowly from the disc at first, with clumped densities  {\bf clumped densities is jargon, use perhaps density of the clumps in the wind}
 of $n_H \sim 10^{11}~\rm{cm^{-3}}$ close to the disc plane.
@@
 up to a terminal velocity equal to the escape velocity at the streamline base
-($\sim10,000~\rm{km~s^{-1}}$). This gradual acceleration means that
-the wind exhibits a stratified ionization structure, with low ionization material
+($\sim10,000~\rm{km~s^{-1}}$). This gradual acceleration results in
+a wind that exhibits a stratified ionization structure, with low ionization material
 in the base of the wind giving way to highly ionized plasma further out.
@@
 by the panels showing the ion fraction $F=n_j/n_{tot}$ of some important ions.
-By clumping the wind, we are able to produce the range of ionization states observed
+With a clumpted wind, we are able to produce the range of ionization states observed
 in quasars and BALQSOs, while adopting a realistic $2-10$ keV X-ray luminosity
@@
 This highlights the first success of our model: 
-clumping means the correct ionization state 
-is maintained in the presence of strong X-rays, 
-allowing large resonance line opacities. 
+clumping allows the correct ionization state 
+to be maintained in the presence of strong X-rays, 
+resulting in large resonance line opacities. 
 At the highest inclinations, the 
@@
 of the strongest absorption in the profile varies with inclination.
-At the lowest inclination BAL sightlines, the strongest absorption occurs at the red edge,
+At the lowest inclination BAL sight lines, the strongest absorption occurs at the red edge,
 whereas at higher inclinations (and for the strongest BALs)
@@
 
-Nonblack saturation is observed in the absorption troughs of BALQSOs \citep{arav1999a,arav1999b}.
-This can be caused either by partial covering of the continuum
+Non-black saturation is observed in the absorption troughs of BALQSOs \citep{arav1999a,arav1999b}.
+This is usually explained either as  partial covering of the continuum
 source or by scattered contributions to the BAL troughs, necessarily
-from an opacity source not cospatial with the BAL forming region.
+from an opacity source not co-spatial with the BAL forming region.
 The scattered light explanation is supported by spectropolarimetry results
@@
 Instead, we find black, saturated troughs at angles $i > 73^\circ$, and the BALs
-are non-saturated at lower inclinations. The reasons for this are readily apparent. 
+are non-saturated at lower inclinations. The reasons for this are inherent in the construction of our model. 
 First, the microclumping assumption does not allow for 
 porosity in the wind, meaning that it does not naturally produce
-a partial covering absorber. To do this, an alternative approach
+a partial covering absorber. To allow this, an alternative approach
 such as {\em macroclumping} would be required \citep[e.g.][]{surlan2012,hamann2008}.
@@
 in a polar direction above the disc.
+{\bf it sounds like what you are suggesting is a low density inner flow, our domain 2 stuff actually permits ...
+or indeed one might be able to produce this within SV is you adopted a different mass loss with radius assumption}
 
@@
 problem with a geometric unification model such as this:
-that the line-to-continuum ratios at hight inclinations are
+that the line-to-continuum ratios at high inclinations are
 significantly affected by disc foreshortening and limb darkening.
@@
 crucially important in determining the emergent line ratios.
+{\bf This is a bit oddly explained.
+Our problem is at low inclination.
+Note that I am a bit concerned with Fig 3; the model spectra and the observations look very different.}
 
@@
 of BALQSOs.
+
+{\bf I have to say I find this hard to understand.
+Are you trying to say that in CVs which we are know are thin disks with winds, the EW of the red-wing of emission lines increases with inclination angle ...
+which I think may be true, and so one would expect that in a unification model for AGN  it should do the same?
+And the fact that it does not, suggests that something else is going on in AGN.
+I also still think that you should move this discussion later in the paper and not bury it here.}
 

### 2015-12-07 paper_mnras.tex
Removed comments

@@
 
-%  a simple model in which
-% quasars are unified by BH mass, Eddington ratio and viewing angle can successfully
-% reproduce UV, optical and X-ray properties of {\em both} 
-% BALQSO's and normal emission line quasars.
-
-% Geometrical unification pictures have suggested that 
-% the BAL fraction can be interpreted as the covering factor
-% of an accretion disc wind (refs), and some also propose
-% that this disc wind may also be the source of the broad emission
-% lines (BELs) seen in QSOs (refs). 
-% Alternatively, there are a number of evolutionary models in which
-% QSOs spend approximately $20\%$ of their lifetime as BALQSOs in which the outflow
-% has a high covering factor (refs). 
-% It is also possible that BALQSOs lie in a distinct region
-% in terms of Eddington ratio (refs), but this is somewhat refuted 
-% by observations (refs). % to e.g. Allen and Eigenvector I papers Ledd of BALQSOs
-% Orientation, evolution, black hole mass and eddington ratio 
-% may all have an effect on the BAL fraction (refs),  % to e.g. Allen
-% and the importance of each must be understood to build up coherent picture.
-
-% The driving mechanism for accretion disc winds is uncertain. The winds responsible 
-% for BALs must at least have some line-driven component,
-% as very strong resonance lines exert a strong line force on the 
-% gas (refs). Line-driven winds are notoriously unstable 
-% \citep{lucysolomon1970,macgregor1979,owockirybicki1984,owockirybicki1985}.
-% meaning that one may expect an unstable and inhomogenous 
-% velocity and density structure (refs). Magnetically driven
-% winds may also produce clumpy winds or `clouds' of material which
-% are magnetically confined (refs here to Shlosman, Begelman and the like).
-% Describe mechanism.
-
-% Evidence for an inhomogenous density structure in an accretion disc wind 
-% and/or the broad emission line region comes from multiple sources. 
-% Microlensing observations of absorption troughs suggest that different lines of sight 
-% exhibit varying velocity components (refs), and BALQSO troughs 
-% are known to exhibit variability (refs).
-
-% trend of L_X with radio jets and Sy 1s
-% trend of BALs with radio loudness
-% see MCGV95
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %These studies contain extensive detail on the code,  so we only briefly describe the key elements of the global ionization calculation and other important aspects.
-
-% {\bf ksl - I a a bit torn over whether we add a few 3 sentences to describe the basic idea.
-Some will be reading this for the first time.
-Items that one would include are that we calculate the radiative transfer in a cylindrical coordinate system of dimension ??
-x ??.
-We have ionization and spectral cycles.
-In each cycle, ??
-photon bundles are generated.
-We stop the ionization cycles after they converge, without any details.
-I think this would be useful because we introduce terms like ``cell'' later on.', and without some kind of description they have no context}
 
@@
 in frequency $\nu$, with the fit parameters deduced from band-limited radiation field estimators.
-% \begin{equation}
-% J_{\nu,i}=K_{pl}\nu^{\alpha_{pl}},
-% \end{equation}
-% for a band $i$, or an exponential 
-% \begin{equation}
-% J_{\nu,i}=K_{exp} e^{(-h\nu/k T_{exp})}.
-% \end{equation}
-% Here, $K_{exp}$, $K_{pl}$, $T_{exp}$ and $\alpha_{pl}$ are spectral fit parameters
-% deduced from the band-limited radiation field estimators.
 The ionization rate out of ion $j$ can then be written as 
@@
 in most of the outflow.
-% It is dealt with self consistently by the spontaneous destruction
-% of $k$-packets with a probability
-
-% \begin{equation}
-% P_{\rm{adiabatic~destruction}} = \frac{C_{\rm{adiabatic}}}{C_{\rm{total}}},
-% \end{equation}
-% where $C_{\rm{adiabatic}}$ and ${C_{\rm{total}}}$ represent the 
-% adiabatic and total cooling rates in the cell.
 
@@
 can then be expressed as 
-
-% \begin{subequations}
-% \begin{align}
-%         \kappa &= f_V \kappa_C(D) \\
-%         \epsilon &= f_V \epsilon_C(D)
-% \end{align}
-% \end{subequations}
 \begin{equation}
@@
 \end{equation}
-% \kappa = f_V \kappa_C(D) && \epsilon = f_V \epsilon_C(D).
-% \end{equation}
 Here the subscript $C$ denotes that the quantity is calculated using the 
@@
 such as collisional excitation or recombination, will increase by a factor of $D$.
-
-% which is defined as 
-% \begin{equation}
-% D = \frac{1}{f} && 
-% \end{equation}
-% We then multiply all densities in the model by $D$, and all emitting volumes
-% by $f$. This has the effect of enhancing all emissivities and opacities
-% that scale with the square of density (such as collisional excitation and recombination) 
-% by a factor $D$. All processes that scale linearly with density 
-% (such as electron scattering and bound-free opacity)
-% will remain unchanged for a given ionization state.
 
@@
 
-% {\bf We need to describe what we did before getting to results.
-We started with parameters similar to those of H14, we created a small grid.
-Limits of the grid are given in table 2.
-This should be a paragraph or section before this one.
-Not all quasars have to have the same parameters and so we have to explain that we have elected to describe one model in detail.
-Was our goal to fix the luminosity and see what was required.
-
-% In next sections, we really need to deal with the difference between this class of models and "the model", and especially "our model".
-We may need to at least in words discuss whether we have "fine tuned" or not, by saying something about other models.}
-
 Here we describe the results from our next-generation model,
@@
 of the emission lines.
-
-% This set of parameters
-% was arrived at by conducting a limited grid search over a 
-% 5-dimensional parameter space involving the variables
-% $r_{min}$, $\theta_{min}$, $f$, $\alpha$ and $R_V$.
-% We evaluated these models based on the following
-% criteria:
-% \begin{itemize}
-% \item Does the model maintain the right ionization state to produce strong BALs ($BI > ??$)?
-% \item Does significant line emission emerge at low inclinations, with $EW\sim50\AA$ in \civ?
-% \item Do H recombination lines appear in the spectrum, $EW\sim50\AA$ in \la?
-% \item Do a certain range of angles produce LoBAL features?
-% \item Does the model compare favourably to quasar composite spectra?
-% \end{itemize}
-% In this section, we present one of the most promising models and discuss
-% the various successes and failures.
-% This allows us to gain insight into fundamental geometrical 
-% and physical constraints and assess the potential for unification. 
-% The full grid, including output synthetic spectra and plots can be found at
-% \url{jhmatthews.github.io/quasar-wind-grid/}.
 
@@
 only continuum to show the effect of the outflow on the continuum level.  
+HST STIS spectrum of PG0946+301 (Arav et al. 2000)
 }
@@
 \end{figure}
-
-\begin{figure*} %fullpage
-\centering
-\includegraphics[width=1.0\textwidth]{figures/0946_estfix.png}
-\caption
-{
-Synthetic spectra at $72^\circ$ compared to an HST STIS spectrum
-of PG0946+301 (Arav et al. 2000). The spectrum is scaled to the flux at 1300\AA\
-for direct comparison. 
-}
-\label{fig:stis}
-\end{figure*} %fullpage
 
@@
 
-% The final possibility is that BALQSOs are not viewed equatorially. 
-% This possibility is supported by measurements of the radio spectral indices
-% of radio-loud BALQSOs (REF) and attempts to explain the polarisation dichotomy 
-% of type 1 and 2 AGN (REF). This would imply that type 1 quasars and BALQSOs are generally 
-% viewed from a fairly narrow range of angles ($\sim0$-$50^\circ$), and could also mean 
-% the BALQSO fraction requires {\em both} evolutionary and geometric explanations. 
-% There is also clear conflict between this explanation and some
-% polarisation results \citep{goodrich1995, cohen1995}(BROTHERTON).
-% We suggest that future modelling should include predictions of polarisation signatures
-% from a detailed radiative transfer simulation, allowing
-
-% When comparing BALQSO and quasar composites, it is apparent
-% that they possess remarkably similar line strengths and widths 
-% \citep[e.g.][]{weymann1991,reichard2003}.  
-% {\bf I think we mean EW here; otherwise I don't understand what we are talking about.
-We could say ``line shapes and equivalent widths''.
-I also think this requries more than one sentence of introduction.} This presents a challenge to our model, as well as the geometric
-% unification picture in general, because these quantities should vary with inclination angle.
-% Limb darkening and foreshortening causes the disc continuum emission to be 
-% strongly anisotropic, yet the line emission in our models is much more isotropic. 
-% This has the effect of enhancing the line-to-continuum ratios at high inclinations. 
-% To construct a scenario where emission 
-% line equivalent widths are comparable at all inclinations requires 
-% significant fine-tuning when considering a classical thin disc. {\bf Is the previous sentence a throwaway line, or has some person done this.  If so, please reference; if not please delete.}
-%An alternative, simpler solution is that the emergent continuum is roughly isotropic.
-
-% Obviously,  one possible solution to this problem is hypothesize a more isotropic distribution for the emergent condition than predicted by a ``classical'' disc. 
-% General relativistic effects -- specifically, light bending
-% and relativistic beaming -- can cause 
-% the accretion disc SED to become more isotropic \citep[e.g.][]{zhang1997,munozdarias2013}.
-Incorporating these effects into {\sc PYTHON} would be a very difficult and time-consuming challenge.
-Therefore, for the purposes of this discussion we have chosen to investigate whether GR effects could produce enough isotropy to address the EW problem, we have generated
-% \ GR disc spectra, we use the code \agn\ \citep{hubeny2000,davishubeny2006,davis2007}. 
-% The output flux at three different wavelengths
-% as a function of inclination for an \agn\ model with the same disc and BH parameters
-% as our clumpy wind model is shown in figure~\ref{fig:f2000}.  The results indicate that 
-% the effects of GR on an AGN disc are much less extreme 
-% in the UV portion of the spectrum than the calculations
-% by \cite{zhang1997} for the X-rays in X-ray binaries.
-% The emission for the disks of AGN is still strongly anisotropic.
-% GR alone therefore cannot explain the line ratio trends in quasars by making the disc
-% emit more isotropically. This supports the findings of \cite{risaliti2011}, 
-% who find that EW distributions in quasars are consistent with anisotropic emission 
-% from optically thick, 
-% disc-like structures for {\em both} the continuum source and BLR. 
-% If this is the case, it has a dramatic affect on the intrinsic
-% BAL fraction inferred from flux-limited samples \citep{goodrich1997,krolikvoit1998}.
-% We will explore these ideas further in a future study.  
-% {\bf Wait!  All this says is that there has to be an alternative explanation.
-% It is not support for any specific explanation!. This last few sentences should
-% be a separate paragraph.  They should start out: An alernative explanation proposed 
-% by risalite is that...}
-
-% Figure 5 also shows the spectrum into the optical,
-% showing that the outflow produces signiciant optical emission lines
-% as well as having a noticeable effect on the continuum shape. This
-% is particularly true around the Balmer jump at $3646\AA$ and is due to
-% a prominent wind-formed recombination continuum.
-
 \subsection{X-ray Properties and Broadband SEDs}
@@
 
-\begin{figure*}
-% \centering
-% \includegraphics[width=1.0\textwidth]{figures/sed_all_balqsos.png}
-% \caption
-% {
-% Broadband SEDs compared to IR and X-ray SEDs for selected BALQSOs 
-% from Grupe \& Nousek (2015).
-% }
-% \label{fig:xray}
-\end{figure*}
-
-%{\bf:  Again this section needs an introduction.  Why is this important?}
-
-One of the main motivations for including a treatment of clumping was
+The main motivation for including a treatment of clumping was
 to avoid over-ionization of the wind in the presence of strong X-rays. 
@@
 monochromatic luminosity ($L_\nu$) at 2~keV and 
-%$\alpha_{OX}$ 
 plotted against $L_\nu$ at $2500$\AA\ for a number of different viewing angles in our model.
-% $\alpha_{OX}$ is a spectral index from near UV to X-rays defined by
-% \begin{equation}
-% \alpha_{OX}=0.3838\log\left(\frac{L_{\nu}(2~keV)}{L_{\nu}(2500~\mbox{\scriptsize{\AA}})}\right),
-% \end{equation}
-% which effectively represents a near-UV to X-ray flux ratio and a measure of X-ray 
-% weakness. 
 The monochromatic luminosities are calculated from the synthetic spectra and thus include
@@
 a unified quasar model.
-
-% We can also examine the emergent X-ray spectra from our model. 
-% Our code is not yet optimized for producing X-ray spectra, as we do not yet 
-% include all lines and levels of e.g. Fe or macro-atom treatments of 
-% higher order ions (cf. Sim et al. 2008, 2010). 
-% However, the bound-free opacity sources are complete, and comparisons of the shape
-% of the heavily absorbed spectra can be useful.
-% Figure 6 shows the broadband SED from the model, compared to a number of BALQSO spectra
-% from \cite{grupenousek2015} - note that lower mass and super-Eddington sources
-% are excluded.
-
-% discuss the figure showing X-ray properties briefly. 
-% Present an X-ray spectrum? compare to observations e.g. Giustini?
-
-% {\bf Figures 5 and 6: $L_{2kev}$ v $L_{2500}$ plot and X-ray spectrum compared to Grupe and Nousek (broadband SED?)}
 
@@
 
-% These line profiles also indicate a potential problem with our model. 
-% \cite{odowd2015} find that the LoBAL profiles in H1413+117 have a 
-% higher velocity onset than the higher ionization BALs, suggesting that the
-% wind becomes less ionized as radius increases. 
-% We find the opposite trend in velocity onsets. In addition, examination of 
-% figure~\ref{fig:wind} shows that ionization parameter decreases with radius, 
-% because the decrease in density wins over geometric dilution of the radiation 
-% field. While the \cite{odowd2015} hypothesis comes from one object,
-% it is clear that {\em at least some} BALQSOs must become less ionized at 
-% higher velocities, contrary to what one expects from our modelling.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% DISCUSSION
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% This could potentially be achieved by wind reprocessing or a more realistic, GR treatment
-% of the accretion disc. We briefly discuss both these possibilities.
-
-% \subsection{Wind reprocessing}
-
-% If the majority of continuum radiation was reprocessed by nearby photoionized plasma (such 
-% as the outflow itself), then this would result in a roughly
-% isotropic radiation field. There are a number of appealing aspects to this scenario.
-% First, it may go some way to explaining recent microlensing (REFs) and timing (REFs)
-% observations which suggest that accretion disc sizes are a factor of $\sim3$ 
-% larger than one expects from a Shakura \& Sunyaev (1973) thin disc. 
-% Second, it implies a wide angle, large covering factor wind in order to 
-% intercept most of the disc continuum. This would make the outflow 
-% an effective feedback mechanism \citep[e.g.][]{borguet2012}, 
-% and would imply that BALQSO outflows
-% have a similar geometry to the ultra-fast outflows seen in nearby AGN 
-% \citep{reeves2003,poundsreeves2009,tombesi2010a}.
-% We note that spectropolarimetry of BALQSOs shows that the light from BAL troughs is $\sim10\%$ 
-% linearly polarised, but the continuum generally has negligible polarisation \citep{lamy2000}.
-% This suggests that the continuum of BALQSOs cannot be significantly enhanced by
-% {\em single} scattering into the line of sight, but does not rule out 
-% {\em multiple} scatterings leading to a more isotropic continuum.
-
-% \subsection{General relativistic effects}
-
-% General relativistic effects -- specifically, light bending
-% and relativistic beaming -- can cause 
-% the accretion disc SED to become more isotropic \citep[e.g.][]{zhang1997,munozdarias2013}.
-% To generate GR disc spectra, we use the code \agn\ \citep{hubeny2000,davishubeny2006,davis2007}. 
-% The output flux at three different wavelengths
-% as a function of inclination for an \agn\ model with the same disc and BH parameters
-% as our clumpy wind model is shown in figure~\ref{fig:f2000}.
-% The effects of GR on an AGN disc are much less extreme 
-% in the UV portion of the spectrum than the calculations
-% by \cite{zhang1997} for the X-rays in X-ray binaries.
-% As a result, the disc emission is still strongly anisotropic.
-% GR alone therefore cannot explain the line ratio trends in quasars.
-
-% To examine the effect of GR on our models, we carry out the following procedure.
-% First, we fit our output spectrum with a polynomial. This continuum fit can 
-% be subtracted from the actual spectrum 
-% to produce a model of the line emission only. We then calculate the 
-% `wind continuum factor', by comparing the model fit with the emergent 
-% disc spectrum without a wind. This factor gives us an approximate way to quantify the 
-% effect of the wind on a disc continuum. It will generally be $>1$ at high inclinations,
-% and $<1$ at low inclinations. This calculates emergent accretion disc spectra from an AGN disc atmosphere
-% including relativistic effects. Finally, produce our final synthetic spectrum 
-% by convolving this the line emission spectrum with the \agn\ model for the model parameters.
-
-% Figure 10 shows the resultant spectrum. Including GR clearly helps
-
-% Can GR effects offer a potential solution? (not quite!)
-
-% {\bf Figures 8 and 9: AGNSPEC F(2000) as a function of viewing angle compared to a BB disc.
-% spectrum compared to composites with AGNSPEC correction.}
-
-% \begin{figure*} %fullpage
-% \centering
-% \includegraphics[width=1.0\textwidth]{figures/adjusted_withbals.png}
-% \caption
-% {
-% $F_\lambda$ normalised to $F_{2000}$.
-{\bf Again, this is a placeholder- but I'm thinking some kind of comparison to composite including the adjusted continuum, showing that we can't get it exactly right}.
-% }
-% \label{fig:finalcomp}
-% \end{figure*} %fullpage
-
-% \subsection{The BALQSO fraction and wind covering factor}
-% \label{sec:balfrac}
-
-% The disc SED has a profound effect on the intrinsic BAL fraction
-% inferred from flux-limited samples. This in turn impacts on 
-% the geometry and covering factor assumed for BALQSO and unified wind models,
-% and even effects the efficiency of feedback.
-% \cite{krolik1998} noted that the effect of limb darkening and foreshortening
-% would result in a signicantly underestimated covering factor for BALQSO winds.
-% The effect is complicated further by the quasar luminosity function -- if 
-% BALQSOs have lower observed luminosities for given accretion disc properties 
-% then they may be drawn from a different bin in the quasar luminosity function 
-% \citep{goodrich1997}. This will also have a similar impact
-% on the LoBALQSOs and FeLoBALQSOs sub-populations.
-% The complex (and as yet unknown) selection effects are understandably 
-% not taken into account by current estimates of the intrinsic BALQSO fraction 
-% \citep{weymann1991, reichard2003, knigge2008, turnermiller2009, allen2011}.
-
-% The way forward is somewhat unclear. Given the lack of available observational 
-% constraints, models cannot readily be used to inform the selection criteria when 
-% calculating the BALQSO fraction. There are two main possibilities:
-% First, the disc emission is roughly isotropic, in which case the BAL fraction
-% estimates should be a good estimate of the covering factor of the outflow,
-% but the question about how this isotropy is achieved remains outstanding.
-% Or second, the disc emission is strongly anisotropic, which follows more
-% naturally from a disc geometry but has large implications
-% for the inferred covering factors, as well as leaving the similar line strengths
-% in BAL and non-BAL quasar compoosites unexplained (see previous sections).
-% Understanding the true nature of the disc SED, including the
-% angular distribution of radiation, is clearly crucial in order
-% to accurately estimate the true covering factor of BALQSO winds.
-
-% A brief comment, citing Goodrich / Krolik \& Voit on the 
-% way in which anisotropy / attenuation affect the inferred
-% BAL fraction. We also need to be aware that there will be a number of selection
-% effects in building up the composites, and we should discuss these
-% and the subtleties involved.
-
-% \begin{figure}
-% \centering
-% \includegraphics[width=0.45\textwidth]{figures/f2000_m9.png}
-% \caption
-% {
-% $F_\lambda$ at $2000$~\AA\ as a function of inclination from
-% \agn\ models. Spectra are computed for BH of $10^9~M_\odot$ with
-% a number of different BH spins and Eddington fractions. The black line
-% shows a standard multi-temperature blackbody AD model.
-% }
-% \label{fig:alpha_ox}
-% \end{figure}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 is independent of the assumed BLR geometry and size.
-% \smallskip
-% \item We have examined the effect of GR on our disc SED, using the disc atmosphere
-% and GR ray-tracing code \agn. While including GR effects
-% does cause the disc SED to become slightly more isotropic,
-% the effect is not large enough to produce uniform line to continuum ratios
-% with viewing angle. We briefly discuss other solutions.
 \end{enumerate}
@@
 a clear challenge to the current disc wind unification picture.
-
-% To resolve these challenges, we suggest the following routes forward.
-% \begin{enumerate}
-% \smallskip
-% \item 
-% \smallskip
-% \item 
-% \smallskip
-% \item It is clear that the commonly accepted paradigm of an equatorial
-% wind with a covering factor of $\sim20\%$ does provide an adequate 
-% unified model, as shown here and by other authors 
-% (e.g. Marin \& Goosman 2013; DiPompeo et al. 2012a).
-% More collimated winds may solve some problems, but must be reconciled with
-% polarisation results that suggest an equatorial geometry.
-% Computing the polarisation of emergent energy packets in our 
-% MCRT code would allow direct comparison
-% between outputs from a known geometry and 
-% spectropolarimetry of quasars and AGN.
-% \smallskip
-% \item In addition to spectropolarimetry, one
-% of the best observational tools for probing outflow geometries
-% is reverberation mapping. We are starting to 
-% incorporate methods for predicting the reverberation
-% outputs from our models. By comparing with observational data, this
-% may provide stronger constraints on outflow geometries.
-% \end{enumerate}
 

### 2015-12-08 paper.tex
still modding

@@
 outflows in AGN, although on very different scales to line-driven instabilities 
-\citep{PSK2000,PK04,progakurosawa2010,proga2014}.  {\bf I do not believe the AGN simulations have the resolution to produce clumping on the scale of hot star winds}
+\citep{PSK2000,PK04,progakurosawa2010,proga2014}.  {\bf KSL: I do not believe the AGN simulations have the resolution to produce clumping on the scale of hot star winds.
+JM: that's why I mention scales, although I can specifically mention resolution if we
+want.}
 Nevertheless, clumpy winds offer an observationally motivated and theoretically 
@@
 Once the ionization structure has converged, the ionization structure is held fixed, and  synthetic spectra are generated at specific inclination angles in a series of "spectral cycles".
-LK02 provide a more detailed  description of the original code; various improvements have been made since then and are descbied by
+LK02 provide a more detailed  description of the original code; various improvements have been made since then and are described by
  \cite{simmacro2005}, H13 and M15.  
@@
 In this scheme, the energy packets interact with either two-level `simple ions' 
-or full `macro-atoms'. This allows one to treat non-LTE line transfer in radiative equilibrium {\bf what does "in radiative equilibrium" here mean}
+or full `macro-atoms'. This allows one to treat non-LTE line transfer in radiative equilibrium {\bf KSL: what does "in radiative equilibrium" here mean? 
+JM: not sure what the question is, really- radiative equilibrium is a
+key assumption in the macro-atom framework.}
 without approximation for elements that are identified as 
@@
 as simple-ions (see M15). In this study,
-only H {\bf and He} are treated as a macro-atom, because 
+only H and He are treated as a macro-atom, because 
 we expect recombination to be important
-in determining their level populations and resultant line emission, and because we were especially interested in the contribution to AGN spectra of \LA.  
-H13 treated all atoms in a two-level approximation.  {\bf I thought we were also doing He}
+in determining their level populations and resultant line emission, 
+and because we are especially interested in the contribution to 
+AGN spectra of \LA.  
+H13 treated all atoms in a two-level approximation.  {\bf KSL:
+I thought we were also doing He. JM: yep, corrected.}
 
@@
 Macro-atoms have their ion and level populations derived from
-MC rate estimators as described by Lucy (2002,2003). Previously (LK02, H13, M15),
-we used a modified Saha approach to calculate the ionization fractions
+MC rate estimators as described by Lucy (2002,2003). 
+Previously (LK02, H13, M15), we used a modified Saha approach to calculate the ionization fractions
 of simple-ions. As part of  this effort, we have now improved {\sc PYTHON} to explicitly solve the 
@@
 in frequency $\nu$, with the fit parameters deduced from band-limited radiation field estimators.
+This allows the calculation of a photoionization rate estimator. Ion abundances are
+then calculated by solving the rate equations between ions. We include collisional ionization
+and photoionization balanced with radiative, dielectronic and collisional (three-body) recombination.
+As in M15, we use a dilute Boltzmann approximation to calculate 
+the population of levels for simple-ions. We stress that this approximation 
+is not required for ions treated as macro-atoms. 
 % \begin{equation}
@@
 % deduced from the band-limited radiation field estimators.
-The ionization rate out of ion $j$ can then be written as 
-\begin{equation}
-R_{j,j+1}(J)= 
-\displaystyle{
-n_j \left(C_{j} n_e + 
-\sum_{band~i=0}^{n}~
-{\int_{\nu_i}^{~\nu_i+1} \frac{4 \pi J_{\nu,i}\sigma_j(\nu)}  {h \nu} d\nu}
-\right),}
-\end{equation}
-where $\sigma_j$ is the photoionization cross-section, $n_e$
-is the electron density and $C_{j}$
-represents the collisional ionization coefficient.
-The recombination rate {\em into} ion $j$ is given by 
-\begin{equation}
-R_{j+1,j}(T_e) = (\alpha^j_{RR} + \alpha^j_{CR}) n_{j+1} n_e,
-\end{equation}
-where each $\alpha^j$ here is the recombination rate coefficient into the ground state of ion $j$.
-The subscripts denote radiative and 
-collisional (three-body) recombination, respectively. 
-$T_e$ is the electron temperature.
-%% We neglect recombination to and from excited states in the simple-ion calculation. 
-For simple-ions, we use a dilute Boltzmann approximation to calculate 
-the population of level $k$ in ionic stage $j$,
-\begin{equation}
-\frac{n_{jk}}{n_j} = \frac{W g_k}{z_j(T_R)} \exp(-E_k/kT_R).
-\end{equation}
-Here $z_j$ is the partition function of ionic stage $j$,
-$T_R$ is the effective radiation temperature,
-$E_k$ is the energy difference between level $k$ and the ground state,
-and $g_k$ is the statistical weight of level $k$. 
-We stress that this approximation is not required for ions
-treated as macro-atoms. {\bf It seems a bit odd that you explain what we do with simple ions our old approach, but don't say what is done for macro-atoms,.  You only say it is not the other.}
+% The ionization rate out of ion $j$ can then be written as 
+% \begin{equation}
+% R_{j,j+1}(J)= 
+% \displaystyle{
+% n_j \left(C_{j} n_e + 
+% \sum_{band~i=0}^{n}~
+% {\int_{\nu_i}^{~\nu_i+1} \frac{4 \pi J_{\nu,i}\sigma_j(\nu)}  {h \nu} d\nu}
+% \right),}
+% \end{equation}
+% where $\sigma_j$ is the photoionization cross-section, $n_e$
+% is the electron density and $C_{j}$
+% represents the collisional ionization coefficient.
+% The recombination rate {\em into} ion $j$ is given by 
+% \begin{equation}
+% R_{j+1,j}(T_e) = (\alpha^j_{RR} + \alpha^j_{CR}) n_{j+1} n_e,
+% \end{equation}
+% where each $\alpha^j$ here is the recombination rate coefficient into the ground state of ion $j$.
+% The subscripts denote radiative and 
+% collisional (three-body) recombination, respectively. 
+% $T_e$ is the electron temperature.
+% %% We neglect recombination to and from excited states in the simple-ion calculation. 
+% For simple-ions, we use a dilute Boltzmann approximation to calculate 
+% the population of level $k$ in ionic stage $j$,
+% \begin{equation}
+% \frac{n_{jk}}{n_j} = \frac{W g_k}{z_j(T_R)} \exp(-E_k/kT_R).
+% \end{equation}
+% Here $z_j$ is the partition function of ionic stage $j$,
+% $T_R$ is the effective radiation temperature,
+% $E_k$ is the energy difference between level $k$ and the ground state,
+% and $g_k$ is the statistical weight of level $k$. 
+% We stress that this approximation is not required for ions
+% treated as macro-atoms. 
+{\bf KSL: 
+It seems a bit odd that you explain what we do with simple ions our old approach, but don't say what is done for macro-atoms,.  You only say it is not the other.
+JM: WE've shortened the seciton on simple-ions as agreed..}
 
@@
 in a polar direction above the disc.  
-{\bf it sounds like what you are suggesting is a low density inner flow, our domain 2 stuff actually permits ...
-or indeed one might be able to produce this within SV is you adopted a different mass loss with radius assumption}
+{\bf KSL: it sounds like what you are suggesting is a low density inner flow, our domain 2 stuff actually permits or indeed one might be able to produce this within SV is you adopted a different mass loss with radius assumption.
+JM: I am being deliberately
+vague about what I am suggesting. I am saying there are three physical
+possibilities: either wind itself causes this scattering contribution, which doesn't happen in our model, or you have partial covering, or you have some additional scatterer.}
 
@@
 crucially important in determining the emergent line ratios.  
-{\bf This is a bit oddly explained.
-Our problem is at low inclination.
-Note that I am a bit concerned with Fig 3; the model spectra and the observations look very different.}
+{\bf KSL: This is a bit oddly explained. Our problem is at low inclination.  Note that I am a bit concerned with Fig 3; the model spectra and the observations look very different.}
 

### 2015-12-08 paper_mnras.tex
still modding

--- 2015-11-12 paper_mnras.tex
@@
 outflows in AGN, although on very different scales to line-driven instabilities 
-\citep{PSK2000,PK04,progakurosawa2010,proga2014}.
+\citep{PSK2000,PK04,progakurosawa2010,proga2014}.  {\bf KSL: I do not believe the AGN simulations have the resolution to produce clumping on the scale of hot star winds.
+JM: that's why I mention scales, although I can specifically mention resolution if we
+want.}
 Nevertheless, clumpy winds offer an observationally motivated and theoretically 
@@
 
-The basic premise involves generating photons from an accretion disc
-and central object, and computing their radiative transfer through an outflow.
-This outflow is discretized into $n_x \times n_z$ cells in a 2.5D
+The code operates as follows:   This outflow is discretized into $n_x \times n_z$ cells in a 2.5D
 cylindrical geometry with azimuthal symmetry.
-First, the code gradually converges on the global temperature and ionization structure.
-Once these ``ionization cycles'' are complete, then a series of further iterations
-allow one to obtain a detailed synthetic spectrum.
-LK02 provides the basic description of the original code; improvements, 
-see especially \cite{simmacro2005}, H13 and M15, have been 
-described in subsequent reports.  
+From some initial conditions in each cell, the code first calculates the ionization structure of the wind in a series of iterations.
+Each iteration in an ``ionization cycle'' consists of generating photons, actually photon packets, from an accretion disc
+and central object, and calculating how these photon bundles scatter through the wind (eventually escaping the outflow or hitting the disk).
+Then updating the ionization structure based on the properties of the radiation field in each cell, and the process is repeated.
+Once the ionization structure has converged, the ionization structure is held fixed, and  synthetic spectra are generated at specific inclination angles in a series of "spectral cycles".
+LK02 provide a more detailed  description of the original code; various improvements have been made since then and are described by
+ \cite{simmacro2005}, H13 and M15.  
 %A full description of the code will be published elsewhere; 
-We focus here on the specific changes made to improve the ionization calculation 
+We focus here on the specific changes made for this study intended to improve the ionization calculation of H and He
 and to allow for clumping in the wind.
@@
 In this scheme, the energy packets interact with either two-level `simple ions' 
-or full `macro-atoms'. This allows one to treat non-LTE line transfer in radiative equilibrium
+or full `macro-atoms'. This allows one to treat non-LTE line transfer in radiative equilibrium {\bf KSL: what does "in radiative equilibrium" here mean? 
+JM: not sure what the question is, really- radiative equilibrium is a
+key assumption in the macro-atom framework.}
 without approximation for elements that are identified as 
@@
 as simple-ions (see M15). In this study,
-only H is treated as a macro-atom, because 
+only H and He are treated as a macro-atom, because 
 we expect recombination to be important
-in determining their level populations and resultant line emission, and because we were especially interested in the contribution to AGN spectra of \LA.  
-H13 treated all atoms in a two-level approximation.
-
-\subsection{Ionization Scheme}
+in determining their level populations and resultant line emission, 
+and because we are especially interested in the contribution to 
+AGN spectra of \LA.  
+H13 treated all atoms in a two-level approximation.  {\bf KSL:
+I thought we were also doing He. JM: yep, corrected.}
+
+\subsection{Ionization treatment (anything but scheme)}
 
 Macro-atoms have their ion and level populations derived from
-MC rate estimators as described by Lucy (2002,2003). Previously (LK02, H13, M15),
-we used a modified Saha approach to calculate the ionization fractions
+MC rate estimators as described by Lucy (2002,2003). 
+Previously (LK02, H13, M15), we used a modified Saha approach to calculate the ionization fractions
 of simple-ions. As part of  this effort, we have now improved {\sc PYTHON} to explicitly solve the 
@@
 % deduced from the band-limited radiation field estimators.
-The ionization rate out of ion $j$ can then be written as 
-\begin{equation}
-R_{j,j+1}(J)= 
-\displaystyle{
-n_j \left(C_{j} n_e + 
-\sum_{band~i=0}^{n}~
-{\int_{\nu_i}^{~\nu_i+1} \frac{4 \pi J_{\nu,i}\sigma_j(\nu)}  {h \nu} d\nu}
-\right),}
-\end{equation}
-where $\sigma_j$ is the photoionization cross-section, $n_e$
-is the electron density and $C_{j}$
-represents the collisional ionization coefficient.
-The recombination rate {\em into} ion $j$ is given by 
-\begin{equation}
-R_{j+1,j}(T_e) = (\alpha^j_{RR} + \alpha^j_{CR}) n_{j+1} n_e,
-\end{equation}
-where each $\alpha^j$ here is the recombination rate coefficient into the ground state of ion $j$.
-The subscripts denote radiative and 
-collisional (three-body) recombination, respectively. 
-$T_e$ is the electron temperature.
-%% We neglect recombination to and from excited states in the simple-ion calculation. 
-For simple-ions, we use a dilute Boltzmann equation to calculate 
-the population of level $k$ in ionic stage $j$,
-\begin{equation}
-\frac{n_{jk}}{n_j} = \frac{W g_k}{z_j(T_R)} \exp(-E_k/kT_R).
-\end{equation}
-Here $z_j$ is the partition function of ionic stage $j$,
-$T_R$ is the effective radiation temperature,
-$E_k$ is the energy difference between level $k$ and the ground state,
-and $g_k$ is the statistical weight of level $k$. 
-We stress that this approximation is not required for ions
-treated as macro-atoms.
+% The ionization rate out of ion $j$ can then be written as 
+% \begin{equation}
+% R_{j,j+1}(J)= 
+% \displaystyle{
+% n_j \left(C_{j} n_e + 
+% \sum_{band~i=0}^{n}~
+% {\int_{\nu_i}^{~\nu_i+1} \frac{4 \pi J_{\nu,i}\sigma_j(\nu)}  {h \nu} d\nu}
+% \right),}
+% \end{equation}
+% where $\sigma_j$ is the photoionization cross-section, $n_e$
+% is the electron density and $C_{j}$
+% represents the collisional ionization coefficient.
+% The recombination rate {\em into} ion $j$ is given by 
+% \begin{equation}
+% R_{j+1,j}(T_e) = (\alpha^j_{RR} + \alpha^j_{CR}) n_{j+1} n_e,
+% \end{equation}
+% where each $\alpha^j$ here is the recombination rate coefficient into the ground state of ion $j$.
+% The subscripts denote radiative and 
+% collisional (three-body) recombination, respectively. 
+% $T_e$ is the electron temperature.
+% %% We neglect recombination to and from excited states in the simple-ion calculation. 
+% For simple-ions, we use a dilute Boltzmann approximation to calculate 
+% the population of level $k$ in ionic stage $j$,
+% \begin{equation}
+% \frac{n_{jk}}{n_j} = \frac{W g_k}{z_j(T_R)} \exp(-E_k/kT_R).
+% \end{equation}
+% Here $z_j$ is the partition function of ionic stage $j$,
+% $T_R$ is the effective radiation temperature,
+% $E_k$ is the energy difference between level $k$ and the ground state,
+% and $g_k$ is the statistical weight of level $k$. 
+% We stress that this approximation is not required for ions
+% treated as macro-atoms. 
+{\bf KSL: 
+It seems a bit odd that you explain what we do with simple ions our old approach, but don't say what is done for macro-atoms,.  You only say it is not the other.
+JM: WE've shortened the seciton on simple-ions as agreed..}
 
@@
 in a polar direction above the disc.  
+{\bf KSL: it sounds like what you are suggesting is a low density inner flow, our domain 2 stuff actually permits ...
+or indeed one might be able to produce this within SV is you adopted a different mass loss with radius assumption.
+JM: I am being deliberately
+vague about what I am suggesting. I am saying there are three physical
+possibilities: either wind itself causes this scattering contribution, which doesn't happen in our model, or you have partial covering, or you have some additional scatterer.}
 
@@
 crucially important in determining the emergent line ratios.  
+{\bf KSL: This is a bit oddly explained. Our problem is at low inclination.  Note that I am a bit concerned with Fig 3; the model spectra and the observations look very different.}
 

### 2015-12-08 paper.tex

@@
+\documentclass[useAMS,usenatbib]{mn2e_x}
 %%%% Various options for document class.
-%%\documentclass[usenatbib, a4paper, 11pt]{aastex}
-%%\documentclass[preprint, 11pt, a4paper]{aastex}
-%%\documentclass[twocolum]{revtex4}
-%%\documentclass{report}
-%\documentclass[useAMS,usenatbib]{mn2e_x}
-\documentclass[preprint, a4paper, 11pt]{aastex}
 %\usepackage{psfig,morefloats,url}
@@
 \newcommand{\POW}[2]{\mbox{$\rm10^{#1}\rm\:#2$}}
-\def\LUM{\:{\rm ergs\:s^{-1}}}
-\def\FLUX{\:{\rm ergs\:cm^{-2}\:s^{-1}}}
-\def\OIGS{\:{\rm ergs\:cm^{-2}\:s^{-1}\:\AA^{-1}}}
+\def\LUM{\:{\rm erg\:s^{-1}}}
+\def\FLUX{\:{\rm erg\:cm^{-2}\:s^{-1}}}
+\def\OIGS{\:{\rm erg\:cm^{-2}\:s^{-1}\:\AA^{-1}}}
 
@@
 %\author[Matthews et al.]
-\author{
+\author[Matthews et al.]{
 \parbox[t]{\textwidth}{
@@
 picture involving a central black hole, an accretion disc and an associated outflow.
-Here, we continue our tests of  this paradigm by comparing ``average'' quasar spectra to 
+Here, we continue our tests of  this paradigm by comparing quasar spectra to 
 synthetic spectra of simple biconical disc wind models, produced with our state-of-the-art 
 Monte Carlo radiative transfer and photoionization code PYTHON.
-Previously, we have shown that we could produce synthetic spectra resembling those of observed AGN for plausible wind models, but only if the X-ray luminosity was limited to about  10$^{42}$ ergs s$^{-1}$.
+Previously, we have shown that we could produce synthetic spectra resembling those of observed AGN for plausible wind models, but only if the X-ray luminosity was limited to about  10$^{43}$ erg s$^{-1}$.
 Here , we investigate the  degree to which  clumping of the outflow allows us to
-produce synthetic spectra in the rest-frame UV that have the characteristics of quasars with X-ray luminosities as large as 10$^{45}$ ergs s$^{-1}$. 
+produce synthetic spectra in the rest-frame UV that have the characteristics of quasars with X-ray luminosities as large as 10$^{45}$ erg s$^{-1}$. 
 We conclude, perhaps not surprisingly,  that clumping does maintain the ionization state of the wind necessary for strong BAL features in the rest-frame UV at more realistic X-ray luminosities.
@@
 excited line emission in, e.g., \civ\ and \la, to emerge at the low inclination, 
-`Type 1 quasar-like' angles. 
-At the highest inclinations, the synthetic spectra possess prominent \mg\ and \al\ BALs, the absorption features seen in LoBAL quasars. 
+`Type 1 quasar-like' angles. At the highest inclinations, the synthetic spectra possess prominent \mg\ and \al\ BALs, the absorption features seen in LoBAL quasars. 
 Despite these successes, we are unable to reproduce 
 the remarkably uniform emission line properties 
-seen in BAL and non-BAL quasar composites. 
-% {\bf This sentence needs to be more precise, especially in 
-% light of the statement earlier in the abstract about ``good agreement''}
+seen in BAL and non-BAL quasar composites, as we find a marked increase
+in emission line equivalent widths at high inclination `BALQSO-like' angles. 
 This is due to a fundamental constraint arising
@@
 involving an accretion disc wind is a promising scenario, but our results 
-pose a number of difficult challenges to such a model.
+pose a number of difficult challenges to models in which an equatorial outflow
+rises from a limb-darkened, foreshortened accretion disc.
 % {\bf There is confusion in the abstract, at least, in what is the model and what is the synthetic spectra, as well as whether there is one model or many models.
@@
 
-\maketitle
 %\begin{keywords}
@@
 %\end{keywords}
+
+\maketitle
 
@@
 disc winds offer a natural explanation for the
-diverse phenemonology of luminous AGN and QSOs \citep[e.g.][]{MCGV95, elvis2000}. 
+diverse phenemonology of luminous AGN and quasars \citep[e.g.][]{MCGV95, elvis2000}. 
 Depending on viewing angle, an observer 
 may see a BALQSO or normal `Type 1' quasar.
-Within this unification framework, the broad-line region (BLR) can 
+Within this {\em geoemtric unification} framework, the broad-line region (BLR) can 
 correspond either to the dense wind base or clumps embedded
@@
 outflows in AGN, although on very different scales to line-driven instabilities 
-\citep{PSK2000,PK04,progakurosawa2010,proga2014}.  {\bf KSL: I do not believe the AGN simulations have the resolution to produce clumping on the scale of hot star winds.
-JM: that's why I mention scales, although I can specifically mention resolution if we
-want.}
+\citep{PSK2000,PK04,progakurosawa2010,proga2014}.  
+% {\bf KSL: I do not believe the AGN simulations have the resolution to produce clumping on the scale of hot star winds.
+% JM: that's why I mention scales, although I can specifically mention resolution if we
+% want.}
 Nevertheless, clumpy winds offer an observationally motivated and theoretically 
@@
 
-% An inhomogenous outflow has been proposed as a model for the BLR (REFs)
-% Clumping is expected in outflows and BLRs.
-
-% The UV spectrum of {\em non-BAL} QSOs is typified by a series
-% of strong emission lines (e.g. \la, \civ, \nv) with an underlying blue continuum
-% - the so-called {\sl `big blue bump'} (BBB). The BBB is normally attributed to blackbody-like
-% emission from an accretion disc surrounding the central black hole (REF), similar
-% to that described by \cite{shakurasunyaev1973}. However,
-% a number of issues have arisen relating to this model. First, 
-% AGN/QSO spectra exhibit a `break' in the spectrum at around $1000$~\AA 
-% which scales only weakly with black hole mass. This potentially 
-% suggests a problem with a thin disc model (e.g. Antonucci). 
-% However, it is possible that this is the result of incorrect intergalactic medium
-% (IGM) corrections (REF) or corresponds to the temperature 
-% at which a line-driven wind carries mass away from the system (laor davis).
-% Second, results from microlensing (REFs) imply that the disc emission 
-% region is $\sim4$ times larger than one might expect from a Shakura-Sunyaev
-% model. Inhomogenous discs have been proposed as an alternative (REFs).
-% These observations appear to pose problems for the thin disc model of luminous,
-% sub-Eddington AGN. However, recent results from \cite{capellupo2015} find 
-% that if one includes a combination of mass-loss, general relativity (GR) and Comptonisation
-% then AGN SEDs can, in general, be fitted well with accretion disc models.
-% Uncovering the intrinsic disc SED and understanding the effect of the outflow on the accretion 
-% mechanism is clearly crucial if we are to properly understand the physical nature
-% of AGN.
-
-% The geometry and size of the BLR is also a matter of contention. 
-% The main constraints on the emission region size come from microlensing (REFs)
-% and reverberation mapping (REFs). While these observations have mostly been
-% carried out for Seyfert galaxies, there are also a few instances of these methods
-% being applied to quasars (REFs). A number of different proposals have been made 
-% for the origin of the BLR. Early AGN unification scenarios posited that the broad emission lines
-% where produced by clouds of plasma orbiting fairly close to the BH (refs).
-% Since then, multiple interpretations of a disc wind model have been proposed,
-% with varying radii and geometries (refs).
-
-We have been engaged in a project to determine whether it is possible to simulate the properties of the spectra of AGN, including BAL QSOs, using simple kinematic prescriptions for biconical disc winds using a Monte Carlo radiative transfer (MCRT) code that calculates the ionization structure of the wind and simulates the spectra from such a system \citep[][hereafter H13]{simlong2008,sim2010,higginbottom2013}.
-The results have encouraging in the sense that in H13, we showed we could produce simulated spectra that resembled that of BAL QSOs, as long as the luminosity of the central engine was relatively low, of order \POW{43}{\LUM} and the mass loss rate was relatively high, of order the mass accretion rate.
-However, at higher luminosities, the wind was so ionized that UV absorption lines were not produced.
+We have been engaged in a project to determine whether it is possible to simulate the properties of the spectra of AGN, including BALQSOs, using simple kinematic prescriptions for biconical disc winds using a Monte Carlo radiative transfer (MCRT) code that calculates the ionization structure of the wind and simulates the spectra from such a system \citep[][hereafter H13]{simlong2008,sim2010,higginbottom2013}.
+The results have been encouraging in the sense that in H13, we showed we could produce simulated spectra that resembled that of BALQSOs, as long as the luminosity of the X-ray source was relatively low, of order \POW{43}{\LUM} and the mass loss rate was relatively high, of order the mass accretion rate.
+However, at higher X-ray luminosities, the wind was so ionized that UV absorption lines were not produced.
 In addition, and in part due to limitations in our radiative transfer code, the model failed to produce spectra with strong emission lines at any inclination angle.
@@
 
-For this study, we use the MCRT code \py\ we have developed to carry out our 
-radiative transfer and photoionization simulations in non-local thermodynamic
-equilibrium (non-LTE). The code can be used to model a variety of
+For this study, we use the MCRT code \py 
+\footnote{Named {\sl c. 1995}, predating the inexorable rise of a certain progamming language.} we have developed to carry out our 
+radiative transfer and photoionization simulations in non-local-thermodynamic-equilibrium 
+(non-LTE). The code can be used to model a variety of
 disc-wind systems; it has been used with application to accreting white dwarfs 
@@
 Once the ionization structure has converged, the ionization structure is held fixed, and  synthetic spectra are generated at specific inclination angles in a series of "spectral cycles".
-LK02 provide a more detailed  description of the original code; various improvements have been made since then and are described by
- \cite{simmacro2005}, H13 and M15.  
+LK02 provide a more detailed  description of the original code; various improvements have been made since then and are described by \cite{simmacro2005}, H13 and M15.
 %A full description of the code will be published elsewhere; 
@@
 
-% {\bf ksl - I a a bit torn over whether we add a few 3 sentences to describe the basic idea.
-Some will be reading this for the first time.
-Items that one would include are that we calculate the radiative transfer in a cylindrical coordinate system of dimension ??
-x ??.
-We have ionization and spectral cycles.
-In each cycle, ??
-photon bundles are generated.
-We stop the ionization cycles after they converge, without any details.
-I think this would be useful because we introduce terms like ``cell'' later on.', and without some kind of description they have no context}
-
-\subsection{Line transfer treatment}
+\subsection{Line transfer}
 
@@
 In this scheme, the energy packets interact with either two-level `simple ions' 
-or full `macro-atoms'. This allows one to treat non-LTE line transfer in radiative equilibrium {\bf KSL: what does "in radiative equilibrium" here mean? 
-JM: not sure what the question is, really- radiative equilibrium is a
-key assumption in the macro-atom framework.}
+or full `macro-atoms'. This allows one to treat non-LTE line transfer in radiative equilibrium, which assumes both statistical equilibrium and that 
+radiative heating balances radiative cooling.
+% {\bf KSL: what does "in radiative equilibrium" here mean? 
+% JM: Defined.}
 without approximation for elements that are identified as 
@@
 AGN spectra of \LA.  
-H13 treated all atoms in a two-level approximation.  {\bf KSL:
-I thought we were also doing He. JM: yep, corrected.}
-
-\subsection{Ionization treatment (anything but scheme)}
+H13 treated all atoms in a two-level approximation.  
+% {\bf KSL:
+% I thought we were also doing He. JM: yep, corrected.}
+
+\subsection{Ionization treatment}
 
@@
 then calculated by solving the rate equations between ions. We include collisional ionization
-and photoionization balanced with radiative, dielectronic and collisional (three-body) recombination.
+and photoionization balanced with radiative, 
+dielectronic and collisional (three-body) recombination.
 As in M15, we use a dilute Boltzmann approximation to calculate 
@@
 % treated as macro-atoms. 
-{\bf KSL: 
-It seems a bit odd that you explain what we do with simple ions our old approach, but don't say what is done for macro-atoms,.  You only say it is not the other.
-JM: WE've shortened the seciton on simple-ions as agreed..}
+% {\bf KSL: 
+% It seems a bit odd that you explain what we do with simple ions our old approach, but don't say what is done for macro-atoms,.  You only say it is not the other.
+% JM: We've shortened the section on simple-ions as agreed..}
 
@@
 The accretion disc is assumed to be geometrically thin, but optically thick.
-We thus treat the disc as an ensemble of blackbodies with a 
+Accordingly, we treat the disc as an ensemble of blackbodies with a 
 \cite{shakurasunyaev1973} effective temperature profile. 
@@
 All photon sources in our model are opaque, meaning
-that r-packets which strike them are destroyed.
+that r-packets that strike them are destroyed.
 The inner radius of the disc extends to the innermost 
@@
 constraint (see Lucy 2002, M15).  
-{\bf I confess, I do not understand what is being said here.
+% {\bf I confess, I do not understand what is being said here.
 I would like to understand it better, and I would like it explained better.
@@
 
-\subsection{A First Approximation for Clumping}
+\subsection{A Simple Approximation for Clumping}
 
@@
 Implementing a treatment of clumping is challenging, for
-two main reasons. First, there are significant 
-computational difficulties associated with adequately
+two main reasons. First, the physical scale lengths and density contrasts 
+associated with these parameters are not well-constrained from observations.  
+Second, there are significant computational difficulties associated with adequately
 resolving and realistically modelling a series of small scale, high density
-regions with a MCRT code. Second, the addition of multiple additional degrees of
-freedom in the model results in significantly wider parameter space.
-Unfortunately, the physical scale lengths and density contrasts 
-associated with these parameters are not well-constrained from observations.
-{\bf Reverse the order of these difficulties.
-The most important is that it is not clear what kind of clumping an AGN wind has; the computational problem is a secondary one.}
+regions with a MCRT code. 
+% Second, the addition of multiple additional degrees of
+% freedom in the model results in significantly wider parameter space.
+% Unfortunately, the physical scale lengths and density contrasts 
+% associated with these parameters are not well-constrained from observations.  
+% {\bf KSL: Reverse the order of these difficulties.  The most important is that it is not clear what kind of clumping an AGN wind has; the computational problem is a secondary one JM: Done..}
 
@@
 used successfully in stellar wind modelling, known as 
-{\em microclumping} \citep{hamann1998,hamann2008}(MORE REFS), which minimizes the computational difficulties. 
+{\em microclumping} \citep{hamann1998,hamann2008}(MORE REFS), 
+which minimizes the computational difficulties. 
 The underlying assumption in microclumping is that clump sizes are much smaller than the 
@@
 \end{equation}
-% \kappa = f_V \kappa_C(D) && \epsilon = f_V \epsilon_C(D).
-% \end{equation}
 Here the subscript $C$ denotes that the quantity is calculated using the 
-enhanced density in the clump. The resultant effect is that {\em linear} processes,
-such as electron scattering, are unchanged, as $f_V$ and $D$ will cancel out. 
-However, any quantity which scales with the {\em square} of density, 
+enhanced density in the clump. The resultant effect is that, {\em for fixed temperature},
+ processes that are {\em linear} in density, such as electron scattering, are unchanged, 
+as $f_V$ and $D$ will cancel out. However, any quantity that scales with the {\em square} of density, 
 such as collisional excitation or recombination, will increase by a factor of $D$.
-
-% which is defined as 
-% \begin{equation}
-% D = \frac{1}{f} && 
-% \end{equation}
-% We then multiply all densities in the model by $D$, and all emitting volumes
-% by $f$. This has the effect of enhancing all emissivities and opacities
-% that scale with the square of density (such as collisional excitation and recombination) 
-% by a factor $D$. All processes that scale linearly with density 
-% (such as electron scattering and bound-free opacity)
-% will remain unchanged for a given ionization state.
+However, in the event that one of these
 
@@
 disc winds \citep{hamann2013}. This is the main motivation for incorporating microclumping
-into our model. This treatment is first-order; it does not adequately
+into our model. This treatment is necessarily simple; it does not adequately
 represent the complex substructures and stratifications in ionization
@@
 \end{itemize}
-In this section, we present one of the most promising models and discuss
+In the next section, we present one of the most promising models and discuss
 the various successes and failures with respect to the above criteria.
@@
 and physical constraints and assess the potential for unification. 
+We then discuss the sensitivity to key parameters in section 5.
 The full grid, including output synthetic spectra and plots can be found at
@@
 
-{\bf I still think we need to avoid using model to be a generic term to describe the outflow and the spectra.
+% {\bf I still think we need to avoid using model to be a generic term to describe the outflow and the spectra.
 If you mean the spectra use "model spectra" or "synthetic spectra'.
@@
 
-% This set of parameters
-% was arrived at by conducting a limited grid search over a 
-% 5-dimensional parameter space involving the variables
-% $r_{min}$, $\theta_{min}$, $f$, $\alpha$ and $R_V$.
-% We evaluated these models based on the following
-% criteria:
-% \begin{itemize}
-% \item Does the model maintain the right ionization state to produce strong BALs ($BI > ??$)?
-% \item Does significant line emission emerge at low inclinations, with $EW\sim50\AA$ in \civ?
-% \item Do H recombination lines appear in the spectrum, $EW\sim50\AA$ in \la?
-% \item Do a certain range of angles produce LoBAL features?
-% \item Does the model compare favourably to quasar composite spectra?
-% \end{itemize}
-% In this section, we present one of the most promising models and discuss
-% the various successes and failures.
-% This allows us to gain insight into fundamental geometrical 
-% and physical constraints and assess the potential for unification. 
-% The full grid, including output synthetic spectra and plots can be found at
-% \url{jhmatthews.github.io/quasar-wind-grid/}.
-
 \begin{table}
@@
 $\alpha_X$ 	 &	 $-0.9$ \\ 
-$L_{X} $ 	 &	 $10^{45}~\rm{ergs~s^{-1}}$$^*$ \\ 
+$L_{X} $ 	 &	 $10^{45}~\rm{erg~s^{-1}}$$^*$ \\ 
 $r_{disc}(min)=r_{X}$   &	 $6r_g=8.8\times10^{14}~{\rm cm}$ \\ 
@@
 \end{tabular}
-\caption{Wind geometry parameters used in the model.}
+\caption{Wind geometry parameters 
+used in the model, as defined in the text and figure 1.
+Parameters differing from the benchmark model of H13 are 
+highlighted with an asterisk.}
 \label{wind_param}
@@
 Figure~\ref{fig:wind} shows the physical properties of the wind.
-The wind rises slowly from the disc at first, with clumped densities  {\bf clumped densities is jargon, use perhaps density of the clumps in the wind}
-of $n_H \sim 10^{11}~\rm{cm^{-3}}$ close to the disc plane.
+The wind rises slowly from the disc at first, with clump densities 
+of $n_H \sim 10^{11}~\rm{cm^{-3}}$ close to the disc plane, 
+where $n_H$ is the local number density of H.
 The flow then accelerates over a scale length of $R_V=10^{19}~\rm{cm}$
@@
 by the panels showing the ion fraction $F=n_j/n_{tot}$ of some important ions.
-With a clumpted wind, we are able to produce the range of ionization states observed
+With a clumped wind, we are able to produce the range of ionization states observed
 in quasars and BALQSOs, while adopting a realistic $2-10$ keV X-ray luminosity
-of $L_{X}=10^{45}~\rm{ergs~s^{-1}}$. Without clumping, this wind would be over-ionized 
+of $L_{X}=10^{45}~\rm{erg~s^{-1}}$. Without clumping, this wind would be over-ionized 
 to the extent that opacities in e.g., \civ\ would be entirely negligible (see H13).
@@
 \end{equation}
-\noindent where $\rm{n_H}$ is the local number density of H, and $\nu$ denotes photon 
+\noindent where $\nu$ denotes photon 
 frequency. Shown in figure~\ref{fig:wind},
@@
 \centering
-\includegraphics[width=1.0\textwidth]{figures/uvspec_estfix.png}
+\includegraphics[width=1.0\textwidth]{figures/uvspec_new.png}
 \caption
 {
-Synthetic spectra at five viewing angles in our model. The coloured lines
-show different quasar and BAL quasar composites, and the dotted line shows a disc
+Synthetic spectra at four viewing angles in our model. At 
+$20^\circ$ and $60^\circ$ we show a comparison to an SDSS quasar composite
+from Recihard et al. (2003). At $73^\circ$ and $76^\circ$ we show a comparison to
+an {\sl HST} STIS spectrum of the high BALnicity BALQSO 
+PG0946+301 (Arav et al. 2000), and an SDSS spectrum of the LoBAL quasar 
+XXXXX (REF), respectively. The dotted line shows a disc
 only continuum to show the effect of the outflow on the continuum level. 
+All the spectra are scaled to the model flux at $2000$\AA, expect for the 
+{\sl HST} STIS spectrum of PG0946+301, which is scaled using a continuum fit
+due to the incomplete wavelength coverage.
+% HST STIS spectrum of PG0946+301 (Arav et al. 2000)
 }
@@
 
-\begin{figure*} %fullpage
-\centering
-\includegraphics[width=1.0\textwidth]{figures/0946_estfix.png}
-\caption
-{
-Synthetic spectra at $72^\circ$ compared to an HST STIS spectrum
-of PG0946+301 (Arav et al. 2000). The spectrum is scaled to the flux at 1300\AA\
-for direct comparison. 
-}
-\label{fig:stis}
-\end{figure*} %fullpage
-
 Figure~\ref{fig:uvspec} shows the synthetic spectrum in the UV from our model. 
 To assess the ability of the model to match real 
-quasar spectra, we also show {\sl Sloan Digital Sky Survey} (SDSS) quasar and BALQSO 
-composites from \cite{reichard2003}, normalised to the flux at 2000\AA\ in each panel. 
+quasar spectra, we also show {\sl Sloan Digital Sky Survey} (SDSS) quasar
+composites from \cite{reichard2003}, normalised to the flux at 2000\AA\
+for low inclinations. Unfortunately, the wide variety of
+line profile shapes and internal trough structure 
+tends to `wash out' BAL troughs to the extent that they do not 
+resemble typical BALQSOs.
+Because of this, we instead use compare to a {\sl Hubble Space Telescope} 
+STIS spectrum of the high BALnicity BALQSO PG0946+301 (Arav et al. 2000),
+and an SDSS spectrum of the LoBAL quasar XXXXX (REF),
+for the angles of $73^\circ$ and $76^\circ$, respectively. 
 We show a cartoon illustrating how geometric effects determine
@@
 FeLoBALQSOs are discussed in section 2.4.
-Clearly, the absorption lines in the 
-synthetic spectra at BALQSO-like angles do not match the composites; this
-is {\em not} due to a failure of our model, but rather because a geometric mean
-BALQSO composite spectrum tends to wash out the broad absorption features due to the wide
-range of absorption characteristics. To demonstrate this, we show a comparison 
-to a {\sl Hubble Space Telescope} STIS spectrum of the high BALnicity BALQSO PG0946+301 
-(Arav et al. 2000) in figure \ref{fig:stis}.
+% Clearly, the absorption lines in the 
+% synthetic spectra at BALQSO-like angles do not match the composites; this
+% is {\em not} due to a failure of our model, but rather because a geometric mean
+% BALQSO composite spectrum tends to wash out the broad absorption features due to the wide
+% range of absorption characteristics. To demonstrate this, we show a comparison 
+% to a {\sl Hubble Space Telescope} STIS spectrum of the high BALnicity BALQSO PG0946+301 
+% (Arav et al. 2000) in figure \ref{fig:stis}.
 
@@
 in a polar direction above the disc.  
-{\bf KSL: it sounds like what you are suggesting is a low density inner flow, our domain 2 stuff actually permits or indeed one might be able to produce this within SV is you adopted a different mass loss with radius assumption.
+% {\bf KSL: it sounds like what you are suggesting is a low density inner flow, our domain 2 stuff actually permits ...
+or indeed one might be able to produce this within SV is you adopted a different mass loss with radius assumption.
 JM: I am being deliberately
-vague about what I am suggesting. I am saying there are three physical
-possibilities: either wind itself causes this scattering contribution, which doesn't happen in our model, or you have partial covering, or you have some additional scatterer.}
+% vague about what I am suggesting. I am saying there are three physical
+% possibilities: either wind itself causes this scattering contribution, which doesn't happen in our model, or you have partial covering, or you have some additional scatterer.}
 
@@
 crucially important in determining the emergent line ratios.  
-{\bf KSL: This is a bit oddly explained. Our problem is at low inclination.  Note that I am a bit concerned with Fig 3; the model spectra and the observations look very different.}
+% {\bf KSL: This is a bit oddly explained. Our problem is at low inclination.  Note that I am a bit concerned with Fig 3; the model spectra and the observations look very different.}
 
@@
 continuum to emerge. Hints that light scattered off a spatially extended 
-wind may contribute signiciantly to the emergent continuum come from radiative transfer s
+wind may contribute signiciantly to the emergent continuum come from radiative transfer
 simulations \citep{simproga2012} and microlensing observations \citep{sluse2015}.
@@
 It is also possible that the equatorial paradigm invoked from early polarisation
-studies \citep{goodrich1995, cohen1995,brotherton2006} is an over-simplification, or is merely incorrect. 
+studies \citep{goodrich1995, cohen1995,brotherton2006} 
+is an over-simplification, or is incorrect. 
 High brightness temperatures in some RL BALQSOs imply polar outflows \citep{zhou2006} 
@@
 
-{\bf I have to say I find this hard to understand.
+% {\bf I have to say I find this hard to understand.
 Are you trying to say that in CVs which we are know are thin disks with winds, the EW of the red-wing of emission lines increases with inclination angle ...
@@
 I also still think that you should move this discussion later in the paper and not bury it here.}
-
-% The final possibility is that BALQSOs are not viewed equatorially. 
-% This possibility is supported by measurements of the radio spectral indices
-% of radio-loud BALQSOs (REF) and attempts to explain the polarisation dichotomy 
-% of type 1 and 2 AGN (REF). This would imply that type 1 quasars and BALQSOs are generally 
-% viewed from a fairly narrow range of angles ($\sim0$-$50^\circ$), and could also mean 
-% the BALQSO fraction requires {\em both} evolutionary and geometric explanations. 
-% There is also clear conflict between this explanation and some
-% polarisation results \citep{goodrich1995, cohen1995}(BROTHERTON).
-% We suggest that future modelling should include predictions of polarisation signatures
-% from a detailed radiative transfer simulation, allowing
-
-% When comparing BALQSO and quasar composites, it is apparent
-% that they possess remarkably similar line strengths and widths 
-% \citep[e.g.][]{weymann1991,reichard2003}.  
-% {\bf I think we mean EW here; otherwise I don't understand what we are talking about.
-We could say ``line shapes and equivalent widths''.
-I also think this requries more than one sentence of introduction.} This presents a challenge to our model, as well as the geometric
-% unification picture in general, because these quantities should vary with inclination angle.
-% Limb darkening and foreshortening causes the disc continuum emission to be 
-% strongly anisotropic, yet the line emission in our models is much more isotropic. 
-% This has the effect of enhancing the line-to-continuum ratios at high inclinations. 
-% To construct a scenario where emission 
-% line equivalent widths are comparable at all inclinations requires 
-% significant fine-tuning when considering a classical thin disc. {\bf Is the previous sentence a throwaway line, or has some person done this.  If so, please reference; if not please delete.}
-%An alternative, simpler solution is that the emergent continuum is roughly isotropic.
-
-% Obviously,  one possible solution to this problem is hypothesize a more isotropic distribution for the emergent condition than predicted by a ``classical'' disc. 
-% General relativistic effects -- specifically, light bending
-% and relativistic beaming -- can cause 
-% the accretion disc SED to become more isotropic \citep[e.g.][]{zhang1997,munozdarias2013}.
-Incorporating these effects into {\sc PYTHON} would be a very difficult and time-consuming challenge.
-Therefore, for the purposes of this discussion we have chosen to investigate whether GR effects could produce enough isotropy to address the EW problem, we have generated
-% \ GR disc spectra, we use the code \agn\ \citep{hubeny2000,davishubeny2006,davis2007}. 
-% The output flux at three different wavelengths
-% as a function of inclination for an \agn\ model with the same disc and BH parameters
-% as our clumpy wind model is shown in figure~\ref{fig:f2000}.  The results indicate that 
-% the effects of GR on an AGN disc are much less extreme 
-% in the UV portion of the spectrum than the calculations
-% by \cite{zhang1997} for the X-rays in X-ray binaries.
-% The emission for the disks of AGN is still strongly anisotropic.
-% GR alone therefore cannot explain the line ratio trends in quasars by making the disc
-% emit more isotropically. This supports the findings of \cite{risaliti2011}, 
-% who find that EW distributions in quasars are consistent with anisotropic emission 
-% from optically thick, 
-% disc-like structures for {\em both} the continuum source and BLR. 
-% If this is the case, it has a dramatic affect on the intrinsic
-% BAL fraction inferred from flux-limited samples \citep{goodrich1997,krolikvoit1998}.
-% We will explore these ideas further in a future study.  
-% {\bf Wait!  All this says is that there has to be an alternative explanation.
-% It is not support for any specific explanation!. This last few sentences should
-% be a separate paragraph.  They should start out: An alernative explanation proposed 
-% by risalite is that...}
-
-% Figure 5 also shows the spectrum into the optical,
-% showing that the outflow produces signiciant optical emission lines
-% as well as having a noticeable effect on the continuum shape. This
-% is particularly true around the Balmer jump at $3646\AA$ and is due to
-% a prominent wind-formed recombination continuum.
 
@@
 
-% \begin{figure} %fullpage
-% \centering
-% \includegraphics[width=1.0\textwidth]{figures/sed_all_balqsos.png}
-% \caption
-% {
-% Broadband SEDs compared to IR and X-ray SEDs for selected BALQSOs 
-% from Grupe \& Nousek (2015).
-% }
-% \label{fig:xray}
-% \end{figure} %fullpage
-
-%{\bf:  Again this section needs an introduction.  Why is this important?}
-
-One of the main motivations for including a treatment of clumping was
+The main motivation for including a treatment of clumping was
 to avoid over-ionization of the wind in the presence of strong X-rays. 
@@
 
-% To resolve these challenges, we suggest the following routes forward.
-% \begin{enumerate}
-% \smallskip
-% \item 
-% \smallskip
-% \item 
-% \smallskip
-% \item It is clear that the commonly accepted paradigm of an equatorial
-% wind with a covering factor of $\sim20\%$ does provide an adequate 
-% unified model, as shown here and by other authors 
-% (e.g. Marin \& Goosman 2013; DiPompeo et al. 2012a).
-% More collimated winds may solve some problems, but must be reconciled with
-% polarisation results that suggest an equatorial geometry.
-% Computing the polarisation of emergent energy packets in our 
-% MCRT code would allow direct comparison
-% between outputs from a known geometry and 
-% spectropolarimetry of quasars and AGN.
-% \smallskip
-% \item In addition to spectropolarimetry, one
-% of the best observational tools for probing outflow geometries
-% is reverberation mapping. We are starting to 
-% incorporate methods for predicting the reverberation
-% outputs from our models. By comparing with observational data, this
-% may provide stronger constraints on outflow geometries.
-% \end{enumerate}
-
 \section*{Acknowledgements}
 
-The work of JHM, SWM, NSH and CKL is supported by the
+The work of JHM, SWM, NSH and CK is supported by the
 Science and Technology Facilities Council (STFC),

### 2015-12-08 paper_mnras.tex

--- 2015-12-07 paper_mnras.tex
@@
 picture involving a central black hole, an accretion disc and an associated outflow.
-Here, we continue our tests of  this paradigm by comparing ``average'' quasar spectra to 
-synthetic spectra of simple biconical disc wind models, using our state-of-the-art 
-Monte Carlo radiative transfer and photoionization code.
-In particular, we investigate whether clumping of the outflow allows us to 
-produce synthetic spectra in the rest-frame UV that have the characteristics of quasars. 
-We find that a simple treatment of clumping (`microclumping') 
-allows for a more realistic X-ray luminosities, while maintaining the ionization 
-state necessary for strong BAL features in the rest-frame UV. 
+Here, we continue our tests of  this paradigm by comparing quasar spectra to 
+synthetic spectra of simple biconical disc wind models, produced with our state-of-the-art 
+Monte Carlo radiative transfer and photoionization code PYTHON.
+Previously, we have shown that we could produce synthetic spectra resembling those of observed AGN for plausible wind models, but only if the X-ray luminosity was limited to about  10$^{43}$ erg s$^{-1}$.
+Here , we investigate the  degree to which  clumping of the outflow allows us to
+produce synthetic spectra in the rest-frame UV that have the characteristics of quasars with X-ray luminosities as large as 10$^{45}$ erg s$^{-1}$. 
+We conclude, perhaps not surprisingly,  that clumping does maintain the ionization state of the wind necessary for strong BAL features in the rest-frame UV at more realistic X-ray luminosities.
 We examine the X-ray properties of these simple clumped models
 and find good agreement with existing X-ray samples of AGN and quasars.
-The dense, X-ray heated wind produces strong recombination and collisionally 
+In addition, the dense, X-ray heated wind produces strong recombination and collisionally 
 excited line emission in, e.g., \civ\ and \la, to emerge at the low inclination, 
-`Type 1 quasar-like' angles. 
-At the highest inclinations, the synthetic spectra possess prominent \mg\ and \al\ BALs, the absorption features seen in LoBAL quasars. 
+`Type 1 quasar-like' angles. At the highest inclinations, the synthetic spectra possess prominent \mg\ and \al\ BALs, the absorption features seen in LoBAL quasars. 
 Despite these successes, we are unable to reproduce 
 the remarkably uniform emission line properties 
-seen in BAL and non-BAL quasar composites. 
-% {\bf This sentence needs to be more precise, especially in 
-% light of the statement earlier in the abstract about ``good agreement''}
+seen in BAL and non-BAL quasar composites, as we find a marked increase
+in emission line equivalent widths at high inclination `BALQSO-like' angles. 
 This is due to a fundamental constraint arising
@@
 \citep{PSK2000,PK04,progakurosawa2010,proga2014}.  
+% {\bf KSL: I do not believe the AGN simulations have the resolution to produce clumping on the scale of hot star winds.
+% JM: that's why I mention scales, although I can specifically mention resolution if we
+% want.}
 Nevertheless, clumpy winds offer an observationally motivated and theoretically 
@@
 
-For this study, we use the MCRT code \py\ we have developed to carry out our 
-radiative transfer and photoionization simulations in non-local thermodynamic
-equilibrium (non-LTE). The code can be model a variety of
+For this study, we use the MCRT code \py 
+\footnote{Named {\sl c. 1995}, predating the inexorable rise of a certain progamming language.} we have developed to carry out our 
+radiative transfer and photoionization simulations in non-local-thermodynamic-equilibrium 
+(non-LTE). The code can be used to model a variety of
 disc-wind systems; it has been used with application to accreting white dwarfs 
@@
 
-The basic premise involves generating photons from an accretion disc
-and central object, and computing their radiative transfer through an outflow.
-This outflow is discretized into $n_x \times n_z$ cells in a 2.5D
+The code operates as follows:   This outflow is discretized into $n_x \times n_z$ cells in a 2.5D
 cylindrical geometry with azimuthal symmetry.
-First, the code gradually converges on the global temperature and ionization structure.
-Once these ``ionization cycles'' are complete, then a series of further iterations
-allow one to obtain a detailed synthetic spectrum.
-LK02 provides the basic description of the original code; improvements, 
-see especially \cite{simmacro2005}, H13 and M15, have been 
-described in subsequent reports.  
+From some initial conditions in each cell, the code first calculates the ionization structure of the wind in a series of iterations.
+Each iteration in an ``ionization cycle'' consists of generating photons, actually photon packets, from an accretion disc
+and central object, and calculating how these photon bundles scatter through the wind (eventually escaping the outflow or hitting the disk).
+Then updating the ionization structure based on the properties of the radiation field in each cell, and the process is repeated.
+Once the ionization structure has converged, the ionization structure is held fixed, and  synthetic spectra are generated at specific inclination angles in a series of "spectral cycles".
+LK02 provide a more detailed  description of the original code; various improvements have been made since then and are described by \cite{simmacro2005}, H13 and M15.
 %A full description of the code will be published elsewhere; 
-We focus here on the specific changes made to improve the ionization calculation 
+We focus here on the specific changes made for this study intended to improve the ionization calculation of H and He
 and to allow for clumping in the wind.
@@
 In this scheme, the energy packets interact with either two-level `simple ions' 
-or full `macro-atoms'. This allows one to treat non-LTE line transfer in radiative equilibrium
+or full `macro-atoms'. This allows one to treat non-LTE line transfer in radiative equilibrium, which assumes both statistical equilibrium and that 
+radiative heating balances radiative cooling.
+% {\bf KSL: what does "in radiative equilibrium" here mean? 
+% JM: Defined.}
 without approximation for elements that are identified as 
@@
 as simple-ions (see M15). In this study,
-only H is treated as a macro-atom, because 
+only H and He are treated as a macro-atom, because 
 we expect recombination to be important
-in determining their level populations and resultant line emission, and because we were especially interested in the contribution to AGN spectra of \LA.  
+in determining their level populations and resultant line emission, 
+and because we are especially interested in the contribution to 
+AGN spectra of \LA.  
 H13 treated all atoms in a two-level approximation.  
-
-\subsection{Ionization Scheme}
+% {\bf KSL:
+% I thought we were also doing He. JM: yep, corrected.}
+
+\subsection{Ionization treatment}
 
 Macro-atoms have their ion and level populations derived from
-MC rate estimators as described by Lucy (2002,2003). Previously (LK02, H13, M15),
-we used a modified Saha approach to calculate the ionization fractions
+MC rate estimators as described by Lucy (2002,2003). 
+Previously (LK02, H13, M15), we used a modified Saha approach to calculate the ionization fractions
 of simple-ions. As part of  this effort, we have now improved {\sc PYTHON} to explicitly solve the 
@@
 in frequency $\nu$, with the fit parameters deduced from band-limited radiation field estimators.
-The ionization rate out of ion $j$ can then be written as 
-\begin{equation}
-R_{j,j+1}(J)= 
-\displaystyle{
-n_j \left(C_{j} n_e + 
-\sum_{band~i=0}^{n}~
-{\int_{\nu_i}^{~\nu_i+1} \frac{4 \pi J_{\nu,i}\sigma_j(\nu)}  {h \nu} d\nu}
-\right),}
-\end{equation}
-where $\sigma_j$ is the photoionization cross-section, $n_e$
-is the electron density and $C_{j}$
-represents the collisional ionization coefficient.
-The recombination rate {\em into} ion $j$ is given by 
-\begin{equation}
-R_{j+1,j}(T_e) = (\alpha^j_{RR} + \alpha^j_{CR}) n_{j+1} n_e,
-\end{equation}
-where each $\alpha^j$ here is the recombination rate coefficient into the ground state of ion $j$.
-The subscripts denote radiative and 
-collisional (three-body) recombination, respectively. 
-$T_e$ is the electron temperature.
-%% We neglect recombination to and from excited states in the simple-ion calculation. 
-For simple-ions, we use a dilute Boltzmann equation to calculate 
-the population of level $k$ in ionic stage $j$,
-\begin{equation}
-\frac{n_{jk}}{n_j} = \frac{W g_k}{z_j(T_R)} \exp(-E_k/kT_R).
-\end{equation}
-Here $z_j$ is the partition function of ionic stage $j$,
-$T_R$ is the effective radiation temperature,
-$E_k$ is the energy difference between level $k$ and the ground state,
-and $g_k$ is the statistical weight of level $k$. 
-We stress that this approximation is not required for ions
-treated as macro-atoms.
+This allows the calculation of a photoionization rate estimator. Ion abundances are
+then calculated by solving the rate equations between ions. We include collisional ionization
+and photoionization balanced with radiative, 
+dielectronic and collisional (three-body) recombination.
+As in M15, we use a dilute Boltzmann approximation to calculate 
+the population of levels for simple-ions. We stress that this approximation 
+is not required for ions treated as macro-atoms. 
+% \begin{equation}
+% J_{\nu,i}=K_{pl}\nu^{\alpha_{pl}},
+% \end{equation}
+% for a band $i$, or an exponential 
+% \begin{equation}
+% J_{\nu,i}=K_{exp} e^{(-h\nu/k T_{exp})}.
+% \end{equation}
+% Here, $K_{exp}$, $K_{pl}$, $T_{exp}$ and $\alpha_{pl}$ are spectral fit parameters
+% deduced from the band-limited radiation field estimators.
+% The ionization rate out of ion $j$ can then be written as 
+% \begin{equation}
+% R_{j,j+1}(J)= 
+% \displaystyle{
+% n_j \left(C_{j} n_e + 
+% \sum_{band~i=0}^{n}~
+% {\int_{\nu_i}^{~\nu_i+1} \frac{4 \pi J_{\nu,i}\sigma_j(\nu)}  {h \nu} d\nu}
+% \right),}
+% \end{equation}
+% where $\sigma_j$ is the photoionization cross-section, $n_e$
+% is the electron density and $C_{j}$
+% represents the collisional ionization coefficient.
+% The recombination rate {\em into} ion $j$ is given by 
+% \begin{equation}
+% R_{j+1,j}(T_e) = (\alpha^j_{RR} + \alpha^j_{CR}) n_{j+1} n_e,
+% \end{equation}
+% where each $\alpha^j$ here is the recombination rate coefficient into the ground state of ion $j$.
+% The subscripts denote radiative and 
+% collisional (three-body) recombination, respectively. 
+% $T_e$ is the electron temperature.
+% %% We neglect recombination to and from excited states in the simple-ion calculation. 
+% For simple-ions, we use a dilute Boltzmann approximation to calculate 
+% the population of level $k$ in ionic stage $j$,
+% \begin{equation}
+% \frac{n_{jk}}{n_j} = \frac{W g_k}{z_j(T_R)} \exp(-E_k/kT_R).
+% \end{equation}
+% Here $z_j$ is the partition function of ionic stage $j$,
+% $T_R$ is the effective radiation temperature,
+% $E_k$ is the energy difference between level $k$ and the ground state,
+% and $g_k$ is the statistical weight of level $k$. 
+% We stress that this approximation is not required for ions
+% treated as macro-atoms. 
+% {\bf KSL: 
+% It seems a bit odd that you explain what we do with simple ions our old approach, but don't say what is done for macro-atoms,.  You only say it is not the other.
+% JM: We've shortened the section on simple-ions as agreed..}
 
@@
 constraint (see Lucy 2002, M15).  
+% {\bf I confess, I do not understand what is being said here.
+I would like to understand it better, and I would like it explained better.
+How do we avoid, generating for example recombination photons from non-macro atoms.}
 
@@
 
-\subsection{A First Approximation for Clumping}
-
-Our previous modelling efforts assumed a smooth outflow, 
+\subsection{A Simple Approximation for Clumping}
+
+Our previous modelling efforts, we have assumed a smooth outflow, 
 in which the density at a given point was determined only by the 
@@
 Implementing a treatment of clumping is challenging, for
-two main reasons. First, there are significant 
-computational difficulties associated with adequately
+two main reasons. First, the physical scale lengths and density contrasts 
+associated with these parameters are not well-constrained from observations.  
+Second, there are significant computational difficulties associated with adequately
 resolving and realistically modelling a series of small scale, high density
-regions with a MCRT code. Second, the addition of multiple additional degrees of
-freedom in the model results in significantly wider parameter space.
-Unfortunately, the physical scale lengths and density contrasts 
-associated with these parameters cannot be well-constrained from observations.
-
-To allow for clumping in our outflow we adopt a simple approximation
+regions with a MCRT code. 
+% Second, the addition of multiple additional degrees of
+% freedom in the model results in significantly wider parameter space.
+% Unfortunately, the physical scale lengths and density contrasts 
+% associated with these parameters are not well-constrained from observations.  
+% {\bf KSL: Reverse the order of these difficulties.  The most important is that it is not clear what kind of clumping an AGN wind has; the computational problem is a secondary one JM: Done..}
+
+Given the lack of knowledge about the actual type of clumping, we have adopt a simple approximation
 used successfully in stellar wind modelling, known as 
-{\em microclumping} \citep{hamann1998,hamann2008}(MORE REFS). 
-The key assumption is that typical clump sizes are much smaller than the 
+{\em microclumping} \citep{hamann1998,hamann2008}(MORE REFS), 
+which minimizes the computational difficulties. 
+The underlying assumption in microclumping is that clump sizes are much smaller than the 
 typical photon mean free path, and thus the clumps are 
@@
 Here the subscript $C$ denotes that the quantity is calculated using the 
-enhanced density in the clump. The resultant effect is that {\em linear} processes,
-such as electron scattering, are unchanged, as $f_V$ and $D$ will cancel out. 
-However, any quantity which scales with the {\em square} of density, 
+enhanced density in the clump. The resultant effect is that, {\em for fixed temperature},
+ processes that are {\em linear} in density, such as electron scattering, are unchanged, 
+as $f_V$ and $D$ will cancel out. However, any quantity that scales with the {\em square} of density, 
 such as collisional excitation or recombination, will increase by a factor of $D$.
+However, in the event that one of these
 
@@
 disc winds \citep{hamann2013}. This is the main motivation for incorporating microclumping
-into our model. This treatment is first-order; it does not adequately
+into our model. This treatment is necessarily simple; it does not adequately
 represent the complex substructures and stratifications in ionization
-state we expect in AGN outflows. Nevertheless, clumping is clearly
-important in these flows, and this parameterization allows a simple estimate
-for the effect clumping might have on the ionization state and emergent 
+state we expect in AGN outflows. Nevertheless,  this parameterization allows simple estimates
+of the effect clumping might have on the ionization state and emergent 
 line emission. 
@@
 with $BI > 0$ at $\sim20\%$ of viewing angles?
-\item Does significant line emission emerge at low inclinations, with $EW\sim40\AA$ in \civ?
-\item Do H recombination lines appear in the spectrum, $EW\sim50\AA$ in \la?
-\item Do a small subset of BAL angles produce LoBAL features?
-\item Does the model compare favourably to quasar composite spectra?
+\item Do the synthetic spectra show  line emission emerge at low inclinations, with $EW\sim40\AA$ in \civ?
+\item Do H recombination lines appear in the spectra, $EW\sim50\AA$ in \la?
+\item Do the spectra  produce LoBAL features at a  small subset of BAL angles?
+\item Does the model spectra resemble quasar composite spectra?
 \end{itemize}
-In this section, we present one of the most promising models and discuss
+In the next section, we present one of the most promising models and discuss
 the various successes and failures with respect to the above criteria.
@@
 and physical constraints and assess the potential for unification. 
+We then discuss the sensitivity to key parameters in section 5.
 The full grid, including output synthetic spectra and plots can be found at
 \url{jhmatthews.github.io/quasar-wind-grid/}.
+
+% {\bf I still think we need to avoid using model to be a generic term to describe the outflow and the spectra.
+If you mean the spectra use "model spectra" or "synthetic spectra'.
+Note - the whole question of the model grid and the selection of one specific instantiation is not dealt with well.}
 
@@
 Figure~\ref{fig:wind} shows the physical properties of the wind.
-The wind rises slowly from the disc at first, with clumped densities
-of $n_H \sim 10^{11}~\rm{cm^{-3}}$ close to the disc plane.
+The wind rises slowly from the disc at first, with clump densities 
+of $n_H \sim 10^{11}~\rm{cm^{-3}}$ close to the disc plane, 
+where $n_H$ is the local number density of H.
 The flow then accelerates over a scale length of $R_V=10^{19}~\rm{cm}$
 up to a terminal velocity equal to the escape velocity at the streamline base
-($\sim10,000~\rm{km~s^{-1}}$). This gradual acceleration means that
-the wind exhibits a stratified ionization structure, with low ionization material
+($\sim10,000~\rm{km~s^{-1}}$). This gradual acceleration results in
+a wind that exhibits a stratified ionization structure, with low ionization material
 in the base of the wind giving way to highly ionized plasma further out.
@@
 by the panels showing the ion fraction $F=n_j/n_{tot}$ of some important ions.
-By clumping the wind, we are able to produce the range of ionization states observed
+With a clumped wind, we are able to produce the range of ionization states observed
 in quasars and BALQSOs, while adopting a realistic $2-10$ keV X-ray luminosity
-of $L_{X}=10^{45}~\rm{ergs~s^{-1}}$. Without clumping, this wind would be over-ionized 
+of $L_{X}=10^{45}~\rm{erg~s^{-1}}$. Without clumping, this wind would be over-ionized 
 to the extent that opacities in e.g., \civ\ would be entirely negligible (see H13).
@@
 \centering
-\includegraphics[width=1.0\textwidth]{figures/uvspec_estfix.png}
+\includegraphics[width=1.0\textwidth]{figures/uvspec_new.png}
 \caption
 {
-Synthetic spectra at five viewing angles in our model. The coloured lines
-show different quasar and BAL quasar composites, and the dotted line shows a disc
+Synthetic spectra at four viewing angles in our model. At 
+$20^\circ$ and $60^\circ$ we show a comparison to an SDSS quasar composite
+from Recihard et al. (2003). At $73^\circ$ and $76^\circ$ we show a comparison to
+an {\sl HST} STIS spectrum of the high BALnicity BALQSO 
+PG0946+301 (Arav et al. 2000), and an SDSS spectrum of the LoBAL quasar 
+XXXXX (REF), respectively. The dotted line shows a disc
 only continuum to show the effect of the outflow on the continuum level. 
-HST STIS spectrum of PG0946+301 (Arav et al. 2000)
+All the spectra are scaled to the model flux at $2000$\AA, expect for the 
+{\sl HST} STIS spectrum of PG0946+301, which is scaled using a continuum fit
+due to the incomplete wavelength coverage.
+% HST STIS spectrum of PG0946+301 (Arav et al. 2000)
 }
@@
 To assess the ability of the model to match real 
-quasar spectra, we also show {\sl Sloan Digital Sky Survey} (SDSS) quasar and BALQSO 
-composites from \cite{reichard2003}, normalised to the flux at 2000\AA\ in each panel. 
+quasar spectra, we also show {\sl Sloan Digital Sky Survey} (SDSS) quasar
+composites from \cite{reichard2003}, normalised to the flux at 2000\AA\
+for low inclinations. Unfortunately, the wide variety of
+line profile shapes and internal trough structure 
+tends to `wash out' BAL troughs to the extent that they do not 
+resemble typical BALQSOs.
+Because of this, we instead use compare to a {\sl Hubble Space Telescope} 
+STIS spectrum of the high BALnicity BALQSO PG0946+301 (Arav et al. 2000),
+and an SDSS spectrum of the LoBAL quasar XXXXX (REF),
+for the angles of $73^\circ$ and $76^\circ$, respectively. 
 We show a cartoon illustrating how geometric effects determine
@@
 in a polar direction above the disc.  
+% {\bf KSL: it sounds like what you are suggesting is a low density inner flow, our domain 2 stuff actually permits ...
+or indeed one might be able to produce this within SV is you adopted a different mass loss with radius assumption.
+JM: I am being deliberately
+% vague about what I am suggesting. I am saying there are three physical
+% possibilities: either wind itself causes this scattering contribution, which doesn't happen in our model, or you have partial covering, or you have some additional scatterer.}
 
@@
 crucially important in determining the emergent line ratios.  
+% {\bf KSL: This is a bit oddly explained. Our problem is at low inclination.  Note that I am a bit concerned with Fig 3; the model spectra and the observations look very different.}
 
@@
 of BALQSOs.
+
+% {\bf I have to say I find this hard to understand.
+Are you trying to say that in CVs which we are know are thin disks with winds, the EW of the red-wing of emission lines increases with inclination angle ...
+which I think may be true, and so one would expect that in a unification model for AGN  it should do the same?
+And the fact that it does not, suggests that something else is going on in AGN.
+I also still think that you should move this discussion later in the paper and not bury it here.}
 
@@
 
-The work of JHM, SWM, NSH and CKL is supported by the
+The work of JHM, SWM, NSH and CK is supported by the
 Science and Technology Facilities Council (STFC),

### 2015-12-08 paper.tex
about to change order

@@
 X-ray ($2$~keV) luminosity of the our clumped model (red squares) 
-and the H13 model (purple squares), plotted against monochromatic luminosity 
+and the H13 model (blue squares), plotted against monochromatic luminosity 
 at 2500\AA. The points are labeled according to inclination; angles
 $>70^\circ$ correspond to BALs in our scheme (see figure 4).
-Also plotted are the samples considered by Saez et al. 2012 on a similar plot; 
-The COMBI-7 AGN and the BQS samples Steffen et al. (2006) and the Saez et al. (2012) 
+Also plotted are masurements from 
+the COMBI-7 AGN and the BQS samples (Steffen et al. 2006) and the Saez et al. (2012) 
 sample of BALQSOs. The dotted line shows the best fit relation for non-BALQSOs 

### 2015-12-08 paper_mnras.tex
still working

@@
 
-% {\bf I have to say I find this hard to understand.
+% % {\bf I have to say I find this hard to understand.
 Are you trying to say that in CVs which we are know are thin disks with winds, the EW of the red-wing of emission lines increases with inclination angle ...
@@
 inferences are fraught with complex selection effects.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% DISCUSSION???
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2015-12-09 paper.tex
still working
reordered paper

@@
 \def\heii{He~\textsc{ii}}
+\def\heiiline{He~\textsc{ii}~$4686$\AA}
 \def\mg{Mg~\textsc{ii}}
@@
 \citep{goodrich1995, cohen1995}, although there is also evidence
-for polar BAL outflows  in radio-loud (RL) sources \citep{zhou2006}.
+for polar BAL outflows  in radio-loud (RL) sources \citep{zhou2006,ghoshpunsly2007}.
 % although this geometry is contradicted
@@
 may see a BALQSO or normal `Type 1' quasar.
-Within this {\em geoemtric unification} framework, the broad-line region (BLR) can 
+Within this {\em geometric unification} framework, the broad-line region (BLR) can 
 correspond either to the dense wind base or clumps embedded
@@
 
-\subsection{Ionization treatment}
+\subsection{Ionization and Excitation Treatment}
 
@@
 MC rate estimators as described by Lucy (2002,2003). 
-Previously (LK02, H13, M15), we used a modified Saha approach to calculate the ionization fractions
-of simple-ions. As part of  this effort, we have now improved {\sc PYTHON} to explicitly solve the 
+Previously (LK02, H13, M15), we used a modified Saha approach to 
+calculate the ionization fractions
+of simple-ions. As part of  this effort, we have 
+now improved {\sc PYTHON} to explicitly solve the 
 rate equations between ions in non-LTE. This dispenses with a number of small assumptions 
@@
 This allows the calculation of a photoionization rate estimator. Ion abundances are
-then calculated by solving the rate equations between ions. We include collisional ionization
-and photoionization balanced with radiative, 
+then calculated by solving the rate equations between ions. We include collisional ionization and photoionization balanced with radiative, 
 dielectronic and collisional (three-body) recombination.
 As in M15, we use a dilute Boltzmann approximation to calculate 
-the population of levels for simple-ions. We stress that this approximation 
-is not required for ions treated as macro-atoms. 
+the populations of levels for simple-ions. We stress that this approximation 
+is not required for macro-atom levels. 
 % \begin{equation}
@@
 
-\subsection{The Simulation Grid: Arriving at a next-generation model}
+\subsection{The Simulation Grid}
+% Arriving at a next-generation model}
 
@@
 quasar of $10^9M_\odot$ and an eddington fraction of $0.2$; see section~\ref{sec:xray}).
+
 We then evaluated these models based on the following criteria:
@@
 \item Does the model avoid over-ionization and thus produce UV absorption lines 
-with $BI > 0$ at $\sim20\%$ of viewing angles?
-\item Do the synthetic spectra show  line emission emerge at low inclinations, with $EW\sim40\AA$ in \civ?
-\item Do H recombination lines appear in the spectra, $EW\sim50\AA$ in \la?
-\item Do the spectra  produce LoBAL features at a  small subset of BAL angles?
+with $BI > 0$ at $\sim20\%$ of viewing angles (e.g. Knigge et al. 2010)?
+\item Do the synthetic spectra show  line emission emerge at low inclinations, with $EW\sim40\AA$ in \civ \citep[e.g. ][]{shen2011}?
+\item Do H recombination lines appear in the spectra, $EW\sim50\AA$ in \la 
+\citep[e.g. ][]{dipompeo2012}?
+\item Do the spectra produce \mg\ and \al\ (LoBAL) absorption 
+features with $BI > 0$ at a small subset of BAL angles?
 \item Does the model spectra resemble quasar composite spectra?
 \end{itemize}
-In the next section, we present one of the most promising models and discuss
+Where $BI$ is the `Balnicity Index' (Weymann et al. 1991), given by
+\begin{equation}
+BI = \int^{25000}_{3000} \left( 1 - \frac{f(v)}{0.9} \right) dv.
+\end{equation}
+The constant $C=0$ everywhere, unless the normalized flux
+has satisfied $f(v)<0.9$ continuously for at least $2000$~km~s$^{−1}$, 
+whereby $C$ is set to $1$.
+
+In the next section, we present one of the most promising models,
+which we refer to as the fiducial model, and discuss
 the various successes and failures with respect to the above criteria.
@@
 
-\section{Results and Discussion}
-
-Here we describe the results from our next-generation model,
+\section{Results From A Fiducial Model}
+
+Here we describe the results from an fiducial model,
 and discuss these results in the context of the criteria 
@@
 the X-ray properties of this particular model to samples of
-quasars and luminous AGN. We also examine trends with inclination in the synthetic spectra, 
-both in terms of the range of ionization states of the absorption lines and equivalent widths 
-of the emission lines.
+quasars and luminous AGN. 
+% We also examine trends with inclination in the synthetic spectra, 
+% both in terms of the range of ionization states of the absorption lines and equivalent widths of the emission lines.
 
@@
 
-\begin{figure*} %fullpage
+\begin{figure} %fullpage
 \centering
@@
 intersect material of different ionization states.
-The line luminosities represent the luminosity of photons
+The line luminosities, $L$, represent the luminosity of photons
 escaping the Sobolev region for each line. These photons do not
@@
 \label{fig:wind}
-\end{figure*} %fullpage
+\end{figure} %fullpage
 
@@
 This explains why a factor of 100 increase in X-ray luminosity requires
-a clumping factor of 0.01, even though the value of $U_H$ decreases by only a factor of $\sim10$ 
-compared to H13. 
+a clumping factor of 0.01, even though the value of $U_H$ decreases by only a factor of $\sim10$ compared to H13. 
 %This is also the reason for significant Lyman edge photoabsorption
@@
 
-Clumping also causes the total line luminosity to increase dramatically,
-as recombination and collisional excitation are both proportional to
-density squared. This line emission typically emerges on the edge of the wind
+The total line luminosity also increases dramatically compared to H13. 
+This is due to heating of the plasma by the increased the increased X-ray 
+luminosity heating the plasma, while clumping prevents over-ionization.
+This line emission typically emerges on the edge of the wind
 nearest the central source. The location of the line emitting regions
-is dependent on the ionization state, as well as the X-rays heating the plasma.
+is dependent on the ionization state, as well as the incident X-rays.
 The radii of these emitting regions is important,
-and can be compared to observations. The line luminosities 
+and can be compared to observations. The line luminosities, $L$,
 shown in the figure correspond to the luminosity in $\LUM$ of photons
 escaping the Sobolev region for each line. 
-This is equivalent to $\beta_{ul} n_u A_{ul}$, where the three quantities
-represent the Sobolev escape probability, upper level number density and 
-Einstein A coefficient for the line. 
+% This is equivalent to $\beta_{ul} n_u A_{ul}$, where the three quantities
+% represent the Sobolev escape probability, upper level number density and 
+% Einstein A coefficient for the line. 
 As shown in figure~\ref{fig:wind},
@@
 \label{fig:uvspec}
-\end{figure*} %fullpage
+\end{figure} %fullpage
 
@@
 
-Non-black saturation is observed in the absorption troughs of BALQSOs \citep{arav1999a,arav1999b}.
+Non-black saturation is observed in the absorption troughs of BALQSOs \citep{arav1999b,arav1999}.
 This is usually explained either as  partial covering of the continuum
@@
 a partial covering absorber. To allow this, an alternative approach
-such as {\em macroclumping} would be required \citep[e.g.][]{surlan2012,hamann2008}.
+such as {\em macroclumping} would be required \citep[e.g.][]{hamann2008,surlan2012}.
 Second, our wind does not have a significant scattering 
@@
 \subsubsection{Broad emission lines (`quasar-like' angles)}
-
-\begin{figure*} %fullpage
-\centering
-\includegraphics[width=1.0\textwidth]{figures/ew.png}
-\caption
-{
-Physical properties of the outflow, shown by the coloured contours.
-The solid black line marks a sphere at $1000~r_G$.
-The dotted lines show the $72^\circ$ and $78^\circ$ sightlines 
-to the centre of the system, and illustrate that different sightlines
-intersect material of different ionization states.
-}
-\label{fig:ew}
-\end{figure*} %fullpage
 
@@
 
-\subsubsection{The Angular Distribution of Line And Continuum Emission}
-\label{{sec:angular}}
-
-In order to quantitatively assess how emission lines change with 
-inclination when blue-shifted absorption 
-may affect the line profile, we define the `red wing equivalent width' ($W_{\lambda,RW}$) as
-\begin{equation}
-W_{\lambda,RW} = \int_{\lambda_0}^{\lambda^\prime} \left( 1 - \frac{F_\lambda}{F_0} \right) d\lambda
-\label{rwew}
-\end{equation}
-where $F_0$ is the continuum flux and the integral is calculated from $\lambda_0$, line centre,
-to a wavelength $\lambda^\prime$ where the flux has returned to the continuum level.
-This quantity is shown as a function of inclination in figure 5 for the \civ\ and \mg\ UV lines.
-We also plot show the $W_{\lambda,RW}$ expected from isotropic line emission and a foreshortened 
-and limb darkened disc  as well as $1/2$ equivalent widths from \cite{dipompeo2012b}.
-
-BALQSOs and quasars generally possess very similar emission line properties 
-\citep[e.g.][]{weymann1991,reichard2003}. 
-Clearly, the variation with inclination in our models is far greater than 
-than the variation between, and standard deviation within, quasar and BALQSO samples.  
-This presents a challenge to our model, as well as the geometric unification picture in general.
-One obvious potential solution is to hypothesize a more isotropic distribution 
-for the emergent condition than predicted by a classical thin disc. 
-General relativistic effects -- specifically, light bending
-and relativistic beaming -- can cause 
-the accretion disc SED to become more isotropic \citep[e.g.][]{zhang1997,munozdarias2013}. 
-However, we have verified using AGNSPEC \citep{hubeny2000,hubeny2001,hubenyhubeny1997}
-that this effect is small in the UV and optical wavelength regimes, 
-and the disc is still anisotropic.
-
-Reprocessing by an extended outflow may also cause a more isotropic
-continuum to emerge. Hints that light scattered off a spatially extended 
-wind may contribute signiciantly to the emergent continuum come from radiative transfer
-simulations \citep{simproga2012} and microlensing observations \citep{sluse2015}.
-However, neither of these examples have sufficient reprocessing efficiencies to 
-compensate for the disc anisotropy in this case.
-An alternative explanation is that the BLR has the same angular distribution 
-of emission as the accretion disc.
-Indeed, \cite{risaliti2011} find that EW distributions in quasars are consistent with anisotropic emission 
-from optically thick, disc-like structures for {\em both} the continuum source and BLR. 
-If this is the case, it has a dramatic affect on the intrinsic
-BAL fraction inferred from flux-limited samples \citep{goodrich1997,krolikvoit1998}.
-
-It is also possible that the equatorial paradigm invoked from early polarisation
-studies \citep{goodrich1995, cohen1995,brotherton2006} 
-is an over-simplification, or is incorrect. 
-High brightness temperatures in some RL BALQSOs imply polar outflows \citep{zhou2006} 
-and \cite{bruni2012} find that
-RL BALQSOs possess similar radio spectral indices to normal RL quasars, 
-suggestive of comparable inclinations. 
-In addition, \cite{marin2013} find a bending angle of $\sim45^\circ$ is required to 
-explain the polarisation dichotomy of type 1 and 2 AGN using an Elvis-type wind 
-model (Elvis 2000). It is therefore possible 
-that type 1 quasars and BALQSOs are generally viewed from a fairly narrow range of angles 
-($\sim0$-$45^\circ$), or that {\em both} evolutionary and geometric explanations are required.
-We suggest that future modelling should include predictions of polarisation signatures
-from a detailed radiative transfer simulation, allowing direct comparison with spectropolarimetry
-of BALQSOs.
-
 % {\bf I have to say I find this hard to understand.
@@
 \label{fig:xray}
-\end{figure*} %fullpage
+\end{figure} %fullpage
 
@@
 it is also important to assess whether the X-ray properties of this
-next-generation model agree well with quasar and BALQSO samples for the relevant
+fiducial model agree well with quasar and BALQSO samples for the relevant
 inclinations.
@@
 is also shown. For low inclination, `quasar-like' viewing angles,
-we now find excellent agreement with AGN samples. The gradient from $20^\circ$ to
+we now find excellent agreement with AGN samples. The slight gradient from $20^\circ$ to
 $60^\circ$ in our models is caused by a combination of disc foreshortening/limb-darkening 
@@
 
-Our models slightly over-predict the emergent X-ray luminosity at BAL angles, 
-although we are limited by poor sample sizes. 
-% It is possible that this is due to our wind being overly optically thick to 
-% electron scattering at angles which look through the wind. 
-If BALQSOs were {\em intrinsically} 
-X-ray weak \citep[as suggested by, e.g.][]{morabito2013},
-our isotropic assumption for the X-ray source would be incorrect. 
-A polar-biased X-ray source would result in a lower clumping factor being
-required in our model. Our specific wind
-prescription will also affect the opacities, densities and resultant
-ionization structure, which can change the absorption characteristics and resultant
-luminosities.
-Nevertheless, our input X-ray spectrum
-now reproduces the X-ray properties of a luminous quasar as an output,
-and at least some BAL angles match the observations.
-This satisifies the first-order requirement for the X-ray properties of 
-a unified quasar model.
+% JM XXX -- only include this if it's true!
+% Our models slightly over-predict the emergent X-ray luminosity at BAL angles, 
+% although we are limited by poor sample sizes. 
+% % It is possible that this is due to our wind being overly optically thick to 
+% % electron scattering at angles which look through the wind. 
+% If BALQSOs were {\em intrinsically} 
+% X-ray weak \citep[as suggested by, e.g.][]{morabito2013},
+% our isotropic assumption for the X-ray source would be incorrect. 
+% A polar-biased X-ray source would result in a lower clumping factor being
+% required in our model. Our specific wind
+% prescription will also affect the opacities, densities and resultant
+% ionization structure, which can change the absorption 
+% characteristics and resultant luminosities.
+% Nevertheless, our input X-ray spectrum
+% now reproduces the X-ray properties of a luminous quasar as an output,
+% and at least some BAL angles match the observations.
+% This satisifies the first-order requirement for the X-ray properties of 
+% a unified quasar model.
 
@@
 \label{fig:lobal}
-\end{figure*} %fullpage
+\end{figure} %fullpage
 
@@
 FeLoBAL quasars, due to a foreshortened and attenuated continuum, 
-although, as noted in section~\ref{discsed}, BAL fraction 
+although, as noted in section~\ref{angular}, BAL fraction 
 inferences are fraught with complex selection effects.
@@
 
+% DISCUSSION???
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+ \section{Discussion: Parameter Sensitivity and Inclination Dependence}
+
+ We have demonstrated that our fiducial model successfully reproduces much of
+ the phenomenology of luminous AGN and quasars, with a few exceptions.
+ Here, we discuss these shortcomings, by discussing parameter sensitivity
+ and the dependence of line EWs on inclination.
+
+\subsection{The Angular Distribution of Line And Continuum Emission}
+\label{sec:angular}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.45\textwidth]{figures/ew.png}
+\caption
+{
+$W_{\lambda,RW}$ as a function of inclination in our example model (red line).
+We also the mean $1/2$ equivalent width from DiPompeo et al. (2012) as a horizontal
+line, with the shaded area corresponding to the standard deviation.
+}
+\label{fig:ew}
+\end{figure}
+
+In order to quantitatively assess how emission lines change with 
+inclination when blue-shifted absorption 
+may affect the line profile, we define the `red wing equivalent width' ($W_{\lambda,RW}$) as
+\begin{equation}
+W_{\lambda,RW} = \int_{\lambda_0}^{\lambda^\prime} \left( 1 - \frac{F_\lambda}{F_0} \right) d\lambda
+\label{rwew}
+\end{equation}
+where $F_0$ is the continuum flux and the integral is calculated from $\lambda_0$, line centre,
+to a wavelength $\lambda^\prime$ where the flux has returned to the continuum level.
+This quantity is shown as a function of inclination in figure 5 for the \civ\ and \mg\ UV lines.
+We also show the $W_{\lambda,RW}$ expected from isotropic line emission and a foreshortened 
+and limb darkened disc  as well as $1/2$ equivalent widths from \cite{dipompeo2012b}.
+
+BALQSOs and quasars generally possess very similar emission line properties 
+\citep[e.g.][]{weymann1991,reichard2003}. 
+Clearly, the variation with inclination in our models is far greater than 
+than the variation between, and standard deviation within, quasar and BALQSO samples.  
+This presents a challenge to our model, as well as the geometric unification picture in general.
+One obvious potential solution is to hypothesize a more isotropic distribution 
+for the emergent condition than predicted by a classical thin disc. 
+General relativistic effects -- specifically, light bending
+and relativistic beaming -- can cause 
+the accretion disc SED to become more isotropic \citep[e.g.][]{zhang1997,munozdarias2013}. 
+However, we have verified using AGNSPEC \citep{hubeny2000,hubeny2001,hubenyhubeny1997}
+that this effect is small in the UV and optical wavelength regimes, 
+and the disc is still anisotropic.
+
+Reprocessing by an extended outflow may also cause a more isotropic
+continuum to emerge. Hints that light scattered off a spatially extended 
+wind may contribute signiciantly to the emergent continuum come from radiative transfer
+simulations \citep{simproga2012} and microlensing observations \citep{sluse2015}.
+However, neither of these examples have sufficient reprocessing efficiencies to 
+compensate for the disc anisotropy in this case.
+An alternative explanation is that the BLR has the same angular distribution 
+of emission as the accretion disc.
+Indeed, \cite{risaliti2011} find that EW distributions in quasars 
+are consistent with anisotropic emission 
+from optically thick, disc-like structures for {\em both} the continuum source and BLR. 
+If this is the case, it has a dramatic affect on the intrinsic
+BAL fraction inferred from flux-limited samples \citep{goodrich1997,krolikvoit1998}.
+
+It is also possible that the equatorial paradigm invoked from early polarisation
+studies \citep{goodrich1995, cohen1995,brotherton2006} 
+is an over-simplification, or is incorrect. 
+High brightness temperatures in some RL BALQSOs imply polar outflows \citep{zhou2006} 
+and \cite{bruni2012} find that
+RL BALQSOs possess similar radio spectral indices to normal RL quasars, 
+suggestive of comparable inclinations. 
+In addition, \cite{marin2013} find a bending angle of $\sim45^\circ$ is required to 
+explain the polarisation dichotomy of type 1 and 2 AGN using an Elvis-type wind 
+model (Elvis 2000). It is therefore possible 
+that type 1 quasars and BALQSOs are generally viewed from a fairly narrow range of less
+equatorial angles ($\sim0$-$45^\circ$), or that {\em both} 
+evolutionary and geometric explanations are required.
+We suggest that future modelling should include predictions of polarisation signatures
+from a detailed radiative transfer simulation, allowing direct 
+comparison with spectropolarimetry of BALQSOs.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 % SUMMARY
@@
 
-\section{Summary}
+\section{Summary And Conclusions}
 
@@
 We find the following main points:
-
 \begin{enumerate}
-\item We have introduced a first-order treatment 
-of clumping in our model, and found that it can now maintain
-the required ionization state while agreeing well with the X-ray
-properties of AGN/QSOs.
+\item We have introduced a simple treatment 
+of clumping in our model, and found that it moderates the ionizaiton state
+sufficiently to allow for the 
+formation of strong UV BALs while agreeing well with the X-ray
+properties of luminous AGN and quasars. 
 \smallskip
-\item We have shown that the degree of ionization stratification
-in the model is sufficient that LoBAL line profiles
-are seen at a subset of viewing angles, and Fe~\textsc{ii}
+\item We find that a clumpy outflow model naturally 
+reproduces the range of ionization states
+expected in quasars, due to it's stratified density
+and temperature structure. 
+LoBAL line profiles are seen at a subset of viewing angles, and Fe~\textsc{ii}
 absorption is seen at particularly high inclinations.
 \smallskip
-\item We find that clumping also causes a significant 
+\item We find that the higher X-ray luminosity 
+causes a significant 
 increase in the strength of the  emission
@@
 of collisionally excited resonance lines (such as \civ, \nv)
-and recombination lines (such as \la, \ha\ and the Balmer series).
+and recombination lines (such as \la\ and \heiiline).
 \smallskip
@@
 fails to reproduce this behaviour.
-This is due to a fundamental constraint discussed further in section~\ref{sec:angular}. If the BLR
-emits fairly isotropically then for a foreshortened, limb-darkened classical thin accretion disc
-it is simply not possible to achieve line ratios at low inclinations that are comparable to
-those at high inclinations. This is a robust conclusion which 
-is independent of the assumed BLR geometry and size.
+This is due to a fundamental constraint discussed further in 
+section~\ref{sec:angular}. If the BLR emits fairly isotropically then for a 
+foreshortened, limb-darkened accretion disc 
+it is simply not possible to achieve line ratios at low inclinations 
+that are comparable to those at high inclinations. 
+Furthermore, this is conclusion is independent of the assumed 
+BLR geometry and size.
 \end{enumerate}
@@
 model, and suggests that a simple biconical geometry such as this can come close to 
-explaining much of the  phenomenology of quasars. Nevertheless, our conclusions pose 
-a clear challenge to the current disc wind unification picture.
+explaining much of the  phenomenology of quasars. However, our conclusions pose 
+a clear challenge to a picture in which BALQSOs are
+explained by an equatorial wind rising from a classical thin disc. 
+We suggest that obtaining reliable observational orientation indicators and 
+exploring alternative outflow geometries in simulations
+are obvious avenues for exploration.
 

### 2015-12-09 paper_mnras.tex
reordered paper

--- 2015-12-08 paper_mnras.tex
@@
 \item Does the model avoid over-ionization and thus produce UV absorption lines 
-with $BI > 0$ at $\sim20\%$ of viewing angles?
-\item Do the synthetic spectra show  line emission emerge at low inclinations, with $EW\sim40\AA$ in \civ?
-\item Do H recombination lines appear in the spectra, $EW\sim50\AA$ in \la?
-\item Do the spectra  produce LoBAL features at a  small subset of BAL angles?
+with $BI > 0$ at $\sim20\%$ of viewing angles (e.g. Knigge et al. 2010)?
+\item Do the synthetic spectra show  line emission emerge at low inclinations, with $EW\sim40\AA$ in \civ \citep[e.g. ][]{shen2011}?
+\item Do H recombination lines appear in the spectra, $EW\sim50\AA$ in \la 
+\citep[e.g. ][]{dipompeo2012}?
+\item Do the spectra produce \mg\ and \al\ (LoBAL) absorption 
+features with $BI > 0$at a small subset of BAL angles?
 \item Does the model spectra resemble quasar composite spectra?
 \end{itemize}
+Where $BI$ is the `Balnicity Index' (Weymann et al. 1991), given by
+\begin{equation}
+BI = \int^{25000}_{3000} \left( 1 - \frac{f(v)}{0.9} \right) dv.
+\end{equation}
+The constant $C=0$ everywhere, unless the normalized flux
+has satisfied $f(v)<0.9$ continuously for at least $2000$~km~s$^{−1}$, 
+whereby $C$ is set to $1$.
 In the next section, we present one of the most promising models and discuss
@@
 
-\section{Results and Discussion}
-
-Here we describe the results from our next-generation model,
+\section{Results From An Example Model}
+
+Here we describe the results from an example model,
 and discuss these results in the context of the criteria 
@@
 
-\begin{figure*} %fullpage
+\begin{figure*}
 \centering
@@
 \label{fig:wind}
-\end{figure*} %fullpage
+\end{figure*}
 
@@
 \label{fig:uvspec}
-\end{figure*} %fullpage
+\end{figure*}
 
@@
 \label{fig:xray}
-\end{figure*} %fullpage
+\end{figure*}
 
@@
 it is also important to assess whether the X-ray properties of this
-next-generation model agree well with quasar and BALQSO samples for the relevant
+example model agree well with quasar and BALQSO samples for the relevant
 inclinations.
@@
 \label{fig:lobal}
-\end{figure*} %fullpage
+\end{figure*}
 
@@
 
+% DISCUSSION???
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+ \section{Discussion: Parameter Sensitivity and Inclination Dependence}
+
+ We have demonstrated that our example model successfully reproduces much of
+ the phenomenology of luminous AGN and quasars, with a few exceptions.
+ Here, we discuss these shortcomings, by discussing parameter sensitivity
+ and the dependence of line EWs on inclination.
+
+\subsection{The Angular Distribution of Line And Continuum Emission}
+\label{sec:angular}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.45\textwidth]{figures/ew.png}
+\caption
+{
+$W_{\lambda,RW}$ as a function of inclination in our example model (red line).
+We also the mean $1/2$ equivalent width from DiPompeo et al. (2012) as a horizontal
+line, with the shaded area corresponding to the standard deviation.
+}
+\label{fig:ew}
+\end{figure}
+
+In order to quantitatively assess how emission lines change with 
+inclination when blue-shifted absorption 
+may affect the line profile, we define the `red wing equivalent width' ($W_{\lambda,RW}$) as
+\begin{equation}
+W_{\lambda,RW} = \int_{\lambda_0}^{\lambda^\prime} \left( 1 - \frac{F_\lambda}{F_0} \right) d\lambda
+\label{rwew}
+\end{equation}
+where $F_0$ is the continuum flux and the integral is calculated from $\lambda_0$, line centre,
+to a wavelength $\lambda^\prime$ where the flux has returned to the continuum level.
+This quantity is shown as a function of inclination in figure 5 for the \civ\ and \mg\ UV lines.
+We also show the $W_{\lambda,RW}$ expected from isotropic line emission and a foreshortened 
+and limb darkened disc  as well as $1/2$ equivalent widths from \cite{dipompeo2012b}.
+
+BALQSOs and quasars generally possess very similar emission line properties 
+\citep[e.g.][]{weymann1991,reichard2003}. 
+Clearly, the variation with inclination in our models is far greater than 
+than the variation between, and standard deviation within, quasar and BALQSO samples.  
+This presents a challenge to our model, as well as the geometric unification picture in general.
+One obvious potential solution is to hypothesize a more isotropic distribution 
+for the emergent condition than predicted by a classical thin disc. 
+General relativistic effects -- specifically, light bending
+and relativistic beaming -- can cause 
+the accretion disc SED to become more isotropic \citep[e.g.][]{zhang1997,munozdarias2013}. 
+However, we have verified using AGNSPEC \citep{hubeny2000,hubeny2001,hubenyhubeny1997}
+that this effect is small in the UV and optical wavelength regimes, 
+and the disc is still anisotropic.
+
+Reprocessing by an extended outflow may also cause a more isotropic
+continuum to emerge. Hints that light scattered off a spatially extended 
+wind may contribute signiciantly to the emergent continuum come from radiative transfer
+simulations \citep{simproga2012} and microlensing observations \citep{sluse2015}.
+However, neither of these examples have sufficient reprocessing efficiencies to 
+compensate for the disc anisotropy in this case.
+An alternative explanation is that the BLR has the same angular distribution 
+of emission as the accretion disc.
+Indeed, \cite{risaliti2011} find that EW distributions in quasars 
+are consistent with anisotropic emission 
+from optically thick, disc-like structures for {\em both} the continuum source and BLR. 
+If this is the case, it has a dramatic affect on the intrinsic
+BAL fraction inferred from flux-limited samples \citep{goodrich1997,krolikvoit1998}.
+
+It is also possible that the equatorial paradigm invoked from early polarisation
+studies \citep{goodrich1995, cohen1995,brotherton2006} 
+is an over-simplification, or is incorrect. 
+High brightness temperatures in some RL BALQSOs imply polar outflows \citep{zhou2006} 
+and \cite{bruni2012} find that
+RL BALQSOs possess similar radio spectral indices to normal RL quasars, 
+suggestive of comparable inclinations. 
+In addition, \cite{marin2013} find a bending angle of $\sim45^\circ$ is required to 
+explain the polarisation dichotomy of type 1 and 2 AGN using an Elvis-type wind 
+model (Elvis 2000). It is therefore possible 
+that type 1 quasars and BALQSOs are generally viewed from a fairly narrow range of less
+equatorial angles ($\sim0$-$45^\circ$), or that {\em both} 
+evolutionary and geometric explanations are required.
+We suggest that future modelling should include predictions of polarisation signatures
+from a detailed radiative transfer simulation, allowing direct 
+comparison with spectropolarimetry of BALQSOs.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 % SUMMARY

### 2015-12-15 paper.tex
about to shorten angular distribution discussion

@@
 % clumpy winds and broad emission lines
-Testing Quasar Unification with Clumpy Wind Models
+Testing Quasar Unification: I. Radiative Transfer in Clumpy Winds
 %Unifying quasars with clumpy wind models
@@
 from the anisotropy of emission from a classical thin disc. 
-Overall, our work suggests that geometric unification
+Overall, our work suggests that BAL outflows can produce significant broad emission
+lines and that accretion disc winds naturally reproduce the range of
+ionization states seen in AGN.
+This suggests that geometric unification
 involving an accretion disc wind is a promising scenario, but our results 
-pose a number of difficult challenges to models in which an equatorial outflow
+pose a specific challenge to models in which an equatorial outflow
 rises from a limb-darkened, foreshortened accretion disc.
@@
 
-Our previous modelling efforts, we have assumed a smooth outflow, 
+In our previous modelling efforts, we have assumed a smooth outflow, 
 in which the density at a given point was determined only by the 
@@
 {\em clumpy}, rather than smooth, and probably on a variety of scales. 
+A clumpy outflow offers a possible solution to the so-called `over-ionization problem' in 
+quasar and AGN outflows \citep{hamann2013}. This is the main motivation for incorporating 
+clumping into our model.
+
 Implementing a treatment of clumping is challenging, for
@@
 % {\bf KSL: Reverse the order of these difficulties.  The most important is that it is not clear what kind of clumping an AGN wind has; the computational problem is a secondary one JM: Done..}
-
-Given the lack of knowledge about the actual type of clumping, we have adopt a simple approximation
+Given the lack of knowledge about the actual type of clumping, we have adopted
+a simple approximation
 used successfully in stellar wind modelling, known as 
-{\em microclumping} \citep{hamann1998,hamann2008}(MORE REFS), 
-which minimizes the computational difficulties. 
-The underlying assumption in microclumping is that clump sizes are much smaller than the 
+{\em microclumping} \citep[e.g.][]{hamann1998,hilliermiller1999,hamann2008}. 
+The underlying assumption of microclumping is that clump sizes are much smaller than the 
 typical photon mean free path, and thus the clumps are 
@@
 enhanced density in the clump. The resultant effect is that, {\em for fixed temperature},
- processes that are {\em linear} in density, such as electron scattering, are unchanged, 
-as $f_V$ and $D$ will cancel out. However, any quantity that scales with the {\em square} of density, 
+ processes that are linear in density, such as electron scattering, are unchanged, 
+as $f_V$ and $D$ will cancel out. However, any quantity that scales with the square of density, 
 such as collisional excitation or recombination, will increase by a factor of $D$.
-However, in the event that one of these
-
-Clumping the wind has an important effect on the ionization state and has
-been proposed as a solution to the so-called `over-ionization problem' in 
-disc winds \citep{hamann2013}. This is the main motivation for incorporating microclumping
-into our model. This treatment is necessarily simple; it does not adequately
+In our models, the temperature is not fixed, and is instead set by balancing heating and 
+cooling in a given cell. In the presence of an X-ray source, this thermal balance is 
+generally dominated by bound-free heating and line cooling. The main effect of including 
+clumping in our modelling is that it moderates the ionization state due to the increased 
+density. This allows an increase in the ionizing luminosity, amplifying the amount of
+bound-free heating and also increasing the competing line cooling term
+(thermal line emission).
+
+This treatment is necessarily simple; it does not adequately
 represent the complex substructures and stratifications in ionization
@@
 line emission.
+
+% is that it moderates the ionization state and temperature structure of the plasma
+
+% Clumping the wind has an important effect on the ionization state and has
+% been proposed as a solution to the so-called `over-ionization problem' in 
+% disc winds \citep{hamann2013}. This is the main motivation for incorporating microclumping
+% into our model. This treatment is necessarily simple; it does not adequately
+% represent the complex substructures and stratifications in ionization
+% state we expect in AGN outflows. Nevertheless, this parameterization allows simple estimates
+% of the effect clumping might have on the ionization state and emergent 
+% line emission.
 % It is also encouraging that microclumping has been used 
@@
 
-We then evaluated these models based on the following criteria:
+We then evaluated these models based on whether their synthetic spectra exhibited the 
+following properties of quasars and BALQSOs:
+
 \begin{itemize}
-\item Does the model avoid over-ionization and thus produce UV absorption lines 
-with $BI > 0$ at $\sim20\%$ of viewing angles (e.g. Knigge et al. 2010)?
-\item Do the synthetic spectra show  line emission emerge at low inclinations, with $EW\sim40\AA$ in \civ \citep[e.g. ][]{shen2011}?
-\item Do H recombination lines appear in the spectra, $EW\sim50\AA$ in \la 
-\citep[e.g. ][]{dipompeo2012}?
-\item Do the spectra produce \mg\ and \al\ (LoBAL) absorption 
-features with $BI > 0$ at a small subset of BAL angles?
-\item Does the model spectra resemble quasar composite spectra?
+\item UV absorption lines 
+with $BI > 0$ at $\sim20\%$ of viewing angles (e.g. Knigge et al. 2010)
+\item Line emission emerging at low inclinations, with $EW\sim40\AA$ in \civ\ \citep[e.g. ][]{shen2011}
+\item H recombination lines with $EW\sim50\AA$ in \la\ \citep[e.g. ][]{shen2011}
+\item  \mg\ and \al\ (LoBAL) absorption features with $BI > 0$ at a small subset of BAL angles
+\item Verisimilitude with quasar composite spectra.
 \end{itemize}
@@
 whereby $C$ is set to $1$.
+
+% the following criteria:
+% \begin{itemize}
+% \item Do the synthetic spectra exhibit UV absorption lines 
+% with $BI > 0$ at $\sim20\%$ of viewing angles (e.g. Knigge et al. 2010)?
+% \item Do the synthetic spectra show  line emission emerge at low inclinations, with $EW\sim40\AA$ in \civ \citep[e.g. ][]{shen2011}?
+% \item Do H recombination lines appear in the spectra, $EW\sim50\AA$ in \la 
+% \citep[e.g. ][]{shen2011}?
+% \item Do the spectra produce \mg\ and \al\ (LoBAL) absorption 
+% features with $BI > 0$ at a small subset of BAL angles?
+% \item Does the model spectra resemble quasar composite spectra?
+% \end{itemize}
+% Where $BI$ is the `Balnicity Index' (Weymann et al. 1991), given by
+% \begin{equation}
+% BI = \int^{25000}_{3000} \left( 1 - \frac{f(v)}{0.9} \right) dv.
+% \end{equation}
+% The constant $C=0$ everywhere, unless the normalized flux
+% has satisfied $f(v)<0.9$ continuously for at least $2000$~km~s$^{−1}$, 
+% whereby $C$ is set to $1$.
 
@@
 \section{Results From A Fiducial Model}
-
-Here we describe the results from an fiducial model,
+Here we describe the results from a fiducial model,
 and discuss these results in the context of the criteria 
@@
 \begin{tabular}{p{3cm}p{4cm}}
-\hline Next-generation Model Parameters 	&	 Value \\ 
+\hline Fiducial Model Parameters 	&	 Value \\ 
 \hline \hline 
@@
 \caption{Wind geometry parameters 
-used in the model, as defined in the text and figure 1.
+used in the fiducial model, as defined in the text and figure 1.
 Parameters differing from the benchmark model of H13 are 
@@
 
+\noindent
 Figure~\ref{fig:wind} shows the physical properties of the wind.
@@
 The total line luminosity also increases dramatically compared to H13. 
-This is due to heating of the plasma by the increased the increased X-ray 
-luminosity heating the plasma, while clumping prevents over-ionization.
+This is due to heating of the plasma by the increased X-ray 
+luminosity, which avoids over-ionization due to clumping.
 This line emission typically emerges on the edge of the wind
@@
 
-Figure~\ref{fig:uvspec} shows the synthetic spectrum in the UV from our model. 
-To assess the ability of the model to match real 
+\noindent
+Figure~\ref{fig:uvspec} shows the synthetic spectrum in the UV from the fiducial model. 
+To assess the ability of the synthetic spectra to match real 
 quasar spectra, we also show {\sl Sloan Digital Sky Survey} (SDSS) quasar
@@
 for low inclinations. Unfortunately, the wide variety of
-line profile shapes and internal trough structure 
-tends to `wash out' BAL troughs to the extent that they do not 
-resemble typical BALQSOs.
-Because of this, we instead use compare to a {\sl Hubble Space Telescope} 
+line profile shapes and internal trough structure in BALQSOs
+tends to `wash out' BAL troughs in composite spectra
+to the extent that BALQSO composites do not resemble typical BALQSOs.
+Because of this, we instead compare to a {\sl Hubble Space Telescope} 
 STIS spectrum of the high BALnicity BALQSO PG0946+301 (Arav et al. 2000),
@@
 
-\subsection{X-ray Properties and Broadband SEDs}
+\subsection{X-ray Properties}
 \label{sec:xray}
@@
 
-\subsection{LoBALs and ionization stratification}
+\subsection{LoBALs and Ionization Stratification}
 
@@
 \centering
-\includegraphics[width=0.45\textwidth]{figures/ew.png}
+\includegraphics[width=0.49\textwidth]{figures/hist_ew.png}
 \caption
 {
-$W_{\lambda,RW}$ as a function of inclination in our example model (red line).
-We also the mean $1/2$ equivalent width from DiPompeo et al. (2012) as a horizontal
-line, with the shaded area corresponding to the standard deviation.
+{\sl Top Panel:} A histogram of $1/2$ equivalent widths ($W_{\lambda}/2$)
+for BALQSOs and non-BAL quasars from the {\sl SDSS DR7} quasar sample (Shen et al. 2011).
+{\sl Bottom Panel:} $W_{\lambda,RW}$ as a function of inclination in our example model (black line).
+The green shaded area indicates viewing angles which look into the wind (`BALQSO-like').
 }
@@
 \end{figure}
+
+% \begin{figure}
+% \centering
+% \includegraphics[width=0.45\textwidth]{figures/ew.png}
+% \caption
+% {
+% $W_{\lambda,RW}$ as a function of inclination in our example model (red line).
+% We also the mean $1/2$ equivalent width from DiPompeo et al. (2012) as a horizontal
+% line, with the shaded area corresponding to the standard deviation.
+% }
+% \label{fig:ew}
+% \end{figure}
 
@@
 BALQSOs and quasars generally possess very similar emission line properties 
-\citep[e.g.][]{weymann1991,reichard2003}. 
-Clearly, the variation with inclination in our models is far greater than 
-than the variation between, and standard deviation within, quasar and BALQSO samples.  
-This presents a challenge to our model, as well as the geometric unification picture in general.
+\citep[e.g.][]{weymann1991,reichard2003}. This is illustrated in the 
+the top panel of figure~\ref{fig:ew}, which shows histograms 
+of \civ\ $1/2$ equivalent widths for BAL and non-BAL quasars from the {\sl SDSS DR7} quasar
+sample \citep{shen2011}. Clearly the variation in $W_{\lambda,RW}$ at 
+BAL-like and quasar-like angles is significantly larger than any systematic 
+differences between the quasar and BALQSO samples.
+The strong dependence of equivalent width on inclination is caused by decreased continuum
+levels at high inclinations. This is due to a combination of
+continuum attenuation through the wind, and the effect of limb darkening and foreshortening
+in our classical thin disc. This presents a challenge to a geometric unification model
+with an equatorial outflow.
+
+% Clearly, the variation with inclination in our models is far greater than 
+% than the variation between, and standard deviation within, quasar and BALQSO samples.  
+% This presents a challenge to our model, as well as the geometric unification picture in general.
 One obvious potential solution is to hypothesize a more isotropic distribution 
@@
 However, we have verified using AGNSPEC \citep{hubeny2000,hubeny2001,hubenyhubeny1997}
-that this effect is small in the UV and optical wavelength regimes, 
+that this effect is small in the UV wavelength regime, 
 and the disc is still anisotropic.
-
 Reprocessing by an extended outflow may also cause a more isotropic
@@
 compensate for the disc anisotropy in this case.
-An alternative explanation is that the BLR has the same angular distribution 
-of emission as the accretion disc.
+
+An alternative explanation is that the BLR has the same anisotropic 
+angular distribution of emission as the accretion disc.
 Indeed, \cite{risaliti2011} find that EW distributions in quasars 
@@
 that type 1 quasars and BALQSOs are generally viewed from a fairly narrow range of less
-equatorial angles ($\sim0$-$45^\circ$), or that {\em both} 
+equatorial angles ($\sim0$-$45^\circ$), or {\em both} 
 evolutionary and geometric explanations are required.

### 2015-12-15 paper_mnras.tex
about to shorten angular distribution discussion

@@
 
-We then evaluated these models based on the following criteria:
+We then evaluated these models based on whether their synthetic spectra exhibited the 
+following properties of quasars and BALQSOs:
+
 \begin{itemize}
-\item Does the model avoid over-ionization and thus produce UV absorption lines 
-with $BI > 0$ at $\sim20\%$ of viewing angles (e.g. Knigge et al. 2010)?
-\item Do the synthetic spectra show  line emission emerge at low inclinations, with $EW\sim40\AA$ in \civ \citep[e.g. ][]{shen2011}?
-\item Do H recombination lines appear in the spectra, $EW\sim50\AA$ in \la 
-\citep[e.g. ][]{dipompeo2012}?
-\item Do the spectra produce \mg\ and \al\ (LoBAL) absorption 
-features with $BI > 0$at a small subset of BAL angles?
-\item Does the model spectra resemble quasar composite spectra?
+\item UV absorption lines 
+with $BI > 0$ at $\sim20\%$ of viewing angles (e.g. Knigge et al. 2010)
+\item Line emission emerging at low inclinations, with $EW\sim40\AA$ in \civ\ \citep[e.g. ][]{shen2011}
+\item H recombination lines with $EW\sim50\AA$ in \la\ \citep[e.g. ][]{shen2011}
+\item  \mg\ and \al\ (LoBAL) absorption features with $BI > 0$ at a small subset of BAL angles
+\item Verisimilitude with quasar composite spectra.
 \end{itemize}
@@
 whereby $C$ is set to $1$.
-In the next section, we present one of the most promising models and discuss
+
+% the following criteria:
+% \begin{itemize}
+% \item Do the synthetic spectra exhibit UV absorption lines 
+% with $BI > 0$ at $\sim20\%$ of viewing angles (e.g. Knigge et al. 2010)?
+% \item Do the synthetic spectra show  line emission emerge at low inclinations, with $EW\sim40\AA$ in \civ \citep[e.g. ][]{shen2011}?
+% \item Do H recombination lines appear in the spectra, $EW\sim50\AA$ in \la 
+% \citep[e.g. ][]{shen2011}?
+% \item Do the spectra produce \mg\ and \al\ (LoBAL) absorption 
+% features with $BI > 0$ at a small subset of BAL angles?
+% \item Does the model spectra resemble quasar composite spectra?
+% \end{itemize}
+% Where $BI$ is the `Balnicity Index' (Weymann et al. 1991), given by
+% \begin{equation}
+% BI = \int^{25000}_{3000} \left( 1 - \frac{f(v)}{0.9} \right) dv.
+% \end{equation}
+% The constant $C=0$ everywhere, unless the normalized flux
+% has satisfied $f(v)<0.9$ continuously for at least $2000$~km~s$^{−1}$, 
+% whereby $C$ is set to $1$.
+
+In the next section, we present one of the most promising models,
+which we refer to as the fiducial model, and discuss
 the various successes and failures with respect to the above criteria.
@@
 
-\section{Results From An Example Model}
-
-Here we describe the results from an example model,
+\section{Results From A Fiducial Model}
+Here we describe the results from a fiducial model,
 and discuss these results in the context of the criteria 
@@
 it is also important to assess whether the X-ray properties of this
-example model agree well with quasar and BALQSO samples for the relevant
+fiducial model agree well with quasar and BALQSO samples for the relevant
 inclinations.
@@
 
- We have demonstrated that our example model successfully reproduces much of
+ We have demonstrated that our fiducial model successfully reproduces much of
  the phenomenology of luminous AGN and quasars, with a few exceptions.

### 2015-12-17 paper.tex
about to clean up

@@
 \title
-{
+[Testing Quasar Unification]{
 % Modelling quasar outflows:
 % clumpy winds and broad emission lines
-Testing Quasar Unification: I. Radiative Transfer in Clumpy Winds
+Testing Quasar Unification: Radiative Transfer in Clumpy Winds
 %Unifying quasars with clumpy wind models
@@
 Monte Carlo radiative transfer and photoionization code PYTHON.  
-Previously, we have shown that we could produce synthetic spectra resembling those of observed AGN for plausible wind models, but only if the X-ray luminosity was limited to about  10$^{43}$ erg s$^{-1}$.
-Here , we investigate the  degree to which  clumping of the outflow allows us to
-produce synthetic spectra in the rest-frame UV that have the characteristics of quasars with X-ray luminosities as large as 10$^{45}$ erg s$^{-1}$. 
-We conclude, perhaps not surprisingly,  that clumping does maintain the ionization state of the wind necessary for strong BAL features in the rest-frame UV at more realistic X-ray luminosities.
-We examine the X-ray properties of these simple clumped models
+Previously, we have shown that we could produce synthetic spectra 
+resembling those of observed broad absorption line (BAL) quasars 
+for plausible wind models, but only if the X-ray luminosity was limited to about  
+10$^{43}$~erg~s$^{-1}$. Here, we investigate the  degree to which
+clumping of the outflow allows us to 
+produce synthetic spectra in the rest-frame ultraviolet (UV) 
+that have the characteristics of quasars with X-ray luminosities as 
+large as 10$^{45}$ erg s$^{-1}$. 
+We conclude, perhaps not surprisingly, that clumping does maintain the ionization 
+state of the wind necessary for strong BAL features in the rest-frame UV at more 
+realistic X-ray luminosities. We examine the X-ray properties of our fiducial clumped model
 and find good agreement with existing X-ray samples of AGN and quasars.
 In addition, the dense, X-ray heated wind produces strong recombination and collisionally 
-excited line emission in, e.g., \civ\ and \la, to emerge at the low inclination, 
-`Type 1 quasar-like' angles. At the highest inclinations, the synthetic spectra possess prominent \mg\ and \al\ BALs, the absorption features seen in LoBAL quasars. 
-Despite these successes, we are unable to reproduce 
-the remarkably uniform emission line properties 
-seen in BAL and non-BAL quasar composites, as we find a marked increase
-in emission line equivalent widths at high inclination `BALQSO-like' angles. 
-This is due to a fundamental constraint arising
-from the anisotropy of emission from a classical thin disc. 
+excited line emission in, e.g., \la and \civ\, to emerge at the low inclination, 
+`Type 1 quasar-like' angles. At the highest inclinations, the synthetic spectra 
+possess prominent \mg\ and \al\ BALs, the absorption features seen in LoBAL quasars. 
+Despite these successes, we are unable to reproduce all the emission lines seen in
+quasar spectra with the correct equivalent width 
+ratios in any of the models in our initial simulation grid,
+and we find an angular dependence of emission line equivalent width despite the 
+remarkable similarities in the observed spectral properties of BAL and non-BAL quasars.
 Overall, our work suggests that BAL outflows can produce significant broad emission
 lines and that accretion disc winds naturally reproduce the range of
-ionization states seen in AGN.
-This suggests that geometric unification
-involving an accretion disc wind is a promising scenario, but our results 
-pose a specific challenge to models in which an equatorial outflow
-rises from a limb-darkened, foreshortened accretion disc.
+ionization states seen in AGN, but a full quantitative agreement 
+with quasar and BALQSO properties is not forthcoming.
+% the remarkably uniform emission line properties 
+% seen in BAL and non-BAL quasar composites, as we find a marked increase
+% in emission line equivalent widths at high inclination `BALQSO-like' angles. 
+% This is due to a fundamental constraint arising
+% from the anisotropy of emission from a classical thin disc. 
+% Overall, our work suggests that BAL outflows can produce significant broad emission
+% lines and that accretion disc winds naturally reproduce the range of
+% ionization states seen in AGN.
+% This suggests that geometric unification
+% involving an accretion disc wind is a promising scenario, but our results 
+% pose a specific challenge to models in which an equatorial outflow
+% rises from a limb-darkened, foreshortened accretion disc.
 % {\bf There is confusion in the abstract, at least, in what is the model and what is the synthetic spectra, as well as whether there is one model or many models.
@@
 Due to their ubiquitous nature,
-disc winds offer a natural explanation for the
+disc winds offer a natural way to {\em unify} much of the
 diverse phenemonology of luminous AGN and quasars \citep[e.g.][]{MCGV95, elvis2000}. 
@@
 may see a BALQSO or normal `Type 1' quasar.
-Within this {\em geometric unification} framework, the broad-line region (BLR) can 
+Within this geometric unification framework, the broad-line region (BLR) can 
 correspond either to the dense wind base or clumps embedded
-in the outflow. Indeed, \cite{elitzur2014} show that a disc-wind BLR scenario
-naturally explains the emission line evolution of AGN.
+in the outflow. 
+% Indeed, \cite{elitzur2014} show that a disc-wind BLR scenario
+% naturally explains the emission line evolution of AGN.
 A biconical wind model can also readily explain the various sub-classifications of BALQSOs: 
@@
 
-We have been engaged in a project to determine whether it is possible to simulate the properties of the spectra of AGN, including BALQSOs, using simple kinematic prescriptions for biconical disc winds using a Monte Carlo radiative transfer (MCRT) code that calculates the ionization structure of the wind and simulates the spectra from such a system \citep[][hereafter H13]{simlong2008,sim2010,higginbottom2013}.
+We have been engaged in a project to determine whether it is possible to simulate the properties of the spectra of AGN, including BALQSOs, using simple kinematic prescriptions for biconical disc winds using a Monte Carlo radiative transfer (MCRT) code that calculates the ionization structure of the wind and simulates the spectra from such a system \citep[][hereafter H13 and H14]{simlong2008,sim2010,higginbottom2013,H14}.
 The results have been encouraging in the sense that in H13, we showed we could produce simulated spectra that resembled that of BALQSOs, as long as the luminosity of the X-ray source was relatively low, of order \POW{43}{\LUM} and the mass loss rate was relatively high, of order the mass accretion rate.
@@
 (non-LTE). The code can be used to model a variety of
-disc-wind systems; it has been used with application to accreting white dwarfs 
+disc-wind systems; applications have included accreting white dwarfs 
 (Long \& Knigge 2002, hereafter LK02; Noebauer et al. 2010; 
@@
 From some initial conditions in each cell, the code first calculates the ionization structure of the wind in a series of iterations.
-Each iteration in an ``ionization cycle'' consists of generating photons, actually photon packets, from an accretion disc
-and central object, and calculating how these photon bundles scatter through the wind (eventually escaping the outflow or hitting the disk).
-Then updating the ionization structure based on the properties of the radiation field in each cell, and the process is repeated.
-Once the ionization structure has converged, the ionization structure is held fixed, and  synthetic spectra are generated at specific inclination angles in a series of "spectral cycles".
-LK02 provide a more detailed  description of the original code; various improvements have been made since then and are described by \cite{simmacro2005}, H13 and M15.
+Each iteration in an ``ionization cycle'' consists of generating photons, actually photon packets,
+from an accretion disc and central object, and calculating how these photon 
+bundles scatter through the wind (eventually escaping the outflow or hitting the disk). 
+The ionization and temperature structure is updated based on the properties of the 
+radiation field in each cell, and the process is repeated. The radiative transfer and thermal
+balance is carried out according to the principle of radiative equilibrium, 
+which assumes both statistical equilibrium and that radiative heating balances radiative cooling.
+Once the ionization structure has converged, it is held fixed, 
+and synthetic spectra are generated at specific inclination 
+angles in a series of "spectral cycles". LK02 provide a more detailed  
+description of the original code; various improvements have been made 
+since then and are described by \cite{simmacro2005}, H13 and M15.  
 %A full description of the code will be published elsewhere; 
-We focus here on the specific changes made for this study intended to improve the ionization calculation of H and He
+We focus here on the specific changes made for this study
+intended to improve the ionization calculation of H and He
 and to allow for clumping in the wind.
@@
 (`$r-$packets' and `$k-$packets' respectively; see also section~\ref{sec:photon_sources}). 
+which are reprocessed by `macro-atoms' with associated transition probabilities.
+% according to radiative equilibrium, which assumes both statistical equilibrium 
+% and that radiative heating balances radiative cooling.
 In our case, for reasons of computational efficiency, we adopt the  hybrid macro-atom scheme 
-described by M15.
-%(an improvement over that used by H14 for our earlier quasar study), 
-In this scheme, the energy packets interact with either two-level `simple ions' 
-or full `macro-atoms'. This allows one to treat non-LTE line transfer in radiative equilibrium, which assumes both statistical equilibrium and that 
-radiative heating balances radiative cooling.
-% {\bf KSL: what does "in radiative equilibrium" here mean? 
-% JM: Defined.}
+described by M15. In this scheme, the energy packets interact with either two-level 
+`simple atoms' or full macro-atoms. 
+This allows one to treat non-LTE line transfer in radiative equilibrium
 without approximation for elements that are identified as 
@@
 treatment of resonance lines when elements are identified 
-as simple-ions (see M15). In this study,
+as simple atoms (see M15). In this study,
 only H and He are treated as a macro-atom, because 
@@
 and because we are especially interested in the contribution to 
-AGN spectra of \LA.  
-H13 treated all atoms in a two-level approximation.  
+AGN spectra of \LA.  H13 treated all atoms in a two-level approximation.  
 % {\bf KSL:
@@
 As in M15, we use a dilute Boltzmann approximation to calculate 
-the populations of levels for simple-ions. We stress that this approximation 
+the populations of levels for simple-ions. This dilute approximation 
 is not required for macro-atom levels. 
@@
 
-In our previous modelling efforts, we have assumed a smooth outflow, 
+In our previous modelling efforts, we assumed a smooth outflow, 
 in which the density at a given point was determined only by the 
@@
 two main reasons. First, the physical scale lengths and density contrasts 
-associated with these parameters are not well-constrained from observations.  
+in AGN outflows are not well-constrained from observations.  
 Second, there are significant computational difficulties associated with adequately
@@
 such as collisional excitation or recombination, will increase by a factor of $D$.
+
 In our models, the temperature is not fixed, and is instead set by balancing heating and 
@@
 (thermal line emission).
-
-This treatment is necessarily simple; it does not adequately
+Our clumping treatment is necessarily simple; it does not adequately
 represent the complex substructures and stratifications in ionization
 state we expect in AGN outflows. Nevertheless, this parameterization allows simple estimates
-of the effect clumping might have on the ionization state and emergent 
+of the effect clumping has on the ionization state and emergent 
 line emission.
@@
 and increase $L_X$ to $10^{45}$~erg~s$^{-1}$ (a more realistic value for a 
-quasar of $10^9M_\odot$ and an eddington fraction of $0.2$; see section~\ref{sec:xray}).
-
-We then evaluated these models based on whether their synthetic spectra exhibited the 
+quasar of $10^9M_\odot$ and an Eddington fraction of $0.2$; see section~\ref{sec:xray}).
+
+We then evaluated these models based on 
+how closely their synthetic spectra reproduced the 
 following properties of quasars and BALQSOs:
@@
 with $BI > 0$ at $\sim20\%$ of viewing angles (e.g. Knigge et al. 2010)
-\item Line emission emerging at low inclinations, with $EW\sim40\AA$ in \civ\ \citep[e.g. ][]{shen2011}
-\item H recombination lines with $EW\sim50\AA$ in \la\ \citep[e.g. ][]{shen2011}
-\item  \mg\ and \al\ (LoBAL) absorption features with $BI > 0$ at a small subset of BAL angles
+\item Line emission emerging at low inclinations, with $EW\sim40$\AA in \civ\ \citep[e.g. ][]{shen2011}
+\item H recombination lines with $EW\sim50$\AA in \la\ \citep[e.g. ][]{shen2011}
+\item  \mg\ and \al\ (LoBAL) absorption features with $BI > 0$ at a subset of 
+BAL viewing angles
 \item Verisimilitude with quasar composite spectra.
 \end{itemize}
-Where $BI$ is the `Balnicity Index' (Weymann et al. 1991), given by
+Here $BI$ is the `Balnicity Index' (Weymann et al. 1991), given by
 \begin{equation}
@@
 and physical constraints and assess the potential for unification. 
-We then discuss the sensitivity to key parameters in section 5.
+We then discuss the sensitivity to key parameters in section~\ref{sec:param_sens}.
 The full grid, including output synthetic spectra and plots can be found at
@@
 \hline \hline 
-$r_{min}$ 	&	 $6r_{g}$ & $60r_{g}$ & \multicolumn{2}{|l|}{$300r_{g}$} \\ 
-$\theta_{min}$ 	&	 $40^{\circ}$ & $55^{\circ}$ & \multicolumn{2}{|l|}{$70^{\circ}$} \\ 
+$r_{min}$ 	&	 $60r_{g}$ & $180r_{g}$ & \multicolumn{2}{|l|}{$300r_{g}$} \\ 
+$\theta_{min}$ 	& $55^{\circ}$ & \multicolumn{3}{|l|}{$70^{\circ}$} \\ 
 $R_v$  	        &	 $10^{18}$cm & \multicolumn{3}{|l|}{$10^{19}$cm} \\ 
 $\alpha$ 	&	 $0.5$ & $0.6$ & $0.75$ & $1.5$ \\
-$f_V$ 	&	 $0.01$ & $0.1$ & \multicolumn{2}{|l|}{$1$}  \\
+$f_V$ 	&	 $0.01$ & \multicolumn{3}{|l|}{$0.1$}  \\
 \hline 
 \end{tabular}
-\caption{The grid points used in the parameter search.}
+\caption{The grid points used in the parameter search.
+The sensitivity to some of these parameters is discussed 
+further in section~\ref{sec:param_sens}}
 \label{grid_table}
@@
 
-\section{Results From A Fiducial Model}
+\section{Results and Discussion From A Fiducial Model}
 Here we describe the results from a fiducial model,
@@
 $M_{BH}$ 	 &	 $1\times 10^9~\rm{M_{\odot}}$ \\ 
-$\dot{M}_{acc}$ 	 &	 $5~M_{\odot}yr^{-1} \simeq 0.2~\dot{M}_{Edd}$\\ 
+$\dot{m}_{acc}$ 	 &	 $5~M_{\odot}yr^{-1} \simeq 0.2~\dot{M}_{Edd}$\\ 
 $\alpha_X$ 	 &	 $-0.9$ \\ 
@@
 $r_{disc}(max)$   &	 $3400r_g = 5\times10^{17}~{\rm cm}$ \\ 
-$\dot{M}_{wind}$  &	 $5~M_{\odot}yr^{-1}$ \\ 
+$\dot{m}_{wind}$  &	 $5~M_{\odot}yr^{-1}$ \\ 
 $r_{min}$ 	&	 $300r_{g} = 4.4\times10^{16}~{\rm cm}$\\ 
@@
 $\theta_{max}$ 	&	 $82.0^{\circ}$ \\ 
-$\lambda$ 	&	 $0$ \\ 
+%%$\lambda$ 	&	 $0$ \\ 
 $v_{\infty}(r_0)$ 	&	 $v_{esc}(r_0)$ \\ 
@@
 The total line luminosity also increases dramatically compared to H13. 
-This is due to heating of the plasma by the increased X-ray 
-luminosity, which avoids over-ionization due to clumping.
+This is primarily due to the higher X-ray luminosity increasing the bound-free
+heating in the plasma, which avoids over-ionization due to clumping.
 This line emission typically emerges on the edge of the wind
@@
 As shown in figure~\ref{fig:wind},
-the \civ\ line in our model is typically formed between 
+the \civ\ line in the fiducial model is typically formed between 
 $100-1000~r_G$ ($\sim10^{17}-10^{18}~\rm{cm}$).
@@
 {
-Synthetic spectra at four viewing angles in our model. At 
+Synthetic spectra at four viewing angles for the fiducial model. At 
 $20^\circ$ and $60^\circ$ we show a comparison to an SDSS quasar composite
@@
 PG0946+301 (Arav et al. 2000), and an SDSS spectrum of the LoBAL quasar 
-XXXXX (REF), respectively. The dotted line shows a disc
+SDSS J162901.63+453406.0, respectively. The dotted line shows a disc
 only continuum to show the effect of the outflow on the continuum level. 
@@
 A cartoon describing the broad classes of sightline 
-in our model, illustrating how geometric effects lead to 
+in the fiducial model, illustrating how geometric effects lead to 
 the different emergent spectra. The colour gradient is approximate,
@@
 STIS spectrum of the high BALnicity BALQSO PG0946+301 (Arav et al. 2000),
-and an SDSS spectrum of the LoBAL quasar XXXXX (REF),
+and an SDSS spectrum of the LoBAL quasar SDSS J162901.63+453406.0,
 for the angles of $73^\circ$ and $76^\circ$, respectively. 
@@
 
-Non-black saturation is observed in the absorption troughs of BALQSOs \citep{arav1999b,arav1999}.
+Non-black saturation is observed in the absorption troughs of BALQSOs \citep{arav1999b,arav1999a}.
 This is usually explained either as  partial covering of the continuum
@@
 
+\begin{table}
+\begin{tabular}{p{2cm}p{2cm}p{3cm}}
+\hline Property & Synthetic, $20^\circ$ & Observed  (S11) \\ 
+\hline \hline
+$\log L$[C~\textsc{iv}]  & $44.60$ & $44.42 \pm 0.32$  \\
+$\log L$[Mg~\textsc{ii}] & $43.92$ & $43.54 \pm 0.28$  \\
+$\log (\nu L_{\nu})_{1350}$  & $46.42$ & $46.01 \pm 0.30$ \\
+$\log (\nu L_{\nu})_{3000}$  & $46.18$ & $45.79 \pm 0.30$ \\
+% $\log L$[H~$\alpha$] & $43.46$ & $42.86$ & ?? \\
+% $EW$[C~\textsc{iv}] (erg~s$^{-1}$) & $3.96 \times 10^{44}$ & $2.62 \times 10^{44}$  \\
+% $EW$[Mg~\textsc{ii}] (erg~s$^{-1}$) & $3.50 \times 10^{43}$ & $8.32 \times 10^{43}$ \\
+% $EW$[H~$\alpha$] (erg~s$^{-1}$) & $3.50 \times 10^{43}$ & $8.32 \times 10^{43}$ \\
+% $\log L_{1350}$ (erg~s$^{-1}$~Hz$^{-1}$) & $46.42$ & $45.56$ & $46.01 \pm 0.30$ \\
+% $\log L_{3000}$ (erg~s$^{-1}$~Hz$^{-1}$) & $46.18$ & $45.36$ & $45.79 \pm 0.30$ \\
+% $L_{bol})$ (erg~s$^{-1}$) & 2.62
+% % $L_{1300})$(C\textsc{iv}) & 
+% \\
+% \multicolumn{3}{|l|}{At $73^\circ$ (`BALQSO-like')} \\  
+% $\log L$[C~\textsc{iv}] (erg~s$^{-1}$) & $44.14$ & ??  \\
+% $\log L$[Mg~\textsc{ii}] (erg~s$^{-1}$) & $42.82$ & $44.41$  \\
+% $\log L$[H~$\alpha$] (erg~s$^{-1}$) & $42.86$ & ?? \\
+% % $EW$[C~\textsc{iv}] (erg~s$^{-1}$) & $3.96 \times 10^{44}$ & $2.62 \times 10^{44}$  \\
+% % $EW$[Mg~\textsc{ii}] (erg~s$^{-1}$) & $3.50 \times 10^{43}$ & $8.32 \times 10^{43}$ \\
+% % $EW$[H~$\alpha$] (erg~s$^{-1}$) & $3.50 \times 10^{43}$ & $8.32 \times 10^{43}$ \\
+% $\log L_{1350}$ (erg~s$^{-1}$~Hz$^{-1}$) & $45.56$ & $46.00$ \\
+% $\log L_{3000}$ (erg~s$^{-1}$~Hz$^{-1}$) & $45.36$ & $45.79$ \\
+\hline
+\end{tabular}
+\caption{
+Some derived spectral properties of the fiducial model, at $20^\circ$,
+compared to observations. The observed values are taken from the Shen et al. (2011)
+SDSS DR7 Quasar catalog, and correspond to mean values with standard deviations in log space
+from a subsample with $8.5>\log(M_{BH})<9.5$ and $1.5<\log (L_{bol}/L_{edd}) < 0$,
+where the BH mass is a \civ\ virial estimate. 
+Units are logarithms of values in erg~s$^{-1}$.
+%unless stated.otherwise.
+}
+\label{line_lums}
+\end{table}
+
 We find significant collisionally excited line emission emerges
-at low inclinations in the synthetic spectra, particular in the \civ\ line.
-The improved treatment of recombination also results in a strong \la\ line. 
+at low inclinations in the synthetic spectra, particular in the \civ\ and \nv\
+lines. The improved treatment of recombination also results in a strong \la\ line. 
 In the context of unification, this is a promising result, 
 and shows that a biconical wind can produce significant 
-emission at `quasar-like' angles. 
-The spectra do not contain the strong C~\textsc{iii}]~1909\AA\, 
-line seen in the quasar composite spectra. 
-This is because we do not yet treat C as a full macro-atom with a 
-full collisional rates between forbidden
-or semi-forbidden transitions, as would be required.
+emission at `quasar-like' angles. To demonstrate this further,
+we show line luminosities and monochromatic continuum luminosities
+from the synthetic spectra in table~\ref{line_lums}. These are compared to
+mean values from a subsample of the SDSS DR7 quasar catalog (Shen et al. 2011) 
+with BH mass and Eddington fraction estimates similar to the fiducial model values 
+(see caption). The spectra do not contain the strong 
+C~\textsc{iii}]~1909\AA\, line seen in the quasar composite spectra,
+because semi-forbidden (intercombination)
+lines are not included in our modelling.
+% This is because we do not fully solve the C level populations,
+% and thus the level populations do not accurately reflect those
+% as a full macro-atom with a 
+% full collisional rates between forbidden
+% or semi-forbidden transitions, as would be required.
 The critical density of the C~\textsc{iii}]~1909\AA\, line 
@@
 parameters to produce a C~\textsc{iii}]~1909\AA\ line
-with a proper treament.
-
-The model produces strong emission lines in \civ, \nv\ and \la,
-as well as a weak \mg\ line. The shapes and widths of these lines
-match the composites fairly well. However, the line-to-continuum ratios 
-at low inclinations in our model are significantly weaker than the quasar 
-composites. Increasing the density of the outflow, by altering the mass 
-loss rate  or velocity law, can produce more line emission.
-However, the red wing of the BAL profiles is generally stronger than 
-seen in BALQSO spectra and composites. This illustrates a fundamental 
-problem with a geometric unification model such as this:
-that the line-to-continuum ratios at high inclinations are
-significantly affected by disc foreshortening and limb darkening.
-The angular distribution of the disc radiation is clearly
-crucially important in determining the emergent line ratios.  
+with a proper treament. We note, however, the the presence of
+this line in the spectrum of quasars does {\em not} prohibit denser material having a significant contribution to the spectrum.
+
+% The model produces strong emission lines in \civ, \nv\ and \la,
+% as well as a very weak \mg\ line.
+
+The shapes and widths of these lines
+match the composites fairly well, and the integrated 
+line luminosities are significant when compared to observations.
+However, there are a number of properties of the synthetic spectra
+that are at odds with the observations. First, we find that the ratios of the 
+equivalent width of the \la\ and \mg\ lines
+to \civ\ is much lower than in the composite spectra. This problem 
+has also been seen in simpler photoionization models for the BLR \citep{netzer1990}.
+It may be that a larger region of very dense ($n_e\sim10^{10}$cm$^{-3}$) 
+material is needed, this could correspond to a disc atmosphere or 
+`transition region' (see e.g. Murray et al. 1995; Knigge et al. 1997). 
+While modest changes to geometry may permit this, the initial grid search 
+did not find a parameter space in which the \la\ or \mg\ equivalent widths
+were significantly higher. Second, we find that equivalent widths increase
+with inclinations, to the extent that significantly denser
+models can match the line EWs fairly well at low inclinations but will then
+possess overly strong red wings to the BAL P-Cygni profiles at high inclinations
+(see also figure~\ref{fig:lobal}).
+This angular dependence of EW is expected from a model in which the BLR radiates
+more isotropically than the disc, which in this case is foreshortened and limb darkened.
+It appears to contradict observations, which show remarkably uniform emission
+line properties in quasars and BALQSOs \citep{weymann1991,dipompeo2012b}. 
+The angular distribution of the disc 
+continuum and line emission
+is clearly crucially important in determining the emergent broad 
+line equivalent widths, as suggested by, e.g., the analysis of \cite{risaliti2011}. 
+We shall explore this question further in a future study.  
+% However, the line-to-continuum ratios 
+% at low inclinations in our model are significantly weaker than the quasar 
+% composites. Increasing the density of the outflow, by altering the mass 
+% loss rate  or velocity law, can produce more line emission.
+% However, the red wing of the BAL profiles is generally stronger than 
+% seen in BALQSO spectra and composites. This suggests a fairly 
+% fundamental problem with a geometric unification model in which 
+% The line equivalent widths at high inclinations are
+% significantly affected by disc foreshortening and limb darkening.
+% The angular distribution of the disc radiation is clearly
+% crucially important in determining the emergent line ratios.  
 % {\bf KSL: This is a bit oddly explained. Our problem is at low inclination.  Note that I am a bit concerned with Fig 3; the model spectra and the observations look very different.}
@@
 \centering
-\includegraphics[width=1.0\textwidth]{figures/lx_a05_pre.png}
+\includegraphics[width=0.8\textwidth]{figures/lx_a05_pre.png}
 \caption
@@
 
-The low inclination, `BALQSO-like' viewing angles show moderate agreement with the data,
+The high inclination, `BALQSO-like' viewing angles show moderate agreement with the data,
 and are X-ray weak due to bound-free and electron scattering opacities in the wind.
@@
 \centering
-\includegraphics[width=1.0\textwidth]{figures/c4_angles.png}
+\includegraphics[width=0.8\textwidth]{figures/c4_angles.png}
 \caption
@@
 
-At certain sightlines, the synthetic spectra exhibit blue-shifted BALs in \al\ and \mg --
+At high inclinations, the synthetic spectra exhibit blue-shifted BALs in \al\ and \mg --
 the absorption lines seen in LoBALQSOs, and we even see absorption in Fe~\textsc{ii}
@@
 FeLoBAL quasars, due to a foreshortened and attenuated continuum, 
-although, as noted in section~\ref{angular}, BAL fraction 
-inferences are fraught with complex selection effects.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% DISCUSSION???
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
- \section{Discussion: Parameter Sensitivity and Inclination Dependence}
-
- We have demonstrated that our fiducial model successfully reproduces much of
- the phenomenology of luminous AGN and quasars, with a few exceptions.
- Here, we discuss these shortcomings, by discussing parameter sensitivity
- and the dependence of line EWs on inclination.
-
-\subsection{The Angular Distribution of Line And Continuum Emission}
-\label{sec:angular}
-
-\begin{figure}
+although BAL fraction inferences are fraught with complex selection 
+effects \citep{goodrich1997,krolikvoit1998}.
+
+\subsection{Parameter Sensitivity}
+
+\label{sec:param_sens}
+
+\begin{figure} %fullpage
 \centering
-\includegraphics[width=0.49\textwidth]{figures/hist_ew.png}
+\includegraphics[width=1.0\textwidth]{figures/scatter_c4_grid.png}
 \caption
 {
-{\sl Top Panel:} A histogram of $1/2$ equivalent widths ($W_{\lambda}/2$)
-for BALQSOs and non-BAL quasars from the {\sl SDSS DR7} quasar sample (Shen et al. 2011).
-{\sl Bottom Panel:} $W_{\lambda,RW}$ as a function of inclination in our example model (black line).
-The green shaded area indicates viewing angles which look into the wind (`BALQSO-like').
+The EW of the \civ~$1550$\AA\ line at $20^\circ$ plotted against a) the 
+$BI$ of \civ~$1550$\AA\ at $75^\circ$, b) the EW of the \mg~$2800$\AA\ line 
+at $20^\circ$ and c) the EW of \la\ at $20^\circ$. The circles correspond 
+to the simulation grid for two different values of $f_V$, and the fiducial 
+model is marked with an orange star. 
+We also show a higher X-ray luminosity model and a higher mass loss rate
+with a red star.
 }
-\label{fig:ew}
-\end{figure}
+\label{fig:grid}
+\end{figure} %fullpage
+
+Having selected an individual fiducial model from the simulation grid, it is important
+to briefly explore how specialised this model is, and how small parameter
+changes can affect the synthetic spectra. Figure~\ref{fig:grid}
+shows the EW at a low inclination, and $BI$ at a high inclination for the simulation
+grid. A few conclusions can be drawn from this plot straight away. 
+First, we find that almost all the models with $f_V=0.1$ are over-ionized, and 
+fail to produce strong \civ\ BALs or emission lines. Second, we find that 
+it is difficult to significantly increase line emission while
+keeping the luminosity and mass loss rate of the system fixed. 
+We show an additional point on figure 7 corresponding to a model with an order of
+magnitude higher X-ray luminosity and double the mass loss rate. As expected, 
+this results in far higher line equivalent widths, but fails to produce BALs because
+the collisionally excited emission swamps the BAL profile. In addition,
+this model would lie well above the expected $L_{2kev}-L_{2500}$ 
+relation in figure 5. Such a high X-ray luminosity could therefore 
+not be the cause of the strong line emission seen in {\em all} Type 1 quasars.
+
+The parameter search presented here is by no means exhaustive, and
+we may be limited by the specific parameterisation (from SV93) of the outflow 
+kinematics we have used. Nevertheless, we suggest that the angular distribution
+of {\em both} the line and continuum emission is perhaps the crucial 
+aspect to understand.
+With this in mind, obtaining reliable orientation indicators appears
+to be a crucial observational task if we are to
+further our understanding of BAL outflows 
+and their connection, or lack thereof, to the broad line region.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% DISCUSSION???
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%  \section{Discussion: Parameter Sensitivity and Inclination Dependence}
+
+%  We have demonstrated that our fiducial model successfully reproduces much of
+%  the phenomenology of luminous AGN and quasars, with a few exceptions.
+%  Here, we discuss these shortcomings, by discussing parameter sensitivity
+%  and the dependence of line EWs on inclination.
+
+% \subsection{The Angular Distribution of Line And Continuum Emission}
+% \label{sec:angular}
 
@@
 % \centering
-% \includegraphics[width=0.45\textwidth]{figures/ew.png}
+% \includegraphics[width=0.49\textwidth]{figures/hist_ew.png}
 % \caption
 % {
-% $W_{\lambda,RW}$ as a function of inclination in our example model (red line).
-% We also the mean $1/2$ equivalent width from DiPompeo et al. (2012) as a horizontal
-% line, with the shaded area corresponding to the standard deviation.
+% {\sl Top Panel:} A histogram of $1/2$ equivalent widths ($W_{\lambda}/2$)
+% for BALQSOs and non-BAL quasars from the {\sl SDSS DR7} quasar sample (Shen et al. 2011).
+% {\sl Bottom Panel:} $W_{\lambda,RW}$ as a function of inclination in our example model (black line).
+% The green shaded area indicates viewing angles which look into the wind (`BALQSO-like').
 % }
@@
 
-In order to quantitatively assess how emission lines change with 
-inclination when blue-shifted absorption 
-may affect the line profile, we define the `red wing equivalent width' ($W_{\lambda,RW}$) as
-\begin{equation}
-W_{\lambda,RW} = \int_{\lambda_0}^{\lambda^\prime} \left( 1 - \frac{F_\lambda}{F_0} \right) d\lambda
-\label{rwew}
-\end{equation}
-where $F_0$ is the continuum flux and the integral is calculated from $\lambda_0$, line centre,
-to a wavelength $\lambda^\prime$ where the flux has returned to the continuum level.
-This quantity is shown as a function of inclination in figure 5 for the \civ\ and \mg\ UV lines.
-We also show the $W_{\lambda,RW}$ expected from isotropic line emission and a foreshortened 
-and limb darkened disc  as well as $1/2$ equivalent widths from \cite{dipompeo2012b}.
-
-BALQSOs and quasars generally possess very similar emission line properties 
-\citep[e.g.][]{weymann1991,reichard2003}. This is illustrated in the 
-the top panel of figure~\ref{fig:ew}, which shows histograms 
-of \civ\ $1/2$ equivalent widths for BAL and non-BAL quasars from the {\sl SDSS DR7} quasar
-sample \citep{shen2011}. Clearly the variation in $W_{\lambda,RW}$ at 
-BAL-like and quasar-like angles is significantly larger than any systematic 
-differences between the quasar and BALQSO samples.
-The strong dependence of equivalent width on inclination is caused by decreased continuum
-levels at high inclinations. This is due to a combination of
-continuum attenuation through the wind, and the effect of limb darkening and foreshortening
-in our classical thin disc. This presents a challenge to a geometric unification model
-with an equatorial outflow.
-
-% Clearly, the variation with inclination in our models is far greater than 
-% than the variation between, and standard deviation within, quasar and BALQSO samples.  
-% This presents a challenge to our model, as well as the geometric unification picture in general.
-One obvious potential solution is to hypothesize a more isotropic distribution 
-for the emergent condition than predicted by a classical thin disc. 
-General relativistic effects -- specifically, light bending
-and relativistic beaming -- can cause 
-the accretion disc SED to become more isotropic \citep[e.g.][]{zhang1997,munozdarias2013}. 
-However, we have verified using AGNSPEC \citep{hubeny2000,hubeny2001,hubenyhubeny1997}
-that this effect is small in the UV wavelength regime, 
-and the disc is still anisotropic.
-Reprocessing by an extended outflow may also cause a more isotropic
-continuum to emerge. Hints that light scattered off a spatially extended 
-wind may contribute signiciantly to the emergent continuum come from radiative transfer
-simulations \citep{simproga2012} and microlensing observations \citep{sluse2015}.
-However, neither of these examples have sufficient reprocessing efficiencies to 
-compensate for the disc anisotropy in this case.
-
-An alternative explanation is that the BLR has the same anisotropic 
-angular distribution of emission as the accretion disc.
-Indeed, \cite{risaliti2011} find that EW distributions in quasars 
-are consistent with anisotropic emission 
-from optically thick, disc-like structures for {\em both} the continuum source and BLR. 
-If this is the case, it has a dramatic affect on the intrinsic
-BAL fraction inferred from flux-limited samples \citep{goodrich1997,krolikvoit1998}.
-
-It is also possible that the equatorial paradigm invoked from early polarisation
-studies \citep{goodrich1995, cohen1995,brotherton2006} 
-is an over-simplification, or is incorrect. 
-High brightness temperatures in some RL BALQSOs imply polar outflows \citep{zhou2006} 
-and \cite{bruni2012} find that
-RL BALQSOs possess similar radio spectral indices to normal RL quasars, 
-suggestive of comparable inclinations. 
-In addition, \cite{marin2013} find a bending angle of $\sim45^\circ$ is required to 
-explain the polarisation dichotomy of type 1 and 2 AGN using an Elvis-type wind 
-model (Elvis 2000). It is therefore possible 
-that type 1 quasars and BALQSOs are generally viewed from a fairly narrow range of less
-equatorial angles ($\sim0$-$45^\circ$), or {\em both} 
-evolutionary and geometric explanations are required.
-We suggest that future modelling should include predictions of polarisation signatures
-from a detailed radiative transfer simulation, allowing direct 
-comparison with spectropolarimetry of BALQSOs.
+% % \begin{figure}
+% % \centering
+% % \includegraphics[width=0.45\textwidth]{figures/ew.png}
+% % \caption
+% % {
+% % $W_{\lambda,RW}$ as a function of inclination in our example model (red line).
+% % We also the mean $1/2$ equivalent width from DiPompeo et al. (2012) as a horizontal
+% % line, with the shaded area corresponding to the standard deviation.
+% % }
+% % \label{fig:ew}
+% % \end{figure}
+
+% In order to quantitatively assess how emission lines change with 
+% inclination when blue-shifted absorption 
+% may affect the line profile, we define the `red wing equivalent width' ($W_{\lambda,RW}$) as
+% \begin{equation}
+% W_{\lambda,RW} = \int_{\lambda_0}^{\lambda^\prime} \left( 1 - \frac{F_\lambda}{F_0} \right) d\lambda
+% \label{rwew}
+% \end{equation}
+% where $F_0$ is the continuum flux and the integral is calculated from $\lambda_0$, line centre,
+% to a wavelength $\lambda^\prime$ where the flux has returned to the continuum level.
+% This quantity is shown as a function of inclination in figure 5 for the \civ\ and \mg\ UV lines.
+% We also show the $W_{\lambda,RW}$ expected from isotropic line emission and a foreshortened 
+% and limb darkened disc  as well as $1/2$ equivalent widths from \cite{dipompeo2012b}.
+
+% BALQSOs and quasars generally possess very similar emission line properties 
+% \citep[e.g.][]{weymann1991,reichard2003}. This is illustrated in the 
+% the top panel of figure~\ref{fig:ew}, which shows histograms 
+% of \civ\ $1/2$ equivalent widths for BAL and non-BAL quasars from the {\sl SDSS DR7} quasar
+% sample \citep{shen2011}. Clearly the variation in $W_{\lambda,RW}$ at 
+% BAL-like and quasar-like angles is significantly larger than any systematic 
+% differences between the quasar and BALQSO samples.
+% The strong dependence of equivalent width on inclination is caused by decreased continuum
+% levels at high inclinations. This is due to a combination of
+% continuum attenuation through the wind, and the effect of limb darkening and foreshortening
+% in our classical thin disc. This presents a challenge to a geometric unification model
+% with an equatorial outflow.
+
+% % Clearly, the variation with inclination in our models is far greater than 
+% % than the variation between, and standard deviation within, quasar and BALQSO samples.  
+% % This presents a challenge to our model, as well as the geometric unification picture in general.
+% One obvious potential solution is to hypothesize a more isotropic distribution 
+% for the emergent condition than predicted by a classical thin disc. 
+% General relativistic effects -- specifically, light bending
+% and relativistic beaming -- can cause 
+% the accretion disc SED to become more isotropic \citep[e.g.][]{zhang1997,munozdarias2013}. 
+% However, we have verified using AGNSPEC \citep{hubeny2000,hubeny2001,hubenyhubeny1997}
+% that this effect is small in the UV wavelength regime, 
+% and the disc is still anisotropic.
+% Reprocessing by an extended outflow may also cause a more isotropic
+% continuum to emerge. Hints that light scattered off a spatially extended 
+% wind may contribute signiciantly to the emergent continuum come from radiative transfer
+% simulations \citep{simproga2012} and microlensing observations \citep{sluse2015}.
+% However, neither of these examples have sufficient reprocessing efficiencies to 
+% compensate for the disc anisotropy in this case.
+
+% An alternative explanation is that the BLR has the same anisotropic 
+% angular distribution of emission as the accretion disc.
+% Indeed, \cite{risaliti2011} find that EW distributions in quasars 
+% are consistent with anisotropic emission 
+% from optically thick, disc-like structures for {\em both} the continuum source and BLR. 
+% If this is the case, it has a dramatic affect on the intrinsic
+% BAL fraction inferred from flux-limited samples \citep{goodrich1997,krolikvoit1998}.
+
+% It is also possible that the equatorial paradigm invoked from early polarisation
+% studies \citep{goodrich1995, cohen1995,brotherton2006} 
+% is an over-simplification, or is incorrect. 
+% High brightness temperatures in some RL BALQSOs imply polar outflows \citep{zhou2006} 
+% and \cite{bruni2012} find that
+% RL BALQSOs possess similar radio spectral indices to normal RL quasars, 
+% suggestive of comparable inclinations. 
+% In addition, \cite{marin2013} find a bending angle of $\sim45^\circ$ is required to 
+% explain the polarisation dichotomy of type 1 and 2 AGN using an Elvis-type wind 
+% model (Elvis 2000). It is therefore possible 
+% that type 1 quasars and BALQSOs are generally viewed from a fairly narrow range of less
+% equatorial angles ($\sim0$-$45^\circ$), or {\em both} 
+% evolutionary and geometric explanations are required.
+% We suggest that future modelling should include predictions of polarisation signatures
+% from a detailed radiative transfer simulation, allowing direct 
+% comparison with spectropolarimetry of BALQSOs.
 
@@
 \item We have introduced a simple treatment 
-of clumping in our model, and found that it moderates the ionizaiton state
+of clumping in our model, and found that it moderates the ionization state
 sufficiently to allow for the 
@@
 and recombination lines (such as \la\ and \heiiline).
+However, the equivalent width ratios of the emission lines do not match
+observations, suggesting that a greater volume of dense ($n_e\sim10^{10}$~cm$^{-3}$)
+material may be required.
 \smallskip
-\item The line EWs in our models increase with inclination.
+\item The line EWs in the synthetic spectra increase with inclination.
 BAL and non-BAL quasar composites have comparable EWs, so our model
 fails to reproduce this behaviour.
-This is due to a fundamental constraint discussed further in 
-section~\ref{sec:angular}. If the BLR emits fairly isotropically then for a 
+ If the BLR emits fairly isotropically then for a 
 foreshortened, limb-darkened accretion disc 
-it is simply not possible to achieve line ratios at low inclinations 
+it is not possible to achieve line ratios at low inclinations 
 that are comparable to those at high inclinations. 
-Furthermore, this is conclusion is independent of the assumed 
-BLR geometry and size.
+We suggest that understanding the angular distribution of 
+line and continuum emission is a crucial question for theoretical models.
+% Furthermore, this is conclusion is independent of the assumed 
+% BLR geometry and size.
 \end{enumerate}
@@
 explaining much of the  phenomenology of quasars. However, our conclusions pose 
-a clear challenge to a picture in which BALQSOs are
-explained by an equatorial wind rising from a classical thin disc. 
-We suggest that obtaining reliable observational orientation indicators and 
-exploring alternative outflow geometries in simulations
-are obvious avenues for exploration.
+some challenges to a picture in which BALQSOs are
+explained by an {\em equatorial} wind rising from a classical thin disc, and suggest 
+the angular distribution of emission is important to understand if this 
+geometry is to be refuted or confirmed. We suggest that obtaining reliable 
+observational orientation indicators and 
+exploring a wider parameter space of outflow geometries in simulations
+are obvious avenues for future work.
 
@@
 and made use of the IRIDIS High Performance Computing Facility at the
-University of Southampton. Figures were produced using the {\tt matplotlib} plotting library
-\citep{matplotlib}.
+University of Southampton. Figures were produced using the {\tt matplotlib} plotting library \citep{matplotlib}. This work made use of the Sloan Digital Sky Survey.
+Funding for the Sloan Digital Sky Survey has been provided by
+the Alfred P. Sloan Foundation, the U.S. Department of Energy Office of
+Science, and the Participating Institutions.
 

### 2015-12-17 paper_mnras.tex
about to clean up

@@
 \item H recombination lines with $EW\sim50\AA$ in \la\ \citep[e.g. ][]{shen2011}
-\item  \mg\ and \al\ (LoBAL) absorption features with $BI > 0$ at a small subset of BAL angles
+\item  \mg\ and \al\ (LoBAL) absorption features with $BI > 0$ at a subset of 
+BAL viewing angles
 \item Verisimilitude with quasar composite spectra.
 \end{itemize}
-Where $BI$ is the `Balnicity Index' (Weymann et al. 1991), given by
+Here $BI$ is the `Balnicity Index' (Weymann et al. 1991), given by
 \begin{equation}
@@
 FeLoBAL quasars, due to a foreshortened and attenuated continuum, 
-although, as noted in section~\ref{angular}, BAL fraction 
-inferences are fraught with complex selection effects.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% DISCUSSION???
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
- \section{Discussion: Parameter Sensitivity and Inclination Dependence}
-
- We have demonstrated that our fiducial model successfully reproduces much of
- the phenomenology of luminous AGN and quasars, with a few exceptions.
- Here, we discuss these shortcomings, by discussing parameter sensitivity
- and the dependence of line EWs on inclination.
-
-\subsection{The Angular Distribution of Line And Continuum Emission}
-\label{sec:angular}
-
-\begin{figure}
+although BAL fraction inferences are fraught with complex selection 
+effects \citep{goodrich1997,krolikvoit1998}.
+
+\subsection{Parameter Sensitivity}
+
+\label{sec:param_sens}
+
+\begin{figure*}
 \centering
-\includegraphics[width=0.49\textwidth]{figures/hist_ew.png}
+\includegraphics[width=1.0\textwidth]{figures/scatter_c4_grid.png}
 \caption
 {
-{\sl Top Panel:} A histogram of $1/2$ equivalent widths ($W_{\lambda}/2$)
-for BALQSOs and non-BAL quasars from the {\sl SDSS DR7} quasar sample (Shen et al. 2011).
-{\sl Bottom Panel:} $W_{\lambda,RW}$ as a function of inclination in our example model (black line).
-The green shaded area indicates viewing angles which look into the wind (`BALQSO-like').
+The EW of the \civ~$1550$\AA\ line at $20^\circ$ plotted against a) the 
+$BI$ of \civ~$1550$\AA\ at $75^\circ$, b) the EW of the \mg~$2800$\AA\ line 
+at $20^\circ$ and c) the EW of \la\ at $20^\circ$. The circles correspond 
+to the simulation grid for two different values of $f_V$, and the fiducial 
+model is marked with an orange star. 
+We also show a higher X-ray luminosity model and a higher mass loss rate
+with a red star.
 }
-\label{fig:ew}
-\end{figure}
+\label{fig:grid}
+\end{figure*}
+
+Having selected an individual fiducial model from the simulation grid, it is important
+to briefly explore how specialised this model is, and how small parameter
+changes can affect the synthetic spectra. Figure~\ref{fig:grid}
+shows the EW at a low inclination, and $BI$ at a high inclination for the simulation
+grid. A few conclusions can be drawn from this plot straight away. 
+First, we find that almost all the models with $f_V=0.1$ are over-ionized, and 
+fail to produce strong \civ\ BALs or emission lines. Second, we find that 
+it is difficult to significantly increase line emission while
+keeping the luminosity and mass loss rate of the system fixed. 
+We show an additional point on figure 7 corresponding to a model with an order of
+magnitude higher X-ray luminosity and double the mass loss rate. As expected, 
+this results in far higher line equivalent widths, but fails to produce BALs because
+the collisionally excited emission swamps the BAL profile. In addition,
+this model would lie well above the expected $L_{2kev}-L_{2500}$ 
+relation in figure 5. Such a high X-ray luminosity could therefore 
+not be the cause of the strong line emission seen in {\em all} Type 1 quasars.
+
+The parameter search presented here is by no means exhaustive, and
+we may be limited by the specific parameterisation (from SV93) of the outflow 
+kinematics we have used. Nevertheless, we suggest that the angular distribution
+of {\em both} the line and continuum emission is perhaps the crucial 
+aspect to understand.
+With this in mind, obtaining reliable orientation indicators appears
+to be a crucial observational task if we are to
+further our understanding of BAL outflows 
+and their connection, or lack thereof, to the broad line region.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% DISCUSSION???
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%  \section{Discussion: Parameter Sensitivity and Inclination Dependence}
+
+%  We have demonstrated that our fiducial model successfully reproduces much of
+%  the phenomenology of luminous AGN and quasars, with a few exceptions.
+%  Here, we discuss these shortcomings, by discussing parameter sensitivity
+%  and the dependence of line EWs on inclination.
+
+% \subsection{The Angular Distribution of Line And Continuum Emission}
+% \label{sec:angular}
 

### 2015-12-18 paper.tex
added param grid
version for collabs

@@
 \def\hb{H~$\beta$}
+\def\civline{C~\textsc{iv}~$1550$\AA}
+\def\nvline{N~\textsc{v}~$1240$\AA}
+\def\mgline{Mg~\textsc{ii}~$2800$\AA}
 
@@
 \title
-[Testing Quasar Unification]{
+[Testing Quasar Unification: Radiative Transfer in Clumpy Winds]{
 % Modelling quasar outflows:
@@
 
-%\author[Matthews et al.]
 \author[Matthews et al.]{
@@
 \date{\today}
-%\\
-%Supervisor: Prof. Christian Knigge\\
-%{\sl School of Physics \& Astronomy, University of Southampton,
-%  Southampton, SO17 1BJ, UK}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %
@@
 \begin{abstract} 
-% Broad absorption lines (BALs) in the ultraviolet 
-% are seen in $\sim20\%$ of quasi-stellar objects (QSOs). 
-% Blue-shifted broad absorption lines (BALs) are the most direct evidence of 
-% accretion disc `winds' in such systems; mass loaded outflows
-% emanating from the disc that may be driven by line forces or
-% magnetic processes. 
-% Various unification schemes for
-% quasars and luminous active galactic nuclei (AGN) have proposed
-% that the broad emission line region is roughly cospatial
-% with broad absorption line (BAL) gas and much of the phenomenology of luminous AGN
-% can be explained by a simple geometrical picture involving an accretion
-% disc and associated outflow. Here, we test this paradigm by 
-% utilising our state-of-the-art radiative transfer code to produce synthetic spectra
-% from simple biconical disc wind models. 
-% In particular, we expand on our previous 
-% work in which a benchmark model for BAL quasars was produced. 
-% We have conducted a limited parameter search with the aim of unifying quasar phenomenology,
-% and arrive at an improved model. The grid is now publicly available.
-% We find that a simple treatment of clumping (`microclumping') 
-% allows for a more realistic X-ray luminosity in the model by lowering the 
-% ionization parameter. We examine the X-ray properties of this new model
-% and find good agreement with existing X-ray samples of AGN and QSOs.
-% We find that the dense, X-ray heated wind 
-% produces strong H recombination and collisionally excited resonance 
-% line emission to emerge at the low inclination angles, 
-% which represent quasars within this unification scenario.
-% % We also treat Hydrogen using a `macro-atom' approach in order to 
-% % examine the effect of recombination on Hydrogen emission lines, and
-% % this results in significant line emission in Lyman~$\alpha$ and the Balmer series.
-% However, we are unable to reproduce the remarkably similar of line-to-continuum
-% ratios between BAL and non-BAL quasar composites.
-% This is due to a fundamental constraint arising
-% from the anisotropy of emission from a classical thin disc. 
-% We briefly explore the effect of relativistic beaming, gravitational redshift and 
-% light bending on the angular distribution of disc continuum emission. 
-% We find that these general relativistic effects do cause the disc to
-% emit slightly more isotropically, but this is not yet sufficient to produce a
-% self-consistent model. We discuss wind reprocessing as a potential solution.
-% Overall, our work suggests that geometric unification
-% involving an accretion disc wind is a promising scenario, but our results 
-% pose a number of difficult challenges to such a model.
-% Determining the true geometry of ADWs and uncovering the true disc spectral 
-% (and angular) energy distribution are key next stpng if we are to build up a 
-% holistic picture of the quasar population.
 Various unification schemes have been proposed to interpret the complex phenomenology 
@@
 In addition, the dense, X-ray heated wind produces strong recombination and collisionally 
-excited line emission in, e.g., \la and \civ\, to emerge at the low inclination, 
+excited line emission in, e.g., \la\ and \civline, to emerge at the low inclination, 
 `Type 1 quasar-like' angles. At the highest inclinations, the synthetic spectra 
@@
 remarkable similarities in the observed spectral properties of BAL and non-BAL quasars.
-Overall, our work suggests that BAL outflows can produce significant broad emission
-lines and that accretion disc winds naturally reproduce the range of
-ionization states seen in AGN, but a full quantitative agreement 
-with quasar and BALQSO properties is not forthcoming.
-% the remarkably uniform emission line properties 
-% seen in BAL and non-BAL quasar composites, as we find a marked increase
-% in emission line equivalent widths at high inclination `BALQSO-like' angles. 
-% This is due to a fundamental constraint arising
-% from the anisotropy of emission from a classical thin disc. 
-% Overall, our work suggests that BAL outflows can produce significant broad emission
-% lines and that accretion disc winds naturally reproduce the range of
-% ionization states seen in AGN.
-% This suggests that geometric unification
-% involving an accretion disc wind is a promising scenario, but our results 
-% pose a specific challenge to models in which an equatorial outflow
-% rises from a limb-darkened, foreshortened accretion disc.
-% {\bf There is confusion in the abstract, at least, in what is the model and what is the synthetic spectra, as well as whether there is one model or many models.
-We need to try to be clear.
-The model should be a clumped biconical outflow.
-There are then particular instantiations of the model.
-And then there are synthetic spectra}
+Overall, our work suggests that a biconical wind model
+reproduces much of the qualitative behaviour expected from a unified model. 
+However, we cannot yet provide quantitative matches with quasar properties at all 
+viewing angles; whether disc winds can successfully unify quasars is therefore 
+still an open question.
 \end{abstract}
 
-%\begin{keywords}
-%AGN: outflows
-%\end{keywords}
+% \begin{keywords}
+% galaxies: active; accretion, accretion discs; (galaxies:) quasars: emission lines;
+% (galaxies:) quasars: absorption lines
+% \end{keywords}
 
@@
 The BBB is often attributed to emission from a 
-geometrically thin, optically thick accretion disc surrounding the central black hole, similar
-to that described by \cite{shakurasunyaev1973}.
+geometrically thin, optically thick accretion disc surrounding the central black hole (BH), similar to that described by \cite{shakurasunyaev1973}.
 % {\bf Note: the first half of this paragraph and the second do not follow from one another.  
@@
 for polar BAL outflows  in radio-loud (RL) sources \citep{zhou2006,ghoshpunsly2007}.
-% although this geometry is contradicted
-% by more recent studies of radio spectral indices \citep{dipompeo2012}.
 
@@
 in the outflow. 
-% Indeed, \cite{elitzur2014} show that a disc-wind BLR scenario
-% naturally explains the emission line evolution of AGN.
 A biconical wind model can also readily explain the various sub-classifications of BALQSOs: 
@@
 
-% As well as acting as a source of photoionized plasma, a 
-% As well as imprinting clear line absorption and emission
-% features, disc winds may also have a profound effect on the structure and 
-% emergent {\em continuum} of the accretion disc itself.
-% Mass-loss will alter the accretion rate and resultant 
-% temperature of the accretion disc, possibly explaining some 
-% of the features typically seen in luminous AGN \citep{knigge1999,laordavis2014}.
-% There have been numerous difficulties when confronting 
-% theoretical accretion disc models with observations 
-% \citep[see e.g.][]{blaes1998}. However, AGN spectral energy distributions (SEDs) can now, 
-% in general, be fitted well with accretion disc models
-% when the effects of general relativity (GR), Comptonisation
-% and mass-loss are included \citep{capellupo2015}. Mass-loss therefore appears to be 
-% critical if an accretion disc model is to successfully fit AGN SEDs, 
-% particular in the UV region of the spectrum.
-
-%{\bf ksl: I don't see what this paragraph has to do with our problem, which we need to clearly explain} Despite the clear importance of ADWs in understanding AGN SEDs and accretion physics,
 Despite the clear importance of disc winds in shaping quasar and AGN spectra,  
@@
 \citep{reeves2003,poundsreeves2009,tombesi2010a}.
-% The presence of line-locked features \citep{bowler2014} 
-% and the `ghost of \la' (Arav et al. 1996; Arav 1996; North 2006; but see 
-% also Cottis et al. 2010) \nocite{arav1995, arav1996, north2006,cottis2010}
-% in the spectra of some BALQSOs also gives clearer evidence that line-driving is
-% at least partially contributing to the acceleration of the wind.
 The efficiency of line-driving is crucially dependent on the ionization state 
@@
 a region of `hitchhiking gas' that could shield the wind from the central X-ray source. 
-% Hydrodynamic simulations of line-driven disc winds also found a shielding region
-% was required to maintain the correct ionization state \citep{PSK2000,PK04}. 
-% However, \cite{sim2010_hydro} and \cite{H14} showed that including multiple scattering means the ionizing radiation field could still reach the previously shielded regions 
-% in those particular models.
-An additional or alternative solution is that the wind is clumped \citep[e.g.][]{hamann2013}
+An additional or alternative solution is that the wind is clumped 
+\citep[e.g.][]{hamann2013}
 possibly on multiple scale lengths. Local density enhancements could lower the 
@@
 \citep{PSK2000,PK04,progakurosawa2010,proga2014}.  
-% {\bf KSL: I do not believe the AGN simulations have the resolution to produce clumping on the scale of hot star winds.
-% JM: that's why I mention scales, although I can specifically mention resolution if we
-% want.}
 Nevertheless, clumpy winds offer an observationally motivated and theoretically 
@@
 The remainder of this paper is organized as follows:
-% There has been some success using simple kinematic prescriptions for biconical disc winds to model  AGN and quasar outflows \citep[][hereafter H13]{simlong2008,sim2010,higginbottom2013}.
-H13 successfully produced a benchmark model for BALQSOs.
-However, the model had two key drawbacks.
-First, an unrealistically low X-ray luminosity was required in order to prevent over-ionization of the outflow.
-Second, the model failed to produce the strong emission lines  required at low inclinations in a unified model.
-In this paper, we attempt to address these issues, and test the disc wind  unification model using Monte Carlo radiative transfer (MCRT) and photoionization  calculations.
-The paper is organised as follows.
 In section 2, we describe some of the important photoionization 
@@
 since then and are described by \cite{simmacro2005}, H13 and M15.  
-%A full description of the code will be published elsewhere; 
 We focus here on the specific changes made for this study
@@
 and to allow for clumping in the wind.
-%These studies contain extensive detail on the code,  so we only briefly describe the key elements of the global ionization calculation and other important aspects.
 
@@
 which are reprocessed by `macro-atoms' with associated transition probabilities.
-% according to radiative equilibrium, which assumes both statistical equilibrium 
-% and that radiative heating balances radiative cooling.
 In our case, for reasons of computational efficiency, we adopt the  hybrid macro-atom scheme 
@@
 AGN spectra of \LA.  H13 treated all atoms in a two-level approximation.
-% {\bf KSL:
-% I thought we were also doing He. JM: yep, corrected.}
 
@@
 is not required for macro-atom levels.
-% \begin{equation}
-% J_{\nu,i}=K_{pl}\nu^{\alpha_{pl}},
-% \end{equation}
-% for a band $i$, or an exponential 
-% \begin{equation}
-% J_{\nu,i}=K_{exp} e^{(-h\nu/k T_{exp})}.
-% \end{equation}
-% Here, $K_{exp}$, $K_{pl}$, $T_{exp}$ and $\alpha_{pl}$ are spectral fit parameters
-% deduced from the band-limited radiation field estimators.
-% The ionization rate out of ion $j$ can then be written as 
-% \begin{equation}
-% R_{j,j+1}(J)= 
-% \displaystyle{
-% n_j \left(C_{j} n_e + 
-% \sum_{band~i=0}^{n}~
-% {\int_{\nu_i}^{~\nu_i+1} \frac{4 \pi J_{\nu,i}\sigma_j(\nu)}  {h \nu} d\nu}
-% \right),}
-% \end{equation}
-% where $\sigma_j$ is the photoionization cross-section, $n_e$
-% is the electron density and $C_{j}$
-% represents the collisional ionization coefficient.
-% The recombination rate {\em into} ion $j$ is given by 
-% \begin{equation}
-% R_{j+1,j}(T_e) = (\alpha^j_{RR} + \alpha^j_{CR}) n_{j+1} n_e,
-% \end{equation}
-% where each $\alpha^j$ here is the recombination rate coefficient into the ground state of ion $j$.
-% The subscripts denote radiative and 
-% collisional (three-body) recombination, respectively. 
-% $T_e$ is the electron temperature.
-% %% We neglect recombination to and from excited states in the simple-ion calculation. 
-% For simple-ions, we use a dilute Boltzmann approximation to calculate 
-% the population of level $k$ in ionic stage $j$,
-% \begin{equation}
-% \frac{n_{jk}}{n_j} = \frac{W g_k}{z_j(T_R)} \exp(-E_k/kT_R).
-% \end{equation}
-% Here $z_j$ is the partition function of ionic stage $j$,
-% $T_R$ is the effective radiation temperature,
-% $E_k$ is the energy difference between level $k$ and the ground state,
-% and $g_k$ is the statistical weight of level $k$. 
-% We stress that this approximation is not required for ions
-% treated as macro-atoms. 
-% {\bf KSL: 
-% It seems a bit odd that you explain what we do with simple ions our old approach, but don't say what is done for macro-atoms,.  You only say it is not the other.
-% JM: We've shortened the section on simple-ions as agreed..}
 
@@
 $r_G = GM_{BH}/c^2$ is the gravitational radius.
-For a $10^9~M_\odot$ black hole, this is equal to $8.8\times10^{14}~{\rm cm}$ 
+For a $10^9~M_\odot$ BH, this is equal to $8.8\times10^{14}~{\rm cm}$ 
 or $\sim10^{-4}~{\rm pc}$.
@@
 regions with a MCRT code. 
-% Second, the addition of multiple additional degrees of
-% freedom in the model results in significantly wider parameter space.
-% Unfortunately, the physical scale lengths and density contrasts 
-% associated with these parameters are not well-constrained from observations.  
-% {\bf KSL: Reverse the order of these difficulties.  The most important is that it is not clear what kind of clumping an AGN wind has; the computational problem is a secondary one JM: Done..}
 Given the lack of knowledge about the actual type of clumping, we have adopted
@@
 
-% is that it moderates the ionization state and temperature structure of the plasma
-
-% Clumping the wind has an important effect on the ionization state and has
-% been proposed as a solution to the so-called `over-ionization problem' in 
-% disc winds \citep{hamann2013}. This is the main motivation for incorporating microclumping
-% into our model. This treatment is necessarily simple; it does not adequately
-% represent the complex substructures and stratifications in ionization
-% state we expect in AGN outflows. Nevertheless, this parameterization allows simple estimates
-% of the effect clumping might have on the ionization state and emergent 
-% line emission.
-% It is also encouraging that microclumping has been used 
-% successfully in fits to O-star wind spectra \citep{hillier1991eswingsmodel}.
-
 \subsection{The Simulation Grid}
-% Arriving at a next-generation model}
 
@@
 with $BI > 0$ at $\sim20\%$ of viewing angles (e.g. Knigge et al. 2010)
-\item Line emission emerging at low inclinations, with $EW\sim40$\AA in \civ\ \citep[e.g. ][]{shen2011}
+\item Line emission emerging at low inclinations, with $EW\sim40$\AA in \civline\ \citep[e.g. ][]{shen2011}
 \item H recombination lines with $EW\sim50$\AA in \la\ \citep[e.g. ][]{shen2011}
@@
 
-% the following criteria:
-% \begin{itemize}
-% \item Do the synthetic spectra exhibit UV absorption lines 
-% with $BI > 0$ at $\sim20\%$ of viewing angles (e.g. Knigge et al. 2010)?
-% \item Do the synthetic spectra show  line emission emerge at low inclinations, with $EW\sim40\AA$ in \civ \citep[e.g. ][]{shen2011}?
-% \item Do H recombination lines appear in the spectra, $EW\sim50\AA$ in \la 
-% \citep[e.g. ][]{shen2011}?
-% \item Do the spectra produce \mg\ and \al\ (LoBAL) absorption 
-% features with $BI > 0$ at a small subset of BAL angles?
-% \item Does the model spectra resemble quasar composite spectra?
-% \end{itemize}
-% Where $BI$ is the `Balnicity Index' (Weymann et al. 1991), given by
-% \begin{equation}
-% BI = \int^{25000}_{3000} \left( 1 - \frac{f(v)}{0.9} \right) dv.
-% \end{equation}
-% The constant $C=0$ everywhere, unless the normalized flux
-% has satisfied $f(v)<0.9$ continuously for at least $2000$~km~s$^{−1}$, 
-% whereby $C$ is set to $1$.
-
 In the next section, we present one of the most promising models,
@@
 \url{jhmatthews.github.io/quasar-wind-grid/}.
-
-% {\bf I still think we need to avoid using model to be a generic term to describe the outflow and the spectra.
-If you mean the spectra use "model spectra" or "synthetic spectra'.
-Note - the whole question of the model grid and the selection of one specific instantiation is not dealt with well.}
 
@@
 As shown in figure~\ref{fig:wind},
-the \civ\ line in the fiducial model is typically formed between 
+the \civline\ line in the fiducial model is typically formed between 
 $100-1000~r_G$ ($\sim10^{17}-10^{18}~\rm{cm}$).
@@
 and also compares favourably with microlensing measurements of the size of the
-\civ\ emission line region in the BALQSO H1413+117 \citep{odowd2015}.
+\civline\ emission line region in the BALQSO H1413+117 \citep{odowd2015}.
 
@@
 All the spectra are scaled to the model flux at $2000$\AA, expect for the 
-{\sl HST} STIS spectrum of PG0946+301, which is scaled using a continuum fit
+{\sl HST} STIS spectrum of PG0946+301, which is scaled to $1350$\AA
 due to the incomplete wavelength coverage.
@@
 \end{figure}
+
+\begin{figure} %fullpage
+\centering
+\includegraphics[width=1.0\textwidth]{figures/sed.png}
+\caption
+{
+Synthetic spectra at two viewing angles, 
+this time in frequency space and including the optical band,
+compared to the non-BAL SDSS quasar composite. The spectra are normalised to the flux at 
+$2000$\AA, then an offset of 2 is applied per spectrum for clarity. 
+}
+\label{fig:sed}
+\end{figure} %fullpage
 
@@
 FeLoBALQSOs are discussed in section 2.4.
-% Clearly, the absorption lines in the 
-% synthetic spectra at BALQSO-like angles do not match the composites; this
-% is {\em not} due to a failure of our model, but rather because a geometric mean
-% BALQSO composite spectrum tends to wash out the broad absorption features due to the wide
-% range of absorption characteristics. To demonstrate this, we show a comparison 
-% to a {\sl Hubble Space Telescope} STIS spectrum of the high BALnicity BALQSO PG0946+301 
-% (Arav et al. 2000) in figure \ref{fig:stis}.
 
@@
 line shapes (see e.g. Trump et al. 2006; Knigge et al 2008, Filiz Ak et al. 2014).
-In addition, the line profile shape is strongly dependent 
-on the density, ionization and velocity 
-profiles intersected by the line of sight. Thus, small tweaks of the velocity
-law and angular distributions of streamlines can dramatically alter
-the shape of the line.
+% In addition, the line profile shape is strongly dependent 
+% on the density, ionization and velocity 
+% profiles intersected by the line of sight. Thus, small tweaks of the velocity
+% law and angular distributions of streamlines can dramatically alter
+% the shape of the line.
 
@@
 such as {\em macroclumping} would be required \citep[e.g.][]{hamann2008,surlan2012}.
-Second, our wind does not have a significant scattering 
-contribution along sightlines which do not pass through the BAL region,
+Second, our wind does not have a significant scattering contribution 
+along sightlines which do not pass through the BAL region,
 meaning that any scattered component to the BAL troughs is absorbed by line opacity.
@@
 that an additional source of electron opacity is required, potentially
-in a polar direction above the disc.  
-% {\bf KSL: it sounds like what you are suggesting is a low density inner flow, our domain 2 stuff actually permits ...
-or indeed one might be able to produce this within SV is you adopted a different mass loss with radius assumption.
-JM: I am being deliberately
-% vague about what I am suggesting. I am saying there are three physical
-% possibilities: either wind itself causes this scattering contribution, which doesn't happen in our model, or you have partial covering, or you have some additional scatterer.}
+in a polar direction above the disc. We note the scattering contribution
+from plasma in polar regions is significant in some `outflow-from-inflow'
+simulations \citep{KP09, simproga2012}.
 
@@
 lines are not included in our modelling.
+
+In figure~\ref{fig:sed}, we show an $F_{\nu}$ spectrum with broader waveband coverage
+that includes the optical, showing that our synthetic spectra 
+also exhibit \ha\ and \hb\ emission. 
+In this panel, we include a low inclination and 
+also a very high inclination 
+spectrum, which looks underneath the wind cone. This model shows 
+strong line emission with very similar widths and line ratios to the quasar composites,
+although velocity projection effects mean the Balmer lines are double peaked, 
+as seen  in `disc emitter' systems.
+The increased line equivalent widths (EWs) are due to a weakened continuum at high inclination from wind attenuation and 
+disc foreshortening / limb darkening. This effect also 
+leads to a redder continuum slope, as seen in quasars, which is
+due to Balmer continuum and Balmer and Fe~\textsc{ii} line emission.
+The high inclination viewing angle is a physically motivated quasar model,
+but does show that a model such as this can naturally reproduce quasar emission lines
+if the emissivity of the wind is increased {\em with respect to the disc continuum}.
+In addition, it neatly demonstrates how a stratified outflow can naturally
+reproduce the range of ionization states seen in quasars.
 % This is because we do not fully solve the C level populations,
@@
 % or semi-forbidden transitions, as would be required.
-The critical density of the C~\textsc{iii}]~1909\AA\, line 
-is $n_e\sim10^{9.5}~\rm{cm^{-3}}$ \citep{wei1988}, which is higher than much of the 
-outer portion of our wind. 
-We therefore expect a model with these 
-parameters to produce a C~\textsc{iii}]~1909\AA\ line
-with a proper treament. We note, however, the the presence of
-this line in the spectrum of quasars does {\em not} prohibit denser material having a significant contribution to the spectrum.
+% The critical density of the C~\textsc{iii}]~1909\AA\, line 
+% is $n_e\sim10^{9.5}~\rm{cm^{-3}}$ \citep{wei1988}, which is higher than much of the 
+% outer portion of our wind. 
+% We therefore expect a model with these 
+% parameters to produce a C~\textsc{iii}]~1909\AA\ line
+% with a proper treament. We note, however, the the presence of
+% this line in the spectrum of quasars does {\em not} prohibit denser material having a significant contribution to the spectrum.
 
@@
 
-The shapes and widths of these lines
-match the composites fairly well, and the integrated 
-line luminosities are significant when compared to observations.
-However, there are a number of properties of the synthetic spectra
+Despite a number of successes, 
+there are a some properties of the synthetic spectra
 that are at odds with the observations. First, we find that the ratios of the 
-equivalent width of the \la\ and \mg\ lines
-to \civ\ is much lower than in the composite spectra. This problem 
-has also been seen in simpler photoionization models for the BLR \citep{netzer1990}.
+EW of the \la\ and \mgline\ lines
+to the EW of \civline\ is much lower than in the composite spectra. 
+This problem has also been seen in simpler photoionization models for the 
+BLR \citep{netzer1990}.
 It may be that a larger region of very dense ($n_e\sim10^{10}$cm$^{-3}$) 
-material is needed, this could correspond to a disc atmosphere or 
+material is needed, which could correspond to a disc atmosphere or 
 `transition region' (see e.g. Murray et al. 1995; Knigge et al. 1997). 
 While modest changes to geometry may permit this, the initial grid search 
-did not find a parameter space in which the \la\ or \mg\ equivalent widths
-were significantly higher. Second, we find that equivalent widths increase
-with inclinations, to the extent that significantly denser
+did not find a parameter space in which the \la\ or \mg\ EWs
+were significantly higher (see section~\ref{sec:param_sens}. 
+Second, we find that EWs increase
+with inclination, to the extent that significantly denser
 models can match the line EWs fairly well at low inclinations but will then
 possess overly strong red wings to the BAL P-Cygni profiles at high inclinations
-(see also figure~\ref{fig:lobal}).
-This angular dependence of EW is expected from a model in which the BLR radiates
+(see figures~\ref{fig:uvspec} and \ref{fig:sed}; also figure~\ref{fig:lobal}).
+This angular dependence is expected from a model in which the BLR radiates
 more isotropically than the disc, which in this case is foreshortened and limb darkened.
@@
 is clearly crucially important in determining the emergent broad 
-line equivalent widths, as suggested by, e.g., the analysis of \cite{risaliti2011}. 
+line EWs, as suggested by, e.g., the analysis of \cite{risaliti2011}. 
 We shall explore this question further in a future study.
-% However, the line-to-continuum ratios 
-% at low inclinations in our model are significantly weaker than the quasar 
-% composites. Increasing the density of the outflow, by altering the mass 
-% loss rate  or velocity law, can produce more line emission.
-% However, the red wing of the BAL profiles is generally stronger than 
-% seen in BALQSO spectra and composites. This suggests a fairly 
-% fundamental problem with a geometric unification model in which 
-% The line equivalent widths at high inclinations are
-% significantly affected by disc foreshortening and limb darkening.
-% The angular distribution of the disc radiation is clearly
-% crucially important in determining the emergent line ratios.  
-% {\bf KSL: This is a bit oddly explained. Our problem is at low inclination.  Note that I am a bit concerned with Fig 3; the model spectra and the observations look very different.}
-
-% {\bf I have to say I find this hard to understand.
-Are you trying to say that in CVs which we are know are thin disks with winds, the EW of the red-wing of emission lines increases with inclination angle ...
-which I think may be true, and so one would expect that in a unification model for AGN  it should do the same?
-And the fact that it does not, suggests that something else is going on in AGN.
-I also still think that you should move this discussion later in the paper and not bury it here.}
 
@@
 \centering
-\includegraphics[width=0.8\textwidth]{figures/lx_a05_pre.png}
+\includegraphics[width=0.9\textwidth]{figures/lx_a05_pre.png}
 \caption
@@
 compared to BALQSOs.
-
-% JM XXX -- only include this if it's true!
-% Our models slightly over-predict the emergent X-ray luminosity at BAL angles, 
-% although we are limited by poor sample sizes. 
-% % It is possible that this is due to our wind being overly optically thick to 
-% % electron scattering at angles which look through the wind. 
-% If BALQSOs were {\em intrinsically} 
-% X-ray weak \citep[as suggested by, e.g.][]{morabito2013},
-% our isotropic assumption for the X-ray source would be incorrect. 
-% A polar-biased X-ray source would result in a lower clumping factor being
-% required in our model. Our specific wind
-% prescription will also affect the opacities, densities and resultant
-% ionization structure, which can change the absorption 
-% characteristics and resultant luminosities.
-% Nevertheless, our input X-ray spectrum
-% now reproduces the X-ray properties of a luminous quasar as an output,
-% and at least some BAL angles match the observations.
-% This satisifies the first-order requirement for the X-ray properties of 
-% a unified quasar model.
 
@@
 magnitude higher X-ray luminosity and double the mass loss rate. As expected, 
-this results in far higher line equivalent widths, but fails to produce BALs because
+this results in far higher line EWs, but fails to produce BALs because
 the collisionally excited emission swamps the BAL profile. In addition,
@@
 kinematics we have used. Nevertheless, we suggest that the angular distribution
-of {\em both} the line and continuum emission is perhaps the crucial 
-aspect to understand.
-With this in mind, obtaining reliable orientation indicators appears
-to be a crucial observational task if we are to
+of both the line and continuum emission is perhaps the crucial 
+aspect to understand. With this in mind, obtaining reliable orientation 
+indicators appears to be a crucial observational task if we are to
 further our understanding of BAL outflows 
-and their connection, or lack thereof, to the broad line region.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% DISCUSSION???
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%  \section{Discussion: Parameter Sensitivity and Inclination Dependence}
-
-%  We have demonstrated that our fiducial model successfully reproduces much of
-%  the phenomenology of luminous AGN and quasars, with a few exceptions.
-%  Here, we discuss these shortcomings, by discussing parameter sensitivity
-%  and the dependence of line EWs on inclination.
-
-% \subsection{The Angular Distribution of Line And Continuum Emission}
-% \label{sec:angular}
-
-% \begin{figure}
-% \centering
-% \includegraphics[width=0.49\textwidth]{figures/hist_ew.png}
-% \caption
-% {
-% {\sl Top Panel:} A histogram of $1/2$ equivalent widths ($W_{\lambda}/2$)
-% for BALQSOs and non-BAL quasars from the {\sl SDSS DR7} quasar sample (Shen et al. 2011).
-% {\sl Bottom Panel:} $W_{\lambda,RW}$ as a function of inclination in our example model (black line).
-% The green shaded area indicates viewing angles which look into the wind (`BALQSO-like').
-% }
-% \label{fig:ew}
-% \end{figure}
-
-% % \begin{figure}
-% % \centering
-% % \includegraphics[width=0.45\textwidth]{figures/ew.png}
-% % \caption
-% % {
-% % $W_{\lambda,RW}$ as a function of inclination in our example model (red line).
-% % We also the mean $1/2$ equivalent width from DiPompeo et al. (2012) as a horizontal
-% % line, with the shaded area corresponding to the standard deviation.
-% % }
-% % \label{fig:ew}
-% % \end{figure}
-
-% In order to quantitatively assess how emission lines change with 
-% inclination when blue-shifted absorption 
-% may affect the line profile, we define the `red wing equivalent width' ($W_{\lambda,RW}$) as
-% \begin{equation}
-% W_{\lambda,RW} = \int_{\lambda_0}^{\lambda^\prime} \left( 1 - \frac{F_\lambda}{F_0} \right) d\lambda
-% \label{rwew}
-% \end{equation}
-% where $F_0$ is the continuum flux and the integral is calculated from $\lambda_0$, line centre,
-% to a wavelength $\lambda^\prime$ where the flux has returned to the continuum level.
-% This quantity is shown as a function of inclination in figure 5 for the \civ\ and \mg\ UV lines.
-% We also show the $W_{\lambda,RW}$ expected from isotropic line emission and a foreshortened 
-% and limb darkened disc  as well as $1/2$ equivalent widths from \cite{dipompeo2012b}.
-
-% BALQSOs and quasars generally possess very similar emission line properties 
-% \citep[e.g.][]{weymann1991,reichard2003}. This is illustrated in the 
-% the top panel of figure~\ref{fig:ew}, which shows histograms 
-% of \civ\ $1/2$ equivalent widths for BAL and non-BAL quasars from the {\sl SDSS DR7} quasar
-% sample \citep{shen2011}. Clearly the variation in $W_{\lambda,RW}$ at 
-% BAL-like and quasar-like angles is significantly larger than any systematic 
-% differences between the quasar and BALQSO samples.
-% The strong dependence of equivalent width on inclination is caused by decreased continuum
-% levels at high inclinations. This is due to a combination of
-% continuum attenuation through the wind, and the effect of limb darkening and foreshortening
-% in our classical thin disc. This presents a challenge to a geometric unification model
-% with an equatorial outflow.
-
-% % Clearly, the variation with inclination in our models is far greater than 
-% % than the variation between, and standard deviation within, quasar and BALQSO samples.  
-% % This presents a challenge to our model, as well as the geometric unification picture in general.
-% One obvious potential solution is to hypothesize a more isotropic distribution 
-% for the emergent condition than predicted by a classical thin disc. 
-% General relativistic effects -- specifically, light bending
-% and relativistic beaming -- can cause 
-% the accretion disc SED to become more isotropic \citep[e.g.][]{zhang1997,munozdarias2013}. 
-% However, we have verified using AGNSPEC \citep{hubeny2000,hubeny2001,hubenyhubeny1997}
-% that this effect is small in the UV wavelength regime, 
-% and the disc is still anisotropic.
-% Reprocessing by an extended outflow may also cause a more isotropic
-% continuum to emerge. Hints that light scattered off a spatially extended 
-% wind may contribute signiciantly to the emergent continuum come from radiative transfer
-% simulations \citep{simproga2012} and microlensing observations \citep{sluse2015}.
-% However, neither of these examples have sufficient reprocessing efficiencies to 
-% compensate for the disc anisotropy in this case.
-
-% An alternative explanation is that the BLR has the same anisotropic 
-% angular distribution of emission as the accretion disc.
-% Indeed, \cite{risaliti2011} find that EW distributions in quasars 
-% are consistent with anisotropic emission 
-% from optically thick, disc-like structures for {\em both} the continuum source and BLR. 
-% If this is the case, it has a dramatic affect on the intrinsic
-% BAL fraction inferred from flux-limited samples \citep{goodrich1997,krolikvoit1998}.
-
-% It is also possible that the equatorial paradigm invoked from early polarisation
-% studies \citep{goodrich1995, cohen1995,brotherton2006} 
-% is an over-simplification, or is incorrect. 
-% High brightness temperatures in some RL BALQSOs imply polar outflows \citep{zhou2006} 
-% and \cite{bruni2012} find that
-% RL BALQSOs possess similar radio spectral indices to normal RL quasars, 
-% suggestive of comparable inclinations. 
-% In addition, \cite{marin2013} find a bending angle of $\sim45^\circ$ is required to 
-% explain the polarisation dichotomy of type 1 and 2 AGN using an Elvis-type wind 
-% model (Elvis 2000). It is therefore possible 
-% that type 1 quasars and BALQSOs are generally viewed from a fairly narrow range of less
-% equatorial angles ($\sim0$-$45^\circ$), or {\em both} 
-% evolutionary and geometric explanations are required.
-% We suggest that future modelling should include predictions of polarisation signatures
-% from a detailed radiative transfer simulation, allowing direct 
-% comparison with spectropolarimetry of BALQSOs.
+and their connection, or lack thereof, to the 
+broad line region.
 

### 2015-12-18 paper_mnras.tex
version for collabs

@@
 with $BI > 0$ at $\sim20\%$ of viewing angles (e.g. Knigge et al. 2010)
-\item Line emission emerging at low inclinations, with $EW\sim40\AA$ in \civ\ \citep[e.g. ][]{shen2011}
-\item H recombination lines with $EW\sim50\AA$ in \la\ \citep[e.g. ][]{shen2011}
+\item Line emission emerging at low inclinations, with $EW\sim40$\AA in \civline\ \citep[e.g. ][]{shen2011}
+\item H recombination lines with $EW\sim50$\AA in \la\ \citep[e.g. ][]{shen2011}
 \item  \mg\ and \al\ (LoBAL) absorption features with $BI > 0$ at a subset of 
@@
 \end{figure}
+
+\begin{figure*}
+\centering
+\includegraphics[width=1.0\textwidth]{figures/sed.png}
+\caption
+{
+Synthetic spectra at two viewing angles, 
+this time in frequency space and including the optical band,
+compared to the non-BAL SDSS quasar composite. The spectra are normalised to the flux at 
+$2000$\AA, then an offset of 2 is applied per spectrum for clarity. 
+}
+\label{fig:sed}
+\end{figure*}
 

### 2015-12-18 paper.tex
few edits

@@
 compared to the non-BAL SDSS quasar composite. The spectra are normalised to the flux at 
-$2000$\AA, then an offset of 2 is applied per spectrum for clarity. 
+$2000$\AA, then an offset of 2 is applied per spectrum for clarity -- the dotted lines show the zero point of $F_\nu / F_{2000\AA}$ in each case.
 }
@@
 although velocity projection effects mean the Balmer lines are double peaked, 
-as seen  in `disc emitter' systems.
+as seen  in `disc emitter' systems \citep[e.g.][]{eracleous1994}.
 The increased line equivalent widths (EWs) are due to a weakened continuum at high inclination from wind attenuation and 
@@
 `transition region' (see e.g. Murray et al. 1995; Knigge et al. 1997).
+\nocite{knigge1998} 
 While modest changes to geometry may permit this, the initial grid search 

### 2015-12-18 paper.tex
few edits

@@
 did not find a parameter space in which the \la\ or \mg\ EWs
-were significantly higher (see section~\ref{sec:param_sens}. 
+were significantly higher (see section~\ref{sec:param_sens}). 
 Second, we find that EWs increase

### 2015-12-18 paper.tex
few edits

@@
 \def\la{Ly~$\alpha$}
-\def\ha{H~$\alpha$}
-\def\hb{H~$\beta$}
+\def\ha{H$\alpha$}
+\def\hb{H$\beta$}
 \def\civline{C~\textsc{iv}~$1550$\AA}
@@
 Second, we find that EWs increase
-with inclination, to the extent that significantly denser
+with inclination 
+(see figures~\ref{fig:uvspec} and \ref{fig:sed}; also figure~\ref{fig:lobal})
+, to the extent that significantly denser
 models can match the line EWs fairly well at low inclinations but will then
 possess overly strong red wings to the BAL P-Cygni profiles at high inclinations
-(see figures~\ref{fig:uvspec} and \ref{fig:sed}; also figure~\ref{fig:lobal}).
 This angular dependence is expected from a model in which the BLR radiates

### 2015-12-18 paper_mnras.tex
few edits

@@
 did not find a parameter space in which the \la\ or \mg\ EWs
-were significantly higher (see section~\ref{sec:param_sens}. 
+were significantly higher (see section~\ref{sec:param_sens}). 
 Second, we find that EWs increase
-with inclination, to the extent that significantly denser
+with inclination 
+(see figures~\ref{fig:uvspec} and \ref{fig:sed}; also figure~\ref{fig:lobal})
+, to the extent that significantly denser
 models can match the line EWs fairly well at low inclinations but will then
 possess overly strong red wings to the BAL P-Cygni profiles at high inclinations
-(see figures~\ref{fig:uvspec} and \ref{fig:sed}; also figure~\ref{fig:lobal}).
 This angular dependence is expected from a model in which the BLR radiates

### 2015-12-21 paper.tex
approaching submission ready

@@
 James~H.~Matthews$^1$\thanks{jm8g08@soton.ac.uk}, Christian~Knigge$^1$, 
-Nick~Higginbottom$^1$, Knox~S.~Long$^2$, Stuart~A.~Sim$^3$ and Sam~W.~Mangham$^1$
+Knox~S.~Long$^2$, Stuart~A.~Sim$^3$, Nick~Higginbottom$^1$ and Sam~W.~Mangham$^1$
 }
@@
 \begin{abstract} 
-Various unification schemes have been proposed to interpret the complex phenomenology 
-of quasars and luminous active galactic nuclei (AGN) in terms of  a simple axisymmetric 
-picture involving a central black hole, an accretion disc and an associated outflow.
-Here, we continue our tests of  this paradigm by comparing quasar spectra to 
-synthetic spectra of simple biconical disc wind models, produced with our state-of-the-art 
-Monte Carlo radiative transfer and photoionization code PYTHON.  
-Previously, we have shown that we could produce synthetic spectra 
-resembling those of observed broad absorption line (BAL) quasars 
-for plausible wind models, but only if the X-ray luminosity was limited to about  
-10$^{43}$~erg~s$^{-1}$. Here, we investigate the  degree to which
-clumping of the outflow allows us to 
-produce synthetic spectra in the rest-frame ultraviolet (UV) 
-that have the characteristics of quasars with X-ray luminosities as 
-large as 10$^{45}$ erg s$^{-1}$. 
-We conclude, perhaps not surprisingly, that clumping does maintain the ionization 
-state of the wind necessary for strong BAL features in the rest-frame UV at more 
-realistic X-ray luminosities. We examine the X-ray properties of our fiducial clumped model
-and find good agreement with existing X-ray samples of AGN and quasars.
-In addition, the dense, X-ray heated wind produces strong recombination and collisionally 
-excited line emission in, e.g., \la\ and \civline, to emerge at the low inclination, 
-`Type 1 quasar-like' angles. At the highest inclinations, the synthetic spectra 
-possess prominent \mg\ and \al\ BALs, the absorption features seen in LoBAL quasars. 
-Despite these successes, we are unable to reproduce all the emission lines seen in
-quasar spectra with the correct equivalent width 
-ratios in any of the models in our initial simulation grid,
-and we find an angular dependence of emission line equivalent width despite the 
-remarkable similarities in the observed spectral properties of BAL and non-BAL quasars.
-Overall, our work suggests that a biconical wind model
-reproduces much of the qualitative behaviour expected from a unified model. 
-However, we cannot yet provide quantitative matches with quasar properties at all 
-viewing angles; whether disc winds can successfully unify quasars is therefore 
-still an open question.
+Various unification schemes interpret the complex phenomenology of quasars and luminous active galactic nuclei (AGN) in terms of a simple picture involving a central black hole, an accretion disc and an associated outflow.
+Here, we continue our tests of this paradigm by comparing quasar spectra to synthetic spectra of biconical disc wind models, produced with our state-of-the-art Monte Carlo radiative transfer code.
+Previously, we have shown that we could produce synthetic spectra resembling those of observed broad absorption line (BAL) quasars, but only if the X-ray luminosity was limited to about
+10$^{43}$~erg~s$^{-1}$.
+Here, we show that clumping the outflow maintains the ionization state necessary for BAL features in the rest-frame UV at more realistic X-ray luminosities.
+Our fiducial model shows good agreement with X-ray properties of AGN and the dense, X-ray heated wind produces strong line emission in, e.g., \la\ and \civline at low inclinations.
+At high inclinations, the synthetic spectra possess prominent LoBAL features.
+Despite these successes, we cannot reproduce all the emission lines seen in quasar spectra with the correct equivalent width ratios, and we find an angular dependence of emission line equivalent width despite the remarkable similarities in the observed spectral properties of BAL and non-BAL quasars.
+Overall, our work suggests that a biconical wind can reproduce much of the qualitative behaviour expected from a unified model, but we cannot yet provide quantitative matches with quasar properties at all viewing angles.
+Whether disc winds can successfully unify quasars is therefore still an open question.
 \end{abstract}
 
-% \begin{keywords}
-% galaxies: active; accretion, accretion discs; (galaxies:) quasars: emission lines;
-% (galaxies:) quasars: absorption lines
-% \end{keywords}
+\begin{keywords}
+galaxies: active; accretion, accretion discs; (galaxies:) quasars: emission lines;
+(galaxies:) quasars: absorption lines; methods: numerical; radiative transfer.
+\end{keywords}
 
@@
 ultraviolet seen in approximately $20\%$ of quasars
-\citep{weymann1991, reichard2003, knigge2008, turnermiller2009, allen2011}.
+\citep{weymann1991, knigge2008, allen2011}.
 The simplest explanation for the incidence of 
@@
 the covering factor of the outflow. 
-Polarisation studies expect the wind to be roughly equatorial
+Polarisation studies suggest that the wind is roughly equatorial
 \citep{goodrich1995, cohen1995}, although there is also evidence
@@
 
-Despite the clear importance of disc winds in shaping quasar and AGN spectra,  
-much of the underlying outflow physics remains highly uncertain. 
-Several possible driving mechanisms have been proposed, including
+Despite the importance of disc winds in shaping quasar and AGN spectra,  
+much of the underlying outflow physics remains uncertain. 
+Several driving mechanisms have been proposed, including
 thermal pressure \citep{weymann1982, begelman1991}, magnetocentrifugal forces 
@@
 \citep{PSK2000,PK04,progakurosawa2010,proga2014}.  
-Nevertheless, clumpy winds offer an observationally motivated and theoretically 
+In summary, clumpy winds offer an observationally motivated and theoretically 
 predicted way to lower the ionization state of a plasma, possibly in tandem
@@
 
-We have been engaged in a project to determine whether it is possible to simulate the properties of the spectra of AGN, including BALQSOs, using simple kinematic prescriptions for biconical disc winds using a Monte Carlo radiative transfer (MCRT) code that calculates the ionization structure of the wind and simulates the spectra from such a system \citep[][hereafter H13 and H14]{simlong2008,sim2010,higginbottom2013,H14}.
+We have been engaged in a project to determine whether it is possible to simulate the properties of 
+the spectra of AGN, including BALQSOs, using simple kinematic prescriptions for biconical disc winds.
+To address this question, we use a Monte Carlo radiative transfer (MCRT) code that calculates the ionization structure of the wind 
+and simulates the spectra from such a system 
+\citep[][hereafter H13 and H14]{simlong2008,sim2010,higginbottom2013,H14}.
 The results have been encouraging in the sense that in H13, we showed we could produce simulated spectra that resembled that of BALQSOs, as long as the luminosity of the X-ray source was relatively low, of order \POW{43}{\LUM} and the mass loss rate was relatively high, of order the mass accretion rate.
@@
 a description of our clumping implementation and success criteria. 
-Section 4 contains the results from a clumped model, which we discuss results
-in comparison to observational data. Finally, we summarise our findings in section 5.
+Section 4 contains the results from a clumped model, 
+with comparisons to observational data, as well as some discussion. 
+Finally, we summarise our findings in section 5.
 
@@
 cylindrical geometry with azimuthal symmetry. 
-From some initial conditions in each cell, the code first calculates the ionization structure of the wind in a series of iterations.
+From some initial conditions in each cell (typically $T_e \sim 40,000$K in AGN, with 
+dilute LTE abundances), 
+the code first calculates the ionization structure of the wind in a series of iterations. 
 Each iteration in an ``ionization cycle'' consists of generating photons, actually photon packets, 
@@
 terms of indivisible energy quanta of radiant or kinetic energy 
-(`$r-$packets' and `$k-$packets' respectively; see also section~\ref{sec:photon_sources}). 
+(`$r-$packets' and `$k-$packets' respectively; see also section~\ref{sec:photon_sources}),
 which are reprocessed by `macro-atoms' with associated transition probabilities.
@@
 as simple atoms (see M15). In this study,
-only H and He are treated as a macro-atom, because 
-we expect recombination to be important
-in determining their level populations and resultant line emission, 
-and because we are especially interested in the contribution to 
+only H and He are treated as macro-atoms, because the process is computationally
+intensive, and we expect recombination to be particularly important
+in determining their level populations and resultant line emission.
+We are also especially interested in the contribution to 
 AGN spectra of \LA.  H13 treated all atoms in a two-level approximation.
@@
 rate equations between ions in non-LTE. This dispenses with a number of small assumptions 
-made in the modified Saha approach, is more numerically stable, and, in principle, allows 
-the direct addition of extra physical processes that would previously have necessitated 
-approximate treatments.
+made in the modified Saha approach, is more numerically stable, and
+prepares for a more accurate treatment of other physical processes in future. 
+% in principle, allows 
+% the direct addition of extra physical processes that would previously have necessitated 
+% approximate treatments.
 
@@
 We include two sources of r-packets in our model:
-An accretion disc and central X-ray source.
+An accretion disc and a central X-ray source.
 The accretion disc is assumed to be geometrically thin, but optically thick.
@@
 The X-ray source is treated as an isotropic sphere at the ISCO,
-which emits r-packets according to a power law in flux with index $\alpha_X$, of the form
+which emits $r$-packets according to a power law in flux with index $\alpha_X$, of the form
 \begin{equation}
@@
 produces the specified 2-10~keV luminosity, $L_X$.
-In addition to the disc and X-ray source, 
-the wind is able to reprocess radiation. However, new 
-photon packets are not produced in the wind (as in LK02). 
-Instead, this reprocessing is dealt with by enforcing strict
+Photons, or $r$-packets, produced by the accretion disc and central X-ray source
+are reprocessed by the wind. This reprocessing is dealt with by enforcing strict
 radiative equilibrium ({\em modulo} adiabatic cooling; see section~2.3)
-via an indivisible energy packet
-constraint (see Lucy 2002, M15).  
+via an indivisible energy packet constraint (see Lucy 2002, M15).  
+% In addition to the disc and X-ray source, 
+% the wind is able to reprocess radiation. However, new 
+% photon packets are not produced in the wind (as in LK02). 
+% Instead, this reprocessing is dealt with by enforcing strict
+% radiative equilibrium ({\em modulo} adiabatic cooling; see section~2.3)
+% via an indivisible energy packet
+% constraint (see Lucy 2002, M15).  
 % {\bf I confess, I do not understand what is being said here.
@@
 
-In our model, a biconical disc wind rises from the accretion 
+In the SV93 model, a biconical disc wind rises from the accretion 
 disc between launch radii $r_{min}$ and $r_{max}$.
@@
 \item Line emission emerging at low inclinations, with $EW\sim40$\AA in \civline\ \citep[e.g. ][]{shen2011}
-\item H recombination lines with $EW\sim50$\AA in \la\ \citep[e.g. ][]{shen2011}
+\item H recombination lines with $EW\sim50$\AA\ in \la\ \citep[e.g. ][]{shen2011}
 \item  \mg\ and \al\ (LoBAL) absorption features with $BI > 0$ at a subset of 
@@
 Contour plots showing the logarithm of some important 
-physical properties of the outflow. Symbols are defined in the text.
+physical properties of the outflow. The spatial scales are
+logarithmic and the $x$ and $z$ scales are not the same.
+Symbols are defined in the text.
 The solid black line marks a sphere at $1000~r_G$.
@@
 Figure~\ref{fig:wind} shows the physical properties of the wind.
-The wind rises slowly from the disc at first, with clump densities 
+The wind rises slowly from the disc at first, with densities within clumps
 of $n_H \sim 10^{11}~\rm{cm^{-3}}$ close to the disc plane, 
@@
 
-The total line luminosity also increases dramatically compared to H13. 
-This is primarily due to the higher X-ray luminosity increasing the bound-free
-heating in the plasma, which avoids over-ionization due to clumping.
+The total line luminosity also increases dramatically compared to the unclumped model
+described by H13. This is because the denser outflow can absorb the increased
+X-ray luminosity without becoming over-ionized, leading to a hot plasma which
+produces strong collisionally excited line emission.
 This line emission typically emerges on the edge of the wind
@@
 All the spectra are scaled to the model flux at $2000$\AA, expect for the 
-{\sl HST} STIS spectrum of PG0946+301, which is scaled to $1350$\AA
+{\sl HST} STIS spectrum of PG0946+301, which is scaled to $1350$\AA\
 due to the incomplete wavelength coverage.
@@
 
-Non-black saturation is observed in the absorption troughs of BALQSOs \citep{arav1999b,arav1999a}.
+The absorption profiles seen in BALQSOs are often non-black, but saturated, 
+with flat bases to the absorption troughs \citep{arav1999b,arav1999a}.
+%Non-black saturation is observed in the absorption troughs of BALQSOs \citep{arav1999b,arav1999a}.
 This is usually explained either as  partial covering of the continuum
@@
 The scattered light explanation is supported by spectropolarimetry results
-\citep{lamy2000}. Our spectra do not show nonblack saturation.
-Instead, we find black, saturated troughs at angles $i > 73^\circ$, and the BALs
-are non-saturated at lower inclinations. The reasons for this are inherent in the construction of our model. 
+\citep{lamy2000}. Our spectra do not show non-black, saturated profiles.
+We find black, saturated troughs at angles $i > 73^\circ$, and the BALs
+are non-saturated at lower inclinations. The reasons for this are inherent 
+in the construction of our model. 
 First, the microclumping assumption does not allow for 
@@
 
-We find significant collisionally excited line emission emerges
+Unlike H13, we now find significant collisionally excited line emission emerges
 at low inclinations in the synthetic spectra, particular in the \civ\ and \nv\
-lines. The improved treatment of recombination also results in a strong \la\ line. 
+lines. We also find a strong \la\ line and weak He~\textsc{ii}~$1640$\AA\ line
+as a result of our improved treatment of recombination using macro-atoms. 
 In the context of unification, this is a promising result, 
@@
 (see caption). The spectra do not contain the strong 
-C~\textsc{iii}]~1909\AA\, line seen in the quasar composite spectra,
-because semi-forbidden (intercombination)
-lines are not included in our modelling.
+C~\textsc{iii}]~1909\AA\ line seen in the quasar composite spectra, 
+but this is due to a limitation of our current treatment of C; semi-forbidden
+(intercombination) lines are not included in our modelling.
 
@@
 spectrum, which looks underneath the wind cone. This model shows 
-strong line emission with very similar widths and line ratios to the quasar composites,
-although velocity projection effects mean the Balmer lines are double peaked, 
-as seen  in `disc emitter' systems \citep[e.g.][]{eracleous1994}.
-The increased line equivalent widths (EWs) are due to a weakened continuum at high inclination from wind attenuation and 
-disc foreshortening / limb darkening. This effect also 
+strong line emission with very similar widths and line ratios to the quasar composites, and
+the Balmer lines are double peaked, due to velocity projection effects.  
+Such double-peaked lines are seen in so-called `disc emitter' systems 
+\citep[e.g.][]{eracleous1994} but not the majority of AGN.     
+The line equivalent widths (EWs) increase at high inclination
+due to a weakened continuum from wind attenuation, 
+disc foreshortening and limb darkening. This effect also 
 leads to a redder continuum slope, as seen in quasars, which is
 due to Balmer continuum and Balmer and Fe~\textsc{ii} line emission.
-The high inclination viewing angle is a physically motivated quasar model,
+This extreme $89^\circ$ viewing angle cannot represent a typical quasar within a unified model,
 but does show that a model such as this can naturally reproduce quasar emission lines
@@
 there are a some properties of the synthetic spectra
-that are at odds with the observations. First, we find that the ratios of the 
+that are at odds with the observations. First, the ratios of the 
 EW of the \la\ and \mgline\ lines
-to the EW of \civline\ is much lower than in the composite spectra. 
-This problem has also been seen in simpler photoionization models for the 
+to the EW of \civline\ are much lower than in the composite spectra. 
+Similar problems have also been seen in simpler photoionization models for the 
 BLR \citep{netzer1990}.
@@
 material is needed, which could correspond to a disc atmosphere or 
-`transition region' (see e.g. Murray et al. 1995; Knigge et al. 1997).
-\nocite{knigge1998} 
+`transition region' 
+(see e.g. Murray et al. 1995; Knigge et al. 1997). \nocite{knigge1998} 
 While modest changes to geometry may permit this, the initial grid search 
@@
 were significantly higher (see section~\ref{sec:param_sens}). 
-Second, we find that EWs increase
-with inclination 
-(see figures~\ref{fig:uvspec} and \ref{fig:sed}; also figure~\ref{fig:lobal})
-, to the extent that significantly denser
-models can match the line EWs fairly well at low inclinations but will then
-possess overly strong red wings to the BAL P-Cygni profiles at high inclinations
-This angular dependence is expected from a model in which the BLR radiates
-more isotropically than the disc, which in this case is foreshortened and limb darkened.
-It appears to contradict observations, which show remarkably uniform emission
+Second, we find that EWs increase with inclination 
+(see figures~\ref{fig:uvspec} and \ref{fig:sed}; also figure~\ref{fig:lobal}), 
+to the extent that, even though significantly denser
+models can match the line EWs fairly well at low inclinations, they will then
+possess overly strong red wings to the BAL P-Cygni profiles at high inclinations.
+The fact that the EW increase in our model are directly related to limb-darkening 
+and foreshortening of the continuum. 
+This appears to contradict observations, which show remarkably uniform emission
 line properties in quasars and BALQSOs \citep{weymann1991,dipompeo2012b}. 
 The angular distribution of the disc 
-continuum and line emission
-is clearly crucially important in determining the emergent broad 
+continuum and line emission is clearly crucially important in determining the emergent broad 
 line EWs, as suggested by, e.g., the analysis of \cite{risaliti2011}. 
@@
 
-The main motivation for including a treatment of clumping was
+The main motivation for adding clumping to the model was
 to avoid over-ionization of the wind in the presence of strong X-rays. 
@@
 we now find excellent agreement with AGN samples. The slight gradient from $20^\circ$ to
-$60^\circ$ in our models is caused by a combination of disc foreshortening/limb-darkening 
-(resulting in a lower $L_{2500}$ for higher inclinations) and the fact that the disk 
+$60^\circ$ in our models is caused by a combination of disc foreshortening and limb-darkening 
+(resulting in a lower $L_{2500}$ for higher inclinations), and the fact that the disk 
 is opaque, and thus the X-ray source subtends a smaller solid angle at high inclinations
@@
 The high inclination, `BALQSO-like' viewing angles show moderate agreement with the data,
-and are X-ray weak due to bound-free and electron scattering opacities in the wind.
+and are X-ray weak due to bound-free absorption and electron scattering in the wind.
 Typically, BALQSOs show strong X-ray absorption with columns 
@@
 and supports Hamann et al.'s (2013) suggestion that 
-this explains the weaker X-ray absorption in mini-BALs 
+geometric effects explain the weaker X-ray absorption in mini-BALs 
 compared to BALQSOs.
@@
 The parameter search presented here is by no means exhaustive, and
-we may be limited by the specific parameterisation (from SV93) of the outflow 
+we may be limited by the specific parameterisation of the outflow 
 kinematics we have used. Nevertheless, we suggest that the angular distribution
@@
 prescription for a biconical disc wind, with
-the aim of expanding on the work of H13 and assessing 
-the viability of such a model for geometric unification of quasars.
-We find the following main points:
+the aim of expanding on the work of H13. To do this, we introduced two main
+improvements: First, we included a simple treatment of clumping, and second, 
+we improved the modelling of recombination lines by treating H and He as
+`macro-atoms'. Having selected a fiducial model from an initial simulation grid,
+we assessed the viability of such a model for geometric 
+unification of quasars, and found the following main points:
 \begin{enumerate}
-\item We have introduced a simple treatment 
-of clumping in our model, and found that it moderates the ionization state
+\item Clumping moderates the ionization state
 sufficiently to allow for the 
@@
 \smallskip
-\item We find that a clumpy outflow model naturally 
+\item A clumpy outflow model naturally 
 reproduces the range of ionization states
@@
 \smallskip
-\item We find that the higher X-ray luminosity 
-causes a significant 
-increase in the strength of the  emission
-lines produced by the model. This is true both
-of collisionally excited resonance lines (such as \civ, \nv)
-and recombination lines (such as \la\ and \heiiline).
+\item The synthetic spectra show \la\ line and weak He~\textsc{ii}~$1640$\AA\ line
+as a result of our improved treatment of recombination using macro-atoms. We also see
+Balmer emission lines and a Balmer recombination continuum in the optical spectrum, but this
+is only really significant at high inclination where to continuum is suppressed.  
+\smallskip
+\item The higher X-ray luminosity causes a significant 
+increase in the strength of the collisionally excited emission
+lines produced by the model. 
 However, the equivalent width ratios of the emission lines do not match

### 2015-12-22 paper.tex
some more late changes

@@
 10$^{43}$~erg~s$^{-1}$.
-Here, we show that clumping the outflow maintains the ionization state necessary for BAL features in the rest-frame UV at more realistic X-ray luminosities.
+Here, we show that clumping the outflow can maintain the ionization state necessary for BAL features in the rest-frame UV at more realistic X-ray luminosities.
 Our fiducial model shows good agreement with X-ray properties of AGN and the dense, X-ray heated wind produces strong line emission in, e.g., \la\ and \civline at low inclinations.
 At high inclinations, the synthetic spectra possess prominent LoBAL features.
-Despite these successes, we cannot reproduce all the emission lines seen in quasar spectra with the correct equivalent width ratios, and we find an angular dependence of emission line equivalent width despite the remarkable similarities in the observed spectral properties of BAL and non-BAL quasars.
+Despite these successes, we cannot reproduce all the emission lines seen in quasar spectra with the correct equivalent-width ratios, and and we find an angular dependence of emission-line equivalent width despite the remarkable similarities in the observed emission line properties of BAL and non-BAL quasars.
 Overall, our work suggests that a biconical wind can reproduce much of the qualitative behaviour expected from a unified model, but we cannot yet provide quantitative matches with quasar properties at all viewing angles.
@@
 \begin{keywords}
-galaxies: active; accretion, accretion discs; (galaxies:) quasars: emission lines;
-(galaxies:) quasars: absorption lines; methods: numerical; radiative transfer.
+galaxies: active -- accretion, accretion discs -- (galaxies:) quasars: emission lines --
+(galaxies:) quasars: absorption lines -- methods: numerical -- radiative transfer.
 \end{keywords}
@@
 follows \cite{SV93}, and is described further by
-LK02, H13 and M15. A schematic is shown in figure~\ref{fig:cartoon},
+LK02, H13 and M15. A schematic is shown in Fig.~\ref{fig:cartoon},
 with key aspects marked. The general biconical
@@
 variables $r_{min}$, $\theta_{min}$, $f_V$, $\alpha$ and $R_v$.
-The grid points are shown in table 1.
+The grid points are shown in Table 1.
 The aim here was to first fix $M_{BH}$ and $\dot{m}$ to their H13 values,
@@
 \item UV absorption lines 
-with $BI > 0$ at $\sim20\%$ of viewing angles (e.g. Knigge et al. 2010)
-\item Line emission emerging at low inclinations, with $EW\sim40$\AA in \civline\ \citep[e.g. ][]{shen2011}
-\item H recombination lines with $EW\sim50$\AA\ in \la\ \citep[e.g. ][]{shen2011}
+with $BI > 0$ at $\sim20\%$ of viewing angles (e.g. Knigge et al. 2010);
+\item Line emission emerging at low inclinations, with $EW\sim40$\AA in \civline\ \citep[e.g. ][]{shen2011};
+\item H recombination lines with $EW\sim50$\AA\ in \la\ \citep[e.g. ][]{shen2011};
 \item  \mg\ and \al\ (LoBAL) absorption features with $BI > 0$ at a subset of 
-BAL viewing angles
+BAL viewing angles;
 \item Verisimilitude with quasar composite spectra.
@@
 \begin{equation}
-BI = \int^{25000}_{3000} \left( 1 - \frac{f(v)}{0.9} \right) dv.
+BI = \int^{25000~{\rm km~s}^{-1}}_{3000~{\rm km~s}^{-1}} \left( 1 - \frac{f(v)}{0.9} \right) dv.
 \end{equation}
@@
 and discuss these results in the context of the criteria 
-presented in section 3.4. The parameters of this model are shown in table~2.
+presented in section 3.4. The parameters of this model are shown in Table~2.
 Parameters differing from the benchmark model of H13 are 
@@
 \noindent
-Figure~\ref{fig:wind} shows the physical properties of the wind.
+Fig.~\ref{fig:wind} shows the physical properties of the wind.
 The wind rises slowly from the disc at first, with densities within clumps
@@
 in the base of the wind giving way to highly ionized plasma further out.
-This is illustrated in figure~\ref{fig:wind} 
+This is illustrated in Fig.~\ref{fig:wind} 
 by the panels showing the ion fraction $F=n_j/n_{tot}$ of some important ions.
@@
 \begin{equation}
-U_H = \frac{4\pi}{n_H c}\int_{13.6{\rm{eV}}}^{\infty}\frac{{J_{\nu}d\nu}}{h\nu}.
+U_H = \frac{4\pi}{n_H c}\int_{13.6{\rm{eV}} / h}^{\infty}\frac{{J_{\nu}d\nu}}{h\nu}.
 \end{equation}
 \noindent where $\nu$ denotes photon 
-frequency. Shown in figure~\ref{fig:wind},
+frequency. Shown in Fig.~\ref{fig:wind},
 the ionization parameter is a useful measure of the global ionization state,
@@
 % Einstein A coefficient for the line. 
-As shown in figure~\ref{fig:wind},
+As shown in Fig.~\ref{fig:wind},
 the \civline\ line in the fiducial model is typically formed between 
@@
 \noindent
-Figure~\ref{fig:uvspec} shows the synthetic spectrum in the UV from the fiducial model. 
+Fig.~\ref{fig:uvspec} shows the synthetic spectrum in the UV from the fiducial model. 
 To assess the ability of the synthetic spectra to match real 
@@
 We show a cartoon illustrating how geometric effects determine
-the output spectra in figure~\ref{fig:sightline}.
+the output spectra in Fig.~\ref{fig:sightline}.
 
@@
 SDSS DR7 Quasar catalog, and correspond to mean values with standard deviations in log space
-from a subsample with $8.5>\log(M_{BH})<9.5$ and $1.5<\log (L_{bol}/L_{edd}) < 0$,
+from a subsample with $8.5>\log(M_{BH})<9.5$ and $1.5<\log (L_{bol}/L_{Edd}) < 0$,
 where the BH mass is a \civ\ virial estimate. 
@@
 we show line luminosities and monochromatic continuum luminosities
-from the synthetic spectra in table~\ref{line_lums}. These are compared to
+from the synthetic spectra in Table~\ref{line_lums}. These are compared to
 mean values from a subsample of the SDSS DR7 quasar catalog (Shen et al. 2011) 
@@
 
-In figure~\ref{fig:sed}, we show an $F_{\nu}$ spectrum with broader waveband coverage
+In Fig.~\ref{fig:sed}, we show an $F_{\nu}$ spectrum with broader waveband coverage
 that includes the optical, showing that our synthetic spectra 
@@
 Second, we find that EWs increase with inclination 
-(see figures~\ref{fig:uvspec} and \ref{fig:sed}; also figure~\ref{fig:lobal}), 
+(see Fig.~\ref{fig:uvspec} and Fig.~\ref{fig:sed}; also Fig.~\ref{fig:lobal}), 
 to the extent that, even though significantly denser
@@
 
-Figure~\ref{fig:xray} shows the emergent
+Fig.~\ref{fig:xray} shows the emergent
 monochromatic luminosity ($L_\nu$) at 2~keV and 
@@
 at the highest inclinations. Line profiles in velocity space 
-for \civ, \al\ and \mg, are shown in figure~\ref{fig:lobal} for a range
+for \civ, \al\ and \mg, are shown in Fig.~\ref{fig:lobal} for a range
 of BALQSO viewing angles. We find that ionization stratification
@@
 to briefly explore how specialised this model is, and how small parameter
-changes can affect the synthetic spectra. Figure~\ref{fig:grid}
+changes can affect the synthetic spectra. Fig.~\ref{fig:grid}
 shows the EW at a low inclination, and $BI$ at a high inclination for the simulation
@@
 reproduces the range of ionization states
-expected in quasars, due to it's stratified density
+expected in quasars, due to its stratified density
 and temperature structure. 
@@
 lines produced by the model. 
-However, the equivalent width ratios of the emission lines do not match
+However, the equivalent-width ratios of the emission lines do not match
 observations, suggesting that a greater volume of dense ($n_e\sim10^{10}$~cm$^{-3}$)

### 2015-12-22 generate/agnspec_fig/agnspec.py
added generate

@@ -1,0 +1,180 @@
+#!/usr/bin/env python
+from pylab import *
+import py_read_output as r 
+import py_plot_output as pl
+import py_plot_util as util 
+import os, sys 
+from constants import *
+import numpy as np
+import pretty
+from pretty import *
+
+D = 100.0 * PARSEC
+
+def Ledd (m):
+
+	'''
+	calculates eddington luminosity for a solar mass m
+	
+	Args:
+		m	mass in solar masses
+	
+	returns:
+		Eddington luminosity in ergs s^-1, float
+	'''
+	
+	m *= MSOL
+	
+	consts = (4.0 * PI * G * C * MPROT ) / THOMPSON
+	
+	L = consts * m
+	
+	return L
+
+def run_agnspec(fname, mass=1e9, mdot=5, angm=0, alpha=0.01, inc=80):
+
+	mu = np.cos(inc / 180.0 * np.pi)
+
+	print inc, mu
+
+	param_string = "mass=%8.4e,mdot=%8.4e,angm=%.6f,alpha=%.6f,mu=%8.4e,savename=\"%s\"" % (mass, mdot, angm, alpha, mu, fname)
+
+	print param_string
+	os.system("idl -e 'agnspec,%s' > idl.out" % param_string)
+
+	return 0
+
+def read_agnspec(fname):
+
+	nu, lnu = np.loadtxt(fname, unpack=True, usecols=(0,1))
+
+	wave = (C / nu) / ANGSTROM
+
+	llambda = nu * lnu / wave
+
+	flambda = llambda / 4.0 / PI / (D*D)
+
+	return wave, flambda
+
+def mdot_from_edd ( edd, m , eta = 0.1):
+
+	''' 
+	calculates an accretion rate from an eddington fraction
+	Args:
+		edd_frac		eddington fraction
+		m			mass of central object in solar masses
+		eta			accretion efficiency, set to 1 (0.1 more realistic)
+	
+	returns:
+		mdot in solar masses / yr
+	'''
+	
+	L = Ledd (m)		# eddington luminosity
+	
+	mdot = edd * L / ( (C ** 2) )
+	
+	mdot *= 1.0 / eta
+	
+	mdot = mdot * ( YR ) / MSOL	# normalise units
+	
+	return mdot
+
+def run_grid(masses, edd_frac, spin, incs):
+
[…]

### 2015-12-22 generate/angles/angle_plot.py

@@ -1,0 +1,284 @@
+#!/usr/bin/env python
+from pylab import *
+import py_read_output as r 
+import py_plot_output as pl
+import py_plot_util as util 
+import os, sys 
+from constants import *
+import numpy as np
+from collections import OrderedDict
+from plot_norm import make_f, get_continuum
+import plot_norm as _plot_norm
+from pretty import *
+try:
+	from thread import get_ident as _get_ident
+except ImportError:
+	from dummy_thread import get_ident as _get_ident
+
+
+def add_after(pf, key_after, newkey, newval):
+
+	before_dict = OrderedDict()
+	after_dict = OrderedDict()
+	new_dict = OrderedDict([(newkey, newval)])
+	after = False 
+
+	for key,val in pf.viewitems():
+
+		if after:
+			after_dict[key] = val
+		else:
+			before_dict[key] = val
+
+		if key == key_after:
+			after = True
+
+
+	all_dicts = OrderedDict(before_dict.items() + new_dict.items()  + after_dict.items())
+
+	return all_dicts
+
+def vel_nu (nu, nu_0):
+	'''
+	Returns the velocity of a frequency nu with respect to 
+	line centre nu_0 in units of cm/s
+	'''
+	delta_nu = nu - nu_0
+	
+	vel = C * delta_nu / nu_0
+	
+	return vel
+
+def nu_vel(v, nu_0):
+	'''
+	Returns the frequency of a velocity v with respect to 
+	line centre nu_0 in units of cm/s
+	'''
+	
+	nu =  (nu_0 * v / C) + nu_0
+	
+	return nu
+
+
+def normalize(w, f):
+
+	a = get_continuum(w, f, [1215,1550,1400,2800], lmin=1300, lmax=3000, deg=2)
+
+	#fnorm = f/make_f(a, w)
+
+	#fnorm = f / util.get_flux_at_wavelength(w,f,1450)
+
+	return make_f(a, w)
+
+
+
+def make_c4_plot(s, name, angmin=70, angmax=82):
+
+	nangles = len(s.colnames) - 9
+
+	nu_c4 = C / (1550.0 * ANGSTROM)
+	big_tick_labels(18)
+
[…]

### 2015-12-22 generate/cartoon/SV_cartoon.py

@@ -1,0 +1,97 @@
+'''
+SV_cartoon.py 
+
+This script creates the cartoon figure for 
+the 2014 CV paper. The data were scraped from Dexter.
+'''
+
+import matplotlib.mlab as mlab
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib as mpl
+
+plt.xkcd()
+
+
+#mpl.rcParams['pdf.use14corefonts'] = True
+#mpl.rc('font',**{'family':'sans-serif','sans-serif':['Helvetica']})
+## for Palatino and other serif fonts use:
+#rc('font',**{'family':'serif','serif':['Palatino']})
+#mpl.rc('text', usetex=True)
+
+thetamin=72.0
+thetamax=80.0
+diskmax=25.0
+xmin=10.0
+xmax=18.0
+rstar=2.0
+
+xwindmax=40.0
+zwindmax=(xwindmax-xmin)*np.tan(np.radians(90.0-thetamin))
+
+
+posx=np.arange(xmin,xwindmax,(xmax-xmin)/10.0)
+ymin1=[]
+ymax1=[]
+
+x=np.array([xmin,xmax,xwindmax])
+y1=np.array([0.0,(xmax-xmin)*np.tan(np.radians(90.0-thetamin)),(xwindmax-xmin)*np.tan(np.radians(90.0-thetamin))])
+y2=np.array([0.0,0.0,(xwindmax-xmax)*np.tan(np.radians(90.0-thetamax))])
+
+lsize=14
+tsize=16 
+
+fig=plt.figure()
+ax=fig.add_subplot(1,1,1)
+ax.plot(x,y1,x,y2,color='black')
+ax.plot(-1.0*x,y1,-1.0*x,y2,color='black')
+ax.plot(-1.0*x,-1.0*y1,-1.0*x,-1.0*y2,color='black')
+ax.plot(x,-1.0*y1,x,-1.0*y2,color='black')
+ax.set_xlim([-1.0*xwindmax,xwindmax])
+plt.fill_between(x,y1, y2, facecolor='0.9', interpolate=True)
+plt.fill_between(-1.0*x,y1, y2, facecolor='0.9', interpolate=True)
+plt.fill_between(x,-1.0*y1, -1.0*y2, facecolor='0.9', interpolate=True)
[…]

### 2015-12-22 generate/cartoon/just_text.py

@@ -1,0 +1,94 @@
+'''
+SV_cartoon.py 
+
+This script creates the cartoon figure for 
+the 2014 CV paper. The data were scraped from Dexter.
+'''
+
+import matplotlib.mlab as mlab
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib as mpl
+
+#plt.xkcd()
+
+
+#mpl.rcParams['pdf.use14corefonts'] = True
+#mpl.rc('font',**{'family':'sans-serif','sans-serif':['Helvetica']})
+## for Palatino and other serif fonts use:
+#rc('font',**{'family':'serif','serif':['Palatino']})
+#mpl.rc('text', usetex=True)
+
+thetamin=72.0
+thetamax=80.0
+diskmax=25.0
+xmin=10.0
+xmax=18.0
+rstar=2.0
+
+xwindmax=40.0
+zwindmax=(xwindmax-xmin)*np.tan(np.radians(90.0-thetamin))
+
+
+posx=np.arange(xmin,xwindmax,(xmax-xmin)/10.0)
+ymin1=[]
+ymax1=[]
+
+x=np.array([xmin,xmax,xwindmax])
+y1=np.array([0.0,(xmax-xmin)*np.tan(np.radians(90.0-thetamin)),(xwindmax-xmin)*np.tan(np.radians(90.0-thetamin))])
+y2=np.array([0.0,0.0,(xwindmax-xmax)*np.tan(np.radians(90.0-thetamax))])
+
+lsize=14
+tsize=16 
+
+fig=plt.figure()
+ax=fig.add_subplot(1,1,1)
+ax.plot(x,y1,x,y2,color='black', linewidth=0)
+ax.plot(-1.0*x,y1,-1.0*x,y2,color='black', linewidth=0)
+ax.plot(-1.0*x,-1.0*y1,-1.0*x,-1.0*y2,color='black', linewidth=0)
+ax.plot(x,-1.0*y1,x,-1.0*y2,color='black', linewidth=0)
+ax.set_xlim([-1.0*xwindmax,xwindmax])
+
+# plt.fill_between(x,y1, y2, facecolor='0.9', interpolate=True)
+# plt.fill_between(-1.0*x,y1, y2, facecolor='0.9', interpolate=True)
+# plt.fill_between(x,-1.0*y1, -1.0*y2, facecolor='0.9', interpolate=True)
[…]

### 2015-12-22 generate/cartoon/xkcd_cart.py

@@ -1,0 +1,100 @@
+'''
+SV_cartoon.py 
+
+This script creates the cartoon figure for 
+the 2014 CV paper. The data were scraped from Dexter.
+'''
+
+import matplotlib.mlab as mlab
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib as mpl
+
+plt.xkcd()
+
+
+#mpl.rcParams['pdf.use14corefonts'] = True
+#mpl.rc('font',**{'family':'sans-serif','sans-serif':['Helvetica']})
+## for Palatino and other serif fonts use:
+#rc('font',**{'family':'serif','serif':['Palatino']})
+#mpl.rc('text', usetex=True)
+
+thetamin=72.0
+thetamax=80.0
+diskmax=25.0
+xmin=10.0
+xmax=18.0
+rstar=2.0
+
+xwindmax=40.0
+zwindmax=(xwindmax-xmin)*np.tan(np.radians(90.0-thetamin))
+
+
+posx=np.arange(xmin,xwindmax,(xmax-xmin)/10.0)
+ymin1=[]
+ymax1=[]
+
+x=np.array([xmin,xmax,xwindmax])
+y1=np.array([0.0,(xmax-xmin)*np.tan(np.radians(90.0-thetamin)),(xwindmax-xmin)*np.tan(np.radians(90.0-thetamin))])
+y2=np.array([0.0,0.0,(xwindmax-xmax)*np.tan(np.radians(90.0-thetamax))])
+
+lsize=14
+tsize=16 
+
+fig=plt.figure()
+ax=fig.add_subplot(1,1,1)
+ax.plot(x,y1,x,y2,color='black')
+ax.plot(-1.0*x,y1,-1.0*x,y2,color='black')
+ax.plot(-1.0*x,-1.0*y1,-1.0*x,-1.0*y2,color='black')
+ax.plot(x,-1.0*y1,x,-1.0*y2,color='black')
+ax.set_xlim([-1.0*xwindmax,xwindmax])
+plt.fill_between(x,y1, y2, facecolor='0.9', interpolate=True)
+plt.fill_between(-1.0*x,y1, y2, facecolor='0.9', interpolate=True)
+plt.fill_between(x,-1.0*y1, -1.0*y2, facecolor='0.9', interpolate=True)
+plt.fill_between(-1.0*x,-1.0*y1, -1.0*y2, facecolor='0.9', interpolate=True)
[…]

### 2015-12-22 generate/egv1/egv.py

@@ -1,0 +1,55 @@
+#!/usr/bin/env python
+from pylab import *
+import py_read_output as r 
+import py_plot_output as pl
+import py_plot_util as util 
+import os, sys 
+from constants import *
+import numpy as np
+from pretty import *
+
+eddmod =[0.2]
+mbhmod = [1e9]
+
+
+mbh, l = np.loadtxt("balqsos_mbh_ledd.dat", unpack=True, usecols=(2,3))
+
+names1, names2 = np.loadtxt("balqsos_mbh_ledd.dat", unpack=True, usecols=(0,1), dtype="str")
+
+
+names = []
+locs = []
+for i in range(len(names1)):
+
+	names.append(names1[i] + ' ' + names2[i])
+
+	print names[i]
+
+	#if names[i] == 'PG 1001+054' or names[i] == 'Mkn 231':
+	if names[i] == 'Mkn 231':
+		locs.append(i)
+#names = names1 + names2
+#print names
+
+set_pretty()
+
+colors=get_colors()
+
+scatter(10.0**mbh, 10.0**l, marker="x", s=100, c="k")
+scatter(mbhmod, eddmod, marker="*", s=100, c="r")
+
+
+for j in locs:
+	print mbh[j], l[j], names[j]
+	text(mbh[j], l[j], names[j])
+
+xlabel(r"$M_{BH} (M_\odot)$", fontsize=20)
+ylabel(r"$L/L_{edd}$", fontsize=20)
+
+loglog()
+
+savefig("egv.png", dpi=500)
+
+
+
+

### 2015-12-22 generate/ew/ew.py

@@ -1,0 +1,280 @@
+#from plot_norm import *
+import numpy as numpy
+from pylab import *
+import os, sys
+from cobra_sub import smooth
+import py_read_output as r 
+import py_plot_output as pl
+import py_plot_util as util 
+import matplotlib.pyplot as plt
+import matplotlib.gridspec as gridspec
+from plot_norm import *
+from constants import *
+from pretty import *
+
+set_pretty()
+
+def get_continuum(wave, spec, lines = [1215,1400,1550,1640,2800,1900], lmin=1000, lmax = 2000, deg = 3):
+
+	i_jump = (wave > lmin) * (wave < lmax)
+
+	i_lines = np.zeros(len(wave), dtype=bool)
+
+	for i in range(len(wave)):
+
+		comp = lines - wave[i]
+		comp = np.absolute(comp)
+
+		i_line = (comp < 100)
+
+		if np.sum(i_line) == 0:
+			i_lines[i] = True
+		else:
+			i_lines[i] = False		
+
+	i_select = i_jump * i_lines
+
+	continuum_points = wave[i_select]
+
+	#print continuum_points, i_select
+
+	coefficients = np.polyfit(continuum_points, spec[i_select], deg)
+
+	return coefficients
+
+def make_f(a, x):
+
+ 	deg = len(a)
+ 	y = 0
+
+ 	for i in range(deg):
+ 		y += a[i] * (x**(deg - i - 1))
+
+ 	return y
+
+def find_line(w,f, wline = 6563, window_size=100, rw = False):
+
+	fabs_w = np.fabs(w - wline)
+
+	if rw:
+		w_bool = (fabs_w < window_size) * (w > wline)
+	else:
+		w_bool = (fabs_w < window_size) 
+
+	# create windows to look in
+	w_window = w
+	f_window = w_bool * f
+
+	# return arrays with length over specified 2*window_size
+	return w_window[f_window >0], f_window[f_window >0]
+
+
+def get_line_EW(s, angle_string = "A20P0.50", wline=6563, delta = 1.2):
+
+
+
+	line_w, line_f = find_line(s, angle_string, w=wline)
+
+	#print "Finding EW of line at %i A" % wline
+	
+	cont_t = line_f[1:10]
[…]

### 2015-12-22 generate/ew/ew_with_hist.py

@@ -1,0 +1,308 @@
+#from plot_norm import *
+import numpy as numpy
+from pylab import *
+import os, sys
+from cobra_sub import smooth
+import py_read_output as r 
+import py_plot_output as pl
+import py_plot_util as util 
+import matplotlib.pyplot as plt
+import matplotlib.gridspec as gridspec
+from plot_norm import *
+from constants import *
+from pretty import *
+
+set_pretty()
+
+def get_continuum(wave, spec, lines = [1215,1400,1550,1640,2800,1900], lmin=1000, lmax = 2000, deg = 3):
+
+	i_jump = (wave > lmin) * (wave < lmax)
+
+	i_lines = np.zeros(len(wave), dtype=bool)
+
+	for i in range(len(wave)):
+
+		comp = lines - wave[i]
+		comp = np.absolute(comp)
+
+		i_line = (comp < 100)
+
+		if np.sum(i_line) == 0:
+			i_lines[i] = True
+		else:
+			i_lines[i] = False		
+
+	i_select = i_jump * i_lines
+
+	continuum_points = wave[i_select]
+
+	#print continuum_points, i_select
+
+	coefficients = np.polyfit(continuum_points, spec[i_select], deg)
+
+	return coefficients
+
+def make_f(a, x):
+
+ 	deg = len(a)
+ 	y = 0
+
+ 	for i in range(deg):
+ 		y += a[i] * (x**(deg - i - 1))
+
+ 	return y
+
+def find_line(w,f, wline = 6563, window_size=100, rw = False):
+
+	fabs_w = np.fabs(w - wline)
+
+	if rw:
+		w_bool = (fabs_w < window_size) * (w > wline)
+	else:
+		w_bool = (fabs_w < window_size) 
+
+	# create windows to look in
+	w_window = w
+	f_window = w_bool * f
+
+	# return arrays with length over specified 2*window_size
+	return w_window[f_window >0], f_window[f_window >0]
+
+
+def get_line_EW(s, angle_string = "A20P0.50", wline=6563, delta = 1.2):
+
+
+
+	line_w, line_f = find_line(s, angle_string, w=wline)
+
+	#print "Finding EW of line at %i A" % wline
+	
+	cont_t = line_f[1:10]
[…]

### 2015-12-22 generate/ew/ew_xkcd.py

@@ -1,0 +1,277 @@
+#from plot_norm import *
+import numpy as numpy
+from pylab import *
+import os, sys
+from cobra_sub import smooth
+import py_read_output as r 
+import py_plot_output as pl
+import py_plot_util as util 
+import matplotlib.pyplot as plt
+import matplotlib.gridspec as gridspec
+from plot_norm import *
+from constants import *
+from pretty import *
+
+#set_pretty()
+xkcd()
+
+def get_continuum(wave, spec, lines = [1215,1400,1550,1640,2800,1900], lmin=1000, lmax = 2000, deg = 3):
+
+	i_jump = (wave > lmin) * (wave < lmax)
+
+	i_lines = np.zeros(len(wave), dtype=bool)
+
+	for i in range(len(wave)):
+
+		comp = lines - wave[i]
+		comp = np.absolute(comp)
+
+		i_line = (comp < 100)
+
+		if np.sum(i_line) == 0:
+			i_lines[i] = True
+		else:
+			i_lines[i] = False		
+
+	i_select = i_jump * i_lines
+
+	continuum_points = wave[i_select]
+
+	#print continuum_points, i_select
+
+	coefficients = np.polyfit(continuum_points, spec[i_select], deg)
+
+	return coefficients
+
+def make_f(a, x):
+
+ 	deg = len(a)
+ 	y = 0
+
+ 	for i in range(deg):
+ 		y += a[i] * (x**(deg - i - 1))
+
+ 	return y
+
+def find_line(w,f, wline = 6563, window_size=100, rw = False):
+
+	fabs_w = np.fabs(w - wline)
+
+	if rw:
+		w_bool = (fabs_w < window_size) * (w > wline)
+	else:
+		w_bool = (fabs_w < window_size) 
+
+	# create windows to look in
+	w_window = w
+	f_window = w_bool * f
+
+	# return arrays with length over specified 2*window_size
+	return w_window[f_window >0], f_window[f_window >0]
+
+
+def get_line_EW(s, angle_string = "A20P0.50", wline=6563, delta = 1.2):
+
+
+
+	line_w, line_f = find_line(s, angle_string, w=wline)
+
+	#print "Finding EW of line at %i A" % wline
+	
[…]

### 2015-12-22 generate/ew/line_lums.py

@@ -1,0 +1,159 @@
+#!/usr/bin/env python
+from pylab import *
+import py_read_output as r 
+import py_plot_output as pl
+import py_plot_util as util 
+import os, sys 
+from constants import *
+import numpy as np
+import pretty
+
+
+def get_continuum(wave, spec, lines = [1215,1400,1550,1640,2800,1900], lmin=1000, lmax = 2000, deg = 3):
+
+	i_jump = (wave > lmin) * (wave < lmax)
+
+	i_lines = np.zeros(len(wave), dtype=bool)
+
+	for i in range(len(wave)):
+
+		comp = lines - wave[i]
+		comp = np.absolute(comp)
+
+		i_line = (comp < 100)
+
+		if np.sum(i_line) == 0:
+			i_lines[i] = True
+		else:
+			i_lines[i] = False		
+
+	i_select = i_jump * i_lines
+
+	continuum_points = wave[i_select]
+
+	#print continuum_points, i_select
+
+	coefficients = np.polyfit(continuum_points, spec[i_select], deg)
+
+	return coefficients
+
+def make_f(a, x):
+
+ 	deg = len(a)
+ 	y = 0
+
+ 	for i in range(deg):
+ 		y += a[i] * (x**(deg - i - 1))
+
+ 	return y
+
+def find_line(w,f, wline = 6563, window_size=100, rw = False):
+
+	fabs_w = np.fabs(w - wline)
+
+	if rw:
+		w_bool = (fabs_w < window_size) * (w > wline)
+	else:
+		w_bool = (fabs_w < window_size) 
+
+	# create windows to look in
+	w_window = w
+	f_window = w_bool * f
+
+	# return arrays with length over specified 2*window_size
+	return w_window[f_window >0], f_window[f_window >0]
+
+
+def normalize(w, f, lmin=1300, lmax=3000):
+
+	a = get_continuum(w, f, [1215,1550,1400,2800,6563], lmin=lmin, lmax=lmax, deg=2)
+
+	#fnorm = f/make_f(a, w)
+
+	#fnorm = f / util.get_flux_at_wavelength(w,f,1450)
+
+	return make_f(a, w)
+
+
+
[…]

### 2015-12-22 generate/specs/grid11/ew.py

@@ -1,0 +1,247 @@
+#from plot_norm import *
+import numpy as numpy
+from pylab import *
+import os, sys
+from cobra_sub import smooth
+import py_read_output as r 
+import py_plot_output as pl
+import py_plot_util as util 
+import matplotlib.pyplot as plt
+import matplotlib.gridspec as gridspec
+from plot_norm import *
+from constants import *
+from pretty import *
+
+set_pretty()
+
+def get_continuum(wave, spec, lines = [1215,1400,1550,1640,2800,1900], lmin=1000, lmax = 2000, deg = 3):
+
+	i_jump = (wave > lmin) * (wave < lmax)
+
+	i_lines = np.zeros(len(wave), dtype=bool)
+
+	for i in range(len(wave)):
+
+		comp = lines - wave[i]
+		comp = np.absolute(comp)
+
+		i_line = (comp < 100)
+
+		if np.sum(i_line) == 0:
+			i_lines[i] = True
+		else:
+			i_lines[i] = False		
+
+	i_select = i_jump * i_lines
+
+	continuum_points = wave[i_select]
+
+	#print continuum_points, i_select
+
+	coefficients = np.polyfit(continuum_points, spec[i_select], deg)
+
+	return coefficients
+
+def make_f(a, x):
+
+ 	deg = len(a)
+ 	y = 0
+
+ 	for i in range(deg):
+ 		y += a[i] * (x**(deg - i - 1))
+
+ 	return y
+
+def find_line(w,f, wline = 6563, window_size=100, rw = False):
+
+	fabs_w = np.fabs(w - wline)
+
+	if rw:
+		w_bool = (fabs_w < window_size) * (w > wline)
+	else:
+		w_bool = (fabs_w < window_size) 
+
+	# create windows to look in
+	w_window = w
+	f_window = w_bool * f
+
+	# return arrays with length over specified 2*window_size
+	return w_window[f_window >0], f_window[f_window >0]
+
+
+def get_line_EW(s, angle_string = "A20P0.50", wline=6563, delta = 1.2):
+
+
+
+	line_w, line_f = find_line(s, angle_string, w=wline)
+
[…]

### 2015-12-22 generate/specs/grid11/ew2.py

@@ -1,0 +1,8 @@
+#!/usr/bin/env python
+from pylab import *
+import py_read_output as r 
+import py_plot_output as pl
+import py_plot_util as util 
+import os, sys 
+from constants import *
+import numpy as np

### 2015-12-22 generate/specs/grid11/winds/lin.py

@@ -1,0 +1,131 @@
+#!/usr/bin/env python
+from pylab import *
+import py_read_output as r 
+import py_plot_output as pl
+import py_plot_util as util 
+import os, sys 
+from constants import *
+import numpy as np
+from pretty import *
+
+set_pretty()
+
+from matplotlib.colors import LinearSegmentedColormap
+
+
+#cm_use = get_viridis()
+cm_use=get_optb()
+# f = open("nextgen_alpha1_long.complete", "r")
+
+# data_old = []
+# count = 0
+# for line in f:
+# 	data = line.split()
+
+# 	if len(data) != len(data_old):
+# 		print count, len(data), len(data_old)
+
+# 	count+=1
+# 	data_old = data
+
+# #sys.exit()
+
+RG = 8.85e14
+x1000 = np.logspace(14.0, np.log10(RG*1000-10000000),num=1000)
+
+
+y1000 = np.sqrt((RG*1000)**2 - x1000**2)
+
+x1000 = np.append(x1000,RG*1000)
+y1000 = np.append(y1000,1e-99)
+#n
+xuse= np.append(x1000,1e19)
+
+
+print x1000, y1000
+
+
+
+root = "nextgen_a05_79c"
+#util.run_py_wind(root,vers="79c",cmds=["1","1","1","M","2","2","-1","i","0","13","3","12","2","0","c","3","q"])
+d = r.read_pywind_summary(root)
+
+
+strings = ["ionO5", "ionO6", "ionN5", "ionC4", "ionAl3", "ionMg2", "ionHe1", "ionHe2", "ionHe3"]
+levs = [np.arange(-4,0,0.1), np.arange(-4,0,0.1),  np.arange(-4,0,0.1), np.arange(-4,0,0.1),np.arange(-4,0,0.1),np.arange(-4,0,0.1),np.arange(-4,0,0.1), np.arange(-4,0,0.1), np.arange(-4,0,0.1)]
[…]

### 2015-12-22 generate/specs/grid11/winds/link.py

@@ -1,0 +1,128 @@
+#!/usr/bin/env python
+from pylab import *
+import py_read_output as r 
+import py_plot_output as pl
+import py_plot_util as util 
+import os, sys 
+from constants import *
+import numpy as np
+from pretty import *
+
+set_pretty()
+
+from matplotlib.colors import LinearSegmentedColormap
+
+
+#cm_use = get_viridis()
+cm_use=get_optb()
+# f = open("nextgen_alpha1_long.complete", "r")
+
+# data_old = []
+# count = 0
+# for line in f:
+# 	data = line.split()
+
+# 	if len(data) != len(data_old):
+# 		print count, len(data), len(data_old)
+
+# 	count+=1
+# 	data_old = data
+
+# #sys.exit()
+
+RG = 8.85e14
+x1000 = np.logspace(14.0, np.log10(RG*1000-10000000),num=1000)
+
+
+y1000 = np.sqrt((RG*1000)**2 - x1000**2)
+
+x1000 = np.append(x1000,RG*1000)
+y1000 = np.append(y1000,1e-99)
+#n
+xuse= np.append(x1000,1e19)
+
+
+print x1000, y1000
+
+
+root = "nextgen_a05_79c_he"
+#util.run_py_wind(root,vers="79c",cmds=["1","1","1","M","2","2","-1","i","0","13","3","12","2","0","c","3","q"])
+d = r.read_pywind_summary(root)
+
+
+strings = ["ionO5", "ionO6", "ionN5", "ionC4", "ionAl3", "ionMg2", "ionHe1", "ionHe2", "ionHe3"]
+levs = [np.arange(-4,0,0.1), np.arange(-4,0,0.1),  np.arange(-4,0,0.1), np.arange(-4,0,0.1),np.arange(-4,0,0.1),np.arange(-4,0,0.1),np.arange(-4,0,0.1), np.arange(-4,0,0.1), np.arange(-4,0,0.1)]
[…]

### 2015-12-22 generate/specs/grid11/winds/make_windplot.py

@@ -1,0 +1,202 @@
+import matplotlib.pyplot as plt 
+from pylab import * 
+import numpy as np 
+import csv, sys, os, array, warnings, subprocess
+import pywind_sub as ps
+import matplotlib as mpl
+from matplotlib.mlab import bivariate_normal
+from matplotlib.colors import LogNorm
+from matplotlib.backends.backend_pdf import PdfPages
+import matplotlib as mpl
+import time
+import py_read_output as r
+import read_output as rd
+
+
+def run_py_wind (vers, fname, cmds=None, ilv=None):
+	'''
+	run version vers of py_wind on file fname.wind_save
+	'''
+
+	if cmds == None:
+		cmds = np.array(["1", "n","t", "r","v","1","2","3","-1", "I", "i", "1","1","1","2","0","i","0", "1","1","1","2","2","2","2","1","2","3","6", \
+			          "3","6","4","6","5","0","q"])
+
+	x = cmds
+	np.savetxt("_tempcmd.txt", x, fmt = "%s")
+
+
+	isys = os.system('py_wind'+vers+' '+fname+' < _tempcmd.txt > tempfile &')
+	time.sleep(3)
+
+	# remove temporary file
+	#os.system("rm -f _tempcmd.txt")
+	return isys
+
+
+
+
+def run_pydc (vers, fname, nplasma = 1):
+	'''
+	run version vers of py_wind on file fname.wind_save
+	'''
+
+	x = np.array(["1","M","4",str(nplasma),"1","-1","r","n","t","w", "q"])
+	np.savetxt("_tempcmd.txt", x, fmt = "%s")
+
+
+	isys = os.system('py_wind'+vers+' '+fname+' < _tempcmd.txt')
+	time.sleep(3)
+
+	# remove temporary file
+	#os.system("rm -f _tempcmd.txt")
+	return isys
+
+#ix,iz,x,z,lx,lz,xmax,zmax=ps.get_wind_geom(fname+'.ioncH1.dat')
+
+
+
+def read_pywind_logspace(filename):
+
+	'''
+	convert to logspace coordinates
+	'''
+
+	x,z,s = r.read_pywind(filename)
+
[…]

### 2015-12-22 generate/specs/grid11/winds/wind.py

@@ -1,0 +1,114 @@
+#!/usr/bin/env python
+from pylab import *
+import py_read_output as r 
+import py_plot_output as pl
+import py_plot_util as util 
+import os, sys 
+from constants import *
+import numpy as np
+from pretty import *
+
+set_pretty()
+
+from matplotlib.colors import LinearSegmentedColormap
+
+
+#cm_use = get_viridis()
+cm_use=get_optb()
+# f = open("nextgen_alpha1_long.complete", "r")
+
+# data_old = []
+# count = 0
+# for line in f:
+# 	data = line.split()
+
+# 	if len(data) != len(data_old):
+# 		print count, len(data), len(data_old)
+
+# 	count+=1
+# 	data_old = data
+
+# #sys.exit()
+
+RG = 8.85e14
+x1000 = np.logspace(14.0, np.log10(RG*1000-10000000),num=1000)
+
+
+y1000 = np.sqrt((RG*1000)**2 - x1000**2)
+
+x1000 = np.append(x1000,RG*1000)
+y1000 = np.append(y1000,1e-99)
+#n
+xuse= np.append(x1000,1e19)
+
+
+print x1000, y1000
+
+
+root = "asi_thmin70_rmin50_a0p75_f0p01_mdotw5"
+d = r.read_pywind_summary(root)
+
+
+strings = ["te", "ne", "ionC4", "ionAl3", "ionMg2", "lum_lines", "ly", "IP"]
+levs = [np.arange(3.4,4.8,0.1), np.arange(7,11,0.1), np.arange(-4,0,0.1),np.arange(-4,0,0.1),np.arange(-4,0,0.1),np.arange(40,45,0.2), np.arange(37,42.5,0.2), np.arange(-3,2,0.2)]
+labels = [r'$\rm{log (electron~temperature/K)}$', r'$\rm{log (electron~density/cm^{-3})}$',r'$\rm{log (C\textsc{iv}~ion~fraction)}$)', r'$\rm{log (Al\textsc{iii}~ion~fraction)}$)', r'$\rm{log (Mg\textsc{ii}~ion~fraction)}$)', r'$\rm{log (total~line~luminosity/erg~s^{-1})}$)',
+r'$\rm{log (Ly}~\rm{\alpha~line~luminosity)/erg~s^{-1}}$)', r'$\log U$']
+log = [1,1,1,1,1,1,1,1]
+
+
[…]

### 2015-12-22 generate/uvspec/0946.py

@@ -1,0 +1,193 @@
+#!/usr/bin/env python
+from pylab import *
+import py_read_output as r 
+import py_plot_output as pl
+import py_plot_util as util 
+import os, sys 
+from constants import *
+import numpy as np
+from pretty import *
+from plot_norm import make_f
+import pyfits as py
+
+
+set_pretty()
+NORM = True
+almost_black = '#262626'
+#nameb = "nextgen_alpha1_long"
+suffix = "_a05_pre"
+
+NORM_WAVELENGTH = 1300
+
+namea = "grid11/nextgen%s" % suffix
+namea = "/Users/jmatthews/Documents/runs/qso_he_test/with_estfix/nextgen_a05_pre_he"
+#nameb = "../specs/grid11/nextgen_uv"
+namec = "asi_thmin70_rmin50_a1_f0p01_mdotw5"
+#namec = "asi_thmin70_rmin50_a0p75_f0p01_mdotw5"
+
+name2 = "fiducial"
+smoda = r.read_spectrum(namea)
+#smodb = r.read_spectrum("../specs/"+nameb)
+#smodc = r.read_spectrum("../specs/"+namec)
+
+
+sdisk = r.read_spectrum("../specs/disk")
+sh13 = r.read_spectrum("../specs/h13")
+
+lines = [835,789,1034,977,1215, 1240, 1400, 1550, 1640]
+textx = [835,789,1034,977,1215, 1400, 1550, 1640]
+ycoords = [9.5,9.5,9.5,9.5,9.5,9.5,9.5,9.5,9.5,9.5,9.5,9.5,9.5]
+line_labels = [r"Ly $\alpha$", r"N~\textsc{v}", r"Si~\textsc{iv}", r"C~\textsc{iv}", r"He~\textsc{ii}", r"Al~\textsc{iii}", "C~\\textsc{iii}]", r"Mg~\textsc{ii}"]
+line_labels = [r"O~\textsc{iii}",r"O~\textsc{vi}",r"O~\textsc{vi}",r"N~\textsc{iii}",r"Ly $\alpha$~\&~N~\textsc{v}", r"Si~\textsc{iv}", r"C~\textsc{iv}", r"He~\textsc{ii}", r"Al~\textsc{iii}~\&~C~\textsc{iii}]", r"Mg~\textsc{ii}"]
+
+angles = [72]
+
+colors = get_colors()
+
+big_tick_labels(18)
+long_ticks()
+
[…]

### 2015-12-22 generate/uvspec/0946_two.py

@@ -1,0 +1,189 @@
+#!/usr/bin/env python
+from pylab import *
+import py_read_output as r 
+import py_plot_output as pl
+import py_plot_util as util 
+import os, sys 
+from constants import *
+import numpy as np
+from pretty import *
+from plot_norm import make_f
+import pyfits as py
+
+
+set_pretty()
+NORM = True
+almost_black = '#262626'
+#nameb = "nextgen_alpha1_long"
+suffix = "_a05_pre"
+
+NORM_WAVELENGTH = 1300
+
+namea = "grid11/nextgen%s" % suffix
+namea = "/Users/jmatthews/Documents/runs/qso_he_test/with_estfix/nextgen_a05_pre_he"
+#nameb = "../specs/grid11/nextgen_uv"
+namec = "asi_thmin70_rmin50_a1_f0p01_mdotw5"
+#namec = "asi_thmin70_rmin50_a0p75_f0p01_mdotw5"
+
+name2 = "fiducial"
+smoda = r.read_spectrum(namea)
+#smodb = r.read_spectrum("../specs/"+nameb)
+#smodc = r.read_spectrum("../specs/"+namec)
+
+
+sdisk = r.read_spectrum("../specs/disk")
+sh13 = r.read_spectrum("../specs/h13")
+
+lines = [835,789,1034,977,1215, 1240, 1400, 1550, 1640, 1860, 1909, 2800]
+textx = [835,789,1034,977,1215, 1400, 1550, 1640, 1860, 2800]
+ycoords = [9.5,9.5,9.5,9.5,9.5,9.5,9.5,9.5,9.5,9.5,9.5,9.5,9.5]
+line_labels = [r"Ly $\alpha$", r"N~\textsc{v}", r"Si~\textsc{iv}", r"C~\textsc{iv}", r"He~\textsc{ii}", r"Al~\textsc{iii}", "C~\\textsc{iii}]", r"Mg~\textsc{ii}"]
+line_labels = [r"O~\textsc{iii}",r"O~\textsc{vi}",r"O~\textsc{vi}",r"N~\textsc{iii}",r"Ly $\alpha$~\&~N~\textsc{v}", r"Si~\textsc{iv}", r"C~\textsc{iv}", r"He~\textsc{ii}", r"Al~\textsc{iii}~\&~C~\textsc{iii}]", r"Mg~\textsc{ii}"]
+
+angles = [20,72]
+
+colors = get_colors()
+
+big_tick_labels(18)
[…]

### 2015-12-22 generate/uvspec/0946_xkcd.py

@@ -1,0 +1,191 @@
+#!/usr/bin/env python
+from pylab import *
+import py_read_output as r 
+import py_plot_output as pl
+import py_plot_util as util 
+import os, sys 
+from constants import *
+import numpy as np
+from pretty import *
+from plot_norm import make_f
+import pyfits as py
+
+
+#set_pretty()
+xkcd()
+
+NORM = True
+almost_black = '#262626'
+#nameb = "nextgen_alpha1_long"
+suffix = "_a05_pre"
+
+NORM_WAVELENGTH = 1300
+
+namea = "grid11/nextgen%s" % suffix
+namea = "/Users/jmatthews/Documents/runs/qso_he_test/with_estfix/nextgen_a05_pre_he"
+#nameb = "../specs/grid11/nextgen_uv"
+namec = "asi_thmin70_rmin50_a1_f0p01_mdotw5"
+#namec = "asi_thmin70_rmin50_a0p75_f0p01_mdotw5"
+
+name2 = "fiducial"
+smoda = r.read_spectrum(namea)
+#smodb = r.read_spectrum("../specs/"+nameb)
+#smodc = r.read_spectrum("../specs/"+namec)
+
+
+sdisk = r.read_spectrum("../specs/disk")
+sh13 = r.read_spectrum("../specs/h13")
+
+lines = [835,789,1034,977,1215, 1240, 1400, 1550, 1640, 1860, 1909, 2800]
+textx = [835,789,1034,977,1215, 1400, 1550, 1640, 1860, 2800]
+ycoords = [9.5,9.5,9.5,9.5,9.5,9.5,9.5,9.5,9.5,9.5,9.5,9.5,9.5]
+line_labels = [r"Ly $\alpha$", r"N~\textsc{v}", r"Si~\textsc{iv}", r"C~\textsc{iv}", r"He~\textsc{ii}", r"Al~\textsc{iii}", "C~\\textsc{iii}]", r"Mg~\textsc{ii}"]
+line_labels = [r"O~\textsc{iii}",r"O~\textsc{vi}",r"O~\textsc{vi}",r"N~\textsc{iii}",r"Ly $\alpha$~\&~N~\textsc{v}", r"Si~\textsc{iv}", r"C~\textsc{iv}", r"He~\textsc{ii}", r"Al~\textsc{iii}~\&~C~\textsc{iii}]", r"Mg~\textsc{ii}"]
+
+angles = [72]
+
+colors = get_colors()
+
[…]

### 2015-12-22 generate/uvspec/h13_uvspec.py

@@ -1,0 +1,129 @@
+#!/usr/bin/env python
+from pylab import *
+import py_read_output as r 
+import py_plot_output as pl
+import py_plot_util as util 
+import os, sys 
+from constants import *
+import numpy as np
+from pretty import *
+from plot_norm import make_f
+
+set_pretty()
+NORM = True
+almost_black = '#262626'
+#nameb = "nextgen_alpha1_long"
+namea = "nextgen_uv"
+#namea = "checkvol_a6"
+namea = "nextgen_a5"
+nameb = "asi_thmin70_rmin50_a0p75_f0p01_mdotw5"
+namec = "asi_thmin70_rmin50_a1_f0p01_mdotw5"
+#namec = "asi_thmin70_rmin50_a0p75_f0p01_mdotw5"
+
+name2 = "fiducial"
+smoda = r.read_spectrum("../specs/"+namea)
+#smodb = r.read_spectrum("../specs/"+nameb)
+#smodc = r.read_spectrum("../specs/"+namec)
+
+
+sdisk = r.read_spectrum("../specs/disk")
+sh13 = r.read_spectrum("../specs/h13")
+
+
+angles = [20,60,72,75,78]
+
+colors = get_colors()
+
+figure(figsize=(10,10))
+
+#run_agnspec
+
+for i in range(len(angles)):
+
+	angle = angles[i]
+	subplot(5,1,i+1)
+	angstr = "A%iP0.50" % angle
+	wwa = smoda["Lambda"]
+	#wwb = smodb["Lambda"]
+	#wwc = smodc["Lambda"]
+
+	NORM_GPC = (1e9*1e9)/(1e4)/1e14
+
+
+	Fdisk = sdisk[angstr] / NORM_GPC
+	Fh13 = sh13[angstr] / NORM_GPC
+
+	Fmoda = smoda[angstr] / NORM_GPC
+	#Fmodb = smodb[angstr]
+	#Fmodc = smodc[angstr]
+
+
+
+	plot(wwa,util.smooth(Fmoda,window_len=5), label=r"Model", c='k', linewidth=2)
+	#plot(wwb,util.smooth(Fmodb), label=r"Model B, $\alpha = 0.75$", c=colors[1], linewidth=2)
+	#plot(wwc,util.smooth(Fmodc), label=r"Model C, $\alpha = 1$", c=colors[2], linewidth=2)
[…]

### 2015-12-22 generate/uvspec/specs/all.py

@@ -1,0 +1,98 @@
+#!/usr/bin/env python
+from pylab import *
+import py_read_output as r 
+import py_plot_output as pl
+import py_plot_util as util 
+import os, sys 
+from constants import *
+import numpy as np
+from pretty import *
+from plot_norm import make_f
+
+set_pretty()
+NORM = True
+
+path = "."
+
+spec_files = [f for f in os.listdir(path) if (f.endswith('.spec') and f!='lines.spec')]
+
+
+for iname in range(len(spec_files)):
+
+
+
+	almost_black = '#262626'
+	name1 = "nextgen_alpha1_long"
+	name2 = spec_files[iname][:-5]
+	specname = name2
+	smod = r.read_spectrum(name1)
+	sdisk = r.read_spectrum("disk_only")
+	sh13 = r.read_spectrum(name2)
+
+	print name2
+
+	angles = [20,40, 75,80]
+
+	figure(figsize=(12,8))
+
+	#run_agnspec
+
+	for i in range(len(angles)):
+
+		angle = angles[i]
+		subplot(4,1,i+1)
+		angstr = "A%iP0.50" % angle
+		ww = smod["Lambda"]
+
+
+		Fdisk = sdisk[angstr]
+		Fmod = smod[angstr]
+		Fh13 = sh13[angstr]
+
+
+
+		plot(ww,util.smooth(Fmod), label="Full model", c="k", linewidth=2)
+		plot(sh13["Lambda"],util.smooth(Fh13), label="for comp", c=almost_black, linewidth=1)
+		plot(sdisk["Lambda"],util.smooth(Fdisk, window_len=100), label="Disc continuum", c="k", linestyle="--")
+
+
+
+		# if NORM:
+		# 	f2000 = util.get_flux_at_wavelength(ww,Fmod,2000)
+		# plot(ww,util.smooth(Fmod/f2000), label="Original Model")
+
+		# read the composites and plot them
+		# if angles[i]<=70:
+
+		# 	w,f = np.loadtxt("/Users/jmatthews/Documents/Python/examples/sdssedrqsobal/sdssedrqsobal.nonbal.spec", unpack=True,usecols=(0,1))
+		# 	f2000 = util.get_flux_at_wavelength(w,f,2000)
+		# 	plot(w,f/f2000, label="non-BAL composite")
+
+		# else:
[…]

### 2015-12-22 generate/uvspec/uv_mast.py

@@ -1,0 +1,176 @@
+#!/usr/bin/env python
+from pylab import *
+import py_read_output as r 
+import py_plot_output as pl
+import py_plot_util as util 
+import os, sys 
+from constants import *
+import numpy as np
+from pretty import *
+from plot_norm import make_f
+import pyfits as py
+
+
+set_pretty()
+NORM = True
+almost_black = '#262626'
+#nameb = "nextgen_alpha1_long"
+suffix = "_a05_pre"
+
+NORM_WAVELENGTH = 1300
+
+namea = "grid11/nextgen%s" % suffix
+#nameb = "../specs/grid11/nextgen_uv"
+namec = "asi_thmin70_rmin50_a1_f0p01_mdotw5"
+#namec = "asi_thmin70_rmin50_a0p75_f0p01_mdotw5"
+
+name2 = "fiducial"
+smoda = r.read_spectrum("../specs/"+namea)
+#smodb = r.read_spectrum("../specs/"+nameb)
+#smodc = r.read_spectrum("../specs/"+namec)
+
+
+sdisk = r.read_spectrum("../specs/disk")
+sh13 = r.read_spectrum("../specs/h13")
+
+lines = [1215, 1240, 1400, 1550, 1640, 1860, 1909, 2800]
+textx = [1215, 1400, 1550, 1640, 1860, 2800]
+ycoords = [2, 50, 50, 50, 50, 50, 50]
+line_labels = [r"Ly $\alpha$", r"N~\textsc{v}", r"Si~\textsc{iv}", r"C~\textsc{iv}", r"He~\textsc{ii}", r"Al~\textsc{iii}", "C~\\textsc{iii}]", r"Mg~\textsc{ii}"]
+line_labels = [r"Ly $\alpha$~\&~N~\textsc{v}", r"Si~\textsc{iv}", r"C~\textsc{iv}", r"He~\textsc{ii}", r"Al~\textsc{iii}~\&~C~\textsc{iii}]", r"Mg~\textsc{ii}"]
+
+angles = [20,60,72,75,78]
+
+colors = get_colors()
+
+def get_hst(f2000):
+
+	files1 = [f for f in os.listdir('../mast/0946/') if "x1d" in f]
+	z = 1.223
+	for i in range(4,len(files1)):
+
+		d = py.getdata('../mast/0946/'+files1[i])
+		w = d["WAVELENGTH"][0] / (1.0 + z)
+		f = d["FLUX"][0]
[…]

### 2015-12-22 generate/uvspec/uvspec.py

@@ -1,0 +1,151 @@
+#!/usr/bin/env python
+from pylab import *
+import py_read_output as r 
+import py_plot_output as pl
+import py_plot_util as util 
+import os, sys 
+from constants import *
+import numpy as np
+from pretty import *
+from plot_norm import make_f
+
+set_pretty()
+NORM = True
+almost_black = '#262626'
+#nameb = "nextgen_alpha1_long"
+suffix = "_a075_pre_he"
+
+
+namea = "grid11/nextgen%s" % suffix
+namea = "/Users/jmatthews/Documents/runs/qso_he_test/with_estfix/nextgen_a05_pre_he"
+#nameb = "../specs/grid11/nextgen_uv"
+namec = "asi_thmin70_rmin50_a1_f0p01_mdotw5"
+#namec = "asi_thmin70_rmin50_a0p75_f0p01_mdotw5"
+
+name2 = "fiducial"
+smoda = r.read_spectrum(namea)
+#smodb = r.read_spectrum("../specs/"+nameb)
+#smodc = r.read_spectrum("../specs/"+namec)
+
+
+sdisk = r.read_spectrum("../specs/disk")
+sh13 = r.read_spectrum("../specs/h13")
+
+lines = [1215, 1240, 1400, 1550, 1640, 1860, 1909, 2800]
+textx = [1215, 1400, 1550, 1640, 1860, 2800]
+ycoords = [2, 50, 50, 50, 50, 50, 50]
+line_labels = [r"Ly $\alpha$", r"N~\textsc{v}", r"Si~\textsc{iv}", r"C~\textsc{iv}", r"He~\textsc{ii}", r"Al~\textsc{iii}", "C~\\textsc{iii}]", r"Mg~\textsc{ii}"]
+line_labels = [r"Ly $\alpha$~\&~N~\textsc{v}", r"Si~\textsc{iv}", r"C~\textsc{iv}", r"He~\textsc{ii}", r"Al~\textsc{iii}~\&~C~\textsc{iii}]", r"Mg~\textsc{ii}"]
+
+angles = [20,60,72,75,78]
+
+colors = get_colors()
+
+figure(figsize=(10,12))
+
+#run_agnspec
+
+for i in range(len(angles)):
+
+	angle = angles[i]
+	subplot(5,1,i+1)
+	angstr = "A%iP0.50" % angle
+	wwa = smoda["Lambda"]
+	#wwb = smodb["Lambda"]
+	#wwc = smodc["Lambda"]
+
[…]

### 2015-12-22 generate/uvspec/uvspec_xkcd.py

@@ -1,0 +1,157 @@
+#!/usr/bin/env python
+from pylab import *
+import py_read_output as r 
+import py_plot_output as pl
+import py_plot_util as util 
+import os, sys 
+from constants import *
+import numpy as np
+from pretty import *
+from plot_norm import make_f
+
+#set_pretty()
+xkcd()
+NORM = True
+almost_black = '#262626'
+#nameb = "nextgen_alpha1_long"
+suffix = "_a075_pre_he"
+
+
+namea = "grid11/nextgen%s" % suffix
+namea = "/Users/jmatthews/Documents/runs/qso_he_test/with_estfix/nextgen_a05_pre_he"
+#nameb = "../specs/grid11/nextgen_uv"
+namec = "asi_thmin70_rmin50_a1_f0p01_mdotw5"
+#namec = "asi_thmin70_rmin50_a0p75_f0p01_mdotw5"
+
+name2 = "fiducial"
+smoda = r.read_spectrum(namea)
+#smodb = r.read_spectrum("../specs/"+nameb)
+#smodc = r.read_spectrum("../specs/"+namec)
+
+
+sdisk = r.read_spectrum("../specs/disk")
+sh13 = r.read_spectrum("../specs/h13")
+
+lines = [1215, 1240, 1400, 1550, 1640, 1860, 1909, 2800]
+textx = [1215, 1400, 1550, 1640, 1860, 2800]
+ycoords = [2, 50, 50, 50, 50, 50, 50]
+line_labels = [r"Ly $\alpha$", r"N~\textsc{v}", r"Si~\textsc{iv}", r"C~\textsc{iv}", r"He~\textsc{ii}", r"Al~\textsc{iii}", "C~\\textsc{iii}]", r"Mg~\textsc{ii}"]
+line_labels = [r"Ly $\alpha$~\&~N~\textsc{v}", r"Si~\textsc{iv}", r"C~\textsc{iv}", r"He~\textsc{ii}", r"Al~\textsc{iii}~\&~C~\textsc{iii}]", r"Mg~\textsc{ii}"]
+
+angles = [20,60,72,75,78]
+
+colors = get_colors()
+
+figure(figsize=(10,8))
+
+#run_agnspec
+
+#for i in range(len(angles)):
+for i in range(1):
+	angle = angles[i]
+	subplot(1,1,i+1)
+	angstr = "A%iP0.50" % angle
+	wwa = smoda["Lambda"]
+	#wwb = smodb["Lambda"]
+	#wwc = smodc["Lambda"]
+
[…]

### 2015-12-22 generate/uvspec/wide.py

@@ -1,0 +1,109 @@
+#!/usr/bin/env python
+from pylab import *
+import py_read_output as r 
+import py_plot_output as pl
+import py_plot_util as util 
+import os, sys 
+from constants import *
+import numpy as np
+from pretty import *
+from plot_norm import make_f
+
+set_pretty()
+NORM = True
+almost_black = '#262626'
+#nameb = "nextgen_alpha1_long"
+namea = "nextgen_a5"
+nameb = "nextgen_opt"
+# namec = "asi_thmin70_rmin50_a1_f0p01_mdotw5"
+# namec = "asi_thmin70_rmin50_a0p75_f0p01_mdotw5"
+
+name2 = "fiducial"
+smoda = r.read_spectrum("../specs/"+namea)
+smodb = r.read_spectrum("../specs/"+nameb)
+# smodc = r.read_spectrum("specs/"+namec)
+
+
+sdisk = r.read_spectrum("../specs/disk")
+sh13 = r.read_spectrum("../specs/h13")
+
+
+angles = [20,60,72,75,80]
+
+colors = get_colors()
+
+figure(figsize=(8,12))
+
+
+
+#run_agnspec
+
+for i in range(len(angles)):
+
+	angle = angles[i]
+	subplot(5,1,i+1)
+	angstr = "A%iP0.50" % angle
+	wwa = smoda["Lambda"]
+	wwb = smodb["Lambda"]
+	select = (wwa <= 2900)
+	select2 = (wwb > 2900)
+	# wwc = smodc["Lambda"]
+
+
+	#Fdisk = sdisk[angstr]
+	#Fh13 = sh13[angstr]
+
+	Fmoda = smoda[angstr]
+	Fmodb = smodb[angstr]
+	#Fmodc = smodc[angstr]
+
+
+
+	plot(wwa[select],util.smooth(Fmoda[select]), label=r"Model A, $\alpha = 0.6$", c='k', linewidth=2)
+	plot(wwb[select2],util.smooth(Fmodb[select2]), c='k', linewidth=2)
+	#plot(wwc,util.smooth(Fmodc), label=r"Model C, $\alpha = 1$", c=colors[2], linewidth=2)
+	#plot(sh13["Lambda"],util.smooth(Fh13), label="H13", c=almost_black, linewidth=1)
+	#plot(sdisk["Lambda"],util.smooth(Fdisk, window_len=100), label="Disc continuum", c="k", linestyle="--")
+
+
[…]

### 2015-12-22 generate/uvspec/wide_com.py

@@ -1,0 +1,126 @@
+#!/usr/bin/env python
+from pylab import *
+import py_read_output as r 
+import py_plot_output as pl
+import py_plot_util as util 
+import os, sys 
+from constants import *
+import numpy as np
+from pretty import *
+from plot_norm import make_f
+
+set_pretty()
+NORM = True
+almost_black = '#262626'
+#nameb = "nextgen_alpha1_long"
+namea = "nextgen_uv"
+namea = "checkvol_a6"
+#namea = "nextgen_a5"
+nameb = "asi_thmin70_rmin50_a0p75_f0p01_mdotw5"
+namec = "asi_thmin70_rmin50_a1_f0p01_mdotw5"
+#namec = "asi_thmin70_rmin50_a0p75_f0p01_mdotw5"
+
+name2 = "fiducial"
+smoda = r.read_spectrum("../specs/"+namea)
+#smodb = r.read_spectrum("../specs/"+nameb)
+#smodc = r.read_spectrum("../specs/"+namec)
+
+
+sdisk = r.read_spectrum("../specs/disk")
+sh13 = r.read_spectrum("../specs/h13")
+
+
+angles = [20,60,72,75,78]
+
+colors = get_colors()
+
+figure(figsize=(10,10))
+
+#run_agnspec
+
+for i in range(len(angles)):
+
+	angle = angles[i]
+	subplot(5,1,i+1)
+	angstr = "A%iP0.50" % angle
+	wwa = smoda["Lambda"]
+	#wwb = smodb["Lambda"]
+	#wwc = smodc["Lambda"]
+
+	NORM_GPC = (1e9*1e9)/(1e4)/1e14
+
+
+	Fdisk = sdisk[angstr] / NORM_GPC
+	Fh13 = sh13[angstr] / NORM_GPC
+
+	Fmoda = smoda[angstr] / NORM_GPC
+	#Fmodb = smodb[angstr]
+	#Fmodc = smodc[angstr]
+
+
+
+	plot(wwa,util.smooth(Fmoda,window_len=5), label=r"Model", c='k', linewidth=2)
+	#plot(wwb,util.smooth(Fmodb), label=r"Model B, $\alpha = 0.75$", c=colors[1], linewidth=2)
+	#plot(wwc,util.smooth(Fmodc), label=r"Model C, $\alpha = 1$", c=colors[2], linewidth=2)
[…]

### 2015-12-22 generate/wind_onepanel/SV_cartoon.py

@@ -1,0 +1,95 @@
+'''
+SV_cartoon.py 
+
+This script creates the cartoon figure for 
+the 2014 CV paper. The data were scraped from Dexter.
+'''
+
+import matplotlib.mlab as mlab
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib as mpl
+
+
+mpl.rcParams['pdf.use14corefonts'] = True
+mpl.rc('font',**{'family':'sans-serif','sans-serif':['Helvetica']})
+## for Palatino and other serif fonts use:
+#rc('font',**{'family':'serif','serif':['Palatino']})
+mpl.rc('text', usetex=True)
+
+thetamin=72.0
+thetamax=80.0
+diskmax=25.0
+xmin=10.0
+xmax=18.0
+rstar=2.0
+
+xwindmax=40.0
+zwindmax=(xwindmax-xmin)*np.tan(np.radians(90.0-thetamin))
+
+
+posx=np.arange(xmin,xwindmax,(xmax-xmin)/10.0)
+ymin1=[]
+ymax1=[]
+
+x=np.array([xmin,xmax,xwindmax])
+y1=np.array([0.0,(xmax-xmin)*np.tan(np.radians(90.0-thetamin)),(xwindmax-xmin)*np.tan(np.radians(90.0-thetamin))])
+y2=np.array([0.0,0.0,(xwindmax-xmax)*np.tan(np.radians(90.0-thetamax))])
+
+lsize=14
+tsize=16 
+
+fig=plt.figure()
+ax=fig.add_subplot(1,1,1)
+ax.plot(x,y1,x,y2,color='black')
+ax.plot(-1.0*x,y1,-1.0*x,y2,color='black')
+ax.plot(-1.0*x,-1.0*y1,-1.0*x,-1.0*y2,color='black')
+ax.plot(x,-1.0*y1,x,-1.0*y2,color='black')
+ax.set_xlim([-1.0*xwindmax,xwindmax])
+plt.fill_between(x,y1, y2, facecolor='0.9', interpolate=True)
+plt.fill_between(-1.0*x,y1, y2, facecolor='0.9', interpolate=True)
+plt.fill_between(x,-1.0*y1, -1.0*y2, facecolor='0.9', interpolate=True)
+plt.fill_between(-1.0*x,-1.0*y1, -1.0*y2, facecolor='0.9', interpolate=True)
[…]

### 2015-12-22 generate/wind_onepanel/one_wind.py

@@ -1,0 +1,174 @@
+#!/usr/bin/env python
+from pylab import *
+import py_read_output as r 
+import py_plot_output as pl
+import py_plot_util as util 
+import os, sys 
+from constants import *
+import numpy as np
+from pretty import *
+
+set_pretty()
+
+from matplotlib.colors import LinearSegmentedColormap
+
+
+cm_use = get_viridis()
+# f = open("nextgen_alpha1_long.complete", "r")
+
+# data_old = []
+# count = 0
+# for line in f:
+# 	data = line.split()
+
+# 	if len(data) != len(data_old):
+# 		print count, len(data), len(data_old)
+
+# 	count+=1
+# 	data_old = data
+
+# #sys.exit()
+
+RG = 8.85e14
+x1000 = np.logspace(14.0, np.log10(RG*1000-10000000),num=1000)
+
+
+y1000 = np.sqrt((RG*1000)**2 - x1000**2)
+
+x1000 = np.append(x1000,RG*1000)
+y1000 = np.append(y1000,1e-99)
+#n
+xuse= np.append(x1000,1e19)
+
+
+print x1000, y1000
+
+
+d = r.read_pywind_summary("nextgen_a05")
+
+
+strings = ["te"]
+levs = [np.arange(-3,2,0.2)]
+levs = [np.arange(3,5,0.1)]
+labels = [r'$\log U$']
+log = [1]
+
+
+fig = figure(figsize=[1,1])
+
+x,z,var = util.wind_to_masked(d, strings[0])
+
+if log[0]:
+	var = np.log10(var)
+
+
+
+# select = (var.mask == False)*(z<1e19)
+
+# z = z[select]
+# x = x[select]
+# # e = e[(e.mask == False)]
+
+# import matplotlib.tri as tri
+# T = tri.Triangulation(x.flatten(), z.flatten())
+
+
+# var = var[select]
+# var = var.flatten()
+
+
+#tricontourf(T,np.log10(var), mask = var.mask, levels = levs[0], extend="both", cmap=cm_use)
+
+contourf(x,z,var, extend='both', levels=levs[0], cmap=cm_use)
+#grid()
+#loglog()
+pretty_axes()
+xlim(-8.85e14,1e18)
[…]

### 2015-12-22 generate/wind_plot/lin.py

@@ -1,0 +1,125 @@
+#!/usr/bin/env python
+from pylab import *
+import py_read_output as r 
+import py_plot_output as pl
+import py_plot_util as util 
+import os, sys 
+from constants import *
+import numpy as np
+from pretty import *
+
+set_pretty()
+
+from matplotlib.colors import LinearSegmentedColormap
+
+
+#cm_use = get_viridis()
+cm_use=get_optb()
+# f = open("nextgen_alpha1_long.complete", "r")
+
+# data_old = []
+# count = 0
+# for line in f:
+# 	data = line.split()
+
+# 	if len(data) != len(data_old):
+# 		print count, len(data), len(data_old)
+
+# 	count+=1
+# 	data_old = data
+
+# #sys.exit()
+
+RG = 8.85e14
+x1000 = np.logspace(14.0, np.log10(RG*1000-10000000),num=1000)
+
+
+y1000 = np.sqrt((RG*1000)**2 - x1000**2)
+
+x1000 = np.append(x1000,RG*1000)
+y1000 = np.append(y1000,1e-99)
+#n
+xuse= np.append(x1000,1e19)
+
+
+print x1000, y1000
+
+
+root = "nextgen_a05_pre_he"
+d = r.read_pywind_summary(root)
+
+
+strings = ["te", "ne", "IP", "ionC4", "ionAl3", "ionMg2", "lum_lines", "ly", "lineC4"]
+levs = [np.arange(3.4,4.8,0.1), np.arange(7,11,0.1),  np.arange(-3,2,0.2), np.arange(-2,0.1,0.1),np.arange(-4,0,0.1),np.arange(-4,0,0.1),np.arange(40,44,0.1), np.arange(37,42.5,0.2), np.arange(37,42.5,0.2)]
+labels = [r'$\rm{log (electron~temperature/K)}$', r'$\rm{log (electron~density/cm^{-3})}$',r'$\log U$',r'$\rm{log (C\textsc{iv}~ion~fraction)}$', r'$\rm{log (Al\textsc{iii}~ion~fraction)}$', r'$\rm{log (Mg\textsc{ii}~ion~fraction)}$', r'$\rm{log (total~line~luminosity/erg~s^{-1})}$',
[…]

### 2015-12-22 generate/wind_plot/link.py

@@ -1,0 +1,126 @@
+#!/usr/bin/env python
+from pylab import *
+import py_read_output as r 
+import py_plot_output as pl
+import py_plot_util as util 
+import os, sys 
+from constants import *
+import numpy as np
+from pretty import *
+
+set_pretty()
+
+from matplotlib.colors import LinearSegmentedColormap
+
+
+#cm_use = get_viridis()
+cm_use=get_optb()
+# f = open("nextgen_alpha1_long.complete", "r")
+
+# data_old = []
+# count = 0
+# for line in f:
+# 	data = line.split()
+
+# 	if len(data) != len(data_old):
+# 		print count, len(data), len(data_old)
+
+# 	count+=1
+# 	data_old = data
+
+# #sys.exit()
+
+RG = 8.85e14
+x1000 = np.logspace(14.0, np.log10(RG*1000-10000000),num=1000)
+
+
+y1000 = np.sqrt((RG*1000)**2 - x1000**2)
+
+x1000 = np.append(x1000,RG*1000)
+y1000 = np.append(y1000,1e-99)
+#n
+xuse= np.append(x1000,1e19)
+
+
+print x1000, y1000
+
+
+root = "nextgen_a05_pre_he"
+d = r.read_pywind_summary(root)
+
+
+
+strings = ["te", "ne", "IP", "ionC4", "ionAl3", "ionMg2", "lum_lines", "ly", "lineC4"]
+levs = [np.arange(3.4,4.8,0.1), np.arange(7,11,0.1),  np.arange(-3,2,0.2), np.arange(-4,0,0.1),np.arange(-4,0,0.1),np.arange(-4,0,0.1),np.arange(40,44,0.1), np.arange(37,42.5,0.2), np.arange(37,42.5,0.2)]
+labels = [r'$\rm{log (electron~temperature/K)}$', r'$\rm{log (electron~density/cm^{-3})}$',r'$\log U$',r'$\rm{log (C\textsc{iv}~ion~fraction)}$', r'$\rm{log (Al\textsc{iii}~ion~fraction)}$', r'$\rm{log (Mg\textsc{ii}~ion~fraction)}$', r'$\rm{log (total~line~luminosity/erg~s^{-1})}$',
[…]

### 2015-12-22 generate/wind_plot/link_8.py

@@ -1,0 +1,135 @@
+#!/usr/bin/env python
+from pylab import *
+import py_read_output as r 
+import py_plot_output as pl
+import py_plot_util as util 
+import os, sys 
+from constants import *
+import numpy as np
+from pretty import *
+
+set_pretty()
+
+from matplotlib.colors import LinearSegmentedColormap
+
+
+#cm_use = get_viridis()
+cm_use=get_optb()
+# f = open("nextgen_alpha1_long.complete", "r")
+
+# data_old = []
+# count = 0
+# for line in f:
+# 	data = line.split()
+
+# 	if len(data) != len(data_old):
+# 		print count, len(data), len(data_old)
+
+# 	count+=1
+# 	data_old = data
+
+# #sys.exit()
+
+RG = 8.85e14
+x1000 = np.logspace(14.0, np.log10(RG*1000-10000000),num=1000)
+
+
+y1000 = np.sqrt((RG*1000)**2 - x1000**2)
+
+x1000 = np.append(x1000,RG*1000)
+y1000 = np.append(y1000,1e-99)
+#n
+xuse= np.append(x1000,1e19)
+
+
+print x1000, y1000
+
+
+root = "nextgen_a05_pre_he"
+d = r.read_pywind_summary(root)
+
+
+
+strings = ["te", "ne", "IP", "ionC4", "ionAl3", "ionMg2", "ly", "lineC4"]
+levs = [np.arange(3.4,4.8,0.1), np.arange(7,11,0.1),  np.arange(-3,2,0.2), np.arange(-4,0,0.1),np.arange(-4,0,0.1),np.arange(-4,0,0.1), np.arange(37,42.5,0.2), np.arange(37,42.5,0.2)]
+labels = [r'$\rm{log (electron~temperature/K)}$', r'$\rm{log (electron~density/cm^{-3})}$',r'$\log U$',r'$\rm{log (C\textsc{iv}~ion~fraction)}$', r'$\rm{log (Al\textsc{iii}~ion~fraction)}$', r'$\rm{log (Mg\textsc{ii}~ion~fraction)}$',
+r'$\rm{log (Ly}~\rm{\alpha~line~luminosity)/erg~s^{-1}}$)', r'$\rm{log (C\textsc{iv}~line~luminosity/erg~s^{-1})}$']
+log = [1,1,1,1,1,1,1,1,1,1,1,1]
[…]

### 2015-12-22 generate/xray/alpha_ox.py

@@ -1,0 +1,271 @@
+#!/usr/bin/env python
+'''
+alpha_ox.py makes plots of alpha_ox and L_2kev plotted
+against L_2500 
+'''
+from pylab import *
+import py_read_output as r 
+import numpy as np 
+import os, sys
+import py_plot_util as util
+from constants import *
+from astropy.io import ascii
+from pretty import *
+#import disk
+
+# some functions for getting mean monochromatic fluxes in a bin
+def get_flux_inwbin(lambda_array, flux_array, w, binsize=1, log=False):
+	wstart = w - (0.5*binsize)
+	wstop = w + (0.5*binsize)
+	select = (lambda_array > wstart) * (lambda_array < wstop)
+	return np.mean(flux_array[select])
+
+def get_flux_infbin(f_array, flux_array, f, binsize=0.1, log=False):
+
+	binsize *= f
+
+	fstart = f - (0.5 * binsize)
+	fstop = f + (0.5 * binsize)
+	select = (f_array > fstart) * (f_array < fstop)
+	return np.mean(flux_array[select])
+
+def get_flux_at_f(f_array, flux_array, f):
+
+	i = np.abs(f_array - f).argmin()
+
+	return flux_array[i]
+
+
+
+r.setpars()
+rcParams["legend.frameon"] = "False"
+rcParams["legend.numpoints"] = 1
+colors = ["r", "g"]
+
+# fnames to use
+fnames = [("fiducial_xray", "fiducial_uv"), ("../specs/nextgen_a5_xray", "../specs/nextgen_a5")]
+fnames = [("fiducial_xray", "fiducial_uv"), ("../specs/nextgen_3_30", "../specs/nextgen_uv")]
+fnames = [("../specs/fiducial_xray_fine", "../specs/h13.spec"), ("../specs/checkvol_a6_xray", "../specs/checkvol_a6")]
+fnames = [("../specs/fiducial_xray_fine", "../specs/h13.spec"), ("../specs/grid10/nextgen_a05_3_30", "../specs/grid10/nextgen_a05")]
+
+# 9 before
+label=fnames[1][0][16:]
+
+
+# load the Steffen et al. data
[…]

### 2015-12-22 generate/xray/lx.py

@@ -1,0 +1,255 @@
+#!/usr/bin/env python
+'''
+alpha_ox.py makes plots of alpha_ox and L_2kev plotted
+against L_2500 
+'''
+from pylab import *
+import py_read_output as r 
+import numpy as np 
+import os, sys
+import py_plot_util as util
+from constants import *
+from astropy.io import ascii
+from pretty import *
+#import disk
+
+# some functions for getting mean monochromatic fluxes in a bin
+def get_flux_inwbin(lambda_array, flux_array, w, binsize=1, log=False):
+	wstart = w - (0.5*binsize)
+	wstop = w + (0.5*binsize)
+	select = (lambda_array > wstart) * (lambda_array < wstop)
+	return np.mean(flux_array[select])
+
+def get_flux_infbin(f_array, flux_array, f, binsize=0.1, log=False):
+
+	binsize *= f
+
+	fstart = f - (0.5 * binsize)
+	fstop = f + (0.5 * binsize)
+	select = (f_array > fstart) * (f_array < fstop)
+	return np.mean(flux_array[select])
+
+def get_flux_at_f(f_array, flux_array, f):
+
+	i = np.abs(f_array - f).argmin()
+
+	return flux_array[i]
+
+
+
+r.setpars()
+rcParams["legend.frameon"] = "False"
+rcParams["legend.numpoints"] = 1
+colors = ["r", "g"]
+colors_xx = get_colors()
+
+# fnames to use
+# fnames = [("fiducial_xray", "fiducial_uv"), ("../specs/nextgen_a5_xray", "../specs/nextgen_a5")]
+# fnames = [("fiducial_xray", "fiducial_uv"), ("../specs/nextgen_3_30", "../specs/nextgen_uv")]
+# fnames = [("../specs/fiducial_xray_fine", "../specs/h13.spec"), ("../specs/checkvol_a6_xray", "../specs/checkvol_a6")]
+
+aaa = "06"
+vers = "pre"
+suffix1 = "_a%s_%s" % (aaa,vers)
+suffix2 = "_a%s_%s_xray" % (aaa,vers)
[…]

### 2015-12-22 generate/xray_sed/compton.py

@@ -1,0 +1,107 @@
+#!/usr/bin/env python
+from pylab import *
+import py_read_output as r 
+import py_plot_output as pl
+import py_plot_util as util 
+import os, sys 
+from constants import *
+import numpy as np
+from pretty import *
+
+
+figure(figsize=(12,7))
+
+#subplot(2,1,1)
+
+#fnames = ["1e45", "1e45_uv"]
+#fnames = ["nextgen_alpha1_long_wide","1e45", "1e45_uv"]
+#fnames = ['nextgen_p3_3',"nextgen_3_30", 'nextgen_30_300', 'nextgen_uv', 'nextgen_opt']
+#fnames = ['checkvol_a6',"checkvol_a6_xray","h13","fiducial_xray_fine","fiducial_uv","fiducial_xray"]
+#fnames = ["h13","fiducial_xray_fine","fiducial_uv","fiducial_xray"]
+fnames = ["grid11/nextgen_a05_pre_xray"]
+NN = len(fnames) - 1
+NN = len(fnames) - 1
+
+alphas = [0.5,0.5,0.75,0.75]
+labels=["1e45, f=0.01", "H13"]
+big_tick_labels(16)
+
+colors = get_colors()
+
+ccc = [colors[0],colors[0], "k", "k"]
+modcols = [colors[0], "k", "k"]
+
+angles = [85]
+
+for iang in range(len(angles)):
+
+	set_pretty()
+
+	all_nu = np.array([])
+	all_f = np.array([])
+	concatenate
+
+	#bounds = [(1e19,1e18),(1e18,1e17),(1e17,1e16),(1e16,1e15),(1e15,1e14)]
+	bounds = [(1e19,1e14),(1e19,1e14),(1e19,1e14),(1e19,1e14),(1e19,1e14),(1e19,1e14),(1e19,1e14)]
+
+	for i in range(len(fnames)):
+
+		s = r.read_spectrum("../specs/"+fnames[NN-i])
+
+		ev = 1.60217657e-19
+
+		angle = angles[iang]
+
+		nu = s["Freq."]
+		w = s["Lambda"]
+
+		flambda = s["A%iP0.50" % angle]
+
+
+		fl_to_fnu = s["Lambda"] / s["Freq."]
+
+		norm = 4.0 * PI * (100.0 * PARSEC) * (100.0 * PARSEC)
+
[…]

### 2015-12-22 generate/xray_sed/find_lines.py

@@ -1,0 +1,157 @@
+#!/usr/bin/env python
+from pylab import *
+import py_read_output as r 
+import py_plot_output as pl
+import py_plot_util as util 
+import os, sys 
+from constants import *
+import numpy as np
+from pretty import *
+
+
+def get_linelist(filenames, ionreturn=False):
+
+	'''
+	function to read in linelist from a bunch of filenames
+	'''
+
+	lines = np.array([])
+	z = np.array([])
+
+	for i in range(len(filenames)):
+
+		x = np.loadtxt(filenames[i], comments="#", usecols=(2,3), unpack=True)
+
+		lines = np.concatenate((lines, x[1]))
+
+		z = np.concatenate((z, x[0]))
+
+	if ionreturn:
+		return lines, z
+	else:
+		return lines
+
+
+# some global plotting params
+logx = True
+# only select lines above this oscillator threshold
+oscillator_threshold = 0.01
+xlims = (0.4,3.5)
+elim = (0.4,3)
+ionlim = (15,27)	# ion limits
+
+# angle we are going to plot at
+angle = 75
+
+
+
+# read in Python synthetic spectrum
+fname = "grid11/nextgen_a05_pre_xray"
+s = r.read_spectrum("../specs/"+fname)
+
+nu = s["Freq."]
+
+# converting from fnu to flambda
+fl_to_fnu = s["Lambda"] / s["Freq."]
+
+# converting from flux to normalisation
+norm = 4.0 * PI * (100.0 * PARSEC) * (100.0 * PARSEC)
+
+#convert to lnu - flambda x fl_to_fnu x norm
+lnu = s["A%iP0.50" % angle] * fl_to_fnu * norm
+
+
+
+
+# now get the atomic data
+z, ion, wave, f = np.loadtxt("data/atomic78/lines_linked_ver_2.py", comments="#", usecols=(1,2,3,4), unpack=True)
+
+energies = C / (wave * ANGSTROM) * HEV * 1e-3 # energy in keV
+
+# print the strong lines
+for i in range(len(f)):
+	if f[i] > oscillator_threshold and energies[i] < elim[1] and energies[i] > elim[0]:
+		print z[i], ion[i], f[i], energies[i]
+
+# select only strong lines
[…]

### 2015-12-22 generate/xray_sed/prepare_xray_data.py

@@ -1,0 +1,35 @@
+#!/usr/bin/env python
+from pylab import *
+import py_read_output as r 
+import py_plot_output as pl
+import py_plot_util as util 
+import os, sys 
+from constants import *
+import numpy as np
+fname = "grid11/nextgen_a05_pre_xray"
+#fname = "fiducial_xray_fine"
+angle = 75
+
+s = r.read_spectrum("../specs/"+fname)
+
+norm = (100.0 * PARSEC) * (100.0 * PARSEC) / (1e10 * PARSEC) / (1e10 * PARSEC)
+
+fl_to_fnu = s["Lambda"] / s["Freq."]
+
+flambda = s["A%iP0.50" % angle]
+
+fnu = flambda * fl_to_fnu * norm
+
+data_to_write = np.ndarray((2, len(fnu)))
+
+data_to_write[0] = s["Freq."]
+data_to_write[1] = fnu
+
+data_to_write = np.transpose(data_to_write )
+
+header_string = "Frequency(Hz)  |   F_nu (erg/s/cm^2/Hz)\nPower law has spectral index 0.9"
+np.savetxt('qsomod_a05_xray_75deg.spec', data_to_write, header=header_string)
+#np.savetxt('h13mod_xray_75deg.spec', data_to_write, header=header_string)
+
+plot(s["Freq."], fnu)
+savefig("testspec.png")

### 2015-12-22 generate/xray_sed/sed.py

@@ -1,0 +1,127 @@
+#!/usr/bin/env python
+from pylab import *
+import py_read_output as r 
+import py_plot_output as pl
+import py_plot_util as util 
+import os, sys 
+from constants import *
+import numpy as np
+from pretty import *
+
+
+figure(figsize=(12,6))
+
+#subplot(2,1,1)
+
+#fnames = ["1e45", "1e45_uv"]
+#fnames = ["nextgen_alpha1_long_wide","1e45", "1e45_uv"]
+#fnames = ['nextgen_p3_3',"nextgen_3_30", 'nextgen_30_300', 'nextgen_uv', 'nextgen_opt']
+#fnames = ['checkvol_a6',"checkvol_a6_xray","h13","fiducial_xray_fine","fiducial_uv","fiducial_xray"]
+#fnames = ["h13","fiducial_xray_fine","fiducial_uv","fiducial_xray"]
+fnames = ["/Users/jmatthews/Documents/runs/qso_he_test/with_estfix/nextgen_a05_pre_he"]
+NN = len(fnames) - 1
+NN = len(fnames) - 1
+
+alphas = [0.5,0.5,0.75,0.75]
+labels=["1e45, f=0.01", "H13"]
+big_tick_labels(18)
+
+lines = np.log10(C/np.array([6563, 4861, 1215, 1240, 1400, 1550, 1909, 2800])/ANGSTROM)
+textx = np.log10(C/np.array([6563, 4861, 1215, 1400, 1550, 1909, 2800])/ANGSTROM)
+#ycoords = [2, 50, 50, 50, 50, 10, 10]
+line_labels = [r"H$\alpha$", r"H$\beta$", r"Ly $\alpha$~\&~N~\textsc{v}", r"Si~\textsc{iv}", r"C~\textsc{iv}", r"C~\textsc{iii}]", r"Mg~\textsc{ii}"]
+
+
+colors = get_colors()
+
+ccc = [colors[0],colors[0], "k", "k"]
+modcols = [colors[0], "k", "k"]
+
+angles = [20, 89]
+geolab = ["`Quasar-like'", "`Below Wind'"]
+
+lims = ((30.5,31.7), (27.5,30.1))
+
+nu_norm = C/2000.0/ANGSTROM
+
+for iang in range(len(angles)):
+
+	#subplot(2,1,iang+1)
+
+	set_pretty()
+
+	all_nu = np.array([])
[…]

### 2015-12-22 generate/xray_sed/test.py

@@ -1,0 +1,25 @@
+#!/usr/bin/env python
+from pylab import *
+import py_read_output as r 
+import py_plot_output as pl
+import py_plot_util as util 
+import os, sys 
+from constants import *
+import numpy as np
+
+
+sed = np.loadtxt("pg1001_sed_rest.dat",unpack=True)
+yerr = [sed[2],sed[3]]
+
+nu = sed[0]
+nulnu = sed[1]
+
+yerr[0] = -10.0 ** (nulnu + yerr[0]) + (10.0**nulnu)
+yerr[1] = 10.0 ** (nulnu + yerr[1]) - (10.0**nulnu)
+
+errorbar(10.0**sed[0], 10.0**sed[1], yerr=yerr, fmt=".")
+
+print yerr
+
+loglog()
+savefig("test.png")

### 2015-12-22 generate/xray_sed/xray_all.py

@@ -1,0 +1,157 @@
+#!/usr/bin/env python
+from pylab import *
+import py_read_output as r 
+import py_plot_output as pl
+import py_plot_util as util 
+import os, sys 
+from constants import *
+import numpy as np
+from pretty import *
+
+
+figure(figsize=(12,7))
+
+#subplot(2,1,1)
+
+#fnames = ["1e45", "1e45_uv"]
+#fnames = ["nextgen_alpha1_long_wide","1e45", "1e45_uv"]
+#fnames = ['nextgen_p3_3',"nextgen_3_30", 'nextgen_30_300', 'nextgen_uv', 'nextgen_opt']
+#fnames = ['checkvol_a6',"checkvol_a6_xray","h13","fiducial_xray_fine","fiducial_uv","fiducial_xray"]
+#fnames = ["h13","fiducial_xray_fine","fiducial_uv","fiducial_xray"]
+fnames = ["grid11/nextgen_a05_pre_xray"]
+NN = len(fnames) - 1
+NN = len(fnames) - 1
+
+alphas = [0.5,0.5,0.75,0.75]
+labels=["1e45, f=0.01", "H13"]
+big_tick_labels(16)
+
+colors = get_colors()
+
+ccc = [colors[0],colors[0], "k", "k"]
+modcols = [colors[0], "k", "k"]
+
+angles = [85]
+
+for iang in range(len(angles)):
+
+	set_pretty()
+
+	all_nu = np.array([])
+	all_f = np.array([])
+	concatenate
+
+	#bounds = [(1e19,1e18),(1e18,1e17),(1e17,1e16),(1e16,1e15),(1e15,1e14)]
+	bounds = [(1e19,1e14),(1e19,1e14),(1e19,1e14),(1e19,1e14),(1e19,1e14),(1e19,1e14),(1e19,1e14)]
+
+	for i in range(len(fnames)):
+
+		s = r.read_spectrum("../specs/"+fnames[NN-i])
+
+		ev = 1.60217657e-19
+
+		angle = angles[iang]
+
+		nu = s["Freq."]
+		w = s["Lambda"]
+
+		flambda = s["A%iP0.50" % angle]
+
+
+		fl_to_fnu = s["Lambda"] / s["Freq."]
+
+		norm = 4.0 * PI * (100.0 * PARSEC) * (100.0 * PARSEC)
+
[…]

### 2015-12-22 generate/xray_sed/xray_all2.py

@@ -1,0 +1,138 @@
+#!/usr/bin/env python
+from pylab import *
+import py_read_output as r 
+import py_plot_output as pl
+import py_plot_util as util 
+import os, sys 
+from constants import *
+import numpy as np
+from pretty import *
+
+
+figure(figsize=(7,10))
+
+#fnames = ["1e45", "1e45_uv"]
+#fnames = ["nextgen_alpha1_long_wide","1e45", "1e45_uv"]
+#fnames = ['nextgen_p3_3',"nextgen_3_30", 'nextgen_30_300', 'nextgen_uv', 'nextgen_opt']
+#fnames = ['checkvol_a6',"checkvol_a6_xray","h13","fiducial_xray_fine","fiducial_uv","fiducial_xray"]
+#fnames=["nextgen_a05_pre_xray", "nextgen_a06_pre_xray", "nextgen_a075_pre_xray", "nextgen_a05_pre_xray_he","nextgen_a06_pre_xray_he"]
+fnames = ["nextgen_a05_pre_xray_he", "nextgen_a05_pre_xray"]
+
+#fnames = ["h13","fiducial_xray_fine","fiducial_uv","fiducial_xray"]
+NN = len(fnames) - 1
+NN = len(fnames) - 1
+
+alphas = [0.5,0.5,0.75,0.75]
+labels=["1e45, f=0.01", "H13"]
+big_tick_labels(16)
+
+colors = get_colors()
+
+#ccc = [colors[0],colors[0], "k", "k"]
+#
+
+
+angles = [60,72,78,75]
+
+for iang in range(len(angles)):
+
+	subplot(4,1,iang+1)
+
+	set_pretty()
+
+	all_nu = np.array([])
+	all_f = np.array([])
+	
+	text(2e17,1e44,"$i=%2i^\circ$" % angles[iang], fontsize=20)
+
+	#bounds = [(1e19,1e18),(1e18,1e17),(1e17,1e16),(1e16,1e15),(1e15,1e14)]
+	#bounds = [(1e19,1e14),(1e19,1e14),(1e19,1e14),(1e19,1e14),(1e19,1e14),(1e19,1e14),(1e19,1e14)]
+
+	for i in range(len(fnames)):
+
+		lname = fnames[i][8:11]
+		if "he" in fnames[i]:
+			lname ="He and H"
+		else:
+			lname = "H"
+
+
[…]

### 2015-12-22 generate/xray_sed/xray_lines.py

@@ -1,0 +1,58 @@
+#!/usr/bin/env python
+from pylab import *
+import py_read_output as r 
+import py_plot_output as pl
+import py_plot_util as util 
+import os, sys 
+from constants import *
+import numpy as np
+from pretty import *
+
+def get_linelist(filenames, ionreturn=False):
+
+	lines = np.array([])
+	z = np.array([])
+
+	for i in range(len(filenames)):
+
+		x = np.loadtxt(filenames[i], comments="#", usecols=(2,3), unpack=True)
+
+		lines = np.concatenate((lines, x[1]))
+
+		z = np.concatenate((z, x[0]))
+
+	if ionreturn:
+		return lines, z
+	else:
+		return lines
+
+z, ion, wave, f = np.loadtxt("data/atomic78/lines_linked_ver_2.py", comments="#", usecols=(1,2,3,4), unpack=True)
+
+set_pretty()
+#select = (z == )
+E = 1e-3 * HEV * C / (wave * ANGSTROM)
+
+#zz = np.array([6,7,8,10,26])
+
+zz, ions = np.loadtxt("elems", unpack=True, usecols=(1,2), dtype='string')
+#ions = ["C","N","O","Ne","Fe"] 
+zz = zz.astype(int)
+
+ions = ions[(zz > 3)]
+zz = zz[(zz > 3)]
+
+
+colors = np.concatenate((get_colors(),get_colors(),get_colors()))
+
+for j in range(len(zz)):
+	select = (z == zz[j])
+	scatter(E[select], ion[select], s=200*f[select], label=ions[j],c=colors[j])
+
+float_legend()
+xlim(0.3,7)
+ylim(0,27)
+semilogx()
+xlabel("Line Energy (eV)")
+ylabel("Ion")
+savefig("ions.png",dpi=200)
+clf()

### 2015-12-22 generate/agnspec_fig/agnspec.py
added generate

@@ -1,180 +1,0 @@
-#!/usr/bin/env python
-from pylab import *
-import py_read_output as r 
-import py_plot_output as pl
-import py_plot_util as util 
-import os, sys 
-from constants import *
-import numpy as np
-import pretty
-from pretty import *
-
-D = 100.0 * PARSEC
-
-def Ledd (m):
-
-	'''
-	calculates eddington luminosity for a solar mass m
-	
-	Args:
-		m	mass in solar masses
-	
-	returns:
-		Eddington luminosity in ergs s^-1, float
-	'''
-	
-	m *= MSOL
-	
-	consts = (4.0 * PI * G * C * MPROT ) / THOMPSON
-	
-	L = consts * m
-	
-	return L
-
-def run_agnspec(fname, mass=1e9, mdot=5, angm=0, alpha=0.01, inc=80):
-
-	mu = np.cos(inc / 180.0 * np.pi)
-
-	print inc, mu
-
-	param_string = "mass=%8.4e,mdot=%8.4e,angm=%.6f,alpha=%.6f,mu=%8.4e,savename=\"%s\"" % (mass, mdot, angm, alpha, mu, fname)
-
-	print param_string
-	os.system("idl -e 'agnspec,%s' > idl.out" % param_string)
-
-	return 0
-
-def read_agnspec(fname):
-
-	nu, lnu = np.loadtxt(fname, unpack=True, usecols=(0,1))
-
-	wave = (C / nu) / ANGSTROM
-
-	llambda = nu * lnu / wave
-
-	flambda = llambda / 4.0 / PI / (D*D)
-
-	return wave, flambda
-
-def mdot_from_edd ( edd, m , eta = 0.1):
-
-	''' 
-	calculates an accretion rate from an eddington fraction
-	Args:
-		edd_frac		eddington fraction
-		m			mass of central object in solar masses
-		eta			accretion efficiency, set to 1 (0.1 more realistic)
-	
-	returns:
-		mdot in solar masses / yr
-	'''
-	
-	L = Ledd (m)		# eddington luminosity
-	
-	mdot = edd * L / ( (C ** 2) )
-	
-	mdot *= 1.0 / eta
-	
-	mdot = mdot * ( YR ) / MSOL	# normalise units
-	
-	return mdot
-
-def run_grid(masses, edd_frac, spin, incs):
-
[…]

### 2015-12-23 paper.tex
final all-in version

@@
 \title
-[Testing Quasar Unification: Radiative Transfer in Clumpy Winds]{
+[Radiative Transfer in Clumpy Winds]{
 % Modelling quasar outflows:
@@
 Here, we continue our tests of this paradigm by comparing quasar spectra to synthetic spectra of biconical disc wind models, produced with our state-of-the-art Monte Carlo radiative transfer code.
-Previously, we have shown that we could produce synthetic spectra resembling those of observed broad absorption line (BAL) quasars, but only if the X-ray luminosity was limited to about
+Previously, we have shown that we could produce synthetic spectra resembling those of observed broad absorption line (BAL) quasars, but only if the X-ray luminosity was limited to
 10$^{43}$~erg~s$^{-1}$.
@@
 which are reprocessed by `macro-atoms' with associated transition probabilities.
+We use the Sobolev approximation \citep[e.g.][]{sobolev1957,sobolev1960,rybickihummer1978}
+to compute the location of line interactions.
 In our case, for reasons of computational efficiency, we adopt the  hybrid macro-atom scheme 
@@
 \centering
-\includegraphics[width=0.45\textwidth]{figures/fig2_cartoon.png}
+\includegraphics[width=0.45\textwidth]{figures/fig1.eps}
 \caption
@@
 via an indivisible energy packet constraint (see Lucy 2002, M15).
-% In addition to the disc and X-ray source, 
-% the wind is able to reprocess radiation. However, new 
-% photon packets are not produced in the wind (as in LK02). 
-% Instead, this reprocessing is dealt with by enforcing strict
-% radiative equilibrium ({\em modulo} adiabatic cooling; see section~2.3)
-% via an indivisible energy packet
-% constraint (see Lucy 2002, M15).  
-% {\bf I confess, I do not understand what is being said here.
-I would like to understand it better, and I would like it explained better.
-How do we avoid, generating for example recombination photons from non-macro atoms.}
 
@@
 quasars and luminous AGN.
-% We also examine trends with inclination in the synthetic spectra, 
-% both in terms of the range of ionization states of the absorption lines and equivalent widths of the emission lines.
 
@@
 $R_v$  	        &	 $10^{19}$cm$^*$ \\ 
-$\alpha$ 	&	 $0.6^*$ \\
+$\alpha$ 	&	 $0.5^*$ \\
 $f_V$ 	&	 $0.01^*$  \\
@@
 $n_z$ 	&	 $200$  \\
-\hline 
-% Derived Parameters 	&	 Value \\ 
-% \hline \hline
-% $L_{\nu}(2500\mbox{\scriptsize{\AA}})$&	 $6.3\times10^{30}~\rm{ergs~s^{-1}~Hz^{-1}}$\\ 
-% $L_{\nu}(2keV)$   &	 $1.2\times10^{25}~\rm{ergs~s^{-1}~Hz^{-1}}$\\ 
-% $L_{bol}$ 	 &	 $2.4\times10^{46}~\rm{ergs~s^{-1}}$\\
-% $M_{bol}$ 	 &	 -27.4\\ 
-% $M_u$            &	 -26.2\\ 
-% $\alpha_{OX} $ 	 &	 -2.2\\ 
 \end{tabular}
@@
 \centering
-\includegraphics[width=1.0\textwidth]{figures/link8.png}
+\includegraphics[width=1.0\textwidth]{figures/fig2.eps}
 \caption
@@
 \centering
-\includegraphics[width=1.0\textwidth]{figures/uvspec_new.png}
+\includegraphics[width=1.0\textwidth]{figures/fig3.eps}
 \caption
@@
 \centering
-\includegraphics[width=0.5\textwidth]{figures/windnew3.png}
+\includegraphics[width=0.5\textwidth]{figures/fig4.eps}
 \caption
@@
 \centering
-\includegraphics[width=1.0\textwidth]{figures/sed.png}
+\includegraphics[width=1.0\textwidth]{figures/fig5.eps}
 \caption
@@
 $\log (\nu L_{\nu})_{3000}$  & $46.18$ & $45.79 \pm 0.30$ \\
-% $\log L$[H~$\alpha$] & $43.46$ & $42.86$ & ?? \\
-% $EW$[C~\textsc{iv}] (erg~s$^{-1}$) & $3.96 \times 10^{44}$ & $2.62 \times 10^{44}$  \\
-% $EW$[Mg~\textsc{ii}] (erg~s$^{-1}$) & $3.50 \times 10^{43}$ & $8.32 \times 10^{43}$ \\
-% $EW$[H~$\alpha$] (erg~s$^{-1}$) & $3.50 \times 10^{43}$ & $8.32 \times 10^{43}$ \\
-% $\log L_{1350}$ (erg~s$^{-1}$~Hz$^{-1}$) & $46.42$ & $45.56$ & $46.01 \pm 0.30$ \\
-% $\log L_{3000}$ (erg~s$^{-1}$~Hz$^{-1}$) & $46.18$ & $45.36$ & $45.79 \pm 0.30$ \\
-% $L_{bol})$ (erg~s$^{-1}$) & 2.62
-% % $L_{1300})$(C\textsc{iv}) & 
-% \\
-% \multicolumn{3}{|l|}{At $73^\circ$ (`BALQSO-like')} \\  
-% $\log L$[C~\textsc{iv}] (erg~s$^{-1}$) & $44.14$ & ??  \\
-% $\log L$[Mg~\textsc{ii}] (erg~s$^{-1}$) & $42.82$ & $44.41$  \\
-% $\log L$[H~$\alpha$] (erg~s$^{-1}$) & $42.86$ & ?? \\
-% % $EW$[C~\textsc{iv}] (erg~s$^{-1}$) & $3.96 \times 10^{44}$ & $2.62 \times 10^{44}$  \\
-% % $EW$[Mg~\textsc{ii}] (erg~s$^{-1}$) & $3.50 \times 10^{43}$ & $8.32 \times 10^{43}$ \\
-% % $EW$[H~$\alpha$] (erg~s$^{-1}$) & $3.50 \times 10^{43}$ & $8.32 \times 10^{43}$ \\
-% $\log L_{1350}$ (erg~s$^{-1}$~Hz$^{-1}$) & $45.56$ & $46.00$ \\
-% $\log L_{3000}$ (erg~s$^{-1}$~Hz$^{-1}$) & $45.36$ & $45.79$ \\
 \hline
@@
 reproduce the range of ionization states seen in quasars.
-% This is because we do not fully solve the C level populations,
-% and thus the level populations do not accurately reflect those
-% as a full macro-atom with a 
-% full collisional rates between forbidden
-% or semi-forbidden transitions, as would be required.
-% The critical density of the C~\textsc{iii}]~1909\AA\, line 
-% is $n_e\sim10^{9.5}~\rm{cm^{-3}}$ \citep{wei1988}, which is higher than much of the 
-% outer portion of our wind. 
-% We therefore expect a model with these 
-% parameters to produce a C~\textsc{iii}]~1909\AA\ line
-% with a proper treament. We note, however, the the presence of
-% this line in the spectrum of quasars does {\em not} prohibit denser material having a significant contribution to the spectrum.
-
-% The model produces strong emission lines in \civ, \nv\ and \la,
-% as well as a very weak \mg\ line.
 
@@
 \centering
-\includegraphics[width=0.9\textwidth]{figures/lx_a05_pre.png}
+\includegraphics[width=0.9\textwidth]{figures/fig6.eps}
 \caption
@@
 \centering
-\includegraphics[width=0.8\textwidth]{figures/c4_angles.png}
+\includegraphics[width=0.8\textwidth]{figures/fig7.eps}
 \caption
@@
 \centering
-\includegraphics[width=1.0\textwidth]{figures/scatter_c4_grid.png}
+\includegraphics[width=1.0\textwidth]{figures/fig8.eps}
 \caption
@@
 \clearpage
-%\appendix
-% \appendix
-% \section{Notes}
 

### 2015-12-23 generate/angles/angle_plot.py

@@ -243,8 +243,8 @@ def BALnicity ( nu_line, nu_array, spec_array):
 
 #name = "../specs/checkvol_a6"
 name = "../specs/grid10/nextgen_a05"
-name = "/Users/jmatthews/Documents/runs/qso_he_test/with_estfix/nextgen_a05_pre_he"
-
+name = "../specs/webgrid/run6_thmin70_rmin50_a0p6_rv1e19_f0p01.spec"
+name = "../specs/webgrid/run5_thmin70_rmin50_a0p5_rv1e19_f0p01.spec"
 s = r.read_spectrum(name)
 make_c4_plot(s, name)
 

### 2015-12-23 generate/uvspec/new_uvspec_fig.py

@@ -1,0 +1,174 @@
+#!/usr/bin/env python
+from pylab import *
+import py_read_output as r 
+import py_plot_output as pl
+import py_plot_util as util 
+import os, sys 
+from constants import *
+import numpy as np
+import pyfits as py
+import sdss
+from pretty import *
+
+
+set_pretty()
+big_tick_labels(18)
+rcParams["axes.linewidth"]=1.5
+NORM = True
+almost_black = '#262626'
+#nameb = "nextgen_alpha1_long"
+suffix = "_a075_pre_he"
+
+PYTHON = os.environ["PYTHON"]
+
+
+namea = "grid11/nextgen%s" % suffix
+namea = "../specs/webgrid/run5_thmin70_rmin50_a0p5_rv1e19_f0p01.spec"
+#nameb = "../specs/grid11/nextgen_uv"
+namec = "asi_thmin70_rmin50_a1_f0p01_mdotw5"
+#namec = "asi_thmin70_rmin50_a0p75_f0p01_mdotw5"
+
+name2 = "fiducial"
+smoda = r.read_spectrum(namea)
+#smodb = r.read_spectrum("../specs/"+nameb)
+#smodc = r.read_spectrum("../specs/"+namec)
+
+
+sdisk = r.read_spectrum("../../generate/specs/disk")
+sh13 = r.read_spectrum("../../generate/specs/h13")
+
+lines = [1215, 1240, 1400, 1550, 1640, 1860, 1909, 2800]
+textx = [1215, 1400, 1550, 1650, 1860, 2800]
+ycoords = [2, 50, 50, 50, 50, 30, 10]
+line_labels = [r"Ly $\alpha$", r"N~\textsc{v}", r"Si~\textsc{iv}", r"C~\textsc{iv}", r"He~\textsc{ii}", r"Al~\textsc{iii}", "C~\\textsc{iii}]", r"Mg~\textsc{ii}"]
+line_labels = [r"Ly $\alpha$~\&~N~\textsc{v}", r"Si~\textsc{iv}", r"C~\textsc{iv}", r"He~\textsc{ii}", r"Al~\textsc{iii}~\&~C~\textsc{iii}]", r"Mg~\textsc{ii}"]
+
+angles = [20,60,73,76]
+
+colors = get_colors()
+
+figure(figsize=(10,12))
+
+NORM_WAVELENGTH = 1300
+
+
[…]

### 2015-12-23 generate/uvspec/sdss.py

@@ -1,0 +1,820 @@
+#!/Library/Frameworks/Python.framework/Versions/2.7/Resources/Python.app/Contents/MacOS/Python
+
+
+import pyfits as py
+import matplotlib.pyplot as plt
+import pylab
+import os, sys
+import numpy as np
+
+
+plt.rcParams["text.usetex"] = "True"
+
+POSITION_DELTA = 0.01
+VARIANCE_DELTA = 1
+
+
+def read_sdss(name):
+    """    
+    Read SDSS spectra fits. Plotting capability.
+
+    :INPUTS:
+       name: Filename of fits spectra
+       
+    :OUTPUTS:
+       wave: wavelength array - Angstroms
+
+       flux: flux array  - Flux lambda erg/s/cm^2/Angstrom
+    """
+    flux=py.getdata(name,0)
+    wdel=py.getval(name,'CD1_1',0)
+    w0=py.getval(name,'CRVAL1',0)
+    wave= 10.0**(w0+wdel*np.arange(len(flux[0])))
+    
+    return(wave,flux[0]*1e-17)
+
+
+
+
+######################################################################
+#
+#		PLOTTING FUNCTIONS
+#
+#
+######################################################################
+
+
+def plot_sdss(name, lmin, lmax, save=True , norm = True):
+
+
+
+	fig = plt.figure()
+
+	ax = fig.add_subplot(111)
+
+	wave, flux = read_sdss(name)
+
+	if norm:
+		flux = normalise(wave, flux, lmin)
+
+	ax.plot(wave, flux)
+
+	plt.xlim(lmin, lmax)
+
+	savename = "%s_%i_%i.png" %( name[:-3], lmin, lmax)
+
+	ax.set_xlabel("$\lambda (\AA)$")
+	ax.set_ylabel("Flux")
+
+	if save: 	
+		plt.savefig( savename )
+
+	#os.system("open -a preview %s" % savename)
+
+def plotall(lmin, lmax):
+
+	fig = plt.figure()
+
+	ax = fig.add_subplot(111)
+
+	f = open("lsfile", "r")
+
+	for line in f:
+		filename = line.split()[0]
+
+		wave, flux = read_sdss(filename)
+
+		flux = normalise(wave, flux, lmin)
+
+		ax.plot(wave, flux)
+		plt.xlim(lmin, lmax)
+
[…]

### 2015-12-23 generate/wind_plot/link_8.py

@@ -9,6 +9,7 @@ import numpy as np
 from pretty import *
 
 set_pretty()
+big_tick_labels(18)
 
 from matplotlib.colors import LinearSegmentedColormap
 
@@ -45,7 +46,7 @@ xuse= np.append(x1000,1e19)
 print x1000, y1000
 
 
-root = "nextgen_a05_pre_he"
+root = "run64_thmin70_rmin50_a0p5_rv1e19_f0p01"
 d = r.read_pywind_summary(root)
 
 
@@ -121,11 +122,11 @@ for i in range(len(strings)):
 
 
 
-subplots_adjust(bottom=0.05, top=0.95, hspace = 0, wspace=0.13, left = 0.08, right=0.92)
+subplots_adjust(bottom=0.05, top=0.95, hspace = 0, wspace=0.2, left = 0.08, right=0.97)
 
 savefig("link8_%s.png" % root, dpi=300)
 savefig("../../figures/link8.png", dpi=300)
-#savefig("../../figures/wind.eps", bbox="tight")
+savefig("../../figures/fig2.eps", bbox="tight")
 
 
 

### 2015-12-23 generate/xray/lx.py

@@ -52,7 +52,7 @@ aaa = "06"
 vers = "pre"
 suffix1 = "_a%s_%s" % (aaa,vers)
 suffix2 = "_a%s_%s_xray" % (aaa,vers)
-fnames = [("../specs/fiducial_xray_fine", "../specs/h13.spec"), ("restart_xrays", "/Users/jmatthews/Documents/runs/qso_he_test/with_estfix/nextgen_a05_pre_he")]
+fnames = [("../specs/fiducial_xray_fine", "../specs/h13.spec"), ("restart_xrays", "../specs/webgrid/run5_thmin70_rmin50_a0p5_rv1e19_f0p01.spec")]
 #fnames = 
 # 9 before
 label=fnames[1][0][16:]
@@ -241,7 +241,7 @@ xlim(27.5,32.5)
 
 
 xlabel(r"$\log[L_{2500}$~(erg~s$^{-1}$~Hz$^{-1}$)]", fontsize=20)
-ylabel(r"$\log[L_{2kev}$~(erg~s$^{-1}$~Hz$^{-1}$)]", fontsize=20)
+ylabel(r"$\log[L_{2keV}$~(erg~s$^{-1}$~Hz$^{-1}$)]", fontsize=20)
 
 subplots_adjust(hspace=0)
 long_ticks()
@@ -251,5 +251,5 @@ savefig("lx%s.png" % suffix1)
 #savefig("lx.png", bbox="tight")
 #
 savefig("../../figures/lx.png", bbox="tight")
-#savefig("../../figures/alpha_ox_%s.eps" % label, bbox="tight")
+savefig("../../figures/fig6.eps", bbox="tight")
 clf()

### 2015-12-23 generate/xray_sed/sed.py

@@ -18,7 +18,7 @@ figure(figsize=(12,6))
 #fnames = ['nextgen_p3_3',"nextgen_3_30", 'nextgen_30_300', 'nextgen_uv', 'nextgen_opt']
 #fnames = ['checkvol_a6',"checkvol_a6_xray","h13","fiducial_xray_fine","fiducial_uv","fiducial_xray"]
 #fnames = ["h13","fiducial_xray_fine","fiducial_uv","fiducial_xray"]
-fnames = ["/Users/jmatthews/Documents/runs/qso_he_test/with_estfix/nextgen_a05_pre_he"]
+fnames = ["../specs/webgrid/run5_thmin70_rmin50_a0p5_rv1e19_f0p01.spec"]
 NN = len(fnames) - 1
 NN = len(fnames) - 1
 
@@ -80,7 +80,7 @@ for iang in range(len(angles)):
 
 		f2000 = util.get_flux_at_wavelength(nu, lnu,nu_norm)
 
-		w,f = np.loadtxt("/Users/jmatthews/Documents/Python/examples/sdssedrqsobal/sdss_hst_combined.dat", unpack=True,usecols=(0,1))
+		w,f = np.loadtxt("/Users/jamesmatthews/Documents/Python/examples/sdssedrqsobal/sdss_hst_combined.dat", unpack=True,usecols=(0,1))
 		nuc = C / (w*ANGSTROM)
 		fl_to_fnu = w / nuc 
 		lnuc = f * fl_to_fnu
@@ -106,7 +106,7 @@ for iang in range(len(angles)):
 		xlim(14.64,15.5)
 		ylim(-4.6,1.2)
 		#ylim(lims[iang][0], lims[iang][1])
-		ylabel(r"$\log [F_\nu / F_{2000\AA}]$ (Arb.)", fontsize=20)
+		ylabel(r"$\log [F_\nu / F_{2000}]$ (Arb.)", fontsize=20)
 
 		#if iang == 0:
 		#	gca().set_xticklabels([])
@@ -121,6 +121,7 @@ subplots_adjust(hspace=0, wspace=0, left=0.08, right=0.97)
 xlabel(r"$\log \nu$", fontsize=20)
 
 savefig("sed.png",dpi=300)
+savefig("../../figures/fig5.eps")
 #sys.exit()
 
 

### 2015-12-23 paper.tex
slimming down

@@
 %%%% Various options for document class.
-%\usepackage{psfig,morefloats,url}
-%use preprint2 for 2 columns paper.
 
@@
 \title
-[Radiative Transfer in Clumpy Winds]{
-% Modelling quasar outflows:
-% clumpy winds and broad emission lines
+[Radiative Transfer in Clumpy Winds]
+{
 Testing Quasar Unification: Radiative Transfer in Clumpy Winds
-%Unifying quasars with clumpy wind models
 }
@@
 
+\maketitle
 \begin{abstract} 
@@
 
-\maketitle
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 geometrically thin, optically thick accretion disc surrounding the central black hole (BH), similar to that described by \cite{shakurasunyaev1973}.
-% {\bf Note: the first half of this paragraph and the second do not follow from one another.  
-% The first half is about spectra the second about outflows and the connection to spectra is not made until the next paragrph.  
-% This needs fixing. JM: Knox, I like this structure...I start with inflow, then move to outflow.}
 In addition to the {\em inflowing} accreting material, 
@@
 
-\begin{figure} %fullpage
+\begin{figure*}
 \centering
@@
 \label{fig:wind}
-\end{figure} %fullpage
+\end{figure*}
 
@@
 a clumping factor of 0.01, even though the value of $U_H$ decreases by only a factor of $\sim10$ compared to H13.
-%This is also the reason for significant Lyman edge photoabsorption
-%at the highest inclinations (see section 4.3).
 
@@
 escaping the Sobolev region for each line. 
-% This is equivalent to $\beta_{ul} n_u A_{ul}$, where the three quantities
-% represent the Sobolev escape probability, upper level number density and 
-% Einstein A coefficient for the line. 
 As shown in Fig.~\ref{fig:wind},
@@
 \label{fig:uvspec}
-\end{figure} %fullpage
+\end{figure*}
 
@@
 \label{fig:sed}
-\end{figure} %fullpage
+\end{figure*}
 
@@
 line shapes (see e.g. Trump et al. 2006; Knigge et al 2008, Filiz Ak et al. 2014).
-% In addition, the line profile shape is strongly dependent 
-% on the density, ionization and velocity 
-% profiles intersected by the line of sight. Thus, small tweaks of the velocity
-% law and angular distributions of streamlines can dramatically alter
-% the shape of the line.
 
@@
 with flat bases to the absorption troughs \citep{arav1999b,arav1999a}.
-%Non-black saturation is observed in the absorption troughs of BALQSOs \citep{arav1999b,arav1999a}.
 This is usually explained either as  partial covering of the continuum
@@
 \label{fig:xray}
-\end{figure} %fullpage
+\end{figure*}
 
@@
 \label{fig:lobal}
-\end{figure} %fullpage
+\end{figure*}
 
@@
 \label{fig:grid}
-\end{figure} %fullpage
+\end{figure*}
 
@@
 
-\bibliography{mybib.bib,stellar.bib,h14.bib,h13.bib,hamann.bib,krolik.bib}
-\clearpage
-\clearpage
+\bibliography{bibs/mybib.bib,bibs/stellar.bib,bibs/h14.bib,bibs/h13.bib,bibs/hamann.bib,bibs/krolik.bib}
 

### 2015-12-23 generate/angles/angle_plot.py

@@ -1,284 +1,0 @@
-#!/usr/bin/env python
-from pylab import *
-import py_read_output as r 
-import py_plot_output as pl
-import py_plot_util as util 
-import os, sys 
-from constants import *
-import numpy as np
-from collections import OrderedDict
-from plot_norm import make_f, get_continuum
-import plot_norm as _plot_norm
-from pretty import *
-try:
-	from thread import get_ident as _get_ident
-except ImportError:
-	from dummy_thread import get_ident as _get_ident
-
-
-def add_after(pf, key_after, newkey, newval):
-
-	before_dict = OrderedDict()
-	after_dict = OrderedDict()
-	new_dict = OrderedDict([(newkey, newval)])
-	after = False 
-
-	for key,val in pf.viewitems():
-
-		if after:
-			after_dict[key] = val
-		else:
-			before_dict[key] = val
-
-		if key == key_after:
-			after = True
-
-
-	all_dicts = OrderedDict(before_dict.items() + new_dict.items()  + after_dict.items())
-
-	return all_dicts
-
-def vel_nu (nu, nu_0):
-	'''
-	Returns the velocity of a frequency nu with respect to 
-	line centre nu_0 in units of cm/s
-	'''
-	delta_nu = nu - nu_0
-	
-	vel = C * delta_nu / nu_0
-	
-	return vel
-
-def nu_vel(v, nu_0):
-	'''
-	Returns the frequency of a velocity v with respect to 
-	line centre nu_0 in units of cm/s
-	'''
-	
-	nu =  (nu_0 * v / C) + nu_0
-	
-	return nu
-
-
-def normalize(w, f):
-
-	a = get_continuum(w, f, [1215,1550,1400,2800], lmin=1300, lmax=3000, deg=2)
-
-	#fnorm = f/make_f(a, w)
-
-	#fnorm = f / util.get_flux_at_wavelength(w,f,1450)
-
-	return make_f(a, w)
-
-
-
-def make_c4_plot(s, name, angmin=70, angmax=82):
-
-	nangles = len(s.colnames) - 9
-
-	nu_c4 = C / (1550.0 * ANGSTROM)
-	big_tick_labels(18)
-
[…]

### 2015-12-23 generate/cartoon/SV_cartoon.py

@@ -1,97 +1,0 @@
-'''
-SV_cartoon.py 
-
-This script creates the cartoon figure for 
-the 2014 CV paper. The data were scraped from Dexter.
-'''
-
-import matplotlib.mlab as mlab
-import numpy as np
-import matplotlib.pyplot as plt
-import matplotlib as mpl
-
-plt.xkcd()
-
-
-#mpl.rcParams['pdf.use14corefonts'] = True
-#mpl.rc('font',**{'family':'sans-serif','sans-serif':['Helvetica']})
-## for Palatino and other serif fonts use:
-#rc('font',**{'family':'serif','serif':['Palatino']})
-#mpl.rc('text', usetex=True)
-
-thetamin=72.0
-thetamax=80.0
-diskmax=25.0
-xmin=10.0
-xmax=18.0
-rstar=2.0
-
-xwindmax=40.0
-zwindmax=(xwindmax-xmin)*np.tan(np.radians(90.0-thetamin))
-
-
-posx=np.arange(xmin,xwindmax,(xmax-xmin)/10.0)
-ymin1=[]
-ymax1=[]
-
-x=np.array([xmin,xmax,xwindmax])
-y1=np.array([0.0,(xmax-xmin)*np.tan(np.radians(90.0-thetamin)),(xwindmax-xmin)*np.tan(np.radians(90.0-thetamin))])
-y2=np.array([0.0,0.0,(xwindmax-xmax)*np.tan(np.radians(90.0-thetamax))])
-
-lsize=14
-tsize=16 
-
-fig=plt.figure()
-ax=fig.add_subplot(1,1,1)
-ax.plot(x,y1,x,y2,color='black')
-ax.plot(-1.0*x,y1,-1.0*x,y2,color='black')
-ax.plot(-1.0*x,-1.0*y1,-1.0*x,-1.0*y2,color='black')
-ax.plot(x,-1.0*y1,x,-1.0*y2,color='black')
-ax.set_xlim([-1.0*xwindmax,xwindmax])
-plt.fill_between(x,y1, y2, facecolor='0.9', interpolate=True)
-plt.fill_between(-1.0*x,y1, y2, facecolor='0.9', interpolate=True)
-plt.fill_between(x,-1.0*y1, -1.0*y2, facecolor='0.9', interpolate=True)
[…]

### 2015-12-23 generate/cartoon/just_text.py

@@ -1,94 +1,0 @@
-'''
-SV_cartoon.py 
-
-This script creates the cartoon figure for 
-the 2014 CV paper. The data were scraped from Dexter.
-'''
-
-import matplotlib.mlab as mlab
-import numpy as np
-import matplotlib.pyplot as plt
-import matplotlib as mpl
-
-#plt.xkcd()
-
-
-#mpl.rcParams['pdf.use14corefonts'] = True
-#mpl.rc('font',**{'family':'sans-serif','sans-serif':['Helvetica']})
-## for Palatino and other serif fonts use:
-#rc('font',**{'family':'serif','serif':['Palatino']})
-#mpl.rc('text', usetex=True)
-
-thetamin=72.0
-thetamax=80.0
-diskmax=25.0
-xmin=10.0
-xmax=18.0
-rstar=2.0
-
-xwindmax=40.0
-zwindmax=(xwindmax-xmin)*np.tan(np.radians(90.0-thetamin))
-
-
-posx=np.arange(xmin,xwindmax,(xmax-xmin)/10.0)
-ymin1=[]
-ymax1=[]
-
-x=np.array([xmin,xmax,xwindmax])
-y1=np.array([0.0,(xmax-xmin)*np.tan(np.radians(90.0-thetamin)),(xwindmax-xmin)*np.tan(np.radians(90.0-thetamin))])
-y2=np.array([0.0,0.0,(xwindmax-xmax)*np.tan(np.radians(90.0-thetamax))])
-
-lsize=14
-tsize=16 
-
-fig=plt.figure()
-ax=fig.add_subplot(1,1,1)
-ax.plot(x,y1,x,y2,color='black', linewidth=0)
-ax.plot(-1.0*x,y1,-1.0*x,y2,color='black', linewidth=0)
-ax.plot(-1.0*x,-1.0*y1,-1.0*x,-1.0*y2,color='black', linewidth=0)
-ax.plot(x,-1.0*y1,x,-1.0*y2,color='black', linewidth=0)
-ax.set_xlim([-1.0*xwindmax,xwindmax])
-
-# plt.fill_between(x,y1, y2, facecolor='0.9', interpolate=True)
-# plt.fill_between(-1.0*x,y1, y2, facecolor='0.9', interpolate=True)
-# plt.fill_between(x,-1.0*y1, -1.0*y2, facecolor='0.9', interpolate=True)
[…]

### 2015-12-23 generate/cartoon/xkcd_cart.py

@@ -1,100 +1,0 @@
-'''
-SV_cartoon.py 
-
-This script creates the cartoon figure for 
-the 2014 CV paper. The data were scraped from Dexter.
-'''
-
-import matplotlib.mlab as mlab
-import numpy as np
-import matplotlib.pyplot as plt
-import matplotlib as mpl
-
-plt.xkcd()
-
-
-#mpl.rcParams['pdf.use14corefonts'] = True
-#mpl.rc('font',**{'family':'sans-serif','sans-serif':['Helvetica']})
-## for Palatino and other serif fonts use:
-#rc('font',**{'family':'serif','serif':['Palatino']})
-#mpl.rc('text', usetex=True)
-
-thetamin=72.0
-thetamax=80.0
-diskmax=25.0
-xmin=10.0
-xmax=18.0
-rstar=2.0
-
-xwindmax=40.0
-zwindmax=(xwindmax-xmin)*np.tan(np.radians(90.0-thetamin))
-
-
-posx=np.arange(xmin,xwindmax,(xmax-xmin)/10.0)
-ymin1=[]
-ymax1=[]
-
-x=np.array([xmin,xmax,xwindmax])
-y1=np.array([0.0,(xmax-xmin)*np.tan(np.radians(90.0-thetamin)),(xwindmax-xmin)*np.tan(np.radians(90.0-thetamin))])
-y2=np.array([0.0,0.0,(xwindmax-xmax)*np.tan(np.radians(90.0-thetamax))])
-
-lsize=14
-tsize=16 
-
-fig=plt.figure()
-ax=fig.add_subplot(1,1,1)
-ax.plot(x,y1,x,y2,color='black')
-ax.plot(-1.0*x,y1,-1.0*x,y2,color='black')
-ax.plot(-1.0*x,-1.0*y1,-1.0*x,-1.0*y2,color='black')
-ax.plot(x,-1.0*y1,x,-1.0*y2,color='black')
-ax.set_xlim([-1.0*xwindmax,xwindmax])
-plt.fill_between(x,y1, y2, facecolor='0.9', interpolate=True)
-plt.fill_between(-1.0*x,y1, y2, facecolor='0.9', interpolate=True)
-plt.fill_between(x,-1.0*y1, -1.0*y2, facecolor='0.9', interpolate=True)
-plt.fill_between(-1.0*x,-1.0*y1, -1.0*y2, facecolor='0.9', interpolate=True)
[…]

### 2015-12-23 generate/egv1/egv.py

@@ -1,55 +1,0 @@
-#!/usr/bin/env python
-from pylab import *
-import py_read_output as r 
-import py_plot_output as pl
-import py_plot_util as util 
-import os, sys 
-from constants import *
-import numpy as np
-from pretty import *
-
-eddmod =[0.2]
-mbhmod = [1e9]
-
-
-mbh, l = np.loadtxt("balqsos_mbh_ledd.dat", unpack=True, usecols=(2,3))
-
-names1, names2 = np.loadtxt("balqsos_mbh_ledd.dat", unpack=True, usecols=(0,1), dtype="str")
-
-
-names = []
-locs = []
-for i in range(len(names1)):
-
-	names.append(names1[i] + ' ' + names2[i])
-
-	print names[i]
-
-	#if names[i] == 'PG 1001+054' or names[i] == 'Mkn 231':
-	if names[i] == 'Mkn 231':
-		locs.append(i)
-#names = names1 + names2
-#print names
-
-set_pretty()
-
-colors=get_colors()
-
-scatter(10.0**mbh, 10.0**l, marker="x", s=100, c="k")
-scatter(mbhmod, eddmod, marker="*", s=100, c="r")
-
-
-for j in locs:
-	print mbh[j], l[j], names[j]
-	text(mbh[j], l[j], names[j])
-
-xlabel(r"$M_{BH} (M_\odot)$", fontsize=20)
-ylabel(r"$L/L_{edd}$", fontsize=20)
-
-loglog()
-
-savefig("egv.png", dpi=500)
-
-
-
-

### 2015-12-23 generate/ew/ew.py

@@ -1,280 +1,0 @@
-#from plot_norm import *
-import numpy as numpy
-from pylab import *
-import os, sys
-from cobra_sub import smooth
-import py_read_output as r 
-import py_plot_output as pl
-import py_plot_util as util 
-import matplotlib.pyplot as plt
-import matplotlib.gridspec as gridspec
-from plot_norm import *
-from constants import *
-from pretty import *
-
-set_pretty()
-
-def get_continuum(wave, spec, lines = [1215,1400,1550,1640,2800,1900], lmin=1000, lmax = 2000, deg = 3):
-
-	i_jump = (wave > lmin) * (wave < lmax)
-
-	i_lines = np.zeros(len(wave), dtype=bool)
-
-	for i in range(len(wave)):
-
-		comp = lines - wave[i]
-		comp = np.absolute(comp)
-
-		i_line = (comp < 100)
-
-		if np.sum(i_line) == 0:
-			i_lines[i] = True
-		else:
-			i_lines[i] = False		
-
-	i_select = i_jump * i_lines
-
-	continuum_points = wave[i_select]
-
-	#print continuum_points, i_select
-
-	coefficients = np.polyfit(continuum_points, spec[i_select], deg)
-
-	return coefficients
-
-def make_f(a, x):
-
- 	deg = len(a)
- 	y = 0
-
- 	for i in range(deg):
- 		y += a[i] * (x**(deg - i - 1))
-
- 	return y
-
-def find_line(w,f, wline = 6563, window_size=100, rw = False):
-
-	fabs_w = np.fabs(w - wline)
-
-	if rw:
-		w_bool = (fabs_w < window_size) * (w > wline)
-	else:
-		w_bool = (fabs_w < window_size) 
-
-	# create windows to look in
-	w_window = w
-	f_window = w_bool * f
-
-	# return arrays with length over specified 2*window_size
-	return w_window[f_window >0], f_window[f_window >0]
-
-
-def get_line_EW(s, angle_string = "A20P0.50", wline=6563, delta = 1.2):
-
-
-
-	line_w, line_f = find_line(s, angle_string, w=wline)
-
-	#print "Finding EW of line at %i A" % wline
-	
-	cont_t = line_f[1:10]
[…]

### 2015-12-23 generate/ew/ew_with_hist.py

@@ -1,308 +1,0 @@
-#from plot_norm import *
-import numpy as numpy
-from pylab import *
-import os, sys
-from cobra_sub import smooth
-import py_read_output as r 
-import py_plot_output as pl
-import py_plot_util as util 
-import matplotlib.pyplot as plt
-import matplotlib.gridspec as gridspec
-from plot_norm import *
-from constants import *
-from pretty import *
-
-set_pretty()
-
-def get_continuum(wave, spec, lines = [1215,1400,1550,1640,2800,1900], lmin=1000, lmax = 2000, deg = 3):
-
-	i_jump = (wave > lmin) * (wave < lmax)
-
-	i_lines = np.zeros(len(wave), dtype=bool)
-
-	for i in range(len(wave)):
-
-		comp = lines - wave[i]
-		comp = np.absolute(comp)
-
-		i_line = (comp < 100)
-
-		if np.sum(i_line) == 0:
-			i_lines[i] = True
-		else:
-			i_lines[i] = False		
-
-	i_select = i_jump * i_lines
-
-	continuum_points = wave[i_select]
-
-	#print continuum_points, i_select
-
-	coefficients = np.polyfit(continuum_points, spec[i_select], deg)
-
-	return coefficients
-
-def make_f(a, x):
-
- 	deg = len(a)
- 	y = 0
-
- 	for i in range(deg):
- 		y += a[i] * (x**(deg - i - 1))
-
- 	return y
-
-def find_line(w,f, wline = 6563, window_size=100, rw = False):
-
-	fabs_w = np.fabs(w - wline)
-
-	if rw:
-		w_bool = (fabs_w < window_size) * (w > wline)
-	else:
-		w_bool = (fabs_w < window_size) 
-
-	# create windows to look in
-	w_window = w
-	f_window = w_bool * f
-
-	# return arrays with length over specified 2*window_size
-	return w_window[f_window >0], f_window[f_window >0]
-
-
-def get_line_EW(s, angle_string = "A20P0.50", wline=6563, delta = 1.2):
-
-
-
-	line_w, line_f = find_line(s, angle_string, w=wline)
-
-	#print "Finding EW of line at %i A" % wline
-	
-	cont_t = line_f[1:10]
[…]

### 2015-12-23 generate/ew/ew_xkcd.py

@@ -1,277 +1,0 @@
-#from plot_norm import *
-import numpy as numpy
-from pylab import *
-import os, sys
-from cobra_sub import smooth
-import py_read_output as r 
-import py_plot_output as pl
-import py_plot_util as util 
-import matplotlib.pyplot as plt
-import matplotlib.gridspec as gridspec
-from plot_norm import *
-from constants import *
-from pretty import *
-
-#set_pretty()
-xkcd()
-
-def get_continuum(wave, spec, lines = [1215,1400,1550,1640,2800,1900], lmin=1000, lmax = 2000, deg = 3):
-
-	i_jump = (wave > lmin) * (wave < lmax)
-
-	i_lines = np.zeros(len(wave), dtype=bool)
-
-	for i in range(len(wave)):
-
-		comp = lines - wave[i]
-		comp = np.absolute(comp)
-
-		i_line = (comp < 100)
-
-		if np.sum(i_line) == 0:
-			i_lines[i] = True
-		else:
-			i_lines[i] = False		
-
-	i_select = i_jump * i_lines
-
-	continuum_points = wave[i_select]
-
-	#print continuum_points, i_select
-
-	coefficients = np.polyfit(continuum_points, spec[i_select], deg)
-
-	return coefficients
-
-def make_f(a, x):
-
- 	deg = len(a)
- 	y = 0
-
- 	for i in range(deg):
- 		y += a[i] * (x**(deg - i - 1))
-
- 	return y
-
-def find_line(w,f, wline = 6563, window_size=100, rw = False):
-
-	fabs_w = np.fabs(w - wline)
-
-	if rw:
-		w_bool = (fabs_w < window_size) * (w > wline)
-	else:
-		w_bool = (fabs_w < window_size) 
-
-	# create windows to look in
-	w_window = w
-	f_window = w_bool * f
-
-	# return arrays with length over specified 2*window_size
-	return w_window[f_window >0], f_window[f_window >0]
-
-
-def get_line_EW(s, angle_string = "A20P0.50", wline=6563, delta = 1.2):
-
-
-
-	line_w, line_f = find_line(s, angle_string, w=wline)
-
-	#print "Finding EW of line at %i A" % wline
-	
[…]

### 2015-12-23 generate/ew/line_lums.py

@@ -1,159 +1,0 @@
-#!/usr/bin/env python
-from pylab import *
-import py_read_output as r 
-import py_plot_output as pl
-import py_plot_util as util 
-import os, sys 
-from constants import *
-import numpy as np
-import pretty
-
-
-def get_continuum(wave, spec, lines = [1215,1400,1550,1640,2800,1900], lmin=1000, lmax = 2000, deg = 3):
-
-	i_jump = (wave > lmin) * (wave < lmax)
-
-	i_lines = np.zeros(len(wave), dtype=bool)
-
-	for i in range(len(wave)):
-
-		comp = lines - wave[i]
-		comp = np.absolute(comp)
-
-		i_line = (comp < 100)
-
-		if np.sum(i_line) == 0:
-			i_lines[i] = True
-		else:
-			i_lines[i] = False		
-
-	i_select = i_jump * i_lines
-
-	continuum_points = wave[i_select]
-
-	#print continuum_points, i_select
-
-	coefficients = np.polyfit(continuum_points, spec[i_select], deg)
-
-	return coefficients
-
-def make_f(a, x):
-
- 	deg = len(a)
- 	y = 0
-
- 	for i in range(deg):
- 		y += a[i] * (x**(deg - i - 1))
-
- 	return y
-
-def find_line(w,f, wline = 6563, window_size=100, rw = False):
-
-	fabs_w = np.fabs(w - wline)
-
-	if rw:
-		w_bool = (fabs_w < window_size) * (w > wline)
-	else:
-		w_bool = (fabs_w < window_size) 
-
-	# create windows to look in
-	w_window = w
-	f_window = w_bool * f
-
-	# return arrays with length over specified 2*window_size
-	return w_window[f_window >0], f_window[f_window >0]
-
-
-def normalize(w, f, lmin=1300, lmax=3000):
-
-	a = get_continuum(w, f, [1215,1550,1400,2800,6563], lmin=lmin, lmax=lmax, deg=2)
-
-	#fnorm = f/make_f(a, w)
-
-	#fnorm = f / util.get_flux_at_wavelength(w,f,1450)
-
-	return make_f(a, w)
-
-
-
[…]

### 2015-12-23 generate/specs/grid11/ew.py

@@ -1,247 +1,0 @@
-#from plot_norm import *
-import numpy as numpy
-from pylab import *
-import os, sys
-from cobra_sub import smooth
-import py_read_output as r 
-import py_plot_output as pl
-import py_plot_util as util 
-import matplotlib.pyplot as plt
-import matplotlib.gridspec as gridspec
-from plot_norm import *
-from constants import *
-from pretty import *
-
-set_pretty()
-
-def get_continuum(wave, spec, lines = [1215,1400,1550,1640,2800,1900], lmin=1000, lmax = 2000, deg = 3):
-
-	i_jump = (wave > lmin) * (wave < lmax)
-
-	i_lines = np.zeros(len(wave), dtype=bool)
-
-	for i in range(len(wave)):
-
-		comp = lines - wave[i]
-		comp = np.absolute(comp)
-
-		i_line = (comp < 100)
-
-		if np.sum(i_line) == 0:
-			i_lines[i] = True
-		else:
-			i_lines[i] = False		
-
-	i_select = i_jump * i_lines
-
-	continuum_points = wave[i_select]
-
-	#print continuum_points, i_select
-
-	coefficients = np.polyfit(continuum_points, spec[i_select], deg)
-
-	return coefficients
-
-def make_f(a, x):
-
- 	deg = len(a)
- 	y = 0
-
- 	for i in range(deg):
- 		y += a[i] * (x**(deg - i - 1))
-
- 	return y
-
-def find_line(w,f, wline = 6563, window_size=100, rw = False):
-
-	fabs_w = np.fabs(w - wline)
-
-	if rw:
-		w_bool = (fabs_w < window_size) * (w > wline)
-	else:
-		w_bool = (fabs_w < window_size) 
-
-	# create windows to look in
-	w_window = w
-	f_window = w_bool * f
-
-	# return arrays with length over specified 2*window_size
-	return w_window[f_window >0], f_window[f_window >0]
-
-
-def get_line_EW(s, angle_string = "A20P0.50", wline=6563, delta = 1.2):
-
-
-
-	line_w, line_f = find_line(s, angle_string, w=wline)
-
[…]

### 2015-12-23 generate/specs/grid11/ew2.py

@@ -1,8 +1,0 @@
-#!/usr/bin/env python
-from pylab import *
-import py_read_output as r 
-import py_plot_output as pl
-import py_plot_util as util 
-import os, sys 
-from constants import *
-import numpy as np

### 2015-12-23 generate/specs/grid11/winds/lin.py

@@ -1,131 +1,0 @@
-#!/usr/bin/env python
-from pylab import *
-import py_read_output as r 
-import py_plot_output as pl
-import py_plot_util as util 
-import os, sys 
-from constants import *
-import numpy as np
-from pretty import *
-
-set_pretty()
-
-from matplotlib.colors import LinearSegmentedColormap
-
-
-#cm_use = get_viridis()
-cm_use=get_optb()
-# f = open("nextgen_alpha1_long.complete", "r")
-
-# data_old = []
-# count = 0
-# for line in f:
-# 	data = line.split()
-
-# 	if len(data) != len(data_old):
-# 		print count, len(data), len(data_old)
-
-# 	count+=1
-# 	data_old = data
-
-# #sys.exit()
-
-RG = 8.85e14
-x1000 = np.logspace(14.0, np.log10(RG*1000-10000000),num=1000)
-
-
-y1000 = np.sqrt((RG*1000)**2 - x1000**2)
-
-x1000 = np.append(x1000,RG*1000)
-y1000 = np.append(y1000,1e-99)
-#n
-xuse= np.append(x1000,1e19)
-
-
-print x1000, y1000
-
-
-
-root = "nextgen_a05_79c"
-#util.run_py_wind(root,vers="79c",cmds=["1","1","1","M","2","2","-1","i","0","13","3","12","2","0","c","3","q"])
-d = r.read_pywind_summary(root)
-
-
-strings = ["ionO5", "ionO6", "ionN5", "ionC4", "ionAl3", "ionMg2", "ionHe1", "ionHe2", "ionHe3"]
-levs = [np.arange(-4,0,0.1), np.arange(-4,0,0.1),  np.arange(-4,0,0.1), np.arange(-4,0,0.1),np.arange(-4,0,0.1),np.arange(-4,0,0.1),np.arange(-4,0,0.1), np.arange(-4,0,0.1), np.arange(-4,0,0.1)]
[…]

### 2015-12-23 generate/specs/grid11/winds/link.py

@@ -1,128 +1,0 @@
-#!/usr/bin/env python
-from pylab import *
-import py_read_output as r 
-import py_plot_output as pl
-import py_plot_util as util 
-import os, sys 
-from constants import *
-import numpy as np
-from pretty import *
-
-set_pretty()
-
-from matplotlib.colors import LinearSegmentedColormap
-
-
-#cm_use = get_viridis()
-cm_use=get_optb()
-# f = open("nextgen_alpha1_long.complete", "r")
-
-# data_old = []
-# count = 0
-# for line in f:
-# 	data = line.split()
-
-# 	if len(data) != len(data_old):
-# 		print count, len(data), len(data_old)
-
-# 	count+=1
-# 	data_old = data
-
-# #sys.exit()
-
-RG = 8.85e14
-x1000 = np.logspace(14.0, np.log10(RG*1000-10000000),num=1000)
-
-
-y1000 = np.sqrt((RG*1000)**2 - x1000**2)
-
-x1000 = np.append(x1000,RG*1000)
-y1000 = np.append(y1000,1e-99)
-#n
-xuse= np.append(x1000,1e19)
-
-
-print x1000, y1000
-
-
-root = "nextgen_a05_79c_he"
-#util.run_py_wind(root,vers="79c",cmds=["1","1","1","M","2","2","-1","i","0","13","3","12","2","0","c","3","q"])
-d = r.read_pywind_summary(root)
-
-
-strings = ["ionO5", "ionO6", "ionN5", "ionC4", "ionAl3", "ionMg2", "ionHe1", "ionHe2", "ionHe3"]
-levs = [np.arange(-4,0,0.1), np.arange(-4,0,0.1),  np.arange(-4,0,0.1), np.arange(-4,0,0.1),np.arange(-4,0,0.1),np.arange(-4,0,0.1),np.arange(-4,0,0.1), np.arange(-4,0,0.1), np.arange(-4,0,0.1)]
[…]

### 2015-12-23 generate/specs/grid11/winds/make_windplot.py

@@ -1,202 +1,0 @@
-import matplotlib.pyplot as plt 
-from pylab import * 
-import numpy as np 
-import csv, sys, os, array, warnings, subprocess
-import pywind_sub as ps
-import matplotlib as mpl
-from matplotlib.mlab import bivariate_normal
-from matplotlib.colors import LogNorm
-from matplotlib.backends.backend_pdf import PdfPages
-import matplotlib as mpl
-import time
-import py_read_output as r
-import read_output as rd
-
-
-def run_py_wind (vers, fname, cmds=None, ilv=None):
-	'''
-	run version vers of py_wind on file fname.wind_save
-	'''
-
-	if cmds == None:
-		cmds = np.array(["1", "n","t", "r","v","1","2","3","-1", "I", "i", "1","1","1","2","0","i","0", "1","1","1","2","2","2","2","1","2","3","6", \
-			          "3","6","4","6","5","0","q"])
-
-	x = cmds
-	np.savetxt("_tempcmd.txt", x, fmt = "%s")
-
-
-	isys = os.system('py_wind'+vers+' '+fname+' < _tempcmd.txt > tempfile &')
-	time.sleep(3)
-
-	# remove temporary file
-	#os.system("rm -f _tempcmd.txt")
-	return isys
-
-
-
-
-def run_pydc (vers, fname, nplasma = 1):
-	'''
-	run version vers of py_wind on file fname.wind_save
-	'''
-
-	x = np.array(["1","M","4",str(nplasma),"1","-1","r","n","t","w", "q"])
-	np.savetxt("_tempcmd.txt", x, fmt = "%s")
-
-
-	isys = os.system('py_wind'+vers+' '+fname+' < _tempcmd.txt')
-	time.sleep(3)
-
-	# remove temporary file
-	#os.system("rm -f _tempcmd.txt")
-	return isys
-
-#ix,iz,x,z,lx,lz,xmax,zmax=ps.get_wind_geom(fname+'.ioncH1.dat')
-
-
-
-def read_pywind_logspace(filename):
-
-	'''
-	convert to logspace coordinates
-	'''
-
-	x,z,s = r.read_pywind(filename)
-
[…]

### 2015-12-23 generate/specs/grid11/winds/wind.py

@@ -1,114 +1,0 @@
-#!/usr/bin/env python
-from pylab import *
-import py_read_output as r 
-import py_plot_output as pl
-import py_plot_util as util 
-import os, sys 
-from constants import *
-import numpy as np
-from pretty import *
-
-set_pretty()
-
-from matplotlib.colors import LinearSegmentedColormap
-
-
-#cm_use = get_viridis()
-cm_use=get_optb()
-# f = open("nextgen_alpha1_long.complete", "r")
-
-# data_old = []
-# count = 0
-# for line in f:
-# 	data = line.split()
-
-# 	if len(data) != len(data_old):
-# 		print count, len(data), len(data_old)
-
-# 	count+=1
-# 	data_old = data
-
-# #sys.exit()
-
-RG = 8.85e14
-x1000 = np.logspace(14.0, np.log10(RG*1000-10000000),num=1000)
-
-
-y1000 = np.sqrt((RG*1000)**2 - x1000**2)
-
-x1000 = np.append(x1000,RG*1000)
-y1000 = np.append(y1000,1e-99)
-#n
-xuse= np.append(x1000,1e19)
-
-
-print x1000, y1000
-
-
-root = "asi_thmin70_rmin50_a0p75_f0p01_mdotw5"
-d = r.read_pywind_summary(root)
-
-
-strings = ["te", "ne", "ionC4", "ionAl3", "ionMg2", "lum_lines", "ly", "IP"]
-levs = [np.arange(3.4,4.8,0.1), np.arange(7,11,0.1), np.arange(-4,0,0.1),np.arange(-4,0,0.1),np.arange(-4,0,0.1),np.arange(40,45,0.2), np.arange(37,42.5,0.2), np.arange(-3,2,0.2)]
-labels = [r'$\rm{log (electron~temperature/K)}$', r'$\rm{log (electron~density/cm^{-3})}$',r'$\rm{log (C\textsc{iv}~ion~fraction)}$)', r'$\rm{log (Al\textsc{iii}~ion~fraction)}$)', r'$\rm{log (Mg\textsc{ii}~ion~fraction)}$)', r'$\rm{log (total~line~luminosity/erg~s^{-1})}$)',
-r'$\rm{log (Ly}~\rm{\alpha~line~luminosity)/erg~s^{-1}}$)', r'$\log U$']
-log = [1,1,1,1,1,1,1,1]
-
-
[…]

### 2015-12-23 generate/uvspec/0946.py

@@ -1,193 +1,0 @@
-#!/usr/bin/env python
-from pylab import *
-import py_read_output as r 
-import py_plot_output as pl
-import py_plot_util as util 
-import os, sys 
-from constants import *
-import numpy as np
-from pretty import *
-from plot_norm import make_f
-import pyfits as py
-
-
-set_pretty()
-NORM = True
-almost_black = '#262626'
-#nameb = "nextgen_alpha1_long"
-suffix = "_a05_pre"
-
-NORM_WAVELENGTH = 1300
-
-namea = "grid11/nextgen%s" % suffix
-namea = "/Users/jmatthews/Documents/runs/qso_he_test/with_estfix/nextgen_a05_pre_he"
-#nameb = "../specs/grid11/nextgen_uv"
-namec = "asi_thmin70_rmin50_a1_f0p01_mdotw5"
-#namec = "asi_thmin70_rmin50_a0p75_f0p01_mdotw5"
-
-name2 = "fiducial"
-smoda = r.read_spectrum(namea)
-#smodb = r.read_spectrum("../specs/"+nameb)
-#smodc = r.read_spectrum("../specs/"+namec)
-
-
-sdisk = r.read_spectrum("../specs/disk")
-sh13 = r.read_spectrum("../specs/h13")
-
-lines = [835,789,1034,977,1215, 1240, 1400, 1550, 1640]
-textx = [835,789,1034,977,1215, 1400, 1550, 1640]
-ycoords = [9.5,9.5,9.5,9.5,9.5,9.5,9.5,9.5,9.5,9.5,9.5,9.5,9.5]
-line_labels = [r"Ly $\alpha$", r"N~\textsc{v}", r"Si~\textsc{iv}", r"C~\textsc{iv}", r"He~\textsc{ii}", r"Al~\textsc{iii}", "C~\\textsc{iii}]", r"Mg~\textsc{ii}"]
-line_labels = [r"O~\textsc{iii}",r"O~\textsc{vi}",r"O~\textsc{vi}",r"N~\textsc{iii}",r"Ly $\alpha$~\&~N~\textsc{v}", r"Si~\textsc{iv}", r"C~\textsc{iv}", r"He~\textsc{ii}", r"Al~\textsc{iii}~\&~C~\textsc{iii}]", r"Mg~\textsc{ii}"]
-
-angles = [72]
-
-colors = get_colors()
-
-big_tick_labels(18)
-long_ticks()
-
[…]

### 2015-12-23 generate/uvspec/0946_two.py

@@ -1,189 +1,0 @@
-#!/usr/bin/env python
-from pylab import *
-import py_read_output as r 
-import py_plot_output as pl
-import py_plot_util as util 
-import os, sys 
-from constants import *
-import numpy as np
-from pretty import *
-from plot_norm import make_f
-import pyfits as py
-
-
-set_pretty()
-NORM = True
-almost_black = '#262626'
-#nameb = "nextgen_alpha1_long"
-suffix = "_a05_pre"
-
-NORM_WAVELENGTH = 1300
-
-namea = "grid11/nextgen%s" % suffix
-namea = "/Users/jmatthews/Documents/runs/qso_he_test/with_estfix/nextgen_a05_pre_he"
-#nameb = "../specs/grid11/nextgen_uv"
-namec = "asi_thmin70_rmin50_a1_f0p01_mdotw5"
-#namec = "asi_thmin70_rmin50_a0p75_f0p01_mdotw5"
-
-name2 = "fiducial"
-smoda = r.read_spectrum(namea)
-#smodb = r.read_spectrum("../specs/"+nameb)
-#smodc = r.read_spectrum("../specs/"+namec)
-
-
-sdisk = r.read_spectrum("../specs/disk")
-sh13 = r.read_spectrum("../specs/h13")
-
-lines = [835,789,1034,977,1215, 1240, 1400, 1550, 1640, 1860, 1909, 2800]
-textx = [835,789,1034,977,1215, 1400, 1550, 1640, 1860, 2800]
-ycoords = [9.5,9.5,9.5,9.5,9.5,9.5,9.5,9.5,9.5,9.5,9.5,9.5,9.5]
-line_labels = [r"Ly $\alpha$", r"N~\textsc{v}", r"Si~\textsc{iv}", r"C~\textsc{iv}", r"He~\textsc{ii}", r"Al~\textsc{iii}", "C~\\textsc{iii}]", r"Mg~\textsc{ii}"]
-line_labels = [r"O~\textsc{iii}",r"O~\textsc{vi}",r"O~\textsc{vi}",r"N~\textsc{iii}",r"Ly $\alpha$~\&~N~\textsc{v}", r"Si~\textsc{iv}", r"C~\textsc{iv}", r"He~\textsc{ii}", r"Al~\textsc{iii}~\&~C~\textsc{iii}]", r"Mg~\textsc{ii}"]
-
-angles = [20,72]
-
-colors = get_colors()
-
-big_tick_labels(18)
[…]

### 2015-12-23 generate/uvspec/0946_xkcd.py

@@ -1,191 +1,0 @@
-#!/usr/bin/env python
-from pylab import *
-import py_read_output as r 
-import py_plot_output as pl
-import py_plot_util as util 
-import os, sys 
-from constants import *
-import numpy as np
-from pretty import *
-from plot_norm import make_f
-import pyfits as py
-
-
-#set_pretty()
-xkcd()
-
-NORM = True
-almost_black = '#262626'
-#nameb = "nextgen_alpha1_long"
-suffix = "_a05_pre"
-
-NORM_WAVELENGTH = 1300
-
-namea = "grid11/nextgen%s" % suffix
-namea = "/Users/jmatthews/Documents/runs/qso_he_test/with_estfix/nextgen_a05_pre_he"
-#nameb = "../specs/grid11/nextgen_uv"
-namec = "asi_thmin70_rmin50_a1_f0p01_mdotw5"
-#namec = "asi_thmin70_rmin50_a0p75_f0p01_mdotw5"
-
-name2 = "fiducial"
-smoda = r.read_spectrum(namea)
-#smodb = r.read_spectrum("../specs/"+nameb)
-#smodc = r.read_spectrum("../specs/"+namec)
-
-
-sdisk = r.read_spectrum("../specs/disk")
-sh13 = r.read_spectrum("../specs/h13")
-
-lines = [835,789,1034,977,1215, 1240, 1400, 1550, 1640, 1860, 1909, 2800]
-textx = [835,789,1034,977,1215, 1400, 1550, 1640, 1860, 2800]
-ycoords = [9.5,9.5,9.5,9.5,9.5,9.5,9.5,9.5,9.5,9.5,9.5,9.5,9.5]
-line_labels = [r"Ly $\alpha$", r"N~\textsc{v}", r"Si~\textsc{iv}", r"C~\textsc{iv}", r"He~\textsc{ii}", r"Al~\textsc{iii}", "C~\\textsc{iii}]", r"Mg~\textsc{ii}"]
-line_labels = [r"O~\textsc{iii}",r"O~\textsc{vi}",r"O~\textsc{vi}",r"N~\textsc{iii}",r"Ly $\alpha$~\&~N~\textsc{v}", r"Si~\textsc{iv}", r"C~\textsc{iv}", r"He~\textsc{ii}", r"Al~\textsc{iii}~\&~C~\textsc{iii}]", r"Mg~\textsc{ii}"]
-
-angles = [72]
-
-colors = get_colors()
-
[…]

### 2015-12-23 generate/uvspec/h13_uvspec.py

@@ -1,129 +1,0 @@
-#!/usr/bin/env python
-from pylab import *
-import py_read_output as r 
-import py_plot_output as pl
-import py_plot_util as util 
-import os, sys 
-from constants import *
-import numpy as np
-from pretty import *
-from plot_norm import make_f
-
-set_pretty()
-NORM = True
-almost_black = '#262626'
-#nameb = "nextgen_alpha1_long"
-namea = "nextgen_uv"
-#namea = "checkvol_a6"
-namea = "nextgen_a5"
-nameb = "asi_thmin70_rmin50_a0p75_f0p01_mdotw5"
-namec = "asi_thmin70_rmin50_a1_f0p01_mdotw5"
-#namec = "asi_thmin70_rmin50_a0p75_f0p01_mdotw5"
-
-name2 = "fiducial"
-smoda = r.read_spectrum("../specs/"+namea)
-#smodb = r.read_spectrum("../specs/"+nameb)
-#smodc = r.read_spectrum("../specs/"+namec)
-
-
-sdisk = r.read_spectrum("../specs/disk")
-sh13 = r.read_spectrum("../specs/h13")
-
-
-angles = [20,60,72,75,78]
-
-colors = get_colors()
-
-figure(figsize=(10,10))
-
-#run_agnspec
-
-for i in range(len(angles)):
-
-	angle = angles[i]
-	subplot(5,1,i+1)
-	angstr = "A%iP0.50" % angle
-	wwa = smoda["Lambda"]
-	#wwb = smodb["Lambda"]
-	#wwc = smodc["Lambda"]
-
-	NORM_GPC = (1e9*1e9)/(1e4)/1e14
-
-
-	Fdisk = sdisk[angstr] / NORM_GPC
-	Fh13 = sh13[angstr] / NORM_GPC
-
-	Fmoda = smoda[angstr] / NORM_GPC
-	#Fmodb = smodb[angstr]
-	#Fmodc = smodc[angstr]
-
-
-
-	plot(wwa,util.smooth(Fmoda,window_len=5), label=r"Model", c='k', linewidth=2)
-	#plot(wwb,util.smooth(Fmodb), label=r"Model B, $\alpha = 0.75$", c=colors[1], linewidth=2)
-	#plot(wwc,util.smooth(Fmodc), label=r"Model C, $\alpha = 1$", c=colors[2], linewidth=2)
[…]

### 2015-12-23 generate/uvspec/new_uvspec_fig.py

@@ -1,174 +1,0 @@
-#!/usr/bin/env python
-from pylab import *
-import py_read_output as r 
-import py_plot_output as pl
-import py_plot_util as util 
-import os, sys 
-from constants import *
-import numpy as np
-import pyfits as py
-import sdss
-from pretty import *
-
-
-set_pretty()
-big_tick_labels(18)
-rcParams["axes.linewidth"]=1.5
-NORM = True
-almost_black = '#262626'
-#nameb = "nextgen_alpha1_long"
-suffix = "_a075_pre_he"
-
-PYTHON = os.environ["PYTHON"]
-
-
-namea = "grid11/nextgen%s" % suffix
-namea = "../specs/webgrid/run5_thmin70_rmin50_a0p5_rv1e19_f0p01.spec"
-#nameb = "../specs/grid11/nextgen_uv"
-namec = "asi_thmin70_rmin50_a1_f0p01_mdotw5"
-#namec = "asi_thmin70_rmin50_a0p75_f0p01_mdotw5"
-
-name2 = "fiducial"
-smoda = r.read_spectrum(namea)
-#smodb = r.read_spectrum("../specs/"+nameb)
-#smodc = r.read_spectrum("../specs/"+namec)
-
-
-sdisk = r.read_spectrum("../../generate/specs/disk")
-sh13 = r.read_spectrum("../../generate/specs/h13")
-
-lines = [1215, 1240, 1400, 1550, 1640, 1860, 1909, 2800]
-textx = [1215, 1400, 1550, 1650, 1860, 2800]
-ycoords = [2, 50, 50, 50, 50, 30, 10]
-line_labels = [r"Ly $\alpha$", r"N~\textsc{v}", r"Si~\textsc{iv}", r"C~\textsc{iv}", r"He~\textsc{ii}", r"Al~\textsc{iii}", "C~\\textsc{iii}]", r"Mg~\textsc{ii}"]
-line_labels = [r"Ly $\alpha$~\&~N~\textsc{v}", r"Si~\textsc{iv}", r"C~\textsc{iv}", r"He~\textsc{ii}", r"Al~\textsc{iii}~\&~C~\textsc{iii}]", r"Mg~\textsc{ii}"]
-
-angles = [20,60,73,76]
-
-colors = get_colors()
-
-figure(figsize=(10,12))
-
-NORM_WAVELENGTH = 1300
-
-
[…]

### 2015-12-23 generate/uvspec/sdss.py

@@ -1,820 +1,0 @@
-#!/Library/Frameworks/Python.framework/Versions/2.7/Resources/Python.app/Contents/MacOS/Python
-
-
-import pyfits as py
-import matplotlib.pyplot as plt
-import pylab
-import os, sys
-import numpy as np
-
-
-plt.rcParams["text.usetex"] = "True"
-
-POSITION_DELTA = 0.01
-VARIANCE_DELTA = 1
-
-
-def read_sdss(name):
-    """    
-    Read SDSS spectra fits. Plotting capability.
-
-    :INPUTS:
-       name: Filename of fits spectra
-       
-    :OUTPUTS:
-       wave: wavelength array - Angstroms
-
-       flux: flux array  - Flux lambda erg/s/cm^2/Angstrom
-    """
-    flux=py.getdata(name,0)
-    wdel=py.getval(name,'CD1_1',0)
-    w0=py.getval(name,'CRVAL1',0)
-    wave= 10.0**(w0+wdel*np.arange(len(flux[0])))
-    
-    return(wave,flux[0]*1e-17)
-
-
-
-
-######################################################################
-#
-#		PLOTTING FUNCTIONS
-#
-#
-######################################################################
-
-
-def plot_sdss(name, lmin, lmax, save=True , norm = True):
-
-
-
-	fig = plt.figure()
-
-	ax = fig.add_subplot(111)
-
-	wave, flux = read_sdss(name)
-
-	if norm:
-		flux = normalise(wave, flux, lmin)
-
-	ax.plot(wave, flux)
-
-	plt.xlim(lmin, lmax)
-
-	savename = "%s_%i_%i.png" %( name[:-3], lmin, lmax)
-
-	ax.set_xlabel("$\lambda (\AA)$")
-	ax.set_ylabel("Flux")
-
-	if save: 	
-		plt.savefig( savename )
-
-	#os.system("open -a preview %s" % savename)
-
-def plotall(lmin, lmax):
-
-	fig = plt.figure()
-
-	ax = fig.add_subplot(111)
-
-	f = open("lsfile", "r")
-
-	for line in f:
-		filename = line.split()[0]
-
-		wave, flux = read_sdss(filename)
-
-		flux = normalise(wave, flux, lmin)
-
-		ax.plot(wave, flux)
-		plt.xlim(lmin, lmax)
-
[…]

### 2015-12-23 generate/uvspec/specs/all.py

@@ -1,98 +1,0 @@
-#!/usr/bin/env python
-from pylab import *
-import py_read_output as r 
-import py_plot_output as pl
-import py_plot_util as util 
-import os, sys 
-from constants import *
-import numpy as np
-from pretty import *
-from plot_norm import make_f
-
-set_pretty()
-NORM = True
-
-path = "."
-
-spec_files = [f for f in os.listdir(path) if (f.endswith('.spec') and f!='lines.spec')]
-
-
-for iname in range(len(spec_files)):
-
-
-
-	almost_black = '#262626'
-	name1 = "nextgen_alpha1_long"
-	name2 = spec_files[iname][:-5]
-	specname = name2
-	smod = r.read_spectrum(name1)
-	sdisk = r.read_spectrum("disk_only")
-	sh13 = r.read_spectrum(name2)
-
-	print name2
-
-	angles = [20,40, 75,80]
-
-	figure(figsize=(12,8))
-
-	#run_agnspec
-
-	for i in range(len(angles)):
-
-		angle = angles[i]
-		subplot(4,1,i+1)
-		angstr = "A%iP0.50" % angle
-		ww = smod["Lambda"]
-
-
-		Fdisk = sdisk[angstr]
-		Fmod = smod[angstr]
-		Fh13 = sh13[angstr]
-
-
-
-		plot(ww,util.smooth(Fmod), label="Full model", c="k", linewidth=2)
-		plot(sh13["Lambda"],util.smooth(Fh13), label="for comp", c=almost_black, linewidth=1)
-		plot(sdisk["Lambda"],util.smooth(Fdisk, window_len=100), label="Disc continuum", c="k", linestyle="--")
-
-
-
-		# if NORM:
-		# 	f2000 = util.get_flux_at_wavelength(ww,Fmod,2000)
-		# plot(ww,util.smooth(Fmod/f2000), label="Original Model")
-
-		# read the composites and plot them
-		# if angles[i]<=70:
-
-		# 	w,f = np.loadtxt("/Users/jmatthews/Documents/Python/examples/sdssedrqsobal/sdssedrqsobal.nonbal.spec", unpack=True,usecols=(0,1))
-		# 	f2000 = util.get_flux_at_wavelength(w,f,2000)
-		# 	plot(w,f/f2000, label="non-BAL composite")
-
-		# else:
[…]

### 2015-12-23 generate/uvspec/uv_mast.py

@@ -1,176 +1,0 @@
-#!/usr/bin/env python
-from pylab import *
-import py_read_output as r 
-import py_plot_output as pl
-import py_plot_util as util 
-import os, sys 
-from constants import *
-import numpy as np
-from pretty import *
-from plot_norm import make_f
-import pyfits as py
-
-
-set_pretty()
-NORM = True
-almost_black = '#262626'
-#nameb = "nextgen_alpha1_long"
-suffix = "_a05_pre"
-
-NORM_WAVELENGTH = 1300
-
-namea = "grid11/nextgen%s" % suffix
-#nameb = "../specs/grid11/nextgen_uv"
-namec = "asi_thmin70_rmin50_a1_f0p01_mdotw5"
-#namec = "asi_thmin70_rmin50_a0p75_f0p01_mdotw5"
-
-name2 = "fiducial"
-smoda = r.read_spectrum("../specs/"+namea)
-#smodb = r.read_spectrum("../specs/"+nameb)
-#smodc = r.read_spectrum("../specs/"+namec)
-
-
-sdisk = r.read_spectrum("../specs/disk")
-sh13 = r.read_spectrum("../specs/h13")
-
-lines = [1215, 1240, 1400, 1550, 1640, 1860, 1909, 2800]
-textx = [1215, 1400, 1550, 1640, 1860, 2800]
-ycoords = [2, 50, 50, 50, 50, 50, 50]
-line_labels = [r"Ly $\alpha$", r"N~\textsc{v}", r"Si~\textsc{iv}", r"C~\textsc{iv}", r"He~\textsc{ii}", r"Al~\textsc{iii}", "C~\\textsc{iii}]", r"Mg~\textsc{ii}"]
-line_labels = [r"Ly $\alpha$~\&~N~\textsc{v}", r"Si~\textsc{iv}", r"C~\textsc{iv}", r"He~\textsc{ii}", r"Al~\textsc{iii}~\&~C~\textsc{iii}]", r"Mg~\textsc{ii}"]
-
-angles = [20,60,72,75,78]
-
-colors = get_colors()
-
-def get_hst(f2000):
-
-	files1 = [f for f in os.listdir('../mast/0946/') if "x1d" in f]
-	z = 1.223
-	for i in range(4,len(files1)):
-
-		d = py.getdata('../mast/0946/'+files1[i])
-		w = d["WAVELENGTH"][0] / (1.0 + z)
-		f = d["FLUX"][0]
[…]

### 2015-12-23 generate/uvspec/uvspec.py

@@ -1,151 +1,0 @@
-#!/usr/bin/env python
-from pylab import *
-import py_read_output as r 
-import py_plot_output as pl
-import py_plot_util as util 
-import os, sys 
-from constants import *
-import numpy as np
-from pretty import *
-from plot_norm import make_f
-
-set_pretty()
-NORM = True
-almost_black = '#262626'
-#nameb = "nextgen_alpha1_long"
-suffix = "_a075_pre_he"
-
-
-namea = "grid11/nextgen%s" % suffix
-namea = "/Users/jmatthews/Documents/runs/qso_he_test/with_estfix/nextgen_a05_pre_he"
-#nameb = "../specs/grid11/nextgen_uv"
-namec = "asi_thmin70_rmin50_a1_f0p01_mdotw5"
-#namec = "asi_thmin70_rmin50_a0p75_f0p01_mdotw5"
-
-name2 = "fiducial"
-smoda = r.read_spectrum(namea)
-#smodb = r.read_spectrum("../specs/"+nameb)
-#smodc = r.read_spectrum("../specs/"+namec)
-
-
-sdisk = r.read_spectrum("../specs/disk")
-sh13 = r.read_spectrum("../specs/h13")
-
-lines = [1215, 1240, 1400, 1550, 1640, 1860, 1909, 2800]
-textx = [1215, 1400, 1550, 1640, 1860, 2800]
-ycoords = [2, 50, 50, 50, 50, 50, 50]
-line_labels = [r"Ly $\alpha$", r"N~\textsc{v}", r"Si~\textsc{iv}", r"C~\textsc{iv}", r"He~\textsc{ii}", r"Al~\textsc{iii}", "C~\\textsc{iii}]", r"Mg~\textsc{ii}"]
-line_labels = [r"Ly $\alpha$~\&~N~\textsc{v}", r"Si~\textsc{iv}", r"C~\textsc{iv}", r"He~\textsc{ii}", r"Al~\textsc{iii}~\&~C~\textsc{iii}]", r"Mg~\textsc{ii}"]
-
-angles = [20,60,72,75,78]
-
-colors = get_colors()
-
-figure(figsize=(10,12))
-
-#run_agnspec
-
-for i in range(len(angles)):
-
-	angle = angles[i]
-	subplot(5,1,i+1)
-	angstr = "A%iP0.50" % angle
-	wwa = smoda["Lambda"]
-	#wwb = smodb["Lambda"]
-	#wwc = smodc["Lambda"]
-
[…]

### 2015-12-23 generate/uvspec/uvspec_xkcd.py

@@ -1,157 +1,0 @@
-#!/usr/bin/env python
-from pylab import *
-import py_read_output as r 
-import py_plot_output as pl
-import py_plot_util as util 
-import os, sys 
-from constants import *
-import numpy as np
-from pretty import *
-from plot_norm import make_f
-
-#set_pretty()
-xkcd()
-NORM = True
-almost_black = '#262626'
-#nameb = "nextgen_alpha1_long"
-suffix = "_a075_pre_he"
-
-
-namea = "grid11/nextgen%s" % suffix
-namea = "/Users/jmatthews/Documents/runs/qso_he_test/with_estfix/nextgen_a05_pre_he"
-#nameb = "../specs/grid11/nextgen_uv"
-namec = "asi_thmin70_rmin50_a1_f0p01_mdotw5"
-#namec = "asi_thmin70_rmin50_a0p75_f0p01_mdotw5"
-
-name2 = "fiducial"
-smoda = r.read_spectrum(namea)
-#smodb = r.read_spectrum("../specs/"+nameb)
-#smodc = r.read_spectrum("../specs/"+namec)
-
-
-sdisk = r.read_spectrum("../specs/disk")
-sh13 = r.read_spectrum("../specs/h13")
-
-lines = [1215, 1240, 1400, 1550, 1640, 1860, 1909, 2800]
-textx = [1215, 1400, 1550, 1640, 1860, 2800]
-ycoords = [2, 50, 50, 50, 50, 50, 50]
-line_labels = [r"Ly $\alpha$", r"N~\textsc{v}", r"Si~\textsc{iv}", r"C~\textsc{iv}", r"He~\textsc{ii}", r"Al~\textsc{iii}", "C~\\textsc{iii}]", r"Mg~\textsc{ii}"]
-line_labels = [r"Ly $\alpha$~\&~N~\textsc{v}", r"Si~\textsc{iv}", r"C~\textsc{iv}", r"He~\textsc{ii}", r"Al~\textsc{iii}~\&~C~\textsc{iii}]", r"Mg~\textsc{ii}"]
-
-angles = [20,60,72,75,78]
-
-colors = get_colors()
-
-figure(figsize=(10,8))
-
-#run_agnspec
-
-#for i in range(len(angles)):
-for i in range(1):
-	angle = angles[i]
-	subplot(1,1,i+1)
-	angstr = "A%iP0.50" % angle
-	wwa = smoda["Lambda"]
-	#wwb = smodb["Lambda"]
-	#wwc = smodc["Lambda"]
-
[…]

### 2015-12-23 generate/uvspec/wide.py

@@ -1,109 +1,0 @@
-#!/usr/bin/env python
-from pylab import *
-import py_read_output as r 
-import py_plot_output as pl
-import py_plot_util as util 
-import os, sys 
-from constants import *
-import numpy as np
-from pretty import *
-from plot_norm import make_f
-
-set_pretty()
-NORM = True
-almost_black = '#262626'
-#nameb = "nextgen_alpha1_long"
-namea = "nextgen_a5"
-nameb = "nextgen_opt"
-# namec = "asi_thmin70_rmin50_a1_f0p01_mdotw5"
-# namec = "asi_thmin70_rmin50_a0p75_f0p01_mdotw5"
-
-name2 = "fiducial"
-smoda = r.read_spectrum("../specs/"+namea)
-smodb = r.read_spectrum("../specs/"+nameb)
-# smodc = r.read_spectrum("specs/"+namec)
-
-
-sdisk = r.read_spectrum("../specs/disk")
-sh13 = r.read_spectrum("../specs/h13")
-
-
-angles = [20,60,72,75,80]
-
-colors = get_colors()
-
-figure(figsize=(8,12))
-
-
-
-#run_agnspec
-
-for i in range(len(angles)):
-
-	angle = angles[i]
-	subplot(5,1,i+1)
-	angstr = "A%iP0.50" % angle
-	wwa = smoda["Lambda"]
-	wwb = smodb["Lambda"]
-	select = (wwa <= 2900)
-	select2 = (wwb > 2900)
-	# wwc = smodc["Lambda"]
-
-
-	#Fdisk = sdisk[angstr]
-	#Fh13 = sh13[angstr]
-
-	Fmoda = smoda[angstr]
-	Fmodb = smodb[angstr]
-	#Fmodc = smodc[angstr]
-
-
-
-	plot(wwa[select],util.smooth(Fmoda[select]), label=r"Model A, $\alpha = 0.6$", c='k', linewidth=2)
-	plot(wwb[select2],util.smooth(Fmodb[select2]), c='k', linewidth=2)
-	#plot(wwc,util.smooth(Fmodc), label=r"Model C, $\alpha = 1$", c=colors[2], linewidth=2)
-	#plot(sh13["Lambda"],util.smooth(Fh13), label="H13", c=almost_black, linewidth=1)
-	#plot(sdisk["Lambda"],util.smooth(Fdisk, window_len=100), label="Disc continuum", c="k", linestyle="--")
-
-
[…]

### 2015-12-23 generate/uvspec/wide_com.py

@@ -1,126 +1,0 @@
-#!/usr/bin/env python
-from pylab import *
-import py_read_output as r 
-import py_plot_output as pl
-import py_plot_util as util 
-import os, sys 
-from constants import *
-import numpy as np
-from pretty import *
-from plot_norm import make_f
-
-set_pretty()
-NORM = True
-almost_black = '#262626'
-#nameb = "nextgen_alpha1_long"
-namea = "nextgen_uv"
-namea = "checkvol_a6"
-#namea = "nextgen_a5"
-nameb = "asi_thmin70_rmin50_a0p75_f0p01_mdotw5"
-namec = "asi_thmin70_rmin50_a1_f0p01_mdotw5"
-#namec = "asi_thmin70_rmin50_a0p75_f0p01_mdotw5"
-
-name2 = "fiducial"
-smoda = r.read_spectrum("../specs/"+namea)
-#smodb = r.read_spectrum("../specs/"+nameb)
-#smodc = r.read_spectrum("../specs/"+namec)
-
-
-sdisk = r.read_spectrum("../specs/disk")
-sh13 = r.read_spectrum("../specs/h13")
-
-
-angles = [20,60,72,75,78]
-
-colors = get_colors()
-
-figure(figsize=(10,10))
-
-#run_agnspec
-
-for i in range(len(angles)):
-
-	angle = angles[i]
-	subplot(5,1,i+1)
-	angstr = "A%iP0.50" % angle
-	wwa = smoda["Lambda"]
-	#wwb = smodb["Lambda"]
-	#wwc = smodc["Lambda"]
-
-	NORM_GPC = (1e9*1e9)/(1e4)/1e14
-
-
-	Fdisk = sdisk[angstr] / NORM_GPC
-	Fh13 = sh13[angstr] / NORM_GPC
-
-	Fmoda = smoda[angstr] / NORM_GPC
-	#Fmodb = smodb[angstr]
-	#Fmodc = smodc[angstr]
-
-
-
-	plot(wwa,util.smooth(Fmoda,window_len=5), label=r"Model", c='k', linewidth=2)
-	#plot(wwb,util.smooth(Fmodb), label=r"Model B, $\alpha = 0.75$", c=colors[1], linewidth=2)
-	#plot(wwc,util.smooth(Fmodc), label=r"Model C, $\alpha = 1$", c=colors[2], linewidth=2)
[…]

### 2015-12-23 generate/wind_onepanel/SV_cartoon.py

@@ -1,95 +1,0 @@
-'''
-SV_cartoon.py 
-
-This script creates the cartoon figure for 
-the 2014 CV paper. The data were scraped from Dexter.
-'''
-
-import matplotlib.mlab as mlab
-import numpy as np
-import matplotlib.pyplot as plt
-import matplotlib as mpl
-
-
-mpl.rcParams['pdf.use14corefonts'] = True
-mpl.rc('font',**{'family':'sans-serif','sans-serif':['Helvetica']})
-## for Palatino and other serif fonts use:
-#rc('font',**{'family':'serif','serif':['Palatino']})
-mpl.rc('text', usetex=True)
-
-thetamin=72.0
-thetamax=80.0
-diskmax=25.0
-xmin=10.0
-xmax=18.0
-rstar=2.0
-
-xwindmax=40.0
-zwindmax=(xwindmax-xmin)*np.tan(np.radians(90.0-thetamin))
-
-
-posx=np.arange(xmin,xwindmax,(xmax-xmin)/10.0)
-ymin1=[]
-ymax1=[]
-
-x=np.array([xmin,xmax,xwindmax])
-y1=np.array([0.0,(xmax-xmin)*np.tan(np.radians(90.0-thetamin)),(xwindmax-xmin)*np.tan(np.radians(90.0-thetamin))])
-y2=np.array([0.0,0.0,(xwindmax-xmax)*np.tan(np.radians(90.0-thetamax))])
-
-lsize=14
-tsize=16 
-
-fig=plt.figure()
-ax=fig.add_subplot(1,1,1)
-ax.plot(x,y1,x,y2,color='black')
-ax.plot(-1.0*x,y1,-1.0*x,y2,color='black')
-ax.plot(-1.0*x,-1.0*y1,-1.0*x,-1.0*y2,color='black')
-ax.plot(x,-1.0*y1,x,-1.0*y2,color='black')
-ax.set_xlim([-1.0*xwindmax,xwindmax])
-plt.fill_between(x,y1, y2, facecolor='0.9', interpolate=True)
-plt.fill_between(-1.0*x,y1, y2, facecolor='0.9', interpolate=True)
-plt.fill_between(x,-1.0*y1, -1.0*y2, facecolor='0.9', interpolate=True)
-plt.fill_between(-1.0*x,-1.0*y1, -1.0*y2, facecolor='0.9', interpolate=True)
[…]

### 2015-12-23 generate/wind_onepanel/one_wind.py

@@ -1,174 +1,0 @@
-#!/usr/bin/env python
-from pylab import *
-import py_read_output as r 
-import py_plot_output as pl
-import py_plot_util as util 
-import os, sys 
-from constants import *
-import numpy as np
-from pretty import *
-
-set_pretty()
-
-from matplotlib.colors import LinearSegmentedColormap
-
-
-cm_use = get_viridis()
-# f = open("nextgen_alpha1_long.complete", "r")
-
-# data_old = []
-# count = 0
-# for line in f:
-# 	data = line.split()
-
-# 	if len(data) != len(data_old):
-# 		print count, len(data), len(data_old)
-
-# 	count+=1
-# 	data_old = data
-
-# #sys.exit()
-
-RG = 8.85e14
-x1000 = np.logspace(14.0, np.log10(RG*1000-10000000),num=1000)
-
-
-y1000 = np.sqrt((RG*1000)**2 - x1000**2)
-
-x1000 = np.append(x1000,RG*1000)
-y1000 = np.append(y1000,1e-99)
-#n
-xuse= np.append(x1000,1e19)
-
-
-print x1000, y1000
-
-
-d = r.read_pywind_summary("nextgen_a05")
-
-
-strings = ["te"]
-levs = [np.arange(-3,2,0.2)]
-levs = [np.arange(3,5,0.1)]
-labels = [r'$\log U$']
-log = [1]
-
-
-fig = figure(figsize=[1,1])
-
-x,z,var = util.wind_to_masked(d, strings[0])
-
-if log[0]:
-	var = np.log10(var)
-
-
-
-# select = (var.mask == False)*(z<1e19)
-
-# z = z[select]
-# x = x[select]
-# # e = e[(e.mask == False)]
-
-# import matplotlib.tri as tri
-# T = tri.Triangulation(x.flatten(), z.flatten())
-
-
-# var = var[select]
-# var = var.flatten()
-
-
-#tricontourf(T,np.log10(var), mask = var.mask, levels = levs[0], extend="both", cmap=cm_use)
-
-contourf(x,z,var, extend='both', levels=levs[0], cmap=cm_use)
-#grid()
-#loglog()
-pretty_axes()
-xlim(-8.85e14,1e18)
[…]

### 2015-12-23 generate/wind_plot/lin.py

@@ -1,125 +1,0 @@
-#!/usr/bin/env python
-from pylab import *
-import py_read_output as r 
-import py_plot_output as pl
-import py_plot_util as util 
-import os, sys 
-from constants import *
-import numpy as np
-from pretty import *
-
-set_pretty()
-
-from matplotlib.colors import LinearSegmentedColormap
-
-
-#cm_use = get_viridis()
-cm_use=get_optb()
-# f = open("nextgen_alpha1_long.complete", "r")
-
-# data_old = []
-# count = 0
-# for line in f:
-# 	data = line.split()
-
-# 	if len(data) != len(data_old):
-# 		print count, len(data), len(data_old)
-
-# 	count+=1
-# 	data_old = data
-
-# #sys.exit()
-
-RG = 8.85e14
-x1000 = np.logspace(14.0, np.log10(RG*1000-10000000),num=1000)
-
-
-y1000 = np.sqrt((RG*1000)**2 - x1000**2)
-
-x1000 = np.append(x1000,RG*1000)
-y1000 = np.append(y1000,1e-99)
-#n
-xuse= np.append(x1000,1e19)
-
-
-print x1000, y1000
-
-
-root = "nextgen_a05_pre_he"
-d = r.read_pywind_summary(root)
-
-
-strings = ["te", "ne", "IP", "ionC4", "ionAl3", "ionMg2", "lum_lines", "ly", "lineC4"]
-levs = [np.arange(3.4,4.8,0.1), np.arange(7,11,0.1),  np.arange(-3,2,0.2), np.arange(-2,0.1,0.1),np.arange(-4,0,0.1),np.arange(-4,0,0.1),np.arange(40,44,0.1), np.arange(37,42.5,0.2), np.arange(37,42.5,0.2)]
-labels = [r'$\rm{log (electron~temperature/K)}$', r'$\rm{log (electron~density/cm^{-3})}$',r'$\log U$',r'$\rm{log (C\textsc{iv}~ion~fraction)}$', r'$\rm{log (Al\textsc{iii}~ion~fraction)}$', r'$\rm{log (Mg\textsc{ii}~ion~fraction)}$', r'$\rm{log (total~line~luminosity/erg~s^{-1})}$',
[…]

### 2015-12-23 generate/wind_plot/link.py

@@ -1,126 +1,0 @@
-#!/usr/bin/env python
-from pylab import *
-import py_read_output as r 
-import py_plot_output as pl
-import py_plot_util as util 
-import os, sys 
-from constants import *
-import numpy as np
-from pretty import *
-
-set_pretty()
-
-from matplotlib.colors import LinearSegmentedColormap
-
-
-#cm_use = get_viridis()
-cm_use=get_optb()
-# f = open("nextgen_alpha1_long.complete", "r")
-
-# data_old = []
-# count = 0
-# for line in f:
-# 	data = line.split()
-
-# 	if len(data) != len(data_old):
-# 		print count, len(data), len(data_old)
-
-# 	count+=1
-# 	data_old = data
-
-# #sys.exit()
-
-RG = 8.85e14
-x1000 = np.logspace(14.0, np.log10(RG*1000-10000000),num=1000)
-
-
-y1000 = np.sqrt((RG*1000)**2 - x1000**2)
-
-x1000 = np.append(x1000,RG*1000)
-y1000 = np.append(y1000,1e-99)
-#n
-xuse= np.append(x1000,1e19)
-
-
-print x1000, y1000
-
-
-root = "nextgen_a05_pre_he"
-d = r.read_pywind_summary(root)
-
-
-
-strings = ["te", "ne", "IP", "ionC4", "ionAl3", "ionMg2", "lum_lines", "ly", "lineC4"]
-levs = [np.arange(3.4,4.8,0.1), np.arange(7,11,0.1),  np.arange(-3,2,0.2), np.arange(-4,0,0.1),np.arange(-4,0,0.1),np.arange(-4,0,0.1),np.arange(40,44,0.1), np.arange(37,42.5,0.2), np.arange(37,42.5,0.2)]
-labels = [r'$\rm{log (electron~temperature/K)}$', r'$\rm{log (electron~density/cm^{-3})}$',r'$\log U$',r'$\rm{log (C\textsc{iv}~ion~fraction)}$', r'$\rm{log (Al\textsc{iii}~ion~fraction)}$', r'$\rm{log (Mg\textsc{ii}~ion~fraction)}$', r'$\rm{log (total~line~luminosity/erg~s^{-1})}$',
[…]

### 2015-12-23 generate/wind_plot/link_8.py

@@ -1,136 +1,0 @@
-#!/usr/bin/env python
-from pylab import *
-import py_read_output as r 
-import py_plot_output as pl
-import py_plot_util as util 
-import os, sys 
-from constants import *
-import numpy as np
-from pretty import *
-
-set_pretty()
-big_tick_labels(18)
-
-from matplotlib.colors import LinearSegmentedColormap
-
-
-#cm_use = get_viridis()
-cm_use=get_optb()
-# f = open("nextgen_alpha1_long.complete", "r")
-
-# data_old = []
-# count = 0
-# for line in f:
-# 	data = line.split()
-
-# 	if len(data) != len(data_old):
-# 		print count, len(data), len(data_old)
-
-# 	count+=1
-# 	data_old = data
-
-# #sys.exit()
-
-RG = 8.85e14
-x1000 = np.logspace(14.0, np.log10(RG*1000-10000000),num=1000)
-
-
-y1000 = np.sqrt((RG*1000)**2 - x1000**2)
-
-x1000 = np.append(x1000,RG*1000)
-y1000 = np.append(y1000,1e-99)
-#n
-xuse= np.append(x1000,1e19)
-
-
-print x1000, y1000
-
-
-root = "run64_thmin70_rmin50_a0p5_rv1e19_f0p01"
-d = r.read_pywind_summary(root)
-
-
-
-strings = ["te", "ne", "IP", "ionC4", "ionAl3", "ionMg2", "ly", "lineC4"]
-levs = [np.arange(3.4,4.8,0.1), np.arange(7,11,0.1),  np.arange(-3,2,0.2), np.arange(-4,0,0.1),np.arange(-4,0,0.1),np.arange(-4,0,0.1), np.arange(37,42.5,0.2), np.arange(37,42.5,0.2)]
-labels = [r'$\rm{log (electron~temperature/K)}$', r'$\rm{log (electron~density/cm^{-3})}$',r'$\log U$',r'$\rm{log (C\textsc{iv}~ion~fraction)}$', r'$\rm{log (Al\textsc{iii}~ion~fraction)}$', r'$\rm{log (Mg\textsc{ii}~ion~fraction)}$',
-r'$\rm{log (Ly}~\rm{\alpha~line~luminosity)/erg~s^{-1}}$)', r'$\rm{log (C\textsc{iv}~line~luminosity/erg~s^{-1})}$']
[…]

### 2015-12-23 generate/xray/alpha_ox.py

@@ -1,271 +1,0 @@
-#!/usr/bin/env python
-'''
-alpha_ox.py makes plots of alpha_ox and L_2kev plotted
-against L_2500 
-'''
-from pylab import *
-import py_read_output as r 
-import numpy as np 
-import os, sys
-import py_plot_util as util
-from constants import *
-from astropy.io import ascii
-from pretty import *
-#import disk
-
-# some functions for getting mean monochromatic fluxes in a bin
-def get_flux_inwbin(lambda_array, flux_array, w, binsize=1, log=False):
-	wstart = w - (0.5*binsize)
-	wstop = w + (0.5*binsize)
-	select = (lambda_array > wstart) * (lambda_array < wstop)
-	return np.mean(flux_array[select])
-
-def get_flux_infbin(f_array, flux_array, f, binsize=0.1, log=False):
-
-	binsize *= f
-
-	fstart = f - (0.5 * binsize)
-	fstop = f + (0.5 * binsize)
-	select = (f_array > fstart) * (f_array < fstop)
-	return np.mean(flux_array[select])
-
-def get_flux_at_f(f_array, flux_array, f):
-
-	i = np.abs(f_array - f).argmin()
-
-	return flux_array[i]
-
-
-
-r.setpars()
-rcParams["legend.frameon"] = "False"
-rcParams["legend.numpoints"] = 1
-colors = ["r", "g"]
-
-# fnames to use
-fnames = [("fiducial_xray", "fiducial_uv"), ("../specs/nextgen_a5_xray", "../specs/nextgen_a5")]
-fnames = [("fiducial_xray", "fiducial_uv"), ("../specs/nextgen_3_30", "../specs/nextgen_uv")]
-fnames = [("../specs/fiducial_xray_fine", "../specs/h13.spec"), ("../specs/checkvol_a6_xray", "../specs/checkvol_a6")]
-fnames = [("../specs/fiducial_xray_fine", "../specs/h13.spec"), ("../specs/grid10/nextgen_a05_3_30", "../specs/grid10/nextgen_a05")]
-
-# 9 before
-label=fnames[1][0][16:]
-
-
-# load the Steffen et al. data
[…]

### 2015-12-23 generate/xray/lx.py

@@ -1,255 +1,0 @@
-#!/usr/bin/env python
-'''
-alpha_ox.py makes plots of alpha_ox and L_2kev plotted
-against L_2500 
-'''
-from pylab import *
-import py_read_output as r 
-import numpy as np 
-import os, sys
-import py_plot_util as util
-from constants import *
-from astropy.io import ascii
-from pretty import *
-#import disk
-
-# some functions for getting mean monochromatic fluxes in a bin
-def get_flux_inwbin(lambda_array, flux_array, w, binsize=1, log=False):
-	wstart = w - (0.5*binsize)
-	wstop = w + (0.5*binsize)
-	select = (lambda_array > wstart) * (lambda_array < wstop)
-	return np.mean(flux_array[select])
-
-def get_flux_infbin(f_array, flux_array, f, binsize=0.1, log=False):
-
-	binsize *= f
-
-	fstart = f - (0.5 * binsize)
-	fstop = f + (0.5 * binsize)
-	select = (f_array > fstart) * (f_array < fstop)
-	return np.mean(flux_array[select])
-
-def get_flux_at_f(f_array, flux_array, f):
-
-	i = np.abs(f_array - f).argmin()
-
-	return flux_array[i]
-
-
-
-r.setpars()
-rcParams["legend.frameon"] = "False"
-rcParams["legend.numpoints"] = 1
-colors = ["r", "g"]
-colors_xx = get_colors()
-
-# fnames to use
-# fnames = [("fiducial_xray", "fiducial_uv"), ("../specs/nextgen_a5_xray", "../specs/nextgen_a5")]
-# fnames = [("fiducial_xray", "fiducial_uv"), ("../specs/nextgen_3_30", "../specs/nextgen_uv")]
-# fnames = [("../specs/fiducial_xray_fine", "../specs/h13.spec"), ("../specs/checkvol_a6_xray", "../specs/checkvol_a6")]
-
-aaa = "06"
-vers = "pre"
-suffix1 = "_a%s_%s" % (aaa,vers)
-suffix2 = "_a%s_%s_xray" % (aaa,vers)
[…]

### 2015-12-23 generate/xray_sed/compton.py

@@ -1,107 +1,0 @@
-#!/usr/bin/env python
-from pylab import *
-import py_read_output as r 
-import py_plot_output as pl
-import py_plot_util as util 
-import os, sys 
-from constants import *
-import numpy as np
-from pretty import *
-
-
-figure(figsize=(12,7))
-
-#subplot(2,1,1)
-
-#fnames = ["1e45", "1e45_uv"]
-#fnames = ["nextgen_alpha1_long_wide","1e45", "1e45_uv"]
-#fnames = ['nextgen_p3_3',"nextgen_3_30", 'nextgen_30_300', 'nextgen_uv', 'nextgen_opt']
-#fnames = ['checkvol_a6',"checkvol_a6_xray","h13","fiducial_xray_fine","fiducial_uv","fiducial_xray"]
-#fnames = ["h13","fiducial_xray_fine","fiducial_uv","fiducial_xray"]
-fnames = ["grid11/nextgen_a05_pre_xray"]
-NN = len(fnames) - 1
-NN = len(fnames) - 1
-
-alphas = [0.5,0.5,0.75,0.75]
-labels=["1e45, f=0.01", "H13"]
-big_tick_labels(16)
-
-colors = get_colors()
-
-ccc = [colors[0],colors[0], "k", "k"]
-modcols = [colors[0], "k", "k"]
-
-angles = [85]
-
-for iang in range(len(angles)):
-
-	set_pretty()
-
-	all_nu = np.array([])
-	all_f = np.array([])
-	concatenate
-
-	#bounds = [(1e19,1e18),(1e18,1e17),(1e17,1e16),(1e16,1e15),(1e15,1e14)]
-	bounds = [(1e19,1e14),(1e19,1e14),(1e19,1e14),(1e19,1e14),(1e19,1e14),(1e19,1e14),(1e19,1e14)]
-
-	for i in range(len(fnames)):
-
-		s = r.read_spectrum("../specs/"+fnames[NN-i])
-
-		ev = 1.60217657e-19
-
-		angle = angles[iang]
-
-		nu = s["Freq."]
-		w = s["Lambda"]
-
-		flambda = s["A%iP0.50" % angle]
-
-
-		fl_to_fnu = s["Lambda"] / s["Freq."]
-
-		norm = 4.0 * PI * (100.0 * PARSEC) * (100.0 * PARSEC)
-
[…]

### 2015-12-23 generate/xray_sed/find_lines.py

@@ -1,157 +1,0 @@
-#!/usr/bin/env python
-from pylab import *
-import py_read_output as r 
-import py_plot_output as pl
-import py_plot_util as util 
-import os, sys 
-from constants import *
-import numpy as np
-from pretty import *
-
-
-def get_linelist(filenames, ionreturn=False):
-
-	'''
-	function to read in linelist from a bunch of filenames
-	'''
-
-	lines = np.array([])
-	z = np.array([])
-
-	for i in range(len(filenames)):
-
-		x = np.loadtxt(filenames[i], comments="#", usecols=(2,3), unpack=True)
-
-		lines = np.concatenate((lines, x[1]))
-
-		z = np.concatenate((z, x[0]))
-
-	if ionreturn:
-		return lines, z
-	else:
-		return lines
-
-
-# some global plotting params
-logx = True
-# only select lines above this oscillator threshold
-oscillator_threshold = 0.01
-xlims = (0.4,3.5)
-elim = (0.4,3)
-ionlim = (15,27)	# ion limits
-
-# angle we are going to plot at
-angle = 75
-
-
-
-# read in Python synthetic spectrum
-fname = "grid11/nextgen_a05_pre_xray"
-s = r.read_spectrum("../specs/"+fname)
-
-nu = s["Freq."]
-
-# converting from fnu to flambda
-fl_to_fnu = s["Lambda"] / s["Freq."]
-
-# converting from flux to normalisation
-norm = 4.0 * PI * (100.0 * PARSEC) * (100.0 * PARSEC)
-
-#convert to lnu - flambda x fl_to_fnu x norm
-lnu = s["A%iP0.50" % angle] * fl_to_fnu * norm
-
-
-
-
-# now get the atomic data
-z, ion, wave, f = np.loadtxt("data/atomic78/lines_linked_ver_2.py", comments="#", usecols=(1,2,3,4), unpack=True)
-
-energies = C / (wave * ANGSTROM) * HEV * 1e-3 # energy in keV
-
-# print the strong lines
-for i in range(len(f)):
-	if f[i] > oscillator_threshold and energies[i] < elim[1] and energies[i] > elim[0]:
-		print z[i], ion[i], f[i], energies[i]
-
-# select only strong lines
[…]

### 2015-12-23 generate/xray_sed/prepare_xray_data.py

@@ -1,35 +1,0 @@
-#!/usr/bin/env python
-from pylab import *
-import py_read_output as r 
-import py_plot_output as pl
-import py_plot_util as util 
-import os, sys 
-from constants import *
-import numpy as np
-fname = "grid11/nextgen_a05_pre_xray"
-#fname = "fiducial_xray_fine"
-angle = 75
-
-s = r.read_spectrum("../specs/"+fname)
-
-norm = (100.0 * PARSEC) * (100.0 * PARSEC) / (1e10 * PARSEC) / (1e10 * PARSEC)
-
-fl_to_fnu = s["Lambda"] / s["Freq."]
-
-flambda = s["A%iP0.50" % angle]
-
-fnu = flambda * fl_to_fnu * norm
-
-data_to_write = np.ndarray((2, len(fnu)))
-
-data_to_write[0] = s["Freq."]
-data_to_write[1] = fnu
-
-data_to_write = np.transpose(data_to_write )
-
-header_string = "Frequency(Hz)  |   F_nu (erg/s/cm^2/Hz)\nPower law has spectral index 0.9"
-np.savetxt('qsomod_a05_xray_75deg.spec', data_to_write, header=header_string)
-#np.savetxt('h13mod_xray_75deg.spec', data_to_write, header=header_string)
-
-plot(s["Freq."], fnu)
-savefig("testspec.png")

### 2015-12-23 generate/xray_sed/sed.py

@@ -1,128 +1,0 @@
-#!/usr/bin/env python
-from pylab import *
-import py_read_output as r 
-import py_plot_output as pl
-import py_plot_util as util 
-import os, sys 
-from constants import *
-import numpy as np
-from pretty import *
-
-
-figure(figsize=(12,6))
-
-#subplot(2,1,1)
-
-#fnames = ["1e45", "1e45_uv"]
-#fnames = ["nextgen_alpha1_long_wide","1e45", "1e45_uv"]
-#fnames = ['nextgen_p3_3',"nextgen_3_30", 'nextgen_30_300', 'nextgen_uv', 'nextgen_opt']
-#fnames = ['checkvol_a6',"checkvol_a6_xray","h13","fiducial_xray_fine","fiducial_uv","fiducial_xray"]
-#fnames = ["h13","fiducial_xray_fine","fiducial_uv","fiducial_xray"]
-fnames = ["../specs/webgrid/run5_thmin70_rmin50_a0p5_rv1e19_f0p01.spec"]
-NN = len(fnames) - 1
-NN = len(fnames) - 1
-
-alphas = [0.5,0.5,0.75,0.75]
-labels=["1e45, f=0.01", "H13"]
-big_tick_labels(18)
-
-lines = np.log10(C/np.array([6563, 4861, 1215, 1240, 1400, 1550, 1909, 2800])/ANGSTROM)
-textx = np.log10(C/np.array([6563, 4861, 1215, 1400, 1550, 1909, 2800])/ANGSTROM)
-#ycoords = [2, 50, 50, 50, 50, 10, 10]
-line_labels = [r"H$\alpha$", r"H$\beta$", r"Ly $\alpha$~\&~N~\textsc{v}", r"Si~\textsc{iv}", r"C~\textsc{iv}", r"C~\textsc{iii}]", r"Mg~\textsc{ii}"]
-
-
-colors = get_colors()
-
-ccc = [colors[0],colors[0], "k", "k"]
-modcols = [colors[0], "k", "k"]
-
-angles = [20, 89]
-geolab = ["`Quasar-like'", "`Below Wind'"]
-
-lims = ((30.5,31.7), (27.5,30.1))
-
-nu_norm = C/2000.0/ANGSTROM
-
-for iang in range(len(angles)):
-
-	#subplot(2,1,iang+1)
-
-	set_pretty()
-
-	all_nu = np.array([])
[…]

### 2015-12-23 generate/xray_sed/test.py

@@ -1,25 +1,0 @@
-#!/usr/bin/env python
-from pylab import *
-import py_read_output as r 
-import py_plot_output as pl
-import py_plot_util as util 
-import os, sys 
-from constants import *
-import numpy as np
-
-
-sed = np.loadtxt("pg1001_sed_rest.dat",unpack=True)
-yerr = [sed[2],sed[3]]
-
-nu = sed[0]
-nulnu = sed[1]
-
-yerr[0] = -10.0 ** (nulnu + yerr[0]) + (10.0**nulnu)
-yerr[1] = 10.0 ** (nulnu + yerr[1]) - (10.0**nulnu)
-
-errorbar(10.0**sed[0], 10.0**sed[1], yerr=yerr, fmt=".")
-
-print yerr
-
-loglog()
-savefig("test.png")

### 2015-12-23 generate/xray_sed/xray_all.py

@@ -1,157 +1,0 @@
-#!/usr/bin/env python
-from pylab import *
-import py_read_output as r 
-import py_plot_output as pl
-import py_plot_util as util 
-import os, sys 
-from constants import *
-import numpy as np
-from pretty import *
-
-
-figure(figsize=(12,7))
-
-#subplot(2,1,1)
-
-#fnames = ["1e45", "1e45_uv"]
-#fnames = ["nextgen_alpha1_long_wide","1e45", "1e45_uv"]
-#fnames = ['nextgen_p3_3',"nextgen_3_30", 'nextgen_30_300', 'nextgen_uv', 'nextgen_opt']
-#fnames = ['checkvol_a6',"checkvol_a6_xray","h13","fiducial_xray_fine","fiducial_uv","fiducial_xray"]
-#fnames = ["h13","fiducial_xray_fine","fiducial_uv","fiducial_xray"]
-fnames = ["grid11/nextgen_a05_pre_xray"]
-NN = len(fnames) - 1
-NN = len(fnames) - 1
-
-alphas = [0.5,0.5,0.75,0.75]
-labels=["1e45, f=0.01", "H13"]
-big_tick_labels(16)
-
-colors = get_colors()
-
-ccc = [colors[0],colors[0], "k", "k"]
-modcols = [colors[0], "k", "k"]
-
-angles = [85]
-
-for iang in range(len(angles)):
-
-	set_pretty()
-
-	all_nu = np.array([])
-	all_f = np.array([])
-	concatenate
-
-	#bounds = [(1e19,1e18),(1e18,1e17),(1e17,1e16),(1e16,1e15),(1e15,1e14)]
-	bounds = [(1e19,1e14),(1e19,1e14),(1e19,1e14),(1e19,1e14),(1e19,1e14),(1e19,1e14),(1e19,1e14)]
-
-	for i in range(len(fnames)):
-
-		s = r.read_spectrum("../specs/"+fnames[NN-i])
-
-		ev = 1.60217657e-19
-
-		angle = angles[iang]
-
-		nu = s["Freq."]
-		w = s["Lambda"]
-
-		flambda = s["A%iP0.50" % angle]
-
-
-		fl_to_fnu = s["Lambda"] / s["Freq."]
-
-		norm = 4.0 * PI * (100.0 * PARSEC) * (100.0 * PARSEC)
-
[…]

### 2015-12-23 generate/xray_sed/xray_all2.py

@@ -1,138 +1,0 @@
-#!/usr/bin/env python
-from pylab import *
-import py_read_output as r 
-import py_plot_output as pl
-import py_plot_util as util 
-import os, sys 
-from constants import *
-import numpy as np
-from pretty import *
-
-
-figure(figsize=(7,10))
-
-#fnames = ["1e45", "1e45_uv"]
-#fnames = ["nextgen_alpha1_long_wide","1e45", "1e45_uv"]
-#fnames = ['nextgen_p3_3',"nextgen_3_30", 'nextgen_30_300', 'nextgen_uv', 'nextgen_opt']
-#fnames = ['checkvol_a6',"checkvol_a6_xray","h13","fiducial_xray_fine","fiducial_uv","fiducial_xray"]
-#fnames=["nextgen_a05_pre_xray", "nextgen_a06_pre_xray", "nextgen_a075_pre_xray", "nextgen_a05_pre_xray_he","nextgen_a06_pre_xray_he"]
-fnames = ["nextgen_a05_pre_xray_he", "nextgen_a05_pre_xray"]
-
-#fnames = ["h13","fiducial_xray_fine","fiducial_uv","fiducial_xray"]
-NN = len(fnames) - 1
-NN = len(fnames) - 1
-
-alphas = [0.5,0.5,0.75,0.75]
-labels=["1e45, f=0.01", "H13"]
-big_tick_labels(16)
-
-colors = get_colors()
-
-#ccc = [colors[0],colors[0], "k", "k"]
-#
-
-
-angles = [60,72,78,75]
-
-for iang in range(len(angles)):
-
-	subplot(4,1,iang+1)
-
-	set_pretty()
-
-	all_nu = np.array([])
-	all_f = np.array([])
-	
-	text(2e17,1e44,"$i=%2i^\circ$" % angles[iang], fontsize=20)
-
-	#bounds = [(1e19,1e18),(1e18,1e17),(1e17,1e16),(1e16,1e15),(1e15,1e14)]
-	#bounds = [(1e19,1e14),(1e19,1e14),(1e19,1e14),(1e19,1e14),(1e19,1e14),(1e19,1e14),(1e19,1e14)]
-
-	for i in range(len(fnames)):
-
-		lname = fnames[i][8:11]
-		if "he" in fnames[i]:
-			lname ="He and H"
-		else:
-			lname = "H"
-
-
[…]

### 2015-12-23 generate/xray_sed/xray_lines.py

@@ -1,58 +1,0 @@
-#!/usr/bin/env python
-from pylab import *
-import py_read_output as r 
-import py_plot_output as pl
-import py_plot_util as util 
-import os, sys 
-from constants import *
-import numpy as np
-from pretty import *
-
-def get_linelist(filenames, ionreturn=False):
-
-	lines = np.array([])
-	z = np.array([])
-
-	for i in range(len(filenames)):
-
-		x = np.loadtxt(filenames[i], comments="#", usecols=(2,3), unpack=True)
-
-		lines = np.concatenate((lines, x[1]))
-
-		z = np.concatenate((z, x[0]))
-
-	if ionreturn:
-		return lines, z
-	else:
-		return lines
-
-z, ion, wave, f = np.loadtxt("data/atomic78/lines_linked_ver_2.py", comments="#", usecols=(1,2,3,4), unpack=True)
-
-set_pretty()
-#select = (z == )
-E = 1e-3 * HEV * C / (wave * ANGSTROM)
-
-#zz = np.array([6,7,8,10,26])
-
-zz, ions = np.loadtxt("elems", unpack=True, usecols=(1,2), dtype='string')
-#ions = ["C","N","O","Ne","Fe"] 
-zz = zz.astype(int)
-
-ions = ions[(zz > 3)]
-zz = zz[(zz > 3)]
-
-
-colors = np.concatenate((get_colors(),get_colors(),get_colors()))
-
-for j in range(len(zz)):
-	select = (z == zz[j])
-	scatter(E[select], ion[select], s=200*f[select], label=ions[j],c=colors[j])
-
-float_legend()
-xlim(0.3,7)
-ylim(0,27)
-semilogx()
-xlabel("Line Energy (eV)")
-ylabel("Ion")
-savefig("ions.png",dpi=200)
-clf()

### 2015-12-23 mnras.py

@@ -1,44 +1,0 @@
-
-
-import sys
-import numpy as np
-filename = sys.argv[1]
-outfilename = sys.argv[2]
-
-
-texfile =  open(filename, "r")
-outfile = open(outfilename, "w")
-
-
-outfile.write("\documentclass[useAMS,usenatbib]{mn2e_x}\n")
-
-fig_env = False
-
-for line in texfile:
-	if "begin{abstract}" in line:
-		outfile.write("\maketitle\n")
-		outfile.write(line)
-
-	elif "\\author{" in line:
-		outfile.write("\\author[Matthews et al.]{\n")
-
-	elif "indent" in line and "rule" in line:
-		if "%" not in line:
-			outfile.write("\\noindent\\rule{8cm}{0.4pt}\n")
-
-	elif "fullpage" in line and "begin{figure}" in line:
-		if fig_env == False:
-			outfile.write("\\begin{figure*}\n")
-			fig_env = True 
-
-	elif fig_env and "end{figure}" in line:
-		outfile.write("\end{figure*}")
-		outfile.write("\n")
-		fig_env = False 
-
-	elif "documentclass" not in line and "maketitle" not in line:
-		outfile.write(line)
-
-
-
-outfile.close()

### 2016-01-21 paper.tex
modding some wording for the reviewer

@@
 which are reprocessed by `macro-atoms' with associated transition probabilities.
-We use the Sobolev approximation \citep[e.g.][]{sobolev1957,sobolev1960,rybickihummer1978}
-to compute the location of line interactions.
+{\bf We use the Sobolev approximation \citep[e.g.][]{sobolev1957,sobolev1960,rybickihummer1978}
+to compute the location and optical depth of line interactions}.
 In our case, for reasons of computational efficiency, we adopt the  hybrid macro-atom scheme 
@@
 prepares for a more accurate treatment of other physical processes in future.
-% in principle, allows 
-% the direct addition of extra physical processes that would previously have necessitated 
-% approximate treatments.
 
@@
 we model the SED in a grid cell using the technique described by H13. In this scheme,
-the mean intensity, $J_{\nu}$ in a series of $n$ bands is modeled as either a power law or exponential
+the mean intensity, $J_{\nu}$, in a series of $n$ bands is modeled as either a power law or exponential
 in frequency $\nu$, with the fit parameters deduced from band-limited radiation field estimators.
@@
 calculating the thermal balance of the plasma (see H13).
-Adiabatic cooling is included, but is insignificant 
-in most of the outflow.
+{\bf 
+Adiabatic cooling in the cell is calculated using the estimator
+\begin{equation}
+C_{ad} = f_V n_e k_B T_e V (\Delta \cdot v),
+\end{equation}
+where $V$ is the cell volume, $T_e$ is the electron temperature,
+$n_e$ is the electron density and $\Delta \cdot v$ is the divergence of the 
+velocity field at the centre of the cell.
+For self-consistency, $k$-packets then have a finite 
+destruction probability of 
+\begin{equation}
+P_{k,destruct} = \frac{C_{ad}}{C_{tot}},
+\end{equation}
+where $C_{tot}$ is the sum over all cooling rates in the cell.
+We find that adiabatic cooling is insignificant in much of
+the outflow.
 
@@
 \cite{elvis2000} to explain the phenomenonology
-of quasars and BALQSOs.
+of quasars and BALQSOs. {\bf However, we do not include the initial
+vertical component present in the Elvis (2000) model, which was
+invoked as a qualitative explanation for narrow absorption lines}.
 
@@
 with correspondingly different ionization and emission characteristics.
+}
 
@@
 with $BI > 0$ at $\sim20\%$ of viewing angles (e.g. Knigge et al. 2010);
-\item Line emission emerging at low inclinations, with $EW\sim40$\AA in \civline\ \citep[e.g. ][]{shen2011};
+\item Line emission emerging at low inclinations, with $EW\sim40$\AA\ in \civline\ \citep[e.g. ][]{shen2011};
 \item H recombination lines with $EW\sim50$\AA\ in \la\ \citep[e.g. ][]{shen2011};
@@
 from highly ionized (yellow) to low ionization (purple) material.
-%[FIGURE NEEDS IMPROVING]
 }
@@
 compared to the non-BAL SDSS quasar composite. The spectra are normalised to the flux at 
-$2000$\AA, then an offset of 2 is applied per spectrum for clarity -- the dotted lines show the zero point of $F_\nu / F_{2000\AA}$ in each case.
+$2000$\AA, then an offset of 2 is applied per spectrum for clarity -- the dotted lines show the zero point of $F_\nu / F_{2000}$ in each case.
 }
@@
 due to Balmer continuum and Balmer and Fe~\textsc{ii} line emission.
-This extreme $89^\circ$ viewing angle cannot represent a typical quasar within a unified model,
-but does show that a model such as this can naturally reproduce quasar emission lines
-if the emissivity of the wind is increased {\em with respect to the disc continuum}.
+
+{\bf This extreme $89^\circ$ viewing angle cannot represent a typical quasar within a unified model, as
+extreme inclinations should be extremely underrepresented in quasar samples due to the
+compton-thick absorber or `Torus' expected at high inclinations ().}
+However, this spectrum does show that a model such as this can 
+naturally reproduce quasar emission lines if the emissivity of the wind is 
+increased {\em with respect to the disc continuum}.
 In addition, it neatly demonstrates how a stratified outflow can naturally
@@
 line and continuum emission is a crucial question for theoretical models.
-% Furthermore, this is conclusion is independent of the assumed 
-% BLR geometry and size.
 \end{enumerate}
@@
 CK also acknowledges a Leverhulme fellowship.
+{\bf We would like to thank the anonymous referee for an insightful
+and constructive report.}
 We would like to thank Omer Blaes, Ivan Hubeny and Shane Davis for their
@@
 and made use of the IRIDIS High Performance Computing Facility at the
-University of Southampton. Figures were produced using the {\tt matplotlib} plotting library \citep{matplotlib}. This work made use of the Sloan Digital Sky Survey.
+University of Southampton. Figures were produced using the {\tt matplotlib} 
+plotting library \citep{matplotlib}. This work made use of the Sloan Digital Sky Survey.
 Funding for the Sloan Digital Sky Survey has been provided by

### 2016-01-26 paper.tex
mod2, sent around

@@
 \begin{abstract} 
-Various unification schemes interpret the complex phenomenology of quasars and luminous active galactic nuclei (AGN) in terms of a simple picture involving a central black hole, an accretion disc and an associated outflow.
-Here, we continue our tests of this paradigm by comparing quasar spectra to synthetic spectra of biconical disc wind models, produced with our state-of-the-art Monte Carlo radiative transfer code.
-Previously, we have shown that we could produce synthetic spectra resembling those of observed broad absorption line (BAL) quasars, but only if the X-ray luminosity was limited to
-10$^{43}$~erg~s$^{-1}$.
-Here, we show that clumping the outflow can maintain the ionization state necessary for BAL features in the rest-frame UV at more realistic X-ray luminosities.
-Our fiducial model shows good agreement with X-ray properties of AGN and the dense, X-ray heated wind produces strong line emission in, e.g., \la\ and \civline at low inclinations.
+Various unification schemes interpret the complex phenomenology of quasars and 
+luminous active galactic nuclei (AGN) in terms of a simple picture involving a 
+central black hole, an accretion disc and an associated outflow. Here, we continue
+our tests of this paradigm by comparing quasar spectra to synthetic spectra of 
+biconical disc wind models, produced with our state-of-the-art Monte Carlo radiative 
+transfer code. Previously, we have shown that we could produce synthetic spectra 
+resembling those of observed broad absorption line (BAL) quasars, but only if the 
+X-ray luminosity was limited to 10$^{43}$~erg~s$^{-1}$. 
+{\bf Here, we introduce a simple treatment of clumping, and find that a volume filling factor of $\sim0.01$ 
+moderates the ionization state sufficently for BAL features to form in the 
+rest-frame UV at more realistic X-ray luminosities.}
+Our fiducial model shows good agreement with X-ray properties of AGN and the dense, 
+X-ray heated wind produces strong line emission in, e.g., \la\ and \civline\ at low inclinations. 
 At high inclinations, the synthetic spectra possess prominent LoBAL features. 
-Despite these successes, we cannot reproduce all the emission lines seen in quasar spectra with the correct equivalent-width ratios, and and we find an angular dependence of emission-line equivalent width despite the remarkable similarities in the observed emission line properties of BAL and non-BAL quasars.
-Overall, our work suggests that a biconical wind can reproduce much of the qualitative behaviour expected from a unified model, but we cannot yet provide quantitative matches with quasar properties at all viewing angles.
-Whether disc winds can successfully unify quasars is therefore still an open question.
+Despite these successes, we cannot reproduce all the emission lines seen in quasar 
+spectra with the correct equivalent-width ratios, and we find an angular dependence of 
+emission-line equivalent width despite the remarkable similarities in the observed emission 
+line properties of BAL and non-BAL quasars. Overall, our work suggests that a biconical wind 
+can reproduce much of the qualitative behaviour expected from a unified model, but we cannot 
+yet provide quantitative matches with quasar properties at all viewing angles. Whether disc 
+winds can successfully unify quasars is therefore still an open question.
 \end{abstract}
@@
 The efficiency of line-driving is crucially dependent on the ionization state 
-of the outflowing plasma, meaning that it is difficult to prevent 
-the wind becoming over-ionized and `failing' in the presence of strong X-rays. 
+of the outflow, and in AGN, unlike O stars, 
+the presence of strong X-ray emission can overionize the wind, 
+causing it to `fail'.
 \cite{MCGV95} proposed a potential solution: 
@@
 An additional or alternative solution is that the wind is clumped 
-\citep[e.g.][]{hamann2013}
+{\bf \citep[e.g.][]{junk1983,weymann1985,hamann2013}}
 possibly on multiple scale lengths. Local density enhancements could lower the 
-ionization parameter of the plasma while still maintaining the same mass-loss 
-rate and column density.
+ionization parameter of the plasma 
+without requiring excessively large total column densities 
+and mass-loss rates.
 
@@
 \citep{krolik1981, emmering1992, dekool1995, cassidyraine1996}.
-Clumping can be caused by magnetic confinement \citep{dekool1995},
-or the instabilities inherent to line-driven winds 
-\citep{lucysolomon1970,macgregor1979,carlberg1980,owockirybicki1984,owockirybicki1985}.
-Additionally, clumping is required to explain the electron scattering wings of emission lines formed
-in line-driven hot star winds \citep{hillier1991eswingsmodel}. Complex substructures 
-are also produced in simulations of line-driven 
-outflows in AGN, although on very different scales to line-driven instabilities 
+{\bf 
+\cite{krolik1981} showed that BLR clouds would be short-lived, suggesting 
+that a confining mechanism is required, such as
+magnetic confinement \citep[e.g.][]{dekool1995}. Alternatively,
+the `line deshadowing instability' (LDI) inherent in line-driven winds
+\citep{lucysolomon1970,macgregor1979,carlberg1980,owockirybicki1984}
+may be responsible for smaller-scale clumping, as is observed in O-star winds
+\citep[][and references therein]{fullerton2011}.
+Indeed, simple models of clumping have successfully explained the electron scattering 
+wings of emission lines formed in these line-driven flows 
+\citep{hillier1991eswingsmodel}.}
+Complex substructures are also produced in simulations of line-driven 
+outflows in AGN, although on very different scales to LDIs 
 \citep{PSK2000,PK04,progakurosawa2010,proga2014}.  
@@
 predicted way to lower the ionization state of a plasma, possibly in tandem
-with a shielding scenario.
+with a shielding scenario. However, it is equally important to note that there 
+is no consensus view of the size or location of the clumps in the outflow.
 
@@
 calculating the thermal balance of the plasma (see H13).
-{\bf 
-Adiabatic cooling in the cell is calculated using the estimator
+{\bf Adiabatic cooling in the cell is calculated using the estimator
 \begin{equation}
-C_{ad} = f_V n_e k_B T_e V (\Delta \cdot v),
+C_{A} = f_V k_B T_e V (\nabla \cdot v) \left(n_e + \sum\limits_{i=1}^{ions} N_i\right),
 \end{equation}
 where $V$ is the cell volume, $T_e$ is the electron temperature,
-$n_e$ is the electron density and $\Delta \cdot v$ is the divergence of the 
-velocity field at the centre of the cell.
-For self-consistency, $k$-packets then have a finite 
+$n_e$ is the electron density, $N_j$ is the number density of ion $j$
+and $\nabla \cdot v$ is the divergence of the 
+velocity field at the centre of the cell. The sum is over all ions 
+included in the simulation.
+For consistency, $k$-packets then have a finite 
 destruction probability of 
 \begin{equation}
-P_{k,destruct} = \frac{C_{ad}}{C_{tot}},
+P_{k,A} = \frac{C_{A}}{C_{tot}},
 \end{equation}
 where $C_{tot}$ is the sum over all cooling rates in the cell.
-We find that adiabatic cooling is insignificant in much of
-the outflow.
+}
 
@@
 with correspondingly different ionization and emission characteristics.
-}
 
@@
 A clumpy outflow offers a possible solution to the so-called `over-ionization problem' in 
-quasar and AGN outflows \citep{hamann2013}. This is the main motivation for incorporating 
-clumping into our model.
-
-Implementing a treatment of clumping is challenging, for
-two main reasons. First, the physical scale lengths and density contrasts 
-in AGN outflows are not well-constrained from observations.  
-Second, there are significant computational difficulties associated with adequately
-resolving and realistically modelling a series of small scale, high density
-regions with a MCRT code. 
+quasar and AGN outflows {\bf \citep[e.g.][]{junk1983,weymann1985,hamann2013}}. 
+This is the main motivation for incorporating clumping into our model.
+
+{\bf Deciding on how to implement clumping into our existing wind models was not straightforward.
+First, and most importantly, the physical scale lengths and density contrasts in AGN outflows are not well-constrained from observations or theory.
+As a result, while one could envision in principle, clouds with a variety of sizes and density contrasts varying perhaps as function of radius, there would have been very little guidance on how to set nominal values of the various parameters of such a model.}
+Second, there are significant computational difficulties associated with adequately resolving and realistically modelling a series of small scale, high density regions with a MCRT
+{\bf -- or for that matter, a hydrodynamical --} code. 
 Given the lack of knowledge about the actual type of clumping, we have adopted
-a simple approximation
-used successfully in stellar wind modelling, known as 
+a simple approximation used successfully in stellar wind modelling, known as 
 {\em microclumping} \citep[e.g.][]{hamann1998,hilliermiller1999,hamann2008}.
+
 The underlying assumption of microclumping is that clump sizes are much smaller than the 
 typical photon mean free path, and thus the clumps are 
-both geometrically and optically thin. This approach 
-allows one to introduce a `volume filling factor', $f_V$. 
-The intra-clump medium is assumed to be a vacuum, so the 
-density of the clumps is then multiplied by the ``density enhancement'' 
+both geometrically and optically thin. {\bf This approach 
+allows one to treat clumps only in terms of their volume filling factor, $f_V$, 
+instead of having to specify separately their size and density distributions.
+In our model, $f_V$ is independent of position (see section~4.4).
+The inter-clump medium is assumed to be unimportant in determining the emergent
+spectrum, and is therefore modeled as a vacuum,
+although the outflow is still non-porous and axisymmetric.}
+The density of the clumps is multiplied by the ``density enhancement'' 
 $D=1/f_V$. Opacities, $\kappa$, and emissivities, $\epsilon$, 
@@
 such as collisional excitation or recombination, will increase by a factor of $D$.
-
 In our models, the temperature is not fixed, and is instead set by balancing heating and 
@@
 (thermal line emission).
+
+{\bf 
+The smallest scale length in a MCRT model such as this is normally the Sobolev length, given by
+\begin{equation}
+l_S = \frac{v_{th}}{| dv/ds |}
+\end{equation}
+This is typically $\sim10^{13}$~cm near the disc plane, increasing outwards.
+We use the mean density to calculate the Sobolev optical depth, which assumes that
+$l_S$ is greater than the typical clump size.
+Thus for the microclumping assumption to be formally correct, 
+clumps should be no larger than $\sim10^{12}$~cm.
+This size scale is not unreasonable for quasar outflows, as
+\cite{dekool1995} suggest that BAL flows may have low filling factors with
+clump sizes of $\sim10^{11}$~cm. }
+% An additional concern with this approach to clumping is that the clumps
+% may rapidly cool and expand into the inter-clump medium. This is a well-known
+% issue in BLR and outflow models (REFs), and requires some kind of confining mechanism,
+% such as magnetic confinement \cite[e.g.][]{dekool1995}. Alternatively, as already discussed,
+% the LDI may cause clumpy flows as expected in stellar winds.}
+
 Our clumping treatment is necessarily simple; it does not adequately
 represent the complex substructures and stratifications in ionization
-state we expect in AGN outflows. Nevertheless, this parameterization allows simple estimates
-of the effect clumping has on the ionization state and emergent 
-line emission.
+state we expect in AGN outflows. 
+Nevertheless, this parameterization 
+allows simple estimates of the effect clumping has on the ionization 
+state and emergent line emission.
 
@@
 
-{\bf This extreme $89^\circ$ viewing angle cannot represent a typical quasar within a unified model, as
-extreme inclinations should be extremely underrepresented in quasar samples due to the
-compton-thick absorber or `Torus' expected at high inclinations ().}
-However, this spectrum does show that a model such as this can 
+{\bf The $89^\circ$ viewing angle cannot represent a typical quasar within a unified model, as
+extreme inclinations should be extremely underrepresented in quasar samples.
+This is in part due to the compton-thick absorber or `torus' 
+expected at high inclinations \cite[e.g.][]{antonucci1985,martinez2007}.
+However, this spectrum does show that a wind model can
 naturally reproduce quasar emission lines if the emissivity of the wind is 
@@
 In addition, it neatly demonstrates how a stratified outflow can naturally
-reproduce the range of ionization states seen in quasars.
+reproduce the range of ionization states seen in quasars.}
 
@@
 
-\subsection{X-ray Properties}
-\label{sec:xray}
-
 \begin{figure*}
@@
 \end{figure*}
+
+\subsection{X-ray Properties}
+\label{sec:xray}
 
@@
 low ionization species.
+
 There is also a correlation between the strength of LoBAL features
@@
 to briefly explore how specialised this model is, and how small parameter
-changes can affect the synthetic spectra. Fig.~\ref{fig:grid}
-shows the EW at a low inclination, and $BI$ at a high inclination for the simulation
-grid. A few conclusions can be drawn from this plot straight away. 
-First, we find that almost all the models with $f_V=0.1$ are over-ionized, and 
-fail to produce strong \civ\ BALs or emission lines. Second, we find that 
-it is difficult to significantly increase line emission while
-keeping the luminosity and mass loss rate of the system fixed. 
+changes can affect the synthetic spectra. {\bf Fig.~\ref{fig:grid}
+shows the EW for} \civline\ {\bf and} \mgline\ {\bf at a low inclination, 
+and $BI$ for} \civline\ {\bf at a high inclination for the simulation
+grid. We find that almost all the models with $f_V=0.1$ are over-ionized, and 
+fail to produce strong} \civ\ {\bf BALs or emission lines. However, 
+the models with $f_V=0.01$ generally produce} \civ\ {\bf BALs and emission lines.
+The fiducial model is representative of this family of models and 
+the spectra are generally similar, although it is clear from the figure
+that we have selected a model near the upper end of the EW distributions.
+
+We find that it is difficult to significantly increase line emission while
+keeping the luminosity and mass loss rate of the system fixed.}
 We show an additional point on figure 7 corresponding to a model with an order of
@@
 \begin{enumerate}
-\item Clumping moderates the ionization state
+\item Clumping the wind with a volume filling factor of $0.01$ 
+moderates the ionization state
 sufficiently to allow for the 
@@
 Balmer emission lines and a Balmer recombination continuum in the optical spectrum, but this
-is only really significant at high inclination where to continuum is suppressed.  
+is only really significant at high inclination where the continuum is suppressed.  
 \smallskip
@@
 CK also acknowledges a Leverhulme fellowship.
-{\bf We would like to thank the anonymous referee for an insightful
+{\bf We would like to thank the anonymous referee for a helpful
 and constructive report.}

### 2016-01-28 paper.tex
nearly ready to submit

@@
 \begin{abstract} 
-Various unification schemes interpret the complex phenomenology of quasars and 
-luminous active galactic nuclei (AGN) in terms of a simple picture involving a 
-central black hole, an accretion disc and an associated outflow. Here, we continue
-our tests of this paradigm by comparing quasar spectra to synthetic spectra of 
-biconical disc wind models, produced with our state-of-the-art Monte Carlo radiative 
-transfer code. Previously, we have shown that we could produce synthetic spectra 
-resembling those of observed broad absorption line (BAL) quasars, but only if the 
-X-ray luminosity was limited to 10$^{43}$~erg~s$^{-1}$. 
-{\bf Here, we introduce a simple treatment of clumping, and find that a volume filling factor of $\sim0.01$ 
+Various unification schemes interpret the complex phenomenology of quasars and luminous active galactic nuclei (AGN) in terms of a simple picture involving a central black hole, an accretion disc and an associated outflow.
+Here, we continue our tests of this paradigm by comparing quasar spectra to synthetic spectra of biconical disc wind models, produced with our state-of-the-art Monte Carlo radiative transfer code.
+Previously, we have shown that we could produce synthetic spectra resembling those of observed broad absorption line (BAL) quasars, but only if the X-ray X-ray luminosity was limited to 10$^{43}$~erg~s$^{-1}$.
+ {\bf Here, we introduce a simple treatment of clumping, and find that a filling factor of $\sim0.01$ 
 moderates the ionization state sufficently for BAL features to form in the 
-rest-frame UV at more realistic X-ray luminosities.}
-Our fiducial model shows good agreement with X-ray properties of AGN and the dense, 
-X-ray heated wind produces strong line emission in, e.g., \la\ and \civline\ at low inclinations. 
-At high inclinations, the synthetic spectra possess prominent LoBAL features. 
-Despite these successes, we cannot reproduce all the emission lines seen in quasar 
-spectra with the correct equivalent-width ratios, and we find an angular dependence of 
-emission-line equivalent width despite the remarkable similarities in the observed emission 
-line properties of BAL and non-BAL quasars. Overall, our work suggests that a biconical wind 
-can reproduce much of the qualitative behaviour expected from a unified model, but we cannot 
-yet provide quantitative matches with quasar properties at all viewing angles. Whether disc 
-winds can successfully unify quasars is therefore still an open question.
+rest-frame UV at more realistic X-ray luminosities.} Our fiducial model shows good agreement with AGN X-ray properties and the wind produces strong line emission in, e.g., \la\ and \civline\ at low inclinations.
+At high inclinations, the spectra possess prominent LoBAL features.
+Despite these successes, we cannot reproduce all emission lines seen in quasar spectra with the correct equivalent-width ratios, and we find an angular dependence of emission-line equivalent width despite the similarities in the observed emission line properties of BAL and non-BAL quasars.
+Overall, our work suggests that biconical winds can reproduce much of the qualitative behaviour expected from a unified model, but we cannot yet provide quantitative matches with quasar properties at all viewing angles.
+Whether disc winds can successfully unify quasars is therefore still an open question.
 \end{abstract}
@@
 follows \cite{SV93}, and is described further by
-LK02, H13 and M15. A schematic is shown in Fig.~\ref{fig:cartoon},
+LK02, H13 and M15. {\bf We emphasise that the purpose of this
+purely kinematic wind model is to provide a simple tool for 
+exploring different outflow geometries and kinematics, and
+the model itself is not hydrodynamic.}
+A schematic is shown in Fig.~\ref{fig:cartoon},
 with key aspects marked. The general biconical
@@
 The poloidal velocity along each individual streamline at a poloidal distance $l$ 
-is then given by
+is then given by \citep[e.g.][]{rybickihummer1978}
 \begin{equation}
@@
 In our model, $f_V$ is independent of position (see section~4.4).
-The inter-clump medium is assumed to be unimportant in determining the emergent
-spectrum, and is therefore modeled as a vacuum,
-although the outflow is still non-porous and axisymmetric.}
+The inter-clump medium is modeled as a vacuum,
+although the outflow is still non-porous and axisymmetric.
+This approach therefore assumes that the inter-clump medium
+is unimportant in determing the output spectrum, which
+we expect to be true only when density constrasts are large and
+the inter-clump medium is both very ionized and of low emissivity and opacity.
+}
 The density of the clumps is multiplied by the ``density enhancement'' 
@@
 {\bf 
-The smallest scale length in a MCRT model such as this is normally the Sobolev length, given by
+The shortest length scale in a Sobolev MCRT treatment such as ours 
+is normally the Sobolev length, given by
 \begin{equation}

### 2016-02-01 paper.tex
updating figures

@@
 purely kinematic wind model is to provide a simple tool for 
-exploring different outflow geometries and kinematics, and
-the model itself is not hydrodynamic.}
+exploring different outflow geometries and kinematics.}
 A schematic is shown in Fig.~\ref{fig:cartoon},

### 2016-02-01 generate/angles/angle_plot.py

@@ -244,7 +244,7 @@ def BALnicity ( nu_line, nu_array, spec_array):
 #name = "../specs/checkvol_a6"
 name = "../specs/grid10/nextgen_a05"
 name = "../specs/webgrid/run6_thmin70_rmin50_a0p6_rv1e19_f0p01.spec"
-name = "../specs/webgrid/run5_thmin70_rmin50_a0p5_rv1e19_f0p01.spec"
+name = "../../../runs/referee_m16/rerun_adiab/run42_thmin70_rmin50_a0p5_rv1e19_f0p01.spec"
 s = r.read_spectrum(name)
 make_c4_plot(s, name)
 

### 2016-02-01 generate/uvspec/new_uvspec_fig.py

@@ -24,6 +24,7 @@ PYTHON = os.environ["PYTHON"]
 
 namea = "grid11/nextgen%s" % suffix
 namea = "../specs/webgrid/run5_thmin70_rmin50_a0p5_rv1e19_f0p01.spec"
+namea = "../../../runs/referee_m16/rerun_adiab/run42_thmin70_rmin50_a0p5_rv1e19_f0p01.spec"
 #nameb = "../specs/grid11/nextgen_uv"
 namec = "asi_thmin70_rmin50_a1_f0p01_mdotw5"
 #namec = "asi_thmin70_rmin50_a0p75_f0p01_mdotw5"

### 2016-02-01 generate/wind_plot/link_8.py

@@ -46,7 +46,7 @@ xuse= np.append(x1000,1e19)
 print x1000, y1000
 
 
-root = "run64_thmin70_rmin50_a0p5_rv1e19_f0p01"
+root = "run42_thmin70_rmin50_a0p5_rv1e19_f0p01"
 d = r.read_pywind_summary(root)
 
 

### 2016-02-01 paper.tex
final version

@@
 Previously, we have shown that we could produce synthetic spectra resembling those of observed broad absorption line (BAL) quasars, but only if the X-ray X-ray luminosity was limited to 10$^{43}$~erg~s$^{-1}$.
- {\bf Here, we introduce a simple treatment of clumping, and find that a filling factor of $\sim0.01$ 
+Here, we introduce a simple treatment of clumping, and find that a filling factor of $\sim0.01$ 
 moderates the ionization state sufficently for BAL features to form in the 
-rest-frame UV at more realistic X-ray luminosities.} Our fiducial model shows good agreement with AGN X-ray properties and the wind produces strong line emission in, e.g., \la\ and \civline\ at low inclinations.
+rest-frame UV at more realistic X-ray luminosities.
+Our fiducial model shows good agreement with AGN X-ray properties and the wind produces strong line emission in, e.g., \la\ and \civline\ at low inclinations.
 At high inclinations, the spectra possess prominent LoBAL features.
@@
 An additional or alternative solution is that the wind is clumped 
-{\bf \citep[e.g.][]{junk1983,weymann1985,hamann2013}}
+\citep[e.g.][]{junk1983,weymann1985,hamann2013}
 possibly on multiple scale lengths. Local density enhancements could lower the 
@@
 \citep{krolik1981, emmering1992, dekool1995, cassidyraine1996}.
-{\bf 
 \cite{krolik1981} showed that BLR clouds would be short-lived, suggesting 
@@
 wings of emission lines formed in these line-driven flows 
-\citep{hillier1991eswingsmodel}.}
+\citep{hillier1991eswingsmodel}.
 Complex substructures are also produced in simulations of line-driven 
@@
 which are reprocessed by `macro-atoms' with associated transition probabilities.
-{\bf We use the Sobolev approximation \citep[e.g.][]{sobolev1957,sobolev1960,rybickihummer1978}
-to compute the location and optical depth of line interactions}.
+We use the Sobolev approximation \citep[e.g.][]{sobolev1957,sobolev1960,rybickihummer1978}
+to compute the location and optical depth of line interactions.
 In our case, for reasons of computational efficiency, we adopt the  hybrid macro-atom scheme 
@@
 calculating the thermal balance of the plasma (see H13).
-{\bf Adiabatic cooling in the cell is calculated using the estimator
+Adiabatic cooling in the cell is calculated using the estimator
 \begin{equation}
@@
 where $C_{tot}$ is the sum over all cooling rates in the cell.
-}
 
@@
 follows \cite{SV93}, and is described further by
-LK02, H13 and M15. {\bf We emphasise that the purpose of this
+LK02, H13 and M15. The purpose of this
 purely kinematic wind model is to provide a simple tool for 
-exploring different outflow geometries and kinematics.}
+exploring different outflow geometries.
 A schematic is shown in Fig.~\ref{fig:cartoon},
@@
 \cite{elvis2000} to explain the phenomenonology
-of quasars and BALQSOs. {\bf However, we do not include the initial
+of quasars and BALQSOs. However, we do not include the initial
 vertical component present in the Elvis (2000) model, which was
-invoked as a qualitative explanation for narrow absorption lines}.
+invoked as a qualitative explanation for narrow absorption lines.
 
@@
 A clumpy outflow offers a possible solution to the so-called `over-ionization problem' in 
-quasar and AGN outflows {\bf \citep[e.g.][]{junk1983,weymann1985,hamann2013}}. 
+quasar and AGN outflows \citep[e.g.][]{junk1983,weymann1985,hamann2013}. 
 This is the main motivation for incorporating clumping into our model.
 
-{\bf Deciding on how to implement clumping into our existing wind models was not straightforward.
+Deciding on how to implement clumping into our existing wind models was not straightforward.
 First, and most importantly, the physical scale lengths and density contrasts in AGN outflows are not well-constrained from observations or theory.
-As a result, while one could envision in principle, clouds with a variety of sizes and density contrasts varying perhaps as function of radius, there would have been very little guidance on how to set nominal values of the various parameters of such a model.}
+As a result, while one could envision in principle, clouds with a variety of sizes and density contrasts varying perhaps as function of radius, there would have been very little guidance on how to set nominal values of the various parameters of such a model.
 Second, there are significant computational difficulties associated with adequately resolving and realistically modelling a series of small scale, high density regions with a MCRT
-{\bf -- or for that matter, a hydrodynamical --} code. 
+-- or for that matter, a hydrodynamical -- code. 
 Given the lack of knowledge about the actual type of clumping, we have adopted
@@
 typical photon mean free path, and thus the clumps are 
-both geometrically and optically thin. {\bf This approach 
+both geometrically and optically thin. This approach 
 allows one to treat clumps only in terms of their volume filling factor, $f_V$, 
@@
 the inter-clump medium is both very ionized and of low emissivity and opacity.
-}
 The density of the clumps is multiplied by the ``density enhancement'' 
@@
 
-{\bf 
 The shortest length scale in a Sobolev MCRT treatment such as ours 
@@
 \cite{dekool1995} suggest that BAL flows may have low filling factors with
-clump sizes of $\sim10^{11}$~cm. }
+clump sizes of $\sim10^{11}$~cm.
 % An additional concern with this approach to clumping is that the clumps
@@
 
-\begin{figure*}
-\centering
-\includegraphics[width=1.0\textwidth]{figures/fig5.eps}
-\caption
-{
-Synthetic spectra at two viewing angles, 
-this time in frequency space and including the optical band,
-compared to the non-BAL SDSS quasar composite. The spectra are normalised to the flux at 
-$2000$\AA, then an offset of 2 is applied per spectrum for clarity -- the dotted lines show the zero point of $F_\nu / F_{2000}$ in each case.
-}
-\label{fig:sed}
-\end{figure*}
-
 \noindent
@@
 
+\begin{figure*}
+\centering
+\includegraphics[width=1.0\textwidth]{figures/fig5.eps}
+\caption
+{
+Synthetic spectra at two viewing angles, 
+this time in frequency space and including the optical band,
+compared to the non-BAL SDSS quasar composite. The spectra are normalised to the flux at 
+$2000$\AA, then an offset of 2 is applied per spectrum for clarity -- the dotted lines show the zero point of $F_\nu / F_{2000}$ in each case.
+}
+\label{fig:sed}
+\end{figure*}
+
 \begin{table}
@@
 
-{\bf The $89^\circ$ viewing angle cannot represent a typical quasar within a unified model, as
+The $89^\circ$ viewing angle cannot represent a typical quasar within a unified model, as
 extreme inclinations should be extremely underrepresented in quasar samples.
@@
 In addition, it neatly demonstrates how a stratified outflow can naturally
-reproduce the range of ionization states seen in quasars.}
+reproduce the range of ionization states seen in quasars.
 
@@
 
+\subsection{X-ray Properties}
+\label{sec:xray}
+
 \begin{figure*}
@@
 
-\subsection{X-ray Properties}
-\label{sec:xray}
-
 The main motivation for adding clumping to the model was
@@
 \centering
-\includegraphics[width=0.8\textwidth]{figures/fig7.eps}
+\includegraphics[width=1.0\textwidth]{figures/fig7.eps}
 \caption
@@
 \end{figure*}
-
-At high inclinations, the synthetic spectra exhibit blue-shifted BALs in \al\ and \mg --
-the absorption lines seen in LoBALQSOs, and we even see absorption in Fe~\textsc{ii}
-at the highest inclinations. Line profiles in velocity space 
-for \civ, \al\ and \mg, are shown in Fig.~\ref{fig:lobal} for a range
-of BALQSO viewing angles. We find that ionization stratification
-of the wind causes lower ionization material to have a smaller covering factor, 
-as demonstrated by figures~\ref{fig:wind} and \ref{fig:lobal}.
-This confirms the behaviour expected from a unification model such as Elvis (2000). 
-LoBALs are only present at viewing angles close to edge-on ($i>75^\circ$),
-as predicted by polarisation results \citep{brotherton1997}.
-As observed in a BALQSO sample by \cite{filizak2014}, we find that
-BAL troughs are wider and deeper when low ionization absorption features are present,
-and high ionization lines have higher blue-edge velocities than the 
-low ionization species.
-
-There is also a correlation between the strength of LoBAL features
-and the amount of continuum attenuation at that sightline, particularly
-blueward of the Lyman edge as the low ionization base 
-intersects the line-of-sight. 
-A model such as this therefore predicts that LoBALQSOs and FeLoBALQSOs 
-have stronger Lyman edge absorption and 
-are more Compton-thick than HiBALQSOs and Type 1 quasars.
-An edge-on scenario also offers a potential explanation for the rarity of LoBAL and
-FeLoBAL quasars, due to a foreshortened and attenuated continuum, 
-although BAL fraction inferences are fraught with complex selection 
-effects \citep{goodrich1997,krolikvoit1998}.
-
-\subsection{Parameter Sensitivity}
-
-\label{sec:param_sens}
 
@@
 
+At high inclinations, the synthetic spectra exhibit blue-shifted BALs in \al\ and \mg --
+the absorption lines seen in LoBALQSOs, and we even see absorption in Fe~\textsc{ii}
+at the highest inclinations. Line profiles in velocity space 
+for \civ, \al\ and \mg, are shown in Fig.~\ref{fig:lobal} for a range
+of BALQSO viewing angles. We find that ionization stratification
+of the wind causes lower ionization material to have a smaller covering factor, 
+as demonstrated by figures~\ref{fig:wind} and \ref{fig:lobal}.
+This confirms the behaviour expected from a unification model such as Elvis (2000). 
+LoBALs are only present at viewing angles close to edge-on ($i>75^\circ$),
+as predicted by polarisation results \citep{brotherton1997}.
+As observed in a BALQSO sample by \cite{filizak2014}, we find that
+BAL troughs are wider and deeper when low ionization absorption features are present,
+and high ionization lines have higher blue-edge velocities than the 
+low ionization species.
+
+There is also a correlation between the strength of LoBAL features
+and the amount of continuum attenuation at that sightline, particularly
+blueward of the Lyman edge as the low ionization base 
+intersects the line-of-sight. 
+A model such as this therefore predicts that LoBALQSOs and FeLoBALQSOs 
+have stronger Lyman edge absorption and 
+are more Compton-thick than HiBALQSOs and Type 1 quasars.
+An edge-on scenario also offers a potential explanation for the rarity of LoBAL and
+FeLoBAL quasars, due to a foreshortened and attenuated continuum, 
+although BAL fraction inferences are fraught with complex selection 
+effects \citep{goodrich1997,krolikvoit1998}.
+
+\subsection{Parameter Sensitivity}
+
+\label{sec:param_sens}
+
 Having selected an individual fiducial model from the simulation grid, it is important
 to briefly explore how specialised this model is, and how small parameter
-changes can affect the synthetic spectra. {\bf Fig.~\ref{fig:grid}
-shows the EW for} \civline\ {\bf and} \mgline\ {\bf at a low inclination, 
-and $BI$ for} \civline\ {\bf at a high inclination for the simulation
+changes can affect the synthetic spectra. Fig.~\ref{fig:grid}
+shows the EW for \civline\ and \mgline\ at a low inclination, 
+and $BI$ for \civline\ at a high inclination for the simulation
 grid. We find that almost all the models with $f_V=0.1$ are over-ionized, and 
-fail to produce strong} \civ\ {\bf BALs or emission lines. However, 
-the models with $f_V=0.01$ generally produce} \civ\ {\bf BALs and emission lines.
+fail to produce strong \civ\ BALs or emission lines. However, 
+the models with $f_V=0.01$ generally produce \civ\ BALs and emission lines.
 The fiducial model is representative of this family of models and 
@@
 We find that it is difficult to significantly increase line emission while
-keeping the luminosity and mass loss rate of the system fixed.}
+keeping the luminosity and mass loss rate of the system fixed.
 We show an additional point on figure 7 corresponding to a model with an order of
@@
 CK also acknowledges a Leverhulme fellowship.
-{\bf We would like to thank the anonymous referee for a helpful
-and constructive report.}
+We would like to thank the anonymous referee for a helpful
+and constructive report.
 We would like to thank Omer Blaes, Ivan Hubeny and Shane Davis for their
@@
 %% \texttt{mn2e.cls} \textsc{Latex} document class. 
-
+\setlength{\bibsep}{0pt}
 \bibliography{bibs/mybib.bib,bibs/stellar.bib,bibs/h14.bib,bibs/h13.bib,bibs/hamann.bib,bibs/krolik.bib}

### 2016-02-01 paperbold.tex
added paperbold
final version

--- 2016-02-01 paper.tex
@@
 follows \cite{SV93}, and is described further by
-LK02, H13 and M15. {\bf We emphasise that the purpose of this
+LK02, H13 and M15. {\bf The purpose of this
 purely kinematic wind model is to provide a simple tool for 
-exploring different outflow geometries and kinematics.}
+exploring different outflow geometries.}
 A schematic is shown in Fig.~\ref{fig:cartoon},
@@
 \subsubsection{Broad emission lines (`quasar-like' angles)}
+
+\begin{figure*}
+\centering
+\includegraphics[width=1.0\textwidth]{figures/fig5.eps}
+\caption
+{
+Synthetic spectra at two viewing angles, 
+this time in frequency space and including the optical band,
+compared to the non-BAL SDSS quasar composite. The spectra are normalised to the flux at 
+$2000$\AA, then an offset of 2 is applied per spectrum for clarity -- the dotted lines show the zero point of $F_\nu / F_{2000}$ in each case.
+}
+\label{fig:sed}
+\end{figure*}
 
@@
 \end{figure*}
-
-\subsection{X-ray Properties}
-\label{sec:xray}
 
@@
 \label{fig:lobal}
+\end{figure*}
+
+\begin{figure*}
+\centering
+\includegraphics[width=1.0\textwidth]{figures/fig8.eps}
+\caption
+{
+The EW of the \civ~$1550$\AA\ line at $20^\circ$ plotted against a) the 
+$BI$ of \civ~$1550$\AA\ at $75^\circ$, b) the EW of the \mg~$2800$\AA\ line 
+at $20^\circ$ and c) the EW of \la\ at $20^\circ$. The circles correspond 
+to the simulation grid for two different values of $f_V$, and the fiducial 
+model is marked with an orange star. 
+We also show a higher X-ray luminosity model and a higher mass loss rate
+with a red star.
+}
+\label{fig:grid}
 \end{figure*}
@@
 \label{sec:param_sens}
-
-\begin{figure*}
-\centering
-\includegraphics[width=1.0\textwidth]{figures/fig8.eps}
-\caption
-{
-The EW of the \civ~$1550$\AA\ line at $20^\circ$ plotted against a) the 
-$BI$ of \civ~$1550$\AA\ at $75^\circ$, b) the EW of the \mg~$2800$\AA\ line 
-at $20^\circ$ and c) the EW of \la\ at $20^\circ$. The circles correspond 
-to the simulation grid for two different values of $f_V$, and the fiducial 
-model is marked with an orange star. 
-We also show a higher X-ray luminosity model and a higher mass loss rate
-with a red star.
-}
-\label{fig:grid}
-\end{figure*}
 

### 2016-02-08 paper.tex
modded paper

@@
 Here, we continue our tests of this paradigm by comparing quasar spectra to synthetic spectra of biconical disc wind models, produced with our state-of-the-art Monte Carlo radiative transfer code.
-Previously, we have shown that we could produce synthetic spectra resembling those of observed broad absorption line (BAL) quasars, but only if the X-ray X-ray luminosity was limited to 10$^{43}$~erg~s$^{-1}$.
+Previously, we have shown that we could produce synthetic spectra resembling those of observed broad absorption line (BAL) quasars, but only if the X-ray
+luminosity was limited to 10$^{43}$~erg~s$^{-1}$. 
 Here, we introduce a simple treatment of clumping, and find that a filling factor of $\sim0.01$ 
@@
 described by M15. In this scheme, the energy packets interact with either two-level 
-`simple atoms' or full macro-atoms. 
+`simple-atoms' or full macro-atoms. 
 This allows one to treat non-LTE line transfer in radiative equilibrium
@@
 calculate the ionization fractions
-of simple-ions. As part of  this effort, we have 
+of simple-atoms. As part of  this effort, we have 
 now improved {\sc PYTHON} to explicitly solve the 
@@
 As in M15, we use a dilute Boltzmann approximation to calculate 
-the populations of levels for simple-ions. This dilute approximation 
+the populations of levels for simple-atoms. This dilute approximation 
 is not required for macro-atom levels.
@@
 We include  free-free, bound-free and bound-bound heating
-and cooling processes in the model. For radiative transfer purposes
+and cooling processes in the model. 
+For radiative transfer purposes
 we treat electron scattering in the Thomson limit, 
@@
 calculating the thermal balance of the plasma (see H13).
-Adiabatic cooling in the cell is calculated using the estimator
+Adiabatic cooling in a cell is calculated using the estimator
 \begin{equation}
@@
 where $V$ is the cell volume, $T_e$ is the electron temperature,
-$n_e$ is the electron density, $N_j$ is the number density of ion $j$
+$n_e$ is the electron density, $N_i$ is the number density of ion $i$
 and $\nabla \cdot v$ is the divergence of the 
@@
 included in the simulation.
-For consistency, $k$-packets then have a finite 
-destruction probability of 
+For consistency, $k$-packets then have a destruction probability of 
 \begin{equation}
@@
 \subsection{Atomic Data}
-
-We use the same atomic data  described by LK02 as updated by H13 and M15, 
-with the addition of direct (collisional) ionization and recombination
-data from \cite{dere2007}. 
+We use the same atomic data  described by LK02 as updated by H13 and M15.
+As in M15, macro-atom level information comes from \textsc{Topbase} \citep{cunto1993}.
+H and He~\textsc{ii} are treated with 10 levels, and we include one He~\textsc{i} 
+level. This is because He is almost always completely ionized 
+and so He~\textsc{i} is unimportant in the simulation.
+% with the addition of direct (collisional) ionization and recombination
+% data from \cite{dere2007}. 
 Photoionization cross-sections are from \textsc{Topbase} \citep{cunto1993} and \cite{vfky}.
-%Dielectronic and 
-Radiative recombination rate coefficients are taken from 
+Dielectronic and Radiative recombination rate coefficients for simple-atoms are taken from 
 the \textsc{Chianti} database version 7.0 \citep{dere1997,landi2012}.
@@
 \smallskip
-\item The synthetic spectra show \la\ line and weak He~\textsc{ii}~$1640$\AA\ line
+\item The synthetic spectra show a \la\ line and weak He~\textsc{ii}~$1640$\AA\ line
 as a result of our improved treatment of recombination using macro-atoms. We also see

### 2016-02-08 paper.tex
removed atomic data sentence

@@
 We use the same atomic data  described by LK02 as updated by H13 and M15.
-As in M15, macro-atom level information comes from \textsc{Topbase} \citep{cunto1993}.
-H and He~\textsc{ii} are treated with 10 levels, and we include one He~\textsc{i} 
-level. This is because He is almost always completely ionized 
-and so He~\textsc{i} is unimportant in the simulation.
-% with the addition of direct (collisional) ionization and recombination
-% data from \cite{dere2007}. 
+As in M15, macro-atom level information is from \textsc{Topbase} \citep{cunto1993}.
 Photoionization cross-sections are from \textsc{Topbase} \citep{cunto1993} and \cite{vfky}.

### 2016-02-08 paper.tex
modded names

@@
 \parbox[t]{\textwidth}{
-James~H.~Matthews$^1$\thanks{jm8g08@soton.ac.uk}, Christian~Knigge$^1$, 
-Knox~S.~Long$^2$, Stuart~A.~Sim$^3$, Nick~Higginbottom$^1$ and Sam~W.~Mangham$^1$
+J.~H.~Matthews$^1$\thanks{jm8g08@soton.ac.uk}, C.~Knigge$^1$, 
+K.~S.~Long$^2$, S.~A.~Sim$^3$, N.~Higginbottom$^1$ and S.~W.~Mangham$^1$
 }

### 2016-02-08 paper.tex
cleaned layout slightly
changing bib formats
added accepted slug
preparing bib for arxiv
sufficiently has an i...

@@
 
-\date{\today}
-
+\date{Accepted 8 February 2016. Received 8 February 2016; in original form 23 December 2015}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Here, we introduce a simple treatment of clumping, and find that a filling factor of $\sim0.01$ 
-moderates the ionization state sufficently for BAL features to form in the 
+moderates the ionization state sufficiently for BAL features to form in the 
 rest-frame UV at more realistic X-ray luminosities.
@@
 material may be required.
-\smallskip
+\bigskip
 \item The line EWs in the synthetic spectra increase with inclination.
@@
 \setlength{\bibsep}{0pt}
-\bibliography{bibs/mybib.bib,bibs/stellar.bib,bibs/h14.bib,bibs/h13.bib,bibs/hamann.bib,bibs/krolik.bib}
+\bibliography{paper.bbl}
 
